### 2020-06-12 output_scripts/Paper_Plots.Rmd
add previous analysis scripts

---
title: "Plots for Latent Hawkes Paper"
author: "Owen G. Ward"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/", echo = FALSE, include = FALSE,
                     message=FALSE)
# setting these to false to only show updates
knitr::opts_chunk$set(message = FALSE)
```

```{r, load_packages, include=FALSE}

# don't write to this path
orig_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"

new_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_orig_code/"

func_dir <- "C:/Users/owenw/Dropbox/with Owen/code/part2/lib/"

library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(bayesplot)
library(viridis)
library(compete)
library(colorspace)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

```

```{r more_setup}
#data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"
jing_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"
plot_path = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/"

```

```{r,echo=FALSE,include=FALSE}
full_data <- readRDS("C:/Users/owenw/Dropbox/with Owen/code/part2/data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
out <- captureOutput(for(current_cohort in fit_cohorts){
  naive_rank_10[[current_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[current_cohort]]])
  expert_rank_10[[current_cohort]] <- expertRankHierarchy(full_data[[cohort_names[current_cohort]]])
})

```

```{r define_functions}
model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})

model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
                  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})

```

The aim of this notebook is a way to quickly and efficiently create all the plots
required for this paper. We will currently build them using the refit version of Jing's fit,
which ignored windows with no events (to confirm we can recreate that exactly).

```{r}
data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"
```

# Figure 2: Contour Plot and C-HP Diagnostics

This is not effected by the final model.

## Figure 2a: Contour Plot

```{r}
current_cohort <- 1
png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
z.func <- function(x,y){
  return(x*y*eta1_mean*exp(-eta2_mean*abs(x-y))/(1+exp(-eta3_mean*(y-x))))
  # this is because axes are flipped that we have y-x in last term
  #return(x*y*eta1_mean/(1+exp(eta2_mean*abs(x-y)-eta3_mean*(y-x))))
}
z_plot <- outer(seq(1,0,-0.01),  
                seq(0,1,0.01), 
                z.func)
my.image.plot(seq(0,1,0.01), seq(0,1,0.01), z_plot,
              xlab=expression(f[j]),ylab=expression(f[i]),
              my.main="(a)", cex.main=2.3, 
              cex.lab=2.5, xLabels=c(1,0), yLabels=c(0,1))
dev.off()

my.image.plot(seq(0,1,0.01), seq(0,1,0.01), z_plot,
              xlab=expression(f[j]),ylab=expression(f[i]),
              my.main="(a)", cex.main=2.3, 
              cex.lab=2.5, xLabels=c(1,0), yLabels=c(0,1))

```

## Fig 2b: C-HP Diagnostics

This is using the correct form of the compensator for a Hawkes process.

```{r,echo=FALSE}
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
f_est <- apply(sim_cohort_hp$f,2,mean)
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
                   observe=list(observe.id),
                   observe.length=list(observe.time),
                   no.events=list(no.events))
unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])

ks.stat.matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
n_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
Lambda_matrix <- matrix(list(),nrow=mice_number,ncol=mice_number)
for(k in 1:mice_number){
  for(l in c(1:mice_number)[-k]){
    i<-expert_rank_10[[current_cohort]][k]
    j<-expert_rank_10[[current_cohort]][l]
    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
    if(length(pair)>0){
      param_mean <- list(lambda0=mean(sim_cohort_hp$lambda0),
                         alpha=model1_fn$alpha.fun(f_est[i],f_est[j],
                                                   eta1_mean,eta2_mean,eta3_mean),
                         beta=mean(sim_cohort_hp$beta))
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_Lambda <- numeric(0)
      for(cur in c(1:length(current_window_vec))){ ## check length > 2
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator==i&
                                          return_df$recipient==j&
                                          return_df$observe.id==cur_win,"event.times"][[1]]
        current_obs_time <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                                        return_df$observe.id==cur_win,"observe.time"]
        Lambda_vec <- uniHawkesCompensator(object=param_mean, events=c(current_event_time,current_obs_time))
        all_Lambda <- c(all_Lambda,Lambda_vec)
        n_matrix[i,j] <- n_matrix[i,j] + length(current_event_time)
      }
      if(length(all_Lambda)>0){
        ks.stat.matrix[i,j] <-  ks.test(all_Lambda,"pexp",rate=1/mean(all_Lambda))$statistic
        Lambda_matrix[i,j][[1]] <- all_Lambda
      }
    }
  }
}

png(paste(plot_path,"/diagonsis_model1_",cohort_names[current_cohort],".png",sep=''),
    width=480,height=480)
# -------------- KS plot (stat)
col.vec <- cRamp(as.vector(ks.stat.matrix))
## need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
#order(as.vector(ks.stat.matrix),method = "")

values <- as.vector(ks.stat.matrix)
sorted_vals <- sort(ks.stat.matrix)
#match(values,sorted_vals)
col.vec.vir <- vir_cols[match(values,sorted_vals)]

####
par(oma = c(6,4,4,1), mar=rep(0,4),
    mgp = c(0, .2, 0))
layout(cbind(matrix(data=c(1:(12*12)), nrow=12, ncol=12, byrow = TRUE),rep(12*12+1,12)), 
       widths=c(rep(1,12),2), heights=rep(1,12))
for(i in expert_rank_10[[current_cohort]]){
  for(j in expert_rank_10[[current_cohort]]){
    if(ks.stat.matrix[i,j]==0){
      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], border = 0, col = 'white')
    }else{
      Lambda.test <- Lambda_matrix[i,j][[1]]
      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
            ylab="",xlab="",axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
            ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
      plot(ecdf(Lambda.test), add=TRUE, do.points=FALSE, verticals=TRUE,col="red", lwd=2)
    }
  }
}
par(mar = c(0,2,0,3),mgp=c(0,0.8,0))

col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)),length.out = 100),
                col.vec = viridis(100))

temp <- cLegend(as.vector(ks.stat.matrix))
#which(temp$x.vec == as.vector(ks.stat.matrix))
## need to adjust this for the legend also.
# image(1, cLegend(as.vector(ks.stat.matrix))$x.vec,
#       matrix(data=cLegend(as.vector(ks.stat.matrix))$x.vec, 
#              ncol=length(cLegend(as.vector(ks.stat.matrix))$x.vec),nrow=1),
#       col=cLegend(as.vector(ks.stat.matrix))$col.vec,
#       xlab="",ylab="",axes=FALSE)
image(1, col_obj$x.vec,
      matrix(data=col_obj$x.vec, 
             ncol=length(col_obj$x.vec),nrow=1),
      col=col_obj$col.vec,
      xlab="",ylab="",axes=FALSE)
axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1,
     cex.axis=2.4)

mtext(text=expert_rank_10[[current_cohort]], side=1, line=1.8, outer=TRUE, cex=1.8,
      at=1/14*c(1:12)-1/22)
mtext(text=expert_rank_10[[current_cohort]], side=2, line=0.5, outer=TRUE, cex=1.8,
      at=1/12*c(12:1)-1/20, las=2)
mtext(text="(b)", side=3, line=1.4, outer=TRUE, cex=2.2,
      at=0.45, font=2)
dev.off()
```

# Figure 3: Comparison of C-HP and C-DCHP

## Figure 3a: Baseline rates

```{r}
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
gamma_mean <- apply(sim_cohort_dchp$gamma,2,mean)
zeta_mean <- apply(sim_cohort_dchp$zeta,2,mean)

# social matrix plot
latent_social_matrix <- gamma_mean%*%t(rep(1,mice_number))+rep(1,mice_number)%*%t(zeta_mean)

png(paste(plot_path,"/lambda0_",cohort_names[current_cohort],".png",sep=''),
    width=400, height=300)
matrixPlotParameter(latent_social_matrix[rev(expert_rank_10[[current_cohort]]),expert_rank_10[[current_cohort]]],
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),title="(a)")
mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
      at=1/17.8*seq(2,12,2)+0.09)
dev.off()
```
## Figure 3b: Ranking Comparison

```{r}
current_cohort <- 1
colors_plot <- viridis(2)
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
    width=400, height=300)
par(oma = c(0,0,2,0), mar = c(3,4,1,1),mgp=c(0,0.5,0))
plot(order(expert_rank_10[[current_cohort]]),
     apply(sim_cohort_hp$f,2,mean),pch=16,cex=1.2,
     #col= "steelblue", 
     col = colors_plot[1],
     ylab="",xlab="",
     xlim=c(1,12.5),ylim=c(0,1), xaxt="n", yaxt="n")
segments(order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)-apply(sim_cohort_hp$f,2,sd),
         order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)+apply(sim_cohort_hp$f,2,sd),
         #col= add.alpha("steelblue",0.8),lwd=2)
         col = add.alpha(colors_plot[1],0.8), lwd =2)
points(order(expert_rank_10[[current_cohort]])+0.2,
       apply(sim_cohort_dchp$f,2,mean),
       pch=16,cex=1.2,
       col=colors_plot[2])
       #col="goldenrod2")
segments(order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)-apply(sim_cohort_dchp$f,2,sd),
         order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)+apply(sim_cohort_dchp$f,2,sd),
         col= add.alpha(colors_plot[2],0.8),lwd=2)
         #col= add.alpha("goldenrod2",0.8),lwd=2)

axis(BELOW<-1, at=1:12, labels=expert_rank_10[[current_cohort]], cex.axis=1.3, tck=-0.015)
mtext(text=11, side=1, line=0.5, cex=1.3, at=6)

axis(LEFT <-2, at=seq(0,1,0.2), labels=seq(0,1,0.2), las= HORIZONTAL<-1,
     cex.axis=1.3, tck=-0.015)
mtext(side=1, text="I&SI rank", line=1.8, cex=1.5)
mtext(side=2, text="Latent rank", line=2.4, cex=1.6)
mtext(side=3, text="(b)", line=0.8, cex=1.6, font=2)
legend('bottomleft', legend = c("C-HP", "C-DCHP"), 
       pch = c(16, 16), lty = c(1, 1), lwd=c(2,2),
       #col=c("steelblue","goldenrod"),
       col=c(colors_plot[1],colors_plot[2]),
       cex=1.5)
dev.off()
```
# Figure 4:
To be added.

# Figure 5:
To be added.

# Figure 6: Latent Rank Cohort comparison

## Figure 6a: Rank vs I&SI

```{r}
### Rank Comparison for Single Cohort ####
current_cohort <- 1

load(paste(jing_data_path,cohort_names[current_cohort],
           "/agg_rank_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

no_method <- 4
plot_latent_df <- data.frame(Methods=rep(1:no_method,each=1000*mice_number),
                             Mice=rep(rep(1:mice_number,each=1000),no_method),
                             force=rep(0,1000*mice_number*no_method))
## agg
plot_latent_df$force[(1:(1000*mice_number))] <- as.vector(sim_agg_rank$x[1001:2000,])

## M1
plot_latent_df$force[(1:(1000*mice_number))+1000*mice_number] <- as.vector(sim_cohort_hp$f)

## M2
plot_latent_df$force[(1:(1000*mice_number))+2000*mice_number] <- as.vector(sim_cohort_dchp$f)

## M3
plot_latent_df$force[(1:(1000*mice_number))+3000*mice_number] <- as.vector(sim_cohort_mmhp$f)

plot_latent_df$Mice <- factor(plot_latent_df$Mice,
                              levels = expert_rank_10[[current_cohort]])
plot_latent_df$Method <- factor(plot_latent_df$Method,
                                labels = c("AggRanking","C-HP","C-DCHP","C-MMHP"))

png(paste(plot_path,"real_rank_one_cohort.png",sep=""),width=600,height=300)

p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(4))+
  #scale_fill_manual(values = c("gray", "steelblue", "goldenrod2" , "firebrick2")) + 
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 11),
        legend.position="none") +
  facet_grid(cols=vars(Method)) +
  xlab("Mice (ranked by I&SI method)") + 
  ylab("Latent rank")
p1
dev.off()
p1
beepr::beep()
```
## Figure 6b: Spearman rank correlation

Not completed. This would need the rankings to be
rerun for all cohorts.

# Figure 7: Pearson residual matrices

Here is where I need to be a bit more careful about using the correct fits.
Currently using all from Jing's saved output.

In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices.

```{r}
current_cohort <- 1

m1_residual_matrix_lst <- list()
m2_residual_matrix_lst <- list()
m3_residual_matrix_lst <- list()
mmhp_residual_matrix_lst <- list()

  print(current_cohort)
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  return_df <- cleanObservationPeriod(current_cohort, clean_data)
  unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
    summarize(count=n(),
              observe=list(observe.id),
              observe.length=list(observe.time),
              no.events=list(no.events))
  unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])

  # M1
  load(paste(jing_data_path,cohort_names[current_cohort],
             "/cohort_hp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
  model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
                         eta_1=mean(sim_cohort_hp$eta_1),
                         eta_2=mean(sim_cohort_hp$eta_2),
                         eta_3=mean(sim_cohort_hp$eta_3),
                         beta=mean(sim_cohort_hp$beta),
                         f=apply(sim_cohort_hp$f,2,mean))
  model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
                                                  nrow=mice_number,ncol=mice_number),
                            alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
                                                                                      model1_par_est$eta_1,
                                                                                      model1_par_est$eta_2,
                                                                                      model1_par_est$eta_3),
                                                    model1_par_est$f),
                            beta_matrix=matrix(model1_par_est$beta,
                                               nrow=mice_number,ncol=mice_number))
  m1_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)

  for(i in 1:mice_number){
    for(j in 1:mice_number){
      pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
      if(length(pair)>0&(i!=j)){
        par_est <- lapply(model1_par_matrix, function(x) x[i,j])
        names(par_est) <- c("lambda0","alpha","beta")
        current_window_vec <- unique_pairs_df$observe[[pair]]
        all_residual <- 0
        for(cur in c(1:length(current_window_vec))){ ## check length > 2
          cur_win <- current_window_vec[cur]
          current_event_time <- return_df[return_df$initiator==i&
                                            return_df$recipient==j&
                                            return_df$observe.id==cur_win,"event.times"][[1]]
          current_obs_time <- return_df[return_df$initiator==i&
                                          return_df$recipient==j&
                                          return_df$observe.id==cur_win,"observe.time"]
          all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est,
                                                                  events=current_event_time,
                                                                  termination = current_obs_time)
        }
        m1_residual_matrix[i,j] <- all_residual
      }
    }
  }

  # M2
  load(paste(jing_data_path,cohort_names[current_cohort],
             "/cohort_dchp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
  model2_par_est <- list(gamma=apply(sim_cohort_dchp$gamma,2,mean),
                         zeta=apply(sim_cohort_dchp$zeta,2,mean),
                         eta_1=mean(sim_cohort_dchp$eta_1),
                         eta_2=mean(sim_cohort_dchp$eta_2),
                         eta_3=mean(sim_cohort_dchp$eta_3),
                         beta=mean(sim_cohort_dchp$beta),
                         f=apply(sim_cohort_dchp$f,2,mean))
  model2_par_matrix <- list(lambda0_matrix=model2_par_est$gamma%*%t(rep(1,mice_number))+
                              rep(1,mice_number)%*%t(model2_par_est$zeta),
                            alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
                                                                                      model2_par_est$eta_1,
                                                                                      model2_par_est$eta_2,
                                                                                      model2_par_est$eta_3),
                                                    model2_par_est$f),
                            beta_matrix=matrix(model2_par_est$beta,
                                               nrow=mice_number,ncol=mice_number))
  m2_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)

  for(i in 1:mice_number){
    for(j in 1:mice_number){
      pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
      if(length(pair)>0&(i!=j)){
        par_est <- lapply(model2_par_matrix, function(x) x[i,j])
        names(par_est) <- c("lambda0","alpha","beta")
        current_window_vec <- unique_pairs_df$observe[[pair]]
        all_residual <- 0
        for(cur in c(1:length(current_window_vec))){ 
          cur_win <- current_window_vec[cur]
          current_event_time <- return_df[return_df$initiator==i&
                                            return_df$recipient==j&
                                            return_df$observe.id==cur_win,"event.times"][[1]]
          current_obs_time <- return_df[return_df$initiator==i&
                                          return_df$recipient==j&
                                          return_df$observe.id==cur_win,"observe.time"]
          all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est,
                                                                  events=current_event_time,
                                                                  termination = current_obs_time)
        }
        m2_residual_matrix[i,j] <- all_residual
      }
    }
  }

```

This is too large to load at the moment again. Can do this on the cluster.

```{r, eval=FALSE}  
  # M3
  load(paste(jing_data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
  load(paste(jing_data_path,cohort_names[current_cohort],
             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
  model3_par_est <- list(lambda0=mean(sim_cohort_mmhp$lambda0),
                         lambda1=mean(sim_cohort_mmhp$lambda1),
                         eta_1=mean(sim_cohort_mmhp$eta_1),
                         eta_2=mean(sim_cohort_mmhp$eta_2),
                         eta_3=mean(sim_cohort_mmhp$eta_3),
                         beta=mean(sim_cohort_mmhp$beta),
                         f=apply(sim_cohort_mmhp$f,2,mean))
  model3_par_matrix <- list(lambda0_matrix=matrix(model3_par_est$lambda0,
                                                  nrow=mice_number,ncol=mice_number),
                            lambda1_matrix=matrix(model3_par_est$lambda1,
                                                  nrow=mice_number,ncol=mice_number),
                            alpha_matrix=formMatrix(function(x,y) model3_fn$alpha.fun(x,y,
                                                                                      model3_par_est$eta_1,
                                                                                      model3_par_est$eta_2),
                                                    model3_par_est$f),
                            beta_matrix=matrix(model3_par_est$beta,
                                               nrow=mice_number,ncol=mice_number),
                            q1_matrix=formMatrix(function(x,y) model3_fn$q1.fun(x,y,model3_par_est$eta_3),
                                                 model3_par_est$f),
                            q2_matrix=formMatrix(function(x,y) model3_fn$q0.fun(x,y,model3_par_est$eta_3),
                                                 model3_par_est$f))
  m3_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
  no_segments <- 5000 # changed from 5000
  window_pr <- c()
  for(i in 1:mice_number){
    print(i)
    for(j in 1:mice_number){
      pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
      if(length(pair)>0&(i!=j)){
        par_est <- lapply(model3_par_matrix, function(x) x[i,j])
        names(par_est) <- c("lambda0","lambda1","alpha","beta","q1","q2")
        current_window_vec <- unique_pairs_df$observe[[pair]]
        all_residual <- 0
        for(cur in c(1:length(current_window_vec))){ ## check length > 2
          cur_win <- current_window_vec[cur]
          current_event_time <- return_df[return_df$initiator==i&
                                            return_df$recipient==j&
                                            return_df$observe.id==cur_win,"event.times"][[1]]
          current_obs_time <- return_df[return_df$initiator==i&
                                          return_df$recipient==j&
                                          return_df$observe.id==cur_win,"observe.time"]
          time_segment <- seq(0,current_obs_time,length.out=no_segments)
          latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean)
          latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5) 
          est.intensity <- mmhpIntensityNumeric(params=par_est,
                                                t=current_event_time,
                                                time.vec=time_segment,
                                                latent.vec=latent_mean)
          est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time,
                                                        latent_z=latent_event)
          all_residual <- all_residual + sum(1/sqrt(est.intensity.events))-
            sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])
          # print(sum(1/sqrt(est.intensity.events))-
          #         sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1]))
          # print(summary(latent_mean))
          # window_pr <- c(window_pr,sum(1/sqrt(est.intensity.events))-
          #                  sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1]))
        }
        m3_residual_matrix[i,j] <- all_residual
      }
    }
  }

```  
These are in part 1 of the thesis folder on Google Drive.

```{r, eval=FALSE}
ind_mmhp_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part1/real_data/"
  # Independent MMHP
  load(paste(ind_mmhp_data_path, cohort_names[current_cohort], 
             "/sep_mmhp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
  load(paste(ind_mmhp_data_path,cohort_names[current_cohort],
             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))

  mmhp_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
  for(i in 1:mice_number){
    print(i)
    for(j in 1:mice_number){
      pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
      if(length(pair)>0&(i!=j)){
        par_est <- list(lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
                        lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
                        alpha=mean(sim_mmhp_sep$alpha[,pair]),
                        beta=mean(sim_mmhp_sep$beta[,pair]),
                        q1=mean(sim_mmhp_sep$q1[,pair]),
                        q2=mean(sim_mmhp_sep$q2[,pair]))
        current_window_vec <- unique_pairs_df$observe[[pair]]
        all_residual <- 0
        for(cur in c(1:length(current_window_vec))){ ## check length > 2
          cur_win <- current_window_vec[cur]
          current_event_time <- return_df[return_df$initiator==i&
                                            return_df$recipient==j&
                                            return_df$observe.id==cur_win,"event.times"][[1]]
          current_obs_time <- return_df[return_df$initiator==i&
                                          return_df$recipient==j&
                                          return_df$observe.id==cur_win,"observe.time"]
          time_segment <- seq(0,current_obs_time,length.out=no_segments)
          latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean)
          latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5) 
          est.intensity <- mmhpIntensityNumeric(params=par_est,
                                                t=current_event_time,
                                                time.vec=time_segment,
                                                latent.vec=latent_mean)
          est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time,
                                                        latent_z=latent_event)
          all_residual <- all_residual + sum(1/sqrt(est.intensity.events))-
            sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])
        }
        mmhp_residual_matrix[i,j] <- all_residual
      }
    }
  }
  m1_residual_matrix_lst[[current_cohort]] <- m1_residual_matrix
  m2_residual_matrix_lst[[current_cohort]] <- m2_residual_matrix
  m3_residual_matrix_lst[[current_cohort]] <- m3_residual_matrix
  mmhp_residual_matrix_lst[[current_cohort]] <- mmhp_residual_matrix

save(m1_residual_matrix_lst, m2_residual_matrix_lst, m3_residual_matrix_lst, mmhp_residual_matrix_lst,
     file = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/pearson_residual_cohort9.RData")
beepr::beep()
```
These would need to be rerun correctly and saved.
For now using an *old* version.

```{r}
load("C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/pearson_residual_cohort9.RData")
png(paste(plot_path,"real_residual_matrix_one_cohort.png",sep=""),width = 800,height = 400)
matrix_lst_plot <- list(
                        mmhp_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                        m1_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-63,max=63,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,legend.mar=c(0.5,.5,0.5,0.95),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-60,-30,0,30,60), out.title="", fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,2))
dev.off()
```
The remaining plot code seems to mostly be in `PaperPlots.R`.

# Figure 8

## Figure 8a: Frobenius norm of interaction predictions, single cohort

## Figure 8b: Same plot aggregated for all cohorts

# Figure 9

## Figure 9a: Predicted Spearman rank for single cohort

## Figure 9b: Predicted Spearman rank for all cohorts

# Figure 10

### 2020-06-12 output_scripts/Prior_Specification.Rmd
add previous analysis scripts

---
title: "Priors for Latent Hawkes"
author: "Owen G. Ward"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

This notebook is to explore prior specifications on the estimated latent fit.

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/", echo = FALSE, include = FALSE,
                     message=FALSE)
# setting these to false to only show updates
knitr::opts_chunk$set(message = FALSE)

```

First load in required packages and set some useful paths. 
I shouldn't be writing to anything here.

```{r, include=FALSE}

# don't write to this path
orig_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"

new_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_orig_code/"

func_dir <- "C:/Users/owenw/Dropbox/with Owen/code/part2/lib/"

library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(fields)
library(bayesplot)
library(compete)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

theme_set(theme_minimal())

```

Then we want to compare the two fits, particularly for the cohorts
which differed.

```{r,echo=FALSE}
full_data <- readRDS("C:/Users/owenw/Dropbox/with Owen/code/part2/data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
out <- captureOutput(for(current_cohort in fit_cohorts){
  naive_rank_10[[current_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[current_cohort]]])
  expert_rank_10[[current_cohort]] <- expertRankHierarchy(full_data[[cohort_names[current_cohort]]])
})

```

# Prior specification for the intensity parameters of MMHP

One concern is the choice of priors for $\lambda_0$ and $\lambda_1$, which is defined as
$\lambda_1 = w_{\lambda}\lambda_0$ for some $w_{\lambda} > 1$. The
priors are currently:

```{r, eval=FALSE}
  //priors
  lambda0 ~ lognormal(0,1);
  w_lambda ~ normal(0,2);  //lognormal
  eta_1 ~ lognormal(0,1);
  eta_2 ~ lognormal(0,1);
  eta_3 ~ lognormal(0,1);
  beta ~ normal(0,10);
  f[alpha_id] ~ normal(1,0.05);

```

We would like to consider better priors here. A more natural choice
of the priors would be `gamma` .

Perhaps most importantly is the results of the prior on the eventual latent
rankings.

## Prior 1

Here we consider

- `lambda0 ~ gamma(0.5,0.001)`
- `w_lambda ~ lognormal(0,2)`

We can examine the results of this and compare to the modified fits
for the first cohort.

```{r}
current_cohort <- 1 # testing on this cohort for now

priors_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/Prior_results/prior_1/"

refit_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"

prior_fit <- readRDS(paste(priors_path,cohort_names[current_cohort],
                         "/cohort_mmhp_stan_fit_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

prior_sim1 <- readRDS(paste(priors_path,cohort_names[current_cohort],
                         "/cohort_mmhp_stan_draws_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

fit_cohort_mmhp_re <- readRDS(paste(refit_path,cohort_names[current_cohort],
                         "/cohort_mmhp_stan_fit_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

sim_cohort_mmhp_re <- readRDS(paste(refit_path,cohort_names[current_cohort],
                         "/cohort_mmhp_stan_draws_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

# want to compare orig_data_path to the new results

# load Jing's example for this version
load(paste(orig_data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

```

Then we can compare the traceplots of both of these.

```{r}

traceplot(fit_cohort_mmhp,pars=c("lambda0","eta_1","eta_2","eta_3","beta","lambda1"))+
  ggtitle("Ignoring null counts")

traceplot(fit_cohort_mmhp_re,pars=c("lambda0","eta_1","eta_2","eta_3","beta","lambda1"))+
  ggtitle("Original priors, including null counts")

traceplot(prior_fit,
          pars=c("lambda0","eta_1","eta_2","eta_3","beta","lambda1"))+
  ggtitle("Prior 1")

```

And the corresponding rankings.

```{r}
traceplot(fit_cohort_mmhp,
          pars=c("f[1]","f[2]","f[3]","f[4]","f[5]","f[6]",
                 "f[7]","f[8]","f[9]","f[10]","f[11]","f[12]"))+
  ggtitle("Ignoring null counts")

traceplot(fit_cohort_mmhp_re,
          pars=c("f[1]","f[2]","f[3]","f[4]","f[5]","f[6]",
                 "f[7]","f[8]","f[9]","f[10]","f[11]","f[12]"))+
  ggtitle("Original priors, including null counts")

traceplot(prior_fit,
          pars=c("f[1]","f[2]","f[3]","f[4]","f[5]","f[6]",
                 "f[7]","f[8]","f[9]","f[10]","f[11]","f[12]"))+
  ggtitle("Prior 1")
```

So this actually leads to even smaller values of `lambda0`, with similar
`lambda1`, but both are still quite different from excluding the null counts.

```{r}
orig_f <-apply(sim_cohort_mmhp$f,2,mean)
refit_f <- apply(sim_cohort_mmhp_re$f,2,mean)
p1_f <- apply(prior_sim1$f,2,mean)

tibble(orig_f,refit_f,p1_f) %>%
  ggplot(aes(orig_f,refit_f)) + geom_point()

tibble(orig_f,refit_f,p1_f) %>%
  ggplot(aes(orig_f,p1_f)) + geom_point()

```

Similarly, the Pearson residual matrices for each of these fits. I only have these
for the new priors and the refits, and I can load in what Jing has saved.

## Prior 2

As a test, lets repeat with a strong prior for `lambda0`

- `lambda0 ~ gamma(1000,1000)`
- `w_lambda ~ lognormal(0,2)`

```{r}
current_cohort <- 1 # testing on this cohort for now

priors_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/Prior_results/prior_2/"

refit_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"

prior_fit <- readRDS(paste(priors_path,cohort_names[current_cohort],
                         "/cohort_mmhp_stan_fit_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

prior_sim2 <- readRDS(paste(priors_path,cohort_names[current_cohort],
                         "/cohort_mmhp_stan_draws_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

# fit_cohort_mmhp_re <- readRDS(paste(refit_path,cohort_names[current_cohort],
#                          "/cohort_mmhp_stan_fit_",
#                          cohort_names[current_cohort],
#                          ".RDS",sep = ''))
# 
# 
# # want to compare orig_data_path to the new results
# 
# # load Jing's example for this version
# load(paste(orig_data_path,cohort_names[current_cohort],
#              "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
#              ".RData",sep=''))

traceplot(fit_cohort_mmhp,pars=c("lambda0","eta_1","eta_2","eta_3","beta","lambda1"))+
  ggtitle("Ignoring null counts")

traceplot(fit_cohort_mmhp_re,pars=c("lambda0","eta_1","eta_2","eta_3","beta","lambda1"))+
  ggtitle("Original priors, including null counts")

traceplot(prior_fit,
          pars=c("lambda0","eta_1","eta_2","eta_3","beta","lambda1"))+
  ggtitle("Prior 2")

```

This doesn't work either, as it essentially seems to pull `lambda0` and
`lambda1` together.

For example, the results from prior 2 for the rankings.

```{r}
traceplot(fit_cohort_mmhp,
          pars=c("f[1]","f[2]","f[3]","f[4]","f[5]","f[6]",
                 "f[7]","f[8]","f[9]","f[10]","f[11]","f[12]"))+
  ggtitle("Original priors, ignoring null counts")

traceplot(fit_cohort_mmhp_re,
          pars=c("f[1]","f[2]","f[3]","f[4]","f[5]","f[6]",
                 "f[7]","f[8]","f[9]","f[10]","f[11]","f[12]"))+
  ggtitle("Original priors, including null counts")

traceplot(prior_fit,
          pars=c("f[1]","f[2]","f[3]","f[4]","f[5]","f[6]",
                 "f[7]","f[8]","f[9]","f[10]","f[11]","f[12]"))+
  ggtitle("Prior 2")
```

```{r}
p2_f <- apply(prior_sim2$f,2,mean)

tibble(orig_f,refit_f,p2_f) %>%
  ggplot(aes(orig_f,refit_f)) + geom_point()

tibble(orig_f,refit_f,p1_f) %>%
  ggplot(aes(orig_f,p2_f)) + geom_point()
```

## Other priors?

- What other priors could be considered here?
- Have not considered changing the priors for the `eta` parameters.

```{r plot_setup,include=FALSE}
data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"
jing_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"
plot_path = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/"

```

# Construct Pearson residuals from these fits

```{r}
# load Jing's PR_matrices

load("C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/pearson_residual_original.RData")

orig_pr <- m3_residual_matrix_lst[[1]]

# load in prior PR_matrices
priors_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/Prior_results/prior_1/"
prior1_pr <- readRDS(paste(priors_path,cohort_names[current_cohort],
                         "/cmmhp_pr_matrix_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

priors_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/Prior_results/prior_2/"
prior2_pr <- readRDS(paste(priors_path,cohort_names[current_cohort],
                         "/cmmhp_pr_matrix_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

# for orig fit, I have a copy of this somewhere also, maybe not locally

# orig_pr
# prior1_pr
```

```{r, include=FALSE}
matrix_lst_plot <- list(
                        orig_pr[rev(expert_rank_10[[current_cohort]]),
                                                  expert_rank_10[[current_cohort]]],
                        prior1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        prior2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]

                        )

myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=3,n_row=3,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-63,max=63,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,legend.mar=c(0.5,.5,0.5,0.05),
                  title_lst=list("Orig","Prior 1","Prior 2"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-60,-30,0,30,60), 
                  out.title="", fake_matrix=FALSE,
                  matrix.mar=c(1.5,1.5,1.5,1))

```

```{r,fig.width=6}
library(plot.matrix)
plot(orig_pr[rev(expert_rank_10[[current_cohort]]),
                                                  expert_rank_10[[current_cohort]]],
     main = "Original")
plot(prior1_pr[rev(expert_rank_10[[current_cohort]]),
                                                  expert_rank_10[[current_cohort]]],
     main = "Prior 1")

plot(prior2_pr[rev(expert_rank_10[[current_cohort]]),
                                                  expert_rank_10[[current_cohort]]],
     main = "Prior 2")

```

So although these priors appear to give similar results in terms of latent
rankings, the estimated MMHP parameters differ widely, leading 
to very different measures of fit.

- What about other outputs?

# Rank comparisons

```{r}

orig_f <- sim_cohort_mmhp$f

colnames(orig_f) <- paste("f_",c(1:12),sep = "")

orig_f <- as_tibble(orig_f) %>% 
  mutate(sim = row_number()) %>%
 pivot_longer(cols = starts_with("f")) 
orig_f %>%
  ggplot(aes(name,value)) + geom_boxplot() +
  ggtitle("Original Fit, no empty windows")

refit_f <- sim_cohort_mmhp_re$f

colnames(refit_f) <- paste("f_",c(1:12),sep = "")

refit_f <-as_tibble(refit_f) %>% 
  mutate(sim = row_number()) %>%
 pivot_longer(cols = starts_with("f")) 
refit_f %>%
  ggplot(aes(name,value)) + geom_boxplot() +
  ggtitle("Original Fit, with empty windows")

p1_f <- prior_sim1$f

colnames(p1_f) <- paste("f_",c(1:12),sep = "")

p1_f <-as_tibble(p1_f) %>% 
  mutate(sim = row_number()) %>%
 pivot_longer(cols = starts_with("f")) 
p1_f %>%
  ggplot(aes(name,value)) + geom_boxplot() +
  ggtitle("Prior 1")

p2_f <- prior_sim2$f

colnames(p2_f) <- paste("f_",c(1:12),sep = "")

p2_f <- as_tibble(p2_f) %>% 
  mutate(sim = row_number()) %>%
 pivot_longer(cols = starts_with("f")) 
p2_f %>%
  ggplot(aes(name,value)) + geom_boxplot() +
  ggtitle("Prior 2")

```

Plot these all in  the one plot.

```{r}
orig_f$model <- "orig"
refit_f$model <- "refit"
p1_f$model <- "p1"
p2_f$model <- "p2"

bind_rows(orig_f,refit_f,p1_f,p2_f) %>%
  ggplot(aes(name,value)) + 
  geom_boxplot(aes(colour = model))

```

So the latent rankings are somewhat similar, even if these lead to
vastly different Pearson residuals.

### 2020-06-17 output_scripts/Null_Windows.Rmd

---
title: "Null Window Correction"
author: "Owen Ward"
date: "6/17/2020"
output: html_document
---

This document briefly reviews the corrections for including empty time
windows in both fitting and evaluating the Hawkes process type models.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "C:/Users/owenw/Documents/Github_Local/MMHP_Latent/")
```

```{r setup_data, include=FALSE,message=FALSE,echo=FALSE}

# specify the path where the data is saved locally
save_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"

no_segments <- 500

library(rstan)
options(mc.cores = parallel::detectCores())

library(compete)
#library(RColorBrewer)
#library(Hmisc)
#library(wCorr)
#library(tidyverse)
library(dplyr)
#library(R.utils)
#library(fields)

source('lib/naiveRankHierarchy.R')
source('lib/expertRankHierarchy.R')
source('lib/cleanData.R') 
source('lib/prepareDataStan.R') 
source('lib/inferLatentMmhp.R')
source('lib/plotUtil.R') 
source('lib/mmhp.R')
source('lib/uniHawkes.R')
source('lib/simulatePrediction.R')
source('lib/myGlicko.R')
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
source('lib/matrixPlotParameter.R')
source('lib/residualStructureScore.R')

#### load the data ####
full_data <- readRDS("data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})

model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
                  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
for(current_cohort in fit_cohorts){
  naive_rank_10[[current_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[current_cohort]]])
  expert_rank_10[[current_cohort]] <- expertRankHierarchy(full_data[[cohort_names[current_cohort]]])
}

```

## Compare Pearson residual matrices

```{r,include=FALSE,echo=FALSE}
current_cohort <- 9
m1_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
                     "/chp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

m2_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
                     "/dchp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

m3_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
                     "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

indep_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
                     "/immhp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

```

```{r, include=FALSE,echo=FALSE}
range(m1_pr)
range(m2_pr)
range(m3_pr)
range(indep_pr)
```

Then we can plot each of these, for each cohort.

```{r}
#current_cohort <- 1
cohorts <- 1:10
cohorts <- cohorts[-3]
for(current_cohort in cohorts){
  cat("Cohort",current_cohort,"\n",sep = " ")
  m1_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
                     "/chp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

m2_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
                     "/dchp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

m3_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
                     "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

indep_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
                     "/immhp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))
matrix_lst_plot <- list(
                        indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-150,max=150,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-150,-75,0,75,150), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
                  )

}

```

Here pairs with no colour (white squares)
indicate values larger than the limits chosen. One cohort is
missing due to not fitting on the cluster in time.
The independent MMHP model now appears to be slightly better than the C-MMHP but the prediction
results shouldn't change, so overall this appears reasonable.
Also, this is using the old priors which can likely lead to a better fit.

## Predictions

For a single cohort now.

```{r}
current_cohort <- 1
load(paste(data_path,cohort_names[current_cohort],
                  "/predict_simulation_",cohort_names[current_cohort],
                  ".RData",sep=''))
```

### 2020-06-17 output_scripts/Null_Windows.Rmd
adjust color scheme for PR matrices to be red blue

@@
 library(compete)
-#library(RColorBrewer)
+library(RColorBrewer)
 #library(Hmisc)
@@
 Also, this is using the old priors which can likely lead to a better fit.
-
-## Predictions
-
-For a single cohort now.
-
-```{r}
-current_cohort <- 1
-load(paste(data_path,cohort_names[current_cohort],
-                  "/predict_simulation_",cohort_names[current_cohort],
-                  ".RData",sep=''))
-```

### 2020-06-21 output_scripts/mod_cmmhp.Rmd
beginning to investigate the properties of c-mmhp more thoroughly

---
title: "Exploring C-MMHP"
author: "Owen Ward"
output:
  html_document:
    toc: yes
    df_print: paged
    toc_float: yes
    code_folding: hide
---

<!-- The aim of this notebook is to explore some properties of the current -->
<!-- C-MMHP model to ensure it captures the correct social dynamics present -->
<!-- in animal interactions. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.height = 4,fig.width = 5)

```

```{r load_mice_data and packages, include=FALSE, echo=FALSE}
library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())

func_dir <- paste(here::here(),"/lib/",sep = "")

output_dir <- paste(here::here(),"/output/",sep = "")

orig_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"

library(tidyverse)
library(R.utils)
library(fields)
library(bayesplot)
library(compete)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

theme_set(theme_minimal())

full_data <- readRDS(paste(here::here(),"/data/mice.RData",sep = ""))
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
out <- captureOutput(for(current_cohort in fit_cohorts){
  naive_rank_10[[current_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[current_cohort]]])
  expert_rank_10[[current_cohort]] <- expertRankHierarchy(full_data[[cohort_names[current_cohort]]])
})

```

# Plot rankings against degree corrected rates

The first goal is to plot the latent ranks against the corresponding
degree corrected rate estimates for the `C-DCHP`.

```{r load_dchp,include=FALSE,echo=FALSE}
current_cohort <- 3

load(paste(orig_data_path,cohort_names[current_cohort],
         "/cohort_dchp_stan_result_",cohort_names[current_cohort],
         ".RData",sep=''))

#fit_cohort_dchp
#sim_cohort_dchp

#dim(sim_cohort_dchp$f)
mean_rank <- apply(sim_cohort_dchp$f,2,mean)

mean_gamma <- apply(sim_cohort_dchp$gamma,2,mean)
mean_zeta <- apply(sim_cohort_dchp$zeta, 2, mean)

mean_values <- tibble(mean_rank,mean_gamma,mean_zeta,
                      isi = expert_rank_10[[current_cohort]])

# mean_values %>%
#   rename(gamma_out = mean_gamma,zeta_in = mean_zeta) %>%
#   pivot_longer(cols = c(gamma_out,zeta_in),names_to = "out_in" ) %>%
#   #rename(in_out = name) %>%
#   ggplot(aes(mean_rank,value,color = out_in)) + geom_point()  +
#   labs(title = "") + theme(legend.title = element_blank())
# 
# 
# 
# mean_values %>%
#   rename(gamma_out = mean_gamma,zeta_in = mean_zeta) %>%
#   pivot_longer(cols = c(gamma_out,zeta_in),names_to = "out_in" ) %>%
#   ggplot(aes(isi,value,color =  out_in))  + geom_point()  +
#   theme(legend.title = element_blank()) +
#   scale_x_continuous(breaks = 1:12) + xlab("I&SI Ranking")

mean_values %>%
  rename(gamma_out = mean_gamma,zeta_in = mean_zeta) %>%
  pivot_longer(cols = c(gamma_out,zeta_in),names_to = "out_in" ) %>%
  mutate(out_in = as.factor(out_in)) %>%
  ggplot(aes(isi,value))  + geom_point()  +
  theme(legend.title = element_blank()) + facet_wrap(~out_in,scales="free") +
  scale_x_continuous(breaks = 1:12) + xlab("I&SI Ranking")

```

```{r}
for(current_cohort in 1:10){
  #cat(paste("Cohort ",current_cohort,sep = ""))
  load(paste(orig_data_path,cohort_names[current_cohort],
         "/cohort_dchp_stan_result_",cohort_names[current_cohort],
         ".RData",sep=''))

  mean_rank <- apply(sim_cohort_dchp$f,2,mean)

  mean_gamma <- apply(sim_cohort_dchp$gamma,2,mean)
  mean_zeta <- apply(sim_cohort_dchp$zeta, 2, mean)

  mean_values <- tibble(mean_rank,mean_gamma,mean_zeta,
                        isi = expert_rank_10[[current_cohort]])
  p1 <- mean_values %>%
    rename(gamma_out = mean_gamma,zeta_in = mean_zeta) %>%
    pivot_longer(cols = c(gamma_out,zeta_in),names_to = "out_in" ) %>%
    mutate(out_in = as.factor(out_in)) %>%
    ggplot(aes(isi,value))  + geom_point()  +
    theme(legend.title = element_blank()) + facet_wrap(~out_in,scales="free") +
    scale_x_continuous(breaks = 1:12) + xlab("I&SI Ranking") +
    ggtitle(paste("Cohort",current_cohort,sep=""))
  print(p1)

}
```

# The Limiting State

## Current Model

We wish to better understand the properties captured by the current form
of the C-MMHP model.

Currently, we have that for each pair $i,j$, $q_1^{i,j}/q_{0}^{i,j}$ is the probability 
that pair transitions out of the active/inactive state. In particular,

$$
q_1^{i,j} = \exp(-\eta_3 f_i)\hspace{1cm}   \ q_{0}^{i,j} = \exp(-\eta_3 f_j),
$$
and the limiting proportion of 
time spent in the active state is $logistic(\eta_3 (f_i-f_j))$.

To illustrate this, lets look at the this for a $f_i$.

```{r, include=FALSE,echo=FALSE,eval=FALSE}
f_i <- 0.1
f_x <- function(x) {
  (exp(-eta_3*x))/( exp(-eta_3*x) + exp(-eta_3*f_i) )
}

curve(f_x,from = 0,to = 1)
f_i

```

```{r,fig.show="hold", out.width="50%"}
f_curr <- function(x,f_i,eta_3) {
  (exp(-eta_3*x))/( exp(-eta_3*x) + exp(-eta_3*f_i) )
}

plot_limit <- function(f_i,eta_3) {
  plt <- ggplot(data.frame(x = c(0,1)),aes(x)) + 
    stat_function(fun = f_curr,
                  args = list(f_i = f_i, eta_3 = eta_3)) + 
    ylab("Limiting Proportion Active") +
    xlab("f_j (Receiver Rank)") + ggtitle(paste("f_i (Send Rank) of ",f_i,sep = ""))
  print(plt)
}

plot_limit(f_i = 0.9,eta_3 = 3)
plot_limit(f_i = 0.1,eta_3 = 3)

```

This indicates a high probability of being in the active state when the attacking mouse
is highly ranked. He is likely to fight with all mice.

When the attacking mouse is poorly ranked, there is quite a high probability he
will attack mice around him, but this is unlikely for mice ranked much higher.

## Alternative Model

We consider some alternative formulations for this limiting behaviour.

One such modification is
$$
q_1^{i,j} = f_i\exp(-\eta_3 f_i) \hspace{1cm}   \ q_{0}^{i,j} = f_j\exp(-\eta_3 f_j),
$$

```{r,fig.show="hold", out.width="50%",include=FALSE}
f_mod <- function(x,f_i,eta_3) {
  (x*exp(-eta_3*x))/( x*exp(-eta_3*x) + f_i*exp(-eta_3*f_i) )
}

plot_limit_1 <- function(f_i,eta_3) {
  plt <- ggplot(data.frame(x = c(0,1)),aes(x)) + 
    stat_function(fun = f_mod,
                  args = list(f_i = f_i, eta_3 = eta_3)) + 
    ylab("Limiting Proportion Active") +
    xlab("f_j (Receiver Rank)") + ggtitle(paste("f_i (Send Rank) of ",f_i,sep = ""))
  print(plt)
}

plot_limit_1(f_i = 0.9,eta_3 = 3)
plot_limit_1(f_i = 0.1,eta_3 = 3)

```

This does not seem appropriate, in that a dominant mouse is very unlikely 
to fight a very weak mouse. Similarly, a weak mouse is more likely to fight a strong 
mouse than an even weaker one than itself.

## Alternative 2

Another alternative is

$$
q_1^{i,j} = f_j\exp(-\eta_3 f_i) \hspace{1cm}   \ q_{0}^{i,j} = f_i\exp(-\eta_3 f_j),
$$

```{r, fig.show="hold", out.width="50%"}
f_mod_2 <- function(x,f_i,eta_3) {
  (f_i*exp(-eta_3*x))/( f_i*exp(-eta_3*x) + x*exp(-eta_3*f_i) )
}

plot_limit_2 <- function(f_i,eta_3) {
  plt <- ggplot(data.frame(x = c(0,1)),aes(x)) + 
    stat_function(fun = f_mod_2,
                  args = list(f_i = f_i, eta_3 = eta_3)) + 
    ylab("Limiting Proportion Active") +
    xlab("f_j (Receiver Rank)") + ggtitle(paste("f_i (Send Rank) of ",f_i,sep = ""))
  print(plt)
}

plot_limit_2(f_i = 0.9,eta_3 = 3)
plot_limit_2(f_i = 0.1,eta_3 = 3)

```

This looks more plausible, but is perhaps similar
(if more complex) to the first model. Here the limiting state of a weak mouse fighting
a stronger one is more likely to be inactive, which seems to be
an improvement.

# The excitation parameter

The excitation parameter is currently defined by

$$
\alpha^{i,j} = \eta_1 f_i f_j \exp(-\eta_2 |f_i-f_j|)
$$

We can look at a contour plot of this for a range of values of $f_i,f_j$,
as is currently in the paper.

```{r, contour_alpha}
f_alpha <- function(f_i,f_j,eta_1,eta_2) {
  eta_1*f_i*f_j * exp(-eta_2*abs(f_i-f_j))
}
plot_alpha <- function(f_alpha, grid_size = 0.1,eta_1 = 1,eta_2 = 1) {
  plt <- tibble(x = seq(0,1,by = grid_size),y = seq(0,1,by = grid_size)) %>%
    expand(x,y) %>%
    mutate(value = map2_dbl(x,y,f_alpha,eta_1,eta_2)) %>%
    ggplot(aes(y,x)) + geom_contour_filled(aes(z = value))  +
    scale_x_reverse()+ 
    xlab("f_j (Receive)") + ylab("f_i (Send)") + geom_abline(slope = -1, intercept = 0,
                                                             col = "red")
  print(plt)
}

plot_alpha(f_alpha,eta_1 = 3, eta_2 = 1,grid_size = 0.01)
```

This appears to capture desirable properties present in animal interactions.

We want this to take larger values when $f_i>f_j$ than when $f_i < f_j$ although it is 
hard to claim it is not symmetric currently.

### 2020-06-22 output_scripts/mod_cmmhp.Rmd
further work on the c-mmhp

@@
     code_folding: hide
+    number_sections: true
 ---
@@
 
+This does not appear to indicate any clear relationship between these degree
+corrected estimates for the out/in baseline rates and the expert
+ranking.
+
 # The Limiting State
@@
 and the limiting proportion of 
-time spent in the active state is $logistic(\eta_3 (f_i-f_j))$.
+time spent in the active state is $logistic(\eta_3 (f_i-f_j))$,
+i.e
+
+$$
+\frac{q_{0}^{i,j}}{q_{0}^{i,j}+q_1^{i,j}}  \equiv \frac{\exp(-\eta_3 f_j)}{\exp(-\eta_3 f_j)+\exp(-\eta_3 f_i)}.
+$$
 
@@
 }
-plot_alpha <- function(f_alpha, grid_size = 0.1,eta_1 = 1,eta_2 = 1) {
+plot_alpha <- function(fun = f_alpha, grid_size = 0.1,eta_1 = 1,eta_2 = 1, ...) {
   plt <- tibble(x = seq(0,1,by = grid_size),y = seq(0,1,by = grid_size)) %>%
     expand(x,y) %>%
-    mutate(value = map2_dbl(x,y,f_alpha,eta_1,eta_2)) %>%
+    mutate(value = map2_dbl(x,y,fun,eta_1,eta_2,...)) %>%
     ggplot(aes(y,x)) + geom_contour_filled(aes(z = value))  +
@@
 We want this to take larger values when $f_i>f_j$ than when $f_i < f_j$ although it is 
-hard to claim it is not symmetric currently.
+hard to claim it is not symmetric currently. This could be due to using a different
+plot function than originally used by Jing.
+
+## Incorporate the latent state
+
+We can also plot $\alpha Z(t)$, which will capture the overall structure
+which will be seen.
+
+```{r}
+
+latent_state <- function(f_i,f_j,eta_3) {
+  exp(-eta_3*f_j)/(exp(-eta_3*f_j) + exp(-eta_3*f_i)  )
+}
+
+f_alpha_z <- function(f_i,f_j,eta_1,eta_2,eta_3) {
+  eta_1*f_i*f_j * exp(-eta_2*abs(f_i-f_j)) * latent_state(f_i,f_j,eta_3)
+}
+
+plot_alpha(fun = f_alpha_z,eta_1 = 3, eta_2 = 1,grid_size = 0.01,eta_3 = 4)
+
+```
+
+This much more clearly captures the upper triangular structure we wish to have.
+
+## With modified latent state
+
+We can repeat this with the second proposed modification above, which seemed 
+to capture the dynamics well.
+
+```{r}
+
+latent_state_2 <- function(f_i,f_j,eta_3) {
+  f_i*exp(-eta_3*f_j)/(f_i*exp(-eta_3*f_j) + f_j*exp(-eta_3*f_i)  )
+}
+
+f_alpha_z <- function(f_i,f_j,eta_1,eta_2,eta_3) {
+  eta_1*f_i*f_j * exp(-eta_2*abs(f_i-f_j)) * latent_state_2(f_i,f_j,eta_3)
+}
+
+plot_alpha(fun = f_alpha_z,eta_1 = 3, eta_2 = 1,grid_size = 0.01,eta_3 = 4)
+
+```
+
+This is almost identical to the previous plot, with perhaps a slight shift when
+both $f_i$ and $f_j$ are large.

### 2020-06-22 output_scripts/New_Priors.Rmd
consider degree corrected c-mmhp

---
title: "Priors for Latent Hawkes"
author: "Owen G. Ward"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_prior/"

library(rstan)
```

```{r mice_setup,include=FALSE,echo=FALSE}
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12
```

# First Prior

To remove some of the issues with the previously specified priors,
we reparameterise `lambda1` and choose more appropriate priors
for `w_lambda,lambda0` and `beta`.

```{r eval=FALSE}

lambda1 = lambda0*(1+w_lambda);
// now w_lambda only has to be positive

//priors
lambda0 ~ gamma(0.1,1); // prior has mean 0.1, var 0.1
w_lambda ~ lognormal(0,2);
eta_1 ~ lognormal(0,1);
eta_2 ~ lognormal(0,1);
eta_3 ~ lognormal(0,1);
beta ~ lognormal(0,2);

```

## Examine `stan` diagnostics

```{r}
fit_cohorts <- 1:10
fit_cohorts <- fit_cohorts[-7]
for(current_cohort in fit_cohorts){
  print(current_cohort)
  load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
  rstan::check_hmc_diagnostics(fit_cohort_mmhp)
}

```

This leads to better results in terms of divergent transitions and
max tree depth, which were both issues previously.

## Param Histograms

We can check the traceplots/posterior distributions
based on these prior choices.

```{r}
current_cohort <- 2
print(current_cohort)
load(paste(data_path,cohort_names[current_cohort],
         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
         ".RData",sep=''))
rstan::stan_hist(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) +
  ggtitle("New Priors")
rstan::traceplot(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) + 
  ggtitle("New Priors")

```
We can similarly look at the original fits (with and without considering the windows with 
no events).

```{r}

orig_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"

new_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"

load(paste(orig_data_path,cohort_names[current_cohort],
         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
         ".RData",sep=''))

rstan::stan_hist(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) +
  ggtitle("Original, no null windows")
rstan::traceplot(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) + 
  ggtitle("Original, no null windows")

fit_cohort_mmhp <- readRDS(paste(new_data_path,cohort_names[current_cohort],
         "/cohort_mmhp_stan_fit_",cohort_names[current_cohort],
         ".RDS",sep=''))

rstan::stan_hist(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) +
  ggtitle("Original, null windows")
rstan::traceplot(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) + 
  ggtitle("Original, null windows")

```

## Latent Rankings

```{r}
p1 <-rstan::traceplot(fit_cohort_mmhp,
                 pars = c("f")) + 
  ggtitle("New Priors")

p1

```

We can compare this to the original priors (both with and excluding the null windows).

```{r}
load(paste(orig_data_path,cohort_names[current_cohort],
         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
         ".RData",sep=''))
p2 <- rstan::traceplot(fit_cohort_mmhp,
                 pars = c("f")) + 
  ggtitle("Original, no null windows")

fit_cohort_mmhp <- readRDS(paste(new_data_path,cohort_names[current_cohort],
         "/cohort_mmhp_stan_fit_",cohort_names[current_cohort],
         ".RDS",sep=''))

p3 <- rstan::traceplot(fit_cohort_mmhp,
                 pars = c("f")) + 
  ggtitle("Original, null windows")

p2
p3

```

```{r,fig.height=9}
ggpubr::ggarrange(p1,p2,p3,nrow=3)
```

These seem similar either way, and maybe tighter with these new priors.

# Lower bound on $\lambda_0$

We run into some issues with this where `w_lambda` can explode,
likely caused by extremely small draws for `lambda0`. To circumvent this
we place a lower bound on `lambda0` of 0.01 and refit this model.

```{r}
data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_p1/"

current_cohort <- 2
print(current_cohort)
load(paste(data_path,cohort_names[current_cohort],
         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
         ".RData",sep=''))
rstan::stan_hist(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) +
  ggtitle("New Priors")
rstan::traceplot(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) + 
  ggtitle("New Priors")

```

This avoids the previous issue with parameters blowing up however one chain
seems to be stuck.

```{r}
  print(current_cohort)
  load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
  rstan::check_hmc_diagnostics(fit_cohort_mmhp)
```
```{r}
p1_new <-rstan::traceplot(fit_cohort_mmhp,
                 pars = c("f")) + 
  ggtitle("New Prior, lower bound on lambda")

p1_new
```
We can compare this to the previous fit.

These fits appear to be slightly tighter overall for some cohorts, but slightly
larger for others.

```{r, fig.height=10}
ggpubr::ggarrange(p1,p1_new,nrow=2)
```

### 2020-06-22 output_scripts/New_Priors.Rmd
improved examples

@@
 ```{r}
-current_cohort <- 2
+current_cohort <- 1
 print(current_cohort)
@@
 ```
+
 We can similarly look at the original fits (with and without considering the windows with 
@@
 ```{r}
+load(paste(data_path,cohort_names[current_cohort],
+         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+         ".RData",sep=''))
+
 p1 <-rstan::traceplot(fit_cohort_mmhp,
@@
 
-current_cohort <- 2
 print(current_cohort)
@@
 ```
+
 We can compare this to the previous fit.
@@
 ```{r, fig.height=10}
+print(current_cohort)
 ggpubr::ggarrange(p1,p1_new,nrow=2)
 ```
+
+We can repeat this for another cohort.
+
+```{r, fig.height=10}
+current_cohort <- 2
+
+print(current_cohort)
+data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_prior//"
+load(paste(data_path,cohort_names[current_cohort],
+           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+           ".RData",sep=''))
+p1 <-rstan::traceplot(fit_cohort_mmhp,
+                 pars = c("f")) + 
+  ggtitle("New Prior")
+
+data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_p1/"
+load(paste(data_path,cohort_names[current_cohort],
+           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+           ".RData",sep=''))
+p1_new <-rstan::traceplot(fit_cohort_mmhp,
+                 pars = c("f")) + 
+  ggtitle("New Prior, lower bound lambda0")
+
+ggpubr::ggarrange(p1,p1_new,nrow=2)
+
+```

### 2020-06-23 output_scripts/New_Priors.Rmd

@@
 ```
+
+# Degree correction for C-MMHP
+
+```{r}
+current_cohort <- 1
+
+dc_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_dc_prior/"
+
+load(paste(dc_data_path,cohort_names[current_cohort],
+           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+           ".RData",sep=''))
+
+rstan::check_hmc_diagnostics(fit_cohort_mmhp)
+
+rstan::stan_hist(fit_cohort_mmhp,
+               pars = c("lambda0","lambda1","w_lambda",
+                        "eta_1","eta_2","eta_3","beta")) +
+  ggtitle("New Degree Corrected")
+
+rstan::traceplot(fit_cohort_mmhp,
+               pars = c("lambda0","lambda1","w_lambda",
+                        "eta_1","eta_2","eta_3","beta")) + 
+  ggtitle("New Degree Corrected")
+
+#bayesplot::rhat(fit_cohort_mmhp)
+
+rstan::traceplot(fit_cohort_mmhp,
+               pars = c("f")) + 
+  ggtitle("New Degree Corrected")
+
+```

### 2020-06-23 output_scripts/New_Priors.Rmd
investigate the degree correction

@@
 
+func_dir <- "../lib/"
+
 library(rstan)
+Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
+options(mc.cores = parallel::detectCores())
+library(tidyverse)
+library(R.utils)
+library(fields)
+library(bayesplot)
+library(compete)
+source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
+source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
+source(paste(func_dir,'cleanData.R',sep = "")) 
+source(paste(func_dir,'prepareDataStan.R',sep = "")) 
+source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
+source(paste(func_dir,'plotUtil.R',sep = "")) 
+source(paste(func_dir,'mmhp.R',sep = ""))
+source(paste(func_dir,'uniHawkes.R',sep = ""))
+source(paste(func_dir,'simulatePrediction.R',sep = ""))
+source(paste(func_dir,'myGlicko.R',sep = ""))
+source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
+source(paste(func_dir,'residualStructureScore.R',sep = ""))
+source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
+
+theme_set(theme_minimal())
 ```
@@
 mice_number <- 12
-```
 
-# First Prior
+full_data <- readRDS("../data/mice.RData")
+# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
+cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cut_off <- 3
+mice_number <- 12
 
-To remove some of the issues with the previously specified priors,
-we reparameterise `lambda1` and choose more appropriate priors
-for `w_lambda,lambda0` and `beta`.
-
-```{r eval=FALSE}
-
-lambda1 = lambda0*(1+w_lambda);
-// now w_lambda only has to be positive
-
-//priors
-lambda0 ~ gamma(0.1,1); // prior has mean 0.1, var 0.1
-w_lambda ~ lognormal(0,2);
-eta_1 ~ lognormal(0,1);
-eta_2 ~ lognormal(0,1);
-eta_3 ~ lognormal(0,1);
-beta ~ lognormal(0,2);
-
-```
-
-## Examine `stan` diagnostics
-
-```{r}
-fit_cohorts <- 1:10
-fit_cohorts <- fit_cohorts[-7]
+# Define the cohorts will be fitted
+fit_cohorts <- c(1:10)
+naive_rank_10 <- list()
+expert_rank_10 <- list()
 for(current_cohort in fit_cohorts){
-  print(current_cohort)
-  load(paste(data_path,cohort_names[current_cohort],
-           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
-  rstan::check_hmc_diagnostics(fit_cohort_mmhp)
+  naive_rank_10[[current_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[current_cohort]]])
+  expert_rank_10[[current_cohort]] <- expertRankHierarchy(full_data[[cohort_names[current_cohort]]])
 }
@@
 
-This leads to better results in terms of divergent transitions and
-max tree depth, which were both issues previously.
+<!-- # First Prior -->
 
-## Param Histograms
+<!-- To remove some of the issues with the previously specified priors, -->
+<!-- we reparameterise `lambda1` and choose more appropriate priors -->
+<!-- for `w_lambda,lambda0` and `beta`. -->
 
-We can check the traceplots/posterior distributions
-based on these prior choices.
+<!-- ```{r eval=FALSE} -->
 
-```{r}
+<!-- lambda1 = lambda0*(1+w_lambda); -->
+<!-- // now w_lambda only has to be positive -->
+
+<!-- //priors -->
+<!-- lambda0 ~ gamma(0.1,1); // prior has mean 0.1, var 0.1 -->
+<!-- w_lambda ~ lognormal(0,2); -->
+<!-- eta_1 ~ lognormal(0,1); -->
+<!-- eta_2 ~ lognormal(0,1); -->
+<!-- eta_3 ~ lognormal(0,1); -->
+<!-- beta ~ lognormal(0,2); -->
+
+<!-- ``` -->
+
+<!-- ## Examine `stan` diagnostics -->
+
+<!-- ```{r} -->
+<!-- fit_cohorts <- 1:10 -->
+<!-- fit_cohorts <- fit_cohorts[-7] -->
+<!-- for(current_cohort in fit_cohorts){ -->
+<!--   print(current_cohort) -->
+<!--   load(paste(data_path,cohort_names[current_cohort], -->
+<!--            "/cohort_mmhp_stan_result_",cohort_names[current_cohort], -->
+<!--            ".RData",sep='')) -->
+<!--   rstan::check_hmc_diagnostics(fit_cohort_mmhp) -->
+<!-- } -->
+
+<!-- ``` -->
+
+<!-- This leads to better results in terms of divergent transitions and -->
+<!-- max tree depth, which were both issues previously. -->
+
+<!-- ## Param Histograms -->
+
+<!-- We can check the traceplots/posterior distributions -->
+<!-- based on these prior choices. -->
+
+<!-- ```{r} -->
+<!-- current_cohort <- 1 -->
+<!-- print(current_cohort) -->
+<!-- load(paste(data_path,cohort_names[current_cohort], -->
+<!--          "/cohort_mmhp_stan_result_",cohort_names[current_cohort], -->
+<!--          ".RData",sep='')) -->
+<!-- rstan::stan_hist(fit_cohort_mmhp, -->
+<!--                pars = c("lambda0","lambda1","w_lambda", -->
+<!--                         "eta_1","eta_2","eta_3","beta")) + -->
+<!--   ggtitle("New Priors") -->
+<!-- rstan::traceplot(fit_cohort_mmhp, -->
+<!--                pars = c("lambda0","lambda1","w_lambda", -->
+<!--                         "eta_1","eta_2","eta_3","beta")) +  -->
+<!--   ggtitle("New Priors") -->
+
+<!-- ``` -->
+
+<!-- We can similarly look at the original fits (with and without considering the windows with  -->
+<!-- no events). -->
+
+<!-- ```{r} -->
+
+<!-- orig_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/" -->
+
+<!-- new_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/" -->
+
+<!-- load(paste(orig_data_path,cohort_names[current_cohort], -->
+<!--          "/cohort_mmhp_stan_result_",cohort_names[current_cohort], -->
+<!--          ".RData",sep='')) -->
+
+<!-- rstan::stan_hist(fit_cohort_mmhp, -->
+<!--                pars = c("lambda0","lambda1","w_lambda", -->
+<!--                         "eta_1","eta_2","eta_3","beta")) + -->
+<!--   ggtitle("Original, no null windows") -->
+<!-- rstan::traceplot(fit_cohort_mmhp, -->
+<!--                pars = c("lambda0","lambda1","w_lambda", -->
+<!--                         "eta_1","eta_2","eta_3","beta")) +  -->
+<!--   ggtitle("Original, no null windows") -->
+
+<!-- fit_cohort_mmhp <- readRDS(paste(new_data_path,cohort_names[current_cohort], -->
+<!--          "/cohort_mmhp_stan_fit_",cohort_names[current_cohort], -->
+<!--          ".RDS",sep='')) -->
+
+<!-- rstan::stan_hist(fit_cohort_mmhp, -->
+<!--                pars = c("lambda0","lambda1","w_lambda", -->
+<!--                         "eta_1","eta_2","eta_3","beta")) + -->
+<!--   ggtitle("Original, null windows") -->
+<!-- rstan::traceplot(fit_cohort_mmhp, -->
+<!--                pars = c("lambda0","lambda1","w_lambda", -->
+<!--                         "eta_1","eta_2","eta_3","beta")) +  -->
+<!--   ggtitle("Original, null windows") -->
+
+<!-- ``` -->
+
+<!-- ## Latent Rankings -->
+
+```{r, include=FALSE}
 current_cohort <- 1
-print(current_cohort)
-load(paste(data_path,cohort_names[current_cohort],
-         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
-         ".RData",sep=''))
-rstan::stan_hist(fit_cohort_mmhp,
-               pars = c("lambda0","lambda1","w_lambda",
-                        "eta_1","eta_2","eta_3","beta")) +
-  ggtitle("New Priors")
-rstan::traceplot(fit_cohort_mmhp,
-               pars = c("lambda0","lambda1","w_lambda",
-                        "eta_1","eta_2","eta_3","beta")) + 
-  ggtitle("New Priors")
-
-```
-
-We can similarly look at the original fits (with and without considering the windows with 
-no events).
-
-```{r}
-
-orig_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"
-
-new_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"
-
-load(paste(orig_data_path,cohort_names[current_cohort],
-         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
-         ".RData",sep=''))
-
-rstan::stan_hist(fit_cohort_mmhp,
-               pars = c("lambda0","lambda1","w_lambda",
-                        "eta_1","eta_2","eta_3","beta")) +
-  ggtitle("Original, no null windows")
-rstan::traceplot(fit_cohort_mmhp,
-               pars = c("lambda0","lambda1","w_lambda",
-                        "eta_1","eta_2","eta_3","beta")) + 
-  ggtitle("Original, no null windows")
-
-fit_cohort_mmhp <- readRDS(paste(new_data_path,cohort_names[current_cohort],
-         "/cohort_mmhp_stan_fit_",cohort_names[current_cohort],
-         ".RDS",sep=''))
-
-rstan::stan_hist(fit_cohort_mmhp,
-               pars = c("lambda0","lambda1","w_lambda",
-                        "eta_1","eta_2","eta_3","beta")) +
-  ggtitle("Original, null windows")
-rstan::traceplot(fit_cohort_mmhp,
-               pars = c("lambda0","lambda1","w_lambda",
-                        "eta_1","eta_2","eta_3","beta")) + 
-  ggtitle("Original, null windows")
-
-```
-
-## Latent Rankings
-
-```{r}
 load(paste(data_path,cohort_names[current_cohort],
@@
 
-We can compare this to the original priors (both with and excluding the null windows).
+<!-- We can compare this to the original priors (both with and excluding the null windows). -->
 
-```{r}
-load(paste(orig_data_path,cohort_names[current_cohort],
-         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
-         ".RData",sep=''))
-p2 <- rstan::traceplot(fit_cohort_mmhp,
-                 pars = c("f")) + 
-  ggtitle("Original, no null windows")
+<!-- ```{r} -->
+<!-- load(paste(orig_data_path,cohort_names[current_cohort], -->
+<!--          "/cohort_mmhp_stan_result_",cohort_names[current_cohort], -->
+<!--          ".RData",sep='')) -->
+<!-- p2 <- rstan::traceplot(fit_cohort_mmhp, -->
+<!--                  pars = c("f")) +  -->
+<!--   ggtitle("Original, no null windows") -->
 
-fit_cohort_mmhp <- readRDS(paste(new_data_path,cohort_names[current_cohort],
-         "/cohort_mmhp_stan_fit_",cohort_names[current_cohort],
-         ".RDS",sep=''))
+<!-- fit_cohort_mmhp <- readRDS(paste(new_data_path,cohort_names[current_cohort], -->
+<!--          "/cohort_mmhp_stan_fit_",cohort_names[current_cohort], -->
+<!--          ".RDS",sep='')) -->
 
-p3 <- rstan::traceplot(fit_cohort_mmhp,
-                 pars = c("f")) + 
-  ggtitle("Original, null windows")
+<!-- p3 <- rstan::traceplot(fit_cohort_mmhp, -->
+<!--                  pars = c("f")) +  -->
+<!--   ggtitle("Original, null windows") -->
 
-p2
-p3
+<!-- p2 -->
+<!-- p3 -->
 
-```
+<!-- ``` -->
 
-```{r,fig.height=9}
-ggpubr::ggarrange(p1,p2,p3,nrow=3)
-```
+<!-- ```{r,fig.height=9} -->
+<!-- ggpubr::ggarrange(p1,p2,p3,nrow=3) -->
+<!-- ``` -->
 
-These seem similar either way, and maybe tighter with these new priors.
+<!-- These seem similar either way, and maybe tighter with these new priors. -->
 
@@
 
-We run into some issues with this where `w_lambda` can explode,
+We have modified the current priors so that 
+$\lambda_1 = \lambda_0(1+w_{\lambda})$ with lognormal priors for
+all parameters. Now $w_{\lambda}>0$ as opposed to $>1$ previously.
+
+We ran into some issues with this where `w_lambda` can explode,
 likely caused by extremely small draws for `lambda0`. To circumvent this
 we place a lower bound on `lambda0` of 0.01 and refit this model.
+
+The resulting posterior draws are shown below for a single cohort.
 
@@
 This avoids the previous issue with parameters blowing up however one chain
-seems to be stuck.
+seems to be stuck. This doesn't occur for other cohorts, and is likely not
+a problem.
 
@@
 ```
+
+Similarly, we can look at the inferred latent ranks.
+
 ```{r}
@@
 
-We can compare this to the previous fit.
+We can compare this to the previous fit (without this lower bound).
 
@@
 
+We instead fit a degree corrected C-MMHP. Here we have
+
+$$
+\lambda_{0}^{i,j} = \gamma_i + \zeta_j
+$$
+
+for each pair. We use Laplacian priors on these (used in DC-HP). We
+can explore the resulting fits.
+
+This seems to avoid the issue with $w_{\lambda}$ taking extremely large values
+also.
+
 ```{r}
@@
 ```
+
+## Compare posterior ranks
+
+Here we plot the latent ranks in the previous section against those
+obtained with the degree correction.
+
+```{r, fig.height=10}
+current_cohort <- 1
+print(current_cohort)
+data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_p1//"
+load(paste(data_path,cohort_names[current_cohort],
+           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+           ".RData",sep=''))
+p1 <-rstan::traceplot(fit_cohort_mmhp,
+                 pars = c("f")) + 
+  ggtitle("Bound lambda0")
+
+data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_dc_prior//"
+load(paste(data_path,cohort_names[current_cohort],
+           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+           ".RData",sep=''))
+p1_new <-rstan::traceplot(fit_cohort_mmhp,
+                 pars = c("f")) + 
+  ggtitle("Degree Corrected")
+
+orig_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"
+
+load(paste(orig_data_path,cohort_names[current_cohort],
+         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+         ".RData",sep=''))
+p2 <- rstan::traceplot(fit_cohort_mmhp,
+                 pars = c("f")) +
+  ggtitle("Original, no null windows")
+
+ggpubr::ggarrange(p1,p1_new,p2,nrow=3)
+```
+
+## Plot ranks against degree parameters
+
+As before, we can also plot these inferred degree corrected rates against
+the I&SI rankings.
+
+```{r}
+cohorts <- 1:10
+#cohorts <- cohorts[c(-3,-6,-7)]
+for(current_cohort in cohorts){
+  #cat(paste("Cohort ",current_cohort,sep = ""))
+  load(paste(dc_data_path,cohort_names[current_cohort],
+         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+         ".RData",sep=''))
+
+  mean_rank <- apply(sim_cohort_mmhp$f,2,mean)
+
+  mean_gamma <- apply(sim_cohort_mmhp$gamma,2,mean)
+  mean_zeta <- apply(sim_cohort_mmhp$zeta, 2, mean)
+
+  mean_values <- tibble(mean_rank,mean_gamma,mean_zeta,
+                        isi = expert_rank_10[[current_cohort]])
+  p1 <- mean_values %>%
+    rename(gamma_out = mean_gamma,zeta_in = mean_zeta) %>%
+    pivot_longer(cols = c(gamma_out,zeta_in),names_to = "out_in" ) %>%
+    mutate(out_in = as.factor(out_in)) %>%
+    ggplot(aes(isi,value))  + geom_point()  +
+    theme(legend.title = element_blank()) + facet_wrap(~out_in,scales="free") +
+    scale_x_continuous(breaks = 1:12) + xlab("I&SI Ranking") +
+    ggtitle(paste("Cohort",current_cohort,sep=""))
+  print(p1)
+
+}
+```
+
+This seems to indicate that the degree correction is somewhat useful for 
+certain mice in providing a more expressive fit.
+
+I'm running this through for the rest of the inference (predictions,
+redisuals) at the moment.

### 2020-06-24 output_scripts/New_Priors.Rmd
lower bound for lambda0 in dc fit also

@@
 library(compete)
+library(RColorBrewer)
 source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
@@
 redisuals) at the moment.
+
+# Plot ranks from DC model against I&SI
+
+```{r}
+cohorts <- 1:10
+#cohorts <- cohorts[c(-3,-6,-7)]
+for(current_cohort in cohorts){
+  #cat(paste("Cohort ",current_cohort,sep = ""))
+  load(paste(dc_data_path,cohort_names[current_cohort],
+         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+         ".RData",sep=''))
+
+  mean_rank <- apply(sim_cohort_mmhp$f,2,mean)
+
+  mean_gamma <- apply(sim_cohort_mmhp$gamma,2,mean)
+  mean_zeta <- apply(sim_cohort_mmhp$zeta, 2, mean)
+
+  mean_values <- tibble(mean_rank,mean_gamma,mean_zeta,
+                        isi = expert_rank_10[[current_cohort]])
+  p1 <- mean_values %>%
+    #rename(gamma_out = mean_gamma,zeta_in = mean_zeta) %>%
+    #pivot_longer(cols = c(gamma_out,zeta_in),names_to = "out_in" ) %>%
+    #mutate(out_in = as.factor(out_in)) %>%
+    ggplot(aes(isi,mean_rank))  + geom_point()  +
+    # theme(legend.title = element_blank()) + facet_wrap(~out_in,scales="free") +
+    scale_x_continuous(breaks = 1:12) + xlab("I&SI Ranking") +
+    ggtitle(paste("Cohort",current_cohort,sep=""))
+  print(p1)
+
+}
+
+```
+
+## Compare these to ranks from original fit
+
+```{r}
+
+cohorts <- 1:10
+#cohorts <- cohorts[c(-3,-6,-7)]
+for(current_cohort in cohorts){
+  #cat(paste("Cohort ",current_cohort,sep = ""))
+  load(paste(dc_data_path,cohort_names[current_cohort],
+         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+         ".RData",sep=''))
+
+  mean_rank_dc <- apply(sim_cohort_mmhp$f,2,mean)
+  load(paste(orig_data_path,cohort_names[current_cohort],
+         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+         ".RData",sep=''))
+
+  mean_rank_orig <- apply(sim_cohort_mmhp$f, 2, mean)
+  mean_values <- tibble(mean_rank_dc, mean_rank_orig,
+                        isi = expert_rank_10[[current_cohort]])
+  p1 <- mean_values %>%
+    pivot_longer(cols = c(mean_rank_dc,mean_rank_orig),names_to = "model") %>%
+    mutate(model = as.factor(model)) %>%  
+    ggplot(aes(isi,value))  + 
+    geom_jitter(aes(color=model), alpha = 0.5,width = 0.1)  +
+    # theme(legend.title = element_blank()) + facet_wrap(~out_in,scales="free") +
+    scale_x_continuous(breaks = 1:12) + xlab("I&SI Ranking") +
+    ggtitle(paste("Cohort",current_cohort,sep=""))
+  print(p1)
+
+}
+
+```
+
+# Pearson Residuals for DC C-MMHP
+
+We wish to examine the effect the degree correction has on model fit in 
+terms of Pearson residuals.
+
+```{r}
+save_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"
+# the path for the result with fixes to account for the null windows
+
+dc_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_dc_prior/"
+
+#cohorts
+
+for(current_cohort in cohorts[-3]) {
+  m1_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
+                     "/chp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
+
+m2_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
+                     "/dchp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
+
+m3_pr <- readRDS(paste(dc_data_path,cohort_names[current_cohort],
+                     "/cmmhp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
+
+indep_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
+                     "/immhp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
+
+matrix_lst_plot <- list(
+                        indep_pr[rev(expert_rank_10[[current_cohort]]),
+                                                                   expert_rank_10[[current_cohort]]],
+                        m1_pr[rev(expert_rank_10[[current_cohort]]),
+                                                                 expert_rank_10[[current_cohort]]],
+                        m2_pr[rev(expert_rank_10[[current_cohort]]),
+                                                                 expert_rank_10[[current_cohort]]],
+                        m3_pr[rev(expert_rank_10[[current_cohort]]),
+                                                                 expert_rank_10[[current_cohort]]]) 
+myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
+                  xLabels=expert_rank_10[[current_cohort]],
+                  yLabels=rev(expert_rank_10[[current_cohort]]),
+                  min=-150,max=150,axis_cex=2,title_cex = 1.8,
+                  colorPalette="RdBu",if.emp=FALSE,
+                  #legend.mar=c(0.5,.5,0.5,0.5),
+                  title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
+                  #title_lst = list("I-MMHP"),
+                  col_axis=c(-150,-75,0,75,150), fake_matrix=FALSE,
+                  matrix.mar=c(2.5,2.5,2.5,1)
+                  )
+}
+
+```
+
+This does not appear any better than the standard C-MMHP.
+
+```{r}
+save_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"
+
+for(current_cohort in cohorts[-3]) {
+  m2_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
+                     "/dchp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
+
+  m3_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
+                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
+                       ".RDS",sep=''))
+
+  m3_pr_dc <- readRDS(paste(dc_data_path,cohort_names[current_cohort],
+                     "/cmmhp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
+  indep_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
+                     "/immhp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
+
+  matrix_lst_plot <- list( indep_pr[rev(expert_rank_10[[current_cohort]]),
+                                              expert_rank_10[[current_cohort]]],
+                           m2_pr[rev(expert_rank_10[[current_cohort]]),
+                                              expert_rank_10[[current_cohort]]],
+    m3_pr[rev(expert_rank_10[[current_cohort]]),
+                                              expert_rank_10[[current_cohort]]],
+                          m3_pr_dc[rev(expert_rank_10[[current_cohort]]),
+                                              expert_rank_10[[current_cohort]]]
+                          ) 
+  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
+                    xLabels=expert_rank_10[[current_cohort]],
+                    yLabels=rev(expert_rank_10[[current_cohort]]),
+                    min=-150,max=150,axis_cex=2,title_cex = 1.8,
+                    colorPalette="RdBu",if.emp=FALSE,
+                    #legend.mar=c(0.5,.5,0.5,0.5),
+                    title_lst=list("I-MMHP","DC-HP","C-MMHP","DC-C-MMHP"), 
+                    #title_lst = list("I-MMHP"),
+                    col_axis=c(-150,-75,0,75,150), fake_matrix=FALSE,
+                    matrix.mar=c(2.5,1.5,2.5,1)
+                    )
+}
+```

### 2020-06-25 output_scripts/New_Priors.Rmd
exploring fits

@@
     scale_x_continuous(breaks = 1:12) + xlab("I&SI Ranking") +
-    ggtitle(paste("Cohort",current_cohort,sep=""))
+    ggtitle(paste("DC C-MMHP Cohort",current_cohort,sep=""))
   print(p1)
@@
                      ".RDS",sep=''))
-  indep_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
-                     "/immhp_pr_matrix_",cohort_names[current_cohort],
+  m1_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
+                     "/chp_pr_matrix_",cohort_names[current_cohort],
                      ".RDS",sep=''))
 
-  matrix_lst_plot <- list( indep_pr[rev(expert_rank_10[[current_cohort]]),
+  matrix_lst_plot <- list( m1_pr[rev(expert_rank_10[[current_cohort]]),
                                               expert_rank_10[[current_cohort]]],
@@
                     #legend.mar=c(0.5,.5,0.5,0.5),
-                    title_lst=list("I-MMHP","DC-HP","C-MMHP","DC-C-MMHP"), 
+                    title_lst=list("C-HP","DC-HP","C-MMHP","DC-C-MMHP"), 
                     #title_lst = list("I-MMHP"),
@@
 ```
+
+# Investigate the Pearson Residuals further
+
+```{r}
+current_cohort <- 1
+
+m2_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
+                   "/dchp_pr_matrix_",cohort_names[current_cohort],
+                   ".RDS",sep=''))
+
+m3_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
+                     "/cmmhp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
+
+m3_pr_dc <- readRDS(paste(dc_data_path,cohort_names[current_cohort],
+                   "/cmmhp_pr_matrix_",cohort_names[current_cohort],
+                   ".RDS",sep=''))
+m1_pr <- readRDS(paste(save_data_path,cohort_names[current_cohort],
+                   "/chp_pr_matrix_",cohort_names[current_cohort],
+                   ".RDS",sep=''))
+
+max(m3_pr_dc)
+
+which(m3_pr_dc == max(m3_pr_dc),arr.ind = T)
+
+i <- 10
+j <- 1
+
+```
+Let's examine this pair further.
+
+```{r}
+
+stan_input_lst <- prepareDataStan(current_cohort)
+row_ind <- which(stan_input_lst$I_fit == i & stan_input_lst$J_fit == j)
+
+pair_events <- stan_input_lst$event_matrix[row_ind, ,]
+window_lengths <- stan_input_lst$finishing_time
+
+# this is the events between this pair
+
+load(paste(dc_data_path,cohort_names[current_cohort],
+         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+         ".RData",sep=''))
+
+fit_cohort_mmhp_dc <- fit_cohort_mmhp
+sim_cohort_mmhp_dc <- sim_cohort_mmhp
+
+load(paste(save_data_path,cohort_names[current_cohort],
+         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+         ".RData",sep=''))
+
+lambda0_pair <- mean(sim_cohort_mmhp_dc$gamma[,i]) +
+  mean(sim_cohort_mmhp_dc$zeta[,j])
+
+lambda0_pair
+
+mean(sim_cohort_mmhp$lambda0)
+
+mean(sim_cohort_mmhp_dc$f[,i]) - mean(sim_cohort_mmhp$f[,i])
+
+mean(sim_cohort_mmhp_dc$f[,j]) - mean(sim_cohort_mmhp$f[,j])
+
+# essentially no difference in the latent ranks, some differences in other parameters
+
+mean(sim_cohort_mmhp_dc$beta) - mean(sim_cohort_mmhp$beta)
+mean(sim_cohort_mmhp_dc$eta_1) - mean(sim_cohort_mmhp$eta_1)
+mean(sim_cohort_mmhp_dc$eta_2) - mean(sim_cohort_mmhp$eta_2)
+mean(sim_cohort_mmhp_dc$eta_3) - mean(sim_cohort_mmhp$eta_3)
+
+```
+
+```{r}
+pair_events <- as.data.frame(t(pair_events))
+colnames(pair_events) <- paste("wind_",c(1:ncol(pair_events)),sep = "")
+
+tidy_events <- tibble(pair_events) %>% 
+  pivot_longer(starts_with("wind"), names_to = "wind") %>%
+  filter(value > 0) %>%
+  group_by(wind) %>%
+  summarise(times = list(value)) %>%
+  mutate(wind_num = stringr::str_extract(wind, pattern = "[:digit:]+"),
+         wind_num = as.numeric(wind_num)) %>%
+  arrange(wind_num)
+
+tidy_events # this is only windows with events now
+
+windows_pair <- tibble(wind_num = 1:length(window_lengths),window_lengths)
+
+events <- windows_pair %>% left_join(tidy_events) %>% select(-wind) %>%
+  rowwise() %>%
+  mutate(num_events = length(times))
+
+```
+
+Then we need to try get the latent states for each of these windows also.
+
+```{r}
+load(paste(dc_data_path,cohort_names[current_cohort],
+         "/cmmhp_est_zt_",cohort_names[current_cohort],
+         ".RData",sep=''))
+
+latent_pair <- interpolation_array_list[[70]]
+rm(interpolation_array_list) # too big to keep around
+
+```
+
+However, the only windows with any uncertainty in their latent state, for this pair, are those where
+
+```{r}
+
+mean_state <- matrix(nrow =  length(window_lengths), ncol = no_segments)
+
+for(i in 1:length(window_lengths)) {
+  mean_state[i, ] <- apply(latent_pair[[i]], 1,var)
+}
+
+as.data.frame(mean_state)
+
+```
+
+Did this happen when not using the degree correction? It seems likely.
+
+```{r}
+load(paste(save_data_path,cohort_names[current_cohort],
+         "/cmmhp_est_zt_",cohort_names[current_cohort],
+         ".RData",sep=''))
+
+latent_pair <- interpolation_array_list[[row_ind]]
+rm(interpolation_array_list) # too big to keep around
+
+mean_state <- matrix(nrow =  length(window_lengths), ncol = no_segments)
+
+for(i in 1:length(window_lengths)) {
+  mean_state[i, ] <- apply(latent_pair[[i]], 1,mean)
+}
+
+as.data.frame(mean_state)
+```
+
+```{r}
+tibble(send = stan_input_lst$I_fit, rec = stan_input_lst$J_fit,
+       num_events = apply(stan_input_lst$Nm, 1, sum), id = row_number(stan_input_lst$I_fit)) %>%
+  arrange(desc(num_events))
+
+```
+
+Let's check from before I updated to account for empty windows.
+
+This is still to big to load locally.
+
+```{r, eval=FALSE}
+old_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/extend_stan/"
+
+current_cohort <- 1
+
+inter_array_list <- readRDS(paste(old_path,cohort_names[current_cohort],
+                                  "/cohort_mmhp_state_array_list_",
+                                  cohort_names[current_cohort],".RDS",sep = ""))
+
+pair_array <- inter_array_list[[row_ind]]
+rm(inter_array_list)
+
+dim(pair_array[[27]])
+
+```
+Let's look at a single pair from Jing's original fit.
+
+```{r}
+single_pair <- readRDS("C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/single_inter_array.RDS")
+
+dim(single_pair[[2]])
+apply(single_pair[[25]],1,var)
+
+for(i in 1:27){
+  try(cat("Mean for window ",i, " is ",
+          mean(apply(single_pair[[i]],1,mean)), "\n",sep=""))
+  try(cat("Var for window ",i, " is ",
+          mean(apply(single_pair[[i]],1,var)),"\n",sep = ""))
+}
+
+```
+We can repeat this for the previous fit also and compare.
+
+```{r}
+for(i in 1:27){
+  try(cat("Mean for window ",i, " is ",
+          mean(apply(pair_array[[i]],1,mean)), "\n",sep=""))
+  try(cat("Var for window ",i, " is ",
+          mean(apply(pair_array[[i]],1,var)),"\n",sep = ""))
+}
+
+```
+These numbers make no sense for sure.
+
+Let's compare to the current model.
+
+```{r}
+load(paste(dc_data_path,cohort_names[current_cohort],
+         "/cmmhp_est_zt_",cohort_names[current_cohort],
+         ".RData",sep=''))
+
+latent_pair <- interpolation_array_list[[69]]
+
+for(i in 1:27){
+  try(cat("Mean for window ",i, " is ",
+          mean(apply(latent_pair[[i]],1,mean)), "\n",sep=""))
+  try(cat("Var for window ",i, " is ",
+          mean(apply(latent_pair[[i]],1,var)),"\n",sep = ""))
+}
+
+```
+So a handful of windows give different results but overall there is little 
+difference, and it seems likely all of these differences are due to different
+parameters and also running less segments for each window.

### 2020-07-02 output_scripts/Diagnostics.Rmd
better explore pair level model fit

---
title: "Diagnostics Week of June 28th"
author: "Owen Ward"
date: "6/30/2020"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
    code_folding: hide
---

The aim of this script is to further investigate model fit by better diagnosttic
plots for mice pairs in a specific window.

```{r setup, include=FALSE, cache=TRUE}
knitr::opts_chunk$set(echo = TRUE)

data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_prior/"

func_dir <- "../lib/"

library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(fields)
library(bayesplot)
library(compete)
library(RColorBrewer)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

source("C:/Users/owenw/Dropbox/with Owen/code/part3/lib/intensityPlot.R")
source("C:/Users/owenw/Dropbox/with Owen/code/part3/lib/uniHawkes.R")

theme_set(theme_minimal())
```

```{r mice_setup,include=FALSE,echo=FALSE, cache=TRUE}
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
for(current_cohort in fit_cohorts){
  naive_rank_10[[current_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[current_cohort]]])
  expert_rank_10[[current_cohort]] <- expertRankHierarchy(full_data[[cohort_names[current_cohort]]])
}

```

# Correction to Pair level rates

A previous bug with C-MMHP was not correctly accounting for the degree corrected `lambda0` and corresponding
`lambda1` between each pair when interpolating the latent states and then identifying the residual matrices. 
We first want to check the effect this has.

```{r}
# output for this correction stored in output_folders/output_june_30 for c_mmhp, others haven't changed

c_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_june30/"

other_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"

cohorts <- 1:10
cohorts <- cohorts[c(-1,-3,-5,-6,-7)] # these did not run on the cluster in time

for(current_cohort in cohorts) {
  m1_pr <- readRDS(paste(other_path,cohort_names[current_cohort],
                     "/chp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

  m2_pr <- readRDS(paste(other_path,cohort_names[current_cohort],
                       "/dchp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  m3_pr <- readRDS(paste(c_mmhp_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  indep_pr <- readRDS(paste(other_path,cohort_names[current_cohort],
                       "/immhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  matrix_lst_plot <- list(
                          indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                     expert_rank_10[[current_cohort]]],
                          m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                          m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                          m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]]) 
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
                    )
}

```

# Examine Intensity and QQ Plot

To do these plots we need to compute the compensators for these models. Using the second
cohort as we have all results for it.

```{r compute diagnostics for single cohort, cache=TRUE, include=FALSE}
current_cohort <- 2
no_segments <- 500 # to run a little faster

old_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"

c_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_june30/"

clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
                   observe=list(observe.id),
                   observe.length=list(observe.time),
                   no.events=list(no.events))
unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])

## cmmhp ####
load(paste(c_mmhp_path, cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
load(paste(c_mmhp_path,cohort_names[current_cohort],
           "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))

raw_real_cmmhp_vec  <- numeric(0)
pr_real_cmmhp_vec <- numeric(0)
Lambda_cmmhp_matrix <- matrix(rep(list(),mice_number*mice_number),
                             nrow=mice_number, ncol=mice_number)

real_N_vec <- numeric(0)
#no_segments <- 500
for(i in 1:mice_number){
  print(i)
  for(j in 1:mice_number){
    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
    if(length(pair)>0&(i!=j)){
      par_est <- list(lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
                      lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
                      alpha=mean(sim_cohort_mmhp$alpha[,pair]),
                      beta=mean(sim_cohort_mmhp$beta),
                      q1=mean(sim_cohort_mmhp$q1[,pair]),
                      q2=mean(sim_cohort_mmhp$q2[,pair]))
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_rescaled_interevent <- numeric(0)
      for(cur in c(1:length(current_window_vec))){ 
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator==i&
                                          return_df$recipient==j&
                                          return_df$observe.id==cur_win,"event.times"][[1]]
        current_obs_time <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                                        return_df$observe.id==cur_win,"observe.time"]
        time_segment <- seq(0,current_obs_time,length.out=no_segments)
        latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean)
        latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5)

        ## Pearson
        est.intensity <- mmhpIntensityNumeric(params=par_est,
                                              t=current_event_time,
                                              time.vec=time_segment,
                                              latent.vec=latent_mean)
        est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time,
                                                      latent_z=latent_event)
        all_prresidual <- sum(1/sqrt(est.intensity.events))-
          sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])
        all_Lambda <- sum(est.intensity)*(time_segment[2]-time_segment[1])

        ## rescaled interevent time
        Lambda_vec <- rep(0,length(current_event_time)+1)
        temp_time_vec <- c(0,current_event_time,current_obs_time)
        for(m in 1:(length(current_event_time)+1)){
          interevent_idx <- (time_segment>=temp_time_vec[m]) & (time_segment<temp_time_vec[m+1])
          Lambda_vec[m] <- sum(est.intensity[interevent_idx])*(time_segment[2]-time_segment[1])
        }
        real_N_vec <- c(real_N_vec, length(current_event_time))
        raw_real_cmmhp_vec <- c(raw_real_cmmhp_vec,all_Lambda)
        pr_real_cmmhp_vec <- c(pr_real_cmmhp_vec,all_prresidual)
        all_rescaled_interevent <- c(all_rescaled_interevent,Lambda_vec)
      }  
      Lambda_cmmhp_matrix[i,j][[1]] <- all_rescaled_interevent
    }
  }
}

rm(interpolation_array_list)
rm(state_array_list)

## cohort hawkes ####
raw_real_c_hawkes_vec  <- numeric(0)
pr_real_c_hawkes_vec <- numeric(0)
Lambda_c_hawkes_matrix <- matrix(rep(list(),mice_number*mice_number),
                               nrow=mice_number, ncol=mice_number)

model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})

load(paste(old_data_path, cohort_names[current_cohort],
           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))

# create a list to store the hawkes parameters for this
model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
                       eta_1=mean(sim_cohort_hp$eta_1),
                       eta_2=mean(sim_cohort_hp$eta_2),
                       eta_3=mean(sim_cohort_hp$eta_3),
                       beta=mean(sim_cohort_hp$beta),
                       f=apply(sim_cohort_hp$f,2,mean))
model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
                                                nrow=mice_number,ncol=mice_number),
                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
                                                                                    model1_par_est$eta_1,
                                                                                    model1_par_est$eta_2,
                                                                                    model1_par_est$eta_3),
                                                  model1_par_est$f),
                          beta_matrix=matrix(model1_par_est$beta,
                                             nrow=mice_number,ncol=mice_number))

for(i in 1:mice_number){
  print(i)
  for(j in 1:mice_number){
    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
    if(length(pair)>0&(i!=j)){
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_rescaled_interevent <- numeric(0)
      for(cur in c(1:length(current_window_vec))){ 
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                                        return_df$observe.id==cur_win,"event.times"][[1]]
        observe_period <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                                        return_df$observe.id==cur_win,"observe.time"]
        #### update this from the stan fit
        hawkes.par <- c(model1_par_matrix$lambda0_matrix[i,j],model1_par_matrix$alpha[i,j],
                        model1_par_matrix$beta[i,j])
        # hawkes.par <- optim(par=c(1,0,100), fn=uniHawkesNegLogLik, method="CG", 
        #                     t=current_event_time, termination = observe_period)
        all_Lambda <- uniHawkesIntegralIntensity(object=list(lambda0=hawkes.par[1],
                                                              alpha=hawkes.par[2],
                                                              beta=hawkes.par[3]),
                                                  events=current_event_time,
                                                  termination = observe_period)
        all_prresidual <- uniHawkesPearsonResidual(object=list(lambda0=hawkes.par[1],
                                                              alpha=abs(hawkes.par[2]),
                                                              beta=hawkes.par[3]),
                                                  events=current_event_time,
                                                  termination = observe_period)

        ## rescaled interevent time
        Lambda_vec <- uniHawkesCompensator(lambda0=hawkes.par[1],
                                           alpha=hawkes.par[2],
                                           beta=hawkes.par[3],
                                           c(0,current_event_time))
        all_rescaled_interevent <- c(all_rescaled_interevent,Lambda_vec)
        raw_real_c_hawkes_vec <- c(raw_real_c_hawkes_vec,all_Lambda)
        pr_real_c_hawkes_vec <- c(pr_real_c_hawkes_vec,all_prresidual)
      }
      Lambda_c_hawkes_matrix[i,j][[1]] <- all_rescaled_interevent
    }
  }
}

## cohort degree corrected hawkes ####
raw_real_dc_hawkes_vec  <- numeric(0)
pr_real_dc_hawkes_vec <- numeric(0)
Lambda_dc_hawkes_matrix <- matrix(rep(list(),mice_number*mice_number),
                               nrow=mice_number, ncol=mice_number)

# model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})

load(paste(old_data_path, cohort_names[current_cohort],
           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))

# create a list to store the hawkes parameters for this
model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
                       #lambda0=mean(sim_cohort_dchp$lambda0),
                       eta_1=mean(sim_cohort_dchp$eta_1),
                       eta_2=mean(sim_cohort_dchp$eta_2),
                       eta_3=mean(sim_cohort_dchp$eta_3),
                       beta=mean(sim_cohort_dchp$beta),
                       f=apply(sim_cohort_dchp$f,2,mean))
model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
                                                model2_par_est$zeta,FUN = "+"),
                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
                                                                                    model2_par_est$eta_1,
                                                                                  model2_par_est$eta_2,
                                                                                    model2_par_est$eta_3),
                                                  model2_par_est$f),
                          beta_matrix=matrix(model2_par_est$beta,
                                             nrow=mice_number,ncol=mice_number))

for(i in 1:mice_number){
  print(i)
  for(j in 1:mice_number){
    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
    if(length(pair)>0&(i!=j)){
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_rescaled_interevent <- numeric(0)
      for(cur in c(1:length(current_window_vec))){ 
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                                        return_df$observe.id==cur_win,"event.times"][[1]]
        observe_period <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                                        return_df$observe.id==cur_win,"observe.time"]
        #### update this from the stan fit
        hawkes.par <- c(model1_par_matrix$lambda0_matrix[i,j],model1_par_matrix$alpha[i,j],
                        model1_par_matrix$beta[i,j])
        # hawkes.par <- optim(par=c(1,0,100), fn=uniHawkesNegLogLik, method="CG", 
        #                     t=current_event_time, termination = observe_period)
        all_Lambda <- uniHawkesIntegralIntensity(object=list(lambda0=hawkes.par[1],
                                                              alpha=hawkes.par[2],
                                                              beta=hawkes.par[3]),
                                                  events=current_event_time,
                                                  termination = observe_period)
        all_prresidual <- uniHawkesPearsonResidual(object=list(lambda0=hawkes.par[1],
                                                              alpha=abs(hawkes.par[2]),
                                                              beta=hawkes.par[3]),
                                                  events=current_event_time,
                                                  termination = observe_period)

        ## rescaled interevent time
        Lambda_vec <- uniHawkesCompensator(lambda0=hawkes.par[1],
                                           alpha=hawkes.par[2],
                                           beta=hawkes.par[3],
                                           c(0,current_event_time))
        all_rescaled_interevent <- c(all_rescaled_interevent,Lambda_vec)
        raw_real_dc_hawkes_vec <- c(raw_real_dc_hawkes_vec,all_Lambda)
        pr_real_dc_hawkes_vec <- c(pr_real_dc_hawkes_vec,all_prresidual)
      }
      Lambda_dc_hawkes_matrix[i,j][[1]] <- all_rescaled_interevent
    }
  }
}

# save(raw_real_hawkes_vec, pr_real_hawkes_vec,Lambda_hawkes_matrix,
#      raw_real_mmpp_vec, pr_real_mmpp_vec, Lambda_mmpp_matrix,
#      raw_real_mmhpsd_vec, pr_real_mmhpsd_vec, Lambda_mmhpsd_matrix,
#      file = "../output/real_diag_four_models.RData")
```

This is for a specific pair in a single window, we want to plot these three models.

```{r}
no_segments <- 500

current_cohort <- 5
current_i <- 8
current_j <- 2
current_win <- 13
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events))
pair <- which(unique_pairs_df$initiator==current_i&unique_pairs_df$recipient==current_j)
unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])

row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
current_event_time <- return_df[row_indicator,"event.times"][[1]]
observe_period <- return_df[row_indicator,"observe.time"]
#no_segments <- 500
time_segment <- seq(0,observe_period,length.out=no_segments)

```

Then we can plot some of these fits.

```{r plot_functions, include=FALSE}
drawRealIntensityPaper<-function(t,object=NULL,simulation=NULL,yupper=10,add=FALSE,color=1,line.width=1,
                                 title_name="",title.cex=9, y.ratio=0, min.y=0, min.x=0, max.x=NULL, 
                                 annotate.time=FALSE, event.cex=1, box.type="l", box.col="gray40", title.line=1){
  # input object: the parameter list used for generating mmhp
  #       simulation: simulation result from simulate.mmhp 
  if(t[1]>0){
    t <- c(0,t)
  }
  if(is.null(max.x)){
    max.x <- tail(t,1)
  }
  if(is.null(object)){
    termination <- tail(t,1)
    n <- length(t)
    plot(0,0,xlim=c(min.x,max.x),ylim=c(min.y,yupper*(1+y.ratio)),
         type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
    box(lty ='solid', col=box.col, lwd=0.7, bty=box.type)
    title(title_name,line=title.line,cex.main=title.cex)
    #left axes
    #axis(2,at=seq(0,yupper,5),labels=FALSE,cex.lab=2,lwd=0,lwd.ticks=1) 
    #text(-termination/50, y=seq(0,yupper,5), labels=seq(0,yupper,5), cex=1.6, srt=0, xpd=TRUE)
    #bottom axes
    # events
    points(t[-1],rep(min.y,n-1),cex=event.cex,pch=16,col="black")
  }else{
    state <- simulation$z
    state_time <- simulation$x
    if(tail(state_time,1)<tail(t,1)){
      state_time <- c(state_time,tail(t,1))
      state <- c(state,3-tail(state,1))
    }
    lambda0 <- object$lambda0
    lambda1 <- object$lambda1
    alpha <- object$alpha
    beta <- object$beta
    termination <- tail(t,1)
    n <- length(t)
    m <- length(state)
    if(is.null(min.y)){
      min.y <- -lambda0
    }
    if(is.null(max.x)){
      max.x <- termination
    }
    #plot(1,4,xlim=c(0.27,23),ylim=c(-0.5,9), type="n",xlab="Time",ylab="",xaxt="n",yaxt="n",cex.lab=1.8,bty="n")

    if(add==FALSE){
      plot(0,0,xlim=c(min.x,max.x),ylim=c(min.y,yupper*(1+y.ratio)),
           type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
      box(lty ='solid', col=box.col, lwd=0.7, bty=box.type)
      title(title_name,line=title.line,cex.main=title.cex)
      #left axes
      #axis(2,at=seq(0,yupper,5),labels=FALSE,cex.lab=2,lwd=0,lwd.ticks=1) 
      #text(-termination/50, y=seq(0,yupper,5), labels=seq(0,yupper,5), cex=1.6, srt=0, xpd=TRUE)
      #bottom axes
      if(annotate.time){
        axis(1,at=seq(0,ceiling(termination),length.out=5),labels=FALSE,cex.lab=2,lwd=0,lwd.ticks=1) #bottom axes
        text(seq(0,ceiling(termination),length.out=5), y=-y.ratio*6, cex=1.7, srt=0, xpd=TRUE,
             labels=round(seq(0,ceiling(termination),length.out=5),0))
      }
      # events
      points(t[-1],rep(min.y,n-1),cex=event.cex,pch=16,col="black")
    }

    if(m==2&state[1]==1&state_time[2]==tail(t,1)){
      drawHawkesIntensityPaper(lambda0,alpha,beta,t,color=color,
                               line.width=line.width)
    }else{
      for(i in 1:(m-1)){
        if(state[i]==1){
          hawkes_time <- t[t>=state_time[i]&t<=state_time[i+1]]
          if(i==1) hawkes_time <- hawkes_time[-1]
          history <- t[t<state_time[i]]
          # bug here
          drawHawkesIntensityPaper(lambda0 =lambda1,
                                   #i,
                                   alpha = alpha,
                                   beta = beta,
                                   #state_time[i],
                                   #state_time[i+1],
                                   #history[-1],
                                   events = hawkes_time,
                                   color=color,line.width=line.width)
        }else{
          segments(x0=state_time[i],x1=state_time[i+1], y0=lambda0,
                   lty=1,col=color,lwd=line.width)
        }
        if(i>1){
          segments(x0=state_time[i],y0=lambda0, y1=lambda1, lty=2, col=color,lwd=line.width)
        }
      }
    }
  }
}

drawHawkesIntensityPaper<-function(lambda0,alpha,beta,events,color=1,line.width=2, termination=NULL){
  # input object: parameters for Hawkes process, include lambda0, alpha, beta 
  #       events: vector of event happening time
  horizon <- tail(events,1)
  events <- events[events>0]
  N <- length(events)

  if(N==1){ # only one event condition
    segments(x0=0, x1=events[1], y0=lambda0, col=color,lwd=line.width)
    segments(x0=events[1], y0=lambda0, y1=lambda0+alpha, col=color,lwd=line.width)
    if(horizon > tail(events,1)){
      lambda.n <- function(s) lambda0+alpha*sum(exp(-beta*(s-events[1])))
      new.lambda.n<-Vectorize(lambda.n)
      curve(new.lambda.n, from=tail(events,1), to=horizon, add=TRUE, col=color,lwd=line.width)
    }
    if( !is.null(title) ) title(main=title)
  }else{
    segments(x0=0, x1=events[1], y0=lambda0, col=color,lwd=line.width)
    segments(x0=events[1], y0=lambda0, y1=lambda0+alpha, col=color,lwd=line.width)

    for(i in 1:(N-1)){
      lambda.n <- function(s) lambda0+alpha*sum(exp(-beta*(rep(s,i)-events[1:i])))
      new.lambda.n<-Vectorize(lambda.n)
      curve(new.lambda.n, from=events[i], to=events[i+1], add=TRUE, col=color,lwd=line.width)
      segments(x0=events[i+1],y0=lambda.n(events[i+1]),y1=lambda.n(events[i+1])+alpha, col=color,lwd=line.width)
    }
  }
  if(!is.null(termination)){
    lambda.n <- function(s) lambda0+alpha*sum(exp(-beta*(rep(s,N)-events[1:N])))
    new.lambda.n<-Vectorize(lambda.n)
    curve(new.lambda.n, from=events[N], to=termination, add=TRUE, col=color,lwd=line.width)
  }
}

```

```{r, fig.width=10}
#par(mfrow=c(2,5), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
#layout(matrix(1:10,nrow=2,byrow=TRUE),widths=rep(1,5),height=c(3,3))
anno.cex <- 1.3
title.cex <- 2.2
title.line <- 0.5
y.upper <- 20
## pp
lambda.pp <- 1/mean(diff(c(0,current_event_time,observe_period)))
drawRealIntensityPaper(current_event_time,
                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
                       title_name="Poisson", title.cex=title.cex, max.x=observe_period, box.col="black")
abline(h=lambda.pp,lwd=2)
mtext(side=1, text="Time", line=1.6, cex=anno.cex)
mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)

## Hawkes
hawkes.par<-optim(par=rep(1,3), fn=uniHawkesNegLogLik, method="L-BFGS-B", 
                  t=current_event_time, termination = observe_period, lower=c(0,1,0))

drawRealIntensityPaper(current_event_time,
                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
                       title_name="Hawkes", title.cex=title.cex, max.x=observe_period, box.col="black")
drawHawkesIntensityPaper(lambda0=hawkes.par$par[1],
                         alpha=hawkes.par$par[2],
                         beta=hawkes.par$par[3],
                         events=current_event_time, termination=observe_period)
mtext(side=1, text="Time", line=1.6, cex=anno.cex)
mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)
mtext(side=1, text="Time", line=1.6, cex=anno.cex)
mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)

```

This ouput is correctly dealing with the C-MMHP parameters now.

```{r load_mmhp_data, cache=TRUE}
data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_june_26/output//"

## MMHP
load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))

mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1),
                 lambda0= (mean(sim_cohort_mmhp$gamma[,current_i])+
                             mean(sim_cohort_mmhp$zeta[,current_j])),
                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
                 beta=mean(sim_cohort_mmhp$beta),
                 q1=mean(sim_cohort_mmhp$q1[,pair]),
                 q2=mean(sim_cohort_mmhp$q2[,pair]))

mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],1,function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
mmhp.est.latent <- interpolateLatentTrajectory(params=mmhp_par,events=current_event_time,zt=mmhp.est.latent,
                                               initial.state=mean(initial_state_list[[pair]][[current_win]]),
                                               termination.time=observe_period,termination.state = 2)

rm(interpolation_array_list)
rm(state_array_list)

```

```{r}
#y.upper <- 10
#title.line <- 1
#title.cex <- 0.1
drawRealIntensityPaper(current_event_time, object=mmhp_par,title.line=title.line,
                       simulation=list(x=c(0,mmhp.est.latent$x.hat),
                                       z=mmhp.est.latent$z.hat),
                       yupper=y.upper, color="black", line.width=2,
                       title_name="MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
mtext(side=1, text="Time", line=1.6, cex=anno.cex)
mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)

```

The corresponding QQ plots also.

```{r}
anno.cex <- 1
#### Hawkes
Lambda.hawkes.test <- Lambda_hawkes_matrix[current_i,current_j][[1]]

p <- ppoints(length(Lambda.hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
q <- quantile(Lambda.hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
plot(qexp(p),q, 
     xlab="",ylab="",xaxt="n",yaxt="n",
     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
mtext(side=1, text="Theoretical Quantiles", line=1.6, cex=anno.cex)
mtext(side=2, text="Empirical Quantiles", line=1.2, cex=anno.cex)
Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)

#### mmhp
Lambda.test.mmhp <- Lambda_mmhp_matrix[current_i,current_j][[1]]
p <- ppoints(length(Lambda.test.mmhp))    # 100 equally spaced points on (0,1), excluding endpoints
q <- quantile(Lambda.test.mmhp,p=p,na.rm=TRUE) # percentiles of the sample distribution
plot(qexp(p),q, 
     xlab="",ylab="",xaxt="n",yaxt="n",
     pch=1,cex=1,col="Black",ylim=c(0,max(q)),xlim=c(0,3))
mtext(side=1, text="Theoretical Quantiles", line=1.6, cex=anno.cex)
mtext(side=2, text="Empirical Quantiles", line=1.2, cex=anno.cex)
Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1)
Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1)
qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
```

### 2020-07-02 output_scripts/Diagnostics.Rmd
add the c-hp,dc-hp and c-mmhp plots for a given pair and window. need to check c-mmhp

@@
 theme_set(theme_minimal())
+
+model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
+
+c_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_june30/"
+
+other_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"
+old_data_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"
+
 ```
@@
 
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
-
 load(paste(old_data_path, cohort_names[current_cohort],
@@
         #### update this from the stan fit
-        hawkes.par <- c(model1_par_matrix$lambda0_matrix[i,j],model1_par_matrix$alpha[i,j],
-                        model1_par_matrix$beta[i,j])
+        hawkes.par <- c(model2_par_matrix$lambda0_matrix[i,j],model2_par_matrix$alpha[i,j],
+                        model2_par_matrix$beta[i,j])
         # hawkes.par <- optim(par=c(1,0,100), fn=uniHawkesNegLogLik, method="CG", 
@@
 
-```{r}
+```{r select cohort pair window}
 no_segments <- 500
 
-current_cohort <- 5
-current_i <- 8
-current_j <- 2
-current_win <- 13
+current_cohort <- 4#5
+current_i <- 2 #8
+current_j <- 8 #2
+current_win <- 42
 clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
@@
 ```{r plot_functions, include=FALSE}
-drawRealIntensityPaper<-function(t,object=NULL,simulation=NULL,yupper=10,add=FALSE,color=1,line.width=1,
-                                 title_name="",title.cex=9, y.ratio=0, min.y=0, min.x=0, max.x=NULL, 
-                                 annotate.time=FALSE, event.cex=1, box.type="l", box.col="gray40", title.line=1){
+drawRealIntensityPaper <- function(t,
+                                   object=NULL,simulation=NULL,
+                                   yupper=10,add=FALSE,color=1,line.width=1,
+                                 title_name="",title.cex=9, y.ratio=0,
+                                 min.y=0, min.x=0, max.x=NULL, 
+                                 annotate.time=FALSE,
+                                 event.cex=1, box.type="l",
+                                 box.col="gray40", title.line=1){
   # input object: the parameter list used for generating mmhp
@@
 
-drawHawkesIntensityPaper<-function(lambda0,alpha,beta,events,color=1,line.width=2, termination=NULL){
+drawHawkesIntensityPaper <- function(lambda0,alpha,beta,
+                                     events,color=1,line.width=2, termination=NULL){
   # input object: parameters for Hawkes process, include lambda0, alpha, beta 
@@
     }
-    if( !is.null(title) ) title(main=title)
+    #if( !is.null(title) ) title(main=title)
   }else{
@@
 
-```{r, fig.width=10}
-#par(mfrow=c(2,5), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
-#layout(matrix(1:10,nrow=2,byrow=TRUE),widths=rep(1,5),height=c(3,3))
-anno.cex <- 1.3
-title.cex <- 2.2
-title.line <- 0.5
+```{r plot intensity in a window, fig.width=10}
 y.upper <- 20
-## pp
-lambda.pp <- 1/mean(diff(c(0,current_event_time,observe_period)))
+title.line <- 1
+title.cex <- 1
+anno.cex <- 1
+
+## Cohort Hawkes ####
+# load the parameters for this pair
+load(paste(old_data_path, cohort_names[current_cohort],
+           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
+                       eta_1=mean(sim_cohort_hp$eta_1),
+                       eta_2=mean(sim_cohort_hp$eta_2),
+                       eta_3=mean(sim_cohort_hp$eta_3),
+                       beta=mean(sim_cohort_hp$beta),
+                       f=apply(sim_cohort_hp$f,2,mean))
+model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
+                                                nrow=mice_number,ncol=mice_number),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model1_par_est$eta_1,
+                                                                                    model1_par_est$eta_2,
+                                                                                    model1_par_est$eta_3),
+                                                  model1_par_est$f),
+                          beta_matrix=matrix(model1_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par <- c(model1_par_matrix$lambda0_matrix[current_i,current_j],
+                model1_par_matrix$alpha[current_i,current_j],
+                        model1_par_matrix$beta[current_i,current_j])
+
 drawRealIntensityPaper(current_event_time,
                        yupper=y.upper, color="black",line.width=2,title.line=title.line,
-                       title_name="Poisson", title.cex=title.cex, max.x=observe_period, box.col="black")
-abline(h=lambda.pp,lwd=2)
+                       title_name="Cohort Hawkes",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par[1],
+                         alpha=hawkes.par[2],
+                         beta=hawkes.par[3],
+                         events=current_event_time, termination=observe_period)
 mtext(side=1, text="Time", line=1.6, cex=anno.cex)
@@
 
-## Hawkes
-hawkes.par<-optim(par=rep(1,3), fn=uniHawkesNegLogLik, method="L-BFGS-B", 
-                  t=current_event_time, termination = observe_period, lower=c(0,1,0))
+#### Degree Corrected Hawkes ####
+load(paste(old_data_path, cohort_names[current_cohort],
+           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
+                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
+                       #lambda0=mean(sim_cohort_dchp$lambda0),
+                       eta_1=mean(sim_cohort_dchp$eta_1),
+                       eta_2=mean(sim_cohort_dchp$eta_2),
+                       eta_3=mean(sim_cohort_dchp$eta_3),
+                       beta=mean(sim_cohort_dchp$beta),
+                       f=apply(sim_cohort_dchp$f,2,mean))
+model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
+                                                model2_par_est$zeta,FUN = "+"),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model2_par_est$eta_1,
+                                                                                  model2_par_est$eta_2,
+                                                                                    model2_par_est$eta_3),
+                                                  model2_par_est$f),
+                          beta_matrix=matrix(model2_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
+                model2_par_matrix$alpha[current_i,current_j],
+                model2_par_matrix$beta[current_i,current_j])
 
@@
                        yupper=y.upper, color="black",line.width=2,title.line=title.line,
-                       title_name="Hawkes", title.cex=title.cex, max.x=observe_period, box.col="black")
-drawHawkesIntensityPaper(lambda0=hawkes.par$par[1],
-                         alpha=hawkes.par$par[2],
-                         beta=hawkes.par$par[3],
+                       title_name="Cohort DC-Hawkes",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par[1],
+                         alpha=hawkes.par[2],
+                         beta=hawkes.par[3],
                          events=current_event_time, termination=observe_period)
@@
 mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)
-mtext(side=1, text="Time", line=1.6, cex=anno.cex)
-mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)
+
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(sim_cohort_hp)
+rm(sim_cohort_dchp)
 
@@
 
-```{r load_mmhp_data, cache=TRUE}
-data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_june_26/output//"
-
-## MMHP
-load(paste(data_path,cohort_names[current_cohort],
+```{r draw_mmhp_fit}
+#current_cohort <- 2
+## Cohort MMHP
+load(paste(c_mmhp_path,cohort_names[current_cohort],
              "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
              ".RData",sep=''))
-load(paste(data_path,cohort_names[current_cohort],
+load(paste(c_mmhp_path,cohort_names[current_cohort],
              "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
 
-mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1),
-                 lambda0= (mean(sim_cohort_mmhp$gamma[,current_i])+
-                             mean(sim_cohort_mmhp$zeta[,current_j])),
+# then adjust the parameters for c-mmhp below here also
+
+mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
+                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
                  alpha=mean(sim_cohort_mmhp$alpha[,pair]),
@@
 
+drawRealIntensityPaper(current_event_time, object=mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,mmhp.est.latent$x.hat),
+                                       z=mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="Cohort MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+mtext(side=1, text="Time", line=1.6, cex=anno.cex)
+mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)
+
 rm(interpolation_array_list)
 rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
 
@@
 
-```{r}
+```{r, eval=FALSE}
 #y.upper <- 10
@@
 
-```{r}
+```{r, eval=FALSE}
 anno.cex <- 1

### 2020-07-03 run_scripts/c_mmhp.R
so that number of segments only specified in one place

@@ -266,7 +266,7 @@ m3_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
 
 m3_residual_array <- array(0, dim =  c(mice_number,mice_number,num_winds))
 
-no_segments <- 500 # changed from 5000
+#no_segments <- 500 # changed from 5000
 window_pr <- c()
 for(i in 1:mice_number){
   print(i)

### 2020-07-06 run_scripts/overall_predict.R
run this locally instead

@@ -3,7 +3,7 @@
 
 ### code ###
 ## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+# source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
 # ### set cohort_id based on job num
 # jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 # jobid <- as.numeric(jobid)
@@ -238,6 +238,8 @@ save(predict_day_norm_df_lst, all_cohort_norm_df, est_array_m1, est_array_m2, es
      est_array_mmhp, est_array_dsnl,
      file = paste(data_path,"plot_N_predict.RData",sep=""))
 
+
+#### everything down to here works fine ####
 
 #### Rank Prediction
 

### 2020-07-07 output_scripts/Diagnostics.Rmd
can run these plots for all cohorts now
run this locally instead
update diagnostics and paper plots

@@
     toc_float: true
-    number_sections: true
+    number_sections: FALSE
     code_folding: hide
@@
 
-The aim of this script is to further investigate model fit by better diagnosttic
-plots for mice pairs in a specific window.
-
-```{r setup, include=FALSE, cache=TRUE}
+<!-- The aim of this script is to further investigate model fit  -->
+<!-- by better diagnostic -->
+<!-- plots for mice pairs in a specific window. -->
+
+```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_prior/"
+
+data_path <- "../output/"
 
@@
 
-c_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_june30/"
-
-other_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"
-old_data_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"
+# c_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_june30/"
+# 
+# other_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"
+# old_data_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"
 
@@
 
-A previous bug with C-MMHP was not correctly accounting for the degree corrected `lambda0` and corresponding
-`lambda1` between each pair when interpolating the latent states and then identifying the residual matrices. 
-We first want to check the effect this has.
+A previous bug with C-MMHP was not correctly accounting for the degree 
+corrected `lambda0` and corresponding
+`lambda1` between each pair when interpolating the latent states and then 
+identifying the residual matrices. This gives more reasonable results for
+overall model fit in terms of the total Pearson residuals summed across all 
+observation windows.
 
 ```{r}
-# output for this correction stored in output_folders/output_june_30 for c_mmhp, others haven't changed
-
-c_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_june30/"
-
-other_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"
-
 cohorts <- 1:10
-cohorts <- cohorts[c(-1,-3,-5,-6,-7)] # these did not run on the cluster in time
 
 for(current_cohort in cohorts) {
-  m1_pr <- readRDS(paste(other_path,cohort_names[current_cohort],
+  m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                      "/chp_pr_matrix_",cohort_names[current_cohort],
@@
 
-  m2_pr <- readRDS(paste(other_path,cohort_names[current_cohort],
+  m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                        "/dchp_pr_matrix_",cohort_names[current_cohort],
@@
 
-  m3_pr <- readRDS(paste(c_mmhp_path,cohort_names[current_cohort],
+  m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                        "/cmmhp_pr_matrix_",cohort_names[current_cohort],
@@
 
-  indep_pr <- readRDS(paste(other_path,cohort_names[current_cohort],
+  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                        "/immhp_pr_matrix_",cohort_names[current_cohort],
@@
                                                                    expert_rank_10[[current_cohort]]]) 
+  cat("Cohort ",current_cohort,"\n",sep="")
   myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
@@
 
-To do these plots we need to compute the compensators for these models. Using the second
-cohort as we have all results for it.
-
-```{r compute diagnostics for single cohort, cache=TRUE, include=FALSE}
-current_cohort <- 2
-no_segments <- 500 # to run a little faster
-
-old_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"
-
-c_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_june30/"
+```{r test pairs, include=FALSE,eval=FALSE}
+current_cohort <- 1
 
@@
             no.events=list(no.events)) 
-unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
-
-## cmmhp ####
-load(paste(c_mmhp_path, cohort_names[current_cohort],
-           "/cohort_mmhp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
-load(paste(c_mmhp_path,cohort_names[current_cohort],
-           "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
-
-raw_real_cmmhp_vec  <- numeric(0)
-pr_real_cmmhp_vec <- numeric(0)
-Lambda_cmmhp_matrix <- matrix(rep(list(),mice_number*mice_number),
-                             nrow=mice_number, ncol=mice_number)
-
-real_N_vec <- numeric(0)
-#no_segments <- 500
-for(i in 1:mice_number){
-  print(i)
-  for(j in 1:mice_number){
-    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
-    if(length(pair)>0&(i!=j)){
-      par_est <- list(lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
-                      lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
-                      alpha=mean(sim_cohort_mmhp$alpha[,pair]),
-                      beta=mean(sim_cohort_mmhp$beta),
-                      q1=mean(sim_cohort_mmhp$q1[,pair]),
-                      q2=mean(sim_cohort_mmhp$q2[,pair]))
-      current_window_vec <- unique_pairs_df$observe[[pair]]
-      all_rescaled_interevent <- numeric(0)
-      for(cur in c(1:length(current_window_vec))){ 
-        cur_win <- current_window_vec[cur]
-        current_event_time <- return_df[return_df$initiator==i&
-                                          return_df$recipient==j&
-                                          return_df$observe.id==cur_win,"event.times"][[1]]
-        current_obs_time <- return_df[return_df$initiator==i&
-                                        return_df$recipient==j&
-                                        return_df$observe.id==cur_win,"observe.time"]
-        time_segment <- seq(0,current_obs_time,length.out=no_segments)
-        latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean)
-        latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5)
-
-        ## Pearson
-        est.intensity <- mmhpIntensityNumeric(params=par_est,
-                                              t=current_event_time,
-                                              time.vec=time_segment,
-                                              latent.vec=latent_mean)
-        est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time,
-                                                      latent_z=latent_event)
-        all_prresidual <- sum(1/sqrt(est.intensity.events))-
-          sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])
-        all_Lambda <- sum(est.intensity)*(time_segment[2]-time_segment[1])
-
-        ## rescaled interevent time
-        Lambda_vec <- rep(0,length(current_event_time)+1)
-        temp_time_vec <- c(0,current_event_time,current_obs_time)
-        for(m in 1:(length(current_event_time)+1)){
-          interevent_idx <- (time_segment>=temp_time_vec[m]) & (time_segment<temp_time_vec[m+1])
-          Lambda_vec[m] <- sum(est.intensity[interevent_idx])*(time_segment[2]-time_segment[1])
-        }
-        real_N_vec <- c(real_N_vec, length(current_event_time))
-        raw_real_cmmhp_vec <- c(raw_real_cmmhp_vec,all_Lambda)
-        pr_real_cmmhp_vec <- c(pr_real_cmmhp_vec,all_prresidual)
-        all_rescaled_interevent <- c(all_rescaled_interevent,Lambda_vec)
-      }  
-      Lambda_cmmhp_matrix[i,j][[1]] <- all_rescaled_interevent
-    }
-  }
-}
-
-rm(interpolation_array_list)
-rm(state_array_list)
-
-## cohort hawkes ####
-raw_real_c_hawkes_vec  <- numeric(0)
-pr_real_c_hawkes_vec <- numeric(0)
-Lambda_c_hawkes_matrix <- matrix(rep(list(),mice_number*mice_number),
-                               nrow=mice_number, ncol=mice_number)
-
-load(paste(old_data_path, cohort_names[current_cohort],
-           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
-
-# create a list to store the hawkes parameters for this
-model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
-                       eta_1=mean(sim_cohort_hp$eta_1),
-                       eta_2=mean(sim_cohort_hp$eta_2),
-                       eta_3=mean(sim_cohort_hp$eta_3),
-                       beta=mean(sim_cohort_hp$beta),
-                       f=apply(sim_cohort_hp$f,2,mean))
-model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
-                                                nrow=mice_number,ncol=mice_number),
-                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
-                                                                                    model1_par_est$eta_1,
-                                                                                    model1_par_est$eta_2,
-                                                                                    model1_par_est$eta_3),
-                                                  model1_par_est$f),
-                          beta_matrix=matrix(model1_par_est$beta,
-                                             nrow=mice_number,ncol=mice_number))
-
-for(i in 1:mice_number){
-  print(i)
-  for(j in 1:mice_number){
-    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
-    if(length(pair)>0&(i!=j)){
-      current_window_vec <- unique_pairs_df$observe[[pair]]
-      all_rescaled_interevent <- numeric(0)
-      for(cur in c(1:length(current_window_vec))){ 
-        cur_win <- current_window_vec[cur]
-        current_event_time <- return_df[return_df$initiator==i&
-                                        return_df$recipient==j&
-                                        return_df$observe.id==cur_win,"event.times"][[1]]
-        observe_period <- return_df[return_df$initiator==i&
-                                        return_df$recipient==j&
-                                        return_df$observe.id==cur_win,"observe.time"]
-        #### update this from the stan fit
-        hawkes.par <- c(model1_par_matrix$lambda0_matrix[i,j],model1_par_matrix$alpha[i,j],
-                        model1_par_matrix$beta[i,j])
-        # hawkes.par <- optim(par=c(1,0,100), fn=uniHawkesNegLogLik, method="CG", 
-        #                     t=current_event_time, termination = observe_period)
-        all_Lambda <- uniHawkesIntegralIntensity(object=list(lambda0=hawkes.par[1],
-                                                              alpha=hawkes.par[2],
-                                                              beta=hawkes.par[3]),
-                                                  events=current_event_time,
-                                                  termination = observe_period)
-        all_prresidual <- uniHawkesPearsonResidual(object=list(lambda0=hawkes.par[1],
-                                                              alpha=abs(hawkes.par[2]),
-                                                              beta=hawkes.par[3]),
-                                                  events=current_event_time,
-                                                  termination = observe_period)
-
-        ## rescaled interevent time
-        Lambda_vec <- uniHawkesCompensator(lambda0=hawkes.par[1],
-                                           alpha=hawkes.par[2],
-                                           beta=hawkes.par[3],
-                                           c(0,current_event_time))
-        all_rescaled_interevent <- c(all_rescaled_interevent,Lambda_vec)
-        raw_real_c_hawkes_vec <- c(raw_real_c_hawkes_vec,all_Lambda)
-        pr_real_c_hawkes_vec <- c(pr_real_c_hawkes_vec,all_prresidual)
-      }
-      Lambda_c_hawkes_matrix[i,j][[1]] <- all_rescaled_interevent
-    }
-  }
-}
-
-## cohort degree corrected hawkes ####
-raw_real_dc_hawkes_vec  <- numeric(0)
-pr_real_dc_hawkes_vec <- numeric(0)
-Lambda_dc_hawkes_matrix <- matrix(rep(list(),mice_number*mice_number),
-                               nrow=mice_number, ncol=mice_number)
-
-# model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
-
-load(paste(old_data_path, cohort_names[current_cohort],
-           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
-
-# create a list to store the hawkes parameters for this
-model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
-                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
-                       #lambda0=mean(sim_cohort_dchp$lambda0),
-                       eta_1=mean(sim_cohort_dchp$eta_1),
-                       eta_2=mean(sim_cohort_dchp$eta_2),
-                       eta_3=mean(sim_cohort_dchp$eta_3),
-                       beta=mean(sim_cohort_dchp$beta),
-                       f=apply(sim_cohort_dchp$f,2,mean))
-model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
-                                                model2_par_est$zeta,FUN = "+"),
-                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
-                                                                                    model2_par_est$eta_1,
-                                                                                  model2_par_est$eta_2,
-                                                                                    model2_par_est$eta_3),
-                                                  model2_par_est$f),
-                          beta_matrix=matrix(model2_par_est$beta,
-                                             nrow=mice_number,ncol=mice_number))
-
-for(i in 1:mice_number){
-  print(i)
-  for(j in 1:mice_number){
-    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
-    if(length(pair)>0&(i!=j)){
-      current_window_vec <- unique_pairs_df$observe[[pair]]
-      all_rescaled_interevent <- numeric(0)
-      for(cur in c(1:length(current_window_vec))){ 
-        cur_win <- current_window_vec[cur]
-        current_event_time <- return_df[return_df$initiator==i&
-                                        return_df$recipient==j&
-                                        return_df$observe.id==cur_win,"event.times"][[1]]
-        observe_period <- return_df[return_df$initiator==i&
-                                        return_df$recipient==j&
-                                        return_df$observe.id==cur_win,"observe.time"]
-        #### update this from the stan fit
-        hawkes.par <- c(model2_par_matrix$lambda0_matrix[i,j],model2_par_matrix$alpha[i,j],
-                        model2_par_matrix$beta[i,j])
-        # hawkes.par <- optim(par=c(1,0,100), fn=uniHawkesNegLogLik, method="CG", 
-        #                     t=current_event_time, termination = observe_period)
-        all_Lambda <- uniHawkesIntegralIntensity(object=list(lambda0=hawkes.par[1],
-                                                              alpha=hawkes.par[2],
-                                                              beta=hawkes.par[3]),
-                                                  events=current_event_time,
-                                                  termination = observe_period)
-        all_prresidual <- uniHawkesPearsonResidual(object=list(lambda0=hawkes.par[1],
-                                                              alpha=abs(hawkes.par[2]),
-                                                              beta=hawkes.par[3]),
-                                                  events=current_event_time,
-                                                  termination = observe_period)
-
-        ## rescaled interevent time
-        Lambda_vec <- uniHawkesCompensator(lambda0=hawkes.par[1],
-                                           alpha=hawkes.par[2],
-                                           beta=hawkes.par[3],
-                                           c(0,current_event_time))
-        all_rescaled_interevent <- c(all_rescaled_interevent,Lambda_vec)
-        raw_real_dc_hawkes_vec <- c(raw_real_dc_hawkes_vec,all_Lambda)
-        pr_real_dc_hawkes_vec <- c(pr_real_dc_hawkes_vec,all_prresidual)
-      }
-      Lambda_dc_hawkes_matrix[i,j][[1]] <- all_rescaled_interevent
-    }
-  }
-}
-
-# save(raw_real_hawkes_vec, pr_real_hawkes_vec,Lambda_hawkes_matrix,
-#      raw_real_mmpp_vec, pr_real_mmpp_vec, Lambda_mmpp_matrix,
-#      raw_real_mmhpsd_vec, pr_real_mmhpsd_vec, Lambda_mmhpsd_matrix,
-#      file = "../output/real_diag_four_models.RData")
+top_pairs <- unique_pairs_df %>% arrange(desc(count))
+
+best_i <- top_pairs$initiator[1]
+best_j <- top_pairs$recipient[1]
+wind <- unlist(lapply(top_pairs$no.events,which.max))[1]
+
 ```
 
-This is for a specific pair in a single window, we want to plot these three models.
-
-```{r select cohort pair window}
+```{r select cohort pair and window,eval=FALSE,include=FALSE}
 no_segments <- 500
@@
 observe_period <- return_df[row_indicator,"observe.time"]
-#no_segments <- 500
 time_segment <- seq(0,observe_period,length.out=no_segments)
@@
 
-Then we can plot some of these fits.
-
-```{r plot_functions, include=FALSE}
+```{r plot_functions, include=FALSE, cache=TRUE}
 drawRealIntensityPaper <- function(t,
@@
 
-```{r plot intensity in a window, fig.width=10}
-y.upper <- 20
-title.line <- 1
-title.cex <- 1
-anno.cex <- 1
+```{r extract hawkes fits, results='hide',eval=FALSE,include=FALSE}
+print(current_cohort)
 
@@
 # load the parameters for this pair
-load(paste(old_data_path, cohort_names[current_cohort],
+load(paste(data_path, cohort_names[current_cohort],
            "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
@@
 
-drawRealIntensityPaper(current_event_time,
-                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
-                       title_name="Cohort Hawkes",
-                       title.cex=title.cex, max.x=observe_period, box.col="black")
-drawHawkesIntensityPaper(lambda0=hawkes.par[1],
-                         alpha=hawkes.par[2],
-                         beta=hawkes.par[3],
-                         events=current_event_time, termination=observe_period)
-mtext(side=1, text="Time", line=1.6, cex=anno.cex)
-mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)
-
 #### Degree Corrected Hawkes ####
-load(paste(old_data_path, cohort_names[current_cohort],
+load(paste(data_path, cohort_names[current_cohort],
            "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
@@
 
-hawkes.par <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
+hawkes.par_dc <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
                 model2_par_matrix$alpha[current_i,current_j],
@@
 
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(sim_cohort_hp)
+rm(sim_cohort_dchp)
+
+```
+
+```{r extract_cmmhp_fit, results='hide',eval=FALSE,include=FALSE}
+print(current_cohort)
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+c_mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
+                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
+                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
+                 beta=mean(sim_cohort_mmhp$beta),
+                 q1=mean(sim_cohort_mmhp$q1[,pair]),
+                 q2=mean(sim_cohort_mmhp$q2[,pair]))
+
+c_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+c_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=c_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+```
+
+```{r extract indep mmhp fit, results='hide',eval=FALSE,include=FALSE}
+
+print(current_cohort)
+#### I-MMHP  ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/sep_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+sep_mmhp_par <- list(lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
+                 lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
+                 alpha=mean(sim_mmhp_sep$alpha[,pair]),
+                 beta=mean(sim_mmhp_sep$beta),
+                 q1=mean(sim_mmhp_sep$q1[,pair]),
+                 q2=mean(sim_mmhp_sep$q2[,pair]))
+
+sep_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+sep_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=sep_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+```
+
+For each cohort, we extract the mouse pair with the most interactions, plotting
+thes estimated intensity in the window with the most interactions along with
+the QQ plot of all events (in all windows) between that pair.
+
+```{r pair diagnostic plot, include=FALSE,eval=FALSE}
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+no_segments <- 500
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+par(mfrow=c(2,4), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
+layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
+anno.cex <- 1.3
+title.cex <- 2.2
+title.line <- 0.5
+y.upper <- 20
+
+#### Cohort Hawkes  ####
+
 drawRealIntensityPaper(current_event_time,
                        yupper=y.upper, color="black",line.width=2,title.line=title.line,
-                       title_name="Cohort DC-Hawkes",
+                       title_name="C-HP",
                        title.cex=title.cex, max.x=observe_period, box.col="black")
@@
                          events=current_event_time, termination=observe_period)
-mtext(side=1, text="Time", line=1.6, cex=anno.cex)
-mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)
+
+### DC Cohort Hawkes ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="DC-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par_dc[1],
+                         alpha=hawkes.par_dc[2],
+                         beta=hawkes.par_dc[3],
+                         events=current_event_time, termination=observe_period)
+
+#### DC C-MMHP ####
+drawRealIntensityPaper(current_event_time, object=c_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,c_mmhp.est.latent$x.hat),
+                                       z=c_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="DC C-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### Sep MMHP ####
+
+drawRealIntensityPaper(current_event_time, object=sep_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,sep_mmhp.est.latent$x.hat),
+                                       z=sep_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="I-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### then the corresponding QQ plots ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+#### Cohort Hawkes ####
+
+Lambda.c_hawkes.test <- Lambda_c_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.c_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.c_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### Cohort DC Hawkes ####
+
+Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.dc_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### DC C-MMHP ####
+Lambda.cmmhp.test <- Lambda_cmmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.cmmhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.cmmhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### I-MMHP ####
+Lambda.immhp.test <- Lambda_mmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.immhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.immhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+```
+
+We want to repeat this for the pair with the most interactions in a single
+cohort, displaying the fitted intensity in the window where they have
+the most interactions.
+
+### Cohort 1
+
+```{r cohort-1,cache=TRUE}
+current_cohort <- 1
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+            observe=list(observe.id),
+            observe.length=list(observe.time),
+            no.events=list(no.events)) 
+top_pairs <- unique_pairs_df %>% arrange(desc(count))
+
+best_i <- top_pairs$initiator[1]
+best_j <- top_pairs$recipient[1]
+wind <- unlist(lapply(top_pairs$no.events,which.max))[1]
+
+win_length <- top_pairs$observe.length[[1]][wind]
+
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+
+actual_win <- which(unique_observe_win$observe.time == win_length)
+
+no_segments <- 500
+
+current_i <- best_i #8
+current_j <- best_j #2
+current_win <- actual_win#wind 
+# this is the 18th window, not the 18th window with observations
+### that this pair have events in, which it should be
+
+pair <- which(unique_pairs_df$initiator==current_i&unique_pairs_df$recipient==current_j)
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+### load the corresponding stan fits ####
+#print(current_cohort)
+
+## Cohort Hawkes ####
+# load the parameters for this pair
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
+                       eta_1=mean(sim_cohort_hp$eta_1),
+                       eta_2=mean(sim_cohort_hp$eta_2),
+                       eta_3=mean(sim_cohort_hp$eta_3),
+                       beta=mean(sim_cohort_hp$beta),
+                       f=apply(sim_cohort_hp$f,2,mean))
+model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
+                                                nrow=mice_number,ncol=mice_number),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model1_par_est$eta_1,
+                                                                                    model1_par_est$eta_2,
+                                                                                    model1_par_est$eta_3),
+                                                  model1_par_est$f),
+                          beta_matrix=matrix(model1_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par <- c(model1_par_matrix$lambda0_matrix[current_i,current_j],
+                model1_par_matrix$alpha[current_i,current_j],
+                        model1_par_matrix$beta[current_i,current_j])
+
+#### Degree Corrected Hawkes ####
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
+                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
+                       #lambda0=mean(sim_cohort_dchp$lambda0),
+                       eta_1=mean(sim_cohort_dchp$eta_1),
+                       eta_2=mean(sim_cohort_dchp$eta_2),
+                       eta_3=mean(sim_cohort_dchp$eta_3),
+                       beta=mean(sim_cohort_dchp$beta),
+                       f=apply(sim_cohort_dchp$f,2,mean))
+model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
+                                                model2_par_est$zeta,FUN = "+"),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model2_par_est$eta_1,
+                                                                                  model2_par_est$eta_2,
+                                                                                    model2_par_est$eta_3),
+                                                  model2_par_est$f),
+                          beta_matrix=matrix(model2_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par_dc <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
+                model2_par_matrix$alpha[current_i,current_j],
+                model2_par_matrix$beta[current_i,current_j])
 
@@
 
-```
-
-This ouput is correctly dealing with the C-MMHP parameters now.
-
-```{r draw_mmhp_fit}
-#current_cohort <- 2
 ## Cohort MMHP
-load(paste(c_mmhp_path,cohort_names[current_cohort],
+load(paste(data_path,cohort_names[current_cohort],
              "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
              ".RData",sep=''))
-load(paste(c_mmhp_path,cohort_names[current_cohort],
+load(paste(data_path,cohort_names[current_cohort],
              "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
@@
 
-mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
+c_mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
                  lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
@@
 
-mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],1,function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
-mmhp.est.latent <- interpolateLatentTrajectory(params=mmhp_par,events=current_event_time,zt=mmhp.est.latent,
-                                               initial.state=mean(initial_state_list[[pair]][[current_win]]),
-                                               termination.time=observe_period,termination.state = 2)
-
-drawRealIntensityPaper(current_event_time, object=mmhp_par,title.line=title.line,
-                       simulation=list(x=c(0,mmhp.est.latent$x.hat),
-                                       z=mmhp.est.latent$z.hat),
-                       yupper=y.upper, color="black", line.width=2,
-                       title_name="Cohort MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
-mtext(side=1, text="Time", line=1.6, cex=anno.cex)
-mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)
+c_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+c_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=c_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
 
@@
 
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/sep_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+sep_mmhp_par <- list(lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
+                 lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
+                 alpha=mean(sim_mmhp_sep$alpha[,pair]),
+                 beta=mean(sim_mmhp_sep$beta),
+                 q1=mean(sim_mmhp_sep$q1[,pair]),
+                 q2=mean(sim_mmhp_sep$q2[,pair]))
+
+sep_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+sep_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=sep_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+# row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+# row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+# current_event_time <- return_df[row_indicator,"event.times"][[1]]
+# observe_period <- return_df[row_indicator,"observe.time"]
+# no_segments <- 500
+# time_segment <- seq(0,observe_period,length.out=no_segments)
+
+par(mfrow=c(2,4), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
+layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
+anno.cex <- 1.3
+title.cex <- 2.2
+title.line <- 0.5
+y.upper <- 20
+
+#### Cohort Hawkes  ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="C-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par[1],
+                         alpha=hawkes.par[2],
+                         beta=hawkes.par[3],
+                         events=current_event_time, termination=observe_period)
+
+### DC Cohort Hawkes ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="DC-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par_dc[1],
+                         alpha=hawkes.par_dc[2],
+                         beta=hawkes.par_dc[3],
+                         events=current_event_time, termination=observe_period)
+
+#### DC C-MMHP ####
+drawRealIntensityPaper(current_event_time, object=c_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,c_mmhp.est.latent$x.hat),
+                                       z=c_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="DC C-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### Sep MMHP ####
+
+drawRealIntensityPaper(current_event_time, object=sep_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,sep_mmhp.est.latent$x.hat),
+                                       z=sep_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="I-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### then the corresponding QQ plots ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+#### Cohort Hawkes ####
+
+Lambda.c_hawkes.test <- Lambda_c_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.c_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.c_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### Cohort DC Hawkes ####
+
+Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.dc_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### DC C-MMHP ####
+Lambda.cmmhp.test <- Lambda_cmmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.cmmhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.cmmhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### I-MMHP ####
+Lambda.immhp.test <- Lambda_mmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.immhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.immhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
 ```
 
-```{r, eval=FALSE}
-#y.upper <- 10
-#title.line <- 1
-#title.cex <- 0.1
-drawRealIntensityPaper(current_event_time, object=mmhp_par,title.line=title.line,
-                       simulation=list(x=c(0,mmhp.est.latent$x.hat),
-                                       z=mmhp.est.latent$z.hat),
+### Cohort 2
+
+```{r cohort-2,cache=TRUE}
+current_cohort <- 2
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+            observe=list(observe.id),
+            observe.length=list(observe.time),
+            no.events=list(no.events)) 
+top_pairs <- unique_pairs_df %>% arrange(desc(count))
+
+best_i <- top_pairs$initiator[1]
+best_j <- top_pairs$recipient[1]
+wind <- unlist(lapply(top_pairs$no.events,which.max))[1]
+
+win_length <- top_pairs$observe.length[[1]][wind]
+
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+actual_win <- which(unique_observe_win$observe.time == win_length)
+
+no_segments <- 500
+
+current_i <- best_i #8
+current_j <- best_j #2
+current_win <- actual_win#wind 
+# this is the 18th window, not the 18th window with observations
+### that this pair have events in, which it should be
+
+# clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+# return_df <- cleanObservationPeriod(current_cohort, clean_data)
+# unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+#   dplyr::summarize(count=n(),
+#             observe=list(observe.id),
+#             observe.length=list(observe.time),
+#             no.events=list(no.events))
+pair <- which(unique_pairs_df$initiator==current_i&unique_pairs_df$recipient==current_j)
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+### load the corresponding stan fits ####
+#print(current_cohort)
+
+## Cohort Hawkes ####
+# load the parameters for this pair
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
+                       eta_1=mean(sim_cohort_hp$eta_1),
+                       eta_2=mean(sim_cohort_hp$eta_2),
+                       eta_3=mean(sim_cohort_hp$eta_3),
+                       beta=mean(sim_cohort_hp$beta),
+                       f=apply(sim_cohort_hp$f,2,mean))
+model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
+                                                nrow=mice_number,ncol=mice_number),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model1_par_est$eta_1,
+                                                                                    model1_par_est$eta_2,
+                                                                                    model1_par_est$eta_3),
+                                                  model1_par_est$f),
+                          beta_matrix=matrix(model1_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par <- c(model1_par_matrix$lambda0_matrix[current_i,current_j],
+                model1_par_matrix$alpha[current_i,current_j],
+                        model1_par_matrix$beta[current_i,current_j])
+
+#### Degree Corrected Hawkes ####
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
+                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
+                       #lambda0=mean(sim_cohort_dchp$lambda0),
+                       eta_1=mean(sim_cohort_dchp$eta_1),
+                       eta_2=mean(sim_cohort_dchp$eta_2),
+                       eta_3=mean(sim_cohort_dchp$eta_3),
+                       beta=mean(sim_cohort_dchp$beta),
+                       f=apply(sim_cohort_dchp$f,2,mean))
+model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
+                                                model2_par_est$zeta,FUN = "+"),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model2_par_est$eta_1,
+                                                                                  model2_par_est$eta_2,
+                                                                                    model2_par_est$eta_3),
+                                                  model2_par_est$f),
+                          beta_matrix=matrix(model2_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par_dc <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
+                model2_par_matrix$alpha[current_i,current_j],
+                model2_par_matrix$beta[current_i,current_j])
+
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(sim_cohort_hp)
+rm(sim_cohort_dchp)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+c_mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
+                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
+                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
+                 beta=mean(sim_cohort_mmhp$beta),
+                 q1=mean(sim_cohort_mmhp$q1[,pair]),
+                 q2=mean(sim_cohort_mmhp$q2[,pair]))
+
+c_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+c_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=c_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/sep_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+sep_mmhp_par <- list(lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
+                 lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
+                 alpha=mean(sim_mmhp_sep$alpha[,pair]),
+                 beta=mean(sim_mmhp_sep$beta),
+                 q1=mean(sim_mmhp_sep$q1[,pair]),
+                 q2=mean(sim_mmhp_sep$q2[,pair]))
+
+sep_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+sep_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=sep_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+no_segments <- 500
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+par(mfrow=c(2,4), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
+layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
+anno.cex <- 1.3
+title.cex <- 2.2
+title.line <- 0.5
+y.upper <- 20
+
+#### Cohort Hawkes  ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="C-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par[1],
+                         alpha=hawkes.par[2],
+                         beta=hawkes.par[3],
+                         events=current_event_time, termination=observe_period)
+
+### DC Cohort Hawkes ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="DC-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par_dc[1],
+                         alpha=hawkes.par_dc[2],
+                         beta=hawkes.par_dc[3],
+                         events=current_event_time, termination=observe_period)
+
+#### DC C-MMHP ####
+drawRealIntensityPaper(current_event_time, object=c_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,c_mmhp.est.latent$x.hat),
+                                       z=c_mmhp.est.latent$z.hat),
                        yupper=y.upper, color="black", line.width=2,
-                       title_name="MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
-mtext(side=1, text="Time", line=1.6, cex=anno.cex)
-mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)
+                       title_name="DC C-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### Sep MMHP ####
+
+drawRealIntensityPaper(current_event_time, object=sep_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,sep_mmhp.est.latent$x.hat),
+                                       z=sep_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="I-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### then the corresponding QQ plots ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+#### Cohort Hawkes ####
+
+Lambda.c_hawkes.test <- Lambda_c_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.c_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.c_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### Cohort DC Hawkes ####
+
+Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.dc_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### DC C-MMHP ####
+Lambda.cmmhp.test <- Lambda_cmmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.cmmhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.cmmhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### I-MMHP ####
+Lambda.immhp.test <- Lambda_mmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.immhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.immhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
 
@@
 
-The corresponding QQ plots also.
-
-```{r, eval=FALSE}
-anno.cex <- 1
-#### Hawkes
-Lambda.hawkes.test <- Lambda_hawkes_matrix[current_i,current_j][[1]]
-
-p <- ppoints(length(Lambda.hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
-q <- quantile(Lambda.hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
-plot(qexp(p),q, 
-     xlab="",ylab="",xaxt="n",yaxt="n",
-     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
-mtext(side=1, text="Theoretical Quantiles", line=1.6, cex=anno.cex)
-mtext(side=2, text="Empirical Quantiles", line=1.2, cex=anno.cex)
-Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
-Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
-qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
-
-#### mmhp
-Lambda.test.mmhp <- Lambda_mmhp_matrix[current_i,current_j][[1]]
-p <- ppoints(length(Lambda.test.mmhp))    # 100 equally spaced points on (0,1), excluding endpoints
-q <- quantile(Lambda.test.mmhp,p=p,na.rm=TRUE) # percentiles of the sample distribution
-plot(qexp(p),q, 
-     xlab="",ylab="",xaxt="n",yaxt="n",
-     pch=1,cex=1,col="Black",ylim=c(0,max(q)),xlim=c(0,3))
-mtext(side=1, text="Theoretical Quantiles", line=1.6, cex=anno.cex)
-mtext(side=2, text="Empirical Quantiles", line=1.2, cex=anno.cex)
-Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1)
-Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1)
-qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+### Cohort 3
+
+```{r cohort-3,cache=TRUE}
+current_cohort <- 3
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+            observe=list(observe.id),
+            observe.length=list(observe.time),
+            no.events=list(no.events)) 
+top_pairs <- unique_pairs_df %>% arrange(desc(count))
+
+best_i <- top_pairs$initiator[1]
+best_j <- top_pairs$recipient[1]
+wind <- unlist(lapply(top_pairs$no.events,which.max))[1]
+
+win_length <- top_pairs$observe.length[[1]][wind]
+
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+actual_win <- which(unique_observe_win$observe.time == win_length)
+
+no_segments <- 500
+
+current_i <- best_i #8
+current_j <- best_j #2
+current_win <- actual_win#wind 
+# this is the 18th window, not the 18th window with observations
+### that this pair have events in, which it should be
+
+# clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+# return_df <- cleanObservationPeriod(current_cohort, clean_data)
+# unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+#   dplyr::summarize(count=n(),
+#             observe=list(observe.id),
+#             observe.length=list(observe.time),
+#             no.events=list(no.events))
+pair <- which(unique_pairs_df$initiator==current_i&unique_pairs_df$recipient==current_j)
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+### load the corresponding stan fits ####
+#print(current_cohort)
+
+## Cohort Hawkes ####
+# load the parameters for this pair
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
+                       eta_1=mean(sim_cohort_hp$eta_1),
+                       eta_2=mean(sim_cohort_hp$eta_2),
+                       eta_3=mean(sim_cohort_hp$eta_3),
+                       beta=mean(sim_cohort_hp$beta),
+                       f=apply(sim_cohort_hp$f,2,mean))
+model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
+                                                nrow=mice_number,ncol=mice_number),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model1_par_est$eta_1,
+                                                                                    model1_par_est$eta_2,
+                                                                                    model1_par_est$eta_3),
+                                                  model1_par_est$f),
+                          beta_matrix=matrix(model1_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par <- c(model1_par_matrix$lambda0_matrix[current_i,current_j],
+                model1_par_matrix$alpha[current_i,current_j],
+                        model1_par_matrix$beta[current_i,current_j])
+
+#### Degree Corrected Hawkes ####
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
+                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
+                       #lambda0=mean(sim_cohort_dchp$lambda0),
+                       eta_1=mean(sim_cohort_dchp$eta_1),
+                       eta_2=mean(sim_cohort_dchp$eta_2),
+                       eta_3=mean(sim_cohort_dchp$eta_3),
+                       beta=mean(sim_cohort_dchp$beta),
+                       f=apply(sim_cohort_dchp$f,2,mean))
+model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
+                                                model2_par_est$zeta,FUN = "+"),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model2_par_est$eta_1,
+                                                                                  model2_par_est$eta_2,
+                                                                                    model2_par_est$eta_3),
+                                                  model2_par_est$f),
+                          beta_matrix=matrix(model2_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par_dc <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
+                model2_par_matrix$alpha[current_i,current_j],
+                model2_par_matrix$beta[current_i,current_j])
+
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(sim_cohort_hp)
+rm(sim_cohort_dchp)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+c_mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
+                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
+                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
+                 beta=mean(sim_cohort_mmhp$beta),
+                 q1=mean(sim_cohort_mmhp$q1[,pair]),
+                 q2=mean(sim_cohort_mmhp$q2[,pair]))
+
+c_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+c_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=c_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/sep_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+sep_mmhp_par <- list(lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
+                 lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
+                 alpha=mean(sim_mmhp_sep$alpha[,pair]),
+                 beta=mean(sim_mmhp_sep$beta),
+                 q1=mean(sim_mmhp_sep$q1[,pair]),
+                 q2=mean(sim_mmhp_sep$q2[,pair]))
+
+sep_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+sep_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=sep_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+no_segments <- 500
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+par(mfrow=c(2,4), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
+layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
+anno.cex <- 1.3
+title.cex <- 2.2
+title.line <- 0.5
+y.upper <- 20
+
+#### Cohort Hawkes  ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="C-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par[1],
+                         alpha=hawkes.par[2],
+                         beta=hawkes.par[3],
+                         events=current_event_time, termination=observe_period)
+
+### DC Cohort Hawkes ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="DC-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par_dc[1],
+                         alpha=hawkes.par_dc[2],
+                         beta=hawkes.par_dc[3],
+                         events=current_event_time, termination=observe_period)
+
+#### DC C-MMHP ####
+drawRealIntensityPaper(current_event_time, object=c_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,c_mmhp.est.latent$x.hat),
+                                       z=c_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="DC C-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### Sep MMHP ####
+
+drawRealIntensityPaper(current_event_time, object=sep_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,sep_mmhp.est.latent$x.hat),
+                                       z=sep_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="I-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### then the corresponding QQ plots ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+#### Cohort Hawkes ####
+
+Lambda.c_hawkes.test <- Lambda_c_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.c_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.c_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### Cohort DC Hawkes ####
+
+Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.dc_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### DC C-MMHP ####
+Lambda.cmmhp.test <- Lambda_cmmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.cmmhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.cmmhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### I-MMHP ####
+Lambda.immhp.test <- Lambda_mmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.immhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.immhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
 ```
+
+### Cohort 4
+
+```{r cohort-4,cache=TRUE}
+current_cohort <- 4
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+            observe=list(observe.id),
+            observe.length=list(observe.time),
+            no.events=list(no.events)) 
+top_pairs <- unique_pairs_df %>% arrange(desc(count))
+
+best_i <- top_pairs$initiator[1]
+best_j <- top_pairs$recipient[1]
+wind <- unlist(lapply(top_pairs$no.events,which.max))[1]
+
+win_length <- top_pairs$observe.length[[1]][wind]
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+actual_win <- which(unique_observe_win$observe.time == win_length)
+
+no_segments <- 500
+
+current_i <- best_i #8
+current_j <- best_j #2
+current_win <- actual_win#wind 
+# this is the 18th window, not the 18th window with observations
+### that this pair have events in, which it should be
+
+# clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+# return_df <- cleanObservationPeriod(current_cohort, clean_data)
+# unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+#   dplyr::summarize(count=n(),
+#             observe=list(observe.id),
+#             observe.length=list(observe.time),
+#             no.events=list(no.events))
+pair <- which(unique_pairs_df$initiator==current_i&unique_pairs_df$recipient==current_j)
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+### load the corresponding stan fits ####
+#print(current_cohort)
+
+## Cohort Hawkes ####
+# load the parameters for this pair
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
+                       eta_1=mean(sim_cohort_hp$eta_1),
+                       eta_2=mean(sim_cohort_hp$eta_2),
+                       eta_3=mean(sim_cohort_hp$eta_3),
+                       beta=mean(sim_cohort_hp$beta),
+                       f=apply(sim_cohort_hp$f,2,mean))
+model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
+                                                nrow=mice_number,ncol=mice_number),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model1_par_est$eta_1,
+                                                                                    model1_par_est$eta_2,
+                                                                                    model1_par_est$eta_3),
+                                                  model1_par_est$f),
+                          beta_matrix=matrix(model1_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par <- c(model1_par_matrix$lambda0_matrix[current_i,current_j],
+                model1_par_matrix$alpha[current_i,current_j],
+                        model1_par_matrix$beta[current_i,current_j])
+
+#### Degree Corrected Hawkes ####
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
+                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
+                       #lambda0=mean(sim_cohort_dchp$lambda0),
+                       eta_1=mean(sim_cohort_dchp$eta_1),
+                       eta_2=mean(sim_cohort_dchp$eta_2),
+                       eta_3=mean(sim_cohort_dchp$eta_3),
+                       beta=mean(sim_cohort_dchp$beta),
+                       f=apply(sim_cohort_dchp$f,2,mean))
+model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
+                                                model2_par_est$zeta,FUN = "+"),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model2_par_est$eta_1,
+                                                                                  model2_par_est$eta_2,
+                                                                                    model2_par_est$eta_3),
+                                                  model2_par_est$f),
+                          beta_matrix=matrix(model2_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par_dc <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
+                model2_par_matrix$alpha[current_i,current_j],
+                model2_par_matrix$beta[current_i,current_j])
+
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(sim_cohort_hp)
+rm(sim_cohort_dchp)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+c_mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
+                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
+                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
+                 beta=mean(sim_cohort_mmhp$beta),
+                 q1=mean(sim_cohort_mmhp$q1[,pair]),
+                 q2=mean(sim_cohort_mmhp$q2[,pair]))
+
+c_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+c_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=c_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/sep_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+sep_mmhp_par <- list(lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
+                 lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
+                 alpha=mean(sim_mmhp_sep$alpha[,pair]),
+                 beta=mean(sim_mmhp_sep$beta),
+                 q1=mean(sim_mmhp_sep$q1[,pair]),
+                 q2=mean(sim_mmhp_sep$q2[,pair]))
+
+sep_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+sep_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=sep_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+no_segments <- 500
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+par(mfrow=c(2,4), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
+layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
+anno.cex <- 1.3
+title.cex <- 2.2
+title.line <- 0.5
+y.upper <- 20
+
+#### Cohort Hawkes  ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="C-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par[1],
+                         alpha=hawkes.par[2],
+                         beta=hawkes.par[3],
+                         events=current_event_time, termination=observe_period)
+
+### DC Cohort Hawkes ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="DC-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par_dc[1],
+                         alpha=hawkes.par_dc[2],
+                         beta=hawkes.par_dc[3],
+                         events=current_event_time, termination=observe_period)
+
+#### DC C-MMHP ####
+drawRealIntensityPaper(current_event_time, object=c_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,c_mmhp.est.latent$x.hat),
+                                       z=c_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="DC C-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### Sep MMHP ####
+
+drawRealIntensityPaper(current_event_time, object=sep_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,sep_mmhp.est.latent$x.hat),
+                                       z=sep_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="I-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### then the corresponding QQ plots ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+#### Cohort Hawkes ####
+
+Lambda.c_hawkes.test <- Lambda_c_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.c_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.c_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### Cohort DC Hawkes ####
+
+Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.dc_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### DC C-MMHP ####
+Lambda.cmmhp.test <- Lambda_cmmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.cmmhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.cmmhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### I-MMHP ####
+Lambda.immhp.test <- Lambda_mmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.immhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.immhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+```
+
+### Cohort 5
+
+```{r cohort-5,cache=TRUE}
+current_cohort <- 5
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+            observe=list(observe.id),
+            observe.length=list(observe.time),
+            no.events=list(no.events)) 
+top_pairs <- unique_pairs_df %>% arrange(desc(count))
+
+best_i <- top_pairs$initiator[1]
+best_j <- top_pairs$recipient[1]
+wind <- unlist(lapply(top_pairs$no.events,which.max))[1]
+
+win_length <- top_pairs$observe.length[[1]][wind]
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+actual_win <- which(unique_observe_win$observe.time == win_length)
+
+no_segments <- 500
+
+current_i <- best_i #8
+current_j <- best_j #2
+current_win <- actual_win#wind 
+# this is the 18th window, not the 18th window with observations
+### that this pair have events in, which it should be
+
+# clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+# return_df <- cleanObservationPeriod(current_cohort, clean_data)
+# unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+#   dplyr::summarize(count=n(),
+#             observe=list(observe.id),
+#             observe.length=list(observe.time),
+#             no.events=list(no.events))
+pair <- which(unique_pairs_df$initiator==current_i&unique_pairs_df$recipient==current_j)
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+### load the corresponding stan fits ####
+#print(current_cohort)
+
+## Cohort Hawkes ####
+# load the parameters for this pair
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
+                       eta_1=mean(sim_cohort_hp$eta_1),
+                       eta_2=mean(sim_cohort_hp$eta_2),
+                       eta_3=mean(sim_cohort_hp$eta_3),
+                       beta=mean(sim_cohort_hp$beta),
+                       f=apply(sim_cohort_hp$f,2,mean))
+model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
+                                                nrow=mice_number,ncol=mice_number),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model1_par_est$eta_1,
+                                                                                    model1_par_est$eta_2,
+                                                                                    model1_par_est$eta_3),
+                                                  model1_par_est$f),
+                          beta_matrix=matrix(model1_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par <- c(model1_par_matrix$lambda0_matrix[current_i,current_j],
+                model1_par_matrix$alpha[current_i,current_j],
+                        model1_par_matrix$beta[current_i,current_j])
+
+#### Degree Corrected Hawkes ####
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
+                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
+                       #lambda0=mean(sim_cohort_dchp$lambda0),
+                       eta_1=mean(sim_cohort_dchp$eta_1),
+                       eta_2=mean(sim_cohort_dchp$eta_2),
+                       eta_3=mean(sim_cohort_dchp$eta_3),
+                       beta=mean(sim_cohort_dchp$beta),
+                       f=apply(sim_cohort_dchp$f,2,mean))
+model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
+                                                model2_par_est$zeta,FUN = "+"),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model2_par_est$eta_1,
+                                                                                  model2_par_est$eta_2,
+                                                                                    model2_par_est$eta_3),
+                                                  model2_par_est$f),
+                          beta_matrix=matrix(model2_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par_dc <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
+                model2_par_matrix$alpha[current_i,current_j],
+                model2_par_matrix$beta[current_i,current_j])
+
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(sim_cohort_hp)
+rm(sim_cohort_dchp)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+c_mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
+                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
+                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
+                 beta=mean(sim_cohort_mmhp$beta),
+                 q1=mean(sim_cohort_mmhp$q1[,pair]),
+                 q2=mean(sim_cohort_mmhp$q2[,pair]))
+
+c_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+c_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=c_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/sep_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+sep_mmhp_par <- list(lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
+                 lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
+                 alpha=mean(sim_mmhp_sep$alpha[,pair]),
+                 beta=mean(sim_mmhp_sep$beta),
+                 q1=mean(sim_mmhp_sep$q1[,pair]),
+                 q2=mean(sim_mmhp_sep$q2[,pair]))
+
+sep_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+sep_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=sep_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+no_segments <- 500
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+par(mfrow=c(2,4), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
+layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
+anno.cex <- 1.3
+title.cex <- 2.2
+title.line <- 0.5
+y.upper <- 20
+
+#### Cohort Hawkes  ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="C-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par[1],
+                         alpha=hawkes.par[2],
+                         beta=hawkes.par[3],
+                         events=current_event_time, termination=observe_period)
+
+### DC Cohort Hawkes ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="DC-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par_dc[1],
+                         alpha=hawkes.par_dc[2],
+                         beta=hawkes.par_dc[3],
+                         events=current_event_time, termination=observe_period)
+
+#### DC C-MMHP ####
+drawRealIntensityPaper(current_event_time, object=c_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,c_mmhp.est.latent$x.hat),
+                                       z=c_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="DC C-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### Sep MMHP ####
+
+drawRealIntensityPaper(current_event_time, object=sep_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,sep_mmhp.est.latent$x.hat),
+                                       z=sep_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="I-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### then the corresponding QQ plots ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+#### Cohort Hawkes ####
+
+Lambda.c_hawkes.test <- Lambda_c_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.c_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.c_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### Cohort DC Hawkes ####
+
+Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.dc_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### DC C-MMHP ####
+Lambda.cmmhp.test <- Lambda_cmmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.cmmhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.cmmhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### I-MMHP ####
+Lambda.immhp.test <- Lambda_mmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.immhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.immhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+```
+
+### Cohort 6
+
+```{r cohort-6,cache=TRUE}
+current_cohort <- 6
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+            observe=list(observe.id),
+            observe.length=list(observe.time),
+            no.events=list(no.events)) 
+top_pairs <- unique_pairs_df %>% arrange(desc(count))
+
+best_i <- top_pairs$initiator[1]
+best_j <- top_pairs$recipient[1]
+wind <- unlist(lapply(top_pairs$no.events,which.max))[1]
+
+win_length <- top_pairs$observe.length[[1]][wind]
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+actual_win <- which(unique_observe_win$observe.time == win_length)
+
+no_segments <- 500
+
+current_i <- best_i #8
+current_j <- best_j #2
+current_win <- actual_win#wind 
+# this is the 18th window, not the 18th window with observations
+### that this pair have events in, which it should be
+
+# clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+# return_df <- cleanObservationPeriod(current_cohort, clean_data)
+# unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+#   dplyr::summarize(count=n(),
+#             observe=list(observe.id),
+#             observe.length=list(observe.time),
+#             no.events=list(no.events))
+pair <- which(unique_pairs_df$initiator==current_i&unique_pairs_df$recipient==current_j)
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+### load the corresponding stan fits ####
+#print(current_cohort)
+
+## Cohort Hawkes ####
+# load the parameters for this pair
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
+                       eta_1=mean(sim_cohort_hp$eta_1),
+                       eta_2=mean(sim_cohort_hp$eta_2),
+                       eta_3=mean(sim_cohort_hp$eta_3),
+                       beta=mean(sim_cohort_hp$beta),
+                       f=apply(sim_cohort_hp$f,2,mean))
+model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
+                                                nrow=mice_number,ncol=mice_number),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model1_par_est$eta_1,
+                                                                                    model1_par_est$eta_2,
+                                                                                    model1_par_est$eta_3),
+                                                  model1_par_est$f),
+                          beta_matrix=matrix(model1_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par <- c(model1_par_matrix$lambda0_matrix[current_i,current_j],
+                model1_par_matrix$alpha[current_i,current_j],
+                        model1_par_matrix$beta[current_i,current_j])
+
+#### Degree Corrected Hawkes ####
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
+                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
+                       #lambda0=mean(sim_cohort_dchp$lambda0),
+                       eta_1=mean(sim_cohort_dchp$eta_1),
+                       eta_2=mean(sim_cohort_dchp$eta_2),
+                       eta_3=mean(sim_cohort_dchp$eta_3),
+                       beta=mean(sim_cohort_dchp$beta),
+                       f=apply(sim_cohort_dchp$f,2,mean))
+model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
+                                                model2_par_est$zeta,FUN = "+"),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model2_par_est$eta_1,
+                                                                                  model2_par_est$eta_2,
+                                                                                    model2_par_est$eta_3),
+                                                  model2_par_est$f),
+                          beta_matrix=matrix(model2_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par_dc <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
+                model2_par_matrix$alpha[current_i,current_j],
+                model2_par_matrix$beta[current_i,current_j])
+
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(sim_cohort_hp)
+rm(sim_cohort_dchp)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+c_mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
+                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
+                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
+                 beta=mean(sim_cohort_mmhp$beta),
+                 q1=mean(sim_cohort_mmhp$q1[,pair]),
+                 q2=mean(sim_cohort_mmhp$q2[,pair]))
+
+c_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+c_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=c_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/sep_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+sep_mmhp_par <- list(lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
+                 lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
+                 alpha=mean(sim_mmhp_sep$alpha[,pair]),
+                 beta=mean(sim_mmhp_sep$beta),
+                 q1=mean(sim_mmhp_sep$q1[,pair]),
+                 q2=mean(sim_mmhp_sep$q2[,pair]))
+
+sep_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+sep_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=sep_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+no_segments <- 500
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+par(mfrow=c(2,4), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
+layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
+anno.cex <- 1.3
+title.cex <- 2.2
+title.line <- 0.5
+y.upper <- 20
+
+#### Cohort Hawkes  ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="C-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par[1],
+                         alpha=hawkes.par[2],
+                         beta=hawkes.par[3],
+                         events=current_event_time, termination=observe_period)
+
+### DC Cohort Hawkes ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="DC-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par_dc[1],
+                         alpha=hawkes.par_dc[2],
+                         beta=hawkes.par_dc[3],
+                         events=current_event_time, termination=observe_period)
+
+#### DC C-MMHP ####
+drawRealIntensityPaper(current_event_time, object=c_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,c_mmhp.est.latent$x.hat),
+                                       z=c_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="DC C-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### Sep MMHP ####
+
+drawRealIntensityPaper(current_event_time, object=sep_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,sep_mmhp.est.latent$x.hat),
+                                       z=sep_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="I-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### then the corresponding QQ plots ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+#### Cohort Hawkes ####
+
+Lambda.c_hawkes.test <- Lambda_c_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.c_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.c_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### Cohort DC Hawkes ####
+
+Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.dc_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### DC C-MMHP ####
+Lambda.cmmhp.test <- Lambda_cmmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.cmmhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.cmmhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### I-MMHP ####
+Lambda.immhp.test <- Lambda_mmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.immhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.immhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+```
+
+### Cohort 7
+
+```{r cohort-7,cache=TRUE}
+y.upper <- 80
+current_cohort <- 7
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+            observe=list(observe.id),
+            observe.length=list(observe.time),
+            no.events=list(no.events)) 
+top_pairs <- unique_pairs_df %>% arrange(desc(count))
+
+best_i <- top_pairs$initiator[1]
+best_j <- top_pairs$recipient[1]
+wind <- unlist(lapply(top_pairs$no.events,which.max))[1]
+
+win_length <- top_pairs$observe.length[[1]][wind]
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+actual_win <- which(unique_observe_win$observe.time == win_length)
+
+no_segments <- 500
+
+current_i <- best_i #8
+current_j <- best_j #2
+current_win <- actual_win#wind 
+# this is the 18th window, not the 18th window with observations
+### that this pair have events in, which it should be
+
+# clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+# return_df <- cleanObservationPeriod(current_cohort, clean_data)
+# unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+#   dplyr::summarize(count=n(),
+#             observe=list(observe.id),
+#             observe.length=list(observe.time),
+#             no.events=list(no.events))
+pair <- which(unique_pairs_df$initiator==current_i&unique_pairs_df$recipient==current_j)
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+### load the corresponding stan fits ####
+#print(current_cohort)
+
+## Cohort Hawkes ####
+# load the parameters for this pair
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
+                       eta_1=mean(sim_cohort_hp$eta_1),
+                       eta_2=mean(sim_cohort_hp$eta_2),
+                       eta_3=mean(sim_cohort_hp$eta_3),
+                       beta=mean(sim_cohort_hp$beta),
+                       f=apply(sim_cohort_hp$f,2,mean))
+model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
+                                                nrow=mice_number,ncol=mice_number),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model1_par_est$eta_1,
+                                                                                    model1_par_est$eta_2,
+                                                                                    model1_par_est$eta_3),
+                                                  model1_par_est$f),
+                          beta_matrix=matrix(model1_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par <- c(model1_par_matrix$lambda0_matrix[current_i,current_j],
+                model1_par_matrix$alpha[current_i,current_j],
+                        model1_par_matrix$beta[current_i,current_j])
+
+#### Degree Corrected Hawkes ####
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
+                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
+                       #lambda0=mean(sim_cohort_dchp$lambda0),
+                       eta_1=mean(sim_cohort_dchp$eta_1),
+                       eta_2=mean(sim_cohort_dchp$eta_2),
+                       eta_3=mean(sim_cohort_dchp$eta_3),
+                       beta=mean(sim_cohort_dchp$beta),
+                       f=apply(sim_cohort_dchp$f,2,mean))
+model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
+                                                model2_par_est$zeta,FUN = "+"),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model2_par_est$eta_1,
+                                                                                  model2_par_est$eta_2,
+                                                                                    model2_par_est$eta_3),
+                                                  model2_par_est$f),
+                          beta_matrix=matrix(model2_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par_dc <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
+                model2_par_matrix$alpha[current_i,current_j],
+                model2_par_matrix$beta[current_i,current_j])
+
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(sim_cohort_hp)
+rm(sim_cohort_dchp)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+c_mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
+                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
+                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
+                 beta=mean(sim_cohort_mmhp$beta),
+                 q1=mean(sim_cohort_mmhp$q1[,pair]),
+                 q2=mean(sim_cohort_mmhp$q2[,pair]))
+
+c_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+c_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=c_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/sep_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+sep_mmhp_par <- list(lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
+                 lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
+                 alpha=mean(sim_mmhp_sep$alpha[,pair]),
+                 beta=mean(sim_mmhp_sep$beta),
+                 q1=mean(sim_mmhp_sep$q1[,pair]),
+                 q2=mean(sim_mmhp_sep$q2[,pair]))
+
+sep_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+sep_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=sep_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+no_segments <- 500
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+par(mfrow=c(2,4), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
+layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
+anno.cex <- 1.3
+title.cex <- 2.2
+title.line <- 0.5
+
+#### Cohort Hawkes  ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="C-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par[1],
+                         alpha=hawkes.par[2],
+                         beta=hawkes.par[3],
+                         events=current_event_time, termination=observe_period)
+
+### DC Cohort Hawkes ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="DC-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par_dc[1],
+                         alpha=hawkes.par_dc[2],
+                         beta=hawkes.par_dc[3],
+                         events=current_event_time, termination=observe_period)
+
+#### DC C-MMHP ####
+drawRealIntensityPaper(current_event_time, object=c_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,c_mmhp.est.latent$x.hat),
+                                       z=c_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="DC C-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### Sep MMHP ####
+
+drawRealIntensityPaper(current_event_time, object=sep_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,sep_mmhp.est.latent$x.hat),
+                                       z=sep_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="I-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### then the corresponding QQ plots ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+#### Cohort Hawkes ####
+
+Lambda.c_hawkes.test <- Lambda_c_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.c_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.c_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### Cohort DC Hawkes ####
+
+Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.dc_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### DC C-MMHP ####
+Lambda.cmmhp.test <- Lambda_cmmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.cmmhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.cmmhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### I-MMHP ####
+Lambda.immhp.test <- Lambda_mmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.immhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.immhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+```
+
+### Cohort 8
+
+```{r cohort-8,cache=TRUE}
+current_cohort <- 8
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+            observe=list(observe.id),
+            observe.length=list(observe.time),
+            no.events=list(no.events)) 
+top_pairs <- unique_pairs_df %>% arrange(desc(count))
+
+best_i <- top_pairs$initiator[1]
+best_j <- top_pairs$recipient[1]
+wind <- unlist(lapply(top_pairs$no.events,which.max))[1]
+
+win_length <- top_pairs$observe.length[[1]][wind]
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+actual_win <- which(unique_observe_win$observe.time == win_length)
+
+no_segments <- 500
+
+current_i <- best_i #8
+current_j <- best_j #2
+current_win <- actual_win#wind 
+# this is the 18th window, not the 18th window with observations
+### that this pair have events in, which it should be
+
+# clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+# return_df <- cleanObservationPeriod(current_cohort, clean_data)
+# unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+#   dplyr::summarize(count=n(),
+#             observe=list(observe.id),
+#             observe.length=list(observe.time),
+#             no.events=list(no.events))
+pair <- which(unique_pairs_df$initiator==current_i&unique_pairs_df$recipient==current_j)
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+### load the corresponding stan fits ####
+#print(current_cohort)
+
+## Cohort Hawkes ####
+# load the parameters for this pair
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
+                       eta_1=mean(sim_cohort_hp$eta_1),
+                       eta_2=mean(sim_cohort_hp$eta_2),
+                       eta_3=mean(sim_cohort_hp$eta_3),
+                       beta=mean(sim_cohort_hp$beta),
+                       f=apply(sim_cohort_hp$f,2,mean))
+model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
+                                                nrow=mice_number,ncol=mice_number),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model1_par_est$eta_1,
+                                                                                    model1_par_est$eta_2,
+                                                                                    model1_par_est$eta_3),
+                                                  model1_par_est$f),
+                          beta_matrix=matrix(model1_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par <- c(model1_par_matrix$lambda0_matrix[current_i,current_j],
+                model1_par_matrix$alpha[current_i,current_j],
+                        model1_par_matrix$beta[current_i,current_j])
+
+#### Degree Corrected Hawkes ####
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
+                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
+                       #lambda0=mean(sim_cohort_dchp$lambda0),
+                       eta_1=mean(sim_cohort_dchp$eta_1),
+                       eta_2=mean(sim_cohort_dchp$eta_2),
+                       eta_3=mean(sim_cohort_dchp$eta_3),
+                       beta=mean(sim_cohort_dchp$beta),
+                       f=apply(sim_cohort_dchp$f,2,mean))
+model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
+                                                model2_par_est$zeta,FUN = "+"),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model2_par_est$eta_1,
+                                                                                  model2_par_est$eta_2,
+                                                                                    model2_par_est$eta_3),
+                                                  model2_par_est$f),
+                          beta_matrix=matrix(model2_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par_dc <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
+                model2_par_matrix$alpha[current_i,current_j],
+                model2_par_matrix$beta[current_i,current_j])
+
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(sim_cohort_hp)
+rm(sim_cohort_dchp)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+c_mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
+                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
+                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
+                 beta=mean(sim_cohort_mmhp$beta),
+                 q1=mean(sim_cohort_mmhp$q1[,pair]),
+                 q2=mean(sim_cohort_mmhp$q2[,pair]))
+
+c_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+c_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=c_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/sep_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+sep_mmhp_par <- list(lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
+                 lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
+                 alpha=mean(sim_mmhp_sep$alpha[,pair]),
+                 beta=mean(sim_mmhp_sep$beta),
+                 q1=mean(sim_mmhp_sep$q1[,pair]),
+                 q2=mean(sim_mmhp_sep$q2[,pair]))
+
+sep_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+sep_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=sep_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+no_segments <- 500
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+par(mfrow=c(2,4), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
+layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
+anno.cex <- 1.3
+title.cex <- 2.2
+title.line <- 0.5
+y.upper <- 20
+
+#### Cohort Hawkes  ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="C-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par[1],
+                         alpha=hawkes.par[2],
+                         beta=hawkes.par[3],
+                         events=current_event_time, termination=observe_period)
+
+### DC Cohort Hawkes ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="DC-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par_dc[1],
+                         alpha=hawkes.par_dc[2],
+                         beta=hawkes.par_dc[3],
+                         events=current_event_time, termination=observe_period)
+
+#### DC C-MMHP ####
+drawRealIntensityPaper(current_event_time, object=c_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,c_mmhp.est.latent$x.hat),
+                                       z=c_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="DC C-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### Sep MMHP ####
+
+drawRealIntensityPaper(current_event_time, object=sep_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,sep_mmhp.est.latent$x.hat),
+                                       z=sep_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="I-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### then the corresponding QQ plots ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+#### Cohort Hawkes ####
+
+Lambda.c_hawkes.test <- Lambda_c_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.c_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.c_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### Cohort DC Hawkes ####
+
+Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.dc_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### DC C-MMHP ####
+Lambda.cmmhp.test <- Lambda_cmmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.cmmhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.cmmhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### I-MMHP ####
+Lambda.immhp.test <- Lambda_mmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.immhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.immhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+```
+
+### Cohort 9
+
+```{r cohort-9,cache=TRUE}
+y.upper <- 60
+current_cohort <- 9
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+            observe=list(observe.id),
+            observe.length=list(observe.time),
+            no.events=list(no.events)) 
+top_pairs <- unique_pairs_df %>% arrange(desc(count))
+
+best_i <- top_pairs$initiator[1]
+best_j <- top_pairs$recipient[1]
+wind <- unlist(lapply(top_pairs$no.events,which.max))[1]
+
+win_length <- top_pairs$observe.length[[1]][wind]
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+actual_win <- which(unique_observe_win$observe.time == win_length)
+
+no_segments <- 500
+
+current_i <- best_i #8
+current_j <- best_j #2
+current_win <- actual_win[1]#wind 
+# this is the 18th window, not the 18th window with observations
+### that this pair have events in, which it should be
+
+# clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+# return_df <- cleanObservationPeriod(current_cohort, clean_data)
+# unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+#   dplyr::summarize(count=n(),
+#             observe=list(observe.id),
+#             observe.length=list(observe.time),
+#             no.events=list(no.events))
+pair <- which(unique_pairs_df$initiator==current_i&unique_pairs_df$recipient==current_j)
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+### load the corresponding stan fits ####
+#print(current_cohort)
+
+## Cohort Hawkes ####
+# load the parameters for this pair
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
+                       eta_1=mean(sim_cohort_hp$eta_1),
+                       eta_2=mean(sim_cohort_hp$eta_2),
+                       eta_3=mean(sim_cohort_hp$eta_3),
+                       beta=mean(sim_cohort_hp$beta),
+                       f=apply(sim_cohort_hp$f,2,mean))
+model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
+                                                nrow=mice_number,ncol=mice_number),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model1_par_est$eta_1,
+                                                                                    model1_par_est$eta_2,
+                                                                                    model1_par_est$eta_3),
+                                                  model1_par_est$f),
+                          beta_matrix=matrix(model1_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par <- c(model1_par_matrix$lambda0_matrix[current_i,current_j],
+                model1_par_matrix$alpha[current_i,current_j],
+                        model1_par_matrix$beta[current_i,current_j])
+
+#### Degree Corrected Hawkes ####
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
+                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
+                       #lambda0=mean(sim_cohort_dchp$lambda0),
+                       eta_1=mean(sim_cohort_dchp$eta_1),
+                       eta_2=mean(sim_cohort_dchp$eta_2),
+                       eta_3=mean(sim_cohort_dchp$eta_3),
+                       beta=mean(sim_cohort_dchp$beta),
+                       f=apply(sim_cohort_dchp$f,2,mean))
+model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
+                                                model2_par_est$zeta,FUN = "+"),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model2_par_est$eta_1,
+                                                                                  model2_par_est$eta_2,
+                                                                                    model2_par_est$eta_3),
+                                                  model2_par_est$f),
+                          beta_matrix=matrix(model2_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par_dc <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
+                model2_par_matrix$alpha[current_i,current_j],
+                model2_par_matrix$beta[current_i,current_j])
+
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(sim_cohort_hp)
+rm(sim_cohort_dchp)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+c_mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
+                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
+                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
+                 beta=mean(sim_cohort_mmhp$beta),
+                 q1=mean(sim_cohort_mmhp$q1[,pair]),
+                 q2=mean(sim_cohort_mmhp$q2[,pair]))
+
+c_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+c_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=c_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/sep_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+sep_mmhp_par <- list(lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
+                 lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
+                 alpha=mean(sim_mmhp_sep$alpha[,pair]),
+                 beta=mean(sim_mmhp_sep$beta),
+                 q1=mean(sim_mmhp_sep$q1[,pair]),
+                 q2=mean(sim_mmhp_sep$q2[,pair]))
+
+sep_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+sep_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=sep_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+no_segments <- 500
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+par(mfrow=c(2,4), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
+layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
+anno.cex <- 1.3
+title.cex <- 2.2
+title.line <- 0.5
+#y.upper <- 20
+
+#### Cohort Hawkes  ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="C-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par[1],
+                         alpha=hawkes.par[2],
+                         beta=hawkes.par[3],
+                         events=current_event_time, termination=observe_period)
+
+### DC Cohort Hawkes ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="DC-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par_dc[1],
+                         alpha=hawkes.par_dc[2],
+                         beta=hawkes.par_dc[3],
+                         events=current_event_time, termination=observe_period)
+
+#### DC C-MMHP ####
+drawRealIntensityPaper(current_event_time, object=c_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,c_mmhp.est.latent$x.hat),
+                                       z=c_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="DC C-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### Sep MMHP ####
+
+drawRealIntensityPaper(current_event_time, object=sep_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,sep_mmhp.est.latent$x.hat),
+                                       z=sep_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="I-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### then the corresponding QQ plots ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+#### Cohort Hawkes ####
+
+Lambda.c_hawkes.test <- Lambda_c_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.c_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.c_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### Cohort DC Hawkes ####
+
+Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.dc_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### DC C-MMHP ####
+Lambda.cmmhp.test <- Lambda_cmmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.cmmhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.cmmhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### I-MMHP ####
+Lambda.immhp.test <- Lambda_mmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.immhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.immhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+```
+
+### Cohort 10
+
+```{r cohort-10,cache=TRUE}
+current_cohort <- 10
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+            observe=list(observe.id),
+            observe.length=list(observe.time),
+            no.events=list(no.events)) 
+top_pairs <- unique_pairs_df %>% arrange(desc(count))
+
+best_i <- top_pairs$initiator[1]
+best_j <- top_pairs$recipient[1]
+wind <- unlist(lapply(top_pairs$no.events,which.max))[1]
+
+win_length <- top_pairs$observe.length[[1]][wind]
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+actual_win <- which(unique_observe_win$observe.time == win_length)
+
+no_segments <- 500
+
+current_i <- best_i #8
+current_j <- best_j #2
+current_win <- actual_win#wind 
+# this is the 18th window, not the 18th window with observations
+### that this pair have events in, which it should be
+
+# clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+# return_df <- cleanObservationPeriod(current_cohort, clean_data)
+# unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+#   dplyr::summarize(count=n(),
+#             observe=list(observe.id),
+#             observe.length=list(observe.time),
+#             no.events=list(no.events))
+pair <- which(unique_pairs_df$initiator==current_i&unique_pairs_df$recipient==current_j)
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+### load the corresponding stan fits ####
+#print(current_cohort)
+
+## Cohort Hawkes ####
+# load the parameters for this pair
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
+                       eta_1=mean(sim_cohort_hp$eta_1),
+                       eta_2=mean(sim_cohort_hp$eta_2),
+                       eta_3=mean(sim_cohort_hp$eta_3),
+                       beta=mean(sim_cohort_hp$beta),
+                       f=apply(sim_cohort_hp$f,2,mean))
+model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
+                                                nrow=mice_number,ncol=mice_number),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model1_par_est$eta_1,
+                                                                                    model1_par_est$eta_2,
+                                                                                    model1_par_est$eta_3),
+                                                  model1_par_est$f),
+                          beta_matrix=matrix(model1_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par <- c(model1_par_matrix$lambda0_matrix[current_i,current_j],
+                model1_par_matrix$alpha[current_i,current_j],
+                        model1_par_matrix$beta[current_i,current_j])
+
+#### Degree Corrected Hawkes ####
+load(paste(data_path, cohort_names[current_cohort],
+           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
+
+# create a list to store the hawkes parameters for this
+model2_par_est <- list(gamma = apply(sim_cohort_dchp$gamma,2,mean),
+                       zeta = apply(sim_cohort_dchp$zeta,2,mean),
+                       #lambda0=mean(sim_cohort_dchp$lambda0),
+                       eta_1=mean(sim_cohort_dchp$eta_1),
+                       eta_2=mean(sim_cohort_dchp$eta_2),
+                       eta_3=mean(sim_cohort_dchp$eta_3),
+                       beta=mean(sim_cohort_dchp$beta),
+                       f=apply(sim_cohort_dchp$f,2,mean))
+model2_par_matrix <- list(lambda0_matrix= outer(model2_par_est$gamma,
+                                                model2_par_est$zeta,FUN = "+"),
+                          alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
+                                                                                    model2_par_est$eta_1,
+                                                                                  model2_par_est$eta_2,
+                                                                                    model2_par_est$eta_3),
+                                                  model2_par_est$f),
+                          beta_matrix=matrix(model2_par_est$beta,
+                                             nrow=mice_number,ncol=mice_number))
+
+hawkes.par_dc <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
+                model2_par_matrix$alpha[current_i,current_j],
+                model2_par_matrix$beta[current_i,current_j])
+
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(sim_cohort_hp)
+rm(sim_cohort_dchp)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+c_mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
+                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
+                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
+                 beta=mean(sim_cohort_mmhp$beta),
+                 q1=mean(sim_cohort_mmhp$q1[,pair]),
+                 q2=mean(sim_cohort_mmhp$q2[,pair]))
+
+c_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+c_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=c_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+## Cohort MMHP
+load(paste(data_path,cohort_names[current_cohort],
+             "/sep_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+
+# then adjust the parameters for c-mmhp below here also
+
+sep_mmhp_par <- list(lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
+                 lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
+                 alpha=mean(sim_mmhp_sep$alpha[,pair]),
+                 beta=mean(sim_mmhp_sep$beta),
+                 q1=mean(sim_mmhp_sep$q1[,pair]),
+                 q2=mean(sim_mmhp_sep$q2[,pair]))
+
+sep_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
+                                1,
+                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
+sep_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
+                                               events=current_event_time,
+                                                       zt=sep_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
+                     termination.time=observe_period,
+                     termination.state = 2)
+
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(initial_state_list)
+rm(termination_state_list)
+
+row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
+row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
+current_event_time <- return_df[row_indicator,"event.times"][[1]]
+observe_period <- return_df[row_indicator,"observe.time"]
+no_segments <- 500
+time_segment <- seq(0,observe_period,length.out=no_segments)
+
+par(mfrow=c(2,4), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
+layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
+anno.cex <- 1.3
+title.cex <- 2.2
+title.line <- 0.5
+y.upper <- 20
+
+#### Cohort Hawkes  ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="C-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par[1],
+                         alpha=hawkes.par[2],
+                         beta=hawkes.par[3],
+                         events=current_event_time, termination=observe_period)
+
+### DC Cohort Hawkes ####
+
+drawRealIntensityPaper(current_event_time,
+                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
+                       title_name="DC-HP",
+                       title.cex=title.cex, max.x=observe_period, box.col="black")
+drawHawkesIntensityPaper(lambda0=hawkes.par_dc[1],
+                         alpha=hawkes.par_dc[2],
+                         beta=hawkes.par_dc[3],
+                         events=current_event_time, termination=observe_period)
+
+#### DC C-MMHP ####
+drawRealIntensityPaper(current_event_time, object=c_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,c_mmhp.est.latent$x.hat),
+                                       z=c_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="DC C-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### Sep MMHP ####
+
+drawRealIntensityPaper(current_event_time, object=sep_mmhp_par,title.line=title.line,
+                       simulation=list(x=c(0,sep_mmhp.est.latent$x.hat),
+                                       z=sep_mmhp.est.latent$z.hat),
+                       yupper=y.upper, color="black", line.width=2,
+                       title_name="I-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
+
+#### then the corresponding QQ plots ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+#### Cohort Hawkes ####
+
+Lambda.c_hawkes.test <- Lambda_c_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.c_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.c_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### Cohort DC Hawkes ####
+
+Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.dc_hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### DC C-MMHP ####
+Lambda.cmmhp.test <- Lambda_cmmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.cmmhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.cmmhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+#### I-MMHP ####
+Lambda.immhp.test <- Lambda_mmhp_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.immhp.test))    # 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.immhp.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
+plot(qexp(p),q, 
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
+mtext(side=1, text="TQ", line=1.6, cex=anno.cex)
+mtext(side=2, text="EQ", line=1.2, cex=anno.cex)
+Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+```

### 2020-07-08 output_scripts/Diagnostics.Rmd
add some further plots

@@
                     )
+}
+
+```
+
+# Latent Ranks vs Expert Ranks
+
+```{r}
+for(current_cohort in 1:10) {
+  #cat("Cohort, ", current_cohort,"\n",sep="")
+  load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+  mean_latent_rank <- apply(sim_cohort_mmhp$f,2,mean)
+
+  ranks <- tibble(expert = expert_rank_10[[current_cohort]],
+                  latent = mean_latent_rank)
+
+  p <- ggplot(ranks,aes(latent,expert)) + geom_point() + 
+    scale_y_continuous(breaks = c(12:1), trans = "reverse") + 
+    ggtitle(paste("Cohort ", current_cohort,sep=""))
+  print(p)
+}
+
+```
+
+# Ranks vs Degree
+
+```{r}
+
+for(current_cohort in 1:10) {
+  cat("Cohort, ", current_cohort,"\n",sep="")
+  load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+  mean_latent_rank <- apply(sim_cohort_mmhp$f,2,mean)
+
+  ranks <- tibble(expert = expert_rank_10[[current_cohort]],
+                  latent = mean_latent_rank)
+  out_degree <- apply(sim_cohort_mmhp$gamma,2,mean)
+  in_degree <- apply(sim_cohort_mmhp$zeta,2,mean)
+
+  degs <- tibble(expert = expert_rank_10[[current_cohort]],
+                  latent = mean_latent_rank,
+                 out_deg = out_degree,
+                 in_deg = in_degree)
+
+  p <- ggplot(degs,aes(latent,out_deg)) + geom_point() + 
+    #scale_y_continuous(breaks = c(12:1), trans = "reverse") + 
+    ggtitle(paste("Out Degree vs Latent Cohort ", current_cohort,sep="")) + 
+    ylab("Out Degree") + xlab("Latent Rank")
+  print(p)
+
+  q <- ggplot(degs,aes(latent,in_deg)) + geom_point() +
+    ggtitle(paste("In Degree vs Latent Cohort ",current_cohort,sep="")) +
+    ylab("In Degree") + xlab("Latent Rank")
+  print(q)
+
+  r <- ggplot(degs,aes(expert,out_deg)) + geom_point() +
+    ggtitle(paste("Out Degree vs Expert Cohort ", current_cohort,sep="")) + 
+    ylab("Out Degree") + xlab("Expert Rank")
+  print(r)
+
+  s <- ggplot(degs,aes(expert,in_deg)) + geom_point() +
+    ggtitle(paste("In Degree vs Expert Cohort ", current_cohort,sep="")) + 
+    ylab("In Degree") + xlab("Expert Rank")
+  print(s)
+
 }

### 2020-07-08 run_scripts/c_mmhp_mod.R
only run the stan fit for now

@@ -104,264 +104,264 @@ save(sim_cohort_mmhp, fit_cohort_mmhp,
                   ".RData",sep=''))
 
 #### Interpolate Latent States ####
-
-print(current_cohort)
-load(paste(save_data_path,cohort_names[current_cohort],
-           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
-clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-return_df <- cleanObservationPeriod(current_cohort, clean_data)
-unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
-  summarize(count=n(),
-            observe=list(observe.id),
-            observe.length=list(observe.time),
-            no.events=list(no.events))
-unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
-
-num_winds <- nrow(unique_observe_win)
-
-state_array_list <- list()
-initial_state_list <- list()
-termination_state_list <- list()
-interpolation_array_list <- list()
-#no_segments <- 5000 # changed this from 5000
-# specify this above
-
-param <- rep(list(),1000)
-for(s in 1:1000){
-  model3_par_est <- list(gamma=sim_cohort_mmhp$gamma[s,],
-                         zeta=sim_cohort_mmhp$zeta[s,],
-                         lambda1=sim_cohort_mmhp$lambda1[s],
-                         eta_1=sim_cohort_mmhp$eta_1[s],
-                         eta_2=sim_cohort_mmhp$eta_2[s],
-                         eta_3=sim_cohort_mmhp$eta_3[s],
-                         beta=sim_cohort_mmhp$beta[s],
-                         w_lambda = sim_cohort_mmhp$w_lambda[s],
-                         f=sim_cohort_mmhp$f[s,])
-  param[[s]] <- list(lambda0_matrix = outer(model3_par_est$gamma, model3_par_est$zeta, FUN = "+"),
-                     # lambda0_matrix=matrix(model3_par_est$lambda0,
-                     #                       nrow=mice_number,ncol=mice_number),
-                     # lambda1_matrix=matrix(model3_par_est$lambda1,
-                     #                       nrow=mice_number,ncol=mice_number),
-                     lambda1_matrix = outer(model3_par_est$gamma,
-                                            model3_par_est$zeta, FUN = "+")*(1+model3_par_est$w_lambda),
-                     alpha_matrix=formMatrix(function(x,y) model3_fn$alpha.fun(x,y,
[…]

### 2020-07-09 run_scripts/c_mmhp_mod.R
adjust the adapt delta and max tree depth for these

@@ -95,7 +95,7 @@ stan_input_lst$delta_1 <- rep(0.5,stan_input_lst$N_til)
 fit_cohort_mmhp <- stan("lib/model3_1_bound.stan",  ## this will need to be updated
                         data = stan_input_lst,
                         warmup = 1000, iter = 2000, chains = 4, thin=4,
-                        control=list(adapt_delta=0.999,max_treedepth=15))
+                        control=list(adapt_delta=0.9))
 sim_cohort_mmhp <- rstan::extract(fit_cohort_mmhp)
 dir.create(paste(save_data_path, cohort_names[current_cohort],sep=''), recursive = TRUE, showWarnings = FALSE)
 save(sim_cohort_mmhp, fit_cohort_mmhp,

### 2020-07-09 output_scripts/Paper_Plots.Rmd
update diagnostics and paper plots
update the paper plots

@@
 author: "Owen G. Ward"
+date: '`r Sys.Date()`'
 output:
   html_document:
-    df_print: paged
     toc: true
+    toc_depth: 2
     toc_float: true
+    number_sections: FALSE
+    code_folding: hide
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_knit$set(root.dir = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/", echo = FALSE, include = FALSE,
-                     message=FALSE)
-# setting these to false to only show updates
-knitr::opts_chunk$set(message = FALSE)
+knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
+                      dev = 'png', fig.height = 4.5, fig.width = 7,
+                      warning = FALSE)
 ```
 
-```{r, load_packages, include=FALSE}
+```{r load_packages, include=FALSE}
 
 # don't write to this path
-orig_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"
+data_path <- "../output/"
 
-new_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_orig_code/"
-
-func_dir <- "C:/Users/owenw/Dropbox/with Owen/code/part2/lib/"
+func_dir <- "../lib/"
 
@@
 
-```{r more_setup}
-#data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"
-jing_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"
-plot_path = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/"
-
-```
-
-```{r,echo=FALSE,include=FALSE}
-full_data <- readRDS("C:/Users/owenw/Dropbox/with Owen/code/part2/data/mice.RData")
+```{r load rankings,echo=FALSE,include=FALSE,results='hide',cache=TRUE}
+full_data <- readRDS("../data/mice.RData")
 # A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
@@
 The aim of this notebook is a way to quickly and efficiently create all the plots
-required for this paper. We will currently build them using the refit version of Jing's fit,
-which ignored windows with no events (to confirm we can recreate that exactly).
-
-```{r}
-data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"
-```
+required for this paper. They will be built with the current fits and models.
 
@@
 
-```{r}
+```{r fig-2a-contour-plot}
 current_cohort <- 1
-png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
-load(paste(jing_data_path,cohort_names[current_cohort],
+#png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
+load(paste(data_path,cohort_names[current_cohort],
            "/cohort_hp_stan_result_",cohort_names[current_cohort],
@@
               cex.lab=2.5, xLabels=c(1,0), yLabels=c(0,1))
-dev.off()
-
-my.image.plot(seq(0,1,0.01), seq(0,1,0.01), z_plot,
-              xlab=expression(f[j]),ylab=expression(f[i]),
-              my.main="(a)", cex.main=2.3, 
-              cex.lab=2.5, xLabels=c(1,0), yLabels=c(0,1))
 
@@
 
-```{r,echo=FALSE}
-load(paste(jing_data_path,cohort_names[current_cohort],
+```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE}
+load(paste(data_path,cohort_names[current_cohort],
            "/cohort_hp_stan_result_",cohort_names[current_cohort],
@@
 
-png(paste(plot_path,"/diagonsis_model1_",cohort_names[current_cohort],".png",sep=''),
-    width=480,height=480)
+# png(paste(plot_path,"/diagonsis_model1_",cohort_names[current_cohort],".png",sep=''),
+#     width=480,height=480)
 # -------------- KS plot (stat)
@@
       at=0.45, font=2)
-dev.off()
+#dev.off()
 ```
@@
 
-```{r}
-load(paste(jing_data_path,cohort_names[current_cohort],
+```{r fig-3a-baseline-rate}
+load(paste(data_path,cohort_names[current_cohort],
            "/cohort_dchp_stan_result_",cohort_names[current_cohort],
@@
 
-png(paste(plot_path,"/lambda0_",cohort_names[current_cohort],".png",sep=''),
-    width=400, height=300)
+# png(paste(plot_path,"/lambda0_",cohort_names[current_cohort],".png",sep=''),
+#     width=400, height=300)
 matrixPlotParameter(latent_social_matrix[rev(expert_rank_10[[current_cohort]]),expert_rank_10[[current_cohort]]],
@@
                     yLabels=rev(expert_rank_10[[current_cohort]]),title="(a)")
-mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
-      at=1/17.8*seq(2,12,2)+0.09)
-dev.off()
+# mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
+#       at=1/17.8*seq(2,12,2)+0.09)
+#dev.off()
 ```
@@
 
-```{r}
+```{r fig-3b-rank-comparison}
 current_cohort <- 1
 colors_plot <- viridis(2)
-load(paste(jing_data_path,cohort_names[current_cohort],
+load(paste(data_path,cohort_names[current_cohort],
            "/cohort_hp_stan_result_",cohort_names[current_cohort],
            ".RData",sep=''))
-load(paste(jing_data_path,cohort_names[current_cohort],
+load(paste(data_path,cohort_names[current_cohort],
            "/cohort_dchp_stan_result_",cohort_names[current_cohort],
            ".RData",sep=''))
-png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
-    width=400, height=300)
+# png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
+#     width=400, height=300)
 par(oma = c(0,0,2,0), mar = c(3,4,1,1),mgp=c(0,0.5,0))
@@
        cex=1.5)
-dev.off()
+#dev.off()
 ```
+
 # Figure 4:
@@
 
-```{r}
+```{r fig-6a-rank-vs-isi}
 ### Rank Comparison for Single Cohort ####
@@
 
-load(paste(jing_data_path,cohort_names[current_cohort],
+load(paste(data_path,cohort_names[current_cohort],
            "/agg_rank_stan_result_",cohort_names[current_cohort],
            ".RData",sep=''))
-load(paste(jing_data_path,cohort_names[current_cohort],
+load(paste(data_path,cohort_names[current_cohort],
            "/cohort_hp_stan_result_",cohort_names[current_cohort],
            ".RData",sep=''))
-load(paste(jing_data_path,cohort_names[current_cohort],
+load(paste(data_path,cohort_names[current_cohort],
            "/cohort_dchp_stan_result_",cohort_names[current_cohort],
            ".RData",sep=''))
-load(paste(jing_data_path,cohort_names[current_cohort],
+load(paste(data_path,cohort_names[current_cohort],
            "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
@@
 
-png(paste(plot_path,"real_rank_one_cohort.png",sep=""),width=600,height=300)
+# png(paste(plot_path,"real_rank_one_cohort.png",sep=""),width=600,height=300)
 
-p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
+p1 <- ggplot(plot_latent_df, 
+             aes(x = Mice, y = force, fill = Method)) +
   geom_boxplot(alpha=0.7) +
@@
         text = element_text(size = 20),
-        axis.text.x=element_text(size = 11),
+        axis.text.x=element_text(size = 10),
         legend.position="none") +
@@
 p1
-dev.off()
-p1
-beepr::beep()
+#dev.off()
+
 ```
@@
 
-# Figure 7: Pearson residual matrices
+<!-- # Figure 7: Pearson residual matrices -->
 
-Here is where I need to be a bit more careful about using the correct fits.
-Currently using all from Jing's saved output.
+<!-- Here is where I need to be a bit more careful about using the correct fits. -->
+<!-- Currently using all from Jing's saved output. -->
 
-In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices.
+<!-- In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices. -->
 
-```{r}
-current_cohort <- 1
+<!-- ```{r} -->
+<!-- current_cohort <- 1 -->
 
-m1_residual_matrix_lst <- list()
-m2_residual_matrix_lst <- list()
-m3_residual_matrix_lst <- list()
-mmhp_residual_matrix_lst <- list()
+<!-- m1_residual_matrix_lst <- list() -->
+<!-- m2_residual_matrix_lst <- list() -->
+<!-- m3_residual_matrix_lst <- list() -->
+<!-- mmhp_residual_matrix_lst <- list() -->
 
-  print(current_cohort)
-  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-  return_df <- cleanObservationPeriod(current_cohort, clean_data)
-  unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
-    summarize(count=n(),
-              observe=list(observe.id),
-              observe.length=list(observe.time),
-              no.events=list(no.events))
-  unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+<!--   print(current_cohort) -->
+<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
+<!--   return_df <- cleanObservationPeriod(current_cohort, clean_data) -->
+<!--   unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% -->
+<!--     summarize(count=n(), -->
+<!--               observe=list(observe.id), -->
+<!--               observe.length=list(observe.time), -->
+<!--               no.events=list(no.events)) -->
+<!--   unique_observe_win <- unique(return_df[,c("observe.id","observe.time")]) -->
 
-  # M1
-  load(paste(jing_data_path,cohort_names[current_cohort],
-             "/cohort_hp_stan_result_",cohort_names[current_cohort],
-             ".RData",sep=''))
-  model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
-                         eta_1=mean(sim_cohort_hp$eta_1),
-                         eta_2=mean(sim_cohort_hp$eta_2),
-                         eta_3=mean(sim_cohort_hp$eta_3),
-                         beta=mean(sim_cohort_hp$beta),
-                         f=apply(sim_cohort_hp$f,2,mean))
-  model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
-                                                  nrow=mice_number,ncol=mice_number),
-                            alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
-                                                                                      model1_par_est$eta_1,
-                                                                                      model1_par_est$eta_2,
-                                                                                      model1_par_est$eta_3),
-                                                    model1_par_est$f),
-                            beta_matrix=matrix(model1_par_est$beta,
-                                               nrow=mice_number,ncol=mice_number))
-  m1_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
+<!--   # M1 -->
+<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
+<!--              "/cohort_hp_stan_result_",cohort_names[current_cohort], -->
+<!--              ".RData",sep='')) -->
+<!--   model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0), -->
+<!--                          eta_1=mean(sim_cohort_hp$eta_1), -->
+<!--                          eta_2=mean(sim_cohort_hp$eta_2), -->
+<!--                          eta_3=mean(sim_cohort_hp$eta_3), -->
+<!--                          beta=mean(sim_cohort_hp$beta), -->
+<!--                          f=apply(sim_cohort_hp$f,2,mean)) -->
+<!--   model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0, -->
+<!--                                                   nrow=mice_number,ncol=mice_number), -->
+<!--                             alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y, -->
+<!--                                                                                       model1_par_est$eta_1, -->
+<!--                                                                                       model1_par_est$eta_2, -->
+<!--                                                                                       model1_par_est$eta_3), -->
+<!--                                                     model1_par_est$f), -->
+<!--                             beta_matrix=matrix(model1_par_est$beta, -->
+<!--                                                nrow=mice_number,ncol=mice_number)) -->
+<!--   m1_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
 
-  for(i in 1:mice_number){
-    for(j in 1:mice_number){
-      pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
-      if(length(pair)>0&(i!=j)){
-        par_est <- lapply(model1_par_matrix, function(x) x[i,j])
-        names(par_est) <- c("lambda0","alpha","beta")
-        current_window_vec <- unique_pairs_df$observe[[pair]]
-        all_residual <- 0
-        for(cur in c(1:length(current_window_vec))){ ## check length > 2
-          cur_win <- current_window_vec[cur]
-          current_event_time <- return_df[return_df$initiator==i&
-                                            return_df$recipient==j&
-                                            return_df$observe.id==cur_win,"event.times"][[1]]
-          current_obs_time <- return_df[return_df$initiator==i&
-                                          return_df$recipient==j&
-                                          return_df$observe.id==cur_win,"observe.time"]
-          all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est,
-                                                                  events=current_event_time,
-                                                                  termination = current_obs_time)
-        }
-        m1_residual_matrix[i,j] <- all_residual
-      }
-    }
-  }
+<!--   for(i in 1:mice_number){ -->
+<!--     for(j in 1:mice_number){ -->
+<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
+<!--       if(length(pair)>0&(i!=j)){ -->
+<!--         par_est <- lapply(model1_par_matrix, function(x) x[i,j]) -->
+<!--         names(par_est) <- c("lambda0","alpha","beta") -->
+<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
+<!--         all_residual <- 0 -->
+<!--         for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
+<!--           cur_win <- current_window_vec[cur] -->
+<!--           current_event_time <- return_df[return_df$initiator==i& -->
+<!--                                             return_df$recipient==j& -->
+<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
+<!--           current_obs_time <- return_df[return_df$initiator==i& -->
+<!--                                           return_df$recipient==j& -->
+<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
+<!--           all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est, -->
+<!--                                                                   events=current_event_time, -->
+<!--                                                                   termination = current_obs_time) -->
+<!--         } -->
+<!--         m1_residual_matrix[i,j] <- all_residual -->
+<!--       } -->
+<!--     } -->
+<!--   } -->
 
-  # M2
-  load(paste(jing_data_path,cohort_names[current_cohort],
-             "/cohort_dchp_stan_result_",cohort_names[current_cohort],
-             ".RData",sep=''))
-  model2_par_est <- list(gamma=apply(sim_cohort_dchp$gamma,2,mean),
-                         zeta=apply(sim_cohort_dchp$zeta,2,mean),
-                         eta_1=mean(sim_cohort_dchp$eta_1),
-                         eta_2=mean(sim_cohort_dchp$eta_2),
-                         eta_3=mean(sim_cohort_dchp$eta_3),
-                         beta=mean(sim_cohort_dchp$beta),
-                         f=apply(sim_cohort_dchp$f,2,mean))
-  model2_par_matrix <- list(lambda0_matrix=model2_par_est$gamma%*%t(rep(1,mice_number))+
-                              rep(1,mice_number)%*%t(model2_par_est$zeta),
-                            alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
-                                                                                      model2_par_est$eta_1,
-                                                                                      model2_par_est$eta_2,
-                                                                                      model2_par_est$eta_3),
-                                                    model2_par_est$f),
-                            beta_matrix=matrix(model2_par_est$beta,
-                                               nrow=mice_number,ncol=mice_number))
-  m2_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
+<!--   # M2 -->
+<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
+<!--              "/cohort_dchp_stan_result_",cohort_names[current_cohort], -->
+<!--              ".RData",sep='')) -->
+<!--   model2_par_est <- list(gamma=apply(sim_cohort_dchp$gamma,2,mean), -->
+<!--                          zeta=apply(sim_cohort_dchp$zeta,2,mean), -->
+<!--                          eta_1=mean(sim_cohort_dchp$eta_1), -->
+<!--                          eta_2=mean(sim_cohort_dchp$eta_2), -->
+<!--                          eta_3=mean(sim_cohort_dchp$eta_3), -->
+<!--                          beta=mean(sim_cohort_dchp$beta), -->
+<!--                          f=apply(sim_cohort_dchp$f,2,mean)) -->
+<!--   model2_par_matrix <- list(lambda0_matrix=model2_par_est$gamma%*%t(rep(1,mice_number))+ -->
+<!--                               rep(1,mice_number)%*%t(model2_par_est$zeta), -->
+<!--                             alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y, -->
+<!--                                                                                       model2_par_est$eta_1, -->
+<!--                                                                                       model2_par_est$eta_2, -->
+<!--                                                                                       model2_par_est$eta_3), -->
+<!--                                                     model2_par_est$f), -->
+<!--                             beta_matrix=matrix(model2_par_est$beta, -->
+<!--                                                nrow=mice_number,ncol=mice_number)) -->
+<!--   m2_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
 
-  for(i in 1:mice_number){
-    for(j in 1:mice_number){
-      pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
-      if(length(pair)>0&(i!=j)){
-        par_est <- lapply(model2_par_matrix, function(x) x[i,j])
-        names(par_est) <- c("lambda0","alpha","beta")
-        current_window_vec <- unique_pairs_df$observe[[pair]]
-        all_residual <- 0
-        for(cur in c(1:length(current_window_vec))){ 
-          cur_win <- current_window_vec[cur]
-          current_event_time <- return_df[return_df$initiator==i&
-                                            return_df$recipient==j&
-                                            return_df$observe.id==cur_win,"event.times"][[1]]
-          current_obs_time <- return_df[return_df$initiator==i&
-                                          return_df$recipient==j&
-                                          return_df$observe.id==cur_win,"observe.time"]
-          all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est,
-                                                                  events=current_event_time,
-                                                                  termination = current_obs_time)
-        }
-        m2_residual_matrix[i,j] <- all_residual
-      }
-    }
-  }
+<!--   for(i in 1:mice_number){ -->
+<!--     for(j in 1:mice_number){ -->
+<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
+<!--       if(length(pair)>0&(i!=j)){ -->
+<!--         par_est <- lapply(model2_par_matrix, function(x) x[i,j]) -->
+<!--         names(par_est) <- c("lambda0","alpha","beta") -->
+<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
+<!--         all_residual <- 0 -->
+<!--         for(cur in c(1:length(current_window_vec))){  -->
+<!--           cur_win <- current_window_vec[cur] -->
+<!--           current_event_time <- return_df[return_df$initiator==i& -->
+<!--                                             return_df$recipient==j& -->
+<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
+<!--           current_obs_time <- return_df[return_df$initiator==i& -->
+<!--                                           return_df$recipient==j& -->
+<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
+<!--           all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est, -->
+<!--                                                                   events=current_event_time, -->
+<!--                                                                   termination = current_obs_time) -->
+<!--         } -->
+<!--         m2_residual_matrix[i,j] <- all_residual -->
+<!--       } -->
+<!--     } -->
+<!--   } -->
 
-```
+<!-- ```   -->
 
-This is too large to load at the moment again. Can do this on the cluster.
+<!-- This is too large to load at the moment again. Can do this on the cluster. -->
 
-```{r, eval=FALSE}  
-  # M3
-  load(paste(jing_data_path,cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
-             ".RData",sep=''))
-  load(paste(jing_data_path,cohort_names[current_cohort],
-             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
-  model3_par_est <- list(lambda0=mean(sim_cohort_mmhp$lambda0),
-                         lambda1=mean(sim_cohort_mmhp$lambda1),
-                         eta_1=mean(sim_cohort_mmhp$eta_1),
-                         eta_2=mean(sim_cohort_mmhp$eta_2),
-                         eta_3=mean(sim_cohort_mmhp$eta_3),
-                         beta=mean(sim_cohort_mmhp$beta),
-                         f=apply(sim_cohort_mmhp$f,2,mean))
-  model3_par_matrix <- list(lambda0_matrix=matrix(model3_par_est$lambda0,
-                                                  nrow=mice_number,ncol=mice_number),
-                            lambda1_matrix=matrix(model3_par_est$lambda1,
-                                                  nrow=mice_number,ncol=mice_number),
-                            alpha_matrix=formMatrix(function(x,y) model3_fn$alpha.fun(x,y,
-                                                                                      model3_par_est$eta_1,
-                                                                                      model3_par_est$eta_2),
-                                                    model3_par_est$f),
-                            beta_matrix=matrix(model3_par_est$beta,
-                                               nrow=mice_number,ncol=mice_number),
-                            q1_matrix=formMatrix(function(x,y) model3_fn$q1.fun(x,y,model3_par_est$eta_3),
-                                                 model3_par_est$f),
-                            q2_matrix=formMatrix(function(x,y) model3_fn$q0.fun(x,y,model3_par_est$eta_3),
-                                                 model3_par_est$f))
-  m3_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
-  no_segments <- 5000 # changed from 5000
-  window_pr <- c()
-  for(i in 1:mice_number){
-    print(i)
-    for(j in 1:mice_number){
-      pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
-      if(length(pair)>0&(i!=j)){
-        par_est <- lapply(model3_par_matrix, function(x) x[i,j])
-        names(par_est) <- c("lambda0","lambda1","alpha","beta","q1","q2")
-        current_window_vec <- unique_pairs_df$observe[[pair]]
-        all_residual <- 0
-        for(cur in c(1:length(current_window_vec))){ ## check length > 2
-          cur_win <- current_window_vec[cur]
-          current_event_time <- return_df[return_df$initiator==i&
-                                            return_df$recipient==j&
-                                            return_df$observe.id==cur_win,"event.times"][[1]]
-          current_obs_time <- return_df[return_df$initiator==i&
-                                          return_df$recipient==j&
-                                          return_df$observe.id==cur_win,"observe.time"]
-          time_segment <- seq(0,current_obs_time,length.out=no_segments)
-          latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean)
-          latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5) 
-          est.intensity <- mmhpIntensityNumeric(params=par_est,
-                                                t=current_event_time,
-                                                time.vec=time_segment,
-                                                latent.vec=latent_mean)
-          est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time,
-                                                        latent_z=latent_event)
-          all_residual <- all_residual + sum(1/sqrt(est.intensity.events))-
-            sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])
-          # print(sum(1/sqrt(est.intensity.events))-
-          #         sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1]))
-          # print(summary(latent_mean))
-          # window_pr <- c(window_pr,sum(1/sqrt(est.intensity.events))-
-          #                  sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1]))
-        }
-        m3_residual_matrix[i,j] <- all_residual
-      }
-    }
-  }
+<!-- ```{r, eval=FALSE}   -->
+<!--   # M3 -->
+<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
+<!--              "/cohort_mmhp_stan_result_",cohort_names[current_cohort], -->
+<!--              ".RData",sep='')) -->
+<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
+<!--              "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep='')) -->
+<!--   model3_par_est <- list(lambda0=mean(sim_cohort_mmhp$lambda0), -->
+<!--                          lambda1=mean(sim_cohort_mmhp$lambda1), -->
+<!--                          eta_1=mean(sim_cohort_mmhp$eta_1), -->
+<!--                          eta_2=mean(sim_cohort_mmhp$eta_2), -->
+<!--                          eta_3=mean(sim_cohort_mmhp$eta_3), -->
+<!--                          beta=mean(sim_cohort_mmhp$beta), -->
+<!--                          f=apply(sim_cohort_mmhp$f,2,mean)) -->
+<!--   model3_par_matrix <- list(lambda0_matrix=matrix(model3_par_est$lambda0, -->
+<!--                                                   nrow=mice_number,ncol=mice_number), -->
+<!--                             lambda1_matrix=matrix(model3_par_est$lambda1, -->
+<!--                                                   nrow=mice_number,ncol=mice_number), -->
+<!--                             alpha_matrix=formMatrix(function(x,y) model3_fn$alpha.fun(x,y, -->
+<!--                                                                                       model3_par_est$eta_1, -->
+<!--                                                                                       model3_par_est$eta_2), -->
+<!--                                                     model3_par_est$f), -->
+<!--                             beta_matrix=matrix(model3_par_est$beta, -->
+<!--                                                nrow=mice_number,ncol=mice_number), -->
+<!--                             q1_matrix=formMatrix(function(x,y) model3_fn$q1.fun(x,y,model3_par_est$eta_3), -->
+<!--                                                  model3_par_est$f), -->
+<!--                             q2_matrix=formMatrix(function(x,y) model3_fn$q0.fun(x,y,model3_par_est$eta_3), -->
+<!--                                                  model3_par_est$f)) -->
+<!--   m3_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
+<!--   no_segments <- 5000 # changed from 5000 -->
+<!--   window_pr <- c() -->
+<!--   for(i in 1:mice_number){ -->
+<!--     print(i) -->
+<!--     for(j in 1:mice_number){ -->
+<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
+<!--       if(length(pair)>0&(i!=j)){ -->
+<!--         par_est <- lapply(model3_par_matrix, function(x) x[i,j]) -->
+<!--         names(par_est) <- c("lambda0","lambda1","alpha","beta","q1","q2") -->
+<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
+<!--         all_residual <- 0 -->
+<!--         for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
+<!--           cur_win <- current_window_vec[cur] -->
+<!--           current_event_time <- return_df[return_df$initiator==i& -->
+<!--                                             return_df$recipient==j& -->
+<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
+<!--           current_obs_time <- return_df[return_df$initiator==i& -->
+<!--                                           return_df$recipient==j& -->
+<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
+<!--           time_segment <- seq(0,current_obs_time,length.out=no_segments) -->
+<!--           latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean) -->
+<!--           latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5)  -->
+<!--           est.intensity <- mmhpIntensityNumeric(params=par_est, -->
+<!--                                                 t=current_event_time, -->
+<!--                                                 time.vec=time_segment, -->
+<!--                                                 latent.vec=latent_mean) -->
+<!--           est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time, -->
+<!--                                                         latent_z=latent_event) -->
+<!--           all_residual <- all_residual + sum(1/sqrt(est.intensity.events))- -->
+<!--             sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1]) -->
+<!--           # print(sum(1/sqrt(est.intensity.events))- -->
+<!--           #         sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])) -->
+<!--           # print(summary(latent_mean)) -->
+<!--           # window_pr <- c(window_pr,sum(1/sqrt(est.intensity.events))- -->
+<!--           #                  sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])) -->
+<!--         } -->
+<!--         m3_residual_matrix[i,j] <- all_residual -->
+<!--       } -->
+<!--     } -->
+<!--   } -->
 
-```  
-These are in part 1 of the thesis folder on Google Drive.
+<!-- ```   -->
+<!-- These are in part 1 of the thesis folder on Google Drive. -->
 
-```{r, eval=FALSE}
-ind_mmhp_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part1/real_data/"
-  # Independent MMHP
-  load(paste(ind_mmhp_data_path, cohort_names[current_cohort], 
-             "/sep_mmhp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
-  load(paste(ind_mmhp_data_path,cohort_names[current_cohort],
-             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
+<!-- ```{r, eval=FALSE} -->
+<!-- ind_mmhp_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part1/real_data/" -->
+<!--   # Independent MMHP -->
+<!--   load(paste(ind_mmhp_data_path, cohort_names[current_cohort],  -->
+<!--              "/sep_mmhp_stan_result_", cohort_names[current_cohort],".RData",sep='')) -->
+<!--   load(paste(ind_mmhp_data_path,cohort_names[current_cohort], -->
+<!--              "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep='')) -->
 
-  mmhp_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
-  for(i in 1:mice_number){
-    print(i)
-    for(j in 1:mice_number){
-      pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
-      if(length(pair)>0&(i!=j)){
-        par_est <- list(lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
-                        lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
-                        alpha=mean(sim_mmhp_sep$alpha[,pair]),
-                        beta=mean(sim_mmhp_sep$beta[,pair]),
-                        q1=mean(sim_mmhp_sep$q1[,pair]),
-                        q2=mean(sim_mmhp_sep$q2[,pair]))
-        current_window_vec <- unique_pairs_df$observe[[pair]]
-        all_residual <- 0
-        for(cur in c(1:length(current_window_vec))){ ## check length > 2
-          cur_win <- current_window_vec[cur]
-          current_event_time <- return_df[return_df$initiator==i&
-                                            return_df$recipient==j&
-                                            return_df$observe.id==cur_win,"event.times"][[1]]
-          current_obs_time <- return_df[return_df$initiator==i&
-                                          return_df$recipient==j&
-                                          return_df$observe.id==cur_win,"observe.time"]
-          time_segment <- seq(0,current_obs_time,length.out=no_segments)
-          latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean)
-          latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5) 
-          est.intensity <- mmhpIntensityNumeric(params=par_est,
-                                                t=current_event_time,
-                                                time.vec=time_segment,
-                                                latent.vec=latent_mean)
-          est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time,
-                                                        latent_z=latent_event)
-          all_residual <- all_residual + sum(1/sqrt(est.intensity.events))-
-            sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])
-        }
-        mmhp_residual_matrix[i,j] <- all_residual
-      }
-    }
-  }
-  m1_residual_matrix_lst[[current_cohort]] <- m1_residual_matrix
-  m2_residual_matrix_lst[[current_cohort]] <- m2_residual_matrix
-  m3_residual_matrix_lst[[current_cohort]] <- m3_residual_matrix
-  mmhp_residual_matrix_lst[[current_cohort]] <- mmhp_residual_matrix
+<!--   mmhp_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
+<!--   for(i in 1:mice_number){ -->
+<!--     print(i) -->
+<!--     for(j in 1:mice_number){ -->
+<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
+<!--       if(length(pair)>0&(i!=j)){ -->
+<!--         par_est <- list(lambda0=mean(sim_mmhp_sep$lambda0[,pair]), -->
+<!--                         lambda1=mean(sim_mmhp_sep$lambda1[,pair]), -->
+<!--                         alpha=mean(sim_mmhp_sep$alpha[,pair]), -->
+<!--                         beta=mean(sim_mmhp_sep$beta[,pair]), -->
+<!--                         q1=mean(sim_mmhp_sep$q1[,pair]), -->
+<!--                         q2=mean(sim_mmhp_sep$q2[,pair])) -->
+<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
+<!--         all_residual <- 0 -->
+<!--         for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
+<!--           cur_win <- current_window_vec[cur] -->
+<!--           current_event_time <- return_df[return_df$initiator==i& -->
+<!--                                             return_df$recipient==j& -->
+<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
+<!--           current_obs_time <- return_df[return_df$initiator==i& -->
+<!--                                           return_df$recipient==j& -->
+<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
+<!--           time_segment <- seq(0,current_obs_time,length.out=no_segments) -->
+<!--           latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean) -->
+<!--           latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5)  -->
+<!--           est.intensity <- mmhpIntensityNumeric(params=par_est, -->
+<!--                                                 t=current_event_time, -->
+<!--                                                 time.vec=time_segment, -->
+<!--                                                 latent.vec=latent_mean) -->
+<!--           est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time, -->
+<!--                                                         latent_z=latent_event) -->
+<!--           all_residual <- all_residual + sum(1/sqrt(est.intensity.events))- -->
+<!--             sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1]) -->
+<!--         } -->
+<!--         mmhp_residual_matrix[i,j] <- all_residual -->
+<!--       } -->
+<!--     } -->
+<!--   } -->
+<!--   m1_residual_matrix_lst[[current_cohort]] <- m1_residual_matrix -->
+<!--   m2_residual_matrix_lst[[current_cohort]] <- m2_residual_matrix -->
+<!--   m3_residual_matrix_lst[[current_cohort]] <- m3_residual_matrix -->
+<!--   mmhp_residual_matrix_lst[[current_cohort]] <- mmhp_residual_matrix -->
 
-save(m1_residual_matrix_lst, m2_residual_matrix_lst, m3_residual_matrix_lst, mmhp_residual_matrix_lst,
-     file = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/pearson_residual_cohort9.RData")
-beepr::beep()
-```
-These would need to be rerun correctly and saved.
-For now using an *old* version.
+<!-- save(m1_residual_matrix_lst, m2_residual_matrix_lst, m3_residual_matrix_lst, mmhp_residual_matrix_lst, -->
+<!--      file = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/pearson_residual_cohort9.RData") -->
+<!-- beepr::beep() -->
+<!-- ``` -->
+<!-- These would need to be rerun correctly and saved. -->
+<!-- For now using an *old* version. -->
 
-```{r}
-load("C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/pearson_residual_cohort9.RData")
-png(paste(plot_path,"real_residual_matrix_one_cohort.png",sep=""),width = 800,height = 400)
-matrix_lst_plot <- list(
-                        mmhp_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]),
-                                                                   expert_rank_10[[current_cohort]]],
-                        m1_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]),
-                                                                 expert_rank_10[[current_cohort]]],
-                        m2_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]),
-                                                                 expert_rank_10[[current_cohort]]],
-                        m3_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]),
-                                                                 expert_rank_10[[current_cohort]]]) 
-myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
-                  xLabels=expert_rank_10[[current_cohort]],
-                  yLabels=rev(expert_rank_10[[current_cohort]]),
-                  min=-63,max=63,axis_cex=2,title_cex = 1.8,
-                  colorPalette="RdBu",if.emp=FALSE,legend.mar=c(0.5,.5,0.5,0.95),
-                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
-                  #title_lst = list("I-MMHP"),
-                  col_axis=c(-60,-30,0,30,60), out.title="", fake_matrix=FALSE,
-                  matrix.mar=c(2.5,2.5,2.5,2))
-dev.off()
-```
-The remaining plot code seems to mostly be in `PaperPlots.R`.
+<!-- ```{r} -->
+<!-- load("C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/pearson_residual_cohort9.RData") -->
+<!-- png(paste(plot_path,"real_residual_matrix_one_cohort.png",sep=""),width = 800,height = 400) -->
+<!-- matrix_lst_plot <- list( -->
+<!--                         mmhp_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]), -->
+<!--                                                                    expert_rank_10[[current_cohort]]], -->
+<!--                         m1_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]), -->
+<!--                                                                  expert_rank_10[[current_cohort]]], -->
+<!--                         m2_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]), -->
+<!--                                                                  expert_rank_10[[current_cohort]]], -->
+<!--                         m3_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]), -->
+<!--                                                                  expert_rank_10[[current_cohort]]])  -->
+<!-- myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2, -->
+<!--                   xLabels=expert_rank_10[[current_cohort]], -->
+<!--                   yLabels=rev(expert_rank_10[[current_cohort]]), -->
+<!--                   min=-63,max=63,axis_cex=2,title_cex = 1.8, -->
+<!--                   colorPalette="RdBu",if.emp=FALSE,legend.mar=c(0.5,.5,0.5,0.95), -->
+<!--                   title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"),  -->
+<!--                   #title_lst = list("I-MMHP"), -->
+<!--                   col_axis=c(-60,-30,0,30,60), out.title="", fake_matrix=FALSE, -->
+<!--                   matrix.mar=c(2.5,2.5,2.5,2)) -->
+<!-- dev.off() -->
+<!-- ``` -->
+<!-- The remaining plot code seems to mostly be in `PaperPlots.R`. -->
 
-# Figure 8
+<!-- # Figure 8 -->
 
-## Figure 8a: Frobenius norm of interaction predictions, single cohort
+<!-- ## Figure 8a: Frobenius norm of interaction predictions, single cohort -->
 
-## Figure 8b: Same plot aggregated for all cohorts
+<!-- ## Figure 8b: Same plot aggregated for all cohorts -->
 
-# Figure 9
+<!-- # Figure 9 -->
 
-## Figure 9a: Predicted Spearman rank for single cohort
+<!-- ## Figure 9a: Predicted Spearman rank for single cohort -->
 
-## Figure 9b: Predicted Spearman rank for all cohorts
+<!-- ## Figure 9b: Predicted Spearman rank for all cohorts -->
 
-# Figure 10
+<!-- # Figure 10 -->

### 2020-07-09 output_scripts/Diagnostics.Rmd
small changes to the diagnostics

@@
 ---
-title: "Diagnostics Week of June 28th"
+title: "Diagnostics"
 author: "Owen Ward"
-date: "6/30/2020"
+date: '`r Sys.Date()`'
 output: 
@@
 
-  ranks <- tibble(expert = expert_rank_10[[current_cohort]],
-                  latent = mean_latent_rank)
+  ranks <- tibble(expert = 1:12,#expert_rank_10[[current_cohort]],
+                  latent = mean_latent_rank[expert_rank_10[[current_cohort]]])
 
@@
 for(current_cohort in 1:10) {
-  cat("Cohort, ", current_cohort,"\n",sep="")
+  cat("Cohort ", current_cohort,"\n",sep="")
   load(paste(data_path,cohort_names[current_cohort],
@@
 
-  ranks <- tibble(expert = expert_rank_10[[current_cohort]],
-                  latent = mean_latent_rank)
   out_degree <- apply(sim_cohort_mmhp$gamma,2,mean)
@@
   degs <- tibble(expert = expert_rank_10[[current_cohort]],
-                  latent = mean_latent_rank,
-                 out_deg = out_degree,
-                 in_deg = in_degree)
+                  latent = mean_latent_rank,#[expert],
+                 out_deg = out_degree,#[expert],
+                 in_deg = in_degree)#[expert])
 

### 2020-07-13 output_scripts/Paper_Plots.Rmd

@@
 
-<!-- # Figure 7: Pearson residual matrices -->
+```{r fig-6b-overall-rank-correlation}
+load("../output/weighted_rank_data.RData")
+#png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
+no_method <- 4
+plot_cor_df <- data.frame(Method=rep(c(1:no_method),each=10),
+                          cor=as.vector(spearman_df))
+plot_cor_df$Method <- factor(plot_cor_df$Method,
+                             labels = c("Agg-rank","C-HP","C-DCHP","C-MMHP"))
+p2 <- ggplot(plot_cor_df, aes(x="", y = cor, fill = Method)) +
+        geom_boxplot(alpha=0.7, width=0.5) +
+        scale_fill_manual(values = viridis::viridis(4)) + 
+        ggtitle("(b)") +
+        ylim(0,1) +
+        theme_bw() +
+        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+              text = element_text(size = 20),
+              axis.text.y =element_text(size = 11),
+              legend.position="none",
+              axis.title.x=element_blank()) +
+        facet_grid(cols=vars(Method)) +
+        ylab("Spearman rank correlation")
+p2
 
-<!-- Here is where I need to be a bit more careful about using the correct fits. -->
-<!-- Currently using all from Jing's saved output. -->
+```
 
-<!-- In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices. -->
+# Figure 7: Pearson residual matrices
 
-<!-- ```{r} -->
-<!-- current_cohort <- 1 -->
+Here is where I need to be a bit more careful about using the correct fits.
+Currently using all from Jing's saved output.
 
-<!-- m1_residual_matrix_lst <- list() -->
-<!-- m2_residual_matrix_lst <- list() -->
-<!-- m3_residual_matrix_lst <- list() -->
-<!-- mmhp_residual_matrix_lst <- list() -->
+In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices.
 
-<!--   print(current_cohort) -->
-<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
-<!--   return_df <- cleanObservationPeriod(current_cohort, clean_data) -->
-<!--   unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% -->
-<!--     summarize(count=n(), -->
-<!--               observe=list(observe.id), -->
-<!--               observe.length=list(observe.time), -->
-<!--               no.events=list(no.events)) -->
-<!--   unique_observe_win <- unique(return_df[,c("observe.id","observe.time")]) -->
+```{r fig-7-prMatrix-Cohort1}
+current_cohort <- 1
 
-<!--   # M1 -->
-<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
-<!--              "/cohort_hp_stan_result_",cohort_names[current_cohort], -->
-<!--              ".RData",sep='')) -->
-<!--   model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0), -->
-<!--                          eta_1=mean(sim_cohort_hp$eta_1), -->
-<!--                          eta_2=mean(sim_cohort_hp$eta_2), -->
-<!--                          eta_3=mean(sim_cohort_hp$eta_3), -->
-<!--                          beta=mean(sim_cohort_hp$beta), -->
-<!--                          f=apply(sim_cohort_hp$f,2,mean)) -->
-<!--   model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0, -->
-<!--                                                   nrow=mice_number,ncol=mice_number), -->
-<!--                             alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y, -->
-<!--                                                                                       model1_par_est$eta_1, -->
-<!--                                                                                       model1_par_est$eta_2, -->
-<!--                                                                                       model1_par_est$eta_3), -->
-<!--                                                     model1_par_est$f), -->
-<!--                             beta_matrix=matrix(model1_par_est$beta, -->
-<!--                                                nrow=mice_number,ncol=mice_number)) -->
-<!--   m1_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
+m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                   "/chp_pr_matrix_",cohort_names[current_cohort],
+                   ".RDS",sep=''))
 
-<!--   for(i in 1:mice_number){ -->
-<!--     for(j in 1:mice_number){ -->
-<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
-<!--       if(length(pair)>0&(i!=j)){ -->
-<!--         par_est <- lapply(model1_par_matrix, function(x) x[i,j]) -->
-<!--         names(par_est) <- c("lambda0","alpha","beta") -->
-<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
-<!--         all_residual <- 0 -->
-<!--         for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
-<!--           cur_win <- current_window_vec[cur] -->
-<!--           current_event_time <- return_df[return_df$initiator==i& -->
-<!--                                             return_df$recipient==j& -->
-<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
-<!--           current_obs_time <- return_df[return_df$initiator==i& -->
-<!--                                           return_df$recipient==j& -->
-<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
-<!--           all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est, -->
-<!--                                                                   events=current_event_time, -->
-<!--                                                                   termination = current_obs_time) -->
-<!--         } -->
-<!--         m1_residual_matrix[i,j] <- all_residual -->
-<!--       } -->
-<!--     } -->
-<!--   } -->
+m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                     "/dchp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
 
-<!--   # M2 -->
-<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
-<!--              "/cohort_dchp_stan_result_",cohort_names[current_cohort], -->
-<!--              ".RData",sep='')) -->
-<!--   model2_par_est <- list(gamma=apply(sim_cohort_dchp$gamma,2,mean), -->
-<!--                          zeta=apply(sim_cohort_dchp$zeta,2,mean), -->
-<!--                          eta_1=mean(sim_cohort_dchp$eta_1), -->
-<!--                          eta_2=mean(sim_cohort_dchp$eta_2), -->
-<!--                          eta_3=mean(sim_cohort_dchp$eta_3), -->
-<!--                          beta=mean(sim_cohort_dchp$beta), -->
-<!--                          f=apply(sim_cohort_dchp$f,2,mean)) -->
-<!--   model2_par_matrix <- list(lambda0_matrix=model2_par_est$gamma%*%t(rep(1,mice_number))+ -->
-<!--                               rep(1,mice_number)%*%t(model2_par_est$zeta), -->
-<!--                             alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y, -->
-<!--                                                                                       model2_par_est$eta_1, -->
-<!--                                                                                       model2_par_est$eta_2, -->
-<!--                                                                                       model2_par_est$eta_3), -->
-<!--                                                     model2_par_est$f), -->
-<!--                             beta_matrix=matrix(model2_par_est$beta, -->
-<!--                                                nrow=mice_number,ncol=mice_number)) -->
-<!--   m2_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
+m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                     "/cmmhp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
 
-<!--   for(i in 1:mice_number){ -->
-<!--     for(j in 1:mice_number){ -->
-<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
-<!--       if(length(pair)>0&(i!=j)){ -->
-<!--         par_est <- lapply(model2_par_matrix, function(x) x[i,j]) -->
-<!--         names(par_est) <- c("lambda0","alpha","beta") -->
-<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
-<!--         all_residual <- 0 -->
-<!--         for(cur in c(1:length(current_window_vec))){  -->
-<!--           cur_win <- current_window_vec[cur] -->
-<!--           current_event_time <- return_df[return_df$initiator==i& -->
-<!--                                             return_df$recipient==j& -->
-<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
-<!--           current_obs_time <- return_df[return_df$initiator==i& -->
-<!--                                           return_df$recipient==j& -->
-<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
-<!--           all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est, -->
-<!--                                                                   events=current_event_time, -->
-<!--                                                                   termination = current_obs_time) -->
-<!--         } -->
-<!--         m2_residual_matrix[i,j] <- all_residual -->
-<!--       } -->
-<!--     } -->
-<!--   } -->
+indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                     "/immhp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
 
-<!-- ```   -->
+matrix_lst_plot <- list(
+                        indep_pr[rev(expert_rank_10[[current_cohort]]),
+                                                                   expert_rank_10[[current_cohort]]],
+                        m1_pr[rev(expert_rank_10[[current_cohort]]),
+                                                                 expert_rank_10[[current_cohort]]],
+                        m2_pr[rev(expert_rank_10[[current_cohort]]),
+                                                                 expert_rank_10[[current_cohort]]],
+                        m3_pr[rev(expert_rank_10[[current_cohort]]),
+                                                                 expert_rank_10[[current_cohort]]]) 
+#cat("Cohort ",current_cohort,"\n",sep="")
+myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
+                  xLabels=expert_rank_10[[current_cohort]],
+                  yLabels=rev(expert_rank_10[[current_cohort]]),
+                  min=-60,max=60,axis_cex=2,title_cex = 1.8,
+                  colorPalette="RdBu",if.emp=FALSE,
+                  #legend.mar=c(0.5,.5,0.5,0.5),
+                  title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
+                  #title_lst = list("I-MMHP"),
+                  col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
+                  matrix.mar=c(2.5,2.5,2.5,1)
+                  )
 
-<!-- This is too large to load at the moment again. Can do this on the cluster. -->
-
-<!-- ```{r, eval=FALSE}   -->
-<!--   # M3 -->
-<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
-<!--              "/cohort_mmhp_stan_result_",cohort_names[current_cohort], -->
-<!--              ".RData",sep='')) -->
-<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
-<!--              "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep='')) -->
-<!--   model3_par_est <- list(lambda0=mean(sim_cohort_mmhp$lambda0), -->
-<!--                          lambda1=mean(sim_cohort_mmhp$lambda1), -->
-<!--                          eta_1=mean(sim_cohort_mmhp$eta_1), -->
-<!--                          eta_2=mean(sim_cohort_mmhp$eta_2), -->
-<!--                          eta_3=mean(sim_cohort_mmhp$eta_3), -->
-<!--                          beta=mean(sim_cohort_mmhp$beta), -->
-<!--                          f=apply(sim_cohort_mmhp$f,2,mean)) -->
-<!--   model3_par_matrix <- list(lambda0_matrix=matrix(model3_par_est$lambda0, -->
-<!--                                                   nrow=mice_number,ncol=mice_number), -->
-<!--                             lambda1_matrix=matrix(model3_par_est$lambda1, -->
-<!--                                                   nrow=mice_number,ncol=mice_number), -->
-<!--                             alpha_matrix=formMatrix(function(x,y) model3_fn$alpha.fun(x,y, -->
-<!--                                                                                       model3_par_est$eta_1, -->
-<!--                                                                                       model3_par_est$eta_2), -->
-<!--                                                     model3_par_est$f), -->
-<!--                             beta_matrix=matrix(model3_par_est$beta, -->
-<!--                                                nrow=mice_number,ncol=mice_number), -->
-<!--                             q1_matrix=formMatrix(function(x,y) model3_fn$q1.fun(x,y,model3_par_est$eta_3), -->
-<!--                                                  model3_par_est$f), -->
-<!--                             q2_matrix=formMatrix(function(x,y) model3_fn$q0.fun(x,y,model3_par_est$eta_3), -->
-<!--                                                  model3_par_est$f)) -->
-<!--   m3_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
-<!--   no_segments <- 5000 # changed from 5000 -->
-<!--   window_pr <- c() -->
-<!--   for(i in 1:mice_number){ -->
-<!--     print(i) -->
-<!--     for(j in 1:mice_number){ -->
-<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
-<!--       if(length(pair)>0&(i!=j)){ -->
-<!--         par_est <- lapply(model3_par_matrix, function(x) x[i,j]) -->
-<!--         names(par_est) <- c("lambda0","lambda1","alpha","beta","q1","q2") -->
-<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
-<!--         all_residual <- 0 -->
-<!--         for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
-<!--           cur_win <- current_window_vec[cur] -->
-<!--           current_event_time <- return_df[return_df$initiator==i& -->
-<!--                                             return_df$recipient==j& -->
-<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
-<!--           current_obs_time <- return_df[return_df$initiator==i& -->
-<!--                                           return_df$recipient==j& -->
-<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
-<!--           time_segment <- seq(0,current_obs_time,length.out=no_segments) -->
-<!--           latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean) -->
-<!--           latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5)  -->
-<!--           est.intensity <- mmhpIntensityNumeric(params=par_est, -->
-<!--                                                 t=current_event_time, -->
-<!--                                                 time.vec=time_segment, -->
-<!--                                                 latent.vec=latent_mean) -->
-<!--           est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time, -->
-<!--                                                         latent_z=latent_event) -->
-<!--           all_residual <- all_residual + sum(1/sqrt(est.intensity.events))- -->
-<!--             sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1]) -->
-<!--           # print(sum(1/sqrt(est.intensity.events))- -->
-<!--           #         sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])) -->
-<!--           # print(summary(latent_mean)) -->
-<!--           # window_pr <- c(window_pr,sum(1/sqrt(est.intensity.events))- -->
-<!--           #                  sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])) -->
-<!--         } -->
-<!--         m3_residual_matrix[i,j] <- all_residual -->
-<!--       } -->
-<!--     } -->
-<!--   } -->
-
-<!-- ```   -->
-<!-- These are in part 1 of the thesis folder on Google Drive. -->
-
-<!-- ```{r, eval=FALSE} -->
-<!-- ind_mmhp_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part1/real_data/" -->
-<!--   # Independent MMHP -->
-<!--   load(paste(ind_mmhp_data_path, cohort_names[current_cohort],  -->
-<!--              "/sep_mmhp_stan_result_", cohort_names[current_cohort],".RData",sep='')) -->
-<!--   load(paste(ind_mmhp_data_path,cohort_names[current_cohort], -->
-<!--              "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep='')) -->
-
-<!--   mmhp_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
-<!--   for(i in 1:mice_number){ -->
-<!--     print(i) -->
-<!--     for(j in 1:mice_number){ -->
-<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
-<!--       if(length(pair)>0&(i!=j)){ -->
-<!--         par_est <- list(lambda0=mean(sim_mmhp_sep$lambda0[,pair]), -->
-<!--                         lambda1=mean(sim_mmhp_sep$lambda1[,pair]), -->
-<!--                         alpha=mean(sim_mmhp_sep$alpha[,pair]), -->
-<!--                         beta=mean(sim_mmhp_sep$beta[,pair]), -->
-<!--                         q1=mean(sim_mmhp_sep$q1[,pair]), -->
-<!--                         q2=mean(sim_mmhp_sep$q2[,pair])) -->
-<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
-<!--         all_residual <- 0 -->
-<!--         for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
-<!--           cur_win <- current_window_vec[cur] -->
-<!--           current_event_time <- return_df[return_df$initiator==i& -->
-<!--                                             return_df$recipient==j& -->
-<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
-<!--           current_obs_time <- return_df[return_df$initiator==i& -->
-<!--                                           return_df$recipient==j& -->
-<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
-<!--           time_segment <- seq(0,current_obs_time,length.out=no_segments) -->
-<!--           latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean) -->
-<!--           latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5)  -->
-<!--           est.intensity <- mmhpIntensityNumeric(params=par_est, -->
-<!--                                                 t=current_event_time, -->
-<!--                                                 time.vec=time_segment, -->
-<!--                                                 latent.vec=latent_mean) -->
-<!--           est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time, -->
-<!--                                                         latent_z=latent_event) -->
-<!--           all_residual <- all_residual + sum(1/sqrt(est.intensity.events))- -->
-<!--             sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1]) -->
-<!--         } -->
-<!--         mmhp_residual_matrix[i,j] <- all_residual -->
-<!--       } -->
-<!--     } -->
-<!--   } -->
-<!--   m1_residual_matrix_lst[[current_cohort]] <- m1_residual_matrix -->
-<!--   m2_residual_matrix_lst[[current_cohort]] <- m2_residual_matrix -->
-<!--   m3_residual_matrix_lst[[current_cohort]] <- m3_residual_matrix -->
-<!--   mmhp_residual_matrix_lst[[current_cohort]] <- mmhp_residual_matrix -->
-
-<!-- save(m1_residual_matrix_lst, m2_residual_matrix_lst, m3_residual_matrix_lst, mmhp_residual_matrix_lst, -->
-<!--      file = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/pearson_residual_cohort9.RData") -->
-<!-- beepr::beep() -->
-<!-- ``` -->
-<!-- These would need to be rerun correctly and saved. -->
-<!-- For now using an *old* version. -->
-
-<!-- ```{r} -->
-<!-- load("C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/pearson_residual_cohort9.RData") -->
-<!-- png(paste(plot_path,"real_residual_matrix_one_cohort.png",sep=""),width = 800,height = 400) -->
-<!-- matrix_lst_plot <- list( -->
-<!--                         mmhp_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]), -->
-<!--                                                                    expert_rank_10[[current_cohort]]], -->
-<!--                         m1_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]), -->
-<!--                                                                  expert_rank_10[[current_cohort]]], -->
-<!--                         m2_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]), -->
-<!--                                                                  expert_rank_10[[current_cohort]]], -->
-<!--                         m3_residual_matrix_lst[[current_cohort]][rev(expert_rank_10[[current_cohort]]), -->
-<!--                                                                  expert_rank_10[[current_cohort]]])  -->
-<!-- myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2, -->
-<!--                   xLabels=expert_rank_10[[current_cohort]], -->
-<!--                   yLabels=rev(expert_rank_10[[current_cohort]]), -->
-<!--                   min=-63,max=63,axis_cex=2,title_cex = 1.8, -->
-<!--                   colorPalette="RdBu",if.emp=FALSE,legend.mar=c(0.5,.5,0.5,0.95), -->
-<!--                   title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"),  -->
-<!--                   #title_lst = list("I-MMHP"), -->
-<!--                   col_axis=c(-60,-30,0,30,60), out.title="", fake_matrix=FALSE, -->
-<!--                   matrix.mar=c(2.5,2.5,2.5,2)) -->
-<!-- dev.off() -->
-<!-- ``` -->
+```
 <!-- The remaining plot code seems to mostly be in `PaperPlots.R`. -->
 
-<!-- # Figure 8 -->
+# Figure 8
 
-<!-- ## Figure 8a: Frobenius norm of interaction predictions, single cohort -->
+## Figure 8a: Frobenius norm of interaction predictions, single cohort
 
-<!-- ## Figure 8b: Same plot aggregated for all cohorts -->
+```{r fig-8a-frob-norm-cohort1}
+load("../output/plot_N_predict.RData")
+current_cohort <- 1
 
-<!-- # Figure 9 -->
+temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
+temp_plot_df$method <- factor(temp_plot_df$method,
+                              levels = c("mmhp","dsnl","m1","m2","m3"),
+                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+temp_plot_df$day <- factor(temp_plot_df$day)
+#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
+p3 <- ggplot(temp_plot_df, aes(x = method, y = norm, fill = method)) +
+  geom_boxplot(alpha=0.7) +
+  scale_fill_manual(values = viridis::viridis(5)) +
+  ggtitle("(a)") +
+  theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.position="right") +
+  facet_grid(cols=vars(day)) +
+  xlab("Prediction horizon (day)") + 
+  ylab("Frobenius norm of error") +
+  ylim(0, 50)
+p3
+```
 
-<!-- ## Figure 9a: Predicted Spearman rank for single cohort -->
+## Figure 8b: Same plot aggregated for all cohorts
 
-<!-- ## Figure 9b: Predicted Spearman rank for all cohorts -->
+```{r fig-8b-frob-norm-all-cohorts}
+load("../output/plot_N_predict.RData")
+temp_plot_df <- all_cohort_norm_df %>% 
+  group_by(day, method) %>% 
+  summarize(avg=mean(norm), n= n(), sd=sd(norm))
 
-<!-- # Figure 10 -->
+temp_plot_df$method <- factor(temp_plot_df$method,
+                              levels = c("mmhp","dsnl","m1","m2","m3"),
+                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+temp_plot_df$day <- factor(temp_plot_df$day)
+
+#png(paste(plot_path,"real_predict_N_all_cohort.png",sep=""),width=600,height=300)
+p4 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
+  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
+  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
+                 position=position_dodge(0.2)) +
+  scale_color_manual(values = viridis::viridis(5)) + 
+  ggtitle("(b)") +
+  theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_text(size = 18)) +
+  xlab("Prediction horizon (day)") + 
+  ylab("Frobenius norm of error") + 
+  coord_cartesian(ylim=c(2.5,57.5)) + 
+  guides(color=guide_legend(title="Model")) 
+p4
+```
+
+# Figure 9
+
+## Figure 9a: Predicted Spearman rank for single cohort
+
+```{r fig-9a-spearman-rank-cohort1}
+load("../output/plot_rank_predict.RData")
+current_cohort <- 1
+temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
+temp_plot_df$method <- factor(temp_plot_df$method,
+                              levels = c("mmhp","dsnl","m1","m2","m3"),
+                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+temp_plot_df$day <- factor(temp_plot_df$day)
+# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),width=600,height=300)
+p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
+  geom_boxplot(alpha=0.7) +
+  scale_fill_manual(values = viridis::viridis(5)) +
+  #scale_fill_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
+  ggtitle("(a)") +
+  theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_blank(),
+        axis.ticks.x = element_blank(), 
+        legend.position="right") +
+  facet_grid(cols=vars(day)) +
+  xlab("Prediction horizon (day)") + 
+  ylab("Spearman rank correlation") +
+  ylim(0, 1)
+p5
+```
+
+## Figure 9b: Predicted Spearman rank for all cohorts
+
+```{r fig-9b-spearman-rank-all-cohorts}
+load("../output/plot_rank_predict.RData")
+temp_plot_df <- all_cohort_rank_df %>% 
+  group_by(day, method) %>% 
+  summarize(avg=mean(spearman), n= n(), sd=sd(spearman))
+
+temp_plot_df$method <- factor(temp_plot_df$method,
+                              levels = c("mmhp","dsnl","m1","m2","m3"),
+                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+temp_plot_df$day <- factor(temp_plot_df$day)
+
+# png(paste(plot_path,"real_predict_rank_all_cohort.png",sep=""),width=600,height=300)
+p6 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
+  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
+  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
+                position=position_dodge(0.2)) +
+  scale_fill_manual(values = viridis::viridis(5)) +
+  #scale_color_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
+  ggtitle("(b)") +
+  theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_text(size = 18)) +
+  xlab("Prediction horizon (day)") + 
+  ylab("Spearman rank correlation") + 
+  coord_cartesian(ylim=c(0,1)) + 
+  guides(color=guide_legend(title="Model")) 
+p6
+```
+
+# Figure 10
+
+## Figure 10a
+
+```{r construct data for plot, results='hide',message=FALSE}
+library(PlayerRatings)
+load(paste(data_path,cohort_names[current_cohort],
+           "/predict_simulation_",cohort_names[current_cohort],
+           ".RData",sep=''))
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]],
+                        cut_off = 1)
+
+df <- full_data[[cohort_names[current_cohort]]]
+df <- df[df$Actor!="Start"&df$Actor!="End",]
+df1 <- expandrows(df)
+df1 <- df1[order(df1$Timestamp),] #ensure in date order
+df1$event <- 1:nrow(df1)
+glick.df <- df1[, c("event","Actor","Recipient","score"), with = FALSE] #need event, actor, recipient, score
+gl <- my_glicko(glick.df, history=TRUE, cval=2)
+
+# ------------------- period
+training_end <- nrow(df[df$day<=18,])
+testing_end <- 1076
+newx <- c(training_end:testing_end)
+
+# ----------------- set pars for plot
+my_col <- c("black", "grey", "orange", "red")
+col_vec <- colorRampPalette(my_col)(mice_number)
+ltypes_vec <- rep(1,mice_number) #c(1,2,3,1,2,3,1,2,3,1,2,3)
+history_width <- 3
+sim_width <- 0.3
+shade_vec <- makeTransparent(col_vec,0.2)
+less_shade_vec <- makeTransparent(col_vec,0.7)
+
+# ---------------- simulation mean and sd
+sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,100))
+for(s in 1:100){
+  print(s)
+  temp_gl <- glickoScoreSimulationWithWindowsReturnAll(predict.sim = m3_predict_sim[5:8,s],
+                                                       history.df = glick.df[1:training_end,])
+  history_matrix <- temp_gl$history[,,1]
+
+  if(testing_end>ncol(temp_gl$history[,,1])){
+    history_matrix <- cbind(history_matrix,
+                            t(matrix(rep(history_matrix[,ncol(history_matrix)],testing_end-ncol(temp_gl$history[,,1])),
+                                     nrow=testing_end-ncol(temp_gl$history[,,1]),byrow=TRUE)))
+  }else{
+    history_matrix <- temp_gl[,1:testing_end]
+  }
+  sim_gl_array[,,s] <- history_matrix[,training_end:testing_end]
+}
+```
+
+```{r fig-10a-glicko-rating}
+par(mar=c(3,5,3,1))
+plot(1, type="n", xlab="", ylab="Glicko ranking", xlim=c(0,dim(gl$history)[2]),
+     ylim=c(min(gl$history[,,1]),max(gl$history[,,1])),
+     cex.axis=2, cex.lab=2)
+for(m in c(1:mice_number)){
+  #history
+  lines(gl$history[m,1:training_end,1],
+        cex=0.6, col=col_vec[m],lwd=history_width,lty=ltypes_vec[m])
+  lines(c(rep(NA,training_end), gl$history[m,(training_end+1):testing_end,1]),
+        cex=0.6, col=shade_vec[m],lwd=history_width,lty=ltypes_vec[m])
+
+  #simulation
+  cur_end <- testing_end
+  mean_vec <- apply(sim_gl_array[m,,],1,function(x) mean(na.omit(x)))
+  sd_vec <- apply(sim_gl_array[m,,],1,function(x) sd(na.omit(x)))
+  polygon(c(newx, rev(newx)), c(mean_vec-sd_vec,rev(mean_vec+sd_vec)),col = shade_vec[m], border = NA)
+  #polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
+  lines(c(rep(NA,training_end),mean_vec),
+        cex=0.6, col=col_vec[m],lwd=1,lty=2)
+}
+
+# annotate the days
+for(d in c(19:21)){
+  abline(v = nrow(df[df$day<=(d-1),]),lty=2,lwd=0.4)
+  text(x=nrow(df[df$day<=(d-1),]),y=2600,d)
+}
+mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
+```
+
+```{r remove some objects, include=FALSE}
+rm(m3_predict_sim)
+rm(m2_predict_sim)
+rm(m1_predict_sim)
+rm(mmhp_predict_sim)
+rm(fit_agg_rank)
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(fit_cohort_mmhp)
+
+# also removing stan fits as they can cause issues in the next chunk
+
+```
+
+## Fig 10b
+
+```{r process for state separation cohort1,eval=FALSE}
+# only run this once and save the results
+# this doesn't need to be rerun ever, even if the stan fits change
+load(paste(data_path,cohort_names[current_cohort],
+             "/cmmhp_est_zt_",cohort_names[current_cohort],
+             ".RData",sep=''))
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+                   observe=list(observe.id),
+                   observe.length=list(observe.time),
+                   no.events=list(no.events))
+unique_observe_win <- unique(return_df[,c("day","observe.id","observe.time")])
+
+## 5.  find how many 1s for each pair
+print(".......state separation plot........")
+total_event_array <- array(0,dim=c(mice_number,mice_number,max(return_df$observe.id)))
+active_event_array <- array(0,dim=c(mice_number,mice_number,max(return_df$observe.id)))
+
+for(i in 1:mice_number){
+  for(j in c(1:mice_number)[-i]){
+    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
+    if(length(pair)>0){
+      current_window_vec <- unique_pairs_df$observe[[pair]]
+      for(cur_win in current_window_vec){
+        row_indicator <- return_df$initiator==i&return_df$recipient==j&return_df$observe.id==cur_win
+        total_event_array[i,j,cur_win] <- length(return_df[row_indicator,"event.times"][[1]])
+        active_event_array[i,j,cur_win] <- sum(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5)
+      }
+    }
+  }
+}
+
+utility_state_day <- array(0,dim=c(21,mice_number,mice_number))
+social_state_day <- array(0,dim=c(21,mice_number,mice_number))
+for(cur_day in c(1:21)){
+  cur_wins <- which(unique_observe_win$day==cur_day)
+  utility_state_day[cur_day,,] <- apply(active_event_array[,,cur_wins],c(1,2),sum)
+  social_state_day[cur_day,,] <- apply(total_event_array[,,cur_wins],c(1,2),sum)-utility_state_day[cur_day,,]
+}
+
+## utility dsnl
+fit_dsnl_active <- stan("../lib/dsnl_poisson.stan",
+                         data=list(day=21,
+                                   Gt=utility_state_day,
+                                   c=1,
+                                   sigma=0.5),
+                         iter=1000, chains=4, control=list(adapt_delta=0.99))
+print(fit_dsnl_active,pars=c("x"))
+sim_dsnl_active <- rstan::extract(fit_dsnl_active)
+
+## social dsnl
+fit_dsnl_inactive <- stan("../lib/dsnl_poisson.stan",
+                           data=list(day=21,
+                                     Gt=social_state_day,
+                                     c=1,
+                                     sigma=1),
+                           iter=1000, chains=4, control=list(adapt_delta=0.99))
+print(fit_dsnl_inactive,pars=c("x"))
+sim_dsnl_inactive <- rstan::extract(fit_dsnl_inactive)
+
+save(sim_dsnl_active, fit_dsnl_active, utility_state_day,
+     sim_dsnl_inactive, fit_dsnl_inactive, social_state_day,
+     file = paste(data_path,cohort_names[current_cohort],
+                  "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
+                  ".RData",sep=''))
+rm(interpolation_array_list)
+rm(state_array_list)
+rm(termination_state_list)
+rm(initial_state_list)
+```
+
+```{r process data for plot 10b}
+current_cohort <- 1
+load(paste(data_path,cohort_names[current_cohort],
+           "/dsnl_poisson_stan_result_",cohort_names[current_cohort],
+           ".RData",sep=''))
+load(paste(data_path,cohort_names[current_cohort],
+           "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
+           ".RData",sep=''))
+sub.types <- c("All", "Active", "Inactive"); # three methods
+task.types <- paste0("day", 1:21);
+
+data.tbl <- data.frame(array(NA, c(2000*3*21, 3)))
+colnames(data.tbl) <- c("sub.type", "task.type", "data.value")  
+source('../lib/myGlicko.R')
+#------------ gl score
+df <- full_data[[cohort_names[current_cohort]]]
+df <- df[df$Actor!="Start"&df$Actor!="End",]
+df1 <- expandrows(df)
+df1 <- df1[order(df1$Timestamp),] #ensure in date order
+df1$event <- 1:nrow(df1)
+glick.df <- df1[, c("event","Actor","Recipient","score"), with = FALSE] #need event, actor, recipient, score
+real.gl <- my_glicko(glick.df, history=TRUE, cval=2)
+clean_data_all <- cleanData(full_data[[cohort_names[current_cohort]]],
+                              cut_off = 1)
+day_end_idx <- unlist(lapply(c(1:21),function(x) max(which(clean_data_all$day==x))))
+
+## All aggregate
+for (t in 1:length(task.types)){
+  temp_vec <- rep(NA,2000)
+  cur_real_rank <- real.gl$history[,day_end_idx[t],1]
+  for(s in c(1:2000)){
+    temp_result <- cor.test(sim_dsnl$x[s,t,], cur_real_rank, method = "spearman")
+    temp_vec[s] <- temp_result$estimate
+  }
+  data.tbl$sub.type[(1:2000)+(t-1)*2000] <- sub.types[1]  
+  data.tbl$task.type[(1:2000)+(t-1)*2000] <- task.types[t];  
+  data.tbl$data.value[(1:2000)+(t-1)*2000] <- temp_vec
+}
+
+## Utility aggregate
+for (t in 1:length(task.types)){
+  temp_vec <- rep(NA,2000)
+  cur_real_rank <- real.gl$history[,day_end_idx[t],1]
+  for(s in c(1:2000)){
+    temp_result <- cor.test(-sim_dsnl_active$x[s,t,], cur_real_rank, method = "spearman")
+    temp_vec[s] <- temp_result$estimate
+  }
+  data.tbl$sub.type[(1:2000)+(t-1)*2000+42000] <- sub.types[2]  
+  data.tbl$task.type[(1:2000)+(t-1)*2000+42000] <- task.types[t];  
+  data.tbl$data.value[(1:2000)+(t-1)*2000+42000] <- temp_vec
+}
+
+## Social aggregate
+for (t in 1:length(task.types)){
+  temp_vec <- rep(NA,2000)
+  cur_real_rank <- real.gl$history[,day_end_idx[t],1]
+  for(s in c(1:2000)){
+    temp_result <- cor.test(sim_dsnl_inactive$x[s,t,], cur_real_rank, method = "spearman")
+    temp_vec[s] <- temp_result$estimate
+  }
+  data.tbl$sub.type[(1:2000)+(t-1)*2000+42000*2] <- sub.types[3]  
+  data.tbl$task.type[(1:2000)+(t-1)*2000+42000*2] <- task.types[t];  
+  data.tbl$data.value[(1:2000)+(t-1)*2000+42000*2] <- temp_vec
+}
+
+data.tbl$sub.type <- factor(data.tbl$sub.type);  
+data.tbl$task.type <- factor(data.tbl$task.type);
+```
+
+```{r fig-10b-rank-correlation}
+par(mar=c(3,5,3,1))
+cx <- 2;  # cex for axis label text; default is 1. bigger numbers make the text bigger, smaller, smaller.  
+x.ttl <- ""; # blank x-axis label  
+y.ttl <- "rank correlation (expert rank)";  
+ttl <- "(b)";  
+#y.lim <- c(min(data.tbl$data.value), max(data.tbl$data.value)+.5); # y-axis limits. +2 at top to give room for legend  
+y.lim <- c(-1,1.2)    
+x.lim <- c(0.5, (length(task.types))) 
+cols <- c('paleturquoise4', 'lightgreen', 'cornsilk')
+shifts <- c(-0.25, 0, 0.25)
+
+plot(x=0, y=0, xlim=x.lim, ylim=y.lim, xaxt='n', col='white', xlab=x.ttl, ylab=y.ttl, main=ttl, cex.main=cx*1.3, cex.axis=cx, cex.lab=cx); 
+axis(side=1, at=1:length(task.types), labels=task.types, cex.axis=cx, cex.lab=cx)  # put on the x-axis labels  
+grid(nx=NA, ny=NULL, col='darkgrey');  
+lines(x=c(-1,100), y=c(0,0), col='darkgrey');  
+for (t.id in 1:length(task.types)) {  
+  for (i in 1:length(sub.types)) {  # t.id <- 1; i <- 1;   
+   inds <- which(data.tbl$sub.type == sub.types[i] & data.tbl$task.type == task.types[t.id])
+   boxplot(data.tbl$data.value[inds], at=t.id+shifts[i], col=cols[i], add=TRUE, 
+           xaxt='n', yaxt='n', bty='n', boxwex=0.35, outpch = 20, outcex = 0.5) 
+  }  
+}  
+legend(x='top', legend=sub.types, fill=cols, horiz=TRUE, cex=cx, bg='white', bty='n')  
+box()
+```

### 2020-07-15 output_scripts/Diagnostics.Rmd
finish plots for paper

@@
 knitr::opts_chunk$set(echo = TRUE)
+
+path_change <- FALSE # if change the data path, set this to false, else TRUE
 
@@
 ```
+
+<!-- # Correlation Issues in Fits -->
+
+<!-- We seek to further -->
 
@@
 
-```{r cohort-1,cache=TRUE}
+```{r cohort-1,cache=path_change}
 current_cohort <- 1
@@
 
-```{r cohort-2,cache=TRUE}
+```{r cohort-2,cache=path_change}
 current_cohort <- 2
@@
 
-```{r cohort-3,cache=TRUE}
+```{r cohort-3,cache=path_change}
 current_cohort <- 3
@@
 
-```{r cohort-4,cache=TRUE}
+```{r cohort-4,cache=path_change}
 current_cohort <- 4
@@
 
-```{r cohort-5,cache=TRUE}
+```{r cohort-5,cache=path_change}
 current_cohort <- 5
@@
 
-```{r cohort-6,cache=TRUE}
+```{r cohort-6,cache=path_change}
 current_cohort <- 6
@@
 
-```{r cohort-7,cache=TRUE}
+```{r cohort-7,cache=path_change}
 y.upper <- 80
@@
 
-```{r cohort-8,cache=TRUE}
+```{r cohort-8,cache=path_change}
 current_cohort <- 8
@@
 
-```{r cohort-9,cache=TRUE}
+```{r cohort-9,cache=path_change}
 y.upper <- 60
@@
 
-```{r cohort-10,cache=TRUE}
+```{r cohort-10,cache=path_change}
 current_cohort <- 10

### 2020-07-15 output_scripts/Paper_Plots.Rmd
finish plots for paper

@@
 source(paste(func_dir,'residualStructureScore.R',sep = ""))
+source(paste(func_dir,'drawIntensity.R',sep =""))
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
@@
 
-The aim of this notebook is a way to quickly and efficiently create all the plots
-required for this paper. They will be built with the current fits and models.
+<!-- The aim of this notebook is a way to quickly and efficiently create all the plots -->
+<!-- required for this paper. They will be built with the current fits and models. -->
 
@@
 # Figure 4:
-To be added.
+
+## Figure 4a Recover Latent Ranks
+```{r fig-4a}
+sim_data_path <- "../output/sims_long/"
+
+load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
+load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
+
+n_sim <- 50
+
+#png(paste(plot_path,"sim_latent_recover.png",sep=""), height=500, width=900)
+par(mfrow=c(3, length(object_par$f_vec_1)),
+    mar=c(0,0,1,0),
+    oma=c(6.5,11,3.5,1))
+
+y.ub <- c(12,12,12,12,12)
+text.y <- c(rep(8,4),8)
+text.x <- c(0.1,0.2,0.4,0.7,0.9)
+text.x.adj <- c(0.3,0.4,0.6,0.5,0.8)
+model_colors <- c("steelblue", "goldenrod2", "firebrick2")
+model_colors <- viridis::viridis(3)
+
+for(m in c(1:3)){
+  for(j in c(1:length(object_par$f_vec_1))){
+    plot(1,4,xlim=c(0,1),ylim=c(0,y.ub[j]),
+         type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+
+    ## Posterior density
+    current_result <- eval(parse(text=paste("sim_model3_stan_sim",m,sep="")))
+    for(i in c(1:n_sim)){
+      lines(density(current_result[[i]]$f[1001:2000,j]),
+            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
+    }
+
+    ## plot true value
+    abline(v=object_par$f_vec_1[j],lwd=1.8,lty=2,col="gray30")
+
+    ## plot box
+    box.wdt <- 1.5
+    box.col <- "black"
+    box(lty = 'solid',col=box.col,lwd=0.7)
+
+    if(m==3){
+      text(text.x.adj[j],text.y[j],text.x[j],cex=2.4)
+    }
+  }
+  ## bottom
+  mtext(text=expression(f[1],f[2],f[3],f[4],f[5]), side=1, line=2.4, outer=TRUE, 
+        at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
+        cex=2.4)
+  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.7,
+        at=0.5)
+  ## top
+  mtext(text="(a)", side=3, line=0, outer=TRUE, cex=3,
+        at=0.5, font=2)
+  ## left
+  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5, outer=TRUE, 
+        at=c(0:2)/3+0.15,
+        cex=2, las=2)
+}
+
+```
+
+## Figure 4b: Recover Latent States
+
+```{r prepare data for 4b}
+plot.s <- 9
+plot.i <- 4
+plot.j <- 5
+
+cur_i <- 4
+cur_j <- 5
+
+test.mmhp <- sim_model3_data[plot.s][[1]]$mmhp_matrix[plot.i,plot.j][[1]]
+temp.t <- test.mmhp$tau
+current.n <- length(temp.t)-1
+time.segment <- seq(0,tail(temp.t,1),length.out=5000)
+
+### Preprocess the model inference result
+## model 1
+#########
+model1_par_est <- list(lambda0=mean(sim_model3_stan_sim1[[plot.s]]$lambda0[1001:2000]),
+                       eta_1=mean(sim_model3_stan_sim1[[plot.s]]$eta_1[1001:2000]),
+                       eta_2=mean(sim_model3_stan_sim1[[plot.s]]$eta_2[1001:2000]),
+                       eta_3=mean(sim_model3_stan_sim1[[plot.s]]$eta_3[1001:2000]),
+                       beta=mean(sim_model3_stan_sim1[[plot.s]]$beta[1001:2000]),
+                       f=apply(sim_model3_stan_sim1[[plot.s]]$f[1001:2000,],2,mean))
+lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0=model1_par_est$lambda0,
+                                                 alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
+                                                                           model1_par_est$f[plot.j],
+                                                                           model1_par_est$eta_1,
+                                                                           model1_par_est$eta_2,
+                                                                           model1_par_est$eta_3),
+                                                 beta=model1_par_est$beta),
+                                     events=temp.t,
+                                     time.vec=time.segment)
+
+## model2
+#############
+model2_par_est <- list(gamma=apply(sim_model3_stan_sim2[[plot.s]]$gamma[1001:2000,],2,mean),
+                       zeta=apply(sim_model3_stan_sim2[[plot.s]]$zeta[1001:2000,],2,mean),
+                       eta_1=mean(sim_model3_stan_sim2[[plot.s]]$eta_1[1001:2000]),
+                       eta_2=mean(sim_model3_stan_sim2[[plot.s]]$eta_2[1001:2000]),
+                       eta_3=mean(sim_model3_stan_sim2[[plot.s]]$eta_3[1001:2000]),
+                       beta=mean(sim_model3_stan_sim2[[plot.s]]$beta[1001:2000]),
+                       f=apply(sim_model3_stan_sim2[[plot.s]]$f[1001:2000,],2,mean))
+
+lambda.m2<-uniHawkesIntensityNumeric(object=list(lambda0=model2_par_est$gamma[plot.i]+
+                                                   model2_par_est$zeta[plot.j],
+                                                 alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+                                                                           model2_par_est$f[plot.j],
+                                                                           model2_par_est$eta_1,
+                                                                           model2_par_est$eta_2,
+                                                                           model2_par_est$eta_3),
+                                                 beta=model2_par_est$beta),
+                                     events=temp.t,
+                                     time.vec=time.segment)
+
+## Model3
+#############
+mmhp_par_est <- list(lambda0=mean(sim_model3_stan_sim3[[plot.s]]$lambda0[1001:2000]),
+                     lambda1=mean(sim_model3_stan_sim3[[plot.s]]$lambda1[1001:2000]),
+                     eta_1=mean(sim_model3_stan_sim3[[plot.s]]$eta_1[1001:2000]),
+                     eta_2=mean(sim_model3_stan_sim3[[plot.s]]$eta_2[1001:2000]),
+                     eta_3=mean(sim_model3_stan_sim3[[plot.s]]$eta_3[1001:2000]),
+                     beta=mean(sim_model3_stan_sim3[[plot.s]]$beta[1001:2000]),
+                     f=apply(sim_model3_stan_sim3[[plot.s]]$f[1001:2000,],2,mean))
+
+object_hat <- list(lambda0=mmhp_par_est$lambda0,
+                   lambda1=mmhp_par_est$lambda1,
+                   alpha=model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
+                                             mmhp_par_est$f[cur_j],
+                                             mmhp_par_est$eta_1,
+                                             mmhp_par_est$eta_2),
+                   beta=mmhp_par_est$beta,
+                   q1=model3_fn$q1.fun(mmhp_par_est$f[cur_i],
+                                       mmhp_par_est$f[cur_j],
+                                       mmhp_par_est$eta_3),
+                   q2=model3_fn$q0.fun(mmhp_par_est$f[cur_i],
+                                       mmhp_par_est$f[cur_j],
+                                       mmhp_par_est$eta_3))
+
+## don't have these parameters....?
+state.est.latent.mmhp <- interpolate_state_est_lst[[plot.s]][plot.i,plot.j][[1]]
+state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp, termination=200)
+
+# where is fixInterpolateState?...
+# this is in one of the files at the top of latent_simulation.Rmd
+# drawIntensity.R
+
+step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,2-state.est.latent.mmhp$z.hat)
+
+lambda.m3 <- mmhpIntensityNumeric(params=object_hat,
+                                  t=temp.t[-1],
+                                  time.vec=time.segment,
+                                  latent.vec=step.fun.est(time.segment))
+
+object_true <- lapply(object_matrix,function(x) x[plot.i,plot.j])
+names(object_true) <- c("lambda0","lambda1","alpha","beta","q1","q2")
+
+lambda.true <- mmhpTrueIntensityNumeric(params=object_true, t=temp.t,
+                                        latent=list(x=fixStateTransition(test.mmhp)$x,
+                                                    z=fixStateTransition(test.mmhp)$z),
+                                        time.vec=time.segment)
+
+```
+
+```{r fig4b-recover-latent-states}
+y.ub <- c(130,72,31)
+#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
+model_colors <- viridis::viridis(3)
+layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
+layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
+my.xlim <- 200#130
+my.long.x <- 205#134.5
+legend.x <- c(135,135,135)
+legend.y <- #c(34,32,32)
+legend.y <- c(62,37,18)#c(22,22,22)
+legend.cex <- 1.5 #3
+line.alpha <- c(0.9,0.6)
+line.wdth <- c(2,2.5)
+# negative.col <- add.alpha('lightskyblue',0.6)
+# positive.col <- add.alpha('tomato',0.6)
+negative.col <- viridis::viridis(5,alpha = 0.6)[1]
+positive.col <- viridis::viridis(5,alpha = 0.6)[4]
+par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
+    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)
+
+# model1
+############
+true.object <- object_true
+
+drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
+                          yupper=y.ub[1], 
+                          color=add.alpha("black", alpha=line.alpha[1]),
+                          line.width=line.wdth[1],
+                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
+                          title_name=paste(plot.i,"->",plot.j),
+                          title.cex = 2,
+                          box.type="n")
+drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
+
+                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
+                                                   model1_par_est$f[plot.j],
+                                                   model1_par_est$eta_1,
+                                                   model1_par_est$eta_2,
+                                                   model1_par_est$eta_3),
+                         beta=model1_par_est$beta,
+                         events=test.mmhp$tau,
+                         color=add.alpha(model_colors[1],
+                                         alpha=line.alpha[2]),
+                         line.width=line.wdth[2])
+
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+# axis(2,at=c(-10,y.ub[1]),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+# axis(3,at=c(-5,my.long.x),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+# axis(4,at=c(-10,y.ub[1]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+## add legend
+# changed 34 to 23, 25 to 18, -20 to -10
+legend(20,104,c("State 1/0 events","State change point"),
+       col = c(NA,"red"),
+       y.intersp=0.85,x.intersp=-0.1, bty = "n",
+       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
+       lty = c(NA,NA), lwd=c(NA,4))
+points(29,84,pch=1,cex=2,col="blue")
+points(26,84,pch=16,cex=2,col="blue")
+legend(legend.x[1],legend.y[1],c("True"),
+       col = c("black"),
+       y.intersp=0.88,x.intersp=0.15,bty = "n",
+       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
+legend(legend.x[1]+18,legend.y[1],c("C-HP"),
+       col = c(model_colors[1]),
+       y.intersp=0.88,x.intersp=0.15,bty = "n",
+       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
+
+# legend(93,24,c("Overestimation","Underestimation"),
+#        col = c(positive.col,negative.col),
+#        y.intersp=0.88,x.intersp=0.5,bty = "n",
+#        lty = c(1,1), lwd = c(20,20), cex=legend.cex,seg.len=0.8)
+
+## delta lambda
+par(mar = c(0,0.3,0,0.1))
+plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,10), type="n",
+     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
+delta.positive <- delta.lambda
+delta.positive[delta.positive<0] <- 0
+delta.negative <- delta.lambda
+delta.negative[delta.negative>0] <- 0
+### hiding these for now ###
+polygon(c(0,lambda.true$time.vec,200),
+        c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,200),
+        c(0,delta.positive,0),col=positive.col,border=NA)
+# segments(0,0,my.xlim,0,col="gray45")
+## draw box
+# change -0.7 to -0.5 and -0.5 to -0.25
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+# axis(2,at=c(-2,y.ub[1]),col="gray35",
+#      line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+# axis(4,at=c(-2,y.ub[1]),col="gray35",
+#      line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+# model2
+############
+drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
+                          yupper=y.ub[2], 
+                          color=add.alpha("black", alpha=line.alpha[1]),
+                          line.width=line.wdth[1],
+                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
+                          box.type="n")
+drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
+                           model2_par_est$zeta[plot.j],
+                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+                                                   model2_par_est$f[plot.j],
+                                                   model2_par_est$eta_1,
+                                                   model2_par_est$eta_2,
+                                                   model2_par_est$eta_3),
+                         beta=model2_par_est$beta,
+                         events=test.mmhp$tau,
+                         color=add.alpha(model_colors[2], alpha=line.alpha[2]),line.width=line.wdth[2])
+legend(legend.x[2],legend.y[2],"C-DCHP",
+       col = model_colors[2],
+       y.intersp=0.88,x.intersp=0.1,bty = "n",
+       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)
+## draw box
+# -20 to -10 to -5 here
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+# axis(2,at=c(-5,y.ub[2]),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+# axis(3,at=c(-5,my.long.x),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+# axis(4,at=c(-5,y.ub[2]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+## delta lambda
+par(mar = c(0,0.3,0,0.1))
+delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
+
+plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), ylim=c(-3,10), type="n",
+     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
+delta.positive <- delta.lambda
+delta.positive[delta.positive<0] <- 0
+delta.negative <- delta.lambda
+delta.negative[delta.negative>0] <- 0
+#### hiding these for now ####
+polygon(c(0,lambda.true$time.vec,200), c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,200), c(0,delta.positive,0),col=positive.col,border=NA)
+# segments(0,0,my.xlim,0,col="gray45")
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+# axis(2,at=c(-20,y.ub[2]),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+# axis(4,at=c(-20,y.ub[2]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+# model3
+########
+par(mar = c(0,0.3,1,0.1))
+drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
+                          yupper=y.ub[3], color=add.alpha("black", alpha=line.alpha[1]),line.width=line.wdth[1],
+                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
+                          box.type="n")
+drawUniMMHPIntensityPaper(object_hat,simulation=list(
+  x=state.est.latent.mmhp.new$x.hat,                                               
+  z=state.est.latent.mmhp.new$z.hat,
+  tau=test.mmhp$tau,zt=test.mmhp$zt,
+  lambda.max=test.mmhp$lambda.max),
+                          yupper=y.ub,add=TRUE,
+                          color=add.alpha(model_colors[3],
+                                      alpha=line.alpha[2]),
+  line.width=line.wdth[2])
+legend(legend.x[3],legend.y[3],"C-MMHP",
+       col = model_colors[3],
+       y.intersp=0.88,x.intersp=0.1,bty = "n",
+       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+# axis(2,at=c(-20,y.ub[3]),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+# axis(3,at=c(-5,my.long.x),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+# axis(4,at=c(-20,y.ub[3]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+legend(55,32,c("Overestimation","Underestimation"),
+       col = c(positive.col,negative.col),
+       y.intersp=0.88,x.intersp=0.5,bty = "n",
+       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)
+
+## delta lambda
+par(mar = c(0,0.3,0,0.1))
+plot(0,0,xlim=c(0,my.xlim), ylim=c(-12,8), type="n",
+     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+delta.lambda <- lambda.m3-lambda.true$lambda.t
+delta.positive <- delta.lambda
+delta.positive[delta.positive<0] <- 0
+delta.negative <- delta.lambda
+delta.negative[delta.negative>0] <- 0
+### hiding these for now
+polygon(c(0,lambda.true$time.vec,200), c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,200), c(0,delta.positive,0),col=positive.col,border=NA)
+# segments(0,0,my.xlim,0,col="gray45")
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+# axis(2,at=c(-20,y.ub[1]),col="gray35",
+#      line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+# axis(4,at=c(-20,y.ub[1]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+## top
+mtext(text="(b)",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
+## bottom
+mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.5)
+## left
+mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.5)
+```
 
 # Figure 5:
-To be added.
+```{r data for fig 5}
+load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
+load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
+## Initialize
+N_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
+Lambda_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
+Lambda_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
+Lambda_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
+Lambda_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
+PR_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
+PR_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
+PR_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
+PR_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
+KS_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
+KS_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
+KS_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
+KS_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
+KS_p_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
+KS_p_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
+KS_p_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
+KS_p_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
+
+## Iteration on 50 simulations
+for(s in c(1:n_sim)){
+  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data[s][[1]], 
+                                        cut_off = cut_off, N = length(object_par$f_vec_1))
+
+  N_array[s,,] <- clean_sim_data$N_count
+
+  ## model 1
+  #########
+  model1_par_est <- list(lambda0=mean(sim_model3_stan_sim1[[s]]$lambda0[1001:2000]),
+                         eta_1=mean(sim_model3_stan_sim1[[s]]$eta_1[1001:2000]),
+                         eta_2=mean(sim_model3_stan_sim1[[s]]$eta_2[1001:2000]),
+                         eta_3=mean(sim_model3_stan_sim1[[s]]$eta_3[1001:2000]),
+                         beta=mean(sim_model3_stan_sim1[[s]]$beta[1001:2000]),
+                         f=apply(sim_model3_stan_sim1[[s]]$f[1001:2000,],2,mean))
+
+  for(i in c(1:5)){
+    for(j in c(1:5)[-i]){
+      current_t <- sim_model3_data[s][[1]]$mmhp_matrix[i,j][[1]]$tau
+      m1_object <- list(lambda0=model1_par_est$lambda0,
+                        alpha=model1_fn$alpha.fun(model1_par_est$f[i],model1_par_est$f[j],model1_par_est$eta_1,model1_par_est$eta_2,model1_par_est$eta_3),
+                        beta=model1_par_est$beta)
+      Lambda_model1_array[s,i,j]<-uniHawkesIntegralIntensity(object=m1_object, 
+                                                             events=current_t,
+                                                             termination = tail(current_t,1))
+      Lambda_test <- uniHawkesCompensator(object=m1_object, events=current_t)
+      KS_model1_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$statistic
+      KS_p_model1_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
+      PR_model1_array[s,i,j] <- uniHawkesPearsonResidual(object=m1_object, 
+                                                         events=current_t,
+                                                         termination = tail(current_t,1))
+    }
+  }
+
+  ## model2
+  #############
+  model2_par_est <- list(gamma=apply(sim_model3_stan_sim2[[s]]$gamma[1001:2000,],2,mean),
+                         zeta=apply(sim_model3_stan_sim2[[s]]$zeta[1001:2000,],2,mean),
+                         eta_1=mean(sim_model3_stan_sim2[[s]]$eta_1[1001:2000]),
+                         eta_2=mean(sim_model3_stan_sim2[[s]]$eta_2[1001:2000]),
+                         eta_3=mean(sim_model3_stan_sim2[[s]]$eta_3[1001:2000]),
+                         beta=mean(sim_model3_stan_sim2[[s]]$beta[1001:2000]),
+                         f=apply(sim_model3_stan_sim2[[s]]$f[1001:2000,],2,mean))
+
+  for(i in c(1:5)){
+    for(j in c(1:5)[-i]){
+      current_t <- sim_model3_data[s][[1]]$mmhp_matrix[i,j][[1]]$tau
+      m2_object <- list(lambda0=model2_par_est$gamma[i]+model2_par_est$zeta[j],
+                        alpha=model1_fn$alpha.fun(model2_par_est$f[i],model2_par_est$f[j],model2_par_est$eta_1,model2_par_est$eta_2,model2_par_est$eta_3),
+                        beta=model2_par_est$beta)
+      Lambda_model2_array[s,i,j]<-uniHawkesIntegralIntensity(object=m1_object, 
+                                                             events=current_t,
+                                                             termination = tail(current_t,1))
+      Lambda_test <- uniHawkesCompensator(object=m2_object, events=current_t)
+      KS_model2_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$statistic
+      KS_p_model2_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
+      PR_model2_array[s,i,j] <- uniHawkesPearsonResidual(object=m2_object, 
+                                                         events=current_t,
+                                                         termination = tail(current_t,1))
+    }
+  }
+
+  ## Model3 & true model
+  ######
+  mmhp_par_est <- list(lambda0=mean(sim_model3_stan_sim3[[s]]$lambda0[1001:2000]),
+                       lambda1=mean(sim_model3_stan_sim3[[s]]$lambda1[1001:2000]),
+                       eta_1=mean(sim_model3_stan_sim3[[s]]$eta_1[1001:2000]),
+                       eta_2=mean(sim_model3_stan_sim3[[s]]$eta_2[1001:2000]),
+                       eta_3=mean(sim_model3_stan_sim3[[s]]$eta_3[1001:2000]),
+                       beta=mean(sim_model3_stan_sim3[[s]]$beta[1001:2000]),
+                       f=apply(sim_model3_stan_sim3[[s]]$f[1001:2000,],2,mean))
+  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data[s][[1]], 
+                                        cut_off = cut_off, N = length(object_par$f_vec_1))
+
+  for(i in c(1:5)){
+    for(j in c(1:5)[-i]){
+      test.mmhp <- sim_model3_data[s][[1]]$mmhp_matrix[i,j][[1]]
+      temp.t <- test.mmhp$tau
+      current.n <- length(temp.t)-1
+      time.segment <- seq(0,tail(temp.t,1),length.out=10000)
+
+      object_hat <- list(lambda0=mmhp_par_est$lambda0,
+                         lambda1=mmhp_par_est$lambda1,
+                         alpha=model3_fn$alpha.fun(mmhp_par_est$f[i],
+                                                   mmhp_par_est$f[j],
+                                                   mmhp_par_est$eta_1,
+                                                   mmhp_par_est$eta_2),
+                         beta=mmhp_par_est$beta,
+                         q1=model3_fn$q1.fun(mmhp_par_est$f[i],
+                                             mmhp_par_est$f[j],
+                                             mmhp_par_est$eta_3),
+                         q2=model3_fn$q0.fun(mmhp_par_est$f[i],
+                                             mmhp_par_est$f[j],
+                                             mmhp_par_est$eta_3))
+
+      object_true <- lapply(object_matrix,function(x) x[i,j])
+      names(object_true) <- c("lambda0","lambda1","alpha","beta","q1","q2")
+
+      ## est Lmabda and [R]
+      Lambda.test <- mmhpCompensator(params=object_hat, 
+                                     t=temp.t,
+                                     pzt=2-event_state_est_lst[[s]][i,j][[1]]$zt_v,
+                                     if.pzt=FALSE)
+      KS_model3_array[s,i,j] <-  ks.test(Lambda.test,"pexp")$statistic
+      KS_p_model3_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
+      state.est.latent.mmhp <- interpolate_state_est_lst[[s]][i,j][[1]]
+      step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,2-state.est.latent.mmhp$z.hat)
+      est.intensity <- mmhpIntensityNumeric(params=object_hat,
+                                            t=temp.t[-1],
+                                            time.vec=time.segment,
+                                            latent.vec=step.fun.est(time.segment))
+      est.intensity.events <- mmhpIntensityAtEvents(params=object_hat, t=temp.t,
+                                                    latent_z=event_state_est_lst[[s]][i,j][[1]]$zt_v)
+      Lambda_model3_array[s,i,j] <- sum(est.intensity)*(time.segment[2]-time.segment[1])
+      PR_model3_array[s,i,j] <- sum(1/sqrt(est.intensity.events))-
+        sum(sqrt(est.intensity))*(time.segment[2]-time.segment[1])
+
+      ## Under the true model
+      Lambda.test.true <- mmhpCompensator(params=object_true,
+                                          t=temp.t,
+                                          pzt=2-test.mmhp$zt[2:length(test.mmhp$zt)],
+                                          if.pzt=FALSE)
+      KS_true_array[s,i,j] <-  ks.test(Lambda.test.true,"pexp")$statistic
+      KS_p_true_array[s,i,j] <-  ks.test(Lambda.test.true,"pexp")$p.value
+      true.intensity <- mmhpTrueIntensityNumeric(params=object_true, t=temp.t,
+                                                 latent=list(x=fixStateTransition(test.mmhp)$x,
+                                                             z=fixStateTransition(test.mmhp)$z),
+                                                 time.vec=time.segment)
+      true.intensity.events <- mmhpIntensityAtEvents(params=object_true, t=temp.t, 
+                                                     latent_z=test.mmhp$zt)
+      Lambda_true_array[s,i,j] <- sum(true.intensity$lambda.t)*(time.segment[2]-time.segment[1])
+      PR_true_array[s,i,j] <- sum(1/sqrt(true.intensity.events))-
+        sum(sqrt(true.intensity$lambda.t))*(time.segment[2]-time.segment[1])
+    }
+  }
+}
+
+```
+
+```{r fig5-residual-ks}
+cols_plot <- viridis::viridis(4)
+#load("../output/sim_model3_fit123_residuals.RData")
+par(mfrow=c(5,5),mar=rep(0.2,4),oma=c(2.4,2.4,0.5,0.5))
+for(i in c(5:1)){
+  for(j in c(5:1)){
+    if(i==j){
+      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
+           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+      if(i==5){
+        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04,col=cols_plot[1],border=NA)
+        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,col=cols_plot[2],border=NA)
+        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,col=cols_plot[3],border=NA)
+        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,col=cols_plot[4],border=NA)
+        text(c(0.43,0.58,0.61,0.4),seq(0.8,0.14,-0.22),
+             c("C-HP", "C-DCHP", "C-MMHP", "True"),
+             cex=1.7)
+      }
+    }else{
+      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
+      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
+      PR <- c(KS_model1_array[,i,j],KS_model2_array[,i,j],
+              KS_model3_array[,i,j],KS_true_array[,i,j])
+      Type <- c(rep(1,n_sim),rep(2,n_sim),rep(3,n_sim),rep(4,n_sim))
+      boxplot(PR ~ Type,  
+              col = cols_plot,
+              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
+              xlab="",ylab="",xaxt="n",yaxt="n")#names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
+    }
+  }
+}
+mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
+      at=c(0:4)/5+0.1)
+mtext(text=c(1:5), side=1, line=1, outer=TRUE, cex=2,
+      at=c(0:4)/5+0.1)
+
+```
 
@@
 load("../output/plot_N_predict.RData")
-current_cohort <- 1
+current_cohort <- 5# cohort 1 looks worse than rest
 
@@
 load("../output/plot_rank_predict.RData")
-current_cohort <- 1
+current_cohort <- 5
 temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
@@
 
-```{r construct data for plot, results='hide',message=FALSE}
+```{r construct data for plot, results='hide',message=FALSE,cache=TRUE}
 library(PlayerRatings)
+
+current_cohort <- 1
+
 load(paste(data_path,cohort_names[current_cohort],
@@
 # ---------------- simulation mean and sd
-sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,100))
-for(s in 1:100){
+sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,200))
+for(s in 1:200){
   print(s)
-  temp_gl <- glickoScoreSimulationWithWindowsReturnAll(predict.sim = m3_predict_sim[5:8,s],
+  temp_gl <- glickoScoreSimulationWithWindowsReturnAll(
+    predict.sim = m3_predict_sim[5:8,s],
     history.df = glick.df[1:training_end,])
@@
     history_matrix <- cbind(history_matrix,
-                            t(matrix(rep(history_matrix[,ncol(history_matrix)],testing_end-ncol(temp_gl$history[,,1])),
-                                     nrow=testing_end-ncol(temp_gl$history[,,1]),byrow=TRUE)))
+                            t(matrix(rep(history_matrix[,ncol(history_matrix)],
+                                         testing_end-ncol(temp_gl$history[,,1])),
+                                     nrow=testing_end-ncol(temp_gl$history[,,1]),
+                                     byrow=TRUE)))
   }else{
+    try(
     history_matrix <- temp_gl[,1:testing_end]
+    )
   }

### 2020-07-15 output_scripts/Paper_Plots.Rmd
update so can cache more easily

@@
 ```{r process data for plot 10b}
+library(PlayerRatings)
 current_cohort <- 1

### 2020-07-16 output_scripts/Paper_Plots.Rmd
try other cohort and try extend timeout limit to see if that fixes it

@@
 
-This is using the correct form of the compensator for a Hawkes process.
+<!-- This is using the correct form of the compensator for a Hawkes process. -->
 
@@
 ### Rank Comparison for Single Cohort ####
-current_cohort <- 1
+current_cohort <- 5
 
@@
 
-Not completed. This would need the rankings to be
-rerun for all cohorts.
+<!-- Not completed. This would need the rankings to be -->
+<!-- rerun for all cohorts. -->
 
@@
 
-Here is where I need to be a bit more careful about using the correct fits.
-Currently using all from Jing's saved output.
-
-In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices.
+<!-- Here is where I need to be a bit more careful about using the correct fits. -->
+<!-- Currently using all from Jing's saved output. -->
+
+<!-- In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices. -->
 
@@
 
-current_cohort <- 1
+current_cohort <- 3
 
@@
 training_end <- nrow(df[df$day<=18,])
-testing_end <- 1076
+testing_end <- nrow(df)#1077 #929 for cohort 5
 newx <- c(training_end:testing_end)
@@
 # ---------------- simulation mean and sd
-sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,200))
-for(s in 1:200){
+sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,100))
+for(s in 1:100){
   print(s)

### 2020-07-16 lib/simulatePrediction.R

@@ -65,7 +65,7 @@ simulateLatentMMHP <- function(lambda0_matrix,
             sim.cur.result <- tryCatch(expr = {withTimeout(simulate.mmhp(object = sim_mmhp_object, 
                                                                          termination=horizon,
                                                                          if.prefer.active=if.prefer.active),
-                                                           timeout = 5)},
+                                                           timeout = 25)},
                                        TimeoutException = function(ex) cat("Timeout. Skipping.\n"))
           }
           temp_mmhp <- sim.cur.result

### 2020-07-16 output_scripts/Paper_Plots.Rmd
try other cohort
fix merge conflict. some issues here with the data for some cohorts in fig 10a

@@
 
-current_cohort <- 3
+current_cohort <- 1
 
@@
 training_end <- nrow(df[df$day<=18,])
-testing_end <- nrow(df)#1077 #929 for cohort 5
+testing_end <- nrow(df)-1#1077 #929 for cohort 5
 newx <- c(training_end:testing_end)

### 2020-07-22 output_scripts/Paper_Plots.Rmd
run the same cohort for all plots, and some small changes to correct some plots

@@
 ```{r fig-2a-contour-plot}
-current_cohort <- 1
+current_cohort <- 5
 #png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
@@
 ```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE}
+current_cohort <- 5
+
 load(paste(data_path,cohort_names[current_cohort],
@@
 ```{r fig-3a-baseline-rate}
+current_cohort <- 5
+
 load(paste(data_path,cohort_names[current_cohort],
@@
 #     width=400, height=300)
-matrixPlotParameter(latent_social_matrix[rev(expert_rank_10[[current_cohort]]),expert_rank_10[[current_cohort]]],
+matrixPlotParameter(latent_social_matrix[rev(expert_rank_10[[current_cohort]]),
+                                         expert_rank_10[[current_cohort]]],
                     xLabels=expert_rank_10[[current_cohort]],
@@
 ```{r fig-3b-rank-comparison}
-current_cohort <- 1
+current_cohort <- 5
+
 colors_plot <- viridis(2)
@@
 axis(BELOW<-1, at=1:12, labels=expert_rank_10[[current_cohort]], cex.axis=1.3, tck=-0.015)
-mtext(text=11, side=1, line=0.5, cex=1.3, at=6)
+#mtext(text=11, side=1, line=0.5, cex=1.3, at=6)
 
@@
 line.wdth <- c(2,2.5)
-# negative.col <- add.alpha('lightskyblue',0.6)
-# positive.col <- add.alpha('tomato',0.6)
-negative.col <- viridis::viridis(5,alpha = 0.6)[1]
-positive.col <- viridis::viridis(5,alpha = 0.6)[4]
+negative.col <- add.alpha('lightskyblue',0.6)
+positive.col <- add.alpha('tomato',0.6)
+#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
+#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
 par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
@@
 
-```{r fig5-residual-ks}
+```{r fig5-residual-ks, fig.height=7}
 cols_plot <- viridis::viridis(4)
@@
       at=c(0:4)/5+0.1)
-mtext(text=c(1:5), side=1, line=1, outer=TRUE, cex=2,
+mtext(text=c(5:1), side=1, line=1, outer=TRUE, cex=2,
       at=c(0:4)/5+0.1)
@@
 
-```{r fig-7-prMatrix-Cohort1}
-current_cohort <- 1
+```{r fig-7-prMatrix-Cohort5, fig.height=7}
+current_cohort <- 5
 
@@
 
-```{r fig-8a-frob-norm-cohort1}
+```{r fig-8a-frob-norm-cohort5}
 load("../output/plot_N_predict.RData")
@@
 
-```{r construct data for plot, results='hide',message=FALSE,cache=TRUE}
+```{r construct data for plot, results='hide',message=FALSE,cache=FALSE}
 library(PlayerRatings)
 
-current_cohort <- 1
+current_cohort <- 5
 
@@
 # ---------------- simulation mean and sd
-sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,100))
-for(s in 1:100){
+sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,1000))
+for(s in 1:1000){
   print(s)
   temp_gl <- glickoScoreSimulationWithWindowsReturnAll(
-    predict.sim = m3_predict_sim[5:8,s],
+    predict.sim = m3_predict_sim[5:8,s], #7 for c 2 and 10
     history.df = glick.df[1:training_end,])
@@
   }else{
-    try(
-    history_matrix <- temp_gl[,1:testing_end]
-    )
+    # this line makes no sense, and should likely never happen
+    # try(
+    history_matrix <- history_matrix[,1:testing_end]#temp_gl$history[,1:testing_end]
+    # )
   }
@@
 # this doesn't need to be rerun ever, even if the stan fits change
+current_cohort <- 5
+
 load(paste(data_path,cohort_names[current_cohort],
@@
 library(PlayerRatings)
-current_cohort <- 1
+current_cohort <- 5
 load(paste(data_path,cohort_names[current_cohort],

### 2020-07-22 lib/matrixPlotParameter.R

@@ -7,8 +7,8 @@ matrixPlotParameter <- function(x, ...){
   #min<--0.78
   #max<-20
   #min<-0
-  yLabels <- rownames(x)
-  xLabels <- colnames(x)
+  #yLabels <- rownames(x)
+  #xLabels <- colnames(x)
   title <-c()
   # check for additional function arguments
   if( length(list(...)) ){
@@ -57,9 +57,9 @@ matrixPlotParameter <- function(x, ...){
   par(mar = c(1,3,1,1),mgp=c(0,0.7,0))
   image(1:length(xLabels), 1:length(yLabels), t(x), col=ColorRamp, xlab="",
         ylab="", axes=FALSE, zlim=c(min,max))
-  axis(BELOW<-1, at=1:length(xLabels), labels=xLabels, cex.axis=1.3, tck=-0.015)
+  axis(BELOW<-1, at=1:length(xLabels), labels=xLabels, cex.axis=1.1, tck=-0.015)
   axis(LEFT <-2, at=1:length(yLabels), labels=yLabels, las= HORIZONTAL<-1,
-       cex.axis=1.3, tck=-0.015)
+       cex.axis=1.1, tck=-0.015)
   mtext(side=3, text=title, line=0.8, cex=1.6, font=2)
   # Color Scale
   par(mar = c(1,2,1,1))
@@ -73,7 +73,8 @@ matrixPlotParameter <- function(x, ...){
 }
 
 # ----- Define a function for plotting a contour plot ----- #
-my.image.plot <- function(..., add = FALSE, xlab=NULL, ylab=NULL, my.main=NULL, cex.main=1, cex.lab = 1,
+my.image.plot <- function(..., add = FALSE, xlab=NULL, ylab=NULL, 
+                          my.main=NULL, cex.main=1, cex.lab = 1,
                           xLabels=NULL, yLabels=NULL,
                           breaks= NULL, nlevel = 64, col = NULL,  
                           horizontal = FALSE, legend.shrink = 0.9, legend.width = 1.2, 
@@ -81,7 +82,8 @@ my.image.plot <- function(..., add = FALSE, xlab=NULL, ylab=NULL, my.main=NULL, 
                           legend.line= 2,                    
                           graphics.reset = FALSE, bigplot = NULL, smallplot = NULL, 
                           legend.only = FALSE,  lab.breaks = NULL, 
[…]

### 2020-07-26 lib/matrixPlotParameter.R
change for the 3 values plot

@@ -254,6 +254,8 @@ myMultiMatrixPlot <- function(X,xLabels,yLabels,min,max,colorPalette,no_matrix,n
   }else if(no_matrix==3){
     layout(matrix(c(1:(no_matrix+3)), nrow=1), 
            widths=c(rep(c(6,1.7),no_matrix-1),6,1.2), heights=1)
+    layout(matrix(c(1:(no_matrix+1)), nrow=1), 
+           widths=c(rep(c(6),no_matrix-1),6,1.2), heights=1)
   }else{
     layout(cbind(matrix(data=c(1:no_matrix), nrow=n_row, ncol=no_matrix/n_row, byrow = TRUE),
                  rep(no_matrix+1,n_row)), 

### 2020-07-26 run_scripts/predict.R

@@ -218,7 +218,8 @@ for(s in 1:predict_sim){
   print(s)
   for(l in c(1:length(mmhp_par_names))){
     for(pair in c(1:nrow(unique_pairs_df))){
-      mmhp_par_matrix[[mmhp_matrix_names[l]]][unique_pairs_df$initiator[pair],unique_pairs_df$recipient[pair]] <- sim_mmhp_sep[[mmhp_par_names[l]]][s,pair]
+      mmhp_par_matrix[[mmhp_matrix_names[l]]][unique_pairs_df$initiator[pair],
+                                              unique_pairs_df$recipient[pair]] <- sim_mmhp_sep[[mmhp_par_names[l]]][s,pair]
     }
   }
   for(cur_win in c(1:nrow(to_predice_obs))){

### 2020-07-26 lib/uniHawkes.R
to identify issues here, which do appear to be happening

@@ -14,6 +14,11 @@ uniHawkesSimulation<-function(object, horizon=NULL, N=NULL){
   beta <- object$beta
   lambda.star <- lambda0
   
+  # if(alpha > beta) {
+  #   print("Uh oh")
+  #   return(0)
+  # }
+  
   if( !is.null(N) ){
     events <- numeric(N)
     U<-runif(1)

### 2020-07-26 output_scripts/Paper_Plots.Rmd
add some more plots for slides

@@
 
+```{r, eval=FALSE}
+par(mar=c(3,3,1,1))
+plot(as.vector(n_matrix[n_matrix>0]), as.vector(ks.stat.matrix[n_matrix>0]),
+     xlab="", ylab="", pch=16, col="gray", cex= 0.8, xaxt="n", yaxt="n",
+     ylim=c(0,0.65))
+mtext("Number of events", cex=1.5, side=1, line=1.8)
+mtext("K-S statistics", cex=1.5, side=2, line=1.5)
+mgp.axis(1,mgp=c(0,0.3,0),at=seq(0,120,10),cex.axis=1,lwd=0,lwd.ticks=0.1)
+mgp.axis(2,mgp=c(0,0.1,0),at=seq(-0.2,0.6,0.2),cex.axis=1,lwd=0,lwd.ticks=0.8)
+```
+
 # Figure 4:
@@
 
-```{r prepare data for 4b}
+```{r prepare data for 4b,cache=TRUE}
 plot.s <- 9
@@
 # Figure 5:
-```{r data for fig 5}
+```{r data for fig 5,cache=TRUE}
 load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
@@
 
+```{r fig-rank-slides, fig.height=3}
+
+p2_slides <- plot_cor_df %>%
+  filter(Method != "Agg-rank") %>%      
+  ggplot(aes(x="", y = cor, fill = Method)) +
+        geom_boxplot(alpha=0.7, width=0.5) +
+        scale_fill_manual(values = viridis::viridis(3)) + 
+        #ggtitle("(b)") +
+        ylim(0,1) +
+        theme_bw() +
+        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+              text = element_text(size = 20),
+              axis.text.y =element_text(size = 11),
+              legend.position="none",
+              axis.title.x=element_blank()) +
+        facet_grid(cols=vars(Method)) +
+        ylab("Rank correlation")
+p2_slides
+
+```
+
 # Figure 7: Pearson residual matrices
@@
                   yLabels=rev(expert_rank_10[[current_cohort]]),
-                  min=-60,max=60,axis_cex=2,title_cex = 1.8,
+                  min=-80,max=80,axis_cex=2,title_cex = 1.8,
                   colorPalette="RdBu",if.emp=FALSE,
                   #legend.mar=c(0.5,.5,0.5,0.5),
-                  title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
+                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
                   #title_lst = list("I-MMHP"),
-                  col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
+                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
                   matrix.mar=c(2.5,2.5,2.5,1)
@@
 ```
+
+```{r fig_pr_slides, fig.height=3, fig.width=7}
+current_cohort <- 5
+
+m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                   "/chp_pr_matrix_",cohort_names[current_cohort],
+                   ".RDS",sep=''))
+
+m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                     "/dchp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
+
+m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                     "/cmmhp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
+
+indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                     "/immhp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
+
+matrix_lst_plot <- list(
+                        #indep_pr[rev(expert_rank_10[[current_cohort]]),
+#                                                                   #expert_rank_10[[current_cohort]]],
+                        m1_pr[rev(expert_rank_10[[current_cohort]]),
+                                                                  expert_rank_10[[current_cohort]]],
+                        m2_pr[rev(expert_rank_10[[current_cohort]]),
+                                                                 expert_rank_10[[current_cohort]]],
+                        m3_pr[rev(expert_rank_10[[current_cohort]]),
+                                                                 expert_rank_10[[current_cohort]]]) 
+#cat("Cohort ",current_cohort,"\n",sep="")
+myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=3,n_row=1,
+                  xLabels=expert_rank_10[[current_cohort]],
+                  yLabels=rev(expert_rank_10[[current_cohort]]),
+                  min=-80,max=80,axis_cex=1,title_cex = 1.8,
+                  colorPalette="RdBu",if.emp=FALSE,
+                  #legend.mar=c(0.5,.5,0.5,0.5),
+                  title_lst=list("C-HP","C-DCHP","C-MMHP"), 
+                  #title_lst = list("I-MMHP"),
+                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
+                  matrix.mar=c(2.5,2.5,2.5,0.5)
+                  )
+
+```
+
 <!-- The remaining plot code seems to mostly be in `PaperPlots.R`. -->
@@
 #png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
-p3 <- ggplot(temp_plot_df, aes(x = method, y = norm, fill = method)) +
+p3 <- temp_plot_df %>%
+  rowwise() %>%
+  mutate(norm = min(norm,60)) %>%
+  ggplot( aes(x = method, y = norm, fill = method)) +
   geom_boxplot(alpha=0.7) +
@@
   ylab("Frobenius norm of error") +
-  ylim(0, 50)
+  ylim(0, 60)
 p3
@@
   group_by(day, method) %>% 
-  summarize(avg=mean(norm), n= n(), sd=sd(norm))
+  summarise(avg=mean(norm), n= n(), sd=sd(norm))
 
@@
 p4
+```
+
+```{r fig-slides-predict}
+load("../output/plot_N_predict_new.RData")
+temp_plot_df <- all_cohort_norm_df %>% 
+  group_by(day, method) %>% 
+  summarise(avg=mean(norm), n= n(), sd=sd(norm),
+            se = sd/sqrt(n))
+
+temp_plot_df$method <- factor(temp_plot_df$method,
+                              levels = c("mmhp","dsnl","m1","m2","m3"),
+                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+temp_plot_df$day <- factor(temp_plot_df$day)
+
+#png(paste(plot_path,"real_predict_N_all_cohort.png",sep=""),width=600,height=300)
+p4_slides <- ggplot(temp_plot_df, 
+                    aes(x=day, y=avg, group=method, color=method)) + 
+  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
+  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
+                 position=position_dodge(0.2)) +
+  scale_color_manual(values = viridis::viridis(5)) + 
+  #ggtitle("(b)") +
+  theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_text(size = 18)) +
+  xlab("Prediction horizon (day)") + 
+  ylab("Frobenius norm of error") + 
+  coord_cartesian(ylim=c(2.5,57.5)) + 
+  guides(color=guide_legend(title="Model")) 
+p4_slides
+
+```
+
+```{r}
+
+all_sims <- do.call(rbind,predict_day_norm_df_lst)
+
+temp_plot_df <- all_sims %>% 
+  group_by(day, method) %>% 
+  summarise(avg=mean(norm), n= n(), sd=sd(norm),
+            se = sd/n)
+
+temp_plot_df$method <- factor(temp_plot_df$method,
+                              levels = c("mmhp","dsnl","m1","m2","m3"),
+                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+temp_plot_df$day <- factor(temp_plot_df$day)
+p4_slides <- temp_plot_df %>% #filter(method != "C-HP") %>% 
+  #filter(method != "I-MMHP") %>%
+  ggplot(aes(x=day, y=avg, group=method, color=method)) + 
+  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
+  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
+                 position=position_dodge(0.2)) +
+  scale_color_manual(values = viridis::viridis(5)) + 
+  #ggtitle("(b)") +
+  theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_text(size = 18)) +
+  xlab("Prediction horizon (day)") + 
+  ylab("Frobenius norm of error") + 
+  coord_cartesian(ylim=c(2.5,57.5)) + 
+  guides(color=guide_legend(title="Model")) #+ ylim(c(0,1000))
+p4_slides
+
 ```
@@
                 position=position_dodge(0.2)) +
-  scale_fill_manual(values = viridis::viridis(5)) +
+  scale_color_manual(values = viridis::viridis(5)) +
   #scale_color_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +

### 2020-07-26 output_scripts/Paper_Plots.Rmd
add plots for slides

@@
                       warning = FALSE)
+
+slides_plots <- TRUE
 ```
@@
 
-```{r fig-rank-slides, fig.height=3}
+```{r fig-rank-slides, fig.height=3,include=slides_plots,eval=slides_plots}
 
@@
 
-```{r fig_pr_slides, fig.height=3, fig.width=7}
+```{r fig_pr_slides, fig.height=3, fig.width=7, include=slides_plots,eval=slides_plots}
 current_cohort <- 5
@@
 ```
+```{r fig-pred-cohort-slides, include=slides_plots,eval=slides_plots, fig.height=3}
+load("../output/plot_N_predict_new.RData")
+current_cohort <- 5# cohort 1 looks worse than rest
+# 3 looks nice
+
+temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
+temp_plot_df$method <- factor(temp_plot_df$method,
+                              levels = c("mmhp","dsnl","m1","m2","m3"),
+                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+temp_plot_df$day <- factor(temp_plot_df$day)
+#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
+p3_slides <- temp_plot_df %>%
+  filter(method != "I-MMHP") %>%
+  rowwise() %>%
+  mutate(norm = min(norm,120)) %>%
+  ggplot( aes(x = method, y = norm, fill = method)) +
+  geom_boxplot(alpha=0.7) +
+  scale_fill_manual(values = viridis::viridis(5)) +
+  #ggtitle("(a)") +
+  theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.position="right") +
+  facet_grid(cols=vars(day)) +
+  xlab("Prediction horizon (day)") + 
+  ylab("Frobenius norm of error") +
+  #ylim(0, 60) +
+  NULL
+p3_slides
+```
 
@@
 
-```{r fig-slides-predict}
+```{r fig-slides-predict,include=slides_plots,eval=slides_plots,fig.height=3}
 load("../output/plot_N_predict_new.RData")
@@
 
-```{r}
+```{r, include=FALSE,eval=FALSE}
 
@@
   geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
-  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
+  geom_errorbar(aes(ymin=max(0,avg-sd), ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                  position=position_dodge(0.2)) +
@@
   ylab("Frobenius norm of error") + 
-  coord_cartesian(ylim=c(2.5,57.5)) + 
+  #coord_cartesian(ylim=c(2.5,57.5)) + 
   guides(color=guide_legend(title="Model")) #+ ylim(c(0,1000))
@@
 
+```{r fig-pred-cor, eval=slides_plots,include=slides_plots,fig.height=3}
+load("../output/plot_rank_predict.RData")
+current_cohort <- 5
+temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
+temp_plot_df$method <- factor(temp_plot_df$method,
+                              levels = c("mmhp","dsnl","m1","m2","m3"),
+                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+temp_plot_df$day <- factor(temp_plot_df$day)
+# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),width=600,height=300)
+temp_plot_df <- temp_plot_df %>%
+  filter(method != "I-MMHP") 
+p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
+  geom_boxplot(alpha=0.7) +
+  scale_fill_manual(values = viridis::viridis(5)) +
+  #scale_fill_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
+  #ggtitle("(a)") +
+  theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_blank(),
+        axis.ticks.x = element_blank(), 
+        legend.position="right") +
+  facet_grid(cols=vars(day)) +
+  xlab("Prediction horizon (day)") + 
+  ylab("Rank correlation") +
+  ylim(0, 1)
+p5
+```
+
 ## Figure 9b: Predicted Spearman rank for all cohorts
@@
 
-```{r construct data for plot, results='hide',message=FALSE,cache=FALSE}
+```{r construct data for plot, results='hide',message=FALSE,cache=TRUE}
 library(PlayerRatings)
@@
 mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
+```
+
+```{r fig-glicko-pred-slides,eval=slides_plots,include=slides_plots}
+par(mar=c(3,5,3,1))
+plot(1, type="n", xlab="", ylab="Glicko ranking", xlim=c(0,dim(gl$history)[2]),
+     ylim=c(min(gl$history[,,1]),max(gl$history[,,1])),
+     cex.axis=2, cex.lab=2)
+for(m in c(1:mice_number)){
+  #history
+  lines(gl$history[m,1:training_end,1],
+        cex=0.6, col=col_vec[m],lwd=history_width,lty=ltypes_vec[m])
+  lines(c(rep(NA,training_end), gl$history[m,(training_end+1):testing_end,1]),
+        cex=0.6, col=shade_vec[m],lwd=history_width,lty=ltypes_vec[m])
+
+  #simulation
+  cur_end <- testing_end
+  mean_vec <- apply(sim_gl_array[m,,],1,function(x) mean(na.omit(x)))
+  sd_vec <- apply(sim_gl_array[m,,],1,function(x) sd(na.omit(x)))
+  polygon(c(newx, rev(newx)), c(mean_vec-sd_vec,rev(mean_vec+sd_vec)),col = shade_vec[m], border = NA)
+  #polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
+  lines(c(rep(NA,training_end),mean_vec),
+        cex=0.6, col=col_vec[m],lwd=1,lty=2)
+}
+
+# annotate the days
+for(d in c(19:21)){
+  abline(v = nrow(df[df$day<=(d-1),]),lty=2,lwd=0.4)
+  text(x=nrow(df[df$day<=(d-1),]),y=2600,d)
+}
+#mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
 ```

### 2020-07-30 output_scripts/Paper_Plots.Rmd
rewrite the simulated stan fits to enfore the stationarity condition

--- 2020-07-26 output_scripts/Paper_Plots.Rmd
@@
 
+```{r fig-pred-cohort-slides, include=slides_plots,eval=slides_plots, fig.height=3}
+load("../output/plot_N_predict.RData")
+current_cohort <- 5# cohort 1 looks worse than rest
+# 3 looks nice
+
+temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
+temp_plot_df$method <- factor(temp_plot_df$method,
+                              levels = c("mmhp","dsnl","m1","m2","m3"),
+                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+temp_plot_df$day <- factor(temp_plot_df$day)
+#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
+p3_slides <- temp_plot_df %>%
+  filter(method != "I-MMHP") %>%
+  rowwise() %>%
+  #mutate(norm = min(norm,100)) %>%
+  ggplot( aes(x = method, y = norm, fill = method)) +
+  geom_boxplot(alpha=0.7) +
+  scale_fill_manual(values = viridis::viridis(5)) +
+  #ggtitle("(a)") +
+  theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.position="right") +
+  facet_grid(cols=vars(day)) +
+  xlab("Prediction horizon (day)") + 
+  ylab("Frobenius norm of error") +
+  ylim(0, 80) +
+  NULL
+p3_slides
+```
+
 ## Figure 8b: Same plot aggregated for all cohorts
@@
 
-```{r fig-slides-predict}
-load("../output/plot_N_predict_new.RData")
+```{r fig-slides-predict,include=slides_plots,eval=slides_plots,fig.height=3}
+load("../output/plot_N_predict.RData")
 temp_plot_df <- all_cohort_norm_df %>% 
@@
 p4_slides <- temp_plot_df %>% #filter(method != "C-HP") %>% 
-  #filter(method != "I-MMHP") %>%
+  filter(method != "I-MMHP") %>%
   ggplot(aes(x=day, y=avg, group=method, color=method)) + 

### 2020-08-05 output_scripts/Diagnostics.Rmd
add some words

@@
 
-data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_prior/"
+#data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_prior/"
 
@@
 
-# Correction to Pair level rates
-
-A previous bug with C-MMHP was not correctly accounting for the degree 
-corrected `lambda0` and corresponding
-`lambda1` between each pair when interpolating the latent states and then 
-identifying the residual matrices. This gives more reasonable results for
-overall model fit in terms of the total Pearson residuals summed across all 
-observation windows.
+<!-- # Correction to Pair level rates -->
+
+<!-- A previous bug with C-MMHP was not correctly accounting for the degree  -->
+<!-- corrected `lambda0` and corresponding -->
+<!-- `lambda1` between each pair when interpolating the latent states and then  -->
+<!-- identifying the residual matrices. This gives more reasonable results for -->
+<!-- overall model fit in terms of the total Pearson residuals summed across all  -->
+<!-- observation windows. -->
+
+# Pearson Residuals
+
+We first compute the Pearson residuals for each of the proposed models for
+each of the 10 cohorts. Here I-MMHP is the unconstrained model which
+does not learn a latent ranking.
 
@@
 
+We can then plot the estimated latent ranks from C-MMHP to the 
+I&SI ranks. They are highly correlated but not identical (I&SI only using counts 
+rather than the times of interactions).
+
 ```{r}
@@
 
+Similarly we can plot the out/in degree parameters of the C-MMHP model
+against both the I&SI ranking and also the latent ranking from the
+model. This indicates that these degree parameters capture a different structure
+to just the dominance of the animals.
+
 ```{r}
@@
 # Examine Intensity and QQ Plot
+
+As a further model checking, for each cohort we take the
+pair with the most interactions and the window which contains the
+most interactions for this pair and plot the estimated intensity and
+the corresponding QQ plot.
 

### 2020-08-25 output_scripts/Deg_Corr_Priors.Rmd

---
title: "Degree Priors"
author: "Owen Ward"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: FALSE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

data_path <- "../output/"

func_dir <- "../lib/"

library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(fields)
library(bayesplot)
library(compete)
library(RColorBrewer)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

source("C:/Users/owenw/Dropbox/with Owen/code/part3/lib/intensityPlot.R")
source("C:/Users/owenw/Dropbox/with Owen/code/part3/lib/uniHawkes.R")

theme_set(theme_minimal())

model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})

```

```{r mice_setup,include=FALSE,echo=FALSE, cache=TRUE}
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
for(current_cohort in fit_cohorts){
  naive_rank_10[[current_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[current_cohort]]])
  expert_rank_10[[current_cohort]] <- expertRankHierarchy(full_data[[cohort_names[current_cohort]]])
}

```

While the currently implemented degree corrected C-MMHP model gives
good overall results, the `double_exponential` priors used for the degree 
rate parameters `gamma` and `zeta` lead to issues with mixing of these
chains. As such, we wish to identify a better choice of prior here
and see how this effects the downstream tasks performed.

# Run for longer

The simplest solution to these mixing issues is to fit the same model,
but adapting some of the stan fit parameters to avoid issues with sampling.

In particular, we consider

- `adapt_delta = 0.999`
- `max_treedepth = 15`

These makes this fit even more computationally demanding. Only several
cohorts were able to complete, for which the overall results looked similar.

Diagnostic plots will be included.

```{r}
orig_data_path <- "../output/"

lognor_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_lognor/"

long_run_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_tree_depth/"

current_cohort <- 8

# compare long run first

# load original fit

load(paste(orig_data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
old_fit <- fit_cohort_mmhp
bayesplot::rhat(old_fit)

load(paste(long_run_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
long_fit <- fit_cohort_mmhp
bayesplot::rhat(long_fit)
```

```{r}
m3_pr_orig <- readRDS(paste(orig_data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

m3_pr_long <- readRDS(paste(long_run_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

summary(as.vector(m3_pr_long-m3_pr_orig))

#####
m1_pr <- readRDS(paste(orig_data_path,cohort_names[current_cohort],
                       "/chp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

m2_pr <- readRDS(paste(orig_data_path,cohort_names[current_cohort],
                       "/dchp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

# m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
#                        "/cmmhp_pr_matrix_",cohort_names[current_cohort],
#                        ".RDS",sep=''))

indep_pr <- readRDS(paste(orig_data_path,cohort_names[current_cohort],
                          "/immhp_pr_matrix_",cohort_names[current_cohort],
                          ".RDS",sep=''))

matrix_lst_plot <- list(
  indep_pr[rev(expert_rank_10[[current_cohort]]),
           expert_rank_10[[current_cohort]]],
  m1_pr[rev(expert_rank_10[[current_cohort]]),
        expert_rank_10[[current_cohort]]],
  m2_pr[rev(expert_rank_10[[current_cohort]]),
        expert_rank_10[[current_cohort]]],
  m3_pr_orig[rev(expert_rank_10[[current_cohort]]),
        expert_rank_10[[current_cohort]]]) 
cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-60,max=60,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
)

matrix_lst_plot <- list(
  indep_pr[rev(expert_rank_10[[current_cohort]]),
           expert_rank_10[[current_cohort]]],
  m1_pr[rev(expert_rank_10[[current_cohort]]),
        expert_rank_10[[current_cohort]]],
  m2_pr[rev(expert_rank_10[[current_cohort]]),
        expert_rank_10[[current_cohort]]],
  m3_pr_long[rev(expert_rank_10[[current_cohort]]),
        expert_rank_10[[current_cohort]]]) 
cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-60,max=60,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
)

```

# Lognormal priors

Alternatively, we consider lognormal priors for `gamma` and `zeta`. We
consider `model_3_1_bound.stan`, with `gamma ~ lognormal(0,1)` and
`zeta ~ lognormal(0,1)` also.

```{r}
lgnor_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_lnor/"

```

```{r compare a cohort}
current_cohort <- 3

load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

orig_fit <- fit_cohort_mmhp
orig_sim <- sim_cohort_mmhp

load(paste(lgnor_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

lnor_fit <- fit_cohort_mmhp
lnor_sim <- sim_cohort_mmhp

```

```{r}
rstan::check_hmc_diagnostics(orig_fit)
rstan::check_hmc_diagnostics(lnor_fit)
```

```{r}
summary(bayesplot::rhat(orig_fit))
summary(bayesplot::rhat(lnor_fit))

```

```{r}
apply(orig_sim$f,2,mean) - apply(lnor_sim$f,2,mean)

plot(apply(orig_sim$f,2,mean),apply(lnor_sim$f,2,mean))

plot(apply(orig_sim$lambda0,2,mean),apply(lnor_sim$lambda0,2,mean))

plot(apply(orig_sim$gamma,2,mean),apply(lnor_sim$gamma,2,mean))
plot(apply(orig_sim$zeta,2,mean),apply(lnor_sim$zeta,2,mean))

hist(apply(orig_sim$lambda0,2,mean) - apply(lnor_sim$lambda0,2,mean))

```

```{r}
mean(orig_sim$w_lambda)-mean(lnor_sim$w_lambda)
mean(lnor_sim$w_lambda)
```

This indicates.

```{r}
plot(orig_sim$w_lambda,lnor_sim$w_lambda)
#dim(orig_sim$alpha)

plot(orig_sim$alpha,lnor_sim$alpha)

plot(orig_sim$beta,lnor_sim$beta)

```

```{r pr-matrices}

for(current_cohort in 1:10) {
  m3_pr_orig <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  m3_pr_lnor <- readRDS(paste(lgnor_path,cohort_names[current_cohort],
                         "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))

  summary(as.vector(m3_pr_lnor-m3_pr_orig))

  #####
  m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                         "/chp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))

  m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                         "/dchp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))

  # m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
  #                        "/cmmhp_pr_matrix_",cohort_names[current_cohort],
  #                        ".RDS",sep=''))

  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                            "/immhp_pr_matrix_",cohort_names[current_cohort],
                            ".RDS",sep=''))

  cat("Cohort ",current_cohort,"\n",sep="")

  matrix_lst_plot <- list(
    indep_pr[rev(expert_rank_10[[current_cohort]]),
             expert_rank_10[[current_cohort]]],
    m1_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m2_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m3_pr_orig[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]]) 
  #cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
  )

  matrix_lst_plot <- list(
    indep_pr[rev(expert_rank_10[[current_cohort]]),
             expert_rank_10[[current_cohort]]],
    m1_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m2_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m3_pr_lnor[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]]) 
  #cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
  )
}

```

# Exponential Priors

```{r}
exp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_exp/"

```

```{r}
current_cohort <- 7

load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

orig_fit <- fit_cohort_mmhp
orig_sim <- sim_cohort_mmhp

load(paste(exp_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

exp_fit <- fit_cohort_mmhp
exp_sim <- sim_cohort_mmhp
```

```{r}
summary(bayesplot::rhat(orig_fit)[-588])
summary(bayesplot::rhat(exp_fit)[-588])
```
Cohorts 7 and 10 still look bad although an improvement for 9.

```{r}
apply(orig_sim$f,2,mean) - apply(exp_sim$f,2,mean)

plot(apply(orig_sim$f,2,mean),apply(exp_sim$f,2,mean))

plot(apply(orig_sim$lambda0,2,mean),apply(exp_sim$lambda0,2,mean))

plot(apply(orig_sim$gamma,2,mean),apply(exp_sim$gamma,2,mean))
plot(apply(orig_sim$zeta,2,mean),apply(exp_sim$zeta,2,mean))

hist(apply(orig_sim$lambda0,2,mean) - apply(exp_sim$lambda0,2,mean))
```

```{r}
fit_cohorts <- 1:10
fit_cohorts <- fit_cohorts[c(-1,-3,-5,-6)]

for(current_cohort in fit_cohorts) {
  m3_pr_orig <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  m3_pr_exp <- readRDS(paste(exp_path,cohort_names[current_cohort],
                         "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))

  summary(as.vector(m3_pr_exp-m3_pr_orig))

  #####
  m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                         "/chp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))

  m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                         "/dchp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))

  # m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
  #                        "/cmmhp_pr_matrix_",cohort_names[current_cohort],
  #                        ".RDS",sep=''))

  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                            "/immhp_pr_matrix_",cohort_names[current_cohort],
                            ".RDS",sep=''))

  cat("Cohort ",current_cohort,"\n",sep="")

  matrix_lst_plot <- list(
    indep_pr[rev(expert_rank_10[[current_cohort]]),
             expert_rank_10[[current_cohort]]],
    m1_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m2_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m3_pr_orig[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]]) 
  #cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
  )

  matrix_lst_plot <- list(
    indep_pr[rev(expert_rank_10[[current_cohort]]),
             expert_rank_10[[current_cohort]]],
    m1_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m2_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m3_pr_lnor[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]]) 
  #cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
  )
}

```

# Inverse Gamma Prior

We instead consider `inv_gamma(1,0.5)` priors for both `gamma` and `zeta`.

```{r}
ing_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_invg_2/"

```

```{r compare a cohort inv gamma}
current_cohort <- 5

load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

orig_fit <- fit_cohort_mmhp
orig_sim <- sim_cohort_mmhp

load(paste(ing_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

ing_fit <- fit_cohort_mmhp
ing_sim <- sim_cohort_mmhp

```

```{r}
rstan::check_hmc_diagnostics(orig_fit)
rstan::check_hmc_diagnostics(ing_fit)
```

```{r}
summary(bayesplot::rhat(orig_fit))
summary(bayesplot::rhat(ing_fit))
```

```{r}
fit_cohorts <- 1:10
#fit_cohorts <- fit_cohorts[c(-1,-3,-5,-6)]

i_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_immhp/"

for(current_cohort in fit_cohorts) {
  m3_pr_orig <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  m3_pr_ing <- readRDS(paste(ing_path,cohort_names[current_cohort],
                         "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))

  summary(as.vector(m3_pr_exp-m3_pr_orig))

  #####
  m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                         "/chp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))

  m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                         "/dchp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))

  # m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
  #                        "/cmmhp_pr_matrix_",cohort_names[current_cohort],
  #                        ".RDS",sep=''))

  indep_pr <- readRDS(paste(i_mmhp_path,cohort_names[current_cohort],
                            "/immhp_pr_matrix_",cohort_names[current_cohort],
                            ".RDS",sep=''))

  cat("Cohort ",current_cohort,"\n",sep="")

  matrix_lst_plot <- list(
    indep_pr[rev(expert_rank_10[[current_cohort]]),
             expert_rank_10[[current_cohort]]],
    m1_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m2_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m3_pr_orig[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]]) 
  #cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
  )

  matrix_lst_plot <- list(
    indep_pr[rev(expert_rank_10[[current_cohort]]),
             expert_rank_10[[current_cohort]]],
    m1_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m2_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m3_pr_lnor[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]]) 
  #cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
  )
}

```

### 2020-08-25 output_scripts/Paper_Plots.Rmd

@@
 
-slides_plots <- TRUE
+slides_plots <- FALSE
 ```
@@
 ```{r prepare data for 4b,cache=TRUE}
-plot.s <- 9
+plot.s <- 7#9
 plot.i <- 4
@@
 
-lambda.m2<-uniHawkesIntensityNumeric(object=list(lambda0=model2_par_est$gamma[plot.i]+
+lambda.m2 <- uniHawkesIntensityNumeric(object=list(
+  lambda0=model2_par_est$gamma[plot.i]+
           model2_par_est$zeta[plot.j],                                        
@@
 
-## don't have these parameters....?
 state.est.latent.mmhp <- interpolate_state_est_lst[[plot.s]][plot.i,plot.j][[1]]
-state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp, termination=200)
-
-# where is fixInterpolateState?...
-# this is in one of the files at the top of latent_simulation.Rmd
-# drawIntensity.R
-
-step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,2-state.est.latent.mmhp$z.hat)
+state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
+                                                 termination=200)
+
+step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,
+                        2-state.est.latent.mmhp$z.hat)
 
@@
 
-lambda.true <- mmhpTrueIntensityNumeric(params=object_true, t=temp.t,
+lambda.true <- mmhpTrueIntensityNumeric(params=object_true,
+                                        t=temp.t,
                        latent=list(x=fixStateTransition(test.mmhp)$x,
@@
 ```{r fig4b-recover-latent-states}
-y.ub <- c(130,72,31)
+y.ub <- c(20,20,20)#c(130,72,31)
 #model_colors <- c("steelblue", "goldenrod2", "firebrick2")
@@
 legend.y <- #c(34,32,32)
-legend.y <- c(62,37,18)#c(22,22,22)
+legend.y <- c(20,12,15)#c(62,37,18)#c(22,22,22)
 legend.cex <- 1.5 #3
@@
 drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
-
                          alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
@@
      line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
-# axis(2,at=c(-10,y.ub[1]),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-# axis(3,at=c(-5,my.long.x),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-# axis(4,at=c(-10,y.ub[1]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
 
@@
 # changed 34 to 23, 25 to 18, -20 to -10
-legend(20,104,c("State 1/0 events","State change point"),
-       col = c(NA,"red"),
-       y.intersp=0.85,x.intersp=-0.1, bty = "n",
-       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
-       lty = c(NA,NA), lwd=c(NA,4))
-points(29,84,pch=1,cex=2,col="blue")
-points(26,84,pch=16,cex=2,col="blue")
+# legend(10,legend.y[1],c("State 1/0 events","State change point"),
+#        col = c(NA,"red"),
+#        y.intersp=0.85,x.intersp=-0.1, bty = "n",
+#        pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
+#        lty = c(NA,NA), lwd=c(NA,4))
+# points(29,84,pch=1,cex=2,col="blue")
+# points(26,84,pch=16,cex=2,col="blue")
 legend(legend.x[1],legend.y[1],c("True"),
@@
        lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
-
-# legend(93,24,c("Overestimation","Underestimation"),
-#        col = c(positive.col,negative.col),
-#        y.intersp=0.88,x.intersp=0.5,bty = "n",
-#        lty = c(1,1), lwd = c(20,20), cex=legend.cex,seg.len=0.8)
 
@@
         c(0,delta.positive,0),col=positive.col,border=NA)
-# segments(0,0,my.xlim,0,col="gray45")
-## draw box
-# change -0.7 to -0.5 and -0.5 to -0.25
+
 axis(1,at=c(-2,my.long.x),col="gray35",
      line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-# axis(2,at=c(-2,y.ub[1]),col="gray35",
-#      line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-# axis(4,at=c(-2,y.ub[1]),col="gray35",
-#      line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
 
@@
        lty = 1, lwd = 5, cex= legend.cex,seg.len=1)
-## draw box
-# -20 to -10 to -5 here
+
 axis(1,at=c(-2,my.long.x),col="gray35",
      line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
-# axis(2,at=c(-5,y.ub[2]),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-# axis(3,at=c(-5,my.long.x),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-# axis(4,at=c(-5,y.ub[2]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+legend(10,legend.y[2],c("State 1/0 events","State change point"),
+       col = c(NA,"red"),
+       y.intersp=0.85,x.intersp=-0.1, bty = "n",
+       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
+       lty = c(NA,NA), lwd=c(NA,4))
+points(14,8,pch=1,cex=2,col="blue")
+points(16,8,pch=16,cex=2,col="blue")
 
@@
 delta.negative[delta.negative>0] <- 0
-#### hiding these for now ####
 polygon(c(0,lambda.true$time.vec,200), c(0,delta.negative,0),col=negative.col,border=NA)
@@
      line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-# axis(2,at=c(-20,y.ub[2]),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-# axis(4,at=c(-20,y.ub[2]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
 
@@
 par(mar = c(0,0.3,1,0.1))
-drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
-                          yupper=y.ub[3], color=add.alpha("black", alpha=line.alpha[1]),line.width=line.wdth[1],
+drawUniMMHPIntensityPaper(true.object,
+                          simulation=fixStateTransition(test.mmhp),
+                          yupper=y.ub[3],
+                          color=add.alpha("black", alpha=line.alpha[1]),
+                          line.width=line.wdth[1],
                           y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
                           box.type="n")
-drawUniMMHPIntensityPaper(object_hat,simulation=list(
+drawUniMMHPIntensityPaper(object_hat,
+                          simulation = list(
   x=state.est.latent.mmhp.new$x.hat,                                          
@@
      line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
-# axis(2,at=c(-20,y.ub[3]),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-# axis(3,at=c(-5,my.long.x),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-# axis(4,at=c(-20,y.ub[3]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-
-legend(55,32,c("Overestimation","Underestimation"),
+
+legend(10,legend.y[3],c("Overestimation","Underestimation"),
        col = c(positive.col,negative.col),
@@
      line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-# axis(2,at=c(-20,y.ub[1]),col="gray35",
-#      line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-# axis(4,at=c(-20,y.ub[1]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
 
@@
   rowwise() %>%
-  mutate(norm = min(norm,60)) %>%
+  #mutate(norm = min(norm,60)) %>%
   ggplot( aes(x = method, y = norm, fill = method)) +
@@
   ylab("Frobenius norm of error") +
-  ylim(0, 60) 
+  ylim(0, 150) +
+  NULL
 p3
@@
 
-```{r process for state separation cohort1,eval=FALSE}
+```{r process for state separation cohort5,eval=FALSE}
 # only run this once and save the results

### 2020-08-26 output_scripts/aug_updates.Rmd
start adding updates for James

---
title: "Comments on Latent Ranking"
author: "Owen Ward"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: FALSE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

data_path <- "../output/"

func_dir <- "../lib/"

library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(fields)
library(bayesplot)
library(compete)
library(RColorBrewer)
library(ggplot2)
library(gridExtra)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

#source("C:/Users/owenw/Dropbox/with Owen/code/part3/lib/intensityPlot.R")
#source("C:/Users/owenw/Dropbox/with Owen/code/part3/lib/uniHawkes.R")

theme_set(theme_minimal())

model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){
  return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))}
  )
```

```{r mice_setup,include=FALSE,echo=FALSE, cache=TRUE}
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
for(current_cohort in fit_cohorts){
  naive_rank_10[[current_cohort]] <-
    naiveRankHierarchy(full_data[[cohort_names[current_cohort]]])
  expert_rank_10[[current_cohort]] <-
    expertRankHierarchy(full_data[[cohort_names[current_cohort]]])
}
```

# Do closer ranked mice fight more?

To see if closer ranked mice fight more, we would like to look
at the conditional intensity as a function of the absolute difference in the
latent ranks.

There are two components to this. Whether a pair of mice will be in the
active state (where fighting is more likely), and, in this active state,
the value of the excitation parameter (which controls the likelihood of
fighting again following a previous fight).

```{r difference in ranking for all cohorts}
for(current_cohort in 1:10) {
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
  # have 1000 draws here
  eta_1_mean <- mean(sim_cohort_mmhp$eta_1)
  eta_2_mean <- mean(sim_cohort_mmhp$eta_2)
  eta_3_mean <- mean(sim_cohort_mmhp$eta_3)

  f_1 <- seq(from = 0.01, to = 0.99, by = 0.01)
  f_2 <- seq(from = 0.01, to = 0.99, by = 0.01)

  possible_vals <- expand_grid(f_1,f_2)

  excitation <- map2_dbl(possible_vals$f_1, possible_vals$f_2,function(.x,.y) 
      eta_1_mean*.x*.y*exp(-eta_2_mean*abs(.x-.y)) )

  prop_active <- map2_dbl(possible_vals$f_1, possible_vals$f_2,function(.x,.y) 
      1/(1+exp(-eta_3_mean*(.x-.y)))
     )

  possible_vals$excit <- excitation
  possible_vals$active <- prop_active

  plot_alpha <- possible_vals %>% ggplot(aes(f_1,f_2)) + 
    geom_raster(aes(fill=excit)) + 
    scale_fill_continuous(name = "alpha",low = "red", high = "blue") + 
    ggtitle(paste("Cohort ", current_cohort,
                  " excitation parameter",sep=""))

  plot_active <- possible_vals %>% ggplot(aes(f_1,f_2)) + 
    geom_raster(aes(fill=active)) + 
    scale_fill_continuous(name = "Prop. active",low = "red", high = "blue") + 
    ggtitle(paste("Cohort ", current_cohort,
                  " proportion of time active",sep=""))
  print(plot_alpha)
  print(plot_active)
}
```

```{r intensity as function of abs diff in ranks, include=FALSE}
current_cohort <- 1
load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
  # have 1000 draws here
eta_1_mean <- mean(sim_cohort_mmhp$eta_1)
eta_2_mean <- mean(sim_cohort_mmhp$eta_2)
eta_3_mean <- mean(sim_cohort_mmhp$eta_3)

f_1 <- seq(from = 0.01, to = 0.99, by = 0.01)
f_2 <- seq(from = 0.01, to = 0.99, by = 0.01)

possible_vals <- expand_grid(f_1,f_2)

excitation <- map2_dbl(possible_vals$f_1, possible_vals$f_2,function(.x,.y) 
    eta_1_mean*.x*.y*exp(-eta_2_mean*abs(.x-.y)) )

prop_active <- map2_dbl(possible_vals$f_1, possible_vals$f_2,function(.x,.y) 
    1/(1+exp(-eta_3_mean*(.x-.y)))
   )

possible_vals$excit <- excitation
possible_vals$active <- prop_active

possible_vals %>% mutate(abs_diff = abs(f_1-f_2)) %>%
  ggplot(aes(abs_diff,excit)) + geom_point()

possible_vals %>% mutate(abs_diff = abs(f_1-f_2)) %>%
  ggplot(aes(abs_diff,prop_active)) + geom_point() +
  xlab("Absolute Difference in Ranks") +
  ylab("Proportion of Active Time")

# plot_alpha <- possible_vals %>% ggplot(aes(f_1,f_2)) + 
#   geom_raster(aes(fill=excit)) + 
#   scale_fill_continuous(name = "alpha",low = "red", high = "blue") + 
#   ggtitle(paste("Cohort ", current_cohort,sep=""))
```

Based on these plots, pairs of mice are more likely to be in the active state
when the instigating mouse is ranked significantly higher than the mouse it
fights. However, in the active state, the excitation parameter (and
the likelihood of continuing to fight) is higher 
when both mice are higher ranked. This is relatively consistent across each of
the cohorts here.

# Exploring $\eta$ parameters

The parameters $\eta_1,\eta_2,\eta_3$ in this model are related to the
probability of being in the active state and the excitation parameter 
when in this active state. We can first look at the posterior distribution
of these parameters and their posterior means.

```{r posterior pairs for eta, message=FALSE}
for(current_cohort in 1:10) {
  #cat("Cohort, ", current_cohort,"\n",sep="")
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

  eta <- tibble(eta_1 = sim_cohort_mmhp$eta_1,
                eta_2 = sim_cohort_mmhp$eta_2,
                eta_3 = sim_cohort_mmhp$eta_3)
  print("Posterior Mean of eta parameters")
  print( eta %>% map_dbl(mean) )

  p <- GGally::ggpairs(eta) + 
    ggtitle(paste("Cohort ", current_cohort,sep=""))

  print(p)
}
```

To explore what these parameters correspond to, the model for
the conditional intensity is given by

$$
\lambda^{i,j}(t) = \gamma_i + \zeta_j +(\lambda_1-\gamma_i-\zeta_j)Z^{i,j}(t) 
$$

$$
+
\eta_1 f_i f_j 
\exp(-\eta_2|f_i-f_j|)Z^{i,j}(t)\sum_{k}\exp(-\beta(t-t_{k}^{i,j})),
$$
with
$$
q_1^{i,j} = \exp(-\eta_3 f_i),\ q_0^{i,j} = \exp(-\eta_3 f_j).
$$
So here, these parameters correspond to:

- $\eta_1$ excitation as a function of the product of the latent ranks.
- $\eta_2$ is related to the absolute difference between the ranks of the mice. 
The posterior mean for this parameter is less than 1 for each cohort, and
the absolute difference between the ranks is upper bounded by 1. Larger
values of $\eta_1$ and small values of $\eta_2$ correspond to a larger
excitation parameter, with pairs more likely to continue fighting.
- $\eta_3$ is related to the state transition probabilities. As the rankings
are between zero and 1, larger values of $\eta_3$ correspond to a higher 
likelihood of being in the active state, particularly if one mice has a high or
low latent ranking.

# Are gamma/zeta associated with rankings?

```{r same plot from previous}
for(current_cohort in 1:10) {
  #cat("Cohort ", current_cohort,"\n",sep="")
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

  mean_latent_rank <- apply(sim_cohort_mmhp$f,2,mean)

  out_degree <- apply(sim_cohort_mmhp$gamma,2,mean)
  in_degree <- apply(sim_cohort_mmhp$zeta,2,mean)

  degs <- tibble(expert = expert_rank_10[[current_cohort]],
                  latent = mean_latent_rank,#[expert],
                 out_deg = out_degree,#[expert],
                 in_deg = in_degree)#[expert])

  p <- ggplot(degs,aes(latent,out_deg)) + geom_point() + 
    #scale_y_continuous(breaks = c(12:1), trans = "reverse") + 
    ggtitle(paste("Out Degree vs Latent Cohort ", current_cohort,sep="")) + 
    ylab("Out Degree (Gamma)") + xlab("Latent Rank")
  #print(p)
  q <- ggplot(degs,aes(latent,in_deg)) + geom_point() +
    ggtitle(paste("In Degree vs Latent Cohort ",current_cohort,sep="")) +
    ylab("In Degree (Zeta)") + xlab("Latent Rank")
  #print(q)
  grid.arrange(p,q, nrow = 1)
}

```

There is a weak relationship between the out degree 
(baseline rate of starting a fight) and the latent rank,
with an even weaker relationship between the in degree
(baseline rate of being fought) and the latent rank.

<!-- # Shuffling the data -->

### 2020-08-26 output_scripts/aug_updates.Rmd
start adding updates for James

@@
 library(ggplot2)
-library(gridExtra)
 source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
@@
 
-# Do closer ranked mice fight more?
+# Exploring eta parameters
 
-To see if closer ranked mice fight more, we would like to look
-at the conditional intensity as a function of the absolute difference in the
-latent ranks.
-
-There are two components to this. Whether a pair of mice will be in the
-active state (where fighting is more likely), and, in this active state,
-the value of the excitation parameter (which controls the likelihood of
-fighting again following a previous fight).
-
-```{r difference in ranking for all cohorts}
-for(current_cohort in 1:10) {
-  load(paste(data_path,cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
-             ".RData",sep=''))
-  # have 1000 draws here
-  eta_1_mean <- mean(sim_cohort_mmhp$eta_1)
-  eta_2_mean <- mean(sim_cohort_mmhp$eta_2)
-  eta_3_mean <- mean(sim_cohort_mmhp$eta_3)
-
-  f_1 <- seq(from = 0.01, to = 0.99, by = 0.01)
-  f_2 <- seq(from = 0.01, to = 0.99, by = 0.01)
-
-  possible_vals <- expand_grid(f_1,f_2)
-
-  excitation <- map2_dbl(possible_vals$f_1, possible_vals$f_2,function(.x,.y) 
-      eta_1_mean*.x*.y*exp(-eta_2_mean*abs(.x-.y)) )
-
-  prop_active <- map2_dbl(possible_vals$f_1, possible_vals$f_2,function(.x,.y) 
-      1/(1+exp(-eta_3_mean*(.x-.y)))
-     )
-
-  possible_vals$excit <- excitation
-  possible_vals$active <- prop_active
-
-  plot_alpha <- possible_vals %>% ggplot(aes(f_1,f_2)) + 
-    geom_raster(aes(fill=excit)) + 
-    scale_fill_continuous(name = "alpha",low = "red", high = "blue") + 
-    ggtitle(paste("Cohort ", current_cohort,
-                  " excitation parameter",sep=""))
-
-  plot_active <- possible_vals %>% ggplot(aes(f_1,f_2)) + 
-    geom_raster(aes(fill=active)) + 
-    scale_fill_continuous(name = "Prop. active",low = "red", high = "blue") + 
-    ggtitle(paste("Cohort ", current_cohort,
-                  " proportion of time active",sep=""))
-  print(plot_alpha)
-  print(plot_active)
-}
-```
-
-```{r intensity as function of abs diff in ranks, include=FALSE}
-current_cohort <- 1
-load(paste(data_path,cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
-             ".RData",sep=''))
-  # have 1000 draws here
-eta_1_mean <- mean(sim_cohort_mmhp$eta_1)
-eta_2_mean <- mean(sim_cohort_mmhp$eta_2)
-eta_3_mean <- mean(sim_cohort_mmhp$eta_3)
-
-f_1 <- seq(from = 0.01, to = 0.99, by = 0.01)
-f_2 <- seq(from = 0.01, to = 0.99, by = 0.01)
-
-possible_vals <- expand_grid(f_1,f_2)
-
-excitation <- map2_dbl(possible_vals$f_1, possible_vals$f_2,function(.x,.y) 
-    eta_1_mean*.x*.y*exp(-eta_2_mean*abs(.x-.y)) )
-
-prop_active <- map2_dbl(possible_vals$f_1, possible_vals$f_2,function(.x,.y) 
-    1/(1+exp(-eta_3_mean*(.x-.y)))
-   )
-
-possible_vals$excit <- excitation
-possible_vals$active <- prop_active
-
-possible_vals %>% mutate(abs_diff = abs(f_1-f_2)) %>%
-  ggplot(aes(abs_diff,excit)) + geom_point()
-
-possible_vals %>% mutate(abs_diff = abs(f_1-f_2)) %>%
-  ggplot(aes(abs_diff,prop_active)) + geom_point() +
-  xlab("Absolute Difference in Ranks") +
-  ylab("Proportion of Active Time")
-
-# plot_alpha <- possible_vals %>% ggplot(aes(f_1,f_2)) + 
-#   geom_raster(aes(fill=excit)) + 
-#   scale_fill_continuous(name = "alpha",low = "red", high = "blue") + 
-#   ggtitle(paste("Cohort ", current_cohort,sep=""))
-```
-
-Based on these plots, pairs of mice are more likely to be in the active state
-when the instigating mouse is ranked significantly higher than the mouse it
-fights. However, in the active state, the excitation parameter (and
-the likelihood of continuing to fight) is higher 
-when both mice are higher ranked. This is relatively consistent across each of
-the cohorts here.
-
-# Exploring $\eta$ parameters
-
-The parameters $\eta_1,\eta_2,\eta_3$ in this model are related to the
-probability of being in the active state and the excitation parameter 
-when in this active state. We can first look at the posterior distribution
-of these parameters and their posterior means.
-
-```{r posterior pairs for eta, message=FALSE}
+```{r}
 for(current_cohort in 1:10) {
@@
                 eta_3 = sim_cohort_mmhp$eta_3)
-  print("Posterior Mean of eta parameters")
-  print( eta %>% map_dbl(mean) )
-
   p <- GGally::ggpairs(eta) + 
@@
 $$
-\lambda^{i,j}(t) = \gamma_i + \zeta_j +(\lambda_1-\gamma_i-\zeta_j)Z^{i,j}(t) 
-$$
-
-$$
-+
+\lambda^{i,j}(t) = \gamma_i + \zeta_j +(\lambda_1-\gamma_i-\zeta_j)Z^{i,j}(t) +
 \eta_1 f_i f_j 
@@
 $$
-with
+where 
 $$
@@
 So here, these parameters correspond to:
-
-- $\eta_1$ excitation as a function of the product of the latent ranks.
-- $\eta_2$ is related to the absolute difference between the ranks of the mice. 
-The posterior mean for this parameter is less than 1 for each cohort, and
-the absolute difference between the ranks is upper bounded by 1. Larger
-values of $\eta_1$ and small values of $\eta_2$ correspond to a larger
-excitation parameter, with pairs more likely to continue fighting.
-- $\eta_3$ is related to the state transition probabilities. As the rankings
-are between zero and 1, larger values of $\eta_3$ correspond to a higher 
-likelihood of being in the active state, particularly if one mice has a high or
-low latent ranking.
+- $\eta_1$
 
@@
 
-```{r same plot from previous}
-for(current_cohort in 1:10) {
-  #cat("Cohort ", current_cohort,"\n",sep="")
-  load(paste(data_path,cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
-             ".RData",sep=''))
-
-  mean_latent_rank <- apply(sim_cohort_mmhp$f,2,mean)
-
-  out_degree <- apply(sim_cohort_mmhp$gamma,2,mean)
-  in_degree <- apply(sim_cohort_mmhp$zeta,2,mean)
-
-  degs <- tibble(expert = expert_rank_10[[current_cohort]],
-                  latent = mean_latent_rank,#[expert],
-                 out_deg = out_degree,#[expert],
-                 in_deg = in_degree)#[expert])
-
-  p <- ggplot(degs,aes(latent,out_deg)) + geom_point() + 
-    #scale_y_continuous(breaks = c(12:1), trans = "reverse") + 
-    ggtitle(paste("Out Degree vs Latent Cohort ", current_cohort,sep="")) + 
-    ylab("Out Degree (Gamma)") + xlab("Latent Rank")
-  #print(p)
-  q <- ggplot(degs,aes(latent,in_deg)) + geom_point() +
-    ggtitle(paste("In Degree vs Latent Cohort ",current_cohort,sep="")) +
-    ylab("In Degree (Zeta)") + xlab("Latent Rank")
-  #print(q)
-  grid.arrange(p,q, nrow = 1)
-}
-
-```
-
-There is a weak relationship between the out degree 
-(baseline rate of starting a fight) and the latent rank,
-with an even weaker relationship between the in degree
-(baseline rate of being fought) and the latent rank.
-
-<!-- # Shuffling the data -->
+# Do closer ranked mice fight more?

### 2020-08-31 output_scripts/aug_updates.Rmd
code to permute the cohorts and fit cmmhp and equivalent in rmd

--- 2020-08-26 output_scripts/aug_updates.Rmd
@@
 
-<!-- # Shuffling the data -->
+# Shuffling the data
+
+Another component of interest is ensuring that there is some 
+structure in this model that would not be captured by 
+random data. To see this, we can simply shuffle the nodes
+involved in fights and look at the corresponding model fits,
+which should not contain any information.
+
+```{r shuffle cohort and stan fit, slow locally}
+current_cohort <- 1
+
+print(paste("Cohort",current_cohort))
+###
+stan_input_lst <- prepareData_permute_Stan(current_cohort)
+### get the corresponding expert rank
+permuted_data <- stan_input_lst$permuted_data
+
+expert_rank_10_curr <- expertRankHierarchy(permuted_data)
+stan_input_lst$alpha_id <- expert_rank_10_curr[1]
+stan_input_lst$delta_1 <- rep(0.5,stan_input_lst$N_til)
+
+fit_cohort_mmhp <- stan("../lib/model3_current.stan", 
+                        ## this will need to be updated
+                        data = stan_input_lst,
+                        warmup = 10, iter = 200, chains = 4, thin=4,
+                        control=list(adapt_delta=0.9,max_treedepth=15))
+
+```

### 2020-08-31 lib/permute_data.R

@@ -1,0 +1,79 @@
+prepareData_permute_Stan <- function(current_cohort) {
+  ### need to permute full_data[[cohort_names[current_cohort]]]
+  ### and then go from there
+  
+  permuted <- permute_raw(current_cohort)
+  clean_data <- cleanData(permuted)
+  return_df <- cleanObservationPeriod(current_cohort, clean_data)
+  
+  unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% dplyr::summarize(count=n(), observe=list(observe.id))
+  unique_observe_win <- unique(return_df[,c("observe.id","observe.time","observe.start","observe.end")])
+  
+  time_array <- array(0,dim=c(nrow(unique_pairs_df),max(return_df$observe.id),max(unlist(lapply(return_df$event.times,length)))+1))
+  event_array <- array(0,dim=c(nrow(unique_pairs_df),max(return_df$observe.id),max(unlist(lapply(return_df$event.times,length)))))
+  count_matrix <- matrix(0,nrow=nrow(unique_pairs_df),ncol=max(return_df$observe.id))
+  delta_window <- c(0,unique_observe_win$observe.start[-1]-unique_observe_win$observe.end[-nrow(unique_observe_win)])
+  finishing_time <- matrix(0,nrow=nrow(unique_pairs_df),ncol=max(return_df$observe.id))
+  max_interevent <- rep(0,nrow(unique_pairs_df))
+  
+  for(pair in 1:nrow(unique_pairs_df)){
+    current_initiator <- as.numeric(unique_pairs_df[pair,"initiator"])
+    current_recipient <- as.numeric(unique_pairs_df[pair,"recipient"])
+    current_window_vec <- unique_pairs_df$observe[[pair]]
+    for(win in 1:max(return_df$observe.id)){
+      row_indicator <- return_df$initiator==current_initiator&return_df$recipient==current_recipient&return_df$observe.id==win
+      if(sum(row_indicator)==0){ # no events during observation window
+        count_matrix[pair,win] <- 0
+        time_array[pair,win,1] <- unique_observe_win[unique_observe_win$observe.id==win,"observe.time"]
+        max_interevent[pair] <- max(max_interevent[pair],time_array[pair,win,1])
+      }else{
+        time_vec <- return_df[row_indicator,"event.times"][[1]]
+        observe_period <- unique_observe_win[unique_observe_win$observe.id==win,"observe.time"]
[…]

### 2020-08-31 output_scripts/aug_updates.Rmd
update for cohorts who have a mouse with no starting or being fought

@@
 ```{r shuffle cohort and stan fit, slow locally}
-current_cohort <- 1
+current_cohort <- 8
 
@@
 
-fit_cohort_mmhp <- stan("../lib/model3_current.stan", 
-                        ## this will need to be updated
-                        data = stan_input_lst,
-                        warmup = 10, iter = 200, chains = 4, thin=4,
-                        control=list(adapt_delta=0.9,max_treedepth=15))
+# fit_cohort_mmhp <- stan("../lib/model3_current.stan", 
+#                         ## this will need to be updated
+#                         data = stan_input_lst,
+#                         warmup = 10, iter = 200, chains = 4, thin=4,
+#                         control=list(adapt_delta=0.9,max_treedepth=15))
 

### 2020-08-31 lib/permute_data.R

@@ -52,6 +52,10 @@ prepareData_permute_Stan <- function(current_cohort) {
 
 permute_raw <- function(current_cohort) {
   orig_raw <- full_data[[cohort_names[current_cohort]]]
+  levels(orig_raw$Actor) <- base::union(levels(orig_raw$Actor),
+                                        levels(orig_raw$Recipient))
+  levels(orig_raw$Recipient) <- base::union(levels(orig_raw$Actor),
+                                            levels(orig_raw$Recipient))
   # then just permute the actor and recipient of these,
   # excluding the start and end rows
   start_rows <- which(orig_raw$Actor == "Start")  

### 2020-09-03 output_scripts/aug_updates.Rmd
update prepare data to allow for permutation. change permute function to take data rather than cohort.

@@
 
-```{r shuffle cohort and stan fit, slow locally}
-current_cohort <- 8
+```{r permute the raw data, include=FALSE, eval=FALSE}
+# first want to check if permuting the raw data is doing what it should
+current_cohort <- 1
+
+orig_data <- full_data[[cohort_names[current_cohort]]]
+perm_data <- permute_raw(orig_raw = orig_data)
+
+dim(orig_data)
+dim(perm_data)
+summary(orig_data$Actor)
+summary(perm_data$Actor)
+## these look more regular, all equally likely to be an actor. good so far
+
+## then clean these and compare
+orig_clean <- cleanData(raw_data = orig_data,cut_off = 1)
+perm_clean <- cleanData(raw_data = perm_data,cut_off = 1)
+
+sum(orig_clean$N_count)
+sum(perm_clean$N_count)
+## how do these differ?, should both have 1077. unless identical times and mice?
+## rows 107,108 have same mice fighting different at identical time. that would cause it?
+## then cleanObservation Period on each of these
+orig_period <- cleanObservationPeriod(current_cohort = 1, raw_df = orig_data,
+                                      clean_data = orig_clean)
+perm_period <- cleanObservationPeriod(current_cohort = 1,raw_df = perm_data,
+                                      clean_data = perm_clean)
+
+sum(orig_period$no.events) # surely this should match with above?
+sum(perm_period$no.events)
+
+## these seem ok anyway
+```
+
+```{r further checking permutation}
+orig_stan_data <- prepareDataStan(current_cohort = 1)
+permute_stan_data <- prepareData_permute_Stan(current_cohort = 1)
+# now all pairs have an interaction
+
+```
+
+```{r shuffle cohort and stan fit, slow locally, include=FALSE,eval=FALSE}
+source(paste(func_dir,'permute_data.R',sep = ""))
+
+current_cohort <- 1
 
@@
 ###
-stan_input_lst <- prepareData_permute_Stan(current_cohort)
+stan_input_lst <- prepareDataStan(current_cohort)
+stan_input_lst_permute <- prepareData_permute_Stan(current_cohort)
 ### get the corresponding expert rank
-permuted_data <- stan_input_lst$permuted_data
+permuted_data <- stan_input_lst_permute$permuted_data
 
@@
 stan_input_lst$delta_1 <- rep(0.5,stan_input_lst$N_til)
+
+sum(stan_input_lst$Nm - stan_input_lst_permute$Nm) 
+# these should be the same size surely?
+
+# seems these are identical... good!
 
@@
 ```
+
+```{r}
+real_cleaned <- cleanData(full_data[[cohort_names[current_cohort]]])
+
+permuted <- permute_raw(current_cohort)
+permuted_cleaned <- cleanData(permuted)
+
+permuted_cleaned$N_count - real_cleaned$N_count
+# these look different which is good
+
+return_df <- cleanObservationPeriod(current_cohort,
+                                    full_data[[cohort_names[current_cohort]]],
+                                    real_cleaned)
+
+per_return_df <- cleanObservationPeriod(current_cohort,permuted,permuted_cleaned)
+
+return_df$initiator - per_return_df$initiator
+# so this is the issue then possibly
+
+```
+
+```{r compare fits from permuted and true data}
+current_cohort <- 4
+
+## load true model fit
+load(paste(data_path,cohort_names[current_cohort],
+           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+           ".RData",sep=''))
+
+true_fit <- fit_cohort_mmhp
+true_post <- sim_cohort_mmhp
+
+## load permuted model fit
+load(paste(data_path,cohort_names[current_cohort],
+           "/permute_cohort_mmhp_stan_result_",cohort_names[current_cohort],
+           ".RData",sep=''))
+
+perm_fit <- fit_cohort_mmhp
+perm_post <- sim_cohort_mmhp
+
+mice_covars <- tibble(true_rank = apply(true_post$f,2,mean),
+       perm_rank = apply(perm_post$f,2,mean),
+       true_gam = apply(true_post$gamma,2,mean),
+       perm_gam = apply(perm_post$gamma,2,mean),
+       true_zeta = apply(true_post$zeta,2,mean),
+       perm_zeta = apply(perm_post$zeta,2,mean))
+
+mice_covars %>% ggplot(aes(true_rank,perm_rank)) + geom_point()
+
+mice_covars %>% ggplot(aes(true_gam,perm_gam)) + geom_point()
+
+mice_covars %>% ggplot(aes(true_zeta,perm_zeta)) + geom_point()
+
+```

### 2020-09-03 lib/cleanData.R

@@ -102,7 +102,7 @@ cleanData <- function(raw_data, cut_off = 3, N = 12){
 ## Output: return_df | for each pair each observation period, record the event times
 ############################################################################
 
-cleanObservationPeriod <- function(current_cohort, raw_df, mice_number=12){
+cleanObservationPeriod <- function(current_cohort, raw_df, clean_data, mice_number=12){
   # raw_df <- full_data[[cohort_names[current_cohort]]]
   # pass this as argument instead, so it can actually be modified
   return_df <- data.frame(day = numeric(),

### 2020-09-03 lib/permute_data.R

@@ -1,10 +1,10 @@
 prepareData_permute_Stan <- function(current_cohort) {
   ### need to permute full_data[[cohort_names[current_cohort]]]
   ### and then go from there
-  
-  permuted <- permute_raw(current_cohort)
-  clean_data <- cleanData(permuted)
-  return_df <- cleanObservationPeriod(current_cohort, clean_data)
+  orig <- full_data[[cohort_names[current_cohort]]]
+  permuted <- permute_raw(orig)
+  clean_data_perm <- cleanData(permuted)
+  return_df <- cleanObservationPeriod(current_cohort, permuted, clean_data_perm)
   
   unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% dplyr::summarize(count=n(), observe=list(observe.id))
   unique_observe_win <- unique(return_df[,c("observe.id","observe.time","observe.start","observe.end")])
@@ -50,8 +50,8 @@ prepareData_permute_Stan <- function(current_cohort) {
 }
 
 
-permute_raw <- function(current_cohort) {
-  orig_raw <- full_data[[cohort_names[current_cohort]]]
+permute_raw <- function(orig_raw) {
+  #orig_raw <- full_data[[cohort_names[current_cohort]]]
   levels(orig_raw$Actor) <- base::union(levels(orig_raw$Actor),
                                         levels(orig_raw$Recipient))
   levels(orig_raw$Recipient) <- base::union(levels(orig_raw$Actor),

### 2020-09-03 lib/prepareDataStan.R

@@ -14,7 +14,7 @@
 ############################################################################
 prepareDataStan <- function(current_cohort){
   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-  return_df <- cleanObservationPeriod(current_cohort, full_data[[cohort_names[current_cohort]]])
+  return_df <- cleanObservationPeriod(current_cohort, full_data[[cohort_names[current_cohort]]], clean_data)
   
   unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% dplyr::summarize(count=n(), observe=list(observe.id))
   unique_observe_win <- unique(return_df[,c("observe.id","observe.time","observe.start","observe.end")])

### 2020-09-03 output_scripts/aug_updates.Rmd
removing some old material

@@
 
-```{r further checking permutation}
+```{r further checking permutation, include=FALSE, eval=FALSE}
 orig_stan_data <- prepareDataStan(current_cohort = 1)
@@
 
-```{r}
-real_cleaned <- cleanData(full_data[[cohort_names[current_cohort]]])
-
-permuted <- permute_raw(current_cohort)
-permuted_cleaned <- cleanData(permuted)
-
-permuted_cleaned$N_count - real_cleaned$N_count
-# these look different which is good
-
-return_df <- cleanObservationPeriod(current_cohort,
-                                    full_data[[cohort_names[current_cohort]]],
-                                    real_cleaned)
-
-per_return_df <- cleanObservationPeriod(current_cohort,permuted,permuted_cleaned)
-
-return_df$initiator - per_return_df$initiator
-# so this is the issue then possibly
-
-```
+Then we want to check these fits and compare them.
 

### 2020-09-14 output_scripts/aug_updates.Rmd
analysis for james

@@
 ```{r compare fits from permuted and true data}
-current_cohort <- 4
+current_cohort <- 1
 
+for(current_cohort in 1:10){
   ## load true model fit
@@
 
-mice_covars %>% ggplot(aes(true_rank,perm_rank)) + geom_point()
+  p <- mice_covars %>% ggplot(aes(true_rank,perm_rank)) + geom_point() +
+    ggtitle(paste("Cohort ",current_cohort,sep = ""))
 
-mice_covars %>% ggplot(aes(true_gam,perm_gam)) + geom_point()
+  q <- mice_covars %>% ggplot(aes(true_gam,perm_gam)) + geom_point()
 
-mice_covars %>% ggplot(aes(true_zeta,perm_zeta)) + geom_point()
+  r <- mice_covars %>% ggplot(aes(true_zeta,perm_zeta)) + geom_point()
+
+  grid.arrange(p,q,r, nrow = 1)
+}
 
 ```
+There does appear to be little to no structure in the estimated parameters 
+after this permutation. For example, all `gamma` and `zeta` parameters display 
+similar values, compared to the range seen in the original data. Similarly,
+there is little to no correlation in the rankings 
+obtained from the true events and the permuted events.

### 2020-09-22 output_scripts/Paper_Plots.Rmd
fix fig4b

@@
 ```{r prepare data for 4b,cache=TRUE}
-plot.s <- 7#9
+plot.s <- 9#7#9
 plot.i <- 4
@@
 #########
-model1_par_est <- list(lambda0=mean(sim_model3_stan_sim1[[plot.s]]$lambda0[1001:2000]),
+model1_par_est <- list(lambda0 =
+                         mean(sim_model3_stan_sim1[[plot.s]]$lambda0[1001:2000]),
                        eta_1=mean(sim_model3_stan_sim1[[plot.s]]$eta_1[1001:2000]),
@@
                        f=apply(sim_model3_stan_sim1[[plot.s]]$f[1001:2000,],2,mean))
-lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0=model1_par_est$lambda0,
-                                     alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
+lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
+                                                   model1_par_est$lambda0,
+                                    alpha =
+                                      model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                     model1_par_est$f[plot.j],
@@
 #############
-model2_par_est <- list(gamma=apply(sim_model3_stan_sim2[[plot.s]]$gamma[1001:2000,],2,mean),
-                       zeta=apply(sim_model3_stan_sim2[[plot.s]]$zeta[1001:2000,],2,mean),
+model2_par_est <- list(gamma=apply(sim_model3_stan_sim2[[plot.s]]$gamma[1001:2000,],
+                                   2,mean),
+                    zeta = 
+                      apply(sim_model3_stan_sim2[[plot.s]]$zeta[1001:2000,],2,mean),
                        eta_1=mean(sim_model3_stan_sim2[[plot.s]]$eta_1[1001:2000]),
@@
 y.ub <- c(20,20,20)#c(130,72,31)
+x_events <- 135#150
 #model_colors <- c("steelblue", "goldenrod2", "firebrick2")
@@
 layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
-my.xlim <- 200#130
-my.long.x <- 205#134.5
-legend.x <- c(135,135,135)
+my.xlim <- 140#160#200#130
+my.long.x <- 140#205#134.5
+legend.x <- c(50,50,50)#c(135,135,135)
 legend.y <- #c(34,32,32)
@@
 ### hiding these for now ###
-polygon(c(0,lambda.true$time.vec,200),
+polygon(c(0,lambda.true$time.vec,x_events),#200
         c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,200),
+polygon(c(0,lambda.true$time.vec,x_events),#200
         c(0,delta.positive,0),col=positive.col,border=NA)
@@
                          events=test.mmhp$tau,
-                         color=add.alpha(model_colors[2], alpha=line.alpha[2]),line.width=line.wdth[2])
+                         color=add.alpha(model_colors[2],
+                                         alpha=line.alpha[2]),
+                         line.width=line.wdth[2])
 legend(legend.x[2],legend.y[2],"C-DCHP",
@@
 
-legend(10,legend.y[2],c("State 1/0 events","State change point"),
+legend(10,legend.y[2],c("State 0/1 events","State change point"),
        col = c(NA,"red"),
@@
 delta.negative[delta.negative>0] <- 0
-polygon(c(0,lambda.true$time.vec,200), c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,200), c(0,delta.positive,0),col=positive.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events), #200
+        c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events), #200
+        c(0,delta.positive,0),col=positive.col,border=NA)
 # segments(0,0,my.xlim,0,col="gray45")
@@
 ### hiding these for now
-polygon(c(0,lambda.true$time.vec,200), c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,200), c(0,delta.positive,0),col=positive.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events), # 200 
+        c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events), # 200 
+        c(0,delta.positive,0),col=positive.col,border=NA)
 # segments(0,0,my.xlim,0,col="gray45")
@@
 
-<!-- Not completed. This would need the rankings to be -->
-<!-- rerun for all cohorts. -->
-
 ```{r fig-6b-overall-rank-correlation}
@@
 
-<!-- Here is where I need to be a bit more careful about using the correct fits. -->
-<!-- Currently using all from Jing's saved output. -->
-
-<!-- In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices. -->
-
 ```{r fig-7-prMatrix-Cohort5, fig.height=7}
@@
   ylab("Frobenius norm of error") +
-  ylim(0, 150) +
+  ylim(0, 150) + # aren't infinite but >150 and <200
   NULL

### 2020-10-12 output_scripts/Paper_Plots.Rmd
start putting together a new plot for fig 3b

@@
       param_mean <- list(lambda0=mean(sim_cohort_hp$lambda0),
-                         alpha=model1_fn$alpha.fun(f_est[i],f_est[j],
-                                                   eta1_mean,eta2_mean,eta3_mean),
+                         alpha=model1_fn$alpha.fun(f_est[i],
+                                                   f_est[j],
+                                                   eta1_mean,
+                                                   eta2_mean,
+                                                   eta3_mean),
                          beta=mean(sim_cohort_hp$beta))
@@
         current_event_time <- return_df[return_df$initiator==i&
-                                          return_df$recipient==j&
+                                          return_df$recipient == j &
                             return_df$observe.id==cur_win,"event.times"][[1]]
@@
                             return_df$observe.id==cur_win,"observe.time"]
-        Lambda_vec <- uniHawkesCompensator(object=param_mean, events=c(current_event_time,current_obs_time))
+        Lambda_vec <- uniHawkesCompensator(object = param_mean,
+                              events = c(current_event_time,
+                                         current_obs_time))
         all_Lambda <- c(all_Lambda,Lambda_vec)
@@
       if(length(all_Lambda)>0){
-        ks.stat.matrix[i,j] <-  ks.test(all_Lambda,"pexp",rate=1/mean(all_Lambda))$statistic
+        ks.stat.matrix[i,j] <-  ks.test(all_Lambda,"pexp",
+                                        rate = 1/mean(all_Lambda))$statistic
         Lambda_matrix[i,j][[1]] <- all_Lambda
@@
     mgp = c(0, .2, 0))
-layout(cbind(matrix(data=c(1:(12*12)), nrow=12, ncol=12, byrow = TRUE),rep(12*12+1,12)), 
+layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
+                    byrow = TRUE),rep(12*12+1,12)), 
        widths=c(rep(1,12),2), heights=rep(1,12))
@@
     if(ks.stat.matrix[i,j]==0){
-      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", axes = FALSE, frame=TRUE)
-      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], border = 0, col = 'white')
+      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
+           axes = FALSE, frame=TRUE)
+      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
+           border = 0, col = 'white')
     }else{
@@
             ylab="",xlab="",axes = FALSE, frame=TRUE)
-      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
+      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], 
+           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
             ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
-      plot(ecdf(Lambda.test), add=TRUE, do.points=FALSE, verticals=TRUE,col="red", lwd=2)
+      plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
+           verticals = TRUE, col = "red", lwd = 2)
     }
@@
       at=1/14*c(1:12)-1/22)
-mtext(text=expert_rank_10[[current_cohort]], side=2, line=0.5, outer=TRUE, cex=1.8,
-      at=1/12*c(12:1)-1/20, las=2)
-mtext(text="(b)", side=3, line=1.4, outer=TRUE, cex=2.2,
+mtext(text = expert_rank_10[[current_cohort]],
+      side = 2, line = 0.5, outer = TRUE, cex = 1.8,
+      at =1/12*c(12:1)-1/20, las = 2)
+mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE,
+      cex = 2.2,
       at=0.45, font=2)
@@
 # social matrix plot
-latent_social_matrix <- gamma_mean%*%t(rep(1,mice_number))+rep(1,mice_number)%*%t(zeta_mean)
-
-# png(paste(plot_path,"/lambda0_",cohort_names[current_cohort],".png",sep=''),
+latent_social_matrix <- gamma_mean %*%
+  t(rep(1,mice_number)) + rep(1,mice_number) %*% t(zeta_mean)
+
+# png(paste(plot_path,"/lambda0_",
+# cohort_names[current_cohort],".png",sep=''),
 #     width=400, height=300)
-matrixPlotParameter(latent_social_matrix[rev(expert_rank_10[[current_cohort]]),
+matrixPlotParameter(latent_social_matrix[
+  rev(expert_rank_10[[current_cohort]]),
                                          expert_rank_10[[current_cohort]]],
                     xLabels=expert_rank_10[[current_cohort]],
-                    yLabels=rev(expert_rank_10[[current_cohort]]),title="(a)")
+                    yLabels=rev(expert_rank_10[[current_cohort]]),
+                    title = "(a)" )
 # mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
@@
 
+# Redone Figure 3
+
+As discussed, it would be interesting to redo figure 3b
+to show the lack of fit in model 2 for one specific pair. This can be somewhat
+extracted from the diagnostics file.
+
+We actually want the empirical CDF plot here.
+
+```{r fig_3b_update, fig.height=7}
+# 2 -> 11 might be good here
+current_cohort <- 5
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+            observe=list(observe.id),
+            observe.length=list(observe.time),
+            no.events=list(no.events)) 
+top_pairs <- unique_pairs_df %>% arrange(desc(count))
+
+best_i <- top_pairs$initiator[8]
+best_j <- top_pairs$recipient[8]
+
+current_i <- best_i #8
+current_j <- best_j #2
+
+### then plots ####
+# par(mfrow = c(1, 2), oma = c(1, 1, 1, 1),
+#      mar = c(2, 3, 2, 1), mgp = c(0.8,0,0))
+# layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
+anno.cex <- 1.3
+title.cex <- 2.2
+title.line <- 0.5
+y.upper <- 20
+#### then the corresponding QQ plot ####
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
+
+p <- ppoints(length(Lambda.dc_hawkes.test))
+# 100 equally spaced points on (0,1), excluding endpoints
+q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE)
+# percentiles of the sample distribution
+plot(qexp(p),q,
+     xlab="",ylab="",xaxt="n",yaxt="n",
+     pch=1, cex=1, col=viridis::viridis(1), ylim=c(0,1), xlim=c(0,4.5))
+mtext(side = 1, text = "Theoretical", line=1.6, cex=anno.cex)
+mtext(side = 2, text = "Empirical", line = 1.2, cex = anno.cex)
+mtext(side = 3, text = "(b)", line = 0.8, cex = 1.6, font = 2)
+# Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1)
+# Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:1),cex.axis=1,lwd=0,lwd.ticks=1)
+qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
+
+### Empirical CDF ####
+
+plot(ecdf(Lambda.dc_hawkes.test), do.points = FALSE,
+     verticals = TRUE, col = viridis::viridis(1), lwd = 2, 
+     xlab = "", ylab = "", xaxt = "n", yaxt = "n",
+     main = "", col.01line = NULL)
+curve(pexp(x,1/mean(Lambda.dc_hawkes.test)),
+      min(Lambda.dc_hawkes.test), max(Lambda.dc_hawkes.test),
+      ylab = "", xlab = "", axes = FALSE,
+      add = TRUE, lwd = 2)
+
+```
+
+```{r repeat entire fig2b for model 2}
+current_cohort <- 5
+
+load(paste(data_path,cohort_names[current_cohort],
+             "/real_diag_four_models_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+load(paste(data_path,cohort_names[current_cohort],
+           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
+           ".RData",sep=''))
+eta1_mean <- mean(sim_cohort_dchp$eta_1)
+eta2_mean <- mean(sim_cohort_dchp$eta_2)
+eta3_mean <- mean(sim_cohort_dchp$eta_3)
+f_est <- apply(sim_cohort_dchp$f,2,mean)
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort, clean_data)
+unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
+  dplyr::summarize(count=n(),
+                   observe=list(observe.id),
+                   observe.length=list(observe.time),
+                   no.events=list(no.events))
+unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+
+ks.stat.matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
+n_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
+Lambda_matrix <- matrix(list(),nrow=mice_number,ncol=mice_number)
+for(k in 1:mice_number){
+  for(l in c(1:mice_number)[-k]){
+    i<-expert_rank_10[[current_cohort]][k]
+    j<-expert_rank_10[[current_cohort]][l]
+    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
+    if(length(pair)>0){
+      param_mean <- list(lambda0=mean(sim_cohort_dchp$lambda0[,pair]),
+                         alpha=model1_fn$alpha.fun(f_est[i],
+                                                   f_est[j],
+                                                   eta1_mean,
+                                                   eta2_mean,
+                                                   eta3_mean),
+                         beta=mean(sim_cohort_dchp$beta))
+      current_window_vec <- unique_pairs_df$observe[[pair]]
+      all_Lambda <- numeric(0)
+      for(cur in c(1:length(current_window_vec))){ ## check length > 2
+        cur_win <- current_window_vec[cur]
+        current_event_time <- return_df[return_df$initiator==i&
+                                          return_df$recipient == j &
+                            return_df$observe.id==cur_win,"event.times"][[1]]
+        current_obs_time <- return_df[return_df$initiator==i&
+                                        return_df$recipient==j&
+                            return_df$observe.id==cur_win,"observe.time"]
+        Lambda_vec <- uniHawkesCompensator(object = param_mean,
+                              events = c(current_event_time,
+                                         current_obs_time))
+        all_Lambda <- c(all_Lambda,Lambda_vec)
+        n_matrix[i,j] <- n_matrix[i,j] + length(current_event_time)
+      }
+      if(length(all_Lambda)>0){
+        ks.stat.matrix[i,j] <-  ks.test(all_Lambda,"pexp",
+                                        rate = 1/mean(all_Lambda))$statistic
+        Lambda_matrix[i,j][[1]] <- all_Lambda
+      }
+    }
+  }
+}
+
+# -------------- KS plot (stat)
+col.vec <- cRamp(as.vector(ks.stat.matrix))
+## need to do some sort of transformation between these here
+vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
+#order(as.vector(ks.stat.matrix),method = "")
+
+values <- as.vector(ks.stat.matrix)
+sorted_vals <- sort(ks.stat.matrix)
+#match(values,sorted_vals)
+col.vec.vir <- vir_cols[match(values,sorted_vals)]
+
+####
+par(oma = c(6,4,4,1), mar=rep(0,4),
+    mgp = c(0, .2, 0))
+layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
+                    byrow = TRUE),rep(12*12+1,12)), 
+       widths=c(rep(1,12),2), heights=rep(1,12))
+for(i in expert_rank_10[[current_cohort]]){
+  for(j in expert_rank_10[[current_cohort]]){
+    if(ks.stat.matrix[i,j]==0){
+      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
+           axes = FALSE, frame=TRUE)
+      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
+           border = 0, col = 'white')
+    }else{
+      Lambda.test <- Lambda_matrix[i,j][[1]]
+      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
+            ylab="",xlab="",axes = FALSE, frame=TRUE)
+      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], 
+           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
+      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
+            ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
+      plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
+           verticals = TRUE, col = "red", lwd = 2)
+    }
+  }
+}
+par(mar = c(0,2,0,3),mgp=c(0,0.8,0))
+
+col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)),
+                            length.out = 100),
+                col.vec = viridis(100))
+
+temp <- cLegend(as.vector(ks.stat.matrix))
+
+image(1, col_obj$x.vec,
+      matrix(data=col_obj$x.vec, 
+             ncol=length(col_obj$x.vec),nrow=1),
+      col=col_obj$col.vec,
+      xlab="",ylab="",axes=FALSE)
+axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1,
+     cex.axis=2.4)
+
+mtext(text=expert_rank_10[[current_cohort]], side=1,
+      line=1.8, outer=TRUE, cex=1.8,
+      at=1/14*c(1:12)-1/22)
+mtext(text = expert_rank_10[[current_cohort]],
+      side = 2, line = 0.5, outer = TRUE, cex = 1.8,
+      at =1/12*c(12:1)-1/20, las = 2)
+mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE,
+      cex = 2.2,
+      at=0.45, font=2)
+
+```
+
+This is good because it shows the most active animal, shows that individual
+out rate too large for this interaction. Just need to make this more
+like the plots in 2b.
+
 # Figure 4:
@@
   for(s in c(1:2000)){
-    temp_result <- cor.test(sim_dsnl$x[s,t,], cur_real_rank, method = "spearman")
+    temp_result <- cor.test(sim_dsnl$x[s,t,], cur_real_rank,
+                            method = "spearman")
     temp_vec[s] <- temp_result$estimate
@@
   for(s in c(1:2000)){
-    temp_result <- cor.test(sim_dsnl_inactive$x[s,t,], cur_real_rank, method = "spearman")
+    temp_result <- cor.test(sim_dsnl_inactive$x[s,t,], 
+                            cur_real_rank, method = "spearman")
     temp_vec[s] <- temp_result$estimate
@@
 par(mar=c(3,5,3,1))
-cx <- 2;  # cex for axis label text; default is 1. bigger numbers make the text bigger, smaller, smaller.  
+cx <- 1.75  # cex for axis label text; 
+# default is 1. bigger numbers make the text bigger, smaller, smaller.  
 x.ttl <- ""; # blank x-axis label  
-y.ttl <- "rank correlation (expert rank)";  
+y.ttl <- "rank corr. (expert rank)";  
 ttl <- "(b)";  
-#y.lim <- c(min(data.tbl$data.value), max(data.tbl$data.value)+.5); # y-axis limits. +2 at top to give room for legend  
+#y.lim <- c(min(data.tbl$data.value), max(data.tbl$data.value)+.5);
+# y-axis limits. +2 at top to give room for legend  
 y.lim <- c(-1,1.2)    
@@
 
-plot(x=0, y=0, xlim=x.lim, ylim=y.lim, xaxt='n', col='white', xlab=x.ttl, ylab=y.ttl, main=ttl, cex.main=cx*1.3, cex.axis=cx, cex.lab=cx); 
-axis(side=1, at=1:length(task.types), labels=task.types, cex.axis=cx, cex.lab=cx)  # put on the x-axis labels  
+plot(x = 0, y = 0, xlim = x.lim, ylim = y.lim, xaxt='n',
+     col = 'white', xlab = x.ttl,
+     ylab = y.ttl, main = ttl,
+     cex.main = cx*1.3, cex.axis = cx, cex.lab = cx); 
+axis(side = 1, at = 1:length(task.types), labels = task.types,
+     cex.axis=cx, cex.lab=cx)  # put on the x-axis labels  
 grid(nx=NA, ny=NULL, col='darkgrey');  
@@
   for (i in 1:length(sub.types)) {  # t.id <- 1; i <- 1;   
-   inds <- which(data.tbl$sub.type == sub.types[i] & data.tbl$task.type == task.types[t.id])
-   boxplot(data.tbl$data.value[inds], at=t.id+shifts[i], col=cols[i], add=TRUE, 
-           xaxt='n', yaxt='n', bty='n', boxwex=0.35, outpch = 20, outcex = 0.5) 
-  }  
-}  
-legend(x='top', legend=sub.types, fill=cols, horiz=TRUE, cex=cx, bg='white', bty='n')  
+   inds <- which(data.tbl$sub.type == sub.types[i] & 
+                   data.tbl$task.type == task.types[t.id])
+   boxplot(data.tbl$data.value[inds], at=t.id+shifts[i],
+           col=cols[i], add=TRUE, 
+           xaxt='n', yaxt='n', bty='n', boxwex=0.35,
+           outpch = 20, outcex = 0.5) 
+  }  
+}  
+legend(x='top', legend = sub.types, fill=cols,
+       horiz = TRUE, cex = cx, bg = 'white', bty = 'n')  
 box()

### 2020-10-15 output_scripts/Paper_Plots.Rmd
add plot to compare ks plots from m1 and m2

@@
 slides_plots <- FALSE
+current_cohort <- 5
 ```
@@
 expert_rank_10 <- list()
-out <- captureOutput(for(current_cohort in fit_cohorts){
-  naive_rank_10[[current_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[current_cohort]]])
-  expert_rank_10[[current_cohort]] <- expertRankHierarchy(full_data[[cohort_names[current_cohort]]])
+out <- captureOutput(for(curr_cohort in fit_cohorts){
+  naive_rank_10[[curr_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[curr_cohort]]])
+  expert_rank_10[[curr_cohort]] <- expertRankHierarchy(full_data[[cohort_names[curr_cohort]]])
 })
@@
 ```{r define_functions}
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
+model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1 +
+                                                        exp(-eta3*(x-y))))})
 
@@
 ```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE}
-current_cohort <- 5
+# current_cohort <- 5
 
@@
 par(mar = c(0,2,0,3),mgp=c(0,0.8,0))
-
+m1_ks <- ks.stat.matrix
 col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)),length.out = 100),
@@
       col=col_obj$col.vec,
-      xlab="",ylab="",axes=FALSE)
+      xlab="",ylab="", axes = FALSE)
 axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1,
@@
 ```{r fig-3a-baseline-rate}
-current_cohort <- 5
+# current_cohort <- 5
 
@@
 ```{r fig-3b-rank-comparison}
-current_cohort <- 5
+# current_cohort <- 5
 
@@
 # 2 -> 11 might be good here
-current_cohort <- 5
+# current_cohort <- 5
 clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
@@
       min(Lambda.dc_hawkes.test), max(Lambda.dc_hawkes.test),
-      ylab = "", xlab = "", axes = FALSE,
+      ylab = "", xlab = "",
       add = TRUE, lwd = 2)
@@
 ```{r repeat entire fig2b for model 2}
-current_cohort <- 5
+# current_cohort <- 5
 
@@
 
+m2_ks <- ks.stat.matrix
+
 # -------------- KS plot (stat)
@@
 mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE,
+      cex = 2.2,
+      at=0.45, font=2)
+
+```
+
+```{r}
+ks_diff <-  (m2_ks - m1_ks)/m1_ks
+ks_diff[is.nan(ks_diff)] <- 0
+# -------------- KS plot (stat)
+col.vec <- cRamp(as.vector(ks_diff))
+## need to do some sort of transformation between these here
+vir_cols <- viridis::viridis(length((as.vector(ks_diff))))
+#order(as.vector(ks.stat.matrix),method = "")
+
+values <- as.vector(ks_diff)
+sorted_vals <- sort(ks_diff)
+#match(values,sorted_vals)
+col.vec.vir <- vir_cols[match(values,sorted_vals)]
+
+####
+par(oma = c(6,4,4,1), mar=rep(0,4),
+    mgp = c(0, .2, 0))
+layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
+                    byrow = TRUE),rep(12*12+1,12)), 
+       widths=c(rep(1,12),2), heights=rep(1,12))
+for(i in expert_rank_10[[current_cohort]]){
+  for(j in expert_rank_10[[current_cohort]]){
+    if(ks_diff[i,j]==0){
+      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
+           axes = FALSE, frame=TRUE)
+      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
+           border = 0, col = 'white')
+    }else{
+      Lambda.test <- Lambda_matrix[i,j][[1]]
+      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
+            ylab="",xlab="",axes = FALSE, frame=TRUE)
+      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
+           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
+      # curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
+      #       ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
+      # plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
+      #      verticals = TRUE, col = "red", lwd = 2)
+    }
+  }
+}
+par(mar = c(0,2,0,3),mgp=c(0,0.8,0))
+
+col_obj <- list(x.vec = seq(min(as.vector(ks_diff)),max(as.vector(ks_diff)),
+                            length.out = 100),
+                col.vec = viridis(100))
+
+# temp <- cLegend(as.vector(ks_diff))
+
+image(1, col_obj$x.vec,
+      matrix(data=col_obj$x.vec, 
+             ncol=length(col_obj$x.vec),nrow=1),
+      col=col_obj$col.vec,
+      xlab="",ylab="")
+# axis(4, at=c(-0.2,0,0.2), labels=c(-0.2,0,0.2), las= HORIZONTAL<-1,
+#      cex.axis=2.4)
+
+mtext(text=expert_rank_10[[current_cohort]], side=1,
+      line=1.8, outer=TRUE, cex=1.8,
+      at=1/14*c(1:12)-1/22)
+mtext(text = expert_rank_10[[current_cohort]],
+      side = 2, line = 0.5, outer = TRUE, cex = 1.8,
+      at =1/12*c(12:1)-1/20, las = 2)
+mtext(text = "(M2 - M1)/M1", side = 3, line = 1.4, outer = TRUE,
       cex = 2.2,
@@
 ### Rank Comparison for Single Cohort ####
-current_cohort <- 5
+# current_cohort <- 5
 
@@
 ```{r fig-7-prMatrix-Cohort5, fig.height=7}
-current_cohort <- 5
+# current_cohort <- 5
 
@@
 ```{r fig_pr_slides, fig.height=3, fig.width=7, include=slides_plots,eval=slides_plots}
-current_cohort <- 5
+# current_cohort <- 5
 
@@
 load("../output/plot_N_predict.RData")
-current_cohort <- 5# cohort 1 looks worse than rest
+# current_cohort <- 5# cohort 1 looks worse than rest
 
@@
 load("../output/plot_N_predict.RData")
-current_cohort <- 5# cohort 1 looks worse than rest
+# current_cohort <- 5# cohort 1 looks worse than rest
 # 3 looks nice
@@
 load("../output/plot_rank_predict.RData")
-current_cohort <- 5
+# current_cohort <- 5
 temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
@@
 
-current_cohort <- 5
+# current_cohort <- 5
 
@@
 # this doesn't need to be rerun ever, even if the stan fits change
-current_cohort <- 5
+# current_cohort <- 5
 
@@
 library(PlayerRatings)
-current_cohort <- 5
+# current_cohort <- 5
 load(paste(data_path,cohort_names[current_cohort],

### 2020-10-18 output_scripts/Paper_Plots.Rmd
change potential fig 3b plot again

@@
 
-```{r}
+```{r construct ks_diff}
 ks_diff <-  (m2_ks - m1_ks)/m1_ks
@@
       at=0.45, font=2)
+
+```
+
+```{r construct ks diff normalised by num events}
+norm_diff <- (m2_ks - m1_ks)/m1_ks
+norm_diff[is.nan(norm_diff)] <- 0
+count_mat <- matrix(0, nrow = mice_number, ncol = mice_number)
+
+for(i in expert_rank_10[[current_cohort]]) {
+  for(j in expert_rank_10[[current_cohort]]) {
+    if( norm_diff[i,j] != 0 ) {
+      num_events <- unique_pairs_df %>% 
+      filter(initiator == i & recipient == j) %>%
+      pull(count)
+      # diff[i,j] <- diff[i,j] / num_events
+      count_mat[i,j] <- num_events
+    }
+  }
+}
+
+tibble(diff_norm = as.vector(norm_diff),
+       events = as.vector(count_mat)) %>%
+  filter(events > 0 ) %>%
+  ggplot(aes(events,diff_norm)) + geom_point() +
+  ylab("(M2-M1)/M1") +
+  theme_minimal()
+
+# # then same plot as above with diff
+# col.vec <- cRamp(as.vector(diff))
+# ## need to do some sort of transformation between these here
+# vir_cols <- viridis::viridis(length((as.vector(diff))))
+# #order(as.vector(ks.stat.matrix),method = "")
+# 
+# values <- as.vector(diff)
+# sorted_vals <- sort(diff)
+# #match(values,sorted_vals)
+# col.vec.vir <- vir_cols[match(values,sorted_vals)]
+# 
+# ####
+# par(oma = c(6,4,4,1), mar=rep(0,4),
+#     mgp = c(0, .2, 0))
+# layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
+#                     byrow = TRUE),rep(12*12+1,12)), 
+#        widths=c(rep(1,12),2), heights=rep(1,12))
+# for(i in expert_rank_10[[current_cohort]]){
+#   for(j in expert_rank_10[[current_cohort]]){
+#     if(diff[i,j]==0){
+#       plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
+#            axes = FALSE, frame=TRUE)
+#       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
+#            border = 0, col = 'white')
+#     }else{
+#       Lambda.test <- Lambda_matrix[i,j][[1]]
+#       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
+#             ylab="",xlab="",axes = FALSE, frame=TRUE)
+#       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
+#            border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
+#       # curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
+#       #       ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
+#       # plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
+#       #      verticals = TRUE, col = "red", lwd = 2)
+#     }
+#   }
+# }
+# par(mar = c(0,2,0,3),mgp=c(0,0.8,0))
+# 
+# col_obj <- list(x.vec = seq(min(as.vector(diff)),max(as.vector(diff)),
+#                             length.out = 100),
+#                 col.vec = viridis(100))
+# 
+# # temp <- cLegend(as.vector(ks_diff))
+# 
+# image(1, col_obj$x.vec,
+#       matrix(data=col_obj$x.vec, 
+#              ncol=length(col_obj$x.vec),nrow=1),
+#       col=col_obj$col.vec,
+#       xlab="",ylab="")
+# # axis(4, at=c(-0.2,0,0.2), labels=c(-0.2,0,0.2), las= HORIZONTAL<-1,
+# #      cex.axis=2.4)
+# 
+# mtext(text=expert_rank_10[[current_cohort]], side=1,
+#       line=1.8, outer=TRUE, cex=1.8,
+#       at=1/14*c(1:12)-1/22)
+# mtext(text = expert_rank_10[[current_cohort]],
+#       side = 2, line = 0.5, outer = TRUE, cex = 1.8,
+#       at =1/12*c(12:1)-1/20, las = 2)
+# mtext(text = "M2-M1 normalised by num events", side = 3, line = 1.4, outer = TRUE,
+#       cex = 2.2,
+#       at=0.45, font=2)
 

### 2020-10-26 output_scripts/Paper_Plots.Rmd
update fig 3 and set up sim for data from m1

--- 2020-10-15 output_scripts/Paper_Plots.Rmd
@@
                     xLabels=expert_rank_10[[current_cohort]],
-                    yLabels=rev(expert_rank_10[[current_cohort]]),
-                    title = "(a)" )
+                    yLabels=rev(expert_rank_10[[current_cohort]]) )
+                    # title = "(a)" )
 # mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
@@
            border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
-      # curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
-      #       ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
-      # plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
-      #      verticals = TRUE, col = "red", lwd = 2)
+
     }
@@
 
+```
+
+```{r construct ks diff normalised by num events}
+norm_diff <- (m2_ks - m1_ks)#/m1_ks
+norm_diff[is.nan(norm_diff)] <- 0
+count_mat <- matrix(0, nrow = mice_number, ncol = mice_number)
+
+for(i in expert_rank_10[[current_cohort]]) {
+  for(j in expert_rank_10[[current_cohort]]) {
+    if( norm_diff[i,j] != 0 ) {
+      num_events <- unique_pairs_df %>% 
+      filter(initiator == i & recipient == j) %>%
+      pull(count)
+      # diff[i,j] <- diff[i,j] / num_events
+      count_mat[i,j] <- num_events
+    }
+  }
+}
+
+tibble(diff_norm = as.vector(norm_diff),
+       events = as.vector(count_mat)) %>%
+  filter(events > 0 ) %>%
+  ggplot(aes(events,diff_norm)) + geom_point() +
+  ylab("M2-M1") +
+  theme_minimal()
+
+tibble(diff_norm = as.vector(norm_diff),
+       events = as.vector(count_mat)) %>%
+  filter(events > 0) %>%
+  ggplot(aes(diff_norm)) + 
+  geom_histogram() +
+  theme_minimal()
+
+```
+```{r repeat for residuals}
+m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                   "/chp_pr_matrix_",cohort_names[current_cohort],
+                   ".RDS",sep=''))
+
+m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                     "/dchp_pr_matrix_",cohort_names[current_cohort],
+                     ".RDS",sep=''))
+
+tibble(m1pr = as.vector(m1_pr),
+       m2pr = as.vector(m2_pr)) %>%
+  mutate(diff = m2pr - m1pr) %>%
+  ggplot(aes(diff)) + 
+  geom_histogram() +
+  labs(x = "M2 PR - M1 PR") +
+  theme_minimal()
+
+```
+
+```{r compute mean decrease in ks-score}
+summary(as.vector(m2_ks[m2_ks != 0]))
+summary(as.vector(m1_ks[m1_ks != 0]))
+
+t.test(as.vector(m2_ks[m2_ks != 0]), as.vector(m1_ks[m1_ks != 0]))
+
+diff <- as.vector(m2_ks[m2_ks != 0]) - as.vector(m1_ks[m1_ks != 0])
+
+length(which(diff < 0))/length(diff)
+summary(diff)
 ```

### 2020-10-26 run_scripts/sim_fits_M1.R

@@ -53,18 +53,12 @@ object_matrix <- list(lambda0_matrix=matrix(object_par$sim_lambda_0,
                       lambda1_matrix=matrix(object_par$sim_lambda_1,
                                             nrow=length(object_par$f_vec_1),
                                             ncol=length(object_par$f_vec_1)),
-                      ### TO DO, should this be model 1 fn here??
-                      ##### working on ####
                       alpha_matrix=formMatrix(function(x,y)
                         object_fn$alpha.fun(x,y,object_par$sim_eta_1,object_par$sim_eta_2),
                         object_par$f_vec_1),
                       beta_matrix=matrix(object_par$sim_beta,
                                          nrow=length(object_par$f_vec_1),
-                                         ncol=length(object_par$f_vec_1)),
-                      q1_matrix=formMatrix(function(x,y) object_fn$q1.fun(x,y,object_par$sim_eta_3),
-                                           object_par$f_vec_1),
-                      q2_matrix=formMatrix(function(x,y) object_fn$q0.fun(x,y,object_par$sim_eta_3),
-                                           object_par$f_vec_1))
+                                         ncol=length(object_par$f_vec_1)))
 
 # matrixPlotParameter(object_matrix$alpha_matrix)
 # object_matrix$q1_matrix
@@ -89,12 +83,12 @@ for(i in c(1:n_sim)){
 
 dir.create(data_path, recursive = TRUE, showWarnings = FALSE)
 save(object_fn, object_par, 
-     object_matrix, sim_model3_data, 
+     object_matrix, sim_model1_data, 
      file = paste(data_path,"sim_model1.RData",sep=''))
 
 
 
-### Fit each model to simulatd data ####
+### Fit each model to simulated data ####
 
 load(paste(data_path,"sim_model1.RData",sep=''))
 

### 2020-11-07 output_scripts/rank_recovery.Rmd
initial sims for rank recovery

---
title: "Rank Recovery"
author: "Owen G. Ward"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: FALSE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(rstan)
library(cmdstanr)
library(compete)
```

# Introduction

We want to consider two further concepts related to the models we have built
and used as comparisons in this paper. In particular:

1. Examine the performance of the comparison models in recovering data simulated under
the (degree corrected) C-MMHP model.
1. Based on the above, and using the I&SI objective, evaluate the 
performance of models when we estimate the latent ranking on a subset of the
data, such as the first half of the events, and then infer the I and SI scores
based on those rankings for the remaining events.

# Comparison models on simulated data

We first simulate a single dense network from the C-MMHP model.

```{r load functions}
source(here("lib",'uniHawkes.R'))
source(here("lib","mmhp.R"))
source(here("lib",'simulatePrediction.R'))
source(here("lib",'plotUtil.R'))
source(here("lib",'inferLatentMmhp.R'))
source(here("lib",'drawIntensity.R'))
source(here("lib",'myGlicko.R'))
source(here("lib",'naiveRankHierarchy.R'))
source(here("lib",'expertRankHierarchy.R'))
cut_off <- 3

model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
  return(eta1 * x * y *exp(-eta2 * abs(x - y))/(1 + exp(-eta3 * (x - y) ) ) ) })

model3_fn <- list(alpha.fun = function(x, y, eta1, eta2){
  return(eta1 * x * y * exp(-eta2 * abs(x - y) ) )},
                  q1.fun = function(x, y, eta3){
                    return(exp(-eta3 * x) )},
                  q0.fun = function(x, y, eta3){
                    return(exp(-eta3* y) ) })

#### Save the simulation parameters ####

object_fn <- list(alpha.fun = function(x, y, eta1, eta2){
  return(eta1* x *y *exp(-eta2 * abs(x - y) ) )},
                  q1.fun = function(x, y, eta3){
                    return(exp(- eta3 * x) )},
                  q0.fun = function(x, y, eta3){
                    return(exp(- eta3 * y) )})

object_par <- list(sim_lambda_0 = 0.08,
                   sim_lambda_1 = 0.15,
                   sim_eta_1 = 2.5,
                   sim_eta_2 = 0.6,
                   sim_eta_3 = 5,
                   sim_beta = 1.5,
                   f_vec_1=c(0.1, 0.2, 0.4, 0.7, 0.9))

object_matrix <- list(lambda0_matrix = matrix(object_par$sim_lambda_0,
                                            nrow = length(object_par$f_vec_1),
                                            ncol = length(object_par$f_vec_1)),
                      lambda1_matrix = matrix(object_par$sim_lambda_1,
                                            nrow = length(object_par$f_vec_1),
                                            ncol = length(object_par$f_vec_1)),
                      alpha_matrix = formMatrix(function(x,y)
                        object_fn$alpha.fun(x, y,
                                            object_par$sim_eta_1, 
                                            object_par$sim_eta_2),
                        object_par$f_vec_1),
                      beta_matrix = matrix(object_par$sim_beta,
                                         nrow = length(object_par$f_vec_1),
                                         ncol = length(object_par$f_vec_1)),
                      q1_matrix = formMatrix(function(x, y) 
                        object_fn$q1.fun(x, y, object_par$sim_eta_3),
                                           object_par$f_vec_1),
                      q2_matrix = formMatrix(function(x, y) 
                        object_fn$q0.fun(x, y, object_par$sim_eta_3),
                                           object_par$f_vec_1))

```

```{r sim data from c-mmhp, cache=TRUE}
sim_model3_data <- simulateLatentMMHP(lambda0_matrix = object_matrix$lambda0_matrix,
                                      lambda1_matrix = object_matrix$lambda1_matrix,
                                      alpha_matrix = object_matrix$alpha_matrix,
                                      beta_matrix = object_matrix$beta_matrix,
                                      q1_matrix = object_matrix$q1_matrix,
                                      q2_matrix = object_matrix$q2_matrix,
                                      horizon = 200)
clean_sim_data <- cleanSimulationData(raw_data = sim_model3_data, 
                                        cut_off = cut_off, 
                                      N = length(object_par$f_vec_1))
```

```{r recover cmmhp model, cache=TRUE}
# model3 <- stan_model(here("lib","sim_model3.stan"))
model3 <- cmdstan_model(here("lib","sim_model3.stan"))
data_list <- list(max_Nm=max(clean_sim_data$N_count),
                    N_til = length(clean_sim_data$I_fit),
                    M=sum(clean_sim_data$N_count>=cut_off),
                    N=length(object_par$f_vec_1),
                    I_fit = clean_sim_data$I_fit,
                    J_fit = clean_sim_data$J_fit,
                    T = tail(clean_sim_data$day_hour,1),
                    Nm = as.vector(clean_sim_data$N_count[clean_sim_data$N_count 
                                                          >= cut_off]),
                    event_matrix = clean_sim_data$event_matrix,
                    interevent_time_matrix = clean_sim_data$time_matrix,
                    max_interevent = clean_sim_data$max_interevent)

model3_stan_fit <- model3$sample(data = data_list,
                                num_warmup = 500,
                                num_samples = 500,
                                chains = 4, 
                                parallel_chains = 4,
                                refresh = 100)

```

```{r extract stan fit}
stanfit <- rstan::read_stan_csv(model3_stan_fit$output_files())

stansims <- rstan::extract(stanfit)
## truth is .1, .2, .4, .7, .9
apply(stansims$f, 2, mean)
apply(stansims$f, 2, sd)
```

```{r fit I&SI}
count_data <- get_wl_matrix(df = cbind(clean_sim_data$start,clean_sim_data$end))
isi.out <- compete::isi98(m = count_data, random = TRUE)
isi_rank <- as.numeric(rev(isi.out$best_order)) # ranked from lowest to highest

table(1:5,isi_rank)
```

### 2020-11-09 output_scripts/rank_recovery.Rmd
degree corrected sim model and corresponding sim example

@@
 model3_stan_fit <- model3$sample(data = data_list,
-                                num_warmup = 500,
-                                num_samples = 500,
+                                iter_warmup = 500,
+                                iter_sampling = 500,
                                 chains = 4, 
@@
 apply(stansims$f, 2, sd)
+
+# most important is the order
+m3_rank <- order(apply(stansims$f, 2, mean))
+#order(apply(stansims$f, 2, sd))
 ```
@@
 
-table(1:5,isi_rank)
+isi_rank
+true_rank <- c(1:5)
+
+table(true_rank, m3_rank)
+table(true_rank, isi_rank)
+table(isi_rank, m3_rank)
 ```
+
+## Simulated from degree corrected model
+
+How does this ranking inference compare when we instead simulate
+data from the proposed degree corrected model.
+
+```{r sim dc mmhp, cache=TRUE}
+gamma_var <- c(0.01, 0.02, 0.03, 0.06, 0.07)
+zeta_var <- c(0.075, 0.02, 0.03, 0.05, 0.08 )
+lambda_dc_matrix <- outer(gamma_var, zeta_var, "+")
+# lambda_dc_matrix
+
+object_dc_matrix <- object_matrix
+object_dc_matrix$lambda0_matrix <- lambda_dc_matrix
+
+sim_model3_data_dc <- 
+  simulateLatentMMHP(lambda0_matrix = object_dc_matrix$lambda0_matrix,
+                      lambda1_matrix = object_dc_matrix$lambda1_matrix,
+                      alpha_matrix = object_dc_matrix$alpha_matrix,
+                      beta_matrix = object_dc_matrix$beta_matrix,
+                      q1_matrix = object_dc_matrix$q1_matrix,
+                      q2_matrix = object_dc_matrix$q2_matrix,
+                      horizon = 200)
+clean_sim_data_dc <- cleanSimulationData(raw_data = sim_model3_data_dc, 
+                                        cut_off = cut_off, 
+                                      N = length(object_par$f_vec_1))
+
+```
+
+```{r fit dc mmhp, cache=TRUE}
+model3_dc <- cmdstan_model(here("lib","sim_model3_dc.stan"))
+data_list_dc <- list(max_Nm = max(clean_sim_data_dc$N_count),
+                    N_til = length(clean_sim_data_dc$I_fit),
+                    M=sum(clean_sim_data_dc$N_count>=cut_off),
+                    N=length(object_par$f_vec_1),
+                    I_fit = clean_sim_data_dc$I_fit,
+                    J_fit = clean_sim_data_dc$J_fit,
+                    T = tail(clean_sim_data_dc$day_hour,1),
+                    Nm = as.vector(clean_sim_data_dc$N_count[
+                      clean_sim_data_dc$N_count 
+                                                          >= cut_off]),
+                    event_matrix = clean_sim_data_dc$event_matrix,
+                    interevent_time_matrix = clean_sim_data_dc$time_matrix,
+                    max_interevent = clean_sim_data_dc$max_interevent)
+
+model3_dc_stan_fit <- model3_dc$sample(data = data_list_dc,
+                                seed = 123,
+                                iter_warmup = 500,
+                                iter_sampling = 500,
+                                chains = 4, 
+                                parallel_chains = 4,
+                                refresh = 100)
+
+stanfit_dc <- rstan::read_stan_csv(model3_dc_stan_fit$output_files())
+stansims_dc <- rstan::extract(stanfit_dc)
+## truth is .1, .2, .4, .7, .9
+apply(stansims_dc$f, 2, mean)
+apply(stansims_dc$f, 2, sd)
+
+# most important is the order
+m3_dc_rank <- order(apply(stansims_dc$f, 2, mean))
+```
+
+Then we can compare the I&SI model here also.
+
+```{r i and si dc}
+count_data_dc <- get_wl_matrix(df = cbind(clean_sim_data_dc$start, 
+                                       clean_sim_data_dc$end))
+isi_dc.out <- compete::isi98(m = count_data_dc, random = TRUE)
+isi_rank_dc <- as.numeric(rev(isi_dc.out$best_order)) # ranked from lowest to highest
+
+isi_rank_dc
+true_rank <- c(1:5)
+
+table(true_rank, m3_rank)
+table(true_rank, isi_rank)
+table(isi_rank, m3_rank)
+```
+
+So when we consider this degree corrected model we also
+correctly recover the latent ranking order in this simulation.

### 2020-11-09 output_scripts/rank_recovery.Rmd
modify to simulate data from dc mmhp model to see the results

@@
     toc_float: true
-    number_sections: FALSE
+    number_sections: TRUE
     code_folding: hide
@@
 
+## Simulated data from original model
+
 ```{r sim data from c-mmhp, cache=TRUE}
@@
 
-```{r recover cmmhp model, cache=TRUE}
+```{r recover cmmhp model, eval=FALSE ,cache=TRUE}
 # model3 <- stan_model(here("lib","sim_model3.stan"))
@@
 model3_stan_fit <- model3$sample(data = data_list,
-                                iter_warmup = 500,
-                                iter_sampling = 500,
+                                seed = 123,
+                                iter_warmup = 50,
+                                iter_sampling = 50,
                                 chains = 4, 
@@
                                 refresh = 100)
+model3_stan_fit$save_object(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "model_3_stan_fit.RDS"))
 
@@
 ```{r extract stan fit}
+model3_stan_fit <- readRDS(here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "model_3_stan_fit.RDS"))
 stanfit <- rstan::read_stan_csv(model3_stan_fit$output_files())
@@
 
-```{r fit dc mmhp, cache=TRUE}
+```{r fit dc mmhp, eval=FALSE}
 model3_dc <- cmdstan_model(here("lib","sim_model3_dc.stan"))
@@
 
+model3_dc_stan_fit$save_object(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "model_3_dc_stan_fit.RDS"))
+```
+
+```{r load dc stan fit}
+model3_dc_stan_fit <- readRDS(here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "model_3_dc_stan_fit.RDS"))
 stanfit_dc <- rstan::read_stan_csv(model3_dc_stan_fit$output_files())
@@
 table(true_rank, m3_rank)
-table(true_rank, isi_rank)
-table(isi_rank, m3_rank)
+table(true_rank, isi_rank_dc)
+table(isi_rank_dc, m3_rank)
 ```
@@
 So when we consider this degree corrected model we also
-correctly recover the latent ranking order in this simulation.
+correctly recover the latent ranking order in this simulation from 
+both the stan fit and the I&SI model.

### 2020-11-09 run_scripts/sim_fits.R

@@ -4,7 +4,7 @@
 #### if running on cluster ####
 source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
 
-data_path <- "output/sims_long/"
+data_path <- "output/sims_m3_dc/"
 
 library(rstan)
 options(mc.cores = parallel::detectCores())
@@ -40,14 +40,15 @@ object_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*
 object_par <- list(sim_lambda_0=0.08,
                    sim_lambda_1=0.15,
                    sim_eta_1=2.5,
+                   gamma_var = c(0.01, 0.02, 0.03, 0.06, 0.07),
+                   zeta_var = c(0.075, 0.02, 0.03, 0.05, 0.08),
                    sim_eta_2=0.6,
                    sim_eta_3=5,
                    sim_beta=1.5,
                    f_vec_1=c(0.1,0.2,0.4,0.7,0.9))
 
-object_matrix <- list(lambda0_matrix=matrix(object_par$sim_lambda_0,
-                                            nrow=length(object_par$f_vec_1),
-                                            ncol=length(object_par$f_vec_1)),
+object_matrix <- list(lambda0_matrix=outer(object_par$gamma_var,
+                                           object_par$zeta_var, "+"),
                       lambda1_matrix=matrix(object_par$sim_lambda_1,
                                             nrow=length(object_par$f_vec_1),
                                             ncol=length(object_par$f_vec_1)),
@@ -101,7 +102,7 @@ sim_model3_stan_fit3 <- rep(list(),n_sim)
 
 model1 <- stan_model("lib/sim_model1.stan")
 model2 <- stan_model("lib/sim_model2.stan")
-model3 <- stan_model("lib/sim_model3.stan")
+model3 <- stan_model("lib/sim_model3_dc.stan")
 
 for(i in c(1:n_sim)){
   clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data[i][[1]], 

### 2020-11-10 output_scripts/rank_recovery.Rmd
add file to sim ranks and compare

@@
 
-We first simulate a single dense network from the C-MMHP model.
+We first simulate a single dense network from the C-MMHP model,
+with a latent rank vector given by
+
+$$
+f =(0.1, 0.2, 0.4, 0.7, 0.9).
+$$
 
@@
 
+We can then extract the posterior mean rank from our fitted model.
+
 ```{r extract stan fit}
@@
 ## truth is .1, .2, .4, .7, .9
+
 apply(stansims$f, 2, mean)
-apply(stansims$f, 2, sd)
+# posterior mean
+# posterior sd
+# apply(stansims$f, 2, sd)
 
@@
 ```
+We can compare this to the ranking from I&SI on the count data alone, which
+is given below.
 
-```{r fit I&SI}
+```{r fit I&SI, results='hide'}
 count_data <- get_wl_matrix(df = cbind(clean_sim_data$start,clean_sim_data$end))
@@
 isi_rank <- as.numeric(rev(isi.out$best_order)) # ranked from lowest to highest
+```
+```{r print isi result}
+isi_rank
+```
 
-isi_rank
+Similarly we can compare these and the true ranking pairwise.
+
+```{r}
 true_rank <- c(1:5)
@@
 # most important is the order
-m3_dc_rank <- order(apply(stansims_dc$f, 2, mean))
+m3_dc_rank <- sort(apply(stansims_dc$f, 2, mean))
 ```
@@
 both the stan fit and the I&SI model.
+
+# Extrapolation from inferred rank on subset
+
+We also wish to consider how well we can infer the latent rank 
+over time, where

### 2020-11-10 run_scripts/sim_rank_isi.R

@@ -1,0 +1,150 @@
+##### compare inferred rank for simulated data using i&si method
+
+source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+
+
+data_path <- "output/rank_sims/sims_m3_dc_isi/"
+
+
+jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+jobid <- as.numeric(jobid)
+sim_id <- jobid
+
+library(here)
+library(tidyverse)
+library(rstan)
+library(compete)
+
+
+source(here("lib",'uniHawkes.R'))
+source(here("lib","mmhp.R"))
+source(here("lib",'simulatePrediction.R'))
+source(here("lib",'plotUtil.R'))
+source(here("lib",'inferLatentMmhp.R'))
+source(here("lib",'drawIntensity.R'))
+source(here("lib",'myGlicko.R'))
+source(here("lib",'naiveRankHierarchy.R'))
+source(here("lib",'expertRankHierarchy.R'))
+cut_off <- 3
+
+model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
+  return(eta1 * x * y *exp(-eta2 * abs(x - y))/(1 + exp(-eta3 * (x - y) ) ) ) })
+
+model3_fn <- list(alpha.fun = function(x, y, eta1, eta2){
+  return(eta1 * x * y * exp(-eta2 * abs(x - y) ) )},
+  q1.fun = function(x, y, eta3){
+    return(exp(-eta3 * x) )},
+  q0.fun = function(x, y, eta3){
+    return(exp(-eta3* y) ) })
+
+
+#### Save the simulation parameters ####
+
+object_fn <- list(alpha.fun = function(x, y, eta1, eta2){
+  return(eta1* x *y *exp(-eta2 * abs(x - y) ) )},
+  q1.fun = function(x, y, eta3){
+    return(exp(- eta3 * x) )},
+  q0.fun = function(x, y, eta3){
+    return(exp(- eta3 * y) )})
+
+object_par <- list(sim_lambda_0 = 0.08,
+                   sim_lambda_1 = 0.15,
+                   sim_eta_1 = 2.5,
+                   sim_eta_2 = 0.6,
+                   sim_eta_3 = 5,
+                   sim_beta = 1.5,
+                   f_vec_1=c(0.1, 0.2, 0.4, 0.7, 0.9))
+
[…]

### 2020-11-11 output_scripts/rank_recovery.Rmd
add glicko comparison for test data

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, tidy = TRUE)
 library(here)
@@
 library(compete)
+library(posterior)
 ```
@@
 $$
-f =(0.1, 0.2, 0.4, 0.7, 0.9).
+f = (0.1, 0.2, 0.4, 0.7, 0.9).
 $$
@@
 
-```{r sim data from c-mmhp, cache=TRUE}
+```{r sim data from c-mmhp, eval=FALSE}
 sim_model3_data <- simulateLatentMMHP(lambda0_matrix = object_matrix$lambda0_matrix,
@@
                                       N = length(object_par$f_vec_1))
+
+saveRDS(clean_sim_data,file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "sim_data_M3.RDS"))
+
 ```
 
-```{r recover cmmhp model, eval=FALSE ,cache=TRUE}
+```{r recover cmmhp model, eval=FALSE}
 # model3 <- stan_model(here("lib","sim_model3.stan"))
+clean_sim_data <- readRDS(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "sim_data_M3.RDS"))
 model3 <- cmdstan_model(here("lib","sim_model3.stan"))
@@
                                 seed = 123,
-                                iter_warmup = 50,
-                                iter_sampling = 50,
+                                iter_warmup = 500,
+                                iter_sampling = 500,
                                 chains = 4, 
@@
                                         "model_3_stan_fit.RDS"))
-stanfit <- rstan::read_stan_csv(model3_stan_fit$output_files())
 
-stansims <- rstan::extract(stanfit)
+m3_draws <- as_draws_df(model3_stan_fit$draws())
+m3_post_rank <- m3_draws %>% select(starts_with("f")) %>% apply(2,mean)
+m3_post_rank
 ## truth is .1, .2, .4, .7, .9
 
-apply(stansims$f, 2, mean)
 # posterior mean
@@
 # most important is the order
-m3_rank <- order(apply(stansims$f, 2, mean))
+m3_rank <- order(m3_post_rank)
 #order(apply(stansims$f, 2, sd))
 ```
+
 We can compare this to the ranking from I&SI on the count data alone, which
-is given below.
+is given below. This incorrectly orders the two lowest ranked nodes.
 
 ```{r fit I&SI, results='hide'}
+clean_sim_data <- readRDS(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "sim_data_M3.RDS") )
 count_data <- get_wl_matrix(df = cbind(clean_sim_data$start,clean_sim_data$end))
@@
 
-```{r}
+```{r overall sim ranks}
 true_rank <- c(1:5)
@@
 
-```{r sim dc mmhp, cache=TRUE}
+```{r sim dc mmhp, eval=FALSE}
 gamma_var <- c(0.01, 0.02, 0.03, 0.06, 0.07)
@@
 
+saveRDS(clean_sim_data_dc,file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "sim_data_M3_dc.RDS"))
+
 ```
@@
 ```{r fit dc mmhp, eval=FALSE}
+clean_sim_data_dc <- readRDS(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "sim_data_M3_dc.RDS"))
 model3_dc <- cmdstan_model(here("lib","sim_model3_dc.stan"))
@@
                                         "model_3_dc_stan_fit.RDS"))
-stanfit_dc <- rstan::read_stan_csv(model3_dc_stan_fit$output_files())
-stansims_dc <- rstan::extract(stanfit_dc)
+m3_dc_draws <- as_draws_df(model3_dc_stan_fit$draws())
+m3_dc_rank <- m3_dc_draws %>% select(starts_with("f")) %>% apply(2,mean)
+m3_dc_rank
 ## truth is .1, .2, .4, .7, .9
-apply(stansims_dc$f, 2, mean)
-apply(stansims_dc$f, 2, sd)
+# apply(stansims_dc$f, 2, sd)
 
 # most important is the order
-m3_dc_rank <- sort(apply(stansims_dc$f, 2, mean))
+m3_dc_rank <- order(m3_dc_rank)
 ```
 
-Then we can compare the I&SI model here also.
+Then we can compare the I&SI model here also. Here there is exact agreement.
 
-```{r i and si dc}
+```{r i and si dc, results='hide'}
+clean_sim_data_dc <- readRDS(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "sim_data_M3_dc.RDS") ) 
 count_data_dc <- get_wl_matrix(df = cbind(clean_sim_data_dc$start, 
@@
 isi_dc.out <- compete::isi98(m = count_data_dc, random = TRUE)
-isi_rank_dc <- as.numeric(rev(isi_dc.out$best_order)) # ranked from lowest to highest
+isi_rank_dc <- as.numeric(rev(isi_dc.out$best_order)) 
+# ranked from lowest to highest
+```
 
+```{r tables of agreement}
 isi_rank_dc
@@
 
-So when we consider this degree corrected model we also
+So when we consider this degree corrected model we
 correctly recover the latent ranking order in this simulation from 
 both the stan fit and the I&SI model.
+
+## Multiple Simulations
+
+To confirm this result we simulate and fit these models to data from 
+the degree corrected model 20 times. We wish to see how many times 
+they agree.
+
+We see that the C-MMHP model somewhat better recovers the true
+ranks in this simulation, with both performing well. We also
+see that any discrepancies from the true ranking are small, with the
+order of a pair of nodes being swapped.
+
+```{r load in sims, options}
+sim_files <- list.files(here("output","rank_sims","sims_m3_dc_isi"))
+
+all_sims <- tibble()
+for(i in seq_along(sim_files)) {
+ single_fit <- readRDS(here("output", "rank_sims", 
+                            "sims_m3_dc_isi",
+                            sim_files[i]))
+ all_sims <- all_sims %>% bind_rows(single_fit)
+}
+
+```
+
+We can look at the overall summary of the ranking of the two models and
+the truth.
+
+```{r summary ranks}
+all_sims %>% 
+  group_by(truth,m3_dc,isi) %>%
+  count() %>% arrange(-n) 
+```
+
+We would like to identify how many times each model correctly recovers the
+full ranking.
+We see that the C-MMHP is fully correct 80% of the time while the 
+I&SI ranking is fully correct in 60% of these simulations.
+
+```{r prop full recover}
+all_sims$sim <- rep(1:20, each = 5)
+
+all_sims %>% select(sim, truth, m3_dc) %>%
+  mutate(diff = truth - m3_dc) %>%
+  group_by(sim) %>%
+  summarise(prop_diff = mean(diff!=0)) %>%
+  summarise(full_recovery = mean(prop_diff == 0))
+
+all_sims %>% select(sim, truth, isi) %>%
+  mutate(diff = truth - isi) %>%
+  group_by(sim) %>%
+  summarise(prop_diff = mean(diff!=0)) %>%
+  summarise(full_recovery = mean(prop_diff == 0))
+```
+
+We see strong agreement between our model and the true ranking of
+the simulated data for most nodes.
+
+```{r truth_m3}
+all_sims %>%
+  group_by(truth, m3_dc) %>%
+  count() %>%
+  mutate(per = n/20) %>%
+  arrange(-per)
+```
+
+Finally, we look at the agreement between the ISI ranking and the truth.
+
+```{r truth isi}
+all_sims %>%
+  group_by(truth, isi) %>%
+  count() %>%
+  mutate(per = n/20) %>%
+  arrange(-per)
+
+```
 
@@
 We also wish to consider how well we can infer the latent rank 
-over time, where
+over time. To investigate this, we wish to split the data in a Mice cohort
+(or simulation data) temporally, and examine the inferred model on the 
+first half of the interactions compared to on the remaining data,
+by looking at the inferred I&SI scores.
+
+```{r compute isi}
+# taking code from compete package
+compute_isi <- function(win_loss_matrix, curr_ranking) {
+  # this takes ranking from highest to lowest
+  wl <- win_loss_matrix[curr_ranking,curr_ranking]
+  n <- as.numeric(dim(wl)[1])
+  m <- matrix(0, n, n)
+  siind <- matrix(0, n, n)
+  I = 0
+  SI = 0
+  for (j in 2:n) {
+      for (i in 1:(j - 1)) {
+          siind[j, i] = j - i
+          siind[i, j] = j - i
+          if (wl[j, i] == 0 & wl[i, j] == 0) {
+              m[j, i] = 0
+              m[i, j] = 0
+          }
+          else {
+              if (wl[j, i] > wl[i, j]) {
+                m[j, i] = 1
+                m[i, j] = -1
+              }
+              if (wl[j, i] < wl[i, j]) {
+                m[j, i] = -1
+                m[i, j] = 1
+              }
+              if (wl[j, i] == wl[i, j]) {
+                m[j, i] = 0.5
+                m[i, j] = 0.5
+              }
+          }
+      }
+  }
+  I = sum(lower.tri(m) * m == 1)
+  SI = sum((lower.tri(m) * m == 1) * siind)
+
+  list(I_score = I, SI_score = SI, wl_mat = wl)
+}
+
+```
+
+```{r check isi function, results='hide'}
+clean_sim_data <- readRDS(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "sim_data_M3.RDS"))
+clean_sim_data_dc$N_count
+
+count_data_dc <- get_wl_matrix(df = cbind(clean_sim_data_dc$start, 
+                                       clean_sim_data_dc$end))
+isi_dc.out <- compete::isi98(m = count_data_dc, random = TRUE)
+
+# these agree
+
+compute_isi(count_data_dc, curr_ranking = c(5,3,1,2,4))
+
+```
+
+We want to fit our models on the first half of the data
+and then compare the ranking estimated from it on 
+the remaining data, in terms of I&SI score.
+
+```{r sim data and split, eval=FALSE}
+sim_model3_data_dc <- 
+  simulateLatentMMHP(lambda0_matrix = object_dc_matrix$lambda0_matrix,
+                      lambda1_matrix = object_dc_matrix$lambda1_matrix,
+                      alpha_matrix = object_dc_matrix$alpha_matrix,
+                      beta_matrix = object_dc_matrix$beta_matrix,
+                      q1_matrix = object_dc_matrix$q1_matrix,
+                      q2_matrix = object_dc_matrix$q2_matrix,
+                      horizon = 200)
+
+sim_data <- tibble(start = sim_model3_data_dc$start,
+                   end = sim_model3_data_dc$end,
+                   day_hour = sim_model3_data_dc$day_hour)
+
+training_data <- sim_data %>% filter(day_hour <= 100)
+test_data <- sim_data %>% filter(day_hour > 100 )
+
+saveRDS(training_data,file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "train_data_dc.RDS"))
+saveRDS(test_data,file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "test_data_dc.RDS"))
+
+```
+
+```{r fit m3 to first half, eval=FALSE}
+training_data <- readRDS(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "train_data_dc.RDS"))
+
+clean_training <- cleanSimulationData(training_data, cut_off = 3, N = 5)
+
+data_list_training <- list(max_Nm = max(clean_training$N_count),
+                    N_til = length(clean_training$I_fit),
+                    M=sum(clean_training$N_count>=cut_off),
+                    N=length(object_par$f_vec_1),
+                    I_fit = clean_training$I_fit,
+                    J_fit = clean_training$J_fit,
+                    T = tail(clean_training$day_hour,1),
+                    Nm = as.vector(clean_training$N_count[
+                      clean_training$N_count 
+                                                          >= cut_off]),
+                    event_matrix = clean_training$event_matrix,
+                    interevent_time_matrix = clean_training$time_matrix,
+                    max_interevent = clean_training$max_interevent)
+
+model3_dc <- cmdstan_model(here("lib","sim_model3_dc.stan"))
+
+model3_dc_train <- model3_dc$sample(data = data_list_training,
+                                seed = 123,
+                                iter_warmup = 500,
+                                iter_sampling = 500,
+                                chains = 4, 
+                                parallel_chains = 4,
+                                refresh = 100)
+
+model3_dc_train$save_object(file = here("output", "rank_sims",
+                                        "rmd_stan",
+                                        "model_3_dc_train_fit.RDS"))
+
+```
+
+```{r get rank from this,results='hide'}
+model3_dc_train <- readRDS(here("output", "rank_sims",
+                                        "rmd_stan",
+                                        "model_3_dc_train_fit.RDS"))
+
+m3_draws_train <- as_draws_df(model3_dc_train$draws())
+m3_train_rank <- m3_draws_train %>% select(starts_with("f")) %>% apply(2,mean)
+
+m3_train_rank
+
+m3_train_rank <- rev(order(m3_train_rank))
+# then feed this ranking into the test data
+
+test_data <- readRDS(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "test_data_dc.RDS"))
+
+```
+
+We can compare the I&SI score from the posterior ranks from the
+first half of the data with that obtained from using the I&SI
+ranks from the first half of the data, which agree here.
+
+```{r fit isi train, results='hide'}
+
+test_wl <- get_wl_matrix(cbind(test_data$start,test_data$end))
+m3_test_score <- compute_isi(test_wl,curr_ranking = m3_train_rank)
+
+# then compare this to isi for test data
+
+training_data <- readRDS(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "train_data_dc.RDS"))
+
+train_wl <- get_wl_matrix(cbind(training_data$start,training_data$end))
+
+isi_train <- isi98(train_wl)
+isi_train_rank <- isi_train$best_order
+
+isi_test_score <- compute_isi(test_wl,curr_ranking = isi_train_rank)
+
+```
+
+```{r}
+m3_test_score
+isi_test_score
+```
+
+How does this compare to the optimal score using only the test data.
+```{r fit isi to test}
+isi98(test_wl)
+```
+
+## Aggregate Ranking Model
+
+We can similarly do this for some of the other models we use
+as comparison, such as the Aggregate ranking model.
+
+```{r fit agg rank training, results='hide'}
+training_data <- readRDS(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "train_data_dc.RDS"))
+
+clean_training <- cleanSimulationData(training_data, cut_off = 3, N = 5)
+
+agg_rank_training <- clean_training$N_count
+
+agg_rank_model <- cmdstan_model(here("lib","latent_rank_agg_sim.stan"))
+
+agg_rank_fit <- agg_rank_model$sample(data = list(n = 5,
+                                                  n_matrix = agg_rank_training),
+                                      seed = 123,
+                                      iter_warmup = 500,
+                                      iter_sampling = 500,
+                                      chains = 4, 
+                                      parallel_chains = 4,
+                                      refresh = 100)
+
+agg_rank_draws_train <- as_draws_df(agg_rank_fit$draws())
+agg_train_mean_rank <- agg_rank_draws_train %>%
+  select(starts_with("x")) %>% apply(2,mean)
+
+agg_rank_train <- order(agg_train_mean_rank)
+```
+
+```{r show agg rank mean}
+agg_train_mean_rank
+```
+
+The aggregate ranking model struggles to correctly identify the correct
+ranking, resulting in a large I&SI score.
+
+```{r compute_isi for agg rank}
+test_data <- readRDS(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "test_data_dc.RDS"))
+test_wl <- get_wl_matrix(cbind(test_data$start, test_data$end))
+
+agg_test_score <- compute_isi(test_wl,curr_ranking = agg_rank_train)
+agg_test_score
+```
+
+## Glicko Model
+
+We can also perform this comparison with the Glicko 
+model on the training data.
+
+```{r fit glicko}
+library(PlayerRatings)
+source(here("lib","myGlicko.R"))
+
+training_data <- readRDS(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "train_data_dc.RDS"))
+
+training_data
+### need score (1) for all of these, along with the row number
+
+glick_df <- training_data %>% 
+  mutate(id = row_number(), score = 1) %>%
+  select(id, start, end , score)
+
+gl_train <- my_glicko(glick_df, history=TRUE, cval=2)
+
+gl_train
+
+gl_ranks <- rev(gl_train$ratings$Player)
+# highest to lowest
+
+```
+
+This correctly recovers the true ranking and will therefore result in 
+the same optimal I&SI score.
+
+```{r glicko test}
+test_data <- readRDS(file = here("output", "rank_sims", 
+                                        "rmd_stan",
+                                        "test_data_dc.RDS"))
+test_wl <- get_wl_matrix(cbind(test_data$start, test_data$end))
+
+glicko_test_score <- compute_isi(test_wl,curr_ranking = gl_ranks)
+glicko_test_score
+
+```

### 2020-11-12 output_scripts/rank_recovery.Rmd
add ranks for m1 and m2 also and some code to tidy this up

@@
 
+Similarly, we can compute the Spearman rank correlation between each of these 
+models and the truth.
+
+```{r some code to summarise these, eval = FALSE}
+### compute spearman rank
+truth <- output_rank$truth
+output_rank %>% 
+  select(m1:isi) %>%
+  map( ~cor.test(truth, .x,
+                method = "spearman")$estimate  ) %>%
+  enframe() %>%
+  unnest(cols = c(value))
+
+output_rank2 <- output_rank
+output_rank2$sim <- 2
+output_rank2
+
+bind_rows(output_rank, output_rank2) %>%
+  group_by(sim) %>%
+  select(m1:isi) %>%
+  map( ~cor.test(truth, .x,
+                 method = "spearman")$estimate  ) %>%
+  enframe() %>%
+  unnest(cols = c(value))
+
+sims_list <- list()
+
+sims_list[[1]] <- output_rank
+sims_list[[2]] <- output_rank2
+
+spear <- function(sim_data) {
+  truth <- sim_data$truth
+  sim_data %>%
+    select(m1:isi) %>%
+    map( ~cor.test(truth, .x,
+                   method = "spearman")$estimate  ) %>%
+    enframe() %>%
+    unnest(cols = c(value))
+}
+
+map_dfr(sims_list, spear) # in a nice long format
+```
+
 # Extrapolation from inferred rank on subset
@@
 
-training_data
+# training_data
 ### need score (1) for all of these, along with the row number

### 2020-11-12 run_scripts/sim_rank_isi.R

@@ -105,6 +105,47 @@ clean_sim_data_dc <- cleanSimulationData(raw_data = sim_model3_data_dc,
 
 ### then fit the stan model (not cmdstanr)
 
+#### model 1 ####
+model1 <- stan_model(here("lib", "sim_model1.stan"))
+
+data_list <- list(max_Nm = max(clean_sim_data_dc$N_count),
+                     N_til = length(clean_sim_data_dc$I_fit),
+                     M=sum(clean_sim_data_dc$N_count>=cut_off),
+                     N=length(object_par$f_vec_1),
+                     I_fit = clean_sim_data_dc$I_fit,
+                     J_fit = clean_sim_data_dc$J_fit,
+                     T = tail(clean_sim_data_dc$day_hour,1),
+                     Nm = as.vector(clean_sim_data_dc$N_count[
+                       clean_sim_data_dc$N_count 
+                       >= cut_off]),
+                     event_matrix = clean_sim_data_dc$event_matrix,
+                     interevent_time_matrix = clean_sim_data_dc$time_matrix,
+                     max_interevent = clean_sim_data_dc$max_interevent)
+
+model1_stan_fit <- sampling(model1, data = data_list,
+                               iter = 1000, chains = 4,
+                               cores = getOption("mc.cores",1L))
+
+
+stansims_m1 <- rstan::extract(model1_stan_fit)
+
+m1_rank <- order(apply(stansims_m1$f, 2, mean))
+
+#### model 2 ####
+
+model2 <- stan_model(here("lib", "sim_model2.stan"))
+
+model2_stan_fit <- sampling(model2, data = data_list,
+                            iter = 1000, chains = 4,
+                            cores = getOption("mc.cores",1L))
+
+
+stansims_m2 <- rstan::extract(model2_stan_fit)
+
+m2_rank <- order(apply(stansims_m2$f, 2, mean))
+
+
+#### model 3 ####
 model3_dc <- stan_model(here("lib","sim_model3_dc.stan"))
 data_list_dc <- list(max_Nm = max(clean_sim_data_dc$N_count),
                      N_til = length(clean_sim_data_dc$I_fit),
@@ -143,10 +184,15 @@ isi_rank_dc <- as.numeric(rev(isi_dc.out$best_order))
 
 ## then save these
 
-output_rank <- tibble(truth = 1:5, m3_dc = m3_dc_rank,
-                      isi = isi_rank_dc)
[…]

### 2020-11-13 output_scripts/rank_recovery.Rmd
update rank recovery with real data from isi_predict

--- 2020-11-11 output_scripts/rank_recovery.Rmd
@@
 library(posterior)
+
+theme_set(theme_minimal())
 ```
@@
 ```{r prop full recover}
-all_sims$sim <- rep(1:20, each = 5)
+all_sims$sim <- rep(1:50, each = 5)
 
@@
   arrange(-per)
+
+```
+
+Similarly, we can summarise this by
+computing the Spearman rank correlation between each of these 
+models and the truth. The C-MMHP model unsurprisingly best recovers the
+true rankings, with the I&SI model performing similarly.
+
+```{r analyse sims}
+sim_files <- list.files(here("output","rank_sims","sims_m3_dc_isi"))
+
+all_sims <- list()
+for(i in seq_along(sim_files)) {
+ single_fit <- readRDS(here("output", "rank_sims", 
+                            "sims_m3_dc_isi",
+                            sim_files[i]))
+ all_sims[[i]] <- single_fit
+}
+
+spear <- function(sim_data) {
+  truth <- sim_data$truth
+  sim_data %>%
+    select(m1:isi) %>%
+    map( ~cor.test(truth, .x,
+                   method = "spearman")$estimate  ) %>%
+    enframe() %>%
+    unnest(cols = c(value))
+}
+
+sim_data <- map_dfr(all_sims, spear)
+
+name <- sim_data$name
+
+sim_data$name <- case_when(
+          name == "isi" ~ "I&SI",
+          name == "m1" ~ "C-HP",
+          name == "m2" ~ "C-DCHP",
+          name == "m3_dc" ~ "C-MMHP")
+
+sim_data$name <- factor(sim_data$name, levels = c("I&SI","C-HP",
+                                                  "C-DCHP", "C-MMHP"))
+
+sim_data %>% 
+  rename(Method = name, corr = value) %>%
+  ggplot(aes(Method,corr)) + geom_boxplot() +
+  labs(y = "Rank Correlation")
+  # in a nice long format
 
@@
                                         "rmd_stan",
-                                        "sim_data_M3.RDS"))
+                                        "sim_data_M3_dc.RDS"))
 clean_sim_data_dc$N_count
@@
 
-compute_isi(count_data_dc, curr_ranking = c(5,3,1,2,4))
+compute_isi(count_data_dc, curr_ranking = c(2,5,4,1,3))
 
@@
 
-agg_rank_train <- order(agg_train_mean_rank)
+# for highest to lowest
+agg_rank_train <- rev(order(agg_train_mean_rank))
 ```
@@
 ```
+
+## Real Data
+
+To be completed.
+
+```{r plot isi scores}
+sim_files <- list.files(here("output","rank_sims","predict_isi"))
+
+all_sims <- list()
+for(i in seq_along(sim_files)) {
+  single_fit <- readRDS(here("output", "rank_sims", 
+                             "predict_isi",
+                             sim_files[i]))
+  all_sims[[i]] <- single_fit
+}
+
+cohort_scores <- all_sims %>%
+  map(~as_tibble(.)) %>%
+  bind_rows(.id="index")
+
+cohort_scores %>% 
+  mutate(ISI = I_score + SI_score) %>%
+  ggplot(aes(model,ISI)) + geom_boxplot()
+```

### 2020-11-13 run_scripts/isi_predict.R

@@ -1,0 +1,250 @@
+### Predictions at a cohort level ####
+### Here we extract the first 15 days of data for each cohort,
+### Determine the rankings and use these to compute the I&SI score,
+### based on this ranking, for the remaining events
+
+### code ###
+## run this if running on the cluster
+source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+### set cohort_id based on job num
+jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+jobid <- as.numeric(jobid)
+cohort_id <- jobid
+#cohort_id <- 1
+####
+data_path <- "output/"
+
+
+library(rstan)
+library(tidyverse)
+options(mc.cores = parallel::detectCores())
+
+
+library(compete)
+library(PlayerRatings)
+#library(RColorBrewer)
+#library(Hmisc)
+#library(wCorr)
+#library(tidyverse)
+library(R.utils)
+#library(fields)
+
+
+
+source('lib/naiveRankHierarchy.R')
+source('lib/expertRankHierarchy.R')
+source('lib/cleanData.R') 
+source('lib/prepareDataStan.R') 
+source('lib/inferLatentMmhp.R')
+source('lib/plotUtil.R') 
+source('lib/mmhp.R')
+source('lib/uniHawkes.R')
+source('lib/simulatePrediction.R')
+source('lib/myGlicko.R')
+source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
+source('lib/matrixPlotParameter.R')
+source('lib/residualStructureScore.R')
+
+
+
+
+
+
+#### then load in the data ####
+
+full_data <- readRDS("data/mice.RData")
+# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
+cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cut_off <- 3
+mice_number <- 12
+
+
[…]

### 2020-11-15 output_scripts/rank_recovery.Rmd
correct typo with isi prediction, ranks the wrong way around and similarly look at the isi scores from fitting to all data.

@@
 
-To be completed.
+Here we estimate the rankings from each model using data from the
+first 15 days of events, and then compute the estimate I&SI scores
+from using those ranks on the remaining held out data.
 
@@
 ```
+
+We can similarly repeat this for fitting each model to all 
+data and look at the estimated I&SI scores based on those
+inferred rankings.
+
+```{r compute isi total, results='hide'}
+score_fits_all <- list()
+source(here("lib","cleanData.R"))
+
+data_path <- "../output/"
+
+full_data <- readRDS(here("data","mice.RData"))
+# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
+cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cut_off <- 3
+mice_number <- 12
+
+mini_wl_matrix <- function(df, num_mice = 12) {
+  # to avoid issues with reordering the data
+  df <- as.data.frame(df)
+  mylevs <- 1:num_mice
+  df[, 1] <- factor(df[, 1], levels = mylevs)
+  df[, 2] <- factor(df[, 2], levels = mylevs)
+  df$result <- 1
+  m1 = stats::xtabs(result ~ ., data = df)
+  m1
+}
+
+compute_isi_score <- function(win_loss_matrix, curr_ranking) {
+  # this takes ranking from highest to lowest
+  wl <- win_loss_matrix[curr_ranking,curr_ranking]
+  n <- as.numeric(dim(wl)[1])
+  m <- matrix(0, n, n)
+  siind <- matrix(0, n, n)
+  I = 0
+  SI = 0
+  for (j in 2:n) {
+    for (i in 1:(j - 1)) {
+      siind[j, i] = j - i
+      siind[i, j] = j - i
+      if (wl[j, i] == 0 & wl[i, j] == 0) {
+        m[j, i] = 0
+        m[i, j] = 0
+      }
+      else {
+        if (wl[j, i] > wl[i, j]) {
+          m[j, i] = 1
+          m[i, j] = -1
+        }
+        if (wl[j, i] < wl[i, j]) {
+          m[j, i] = -1
+          m[i, j] = 1
+        }
+        if (wl[j, i] == wl[i, j]) {
+          m[j, i] = 0.5
+          m[i, j] = 0.5
+        }
+      }
+    }
+  }
+  I = sum(lower.tri(m) * m == 1)
+  SI = sum((lower.tri(m) * m == 1) * siind)
+
+  list(I_score = I, SI_score = SI)
+}
+
+for(current_cohort in 1:10) {
+  # current_cohort <- cohort_id
+  print(paste("Cohort",current_cohort))
+
+  training_day <- 15
+  ## if I change this then I need to refit
+
+  print(current_cohort)
+  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+  return_df <- cleanObservationPeriod(current_cohort, clean_data)
+
+  #### Fit M1 ####
+  load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_hp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+  # highest to lowest
+
+  rank_m1 <- rev(order(apply(sim_cohort_hp$f, 2, mean)))
+
+  #### Predict M2 ####
+  load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_dchp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+  # highest to lowest
+  rank_m2 <- rev(order(apply(sim_cohort_dchp$f, 2, mean)))
+
+  #### Predict M3 ####
+  load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+  # highest to lowest
+  rank_m3 <- rev(order(apply(sim_cohort_mmhp$f, 2, mean)))
+
+  #### Predict Agg Ranking ####
+  load(paste(data_path,cohort_names[current_cohort],
+             "/agg_rank_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+  # highest to lowest
+  rank_agg <- rev(order(apply(sim_agg_rank$x, 2, mean)))
+
+  #### ISI Predict ####
+  full_wl <- mini_wl_matrix(df = cbind(return_df$initiator,
+                                        return_df$recipient))
+
+  isi_train <- isi98(full_wl)
+  isi_rank <- as.numeric(isi_train$best_order)
+
+  #### glicko predict
+  glick_df <- return_df %>% 
+    mutate(id = row_number(), score = 1) %>%
+    select(id, initiator, recipient , score)
+
+  gl_train <- my_glicko(glick_df, history=TRUE, cval=2)
+
+  gl_ranks <- rev(order(gl_train$ratings$Rating))
+
+  #### save this output ####
+
+  ### need to make sure the isi ordering is correct here
+
+  est_ranks <- tibble(isi_full = isi_rank,
+                      agg_full = rank_agg,
+                      glicko_full = gl_ranks,
+                      m1_full = rank_m1,
+                      m2_full = rank_m2,
+                      m3_full = rank_m3)
+
+  # full_wl <- mini_wl_matrix(cbind(return_df$initiator, return_df$recipient))
+  # best_isi <- isi98(full_wl)
+  # this is giving me the ranks correctly but am I mapping them
+  # correctly for reordering the wl matrix?
+
+  ###
+  ## do I want order here?
+  ###
+  scores <- est_ranks %>% map_dfr(~ compute_isi_score(full_wl, .x))
+
+  scores$model <- c("isi","agg", "glicko", "m1","m2","m3")
+  # scores <- scores %>% add_row(tibble_row(I_score = best_isi$I, 
+  #                              SI_score = best_isi$SI,
+  #                              model = "test_isi"))
+
+  score_fits_all[[current_cohort]] <- scores
+
+}
+
+```
+
+```{r plot these isi scores}
+score_fits_all %>%
+  map(~as_tibble(.)) %>%
+  bind_rows(.id="index") %>%
+  mutate(ISI = I_score + SI_score) %>%
+  ggplot(aes(model,ISI)) + geom_boxplot()
+```

### 2020-11-15 run_scripts/isi_predict.R

@@ -5,11 +5,11 @@
 
 ### code ###
 ## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
-### set cohort_id based on job num
-jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
-jobid <- as.numeric(jobid)
-cohort_id <- jobid
+# source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+# ### set cohort_id based on job num
+# jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+# jobid <- as.numeric(jobid)
+# cohort_id <- jobid
 #cohort_id <- 1
 ####
 data_path <- "output/"
@@ -22,6 +22,7 @@ options(mc.cores = parallel::detectCores())
 
 library(compete)
 library(PlayerRatings)
+library(here)
 #library(RColorBrewer)
 #library(Hmisc)
 #library(wCorr)
@@ -70,6 +71,7 @@ model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*
 mini_wl_matrix <- function(df, num_mice = 12) {
   # to avoid issues with reordering the data
   df <- as.data.frame(df)
+  mylevs <- 1:num_mice
   df[, 1] <- factor(df[, 1], levels = mylevs)
   df[, 2] <- factor(df[, 2], levels = mylevs)
   df$result <- 1
@@ -150,14 +152,14 @@ for(current_cohort in 1:10) {
   
   # highest to lowest
   
-  rank_m1 <- order(apply(sim_cohort_hp$f, 2, mean))
+  rank_m1 <- rev(order(apply(sim_cohort_hp$f, 2, mean)))
   
   #### Predict M2 ####
   load(paste(data_path,cohort_names[current_cohort],
              "/cohort_dchp_predict_stan_result_",cohort_names[current_cohort],
              ".RData",sep=''))
   # highest to lowest
-  rank_m2 <- order(apply(sim_cohort_dchp$f, 2, mean))
+  rank_m2 <- rev(order(apply(sim_cohort_dchp$f, 2, mean)))
   
   #### Predict M3 ####
   load(paste(data_path,cohort_names[current_cohort],
@@ -165,7 +167,7 @@ for(current_cohort in 1:10) {
[…]

### 2020-11-15 output_scripts/Paper_Plots.Rmd
adding plots for fig 4 repeated with data simulated from m1 and m2

@@
 ```{r fig-4a}
-sim_data_path <- "../output/sims_long/"
+sim_data_path <- "../output/sims/sims_m3_dc/"
 
@@
 ```{r prepare data for 4b,cache=TRUE}
-plot.s <- 9#7#9
+plot.s <- 1#7#9
 plot.i <- 4
@@
 ```{r fig4b-recover-latent-states}
-y.ub <- c(20,20,20)#c(130,72,31)
+y.ub <- c(17,17,17)#c(130,72,31)
 x_events <- 135#150
@@
 legend.y <- #c(34,32,32)
-legend.y <- c(20,12,15)#c(62,37,18)#c(22,22,22)
+legend.y <- c(15,12,15)#c(62,37,18)#c(22,22,22)
 legend.cex <- 1.5 #3
@@
 
-legend(10,legend.y[2],c("State 0/1 events","State change point"),
+legend(10,legend.y[2]+2,c("State 0/1 events","State change point"),
        col = c(NA,"red"),
@@
        lty = c(NA,NA), lwd=c(NA,4))
-points(14,8,pch=1,cex=2,col="blue")
-points(16,8,pch=16,cex=2,col="blue")
+points(14,8+2,pch=1,cex=2,col="blue")
+points(16,8+2,pch=16,cex=2,col="blue")
 
@@
 
+## Fig 4 repeated for data generated from other models
+
+For completeness, we also wish to repeat the above two plots using data generated 
+from M1 and M2.
+
+For data simulated from M1.
+
+```{r est ranks for m1 sim data}
+m1_path <- "../output/sims/M1/"
+
+m1_files <- list.files(m1_path, pattern = "sim_model1_fit*")
+#m1_files
+
+# load(paste0(m1_path,m1_files[1]))
+sim_model1_stan_sim1_total <- list()
+sim_model1_stan_sim2_total <- list()
+sim_model1_stan_sim3_total <- list()
+
+for(i in seq_along(m1_files)) {
+  load(paste0(m1_path,m1_files[i]))
+  sim_model1_stan_sim1_total[[i]] <- sim_model1_stan_sim1
+  sim_model1_stan_sim2_total[[i]] <- sim_model1_stan_sim2
+  sim_model1_stan_sim3_total[[i]] <- sim_model1_stan_sim3
+
+}
+
+m2_path <- "../output/sims/M2/"
+
+m2_files <- list.files(m2_path, pattern = "sim_model2_fit*")
+#m1_files
+
+# load(paste0(m1_path,m1_files[1]))
+sim_model2_stan_sim1_total <- list()
+sim_model2_stan_sim2_total <- list()
+sim_model2_stan_sim3_total <- list()
+
+for(i in seq_along(m2_files)) {
+  load(paste0(m2_path,m2_files[i]))
+  sim_model2_stan_sim1_total[[i]] <- sim_model2_stan_sim1
+  sim_model2_stan_sim2_total[[i]] <- sim_model2_stan_sim2
+  sim_model2_stan_sim3_total[[i]] <- sim_model2_stan_sim3
+
+}
+
+```
+
+```{r plot est ranks M1 and M2}
+n_sim <- 50
+
+#png(paste(plot_path,"sim_latent_recover.png",sep=""), height=500, width=900)
+par(mfrow=c(3, length(object_par$f_vec_1)),
+    mar=c(0,0,1,0),
+    oma=c(6.5,11,3.5,1))
+
+y.ub <- c(12,12,12,12,12)
+text.y <- c(rep(8,4),8)
+text.x <- c(0.1,0.2,0.4,0.7,0.9)
+text.x.adj <- c(0.3,0.4,0.6,0.5,0.8)
+model_colors <- c("steelblue", "goldenrod2", "firebrick2")
+model_colors <- viridis::viridis(3)
+
+for(m in c(1:3)){
+  for(j in c(1:length(object_par$f_vec_1))){
+    plot(1,4,xlim=c(0,1),ylim=c(0,y.ub[j]),
+         type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+
+    ## Posterior density
+    current_result <- eval(parse(text=paste("sim_model1_stan_sim",
+                                            m,
+                                            "_total",
+                                            sep="")))
+    for(i in c(1:n_sim)){
+      lines(density(current_result[[i]]$f[1001:2000,j]),
+            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
+    }
+
+    ## plot true value
+    abline(v=object_par$f_vec_1[j],lwd=1.8,lty=2,col="gray30")
+
+    ## plot box
+    box.wdt <- 1.5
+    box.col <- "black"
+    box(lty = 'solid',col=box.col,lwd=0.7)
+
+    if(m==3){
+      text(text.x.adj[j],text.y[j],text.x[j],cex=2.4)
+    }
+  }
+  ## bottom
+  mtext(text=expression(f[1],f[2],f[3],f[4],f[5]), side=1, line=2.4, outer=TRUE, 
+        at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
+        cex=2.4)
+  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.7,
+        at=0.5)
+  ## top
+  mtext(text="Simulated from M1", side=3, line=0, outer=TRUE, cex=3,
+        at=0.5, font=2)
+  ## left
+  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5, outer=TRUE, 
+        at=c(0:2)/3+0.15,
+        cex=2, las=2)
+}
+
+for(m in c(1:3)){
+  for(j in c(1:length(object_par$f_vec_1))){
+    plot(1,4,xlim=c(0,1),ylim=c(0,y.ub[j]),
+         type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+
+    ## Posterior density
+    current_result <- eval(parse(text=paste("sim_model2_stan_sim",
+                                            m,
+                                            "_total",
+                                            sep="")))
+    for(i in c(1:n_sim)){
+      lines(density(current_result[[i]]$f[1001:2000,j]),
+            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
+    }
+
+    ## plot true value
+    abline(v=object_par$f_vec_1[j],lwd=1.8,lty=2,col="gray30")
+
+    ## plot box
+    box.wdt <- 1.5
+    box.col <- "black"
+    box(lty = 'solid',col=box.col,lwd=0.7)
+
+    if(m==3){
+      text(text.x.adj[j],text.y[j],text.x[j],cex=2.4)
+    }
+  }
+  ## bottom
+  mtext(text=expression(f[1],f[2],f[3],f[4],f[5]), side=1, line=2.4, outer=TRUE, 
+        at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
+        cex=2.4)
+  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.7,
+        at=0.5)
+  ## top
+  mtext(text="Simulated from M2", side=3, line=0, outer=TRUE, cex=3,
+        at=0.5, font=2)
+  ## left
+  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5, outer=TRUE, 
+        at=c(0:2)/3+0.15,
+        cex=2, las=2)
+}
+```
+
+Similarly, we can then repeat this for Fig 4b also for both simulated 
+data examples, with slightly more difficulty.
+
+```{r process m1 for fig4b}
+plot.s <- 1#7#9
+plot.i <- 4
+plot.j <- 5
+
+cur_i <- plot.i
+cur_j <- plot.j
+
+load(paste0(m1_path,m1_files[plot.s]))
+
+temp.t <- sim_model1_data[[1]]$day_hour[ which(sim_model1_data[[1]]$start == cur_i & 
+                  sim_model1_data[[1]]$end == cur_j)]
+# temp.t <- test.mmhp$tau
+current.n <- length(temp.t)-1
+time.segment <- seq(0,tail(temp.t,1),length.out=5000)
+
+### Preprocess the model inference result
+## model 1
+#########
+model1_par_est <- list(lambda0 =
+                         mean(sim_model1_stan_sim1_total[[plot.s]]$lambda0[1001:2000]),
+                       eta_1=mean(sim_model1_stan_sim1_total[[plot.s]]$eta_1[1001:2000]),
+                       eta_2=mean(sim_model1_stan_sim1_total[[plot.s]]$eta_2[1001:2000]),
+                       eta_3=mean(sim_model1_stan_sim1_total[[plot.s]]$eta_3[1001:2000]),
+                       beta=mean(sim_model1_stan_sim1_total[[plot.s]]$beta[1001:2000]),
+                       f=apply(sim_model1_stan_sim1_total[[plot.s]]$f[1001:2000,],2,mean))
+lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
+                                                   model1_par_est$lambda0,
+                                    alpha =
+                                      model1_fn$alpha.fun(model1_par_est$f[plot.i],
+                                    model1_par_est$f[plot.j],
+                                    model1_par_est$eta_1,
+                                    model1_par_est$eta_2,
+                                    model1_par_est$eta_3),
+                                    beta=model1_par_est$beta),
+                                     events=temp.t,
+                                     time.vec=time.segment)
+
+## model2
+#############
+model2_par_est <- list(gamma=apply(sim_model1_stan_sim2_total[[plot.s]]$gamma[1001:2000,],
+                                   2,mean),
+                    zeta = 
+                      apply(sim_model1_stan_sim2_total[[plot.s]]$zeta[1001:2000,],2,mean),
+                       eta_1=mean(sim_model1_stan_sim2_total[[plot.s]]$eta_1[1001:2000]),
+                       eta_2=mean(sim_model1_stan_sim2_total[[plot.s]]$eta_2[1001:2000]),
+                       eta_3=mean(sim_model1_stan_sim2_total[[plot.s]]$eta_3[1001:2000]),
+                       beta=mean(sim_model1_stan_sim2_total[[plot.s]]$beta[1001:2000]),
+                       f=apply(sim_model1_stan_sim2_total[[plot.s]]$f[1001:2000,],2,mean))
+
+lambda.m2 <- uniHawkesIntensityNumeric(object=list(
+  lambda0=model2_par_est$gamma[plot.i]+
+          model2_par_est$zeta[plot.j],                                        
+  alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+                            model2_par_est$f[plot.j],
+                            model2_par_est$eta_1,
+                            model2_par_est$eta_2,
+                            model2_par_est$eta_3),
+                beta=model2_par_est$beta),
+                events=temp.t,
+                time.vec=time.segment)
+
+## Model3
+#############
+mmhp_par_est <- list(lambda0=mean(sim_model1_stan_sim3_total[[plot.s]]$lambda0[1001:2000]),
+                     lambda1=mean(sim_model1_stan_sim3_total[[plot.s]]$lambda1[1001:2000]),
+                     eta_1=mean(sim_model1_stan_sim3_total[[plot.s]]$eta_1[1001:2000]),
+                     eta_2=mean(sim_model1_stan_sim3_total[[plot.s]]$eta_2[1001:2000]),
+                     eta_3=mean(sim_model1_stan_sim3_total[[plot.s]]$eta_3[1001:2000]),
+                     beta=mean(sim_model1_stan_sim3_total[[plot.s]]$beta[1001:2000]),
+                     f=apply(sim_model1_stan_sim3_total[[plot.s]]$f[1001:2000,],2,mean))
+
+object_hat <- list(lambda0=mmhp_par_est$lambda0,
+                   lambda1=mmhp_par_est$lambda1,
+                   alpha=model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
+                                             mmhp_par_est$f[cur_j],
+                                             mmhp_par_est$eta_1,
+                                             mmhp_par_est$eta_2),
+                   beta=mmhp_par_est$beta,
+                   q1=model3_fn$q1.fun(mmhp_par_est$f[cur_i],
+                                       mmhp_par_est$f[cur_j],
+                                       mmhp_par_est$eta_3),
+                   q2=model3_fn$q0.fun(mmhp_par_est$f[cur_i],
+                                       mmhp_par_est$f[cur_j],
+                                       mmhp_par_est$eta_3))
+
+### need to load in the interpolated latent state here
+#### TO DO ####
+
+state.est.latent.mmhp <- interpolate_state_est_lst[[plot.s]][plot.i,plot.j][[1]]
+state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
+                                                 termination=200)
+
+step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,
+                        2-state.est.latent.mmhp$z.hat)
+
+lambda.m3 <- mmhpIntensityNumeric(params=object_hat,
+                                  t=temp.t[-1],
+                                  time.vec=time.segment,
+                                  latent.vec=step.fun.est(time.segment))
+
+object_true <- lapply(object_matrix,function(x) x[plot.i,plot.j])
+names(object_true) <- c("lambda0","lambda1","alpha","beta","q1","q2")
+
+lambda.true <- mmhpTrueIntensityNumeric(params=object_true,
+                                        t=temp.t,
+                       latent=list(x=fixStateTransition(test.mmhp)$x,
+                              z=fixStateTransition(test.mmhp)$z),
+                              time.vec=time.segment)
+```
+
 # Figure 5:

### 2020-11-15 run_scripts/sim_fits_M1.R
these need to be rerun with fits from dc m3

@@ -104,7 +104,7 @@ sim_model1_stan_fit3 <- rep(list())
 
 model1 <- stan_model("lib/sim_model1.stan")
 model2 <- stan_model("lib/sim_model2.stan")
-model3 <- stan_model("lib/sim_model3.stan")
+model3 <- stan_model("lib/sim_model3_dc.stan")
 
 # for(i in c(1:n_sim)){
 clean_sim_data <- cleanSimulationData(raw_data=sim_model1_data[[1]], 

### 2020-11-15 run_scripts/sim_fits_M2.R

@@ -105,7 +105,7 @@ sim_model2_stan_fit3 <- rep(list())
 
 model1 <- stan_model("lib/sim_model1.stan")
 model2 <- stan_model("lib/sim_model2.stan")
-model3 <- stan_model("lib/sim_model3.stan")
+model3 <- stan_model("lib/sim_model3_dc.stan")
 
 # for(i in c(1:n_sim)){
 clean_sim_data <- cleanSimulationData(raw_data=sim_model2_data[[1]], 

### 2020-11-16 output_scripts/Paper_Plots.Rmd
update these sims to do fig 4 for data from both m1 and m2

@@
 
+library(here)
 library(rstan)
@@
 
-### need to load in the interpolated latent state here
-#### TO DO ####
-
-state.est.latent.mmhp <- interpolate_state_est_lst[[plot.s]][plot.i,plot.j][[1]]
+state_est_fits <- list.files(m1_path, pattern = "fit123_state_est_M1*")
+load(paste0(m1_path,state_est_fits[plot.s]))
+
+state.est.latent.mmhp <- interpolate_state_est_lst[plot.i,plot.j][[1]]
 state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
@@
 lambda.m3 <- mmhpIntensityNumeric(params=object_hat,
-                                  t=temp.t[-1],
+                                  t=temp.t,
                                   time.vec=time.segment,
@@
 object_true <- lapply(object_matrix,function(x) x[plot.i,plot.j])
-names(object_true) <- c("lambda0","lambda1","alpha","beta","q1","q2")
-
-lambda.true <- mmhpTrueIntensityNumeric(params=object_true,
+names(object_true) <- c("lambda0","lambda1","alpha","beta")
+
+lambda.true <- uniHawkesIntensityNumeric(object = object_true,
+                                        events =temp.t,
+                                        time.vec = time.segment)
+```
+
+```{r fig 4b M1 sim}
+source(here("lib","mod_drawHawkesIntensityPaper.R"))
+y.ub <- c(17,17,17)#c(130,72,31)
+x_events <- 135#150
+#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
+model_colors <- viridis::viridis(3)
+layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
+layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
+my.xlim <- 140#160#200#130
+my.long.x <- 140#205#134.5
+legend.x <- c(50,50,50)#c(135,135,135)
+legend.y <- #c(34,32,32)
+legend.y <- c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.cex <- 1.5 #3
+line.alpha <- c(0.9,0.6)
+line.wdth <- c(2,2.5)
+negative.col <- add.alpha('lightskyblue',0.6)
+positive.col <- add.alpha('tomato',0.6)
+#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
+#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
+par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
+    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)
+
+# model1
+############
+true.object <- object_true
+# lambda.true$lambda.t <- lambda.est
+# lambda.true$time.vec <- lambda.m1$time.vec
+
+mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
+                             alpha = true.object$alpha,
+                             beta = true.object$beta,
+                             events = temp.t,
+                             add = FALSE,
+                            yupper=y.ub[1],
+                            color=add.alpha("black", alpha=line.alpha[1]),
+                            line.width=line.wdth[1],
+                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
+                            title_name=paste(plot.i,"->",plot.j),
+                            title.cex = 2,
+                            box.type="n")
+drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
+                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
+                                                   model1_par_est$f[plot.j],
+                                                   model1_par_est$eta_1,
+                                                   model1_par_est$eta_2,
+                                                   model1_par_est$eta_3),
+                         beta=model1_par_est$beta,
+                         events=temp.t,
+                         color=add.alpha(model_colors[1],
+                                         alpha=line.alpha[2]),
+                         line.width=line.wdth[2])
+
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+
+legend(legend.x[1],legend.y[1],c("True"),
+       col = c("black"),
+       y.intersp=0.88,x.intersp=0.15,bty = "n",
+       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
+legend(legend.x[1]+18,legend.y[1],c("C-HP"),
+       col = c(model_colors[1]),
+       y.intersp=0.88,x.intersp=0.15,bty = "n",
+       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
+
+## delta lambda
+par(mar = c(0,0.3,0,0.1))
+plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,10), type="n",
+     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
+delta.positive <- delta.lambda
+delta.positive[delta.positive<0] <- 0
+delta.negative <- delta.lambda
+delta.negative[delta.negative>0] <- 0
+### hiding these for now ###
+polygon(c(0,lambda.true$time.vec,x_events),#200
+        c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events),#200
+        c(0,delta.positive,0),col=positive.col,border=NA)
+
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+# model2
+############
+mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
+                             alpha = true.object$alpha,
+                             beta = true.object$beta,
+                             events = temp.t,
+                             add = FALSE,
+                            yupper=y.ub[1],
+                            color=add.alpha("black", alpha=line.alpha[1]),
+                            line.width=line.wdth[1],
+                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
+                            title_name=paste(plot.i,"->",plot.j),
+                            title.cex = 2,
+                            box.type="n")
+drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
+                           model2_par_est$zeta[plot.j],
+                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+                                                   model2_par_est$f[plot.j],
+                                                   model2_par_est$eta_1,
+                                                   model2_par_est$eta_2,
+                                                   model2_par_est$eta_3),
+                         beta=model2_par_est$beta,
+                         events=temp.t,
+                         color=add.alpha(model_colors[2],
+                                         alpha=line.alpha[2]),
+                         line.width=line.wdth[2])
+legend(legend.x[2],legend.y[2],"C-DCHP",
+       col = model_colors[2],
+       y.intersp=0.88,x.intersp=0.1,bty = "n",
+       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)
+
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+
+legend(10,legend.y[2]+2,c("State 0/1 events","State change point"),
+       col = c(NA,"red"),
+       y.intersp=0.85,x.intersp=-0.1, bty = "n",
+       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
+       lty = c(NA,NA), lwd=c(NA,4))
+points(14,8+2,pch=1,cex=2,col="blue")
+points(16,8+2,pch=16,cex=2,col="blue")
+
+## delta lambda
+par(mar = c(0,0.3,0,0.1))
+delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
+
+plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), ylim=c(-3,10), type="n",
+     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
+delta.positive <- delta.lambda
+delta.positive[delta.positive<0] <- 0
+delta.negative <- delta.lambda
+delta.negative[delta.negative>0] <- 0
+polygon(c(0,lambda.true$time.vec,x_events), #200
+        c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events), #200
+        c(0,delta.positive,0),col=positive.col,border=NA)
+# segments(0,0,my.xlim,0,col="gray45")
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+# model3
+########
+par(mar = c(0,0.3,1,0.1))
+mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
+                             alpha = true.object$alpha,
+                             beta = true.object$beta,
+                             events = temp.t,
+                             add = FALSE,
+                            yupper=y.ub[1],
+                            color=add.alpha("black", alpha=line.alpha[1]),
+                            line.width=line.wdth[1],
+                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
+                            title_name=paste(plot.i,"->",plot.j),
+                            title.cex = 2,
+                            box.type="n")
+drawUniMMHPIntensityPaper(object_hat,
+                          simulation = list(
+  x=state.est.latent.mmhp.new$x.hat,                                          
+  z=state.est.latent.mmhp.new$z.hat,
+  tau=temp.t,
+  lambda.max=max(lambda.m3)),
+                          yupper=y.ub,add=TRUE,
+                          color=add.alpha(model_colors[3],
+                                      alpha=line.alpha[2]),
+  line.width=line.wdth[2])
+legend(legend.x[3],legend.y[3],"C-MMHP",
+       col = model_colors[3],
+       y.intersp=0.88,x.intersp=0.1,bty = "n",
+       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+
+legend(10,legend.y[3],c("Overestimation","Underestimation"),
+       col = c(positive.col,negative.col),
+       y.intersp=0.88,x.intersp=0.5,bty = "n",
+       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)
+
+## delta lambda
+par(mar = c(0,0.3,0,0.1))
+plot(0,0,xlim=c(0,my.xlim), ylim=c(-12,8), type="n",
+     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+delta.lambda <- lambda.m3-lambda.true$lambda.t
+delta.positive <- delta.lambda
+delta.positive[delta.positive<0] <- 0
+delta.negative <- delta.lambda
+delta.negative[delta.negative>0] <- 0
+### hiding these for now
+polygon(c(0,lambda.true$time.vec,x_events), # 200 
+        c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events), # 200 
+        c(0,delta.positive,0),col=positive.col,border=NA)
+# segments(0,0,my.xlim,0,col="gray45")
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+## top
+mtext(text="M1 Sim",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
+## bottom
+mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.5)
+## left
+mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.5)
+
+```
+
+```{r process m2 for fig4b}
+plot.s <- 1#7#9
+plot.i <- 4
+plot.j <- 5
+
+cur_i <- plot.i
+cur_j <- plot.j
+
+load(paste0(m2_path,m2_files[plot.s]))
+
+temp.t <- sim_model2_data[[1]]$day_hour[ which(sim_model2_data[[1]]$start == cur_i & 
+                  sim_model2_data[[1]]$end == cur_j)]
+# temp.t <- test.mmhp$tau
+current.n <- length(temp.t)-1
+time.segment <- seq(0,tail(temp.t,1),length.out=5000)
+
+### Preprocess the model inference result
+## model 1
+#########
+model1_par_est <- list(lambda0 =
+                         mean(sim_model2_stan_sim1_total[[plot.s]]$lambda0[1001:2000]),
+                       eta_1=mean(sim_model2_stan_sim1_total[[plot.s]]$eta_1[1001:2000]),
+                       eta_2=mean(sim_model2_stan_sim1_total[[plot.s]]$eta_2[1001:2000]),
+                       eta_3=mean(sim_model2_stan_sim1_total[[plot.s]]$eta_3[1001:2000]),
+                       beta=mean(sim_model2_stan_sim1_total[[plot.s]]$beta[1001:2000]),
+                       f=apply(sim_model2_stan_sim1_total[[plot.s]]$f[1001:2000,],2,mean))
+lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
+                                                   model1_par_est$lambda0,
+                                    alpha =
+                                      model1_fn$alpha.fun(model1_par_est$f[plot.i],
+                                    model1_par_est$f[plot.j],
+                                    model1_par_est$eta_1,
+                                    model1_par_est$eta_2,
+                                    model1_par_est$eta_3),
+                                    beta=model1_par_est$beta),
+                                     events=temp.t,
+                                     time.vec=time.segment)
+
+## model2
+#############
+model2_par_est <- list(gamma=apply(sim_model2_stan_sim2_total[[plot.s]]$gamma[1001:2000,],
+                                   2,mean),
+                    zeta = 
+                      apply(sim_model2_stan_sim2_total[[plot.s]]$zeta[1001:2000,],2,mean),
+                       eta_1=mean(sim_model2_stan_sim2_total[[plot.s]]$eta_1[1001:2000]),
+                       eta_2=mean(sim_model2_stan_sim2_total[[plot.s]]$eta_2[1001:2000]),
+                       eta_3=mean(sim_model2_stan_sim2_total[[plot.s]]$eta_3[1001:2000]),
+                       beta=mean(sim_model2_stan_sim2_total[[plot.s]]$beta[1001:2000]),
+                       f=apply(sim_model2_stan_sim2_total[[plot.s]]$f[1001:2000,],2,mean))
+
+lambda.m2 <- uniHawkesIntensityNumeric(object=list(
+  lambda0=model2_par_est$gamma[plot.i]+
+          model2_par_est$zeta[plot.j],                                        
+  alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+                            model2_par_est$f[plot.j],
+                            model2_par_est$eta_1,
+                            model2_par_est$eta_2,
+                            model2_par_est$eta_3),
+                beta=model2_par_est$beta),
+                events=temp.t,
+                time.vec=time.segment)
+
+## Model3
+#############
+mmhp_par_est <- list(lambda0=mean(sim_model2_stan_sim3_total[[plot.s]]$lambda0[1001:2000]),
+                     lambda1=mean(sim_model2_stan_sim3_total[[plot.s]]$lambda1[1001:2000]),
+                     eta_1=mean(sim_model2_stan_sim3_total[[plot.s]]$eta_1[1001:2000]),
+                     eta_2=mean(sim_model2_stan_sim3_total[[plot.s]]$eta_2[1001:2000]),
+                     eta_3=mean(sim_model2_stan_sim3_total[[plot.s]]$eta_3[1001:2000]),
+                     beta=mean(sim_model2_stan_sim3_total[[plot.s]]$beta[1001:2000]),
+                     f=apply(sim_model2_stan_sim3_total[[plot.s]]$f[1001:2000,],2,mean))
+
+object_hat <- list(lambda0=mmhp_par_est$lambda0,
+                   lambda1=mmhp_par_est$lambda1,
+                   alpha=model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
+                                             mmhp_par_est$f[cur_j],
+                                             mmhp_par_est$eta_1,
+                                             mmhp_par_est$eta_2),
+                   beta=mmhp_par_est$beta,
+                   q1=model3_fn$q1.fun(mmhp_par_est$f[cur_i],
+                                       mmhp_par_est$f[cur_j],
+                                       mmhp_par_est$eta_3),
+                   q2=model3_fn$q0.fun(mmhp_par_est$f[cur_i],
+                                       mmhp_par_est$f[cur_j],
+                                       mmhp_par_est$eta_3))
+
+state_est_fits <- list.files(m2_path, pattern = "fit123_state_est_M2*")
+load(paste0(m2_path,state_est_fits[plot.s]))
+
+state.est.latent.mmhp <- interpolate_state_est_lst[plot.i,plot.j][[1]]
+state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
+                                                 termination=200)
+
+step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,
+                        2-state.est.latent.mmhp$z.hat)
+
+lambda.m3 <- mmhpIntensityNumeric(params=object_hat,
                                   t=temp.t,
-                       latent=list(x=fixStateTransition(test.mmhp)$x,
-                              z=fixStateTransition(test.mmhp)$z),
-                              time.vec=time.segment)
+                                  time.vec=time.segment,
+                                  latent.vec=step.fun.est(time.segment))
+
+object_true <- lapply(object_matrix,function(x) x[plot.i,plot.j])
+names(object_true) <- c("lambda0","lambda1","alpha","beta")
+
+lambda.true <- uniHawkesIntensityNumeric(object = object_true,
+                                        events =temp.t,
+                                        time.vec = time.segment)
+```
+
+```{r fig 4b M2 sim}
+source(here("lib","mod_drawHawkesIntensityPaper.R"))
+y.ub <- c(17,17,17)#c(130,72,31)
+x_events <- 135#150
+#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
+model_colors <- viridis::viridis(3)
+layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
+layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
+my.xlim <- 140#160#200#130
+my.long.x <- 140#205#134.5
+legend.x <- c(50,50,50)#c(135,135,135)
+legend.y <- #c(34,32,32)
+legend.y <- c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.cex <- 1.5 #3
+line.alpha <- c(0.9,0.6)
+line.wdth <- c(2,2.5)
+negative.col <- add.alpha('lightskyblue',0.6)
+positive.col <- add.alpha('tomato',0.6)
+#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
+#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
+par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
+    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)
+
+# model1
+############
+true.object <- object_true
+# lambda.true$lambda.t <- lambda.est
+# lambda.true$time.vec <- lambda.m1$time.vec
+
+mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
+                             alpha = true.object$alpha,
+                             beta = true.object$beta,
+                             events = temp.t,
+                             add = FALSE,
+                            yupper=y.ub[1],
+                            color=add.alpha("black", alpha=line.alpha[1]),
+                            line.width=line.wdth[1],
+                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
+                            title_name=paste(plot.i,"->",plot.j),
+                            title.cex = 2,
+                            box.type="n")
+drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
+                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
+                                                   model1_par_est$f[plot.j],
+                                                   model1_par_est$eta_1,
+                                                   model1_par_est$eta_2,
+                                                   model1_par_est$eta_3),
+                         beta=model1_par_est$beta,
+                         events=temp.t,
+                         color=add.alpha(model_colors[1],
+                                         alpha=line.alpha[2]),
+                         line.width=line.wdth[2])
+
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+
+legend(legend.x[1],legend.y[1],c("True"),
+       col = c("black"),
+       y.intersp=0.88,x.intersp=0.15,bty = "n",
+       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
+legend(legend.x[1]+18,legend.y[1],c("C-HP"),
+       col = c(model_colors[1]),
+       y.intersp=0.88,x.intersp=0.15,bty = "n",
+       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
+
+## delta lambda
+par(mar = c(0,0.3,0,0.1))
+plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,10), type="n",
+     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
+delta.positive <- delta.lambda
+delta.positive[delta.positive<0] <- 0
+delta.negative <- delta.lambda
+delta.negative[delta.negative>0] <- 0
+### hiding these for now ###
+polygon(c(0,lambda.true$time.vec,x_events),#200
+        c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events),#200
+        c(0,delta.positive,0),col=positive.col,border=NA)
+
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+# model2
+############
+mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
+                             alpha = true.object$alpha,
+                             beta = true.object$beta,
+                             events = temp.t,
+                             add = FALSE,
+                            yupper=y.ub[1],
+                            color=add.alpha("black", alpha=line.alpha[1]),
+                            line.width=line.wdth[1],
+                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
+                            title_name=paste(plot.i,"->",plot.j),
+                            title.cex = 2,
+                            box.type="n")
+drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
+                           model2_par_est$zeta[plot.j],
+                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+                                                   model2_par_est$f[plot.j],
+                                                   model2_par_est$eta_1,
+                                                   model2_par_est$eta_2,
+                                                   model2_par_est$eta_3),
+                         beta=model2_par_est$beta,
+                         events=temp.t,
+                         color=add.alpha(model_colors[2],
+                                         alpha=line.alpha[2]),
+                         line.width=line.wdth[2])
+legend(legend.x[2],legend.y[2],"C-DCHP",
+       col = model_colors[2],
+       y.intersp=0.88,x.intersp=0.1,bty = "n",
+       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)
+
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+
+legend(10,legend.y[2]+2,c("State 0/1 events","State change point"),
+       col = c(NA,"red"),
+       y.intersp=0.85,x.intersp=-0.1, bty = "n",
+       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
+       lty = c(NA,NA), lwd=c(NA,4))
+points(14,8+2,pch=1,cex=2,col="blue")
+points(16,8+2,pch=16,cex=2,col="blue")
+
+## delta lambda
+par(mar = c(0,0.3,0,0.1))
+delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
+
+plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), ylim=c(-3,10), type="n",
+     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
+delta.positive <- delta.lambda
+delta.positive[delta.positive<0] <- 0
+delta.negative <- delta.lambda
+delta.negative[delta.negative>0] <- 0
+polygon(c(0,lambda.true$time.vec,x_events), #200
+        c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events), #200
+        c(0,delta.positive,0),col=positive.col,border=NA)
+# segments(0,0,my.xlim,0,col="gray45")
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+# model3
+########
+par(mar = c(0,0.3,1,0.1))
+mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
+                             alpha = true.object$alpha,
+                             beta = true.object$beta,
+                             events = temp.t,
+                             add = FALSE,
+                            yupper=y.ub[1],
+                            color=add.alpha("black", alpha=line.alpha[1]),
+                            line.width=line.wdth[1],
+                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
+                            title_name=paste(plot.i,"->",plot.j),
+                            title.cex = 2,
+                            box.type="n")
+drawUniMMHPIntensityPaper(object_hat,
+                          simulation = list(
+  x=state.est.latent.mmhp.new$x.hat,                                          
+  z=state.est.latent.mmhp.new$z.hat,
+  tau=temp.t,
+  lambda.max=max(lambda.m3)),
+                          yupper=y.ub,add=TRUE,
+                          color=add.alpha(model_colors[3],
+                                      alpha=line.alpha[2]),
+  line.width=line.wdth[2])
+legend(legend.x[3],legend.y[3],"C-MMHP",
+       col = model_colors[3],
+       y.intersp=0.88,x.intersp=0.1,bty = "n",
+       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+
+legend(10,legend.y[3],c("Overestimation","Underestimation"),
+       col = c(positive.col,negative.col),
+       y.intersp=0.88,x.intersp=0.5,bty = "n",
+       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)
+
+## delta lambda
+par(mar = c(0,0.3,0,0.1))
+plot(0,0,xlim=c(0,my.xlim), ylim=c(-12,8), type="n",
+     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+delta.lambda <- lambda.m3-lambda.true$lambda.t
+delta.positive <- delta.lambda
+delta.positive[delta.positive<0] <- 0
+delta.negative <- delta.lambda
+delta.negative[delta.negative>0] <- 0
+### hiding these for now
+polygon(c(0,lambda.true$time.vec,x_events), # 200 
+        c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events), # 200 
+        c(0,delta.positive,0),col=positive.col,border=NA)
+# segments(0,0,my.xlim,0,col="gray45")
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+## top
+mtext(text="M2 Sim",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
+## bottom
+mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.5)
+## left
+mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.5)
+
 ```

### 2020-11-17 output_scripts/Paper_Plots.Rmd
add frob norm and structure score plots

@@
 library(viridis)
+library(here)
 library(compete)
@@
 
+```{r fig-matrix-structure-score}
+library(NMF)
+source(here("lib","residualStructureScore.R"))
+
+struct_scores <- tibble()
+for(current_cohort in 1:10) {
+  m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                   "/chp_pr_matrix_",cohort_names[current_cohort],
+                   ".RDS",sep=''))
+  ##
+  ## remove animals which are never fought or don't ever fight
+  prob_row <- which(rowSums(m1_pr) == 0)
+  prob_col <- which(colSums(m1_pr) == 0)
+  prob_id <- NA
+  prob_id <- c(prob_row,prob_col)
+  # print(prob_id)
+  if(length(prob_id) != 0) {
+    m1_pr <- m1_pr[-prob_id,-prob_id]
+  }
+
+  ##
+  m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                       "/dchp_pr_matrix_",cohort_names[current_cohort],
+                       ".RDS",sep=''))
+  if(length(prob_id) != 0) {
+    m2_pr <- m2_pr[-prob_id,-prob_id]
+  }
+
+  m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
+                       ".RDS",sep=''))
+  if(length(prob_id) != 0) {
+    m3_pr <- m3_pr[-prob_id,-prob_id]
+  }
+  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
+                       "/immhp_pr_matrix_",cohort_names[current_cohort],
+                       ".RDS",sep=''))
+  print(range(as.vector(indep_pr)))
+  if(length(prob_id) != 0) {
+    indep_pr <- indep_pr[-prob_id,-prob_id]
+  }
+  if(current_cohort == 10) {
+    # one additional row
+    # print("in here")
+    new_prob_row <- which(rowSums(m1_pr) == 0)
+    new_prob_col <- which(colSums(m1_pr) == 0)
+    prob_id <- c(new_prob_row,new_prob_col) 
+    if(length(prob_id) != 0) {
+      m1_pr <- m1_pr[-prob_id, -prob_id]
+      m2_pr <- m2_pr[-prob_id, -prob_id]
+      m3_pr <- m3_pr[-prob_id, -prob_id]
+      indep_pr <- indep_pr[-prob_id, -prob_id]
+    }
+  }
+
+  m1_score <-positiveNegativeApproxError(m1_pr)
+  m2_score <- positiveNegativeApproxError(m2_pr)
+  m3_score <- positiveNegativeApproxError(m3_pr) ## smallest value which is good
+  ind_score <- positiveNegativeApproxError(indep_pr) 
+  ## this doesn't make sense because all negative
+  ## values
+  current_score <- tibble(m1_score, m2_score, m3_score, ind_score)
+  names(current_score) <- c("C-HP","C-DCHP","C-MMHP","I-MMHP")
+  current_score$type <- c("Positive","Negative")
+  current_score$Cohort <- current_cohort
+  struct_scores <-struct_scores %>% bind_rows(current_score)
+}
+
+struct_scores %>% 
+  rename(Pos_Neg = type) %>%
+  pivot_longer(cols = "C-HP":"I-MMHP",
+               names_to = "Method", values_to = "Score") %>%
+  filter(Score > 0) %>%
+  filter(!(Method == "ind_score" & Pos_Neg == "Positive")) %>%
+  ggplot(aes(Method,Score)) + geom_boxplot() +
+  facet_wrap(~Pos_Neg) + theme_minimal()
+
+```
+
 ```{r fig_pr_slides, fig.height=3, fig.width=7, include=slides_plots,eval=slides_plots}
@@
 load("../output/plot_N_predict.RData")
-# current_cohort <- 5# cohort 1 looks worse than rest
+current_cohort <- 5# cohort 1 looks worse than rest
 
@@
 load("../output/plot_rank_predict.RData")
-# current_cohort <- 5
+current_cohort <- 5
 temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
@@
 
-# current_cohort <- 5
+current_cohort <- 5
 

### 2020-11-17 output_scripts/rank_recovery.Rmd
adding plots for fig 4 repeated with data simulated from m1 and m2
add frob norm and structure score plots

@@
 ```{r load in sims, options}
-sim_files <- list.files(here("output","rank_sims","sims_m3_dc_isi"))
+sim_files <- list.files(here("output", "rank_sims",
+                             "sims_m3_dc_isi"))
 
@@
   count() %>%
-  mutate(per = n/20) %>%
+  mutate(per = n/50) %>%
   arrange(-per)
@@
 ```{r analyse sims}
-sim_files <- list.files(here("output","rank_sims","sims_m3_dc_isi"))
+sim_files <- list.files(here("output", "rank_sims",
+                             "sims_m3_dc_isi_sparse"))
 
@@
 How does this compare to the optimal score using only the test data.
+They agree in this instance.
 ```{r fit isi to test}

### 2020-11-17 run_scripts/isi_predict.R

@@ -118,6 +118,13 @@ compute_isi_score <- function(win_loss_matrix, curr_ranking) {
   list(I_score = I, SI_score = SI)
 }
 
+frob_norm <- function(win_loss_matrix, curr_ranking, best_wl) {
+  norm( win_loss_matrix[curr_ranking,curr_ranking] - best_wl,
+        type = "F" )
+}
+
+frob_scores <- tibble()
+
 # Define the cohorts will be fitted
 fit_cohorts <- c(1:10)
 naive_rank_10 <- list()
@@ -214,23 +221,32 @@ for(current_cohort in 1:10) {
   # correctly for reordering the wl matrix?
   
   ###
-  ## do I want order here?
   ###
-  scores <- est_ranks %>% map_dfr(~ compute_isi_score(test_wl, .x))
+  ###
+  
+  ## compute_frob_norm
+  frob_scores <- frob_scores %>%
+    bind_rows(est_ranks %>% map_dfr( ~ frob_norm(test_wl, .x, 
+                                     best_wl = best_isi$best_matrix)))
   
   
-  scores$model <- c("isi","agg", "glicko", "m1","m2","m3")
+  scores <- est_ranks %>% map_dfr(~ compute_isi_score(test_wl, .x),
+                                  .id = "GROUP") %>%
+    rename(model = GROUP)
+  
+  
+  # scores$model <- c("isi","agg", "glicko", "m1","m2","m3")
   scores <- scores %>% add_row(tibble_row(I_score = best_isi$I, 
                                SI_score = best_isi$SI,
                                model = "test_isi"))
   
-  saveRDS(scores, file = here("output", "rank_sims", "predict_isi",
-                              paste0(current_cohort, ".RDS")))
+  # saveRDS(scores, file = here("output", "rank_sims", "predict_isi",
+                              # paste0(current_cohort, ".RDS")))
   
 }
 
 
-## then read all these
+## then read all these ####
 
 sim_files <- list.files(here("output","rank_sims","predict_isi"))
 
@@ -250,3 +266,12 @@ cohort_scores %>%
   mutate(ISI = I_score + SI_score) %>%
   ggplot(aes(model,ISI)) + geom_boxplot()
 
+
+
+### look at frob norms ####
+colnames(frob_scores) <- c("ISI", "Agg", "Glicko",
+                           "M1", "M2", "M3")
+frob_scores %>% rowid_to_column(var = "Cohort") %>%
[…]

### 2020-11-17 output_scripts/Paper_Plots.Rmd
correct typo in glicko ranks and begin creating plot for this

@@
 
+# Figure 5b: Simulation Spearman Rank
+
 # Figure 6: Latent Rank Cohort comparison
@@
                        ".RDS",sep=''))
-  print(range(as.vector(indep_pr)))
+  # print(range(as.vector(indep_pr)))
   if(length(prob_id) != 0) {
@@
   names(current_score) <- c("C-HP","C-DCHP","C-MMHP","I-MMHP")
-  current_score$type <- c("Positive","Negative")
+  current_score$type <- c("Positive Residuals","Negative Residuals")
   current_score$Cohort <- current_cohort
@@
 
-struct_scores %>% 
+struct_plot <- struct_scores %>% 
   rename(Pos_Neg = type) %>%
@@
   filter(Score > 0) %>%
-  filter(!(Method == "ind_score" & Pos_Neg == "Positive")) %>%
+  filter(!(Method == "I-MMHP" & Pos_Neg == "Positive"))
+  # mutate(Method = as.factor(Method, levels = c("I-MMHP","C-HP","C-DCHP",
+  #                                              "C-MMHP"))) %>%
+struct_plot$Method <- factor(struct_plot$Method, levels = c("I-MMHP","C-HP","C-DCHP",
+                                               "C-MMHP") )
+
+struct_plot %>% 
   ggplot(aes(Method,Score)) + geom_boxplot() +
-  facet_wrap(~Pos_Neg) + theme_minimal()
+  facet_wrap(~Pos_Neg, scales = "free") + theme_minimal()
 

### 2020-11-17 run_scripts/sim_rank_isi.R

@@ -14,6 +14,7 @@ library(here)
 library(tidyverse)
 library(rstan)
 library(compete)
+library(PlayerRatings)
 
 options(mc.cores = parallel::detectCores())
 
@@ -187,13 +188,42 @@ isi_dc.out <- compete::isi98(m = count_data_dc, random = TRUE)
 isi_rank_dc <- as.numeric(rev(isi_dc.out$best_order)) 
 
 
+### compute agg ranking ####
+agg_rank_data <- clean_sim_data_dc$N_count
+agg_rank_model <- stan_model(here("lib","latent_rank_agg_sim.stan"))
+
+agg_rank_fit <- rstan::sampling(agg_rank_model,
+                                data = list(n = 5,
+                                            n_matrix = agg_rank_data),
+                                      iter = 1000,
+                                      chains = 4)
+agg_sims <- rstan::extract(agg_rank_fit)
+
+agg_rank <- order(apply(agg_sims$x, 2, mean))
+
+### glicko ranking also ####
+glicko_data <- tibble(start = clean_sim_data_dc$start,
+                      end = clean_sim_data_dc$end)
+
+glicko_data <- glicko_data %>%
+  mutate(id = row_number(), score = 1) %>%
+  select(id, start, end, score)
+
+gl_train <- my_glicko(glicko_data, history=TRUE, cval=2)
+
+gl_train
+
+gl_ranks <- order(gl_train$ratings$Rating)
+
 ## then save these
 
 output_rank <- tibble(truth = 1:5, 
                       m1 = m1_rank,
                       m2 = m2_rank,
                       m3_dc = m3_dc_rank,
-                      isi = isi_rank_dc, 
+                      isi = isi_rank_dc,
+                      agg = agg_rank,
+                      glicko = gl_ranks,
                       sim = rep(sim_id,5))
 
 dir.create(data_path, recursive = TRUE, showWarnings = FALSE)

### 2020-11-18 output_scripts/Paper_Plots.Rmd
add figure 5b sim spearman rank and attempt to modify plot 8b to be clearer

@@
 # Figure 5b: Simulation Spearman Rank
+```{r fig-5b-spearman-sim}
+sim_files <- list.files(here("output", "rank_sims",
+                             "sims_m3_dc_isi_sparse"))
+
+all_sims <- list()
+for(i in seq_along(sim_files)) {
+ single_fit <- readRDS(here("output", "rank_sims", 
+                            "sims_m3_dc_isi_sparse",
+                            sim_files[i]))
+ all_sims[[i]] <- single_fit
+}
+
+spear <- function(sim_data) {
+  truth <- sim_data$truth
+  sim_data %>%
+    select(m1:glicko) %>%
+    map( ~cor.test(truth, .x,
+                   method = "spearman")$estimate  ) %>%
+    enframe() %>%
+    unnest(cols = c(value))
+}
+
+sim_data <- map_dfr(all_sims, spear)
+
+name <- sim_data$name
+
+sim_data$name <- case_when(
+          name == "isi" ~ "I&SI",
+          name == "m1" ~ "C-HP",
+          name == "m2" ~ "C-DCHP",
+          name == "m3_dc" ~ "C-MMHP",
+          name == "agg" ~ "AggRank",
+          name == "glicko" ~ "Glicko")
+
+sim_data$name <- factor(sim_data$name, levels = c("I&SI",
+                                                  "AggRank",
+                                                  "Glicko",
+                                                  "C-HP",
+                                                  "C-DCHP",
+                                                  "C-MMHP"))
+
+sim_data %>% 
+  rename(Method = name, corr = value) %>%
+  ggplot(aes(Method,corr)) + geom_boxplot(aes(fill = Method)) +
+  scale_fill_manual(values = viridis::viridis(6)) +
+  labs(y = "Rank Correlation") + theme_bw()
+```
 
@@
 p4 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
-  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
+  geom_line(aes(linetype = method),
+            size=1.2, alpha=0.8, position=position_dodge(0.2)) +
   geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                  position=position_dodge(0.2)) +
-  scale_color_manual(values = viridis::viridis(5)) + 
+  scale_color_manual(values = viridis::viridis(5)[1:5]) + 
   ggtitle("(b)") +
@@
   coord_cartesian(ylim=c(2.5,57.5)) + 
-  guides(color=guide_legend(title="Model")) 
+  guides(color=guide_legend(title="Model")) +
+  guides(linetype = FALSE)
 p4

### 2020-11-18 output_scripts/rank_recovery.Rmd
correct typo in glicko ranks and begin creating plot for this
small change to compare more methods

@@
  single_fit <- readRDS(here("output", "rank_sims", 
-                            "sims_m3_dc_isi",
+                            "sims_m3_dc_isi_sparse",
                             sim_files[i]))
@@
   sim_data %>%
-    select(m1:isi) %>%
+    select(m1:glicko) %>%
     map( ~cor.test(truth, .x,
@@
           name == "m2" ~ "C-DCHP",
-          name == "m3_dc" ~ "C-MMHP")
+          name == "m3_dc" ~ "C-MMHP",
+          name == "agg" ~ "AggRank",
+          name == "glicko" ~ "Glicko")
 
-sim_data$name <- factor(sim_data$name, levels = c("I&SI","C-HP",
-                                                  "C-DCHP", "C-MMHP"))
+sim_data$name <- factor(sim_data$name, levels = c("I&SI",
+                                                  "AggRank",
+                                                  "Glicko",
+                                                  "C-HP",
+                                                  "C-DCHP",
+                                                  "C-MMHP"))
 
@@
 
-gl_ranks <- rev(gl_train$ratings$Player)
+gl_ranks <- rev(gl_train$ratings$Rating)
 # highest to lowest

### 2020-11-18 output_scripts/Paper_Plots.Rmd
improving plots

@@
 current_cohort <- 5
-```
-
-```{r load_packages, include=FALSE}
 
@@
 ## Figure 4a Recover Latent Ranks
-```{r fig-4a}
+```{r fig-4a, fig.height=4,fig.width=8}
 sim_data_path <- "../output/sims/sims_m3_dc/"
@@
         at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
-        cex=2.4)
-  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.7,
+        cex=2)
+  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.25,
         at=0.5)
   ## top
-  mtext(text="(a)", side=3, line=0, outer=TRUE, cex=3,
+  mtext(text="(a)", side=3, line=0, outer=TRUE, cex=2.5,
         at=0.5, font=2)
@@
         at=c(0:2)/3+0.15,
-        cex=2, las=2)
+        cex=1.75, las=2)
 }
@@
 
-```{r fig4b-recover-latent-states}
+```{r fig4b-recover-latent-states,fig.width=8,fig.height=4}
 y.ub <- c(17,17,17)#c(130,72,31)
@@
 ## bottom
-mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.5)
+mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.25)
 ## left
-mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.5)
+mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.25)
 ```
@@
 #load("../output/sim_model3_fit123_residuals.RData")
-par(mfrow=c(5,5),mar=rep(0.2,4),oma=c(2.4,2.4,0.5,0.5))
+par(mfrow=c(5,5),mar=c(0.2,0.2,0.2,0.2),oma=c(2.4,2.4,2.9,0.5))
 for(i in c(5:1)){
@@
       at=c(0:4)/5+0.1)
+mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)
 
@@
 # Figure 5b: Simulation Spearman Rank
-```{r fig-5b-spearman-sim}
+```{r fig-5b-spearman-sim, fig.height=7}
 sim_files <- list.files(here("output", "rank_sims",
@@
   scale_fill_manual(values = viridis::viridis(6)) +
-  labs(y = "Rank Correlation") + theme_bw()
+  labs(y = "Rank Correlation") + theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.position="right") + ggtitle("(b)")
 ```
@@
 
-```{r fig-8a-frob-norm-cohort5}
+```{r fig-8a-frob-norm-cohort5, fig.width=8,fig.height=4}
 load("../output/plot_N_predict.RData")
@@
   #mutate(norm = min(norm,60)) %>%
+  # rename(Method = method) %>%
   ggplot( aes(x = method, y = norm, fill = method)) +
@@
   NULL
-p3
+p3 + labs(fill = "Method")
 ```
@@
 
-```{r fig-8b-frob-norm-all-cohorts}
+```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4}
 load("../output/plot_N_predict.RData")

### 2020-11-24 output_scripts/Paper_Plots.Rmd
update plots to deal with pair wise intensities

@@
 
-load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
-load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
+# load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
+# load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
+#### need to edit here to account for separate files now
+
+m3_files <- list.files(sim_data_path, pattern = "sim_model3_fit*")
+#m1_files
+
+# load(paste0(m1_path,m1_files[1]))
+sim_model3_stan_sim1_total <- list()
+sim_model3_stan_sim2_total <- list()
+sim_model3_stan_sim3_total <- list()
+
+for(i in seq_along(m3_files)) {
+  load(paste0(sim_data_path,m3_files[i]))
+  sim_model3_stan_sim1_total[[i]] <- sim_model3_stan_sim1
+  sim_model3_stan_sim2_total[[i]] <- sim_model3_stan_sim2
+  sim_model3_stan_sim3_total[[i]] <- sim_model3_stan_sim3
+
+}
 
@@
     ## Posterior density
-    current_result <- eval(parse(text=paste("sim_model3_stan_sim",m,sep="")))
+    # current_result <- eval(parse(text=paste("sim_model3_stan_sim",m,sep="")))
+    current_result <- eval(parse(text=paste("sim_model3_stan_sim",
+                                            m,
+                                            "_total",
+                                            sep="")))
     for(i in c(1:n_sim)){
-      lines(density(current_result[[i]]$f[1001:2000,j]),
+      lines(density(current_result[[i]]$f[,j]),
             col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
@@
 
-test.mmhp <- sim_model3_data[plot.s][[1]]$mmhp_matrix[plot.i,plot.j][[1]]
+load(paste0(sim_data_path, "sim_model3_",
+                               plot.s,
+                              ".RData"))
+test.mmhp <- sim_model3_data$mmhp_matrix[plot.i,plot.j][[1]]
 temp.t <- test.mmhp$tau
 current.n <- length(temp.t)-1
-time.segment <- seq(0,tail(temp.t,1),length.out=5000)
+time.segment <- seq(0, tail(temp.t,1), length.out = 5000)
 
@@
 #########
-model1_par_est <- list(lambda0 =
-                         mean(sim_model3_stan_sim1[[plot.s]]$lambda0[1001:2000]),
-                       eta_1=mean(sim_model3_stan_sim1[[plot.s]]$eta_1[1001:2000]),
-                       eta_2=mean(sim_model3_stan_sim1[[plot.s]]$eta_2[1001:2000]),
-                       eta_3=mean(sim_model3_stan_sim1[[plot.s]]$eta_3[1001:2000]),
-                       beta=mean(sim_model3_stan_sim1[[plot.s]]$beta[1001:2000]),
-                       f=apply(sim_model3_stan_sim1[[plot.s]]$f[1001:2000,],2,mean))
-lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
+model1_par_est <- list(lambda0 = mean(sim_model3_stan_sim1_total[[plot.s]]$lambda0),
+                       eta_1 = mean(sim_model3_stan_sim1_total[[plot.s]]$eta_1),
+                       eta_2 = mean(sim_model3_stan_sim1_total[[plot.s]]$eta_2),
+                       eta_3 = mean(sim_model3_stan_sim1_total[[plot.s]]$eta_3),
+                       beta = mean(sim_model3_stan_sim1_total[[plot.s]]$beta),
+                       f = apply(sim_model3_stan_sim1_total[[plot.s]]$f, 2, mean))
+lambda.m1<-uniHawkesIntensityNumeric(object = list(lambda0 = 
                                                    model1_par_est$lambda0,
@@
                                     model1_par_est$eta_3),
-                                    beta=model1_par_est$beta),
-                                     events=temp.t,
-                                     time.vec=time.segment)
+                                    beta = model1_par_est$beta),
+                                     events = temp.t,
+                                     time.vec = time.segment)
 
@@
 #############
-model2_par_est <- list(gamma=apply(sim_model3_stan_sim2[[plot.s]]$gamma[1001:2000,],
-                                   2,mean),
-                    zeta = 
-                      apply(sim_model3_stan_sim2[[plot.s]]$zeta[1001:2000,],2,mean),
-                       eta_1=mean(sim_model3_stan_sim2[[plot.s]]$eta_1[1001:2000]),
-                       eta_2=mean(sim_model3_stan_sim2[[plot.s]]$eta_2[1001:2000]),
-                       eta_3=mean(sim_model3_stan_sim2[[plot.s]]$eta_3[1001:2000]),
-                       beta=mean(sim_model3_stan_sim2[[plot.s]]$beta[1001:2000]),
-                       f=apply(sim_model3_stan_sim2[[plot.s]]$f[1001:2000,],2,mean))
+model2_par_est <- list(gamma = apply(sim_model3_stan_sim2_total[[plot.s]]$gamma,
+                                     2, mean),
+                    zeta = apply(sim_model3_stan_sim2_total[[plot.s]]$zeta, 2, mean),
+                    eta_1 = mean(sim_model3_stan_sim2_total[[plot.s]]$eta_1),
+                    eta_2 = mean(sim_model3_stan_sim2_total[[plot.s]]$eta_2),
+                    eta_3 = mean(sim_model3_stan_sim2_total[[plot.s]]$eta_3),
+                    beta = mean(sim_model3_stan_sim2_total[[plot.s]]$beta),
+                    f = apply(sim_model3_stan_sim2_total[[plot.s]]$f, 2, mean))
 
 lambda.m2 <- uniHawkesIntensityNumeric(object=list(
-  lambda0=model2_par_est$gamma[plot.i]+
+  lambda0 = model2_par_est$gamma[plot.i]+
           model2_par_est$zeta[plot.j],                                        
-  alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+  alpha = model1_fn$alpha.fun(model2_par_est$f[plot.i],
                             model2_par_est$f[plot.j],
@@
                             model2_par_est$eta_3),
-                beta=model2_par_est$beta),
-                events=temp.t,
-                time.vec=time.segment)
+                beta = model2_par_est$beta),
+                events = temp.t,
+                time.vec = time.segment)
 
 ## Model3
+###
+lam0_vec <- apply(sim_model3_stan_sim3_total[[plot.s]]$lambda0, 2, mean)
+lam1_vec <- apply(sim_model3_stan_sim3_total[[plot.s]]$lambda1, 2, mean)
+lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
+                       ncol = length(object_par$f_vec_1))
+lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
+                       ncol = length(object_par$f_vec_1))
+
+clean_sim_data <- cleanSimulationData(raw_data = sim_model3_data, 
+                                      cut_off = cut_off,
+                                      N = length(object_par$f_vec_1))
+
+for(i in seq_along(lam0_vec)) {
+  row_id <- clean_sim_data$I_fit[i]
+  col_id <- clean_sim_data$J_fit[i]
+  lam0_par_est[row_id, col_id] <- lam0_vec[i]
+  lam1_par_est[row_id, col_id] <- lam1_vec[i]
+}
+
+###
+
 #############
-mmhp_par_est <- list(lambda0=mean(sim_model3_stan_sim3[[plot.s]]$lambda0[1001:2000]),
-                     lambda1=mean(sim_model3_stan_sim3[[plot.s]]$lambda1[1001:2000]),
-                     eta_1=mean(sim_model3_stan_sim3[[plot.s]]$eta_1[1001:2000]),
-                     eta_2=mean(sim_model3_stan_sim3[[plot.s]]$eta_2[1001:2000]),
-                     eta_3=mean(sim_model3_stan_sim3[[plot.s]]$eta_3[1001:2000]),
-                     beta=mean(sim_model3_stan_sim3[[plot.s]]$beta[1001:2000]),
-                     f=apply(sim_model3_stan_sim3[[plot.s]]$f[1001:2000,],2,mean))
-
-object_hat <- list(lambda0=mmhp_par_est$lambda0,
-                   lambda1=mmhp_par_est$lambda1,
-                   alpha=model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
+mmhp_par_est <- list(lambda0 = lam0_par_est,
+                     lambda1 = lam1_par_est,
+                     eta_1 = mean(sim_model3_stan_sim3_total[[plot.s]]$eta_1),
+                     eta_2 = mean(sim_model3_stan_sim3_total[[plot.s]]$eta_2),
+                     eta_3 = mean(sim_model3_stan_sim3_total[[plot.s]]$eta_3),
+                     beta = mean(sim_model3_stan_sim3_total[[plot.s]]$beta),
+                     f = apply(sim_model3_stan_sim3_total[[plot.s]]$f,2,mean))
+
+object_hat <- list(lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
+                   lambda1 = mmhp_par_est$lambda1[cur_i, cur_j],
+                   alpha = model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
                                              mmhp_par_est$f[cur_j],
@@
                                              mmhp_par_est$eta_2),
-                   beta=mmhp_par_est$beta,
-                   q1=model3_fn$q1.fun(mmhp_par_est$f[cur_i],
+                   beta = mmhp_par_est$beta,
+                   q1 = model3_fn$q1.fun(mmhp_par_est$f[cur_i],
                                        mmhp_par_est$f[cur_j],
@@
 
-state.est.latent.mmhp <- interpolate_state_est_lst[[plot.s]][plot.i,plot.j][[1]]
+## then need to load in the state estimate here
+load(paste0(sim_data_path, "fit123_state_est_", plot.s, ".RData"))
+
+state.est.latent.mmhp <- interpolate_state_est_lst[plot.i,plot.j][[1]]
 state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
@@
 step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,
-                        2-state.est.latent.mmhp$z.hat)
-
-lambda.m3 <- mmhpIntensityNumeric(params=object_hat,
-                                  t=temp.t[-1],
-                                  time.vec=time.segment,
-                                  latent.vec=step.fun.est(time.segment))
+                        2 - state.est.latent.mmhp$z.hat)
+
+lambda.m3 <- mmhpIntensityNumeric(params = object_hat,
+                                  t = temp.t[-1],
+                                  time.vec = time.segment,
+                                  latent.vec = step.fun.est(time.segment))
 
@@
 
-lambda.true <- mmhpTrueIntensityNumeric(params=object_true,
-                                        t=temp.t,
-                       latent=list(x=fixStateTransition(test.mmhp)$x,
-                              z=fixStateTransition(test.mmhp)$z),
-                              time.vec=time.segment)
+lambda.true <- mmhpTrueIntensityNumeric(params = object_true,
+                                        t = temp.t,
+                       latent = list(x = fixStateTransition(test.mmhp)$x,
+                                     z = fixStateTransition(test.mmhp)$z),
+                                     time.vec = time.segment)
 
@@
 ```{r fig4b-recover-latent-states,fig.width=8,fig.height=4}
-y.ub <- c(17,17,17)#c(130,72,31)
+y.ub <- c(3,3,3)#c(130,72,31)
 x_events <- 135#150
@@
 my.long.x <- 140#205#134.5
-legend.x <- c(50,50,50)#c(135,135,135)
+legend.x <- c(30,30,30)#c(135,135,135)
 legend.y <- #c(34,32,32)
-legend.y <- c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.y <- c(2.5,2,2)#c(15,12,15)#c(62,37,18)#c(22,22,22)
 legend.cex <- 1.5 #3
@@
 
-legend(10,legend.y[2]+2,c("State 0/1 events","State change point"),
+legend(legend.x[2]-20,
+       legend.y[2]+2,c("State 0/1 events","State change point"),
        col = c(NA,"red"),
@@
 
-legend(10,legend.y[3],c("Overestimation","Underestimation"),
+legend(legend.x[1]-20,legend.y[3],c("Overestimation","Underestimation"),
        col = c(positive.col,negative.col),
@@
     for(i in c(1:n_sim)){
-      lines(density(current_result[[i]]$f[1001:2000,j]),
+      lines(density(current_result[[i]]$f[,j]),
             col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
@@
 load(paste0(m1_path,m1_files[plot.s]))
+clean_sim_data_m1 <- cleanSimulationData(raw_data = sim_model1_data[[1]], 
+                                      cut_off = cut_off,
+                                      N = length(object_par$f_vec_1))
+# this loads in sim data too
 
@@
 model1_par_est <- list(lambda0 = 
-                         mean(sim_model1_stan_sim1_total[[plot.s]]$lambda0[1001:2000]),
-                       eta_1=mean(sim_model1_stan_sim1_total[[plot.s]]$eta_1[1001:2000]),
-                       eta_2=mean(sim_model1_stan_sim1_total[[plot.s]]$eta_2[1001:2000]),
-                       eta_3=mean(sim_model1_stan_sim1_total[[plot.s]]$eta_3[1001:2000]),
-                       beta=mean(sim_model1_stan_sim1_total[[plot.s]]$beta[1001:2000]),
-                       f=apply(sim_model1_stan_sim1_total[[plot.s]]$f[1001:2000,],2,mean))
+                         mean(sim_model1_stan_sim1_total[[plot.s]]$lambda0),
+                   eta_1 = mean(sim_model1_stan_sim1_total[[plot.s]]$eta_1),
+                   eta_2 = mean(sim_model1_stan_sim1_total[[plot.s]]$eta_2),
+                   eta_3 = mean(sim_model1_stan_sim1_total[[plot.s]]$eta_3),
+                   beta = mean(sim_model1_stan_sim1_total[[plot.s]]$beta),
+                   f = apply(sim_model1_stan_sim1_total[[plot.s]]$f,2,mean))
 lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
@@
 #############
-model2_par_est <- list(gamma=apply(sim_model1_stan_sim2_total[[plot.s]]$gamma[1001:2000,],
+model2_par_est <- list(gamma = apply(sim_model1_stan_sim2_total[[plot.s]]$gamma,
                                    2,mean),
-                    zeta = 
-                      apply(sim_model1_stan_sim2_total[[plot.s]]$zeta[1001:2000,],2,mean),
-                       eta_1=mean(sim_model1_stan_sim2_total[[plot.s]]$eta_1[1001:2000]),
-                       eta_2=mean(sim_model1_stan_sim2_total[[plot.s]]$eta_2[1001:2000]),
-                       eta_3=mean(sim_model1_stan_sim2_total[[plot.s]]$eta_3[1001:2000]),
-                       beta=mean(sim_model1_stan_sim2_total[[plot.s]]$beta[1001:2000]),
-                       f=apply(sim_model1_stan_sim2_total[[plot.s]]$f[1001:2000,],2,mean))
+                       zeta = apply(sim_model1_stan_sim2_total[[plot.s]]$zeta,
+                                  2, mean),
+                     eta_1 = mean(sim_model1_stan_sim2_total[[plot.s]]$eta_1),
+                     eta_2 = mean(sim_model1_stan_sim2_total[[plot.s]]$eta_2),
+                     eta_3 = mean(sim_model1_stan_sim2_total[[plot.s]]$eta_3),
+                     beta = mean(sim_model1_stan_sim2_total[[plot.s]]$beta),
+                     f = apply(sim_model1_stan_sim2_total[[plot.s]]$f, 
+                             2, mean))
 
@@
 #############
-mmhp_par_est <- list(lambda0=mean(sim_model1_stan_sim3_total[[plot.s]]$lambda0[1001:2000]),
-                     lambda1=mean(sim_model1_stan_sim3_total[[plot.s]]$lambda1[1001:2000]),
-                     eta_1=mean(sim_model1_stan_sim3_total[[plot.s]]$eta_1[1001:2000]),
-                     eta_2=mean(sim_model1_stan_sim3_total[[plot.s]]$eta_2[1001:2000]),
-                     eta_3=mean(sim_model1_stan_sim3_total[[plot.s]]$eta_3[1001:2000]),
-                     beta=mean(sim_model1_stan_sim3_total[[plot.s]]$beta[1001:2000]),
-                     f=apply(sim_model1_stan_sim3_total[[plot.s]]$f[1001:2000,],2,mean))
-
-object_hat <- list(lambda0=mmhp_par_est$lambda0,
-                   lambda1=mmhp_par_est$lambda1,
-                   alpha=model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
+####
+lam0_vec <- apply(sim_model1_stan_sim3_total[[plot.s]]$lambda0, 2, mean)
+lam1_vec <- apply(sim_model1_stan_sim3_total[[plot.s]]$lambda1, 2, mean)
+lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
+                       ncol = length(object_par$f_vec_1))
+lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
+                       ncol = length(object_par$f_vec_1))
+
+### loaded in sim data again above
+
+for(i in seq_along(lam0_vec)) {
+  row_id <- clean_sim_data_m1$I_fit[i]
+  col_id <- clean_sim_data_m1$J_fit[i]
+  lam0_par_est[row_id, col_id] <- lam0_vec[i]
+  lam1_par_est[row_id, col_id] <- lam1_vec[i]
+}
+####
+mmhp_par_est <- list(lambda0 = lam0_par_est,
+                     lambda1 = lam1_par_est,
+                     eta_1 = mean(sim_model1_stan_sim3_total[[plot.s]]$eta_1),
+                     eta_2 = mean(sim_model1_stan_sim3_total[[plot.s]]$eta_2),
+                     eta_3 = mean(sim_model1_stan_sim3_total[[plot.s]]$eta_3),
+                     beta = mean(sim_model1_stan_sim3_total[[plot.s]]$beta),
+                     f = apply(sim_model1_stan_sim3_total[[plot.s]]$f, 2, mean))
+
+object_hat <- list(lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
+                   lambda1 = mmhp_par_est$lambda1[cur_i, cur_j],
+                   alpha = model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
                                              mmhp_par_est$f[cur_j],
@@
                                              mmhp_par_est$eta_2),
-                   beta=mmhp_par_est$beta,
-                   q1=model3_fn$q1.fun(mmhp_par_est$f[cur_i],
+                   beta = mmhp_par_est$beta,
+                   q1 = model3_fn$q1.fun(mmhp_par_est$f[cur_i],
                                        mmhp_par_est$f[cur_j],
                                        mmhp_par_est$eta_3),
-                   q2=model3_fn$q0.fun(mmhp_par_est$f[cur_i],
+                   q2 = model3_fn$q0.fun(mmhp_par_est$f[cur_i],
                                        mmhp_par_est$f[cur_j],
@@
 state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
-                                                 termination=200)
+                                                 termination = 200)
 
@@
 source(here("lib","mod_drawHawkesIntensityPaper.R"))
-y.ub <- c(17,17,17)#c(130,72,31)
+y.ub <- c(27,27,27)#c(130,72,31)
 x_events <- 135#150
@@
 my.long.x <- 140#205#134.5
-legend.x <- c(50,50,50)#c(135,135,135)
+legend.x <- c(110,110,110)#c(135,135,135)
 legend.y <- #c(34,32,32)
-legend.y <- c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.y <- c(20,20,20)#c(62,37,18)#c(22,22,22)
 legend.cex <- 1.5 #3
@@
 
-legend(10,legend.y[2]+2,c("State 0/1 events","State change point"),
+legend(legend.x[2]-40,
+       legend.y[2]+2,c("State 0/1 events","State change point"),
        col = c(NA,"red"),
@@
        lty = c(NA,NA), lwd=c(NA,4))
-points(14,8+2,pch=1,cex=2,col="blue")
-points(16,8+2,pch=16,cex=2,col="blue")
+points(legend.x[2]-35,16,pch=1,cex=2,col="blue")
+points(legend.x[2]-34,16,pch=16,cex=2,col="blue")
 
@@
 
-legend(10,legend.y[3],c("Overestimation","Underestimation"),
+legend(legend.x[3]-40,
+       legend.y[3],c("Overestimation","Underestimation"),
        col = c(positive.col,negative.col),
@@
 load(paste0(m2_path,m2_files[plot.s]))
+clean_sim_data_m2 <- cleanSimulationData(raw_data = sim_model2_data[[1]], 
+                                      cut_off = cut_off,
+                                      N = length(object_par$f_vec_1))
 
@@
 #########
-model1_par_est <- list(lambda0 =
-                         mean(sim_model2_stan_sim1_total[[plot.s]]$lambda0[1001:2000]),
-                       eta_1=mean(sim_model2_stan_sim1_total[[plot.s]]$eta_1[1001:2000]),
-                       eta_2=mean(sim_model2_stan_sim1_total[[plot.s]]$eta_2[1001:2000]),
-                       eta_3=mean(sim_model2_stan_sim1_total[[plot.s]]$eta_3[1001:2000]),
-                       beta=mean(sim_model2_stan_sim1_total[[plot.s]]$beta[1001:2000]),
-                       f=apply(sim_model2_stan_sim1_total[[plot.s]]$f[1001:2000,],2,mean))
+model1_par_est <- list(lambda0 = mean(sim_model2_stan_sim1_total[[plot.s]]$lambda0),
+                       eta_1 = mean(sim_model2_stan_sim1_total[[plot.s]]$eta_1),
+                       eta_2 = mean(sim_model2_stan_sim1_total[[plot.s]]$eta_2),
+                       eta_3 = mean(sim_model2_stan_sim1_total[[plot.s]]$eta_3),
+                       beta = mean(sim_model2_stan_sim1_total[[plot.s]]$beta),
+                       f = apply(sim_model2_stan_sim1_total[[plot.s]]$f,2,mean))
 lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
@@
 #############
-model2_par_est <- list(gamma=apply(sim_model2_stan_sim2_total[[plot.s]]$gamma[1001:2000,],
+model2_par_est <- list(gamma = apply(sim_model2_stan_sim2_total[[plot.s]]$gamma,
                                    2,mean),
-                    zeta = 
-                      apply(sim_model2_stan_sim2_total[[plot.s]]$zeta[1001:2000,],2,mean),
-                       eta_1=mean(sim_model2_stan_sim2_total[[plot.s]]$eta_1[1001:2000]),
-                       eta_2=mean(sim_model2_stan_sim2_total[[plot.s]]$eta_2[1001:2000]),
-                       eta_3=mean(sim_model2_stan_sim2_total[[plot.s]]$eta_3[1001:2000]),
-                       beta=mean(sim_model2_stan_sim2_total[[plot.s]]$beta[1001:2000]),
-                       f=apply(sim_model2_stan_sim2_total[[plot.s]]$f[1001:2000,],2,mean))
+                    zeta = apply(sim_model2_stan_sim2_total[[plot.s]]$zeta,2,mean),
+                    eta_1 = mean(sim_model2_stan_sim2_total[[plot.s]]$eta_1),
+                    eta_2 = mean(sim_model2_stan_sim2_total[[plot.s]]$eta_2),
+                    eta_3 = mean(sim_model2_stan_sim2_total[[plot.s]]$eta_3),
+                    beta = mean(sim_model2_stan_sim2_total[[plot.s]]$beta),
+                    f = apply(sim_model2_stan_sim2_total[[plot.s]]$f, 2, mean))
 
 lambda.m2 <- uniHawkesIntensityNumeric(object=list(
-  lambda0=model2_par_est$gamma[plot.i]+
+  lambda0 = model2_par_est$gamma[plot.i]+
           model2_par_est$zeta[plot.j],                                        
-  alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+  alpha = model1_fn$alpha.fun(model2_par_est$f[plot.i],
                             model2_par_est$f[plot.j],
@@
                             model2_par_est$eta_3),
-                beta=model2_par_est$beta),
-                events=temp.t,
-                time.vec=time.segment)
+                beta = model2_par_est$beta),
+                events = temp.t,
+                time.vec = time.segment)
 
@@
 #############
-mmhp_par_est <- list(lambda0=mean(sim_model2_stan_sim3_total[[plot.s]]$lambda0[1001:2000]),
-                     lambda1=mean(sim_model2_stan_sim3_total[[plot.s]]$lambda1[1001:2000]),
-                     eta_1=mean(sim_model2_stan_sim3_total[[plot.s]]$eta_1[1001:2000]),
-                     eta_2=mean(sim_model2_stan_sim3_total[[plot.s]]$eta_2[1001:2000]),
-                     eta_3=mean(sim_model2_stan_sim3_total[[plot.s]]$eta_3[1001:2000]),
-                     beta=mean(sim_model2_stan_sim3_total[[plot.s]]$beta[1001:2000]),
-                     f=apply(sim_model2_stan_sim3_total[[plot.s]]$f[1001:2000,],2,mean))
-
-object_hat <- list(lambda0=mmhp_par_est$lambda0,
-                   lambda1=mmhp_par_est$lambda1,
-                   alpha=model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
+lam0_vec <- apply(sim_model2_stan_sim3_total[[plot.s]]$lambda0, 2, mean)
+lam1_vec <- apply(sim_model2_stan_sim3_total[[plot.s]]$lambda1, 2, mean)
+
+lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
+                       ncol = length(object_par$f_vec_1))
+lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
+                       ncol = length(object_par$f_vec_1))
+
+for(i in seq_along(lam0_vec)) {
+  row_id <- clean_sim_data_m2$I_fit
+  col_id <- clean_sim_data_m2$J_fit
+  lam0_par_est[row_id, col_id] <- lam0_vec[i]
+  lam1_par_est[row_id, col_id] <- lam1_vec[i]
+}
+
+mmhp_par_est <- list(lambda0 = lam0_par_est,
+                     lambda1 = lam1_par_est,
+                     eta_1 = mean(sim_model2_stan_sim3_total[[plot.s]]$eta_1),
+                     eta_2 = mean(sim_model2_stan_sim3_total[[plot.s]]$eta_2),
+                     eta_3 = mean(sim_model2_stan_sim3_total[[plot.s]]$eta_3),
+                     beta = mean(sim_model2_stan_sim3_total[[plot.s]]$beta),
+                     f = apply(sim_model2_stan_sim3_total[[plot.s]]$f,2,mean))
+
+object_hat <- list(lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
+                   lambda1 = mmhp_par_est$lambda1[cur_i, cur_j],
+                   alpha = model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
                                              mmhp_par_est$f[cur_j],
@@
 
-lambda.m3 <- mmhpIntensityNumeric(params=object_hat,
-                                  t=temp.t,
-                                  time.vec=time.segment,
-                                  latent.vec=step.fun.est(time.segment))
+lambda.m3 <- mmhpIntensityNumeric(params = object_hat,
+                                  t = temp.t,
+                                  time.vec = time.segment,
+                                  latent.vec = step.fun.est(time.segment))
 
@@
 ```{r data for fig 5,cache=TRUE}
-load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
-load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
+# load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
+# load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
+####
+#### load new format
+
 ## Initialize
-N_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
-Lambda_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
-Lambda_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
-Lambda_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
-Lambda_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
-PR_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
-PR_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
-PR_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
-PR_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
-KS_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
-KS_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
-KS_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
-KS_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
-KS_p_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
-KS_p_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
-KS_p_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
-KS_p_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
+N_array <- array(0, dim = c(n_sim, length(object_par$f_vec_1),
+                         length(object_par$f_vec_1))) 
+Lambda_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                     length(object_par$f_vec_1))) 
+Lambda_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                     length(object_par$f_vec_1)))
+Lambda_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                     length(object_par$f_vec_1))) 
+Lambda_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                   length(object_par$f_vec_1))) 
+PR_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                 length(object_par$f_vec_1)))
+PR_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                 length(object_par$f_vec_1))) 
+PR_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                 length(object_par$f_vec_1)))
+PR_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                               length(object_par$f_vec_1))) 
+KS_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                 length(object_par$f_vec_1)))
+KS_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                 length(object_par$f_vec_1)))
+KS_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                    length(object_par$f_vec_1)))
+KS_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                               length(object_par$f_vec_1)))
+KS_p_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                   length(object_par$f_vec_1)))
+KS_p_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                   length(object_par$f_vec_1)))
+KS_p_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                    length(object_par$f_vec_1)))
+KS_p_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
+                                    length(object_par$f_vec_1)))
 
@@
 for(s in c(1:n_sim)){
-  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data[s][[1]], 
-                                        cut_off = cut_off, N = length(object_par$f_vec_1))
+  load(paste0(sim_data_path,"sim_model3_fit123_",s,".RData"))
+  load(paste(sim_data_path,"fit123_state_est_",s,".RData",sep=''))
+  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data, 
+                                        cut_off = cut_off,
+                                        N = length(object_par$f_vec_1))
 
@@
   #########
-  model1_par_est <- list(lambda0=mean(sim_model3_stan_sim1[[s]]$lambda0[1001:2000]),
-                         eta_1=mean(sim_model3_stan_sim1[[s]]$eta_1[1001:2000]),
-                         eta_2=mean(sim_model3_stan_sim1[[s]]$eta_2[1001:2000]),
-                         eta_3=mean(sim_model3_stan_sim1[[s]]$eta_3[1001:2000]),
-                         beta=mean(sim_model3_stan_sim1[[s]]$beta[1001:2000]),
-                         f=apply(sim_model3_stan_sim1[[s]]$f[1001:2000,],2,mean))
+  model1_par_est <- list(lambda0 = mean(sim_model3_stan_sim1$lambda0),
+                         eta_1 = mean(sim_model3_stan_sim1$eta_1),
+                         eta_2 = mean(sim_model3_stan_sim1$eta_2),
+                         eta_3 = mean(sim_model3_stan_sim1$eta_3),
+                         beta = mean(sim_model3_stan_sim1$beta),
+                         f = apply(sim_model3_stan_sim1$f, 2, mean))
 
@@
     for(j in c(1:5)[-i]){
-      current_t <- sim_model3_data[s][[1]]$mmhp_matrix[i,j][[1]]$tau
-      m1_object <- list(lambda0=model1_par_est$lambda0,
-                        alpha=model1_fn$alpha.fun(model1_par_est$f[i],model1_par_est$f[j],model1_par_est$eta_1,model1_par_est$eta_2,model1_par_est$eta_3),
-                        beta=model1_par_est$beta)
-      Lambda_model1_array[s,i,j]<-uniHawkesIntegralIntensity(object=m1_object, 
-                                                             events=current_t,
+      current_t <- sim_model3_data$mmhp_matrix[i,j][[1]]$tau
+      m1_object <- list(lambda0 = model1_par_est$lambda0,
+                        alpha = model1_fn$alpha.fun(model1_par_est$f[i],
+                                                  model1_par_est$f[j],
+                                                  model1_par_est$eta_1,
+                                                  model1_par_est$eta_2,
+                                                  model1_par_est$eta_3),
+                        beta = model1_par_est$beta)
+      Lambda_model1_array[s,i,j] <- 
+        uniHawkesIntegralIntensity(object = m1_object, 
+                                   events = current_t,
                                    termination = tail(current_t,1))
-      Lambda_test <- uniHawkesCompensator(object=m1_object, events=current_t)
+      Lambda_test <- uniHawkesCompensator(object = m1_object, 
+                                          events = current_t)
       KS_model1_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$statistic
       KS_p_model1_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
-      PR_model1_array[s,i,j] <- uniHawkesPearsonResidual(object=m1_object, 
-                                                         events=current_t,
-                                                         termination = tail(current_t,1))
+      PR_model1_array[s,i,j] <- uniHawkesPearsonResidual(object = m1_object, 
+                                                         events = current_t,
+                                                         termination = 
+                                                           tail(current_t,1))
     }
@@
   #############
-  model2_par_est <- list(gamma=apply(sim_model3_stan_sim2[[s]]$gamma[1001:2000,],2,mean),
-                         zeta=apply(sim_model3_stan_sim2[[s]]$zeta[1001:2000,],2,mean),
-                         eta_1=mean(sim_model3_stan_sim2[[s]]$eta_1[1001:2000]),
-                         eta_2=mean(sim_model3_stan_sim2[[s]]$eta_2[1001:2000]),
-                         eta_3=mean(sim_model3_stan_sim2[[s]]$eta_3[1001:2000]),
-                         beta=mean(sim_model3_stan_sim2[[s]]$beta[1001:2000]),
-                         f=apply(sim_model3_stan_sim2[[s]]$f[1001:2000,],2,mean))
+  model2_par_est <- list(gamma = apply(sim_model3_stan_sim2$gamma, 2, mean),
+                         zeta = apply(sim_model3_stan_sim2$zeta,2,mean),
+                         eta_1 = mean(sim_model3_stan_sim2$eta_1),
+                         eta_2 = mean(sim_model3_stan_sim2$eta_2),
+                         eta_3 = mean(sim_model3_stan_sim2$eta_3),
+                         beta = mean(sim_model3_stan_sim2$beta),
+                         f = apply(sim_model3_stan_sim2$f, 2, mean))
 
@@
     for(j in c(1:5)[-i]){
-      current_t <- sim_model3_data[s][[1]]$mmhp_matrix[i,j][[1]]$tau
-      m2_object <- list(lambda0=model2_par_est$gamma[i]+model2_par_est$zeta[j],
-                        alpha=model1_fn$alpha.fun(model2_par_est$f[i],model2_par_est$f[j],model2_par_est$eta_1,model2_par_est$eta_2,model2_par_est$eta_3),
-                        beta=model2_par_est$beta)
-      Lambda_model2_array[s,i,j]<-uniHawkesIntegralIntensity(object=m1_object, 
-                                                             events=current_t,
+      current_t <- sim_model3_data$mmhp_matrix[i,j][[1]]$tau
+      m2_object <- list(lambda0 = model2_par_est$gamma[i] + 
+                          model2_par_est$zeta[j],
+                        alpha = model1_fn$alpha.fun(model2_par_est$f[i],
+                                                    model2_par_est$f[j],
+                                                    model2_par_est$eta_1,
+                                                    model2_par_est$eta_2,
+                                                    model2_par_est$eta_3),
+                        beta = model2_par_est$beta)
+      Lambda_model2_array[s,i,j] <-
+        uniHawkesIntegralIntensity(object = m1_object, 
+                                   events = current_t,
                                    termination = tail(current_t,1))
-      Lambda_test <- uniHawkesCompensator(object=m2_object, events=current_t)
+      Lambda_test <- uniHawkesCompensator(object = m2_object,
+                                          events = current_t)
       KS_model2_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$statistic
       KS_p_model2_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
-      PR_model2_array[s,i,j] <- uniHawkesPearsonResidual(object=m2_object, 
-                                                         events=current_t,
+      PR_model2_array[s,i,j] <- 
+        uniHawkesPearsonResidual(object = m2_object, 
+                                 events = current_t,
                                  termination = tail(current_t,1))
@@
   ######
-  mmhp_par_est <- list(lambda0=mean(sim_model3_stan_sim3[[s]]$lambda0[1001:2000]),
-                       lambda1=mean(sim_model3_stan_sim3[[s]]$lambda1[1001:2000]),
-                       eta_1=mean(sim_model3_stan_sim3[[s]]$eta_1[1001:2000]),
-                       eta_2=mean(sim_model3_stan_sim3[[s]]$eta_2[1001:2000]),
-                       eta_3=mean(sim_model3_stan_sim3[[s]]$eta_3[1001:2000]),
-                       beta=mean(sim_model3_stan_sim3[[s]]$beta[1001:2000]),
-                       f=apply(sim_model3_stan_sim3[[s]]$f[1001:2000,],2,mean))
-  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data[s][[1]], 
-                                        cut_off = cut_off, N = length(object_par$f_vec_1))
+  lambda_0_est <- apply(sim_model3_stan_sim3$lambda0, 2, mean)
+  lambda_1_est <- apply(sim_model3_stan_sim3$lambda1, 2, mean)
+  ## then put these into a matrix
+  lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
+                         ncol = length(object_par$f_vec_1))
+  lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
+                         ncol = length(object_par$f_vec_1))
+  for(i in seq_along(lambda_0_est)) {
+    row_id <- clean_sim_data$I_fit[i]
+    col_id <- clean_sim_data$J_fit[i]
+    lam0_par_est[row_id, col_id] <- lambda_0_est[i]
+    lam1_par_est[row_id, col_id] <- lambda_1_est[i]
+  }
+  mmhp_par_est <- list(lambda0 = lam0_par_est,
+                       lambda1 = lam1_par_est,
+                       eta_1 = mean(sim_model3_stan_sim3$eta_1),
+                       eta_2 = mean(sim_model3_stan_sim3$eta_2),
+                       eta_3 = mean(sim_model3_stan_sim3$eta_3),
+                       beta = mean(sim_model3_stan_sim3$beta),
+                       f = apply(sim_model3_stan_sim3$f,2,mean))
+  clean_sim_data <- cleanSimulationData(raw_data = sim_model3_data, 
+                                        cut_off = cut_off,
+                                        N = length(object_par$f_vec_1))
 
@@
     for(j in c(1:5)[-i]){
-      test.mmhp <- sim_model3_data[s][[1]]$mmhp_matrix[i,j][[1]]
+      test.mmhp <- sim_model3_data$mmhp_matrix[i,j][[1]]
       temp.t <- test.mmhp$tau
@@
 
-      object_hat <- list(lambda0=mmhp_par_est$lambda0,
-                         lambda1=mmhp_par_est$lambda1,
+      object_hat <- list(lambda0=mmhp_par_est$lambda0[i,j],
+                         lambda1=mmhp_par_est$lambda1[i,j],
                          alpha=model3_fn$alpha.fun(mmhp_par_est$f[i],
@@
       ## est Lmabda and [R]
-      Lambda.test <- mmhpCompensator(params=object_hat, 
-                                     t=temp.t,
-                                     pzt=2-event_state_est_lst[[s]][i,j][[1]]$zt_v,
-                                     if.pzt=FALSE)
+      Lambda.test <- mmhpCompensator(params = object_hat, 
+                                     t = temp.t,
+                                     pzt=2 - 
+                                       event_state_est_lst[i,j][[1]]$zt_v,
+                                     if.pzt = FALSE)
       KS_model3_array[s,i,j] <-  ks.test(Lambda.test,"pexp")$statistic
       KS_p_model3_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
-      state.est.latent.mmhp <- interpolate_state_est_lst[[s]][i,j][[1]]
-      step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,2-state.est.latent.mmhp$z.hat)
-      est.intensity <- mmhpIntensityNumeric(params=object_hat,
-                                            t=temp.t[-1],
-                                            time.vec=time.segment,
-                                            latent.vec=step.fun.est(time.segment))
-      est.intensity.events <- mmhpIntensityAtEvents(params=object_hat, t=temp.t,
-                                                    latent_z=event_state_est_lst[[s]][i,j][[1]]$zt_v)
-      Lambda_model3_array[s,i,j] <- sum(est.intensity)*(time.segment[2]-time.segment[1])
+      state.est.latent.mmhp <- interpolate_state_est_lst[i,j][[1]]
+      step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,
+                              2 - state.est.latent.mmhp$z.hat)
+      est.intensity <- mmhpIntensityNumeric(params = object_hat,
+                                            t = temp.t[-1],
+                                            time.vec = time.segment,
+                                            latent.vec = 
+                                              step.fun.est(time.segment))
+      est.intensity.events <- mmhpIntensityAtEvents(params=object_hat,
+                                                    t = temp.t,
+                                  latent_z = 
+                                    event_state_est_lst[i,j][[1]]$zt_v)
+      Lambda_model3_array[s,i,j] <-
+        sum(est.intensity)*(time.segment[2]-time.segment[1])
       PR_model3_array[s,i,j] <- sum(1/sqrt(est.intensity.events))-
@@
       ## Under the true model
-      Lambda.test.true <- mmhpCompensator(params=object_true,
-                                          t=temp.t,
-                                          pzt=2-test.mmhp$zt[2:length(test.mmhp$zt)],
+      Lambda.test.true <- mmhpCompensator(params = object_true,
+                                          t = temp.t,
+                                          pzt = 2 - 
+                                            test.mmhp$zt[2:length(test.mmhp$zt)],
                                           if.pzt=FALSE)
@@
       KS_p_true_array[s,i,j] <-  ks.test(Lambda.test.true,"pexp")$p.value
-      true.intensity <- mmhpTrueIntensityNumeric(params=object_true, t=temp.t,
-                                                 latent=list(x=fixStateTransition(test.mmhp)$x,
-                                                             z=fixStateTransition(test.mmhp)$z),
-                                                 time.vec=time.segment)
-      true.intensity.events <- mmhpIntensityAtEvents(params=object_true, t=temp.t, 
-                                                     latent_z=test.mmhp$zt)
+      true.intensity <- 
+        mmhpTrueIntensityNumeric(params = object_true,
+                                                 t = temp.t,
+                                 latent = list(x = 
+                                                fixStateTransition(test.mmhp)$x,
+                                               z = 
+                                                fixStateTransition(test.mmhp)$z),
+                                     time.vec = time.segment)
+      true.intensity.events <- mmhpIntensityAtEvents(params = object_true,
+                                                     t = temp.t, 
+                                                     latent_z = test.mmhp$zt)
       Lambda_true_array[s,i,j] <- sum(true.intensity$lambda.t)*(time.segment[2]-time.segment[1])
@@
       if(i==5){
-        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04,col=cols_plot[1],border=NA)
-        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,col=cols_plot[2],border=NA)
-        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,col=cols_plot[3],border=NA)
-        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,col=cols_plot[4],border=NA)
-        text(c(0.43,0.58,0.61,0.4),seq(0.8,0.14,-0.22),
+        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04, 
+                col = cols_plot[1], border = NA)
+        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,
+                col = cols_plot[2], border = NA)
+        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,
+                col = cols_plot[3], border = NA)
+        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,
+                col = cols_plot[4], border = NA)
+        text(c(0.43,0.58,0.61,0.4), seq(0.8,0.14,-0.22),
              c("C-HP", "C-DCHP", "C-MMHP", "True"),
@@
       #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
-      PR <- c(KS_model1_array[,i,j],KS_model2_array[,i,j],
-              KS_model3_array[,i,j],KS_true_array[,i,j])
-      Type <- c(rep(1,n_sim),rep(2,n_sim),rep(3,n_sim),rep(4,n_sim))
+      PR <- c(KS_model1_array[,i,j], KS_model2_array[,i,j],
+              KS_model3_array[,i,j], KS_true_array[,i,j])
+      ### try pr scores instead
+      # PR <- c(PR_model1_array[,i,j],PR_model2_array[,i,j],
+      #         PR_model3_array[,i,j],PR_true_array[,i,j])
+      Type <- c(rep(1,n_sim), rep(2,n_sim), rep(3,n_sim), rep(4,n_sim))
       boxplot(PR ~ Type,  
@@
               #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
-              xlab="",ylab="",xaxt="n",yaxt="n")#names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
+              xlab="",ylab="",xaxt="n",yaxt="n")
+      #names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
     }

### 2020-11-25 output_scripts/Paper_Plots.Rmd
tidying up plots

@@
     select(m1:glicko) %>%
-    map( ~cor.test(truth, .x,
+    purrr::map( ~cor.test(truth, .x,
                    method = "spearman")$estimate  ) %>%
@@
 temp_plot_df$day <- factor(temp_plot_df$day)
-#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
+#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
+# width=600,height=300)
 p3 <- temp_plot_df %>%
@@
 temp_plot_df$day <- factor(temp_plot_df$day)
-#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
+#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
+# width=600,height=300)
 p3_slides <- temp_plot_df %>%
@@
                               levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+                              labels = c("I-MMHP","DSNL",
+                                         "C-HP","C-DCHP",
+                                         "C-MMHP"))
 temp_plot_df$day <- factor(temp_plot_df$day)
@@
 p4 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
-  geom_line(aes(linetype = method),
+  geom_line(#aes(linetype = method),
             size=1.2, alpha=0.8, position=position_dodge(0.2)) +
@@
 p4
+```
+```{r fig-8b-frob-norm-boxplot, fig.width=8, fig.height=4}
+load("../output/plot_N_predict.RData")
+
+all_cohort_box <- all_cohort_norm_df
+
+all_cohort_box$method <- factor(all_cohort_box$method,
+                              levels = c("mmhp","dsnl","m1","m2","m3"),
+                              labels = c("I-MMHP","DSNL",
+                                         "C-HP","C-DCHP",
+                                         "C-MMHP"))
+all_cohort_box$day <- factor(all_cohort_box$day)
+
+all_cohort_box %>% 
+  ggplot(aes(x=method,y=norm, fill = method)) +
+  geom_boxplot() + 
+  facet_grid(cols = vars(day)) +
+  geom_boxplot(alpha=0.7) +
+  scale_fill_manual(values = viridis::viridis(5)) +
+  ggtitle("(b)") +
+  theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.position="right") +
+  facet_grid(cols=vars(day)) +
+  # guides(color=guide_legend(title="Method")) +
+  xlab("Prediction horizon (day)") + 
+  ylab("Frobenius norm of error") +
+  labs(fill = "Method") +
+  # ylim(0, 80) +
+  NULL
+
 ```
@@
                               levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+                              labels = c("I-MMHP","DSNL","C-HP",
+                                         "C-DCHP","C-MMHP"))
 temp_plot_df$day <- factor(temp_plot_df$day)
-# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),width=600,height=300)
+# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),
+# width=600,height=300)
 p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
@@
   scale_fill_manual(values = viridis::viridis(5)) +
-  #scale_fill_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
+  #scale_fill_manual(values =
+  # c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
   ggtitle("(a)") +

### 2020-12-01 output_scripts/Paper_Plots.Rmd
WIP, correcting under/over estimation for fig 4b

@@
 slides_plots <- FALSE
+extra_plots <- FALSE
 current_cohort <- 5
@@
                   q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
+
+```
+
+```{r creat colour df}
+col_df <- tibble(method = c("I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
+            "C-HP", "C-DCHP", "True", "C-MMHP"),
+            cols = viridis(9))
 
@@
 
-colors_plot <- viridis(2)
+colors_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP")) %>%
+  pull(cols) 
 load(paste(data_path,cohort_names[current_cohort],
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, include=FALSE}
 par(mar=c(3,3,1,1))
@@
 
-# Redone Figure 3
-
-As discussed, it would be interesting to redo figure 3b
-to show the lack of fit in model 2 for one specific pair. This can be somewhat
-extracted from the diagnostics file.
-
-We actually want the empirical CDF plot here.
-
-```{r fig_3b_update, fig.height=7}
-# 2 -> 11 might be good here
-# current_cohort <- 5
-clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-return_df <- cleanObservationPeriod(current_cohort, clean_data)
-unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
-  dplyr::summarize(count=n(),
-            observe=list(observe.id),
-            observe.length=list(observe.time),
-            no.events=list(no.events)) 
-top_pairs <- unique_pairs_df %>% arrange(desc(count))
-
-best_i <- top_pairs$initiator[8]
-best_j <- top_pairs$recipient[8]
-
-current_i <- best_i #8
-current_j <- best_j #2
-
-### then plots ####
-# par(mfrow = c(1, 2), oma = c(1, 1, 1, 1),
-#      mar = c(2, 3, 2, 1), mgp = c(0.8,0,0))
-# layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
-anno.cex <- 1.3
-title.cex <- 2.2
-title.line <- 0.5
-y.upper <- 20
-#### then the corresponding QQ plot ####
-load(paste(data_path,cohort_names[current_cohort],
-             "/real_diag_four_models_",cohort_names[current_cohort],
-             ".RData",sep=''))
-Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]
-
-p <- ppoints(length(Lambda.dc_hawkes.test))
-# 100 equally spaced points on (0,1), excluding endpoints
-q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE)
-# percentiles of the sample distribution
-plot(qexp(p),q,
-     xlab="",ylab="",xaxt="n",yaxt="n",
-     pch=1, cex=1, col=viridis::viridis(1), ylim=c(0,1), xlim=c(0,4.5))
-mtext(side = 1, text = "Theoretical", line=1.6, cex=anno.cex)
-mtext(side = 2, text = "Empirical", line = 1.2, cex = anno.cex)
-mtext(side = 3, text = "(b)", line = 0.8, cex = 1.6, font = 2)
-# Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1)
-# Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:1),cex.axis=1,lwd=0,lwd.ticks=1)
-qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
-
-### Empirical CDF ####
-
-plot(ecdf(Lambda.dc_hawkes.test), do.points = FALSE,
-     verticals = TRUE, col = viridis::viridis(1), lwd = 2, 
-     xlab = "", ylab = "", xaxt = "n", yaxt = "n",
-     main = "", col.01line = NULL)
-curve(pexp(x,1/mean(Lambda.dc_hawkes.test)),
-      min(Lambda.dc_hawkes.test), max(Lambda.dc_hawkes.test),
-      ylab = "", xlab = "",
-      add = TRUE, lwd = 2)
-
-```
-
-```{r repeat entire fig2b for model 2}
-# current_cohort <- 5
-
-load(paste(data_path,cohort_names[current_cohort],
-             "/real_diag_four_models_",cohort_names[current_cohort],
-             ".RData",sep=''))
-
-load(paste(data_path,cohort_names[current_cohort],
-           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
-eta1_mean <- mean(sim_cohort_dchp$eta_1)
-eta2_mean <- mean(sim_cohort_dchp$eta_2)
-eta3_mean <- mean(sim_cohort_dchp$eta_3)
-f_est <- apply(sim_cohort_dchp$f,2,mean)
-clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-return_df <- cleanObservationPeriod(current_cohort, clean_data)
-unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
-  dplyr::summarize(count=n(),
-                   observe=list(observe.id),
-                   observe.length=list(observe.time),
-                   no.events=list(no.events))
-unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
-
-ks.stat.matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
-n_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
-Lambda_matrix <- matrix(list(),nrow=mice_number,ncol=mice_number)
-for(k in 1:mice_number){
-  for(l in c(1:mice_number)[-k]){
-    i<-expert_rank_10[[current_cohort]][k]
-    j<-expert_rank_10[[current_cohort]][l]
-    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
-    if(length(pair)>0){
-      param_mean <- list(lambda0=mean(sim_cohort_dchp$lambda0[,pair]),
-                         alpha=model1_fn$alpha.fun(f_est[i],
-                                                   f_est[j],
-                                                   eta1_mean,
-                                                   eta2_mean,
-                                                   eta3_mean),
-                         beta=mean(sim_cohort_dchp$beta))
-      current_window_vec <- unique_pairs_df$observe[[pair]]
-      all_Lambda <- numeric(0)
-      for(cur in c(1:length(current_window_vec))){ ## check length > 2
-        cur_win <- current_window_vec[cur]
-        current_event_time <- return_df[return_df$initiator==i&
-                                          return_df$recipient == j &
-                            return_df$observe.id==cur_win,"event.times"][[1]]
-        current_obs_time <- return_df[return_df$initiator==i&
-                                        return_df$recipient==j&
-                            return_df$observe.id==cur_win,"observe.time"]
-        Lambda_vec <- uniHawkesCompensator(object = param_mean,
-                              events = c(current_event_time,
-                                         current_obs_time))
-        all_Lambda <- c(all_Lambda,Lambda_vec)
-        n_matrix[i,j] <- n_matrix[i,j] + length(current_event_time)
-      }
-      if(length(all_Lambda)>0){
-        ks.stat.matrix[i,j] <-  ks.test(all_Lambda,"pexp",
-                                        rate = 1/mean(all_Lambda))$statistic
-        Lambda_matrix[i,j][[1]] <- all_Lambda
-      }
-    }
-  }
-}
-
-m2_ks <- ks.stat.matrix
-
-# -------------- KS plot (stat)
-col.vec <- cRamp(as.vector(ks.stat.matrix))
-## need to do some sort of transformation between these here
-vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
-#order(as.vector(ks.stat.matrix),method = "")
-
-values <- as.vector(ks.stat.matrix)
-sorted_vals <- sort(ks.stat.matrix)
-#match(values,sorted_vals)
-col.vec.vir <- vir_cols[match(values,sorted_vals)]
-
-####
-par(oma = c(6,4,4,1), mar=rep(0,4),
-    mgp = c(0, .2, 0))
-layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
-                    byrow = TRUE),rep(12*12+1,12)), 
-       widths=c(rep(1,12),2), heights=rep(1,12))
-for(i in expert_rank_10[[current_cohort]]){
-  for(j in expert_rank_10[[current_cohort]]){
-    if(ks.stat.matrix[i,j]==0){
-      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
-           axes = FALSE, frame=TRUE)
-      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
-           border = 0, col = 'white')
-    }else{
-      Lambda.test <- Lambda_matrix[i,j][[1]]
-      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
-            ylab="",xlab="",axes = FALSE, frame=TRUE)
-      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], 
-           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
-      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
-            ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
-      plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
-           verticals = TRUE, col = "red", lwd = 2)
-    }
-  }
-}
-par(mar = c(0,2,0,3),mgp=c(0,0.8,0))
-
-col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)),
-                            length.out = 100),
-                col.vec = viridis(100))
-
-temp <- cLegend(as.vector(ks.stat.matrix))
-
-image(1, col_obj$x.vec,
-      matrix(data=col_obj$x.vec, 
-             ncol=length(col_obj$x.vec),nrow=1),
-      col=col_obj$col.vec,
-      xlab="",ylab="",axes=FALSE)
-axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1,
-     cex.axis=2.4)
-
-mtext(text=expert_rank_10[[current_cohort]], side=1,
-      line=1.8, outer=TRUE, cex=1.8,
-      at=1/14*c(1:12)-1/22)
-mtext(text = expert_rank_10[[current_cohort]],
-      side = 2, line = 0.5, outer = TRUE, cex = 1.8,
-      at =1/12*c(12:1)-1/20, las = 2)
-mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE,
-      cex = 2.2,
-      at=0.45, font=2)
-
-```
-
-```{r construct ks_diff}
-ks_diff <-  (m2_ks - m1_ks)/m1_ks
-ks_diff[is.nan(ks_diff)] <- 0
-# -------------- KS plot (stat)
-col.vec <- cRamp(as.vector(ks_diff))
-## need to do some sort of transformation between these here
-vir_cols <- viridis::viridis(length((as.vector(ks_diff))))
-#order(as.vector(ks.stat.matrix),method = "")
-
-values <- as.vector(ks_diff)
-sorted_vals <- sort(ks_diff)
-#match(values,sorted_vals)
-col.vec.vir <- vir_cols[match(values,sorted_vals)]
-
-####
-par(oma = c(6,4,4,1), mar=rep(0,4),
-    mgp = c(0, .2, 0))
-layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
-                    byrow = TRUE),rep(12*12+1,12)), 
-       widths=c(rep(1,12),2), heights=rep(1,12))
-for(i in expert_rank_10[[current_cohort]]){
-  for(j in expert_rank_10[[current_cohort]]){
-    if(ks_diff[i,j]==0){
-      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
-           axes = FALSE, frame=TRUE)
-      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
-           border = 0, col = 'white')
-    }else{
-      Lambda.test <- Lambda_matrix[i,j][[1]]
-      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
-            ylab="",xlab="",axes = FALSE, frame=TRUE)
-      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
-           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
-
-    }
-  }
-}
-par(mar = c(0,2,0,3),mgp=c(0,0.8,0))
-
-col_obj <- list(x.vec = seq(min(as.vector(ks_diff)),max(as.vector(ks_diff)),
-                            length.out = 100),
-                col.vec = viridis(100))
-
-# temp <- cLegend(as.vector(ks_diff))
-
-image(1, col_obj$x.vec,
-      matrix(data=col_obj$x.vec, 
-             ncol=length(col_obj$x.vec),nrow=1),
-      col=col_obj$col.vec,
-      xlab="",ylab="")
-# axis(4, at=c(-0.2,0,0.2), labels=c(-0.2,0,0.2), las= HORIZONTAL<-1,
-#      cex.axis=2.4)
-
-mtext(text=expert_rank_10[[current_cohort]], side=1,
-      line=1.8, outer=TRUE, cex=1.8,
-      at=1/14*c(1:12)-1/22)
-mtext(text = expert_rank_10[[current_cohort]],
-      side = 2, line = 0.5, outer = TRUE, cex = 1.8,
-      at =1/12*c(12:1)-1/20, las = 2)
-mtext(text = "(M2 - M1)/M1", side = 3, line = 1.4, outer = TRUE,
-      cex = 2.2,
-      at=0.45, font=2)
-
-```
-
-```{r construct ks diff normalised by num events}
-norm_diff <- (m2_ks - m1_ks)#/m1_ks
-norm_diff[is.nan(norm_diff)] <- 0
-count_mat <- matrix(0, nrow = mice_number, ncol = mice_number)
-
-for(i in expert_rank_10[[current_cohort]]) {
-  for(j in expert_rank_10[[current_cohort]]) {
-    if( norm_diff[i,j] != 0 ) {
-      num_events <- unique_pairs_df %>% 
-      filter(initiator == i & recipient == j) %>%
-      pull(count)
-      # diff[i,j] <- diff[i,j] / num_events
-      count_mat[i,j] <- num_events
-    }
-  }
-}
-
-tibble(diff_norm = as.vector(norm_diff),
-       events = as.vector(count_mat)) %>%
-  filter(events > 0 ) %>%
-  ggplot(aes(events,diff_norm)) + geom_point() +
-  ylab("M2-M1") +
-  theme_minimal()
-
-tibble(diff_norm = as.vector(norm_diff),
-       events = as.vector(count_mat)) %>%
-  filter(events > 0) %>%
-  ggplot(aes(diff_norm)) + 
-  geom_histogram() +
-  theme_minimal()
-
-```
-```{r repeat for residuals}
-m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                   "/chp_pr_matrix_",cohort_names[current_cohort],
-                   ".RDS",sep=''))
-
-m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                     "/dchp_pr_matrix_",cohort_names[current_cohort],
-                     ".RDS",sep=''))
-
-tibble(m1pr = as.vector(m1_pr),
-       m2pr = as.vector(m2_pr)) %>%
-  mutate(diff = m2pr - m1pr) %>%
-  ggplot(aes(diff)) + 
-  geom_histogram() +
-  labs(x = "M2 PR - M1 PR") +
-  theme_minimal()
-
-```
-
-```{r compute mean decrease in ks-score}
-summary(as.vector(m2_ks[m2_ks != 0]))
-summary(as.vector(m1_ks[m1_ks != 0]))
-
-t.test(as.vector(m2_ks[m2_ks != 0]), as.vector(m1_ks[m1_ks != 0]))
-
-diff <- as.vector(m2_ks[m2_ks != 0]) - as.vector(m1_ks[m1_ks != 0])
-
-length(which(diff < 0))/length(diff)
-summary(diff)
-```
-
-This is good because it shows the most active animal, shows that individual
-out rate too large for this interaction. Just need to make this more
-like the plots in 2b.
+<!-- # Redone Figure 3 -->
+
+<!-- As discussed, it would be interesting to redo figure 3b -->
+<!-- to show the lack of fit in model 2 for one specific pair. This can be somewhat -->
+<!-- extracted from the diagnostics file. -->
+
+<!-- We actually want the empirical CDF plot here. -->
+
+<!-- ```{r fig_3b_update, fig.height=7, include=FALSE, eval=FALSE} -->
+<!-- # 2 -> 11 might be good here -->
+<!-- # current_cohort <- 5 -->
+<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
+<!-- return_df <- cleanObservationPeriod(current_cohort, clean_data) -->
+<!-- unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% -->
+<!--   dplyr::summarize(count=n(), -->
+<!--             observe=list(observe.id), -->
+<!--             observe.length=list(observe.time), -->
+<!--             no.events=list(no.events))  -->
+<!-- top_pairs <- unique_pairs_df %>% arrange(desc(count)) -->
+
+<!-- best_i <- top_pairs$initiator[8] -->
+<!-- best_j <- top_pairs$recipient[8] -->
+
+<!-- current_i <- best_i #8 -->
+<!-- current_j <- best_j #2 -->
+
+<!-- ### then plots #### -->
+<!-- # par(mfrow = c(1, 2), oma = c(1, 1, 1, 1), -->
+<!-- #      mar = c(2, 3, 2, 1), mgp = c(0.8,0,0)) -->
+<!-- # layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3)) -->
+<!-- anno.cex <- 1.3 -->
+<!-- title.cex <- 2.2 -->
+<!-- title.line <- 0.5 -->
+<!-- y.upper <- 20 -->
+<!-- #### then the corresponding QQ plot #### -->
+<!-- load(paste(data_path,cohort_names[current_cohort], -->
+<!--              "/real_diag_four_models_",cohort_names[current_cohort], -->
+<!--              ".RData",sep='')) -->
+<!-- Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]] -->
+
+<!-- p <- ppoints(length(Lambda.dc_hawkes.test)) -->
+<!-- # 100 equally spaced points on (0,1), excluding endpoints -->
+<!-- q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) -->
+<!-- # percentiles of the sample distribution -->
+<!-- plot(qexp(p),q, -->
+<!--      xlab="",ylab="",xaxt="n",yaxt="n", -->
+<!--      pch=1, cex=1, col=viridis::viridis(1), ylim=c(0,1), xlim=c(0,4.5)) -->
+<!-- mtext(side = 1, text = "Theoretical", line=1.6, cex=anno.cex) -->
+<!-- mtext(side = 2, text = "Empirical", line = 1.2, cex = anno.cex) -->
+<!-- mtext(side = 3, text = "(b)", line = 0.8, cex = 1.6, font = 2) -->
+<!-- # Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1) -->
+<!-- # Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:1),cex.axis=1,lwd=0,lwd.ticks=1) -->
+<!-- qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5) -->
+
+<!-- ### Empirical CDF #### -->
+
+<!-- plot(ecdf(Lambda.dc_hawkes.test), do.points = FALSE, -->
+<!--      verticals = TRUE, col = viridis::viridis(1), lwd = 2,  -->
+<!--      xlab = "", ylab = "", xaxt = "n", yaxt = "n", -->
+<!--      main = "", col.01line = NULL) -->
+<!-- curve(pexp(x,1/mean(Lambda.dc_hawkes.test)), -->
+<!--       min(Lambda.dc_hawkes.test), max(Lambda.dc_hawkes.test), -->
+<!--       ylab = "", xlab = "", -->
+<!--       add = TRUE, lwd = 2) -->
+
+<!-- ``` -->
+
+<!-- ```{r repeat entire fig2b for model 2, include=extra_plots, eval=extra_plots} -->
+<!-- # current_cohort <- 5 -->
+
+<!-- load(paste(data_path,cohort_names[current_cohort], -->
+<!--              "/real_diag_four_models_",cohort_names[current_cohort], -->
+<!--              ".RData",sep='')) -->
+
+<!-- load(paste(data_path,cohort_names[current_cohort], -->
+<!--            "/cohort_dchp_stan_result_",cohort_names[current_cohort], -->
+<!--            ".RData",sep='')) -->
+<!-- eta1_mean <- mean(sim_cohort_dchp$eta_1) -->
+<!-- eta2_mean <- mean(sim_cohort_dchp$eta_2) -->
+<!-- eta3_mean <- mean(sim_cohort_dchp$eta_3) -->
+<!-- f_est <- apply(sim_cohort_dchp$f,2,mean) -->
+<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
+<!-- return_df <- cleanObservationPeriod(current_cohort, clean_data) -->
+<!-- unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% -->
+<!--   dplyr::summarize(count=n(), -->
+<!--                    observe=list(observe.id), -->
+<!--                    observe.length=list(observe.time), -->
+<!--                    no.events=list(no.events)) -->
+<!-- unique_observe_win <- unique(return_df[,c("observe.id","observe.time")]) -->
+
+<!-- ks.stat.matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
+<!-- n_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
+<!-- Lambda_matrix <- matrix(list(),nrow=mice_number,ncol=mice_number) -->
+<!-- for(k in 1:mice_number){ -->
+<!--   for(l in c(1:mice_number)[-k]){ -->
+<!--     i<-expert_rank_10[[current_cohort]][k] -->
+<!--     j<-expert_rank_10[[current_cohort]][l] -->
+<!--     pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
+<!--     if(length(pair)>0){ -->
+<!--       param_mean <- list(lambda0=mean(sim_cohort_dchp$lambda0[,pair]), -->
+<!--                          alpha=model1_fn$alpha.fun(f_est[i], -->
+<!--                                                    f_est[j], -->
+<!--                                                    eta1_mean, -->
+<!--                                                    eta2_mean, -->
+<!--                                                    eta3_mean), -->
+<!--                          beta=mean(sim_cohort_dchp$beta)) -->
+<!--       current_window_vec <- unique_pairs_df$observe[[pair]] -->
+<!--       all_Lambda <- numeric(0) -->
+<!--       for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
+<!--         cur_win <- current_window_vec[cur] -->
+<!--         current_event_time <- return_df[return_df$initiator==i& -->
+<!--                                           return_df$recipient == j & -->
+<!--                             return_df$observe.id==cur_win,"event.times"][[1]] -->
+<!--         current_obs_time <- return_df[return_df$initiator==i& -->
+<!--                                         return_df$recipient==j& -->
+<!--                             return_df$observe.id==cur_win,"observe.time"] -->
+<!--         Lambda_vec <- uniHawkesCompensator(object = param_mean, -->
+<!--                               events = c(current_event_time, -->
+<!--                                          current_obs_time)) -->
+<!--         all_Lambda <- c(all_Lambda,Lambda_vec) -->
+<!--         n_matrix[i,j] <- n_matrix[i,j] + length(current_event_time) -->
+<!--       } -->
+<!--       if(length(all_Lambda)>0){ -->
+<!--         ks.stat.matrix[i,j] <-  ks.test(all_Lambda,"pexp", -->
+<!--                                         rate = 1/mean(all_Lambda))$statistic -->
+<!--         Lambda_matrix[i,j][[1]] <- all_Lambda -->
+<!--       } -->
+<!--     } -->
+<!--   } -->
+<!-- } -->
+
+<!-- m2_ks <- ks.stat.matrix -->
+
+<!-- # -------------- KS plot (stat) -->
+<!-- col.vec <- cRamp(as.vector(ks.stat.matrix)) -->
+<!-- ## need to do some sort of transformation between these here -->
+<!-- vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix)))) -->
+<!-- #order(as.vector(ks.stat.matrix),method = "") -->
+
+<!-- values <- as.vector(ks.stat.matrix) -->
+<!-- sorted_vals <- sort(ks.stat.matrix) -->
+<!-- #match(values,sorted_vals) -->
+<!-- col.vec.vir <- vir_cols[match(values,sorted_vals)] -->
+
+<!-- #### -->
+<!-- par(oma = c(6,4,4,1), mar=rep(0,4), -->
+<!--     mgp = c(0, .2, 0)) -->
+<!-- layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12,  -->
+<!--                     byrow = TRUE),rep(12*12+1,12)),  -->
+<!--        widths=c(rep(1,12),2), heights=rep(1,12)) -->
+<!-- for(i in expert_rank_10[[current_cohort]]){ -->
+<!--   for(j in expert_rank_10[[current_cohort]]){ -->
+<!--     if(ks.stat.matrix[i,j]==0){ -->
+<!--       plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="",  -->
+<!--            axes = FALSE, frame=TRUE) -->
+<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], -->
+<!--            border = 0, col = 'white') -->
+<!--     }else{ -->
+<!--       Lambda.test <- Lambda_matrix[i,j][[1]] -->
+<!--       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test), -->
+<!--             ylab="",xlab="",axes = FALSE, frame=TRUE) -->
+<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],  -->
+<!--            border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)]) -->
+<!--       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test), -->
+<!--             ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2) -->
+<!--       plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE, -->
+<!--            verticals = TRUE, col = "red", lwd = 2) -->
+<!--     } -->
+<!--   } -->
+<!-- } -->
+<!-- par(mar = c(0,2,0,3),mgp=c(0,0.8,0)) -->
+
+<!-- col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)), -->
+<!--                             length.out = 100), -->
+<!--                 col.vec = viridis(100)) -->
+
+<!-- temp <- cLegend(as.vector(ks.stat.matrix)) -->
+
+<!-- image(1, col_obj$x.vec, -->
+<!--       matrix(data=col_obj$x.vec,  -->
+<!--              ncol=length(col_obj$x.vec),nrow=1), -->
+<!--       col=col_obj$col.vec, -->
+<!--       xlab="",ylab="",axes=FALSE) -->
+<!-- axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1, -->
+<!--      cex.axis=2.4) -->
+
+<!-- mtext(text=expert_rank_10[[current_cohort]], side=1, -->
+<!--       line=1.8, outer=TRUE, cex=1.8, -->
+<!--       at=1/14*c(1:12)-1/22) -->
+<!-- mtext(text = expert_rank_10[[current_cohort]], -->
+<!--       side = 2, line = 0.5, outer = TRUE, cex = 1.8, -->
+<!--       at =1/12*c(12:1)-1/20, las = 2) -->
+<!-- mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE, -->
+<!--       cex = 2.2, -->
+<!--       at=0.45, font=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r construct ks_diff} -->
+<!-- ks_diff <-  (m2_ks - m1_ks)/m1_ks -->
+<!-- ks_diff[is.nan(ks_diff)] <- 0 -->
+<!-- # -------------- KS plot (stat) -->
+<!-- col.vec <- cRamp(as.vector(ks_diff)) -->
+<!-- ## need to do some sort of transformation between these here -->
+<!-- vir_cols <- viridis::viridis(length((as.vector(ks_diff)))) -->
+<!-- #order(as.vector(ks.stat.matrix),method = "") -->
+
+<!-- values <- as.vector(ks_diff) -->
+<!-- sorted_vals <- sort(ks_diff) -->
+<!-- #match(values,sorted_vals) -->
+<!-- col.vec.vir <- vir_cols[match(values,sorted_vals)] -->
+
+<!-- #### -->
+<!-- par(oma = c(6,4,4,1), mar=rep(0,4), -->
+<!--     mgp = c(0, .2, 0)) -->
+<!-- layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12,  -->
+<!--                     byrow = TRUE),rep(12*12+1,12)),  -->
+<!--        widths=c(rep(1,12),2), heights=rep(1,12)) -->
+<!-- for(i in expert_rank_10[[current_cohort]]){ -->
+<!--   for(j in expert_rank_10[[current_cohort]]){ -->
+<!--     if(ks_diff[i,j]==0){ -->
+<!--       plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="",  -->
+<!--            axes = FALSE, frame=TRUE) -->
+<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], -->
+<!--            border = 0, col = 'white') -->
+<!--     }else{ -->
+<!--       Lambda.test <- Lambda_matrix[i,j][[1]] -->
+<!--       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test), -->
+<!--             ylab="",xlab="",axes = FALSE, frame=TRUE) -->
+<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], -->
+<!--            border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)]) -->
+
+<!--     } -->
+<!--   } -->
+<!-- } -->
+<!-- par(mar = c(0,2,0,3),mgp=c(0,0.8,0)) -->
+
+<!-- col_obj <- list(x.vec = seq(min(as.vector(ks_diff)),max(as.vector(ks_diff)), -->
+<!--                             length.out = 100), -->
+<!--                 col.vec = viridis(100)) -->
+
+<!-- # temp <- cLegend(as.vector(ks_diff)) -->
+
+<!-- image(1, col_obj$x.vec, -->
+<!--       matrix(data=col_obj$x.vec,  -->
+<!--              ncol=length(col_obj$x.vec),nrow=1), -->
+<!--       col=col_obj$col.vec, -->
+<!--       xlab="",ylab="") -->
+<!-- # axis(4, at=c(-0.2,0,0.2), labels=c(-0.2,0,0.2), las= HORIZONTAL<-1, -->
+<!-- #      cex.axis=2.4) -->
+
+<!-- mtext(text=expert_rank_10[[current_cohort]], side=1, -->
+<!--       line=1.8, outer=TRUE, cex=1.8, -->
+<!--       at=1/14*c(1:12)-1/22) -->
+<!-- mtext(text = expert_rank_10[[current_cohort]], -->
+<!--       side = 2, line = 0.5, outer = TRUE, cex = 1.8, -->
+<!--       at =1/12*c(12:1)-1/20, las = 2) -->
+<!-- mtext(text = "(M2 - M1)/M1", side = 3, line = 1.4, outer = TRUE, -->
+<!--       cex = 2.2, -->
+<!--       at=0.45, font=2) -->
+
+<!-- ``` -->
+
+<!-- ```{r construct ks diff normalised by num events} -->
+<!-- norm_diff <- (m2_ks - m1_ks)#/m1_ks -->
+<!-- norm_diff[is.nan(norm_diff)] <- 0 -->
+<!-- count_mat <- matrix(0, nrow = mice_number, ncol = mice_number) -->
+
+<!-- for(i in expert_rank_10[[current_cohort]]) { -->
+<!--   for(j in expert_rank_10[[current_cohort]]) { -->
+<!--     if( norm_diff[i,j] != 0 ) { -->
+<!--       num_events <- unique_pairs_df %>%  -->
+<!--       filter(initiator == i & recipient == j) %>% -->
+<!--       pull(count) -->
+<!--       # diff[i,j] <- diff[i,j] / num_events -->
+<!--       count_mat[i,j] <- num_events -->
+<!--     } -->
+<!--   } -->
+<!-- } -->
+
+<!-- tibble(diff_norm = as.vector(norm_diff), -->
+<!--        events = as.vector(count_mat)) %>% -->
+<!--   filter(events > 0 ) %>% -->
+<!--   ggplot(aes(events,diff_norm)) + geom_point() + -->
+<!--   ylab("M2-M1") + -->
+<!--   theme_minimal() -->
+
+<!-- tibble(diff_norm = as.vector(norm_diff), -->
+<!--        events = as.vector(count_mat)) %>% -->
+<!--   filter(events > 0) %>% -->
+<!--   ggplot(aes(diff_norm)) +  -->
+<!--   geom_histogram() + -->
+<!--   theme_minimal() -->
+
+<!-- ``` -->
+<!-- ```{r repeat for residuals} -->
+<!-- m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort], -->
+<!--                    "/chp_pr_matrix_",cohort_names[current_cohort], -->
+<!--                    ".RDS",sep='')) -->
+
+<!-- m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort], -->
+<!--                      "/dchp_pr_matrix_",cohort_names[current_cohort], -->
+<!--                      ".RDS",sep='')) -->
+
+<!-- tibble(m1pr = as.vector(m1_pr), -->
+<!--        m2pr = as.vector(m2_pr)) %>% -->
+<!--   mutate(diff = m2pr - m1pr) %>% -->
+<!--   ggplot(aes(diff)) +  -->
+<!--   geom_histogram() + -->
+<!--   labs(x = "M2 PR - M1 PR") + -->
+<!--   theme_minimal() -->
+
+<!-- ``` -->
+
+<!-- ```{r compute mean decrease in ks-score} -->
+<!-- summary(as.vector(m2_ks[m2_ks != 0])) -->
+<!-- summary(as.vector(m1_ks[m1_ks != 0])) -->
+
+<!-- t.test(as.vector(m2_ks[m2_ks != 0]), as.vector(m1_ks[m1_ks != 0])) -->
+
+<!-- diff <- as.vector(m2_ks[m2_ks != 0]) - as.vector(m1_ks[m1_ks != 0]) -->
+
+<!-- length(which(diff < 0))/length(diff) -->
+<!-- summary(diff) -->
+<!-- ``` -->
+
+<!-- This is good because it shows the most active animal, shows that individual -->
+<!-- out rate too large for this interaction. Just need to make this more -->
+<!-- like the plots in 2b. -->
 
@@
 text.x.adj <- c(0.3,0.4,0.6,0.5,0.8)
-model_colors <- c("steelblue", "goldenrod2", "firebrick2")
-model_colors <- viridis::viridis(3)
+
+model_colors <- col_df %>% filter(method %in% c("C-HP",
+                                                "C-DCHP", "C-MMHP")) %>%
+  pull(cols)
 
@@
 ```{r fig4b-recover-latent-states,fig.width=8,fig.height=4}
-y.ub <- c(3,3,3)#c(130,72,31)
-x_events <- 135#150
+y.ub <- c(15,15,15)#c(130,72,31)
+x_events <- 190#135#150
 #model_colors <- c("steelblue", "goldenrod2", "firebrick2")
-model_colors <- viridis::viridis(3)
 layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
 layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
-my.xlim <- 140#160#200#130
-my.long.x <- 140#205#134.5
-legend.x <- c(30,30,30)#c(135,135,135)
+my.xlim <- 200#160#200#130
+my.long.x <- 205#205#134.5
+legend.x <- c(50,50,50)#c(135,135,135)
 legend.y <- #c(34,32,32)
-legend.y <- c(2.5,2,2)#c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.y <- c(10,10,10)#c(15,12,15)#c(62,37,18)#c(22,22,22)
 legend.cex <- 1.5 #3
@@
 
-legend(legend.x[2]-20,
+legend(legend.x[2]-45,
        legend.y[2]+2,c("State 0/1 events","State change point"),
@@
        lty = c(NA,NA), lwd=c(NA,4))
-points(14,8+2,pch=1,cex=2,col="blue")
-points(16,8+2,pch=16,cex=2,col="blue")
+points(8,legend.y[2] - 2, pch = 1, cex = 2, col = "blue")
+points(10,legend.y[2] - 2, pch = 16, cex = 2, col = "blue")
 
@@
 
-plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), ylim=c(-3,10), type="n",
+plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), 
+     ylim=c(-3,10), type="n",
      bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
@@
 
-legend(legend.x[1]-20,legend.y[3],c("Overestimation","Underestimation"),
+legend(legend.x[3]-45,legend.y[3]+2, c("Overestimation","Underestimation"),
        col = c(positive.col,negative.col),
@@
 
-```{r est ranks for m1 sim data}
+```{r est ranks for m1 sim data, include=extra_plots, eval=extra_plots}
 m1_path <- "../output/sims/M1/"
@@
 
-```{r plot est ranks M1 and M2}
+```{r plot est ranks M1 and M2, include=extra_plots, eval=extra_plots}
 n_sim <- 50
@@
 
-```{r process m1 for fig4b}
+```{r process m1 for fig4b, include=extra_plots, eval=extra_plots}
 plot.s <- 1#7#9
@@
 
-```{r fig 4b M1 sim}
+```{r fig 4b M1 sim, include=extra_plots, eval=extra_plots}
 source(here("lib","mod_drawHawkesIntensityPaper.R"))
@@
 
-```{r process m2 for fig4b}
+```{r process m2 for fig4b, include=extra_plots, eval=extra_plots}
 plot.s <- 1#7#9
@@
 
-```{r fig 4b M2 sim}
+```{r fig 4b M2 sim, include=extra_plots, eval=extra_plots}
 source(here("lib","mod_drawHawkesIntensityPaper.R"))
@@
 ```{r fig5-residual-ks, fig.height=7}
-cols_plot <- viridis::viridis(4)
+# cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
+#                                              "True"))
+
+cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
+                                 "True")) %>%
+  arrange(factor(method, levels = c("C-HP","C-DCHP","C-MMHP","True"))) %>%
+  pull(cols)
 #load("../output/sim_model3_fit123_residuals.RData")
@@
 
+plot_cols <- col_df %>% filter(method %in% levels(sim_data$name)) %>%
+  pull(cols)
+
 sim_data %>%
   rename(Method = name, corr = value) %>%
-  ggplot(aes(Method,corr)) + geom_boxplot(aes(fill = Method)) +
-  scale_fill_manual(values = viridis::viridis(6)) +
+  ggplot(aes(Method,corr)) + 
+  geom_boxplot(aes(fill = Method), alpha = 0.7) +
+  scale_fill_manual(values = plot_cols) +
   labs(y = "Rank Correlation") + theme_bw() +
@@
 # png(paste(plot_path,"real_rank_one_cohort.png",sep=""),width=600,height=300)
+plot_cols <- col_df %>% filter(method %in% c("AggRank", "C-HP",
+                                "C-DCHP", "C-MMHP")) %>%
+  pull(cols)
 
@@
   geom_boxplot(alpha=0.7) +
-  scale_fill_manual(values = viridis::viridis(4))+
+  scale_fill_manual(values = plot_cols)+
   #scale_fill_manual(values = c("gray", "steelblue", "goldenrod2" , "firebrick2")) +
@@
         geom_boxplot(alpha=0.7, width=0.5) +
-        scale_fill_manual(values = viridis::viridis(4)) + 
+        scale_fill_manual(values = plot_cols) + 
         ggtitle("(b)") +
@@
 # width=600,height=300)
+
+plot_cols_pred <- col_df %>% filter(method %in% levels(temp_plot_df$method)) %>%
+   arrange(factor(method, levels = c("I-MMHP","DSNL",
+                                     "C-HP", "C-DCHP", "C-MMHP"))) %>%
+                    pull(cols)
+
 p3 <- temp_plot_df %>%
@@
   geom_boxplot(alpha=0.7) +
-  scale_fill_manual(values = viridis::viridis(5)) +
+  scale_fill_manual(values = plot_cols_pred) +
   ggtitle("(a)") +
@@
   ylab("Frobenius norm of error") +
-  ylim(0, 150) + # aren't infinite but >150 and <200
+  ylim(0, 100) + # aren't infinite but >150 and <200
   NULL
@@
   geom_boxplot(alpha=0.7) +
-  scale_fill_manual(values = viridis::viridis(5)) +
+  scale_fill_manual(values = plot_cols_pred) +
   #ggtitle("(a)") +
@@
 
-#png(paste(plot_path,"real_predict_N_all_cohort.png",sep=""),width=600,height=300)
+#png(paste(plot_path,"real_predict_N_all_cohort.png",
+# sep=""),width=600,height=300)
 p4 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
@@
                  position=position_dodge(0.2)) +
-  scale_color_manual(values = viridis::viridis(5)[1:5]) + 
+  scale_color_manual(values = plot_cols_pred) + 
   ggtitle("(b)") +
@@
 ```
+
 ```{r fig-8b-frob-norm-boxplot, fig.width=8, fig.height=4}
@@
   ggplot(aes(x=method,y=norm, fill = method)) +
-  geom_boxplot() + 
-  facet_grid(cols = vars(day)) +
+  # facet_grid(cols = vars(day)) +
   geom_boxplot(alpha=0.7) +
-  scale_fill_manual(values = viridis::viridis(5)) +
+  scale_fill_manual(values = plot_cols_pred) +
   ggtitle("(b)") +
@@
                               levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+                              labels = c("I-MMHP","DSNL","C-HP",
+                                         "C-DCHP","C-MMHP"))
 temp_plot_df$day <- factor(temp_plot_df$day)
 
-#png(paste(plot_path,"real_predict_N_all_cohort.png",sep=""),width=600,height=300)
 p4_slides <- ggplot(temp_plot_df, 
@@
 ```{r fig-9a-spearman-rank-cohort1}
-load("../output/plot_rank_predict.RData")
+load(here("output","plot_rank_predict.RData"))
 # current_cohort <- 5
@@
   geom_boxplot(alpha=0.7) +
-  scale_fill_manual(values = viridis::viridis(5)) +
+  scale_fill_manual(values = plot_cols_pred) +
   #scale_fill_manual(values =
@@
   ylab("Spearman rank correlation") +
-  ylim(0, 1)
-p5
+  # ylim(0, 1) +
+  NULL
+p5 + labs(fill = "Method")
 ```
@@
   ylab("Rank correlation") +
-  ylim(0, 1)
+  # ylim(0, 1) +
+  NULL
 p5
@@
                               levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+                              labels = c("I-MMHP","DSNL","C-HP",
+                                         "C-DCHP","C-MMHP"))
 temp_plot_df$day <- factor(temp_plot_df$day)
@@
                 position=position_dodge(0.2)) +
-  scale_color_manual(values = viridis::viridis(5)) +
+  scale_color_manual(values = plot_cols_pred) +
   #scale_color_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
@@
   ylab("Spearman rank correlation") + 
-  coord_cartesian(ylim=c(0,1)) + 
-  guides(color=guide_legend(title="Model")) 
+  # coord_cartesian(ylim=c(0,1)) + 
+  guides(color=guide_legend(title="Method")) 
 p6
+
+all_cohort_rank_df$method <- factor(all_cohort_rank_df$method,
+                              levels = c("mmhp","dsnl","m1","m2","m3"),
+                              labels = c("I-MMHP","DSNL","C-HP",
+                                         "C-DCHP","C-MMHP"))
+
+p7 <- ggplot(all_cohort_rank_df,
+       aes(x=method, y=spearman, fill=method)) + 
+  # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
+  geom_boxplot(alpha = 0.7) +
+  scale_fill_manual(values = plot_cols_pred) +
+  #scale_color_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
+  ggtitle("(b)") +
+  theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_blank(),
+        axis.ticks.x = element_blank(), 
+        legend.position="right") +
+  facet_grid(cols = vars(day)) +
+  xlab("Prediction horizon (day)") + 
+  ylab("Spearman rank corr.") + 
+  # coord_cartesian(ylim=c(0,1)) + 
+  labs(fill = "Method")
+
+p7
+
 ```
@@
 
-```{r construct data for plot, results='hide',message=FALSE,cache=TRUE}
+```{r construct data for plot, results='hide',message=FALSE}
 library(PlayerRatings)
@@
   sd_vec <- apply(sim_gl_array[m,,],1,function(x) sd(na.omit(x)))
-  polygon(c(newx, rev(newx)), c(mean_vec-sd_vec,rev(mean_vec+sd_vec)),col = shade_vec[m], border = NA)
+  polygon(c(newx, rev(newx)), c(mean_vec-sd_vec,rev(mean_vec+sd_vec)),
+          col = shade_vec[m], border = NA)
   #polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
@@
 print(".......state separation plot........")
-total_event_array <- array(0,dim=c(mice_number,mice_number,max(return_df$observe.id)))
-active_event_array <- array(0,dim=c(mice_number,mice_number,max(return_df$observe.id)))
+total_event_array <- array(0,dim = c(mice_number, mice_number,
+                                   max(return_df$observe.id)))
+active_event_array <- array(0,dim = c(mice_number, mice_number,
+                                    max(return_df$observe.id)))
 
@@
   cur_wins <- which(unique_observe_win$day==cur_day)
-  utility_state_day[cur_day,,] <- apply(active_event_array[,,cur_wins],c(1,2),sum)
-  social_state_day[cur_day,,] <- apply(total_event_array[,,cur_wins],c(1,2),sum)-utility_state_day[cur_day,,]
+  utility_state_day[cur_day,,] <- apply(active_event_array[,,cur_wins],
+                                        c(1, 2), sum)
+  social_state_day[cur_day,,] <- apply(total_event_array[,,cur_wins], 
+                                       c(1, 2), sum) - 
+    utility_state_day[cur_day,,]
 }

### 2020-12-01 output_scripts/Paper_Plots.Rmd

@@
 y.ub <- c(15,15,15)#c(130,72,31)
-x_events <- 190#135#150
+x_events <- 135#150
 #model_colors <- c("steelblue", "goldenrod2", "firebrick2")
@@
 layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
-my.xlim <- 200#160#200#130
-my.long.x <- 205#205#134.5
-legend.x <- c(50,50,50)#c(135,135,135)
+my.xlim <- 140#160#200#130
+my.long.x <- 140#205#134.5
+legend.x <- c(40,40,40)#c(135,135,135)
 legend.y <- #c(34,32,32)
@@
 
-legend(legend.x[2]-45,
+legend(legend.x[2]-35,
        legend.y[2]+2,c("State 0/1 events","State change point"),
@@
 
-legend(legend.x[3]-45,legend.y[3]+2, c("Overestimation","Underestimation"),
+legend(legend.x[3]-30,legend.y[3]+2, c("Overestimation","Underestimation"),
        col = c(positive.col,negative.col),

### 2020-12-01 output_scripts/cmmhp_comparison/sim_comparison.Rmd

---
title: "Simulation Comparison"
author: "Owen G. Ward"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: TRUE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(rstan)
library(cmdstanr)
library(compete)
library(posterior)
library(RColorBrewer)

source(here("lib", 'plotUtil.R'))
source(here("lib", 'simulatePrediction.R'))
source(here("lib", 'mmhp.R'))
source(here("lib", 'uniHawkes.R'))
source(here("lib", 'inferLatentMmhp.R'))
source(here("lib",'cleanData.R')) 
source(here("lib",'prepareDataStan.R')) 
source(here("lib",'drawIntensity.R'))
# source(here("lib",'myGlicko.R',sep = ""))
# source(here("lib",'matrixPlotParameter.R',sep = ""))
# source(here("lib",'residualStructureScore.R',sep = ""))
theme_set(theme_minimal())

dc_sim_path <- here::here("output", "sims", "sims_m3_dc")
comm_sim_path <- here::here("output", "common_rate", "sims_m3")
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')

cut_off <- 3
n_sim <- 50

model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1 +
                                                        exp(-eta3*(x-y))))})

model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
                  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})

```

```{r get isi rank, cache = TRUE}
source(here("lib",'naiveRankHierarchy.R'))
source(here("lib",'expertRankHierarchy.R'))

full_data <- readRDS(here("data","mice.RData"))
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
out <- utils::capture.output(for(curr_cohort in fit_cohorts){
  naive_rank_10[[curr_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[curr_cohort]]])
  expert_rank_10[[curr_cohort]] <- expertRankHierarchy(full_data[[cohort_names[curr_cohort]]])
})
```

Here we compare the results of two versions of our C-MMHP model, namely

- The degree corrected model, where the base rate for a given pair is
$$
\lambda_0^{i,j} = \gamma_i + \zeta_j,
$$

- The common base model, with a common base rate $\lambda_0$ across all pairs.

## Compare rank recovery

We first compare rank recovery. Here we simulate data under each of these
two models and wish to examine the rank recovery in each, relative to
the competing C-HP and C-DCHP models.

### Degree Corrected

```{r rank-recov-dc}
m3_files <- list.files(dc_sim_path, pattern = "sim_model3_fit*")

# load(paste0(m1_path,m1_files[1]))
sim_model3_stan_sim1_total <- list()
sim_model3_stan_sim2_total <- list()
sim_model3_stan_sim3_total <- list()

for(i in seq_along(m3_files)) {
  load(here(dc_sim_path, m3_files[i]))
  sim_model3_stan_sim1_total[[i]] <- sim_model3_stan_sim1
  sim_model3_stan_sim2_total[[i]] <- sim_model3_stan_sim2
  sim_model3_stan_sim3_total[[i]] <- sim_model3_stan_sim3

}

n_sim <- 50

par(mfrow=c(3, length(object_par$f_vec_1)),
    mar=c(0,0,1,0),
    oma=c(6.5,11,3.5,1))

y.ub <- c(12,12,12,12,12)
text.y <- c(rep(8,4),8)
text.x <- c(0.1,0.2,0.4,0.7,0.9)
text.x.adj <- c(0.3,0.4,0.6,0.5,0.8)
model_colors <- viridis::viridis(3)

for(m in c(1:3)){
  for(j in c(1:length(object_par$f_vec_1))){
    plot(1,4,xlim=c(0,1),ylim=c(0,y.ub[j]),
         type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)

    ## Posterior density
    # current_result <- eval(parse(text=paste("sim_model3_stan_sim",m,sep="")))
    current_result <- eval(parse(text=paste("sim_model3_stan_sim",
                                            m,
                                            "_total",
                                            sep="")))
    for(i in c(1:n_sim)){
      lines(density(current_result[[i]]$f[,j]),
            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
    }

    ## plot true value
    abline(v=object_par$f_vec_1[j],lwd=1.8,lty=2,col="gray30")

    ## plot box
    box.wdt <- 1.5
    box.col <- "black"
    box(lty = 'solid',col=box.col,lwd=0.7)

    if(m==3){
      text(text.x.adj[j],text.y[j],text.x[j],cex=2.4)
    }
  }
  ## bottom
  mtext(text=expression(f[1],f[2],f[3],f[4],f[5]), side=1, line=2.4, outer=TRUE, 
        at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
        cex=2)
  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.25,
        at=0.5)
  ## top
  # mtext(text="(a)", side=3, line=0, outer=TRUE, cex=2.5,
  #       at=0.5, font=2)
  ## left
  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5, outer=TRUE, 
        at=c(0:2)/3+0.15,
        cex=1.75, las=2)
}

```

### Common rate

We can also do this for the common rate model.
```{r rank-recov-common}
m3_files <- list.files(comm_sim_path, pattern = "sim_model3_fit*")

# load(paste0(m1_path,m1_files[1]))
sim_model3_stan_sim1_total <- list()
sim_model3_stan_sim2_total <- list()
sim_model3_stan_sim3_total <- list()

for(i in seq_along(m3_files)) {
  load(here(comm_sim_path, m3_files[i]))
  sim_model3_stan_sim1_total[[i]] <- sim_model3_stan_sim1
  sim_model3_stan_sim2_total[[i]] <- sim_model3_stan_sim2
  sim_model3_stan_sim3_total[[i]] <- sim_model3_stan_sim3

}

n_sim <- 50

par(mfrow=c(3, length(object_par$f_vec_1)),
    mar=c(0,0,1,0),
    oma=c(6.5,11,3.5,1))

y.ub <- c(12,12,12,12,12)
text.y <- c(rep(8,4),8)
text.x <- c(0.1,0.2,0.4,0.7,0.9)
text.x.adj <- c(0.3,0.4,0.6,0.5,0.8)
model_colors <- viridis::viridis(3)

for(m in c(1:3)){
  for(j in c(1:length(object_par$f_vec_1))){
    plot(1,4,xlim=c(0,1),ylim=c(0,y.ub[j]),
         type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)

    ## Posterior density
    # current_result <- eval(parse(text=paste("sim_model3_stan_sim",m,sep="")))
    current_result <- eval(parse(text=paste("sim_model3_stan_sim",
                                            m,
                                            "_total",
                                            sep="")))
    for(i in c(1:n_sim)){
      lines(density(current_result[[i]]$f[,j]),
            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
    }

    ## plot true value
    abline(v=object_par$f_vec_1[j],lwd=1.8,lty=2,col="gray30")

    ## plot box
    box.wdt <- 1.5
    box.col <- "black"
    box(lty = 'solid',col=box.col,lwd=0.7)

    if(m==3){
      text(text.x.adj[j],text.y[j],text.x[j],cex=2.4)
    }
  }
  ## bottom
  mtext(text=expression(f[1],f[2],f[3],f[4],f[5]), side=1, line=2.4,
        outer=TRUE, 
        at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
        cex=2)
  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.25,
        at=0.5)
  ## top
  # mtext(text="(a)", side=3, line=0, outer=TRUE, cex=2.5,
  #       at=0.5, font=2)
  ## left
  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5,
        outer=TRUE, 
        at=c(0:2)/3+0.15,
        cex=1.75, las=2)
}
```

## KS Statistics and Pearson Residuals

### Degree Corrected Model

```{r ks-pr-computation-dc}
object_par <- list(sim_lambda_0 = 0.08,
                   sim_lambda_1 = 0.16,
                   sim_eta_1 = 2.5,
                   gamma_var = c(0.01, 0.02, 0.03, 0.06, 0.07),
                   zeta_var = c(0.075, 0.02, 0.03, 0.05, 0.08),
                   sim_eta_2 = 0.6,
                   sim_eta_3 = 5,
                   sim_beta = 1.5,
                   f_vec_1 = c(0.1, 0.2, 0.4, 0.7, 0.9))

N_array <- array(0, dim = c(n_sim, length(object_par$f_vec_1),
                         length(object_par$f_vec_1))) 
Lambda_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1))) 
Lambda_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1)))
Lambda_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1))) 
Lambda_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1))) 
PR_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
PR_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1))) 
PR_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
PR_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                               length(object_par$f_vec_1))) 
KS_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
KS_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
KS_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
KS_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                               length(object_par$f_vec_1)))
KS_p_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1)))
KS_p_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1)))
KS_p_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
KS_p_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))

## Iteration on 50 simulations
for(s in c(1:n_sim)){
  load(here(dc_sim_path,paste0("sim_model3_fit123_",s,".RData")))
  load(here(dc_sim_path,paste0("fit123_state_est_",s,".RData",sep='')))
  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data, 
                                        cut_off = cut_off,
                                        N = length(object_par$f_vec_1))

  N_array[s,,] <- clean_sim_data$N_count

  ## model 1
  #########
  model1_par_est <- list(lambda0 = mean(sim_model3_stan_sim1$lambda0),
                         eta_1 = mean(sim_model3_stan_sim1$eta_1),
                         eta_2 = mean(sim_model3_stan_sim1$eta_2),
                         eta_3 = mean(sim_model3_stan_sim1$eta_3),
                         beta = mean(sim_model3_stan_sim1$beta),
                         f = apply(sim_model3_stan_sim1$f, 2, mean))

  for(i in c(1:5)){
    for(j in c(1:5)[-i]){
      current_t <- sim_model3_data$mmhp_matrix[i,j][[1]]$tau
      m1_object <- list(lambda0 = model1_par_est$lambda0,
                        alpha = model1_fn$alpha.fun(model1_par_est$f[i],
                                                  model1_par_est$f[j],
                                                  model1_par_est$eta_1,
                                                  model1_par_est$eta_2,
                                                  model1_par_est$eta_3),
                        beta = model1_par_est$beta)
      Lambda_model1_array[s,i,j] <- 
        uniHawkesIntegralIntensity(object = m1_object, 
                                   events = current_t,
                                   termination = tail(current_t,1))
      Lambda_test <- uniHawkesCompensator(object = m1_object, 
                                          events = current_t)
      KS_model1_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$statistic
      KS_p_model1_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
      PR_model1_array[s,i,j] <- uniHawkesPearsonResidual(object = m1_object, 
                                                         events = current_t,
                                                         termination = 
                                                           tail(current_t,1))
    }
  }

  ## model2
  #############
  model2_par_est <- list(gamma = apply(sim_model3_stan_sim2$gamma, 2, mean),
                         zeta = apply(sim_model3_stan_sim2$zeta,2,mean),
                         eta_1 = mean(sim_model3_stan_sim2$eta_1),
                         eta_2 = mean(sim_model3_stan_sim2$eta_2),
                         eta_3 = mean(sim_model3_stan_sim2$eta_3),
                         beta = mean(sim_model3_stan_sim2$beta),
                         f = apply(sim_model3_stan_sim2$f, 2, mean))

  for(i in c(1:5)){
    for(j in c(1:5)[-i]){
      current_t <- sim_model3_data$mmhp_matrix[i,j][[1]]$tau
      m2_object <- list(lambda0 = model2_par_est$gamma[i] + 
                          model2_par_est$zeta[j],
                        alpha = model1_fn$alpha.fun(model2_par_est$f[i],
                                                    model2_par_est$f[j],
                                                    model2_par_est$eta_1,
                                                    model2_par_est$eta_2,
                                                    model2_par_est$eta_3),
                        beta = model2_par_est$beta)
      Lambda_model2_array[s,i,j] <-
        uniHawkesIntegralIntensity(object = m1_object, 
                                   events = current_t,
                                   termination = tail(current_t,1))
      Lambda_test <- uniHawkesCompensator(object = m2_object,
                                          events = current_t)
      KS_model2_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$statistic
      KS_p_model2_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
      PR_model2_array[s,i,j] <- 
        uniHawkesPearsonResidual(object = m2_object, 
                                 events = current_t,
                                 termination = tail(current_t,1))
    }
  }

  ## Model3 & true model
  ######
  lambda_0_est <- apply(sim_model3_stan_sim3$lambda0, 2, mean)
  lambda_1_est <- apply(sim_model3_stan_sim3$lambda1, 2, mean)
  ## then put these into a matrix
  lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
                         ncol = length(object_par$f_vec_1))
  lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
                         ncol = length(object_par$f_vec_1))
  for(i in seq_along(lambda_0_est)) {
    row_id <- clean_sim_data$I_fit[i]
    col_id <- clean_sim_data$J_fit[i]
    lam0_par_est[row_id, col_id] <- lambda_0_est[i]
    lam1_par_est[row_id, col_id] <- lambda_1_est[i]
  }
  mmhp_par_est <- list(lambda0 = lam0_par_est,
                       lambda1 = lam1_par_est,
                       eta_1 = mean(sim_model3_stan_sim3$eta_1),
                       eta_2 = mean(sim_model3_stan_sim3$eta_2),
                       eta_3 = mean(sim_model3_stan_sim3$eta_3),
                       beta = mean(sim_model3_stan_sim3$beta),
                       f = apply(sim_model3_stan_sim3$f,2,mean))
  clean_sim_data <- cleanSimulationData(raw_data = sim_model3_data, 
                                        cut_off = cut_off,
                                        N = length(object_par$f_vec_1))

  for(i in c(1:5)){
    for(j in c(1:5)[-i]){
      test.mmhp <- sim_model3_data$mmhp_matrix[i,j][[1]]
      temp.t <- test.mmhp$tau
      current.n <- length(temp.t)-1
      time.segment <- seq(0,tail(temp.t,1),length.out=10000)

      object_hat <- list(lambda0=mmhp_par_est$lambda0[i,j],
                         lambda1=mmhp_par_est$lambda1[i,j],
                         alpha=model3_fn$alpha.fun(mmhp_par_est$f[i],
                                                   mmhp_par_est$f[j],
                                                   mmhp_par_est$eta_1,
                                                   mmhp_par_est$eta_2),
                         beta=mmhp_par_est$beta,
                         q1=model3_fn$q1.fun(mmhp_par_est$f[i],
                                             mmhp_par_est$f[j],
                                             mmhp_par_est$eta_3),
                         q2=model3_fn$q0.fun(mmhp_par_est$f[i],
                                             mmhp_par_est$f[j],
                                             mmhp_par_est$eta_3))

      object_true <- lapply(object_matrix,function(x) x[i,j])
      names(object_true) <- c("lambda0","lambda1","alpha","beta","q1","q2")

      ## est Lmabda and [R]
      Lambda.test <- mmhpCompensator(params = object_hat, 
                                     t = temp.t,
                                     pzt=2 - 
                                       event_state_est_lst[i,j][[1]]$zt_v,
                                     if.pzt = FALSE)
      KS_model3_array[s,i,j] <-  ks.test(Lambda.test,"pexp")$statistic
      KS_p_model3_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
      state.est.latent.mmhp <- interpolate_state_est_lst[i,j][[1]]
      step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,
                              2 - state.est.latent.mmhp$z.hat)
      est.intensity <- mmhpIntensityNumeric(params = object_hat,
                                            t = temp.t[-1],
                                            time.vec = time.segment,
                                            latent.vec = 
                                              step.fun.est(time.segment))
      est.intensity.events <- mmhpIntensityAtEvents(params=object_hat,
                                                    t = temp.t,
                                  latent_z = 
                                    event_state_est_lst[i,j][[1]]$zt_v)
      Lambda_model3_array[s,i,j] <-
        sum(est.intensity)*(time.segment[2]-time.segment[1])
      PR_model3_array[s,i,j] <- sum(1/sqrt(est.intensity.events))-
        sum(sqrt(est.intensity))*(time.segment[2]-time.segment[1])

      ## Under the true model
      Lambda.test.true <- mmhpCompensator(params = object_true,
                                          t = temp.t,
                                          pzt = 2 - 
                                            test.mmhp$zt[2:length(test.mmhp$zt)],
                                          if.pzt=FALSE)
      KS_true_array[s,i,j] <-  ks.test(Lambda.test.true,"pexp")$statistic
      KS_p_true_array[s,i,j] <-  ks.test(Lambda.test.true,"pexp")$p.value
      true.intensity <- 
        mmhpTrueIntensityNumeric(params = object_true,
                                                 t = temp.t,
                                 latent = list(x = 
                                                fixStateTransition(test.mmhp)$x,
                                               z = 
                                                fixStateTransition(test.mmhp)$z),
                                     time.vec = time.segment)
      true.intensity.events <- mmhpIntensityAtEvents(params = object_true,
                                                     t = temp.t, 
                                                     latent_z = test.mmhp$zt)
      Lambda_true_array[s,i,j] <- sum(true.intensity$lambda.t)*(time.segment[2]-time.segment[1])
      PR_true_array[s,i,j] <- sum(1/sqrt(true.intensity.events))-
        sum(sqrt(true.intensity$lambda.t))*(time.segment[2]-time.segment[1])
    }
  }
}

cols_plot <- viridis::viridis(4)
#load("../output/sim_model3_fit123_residuals.RData")
par(mfrow=c(5,5),mar=c(0.2,0.2,0.2,0.2),oma=c(2.4,2.4,2.9,0.5))
for(i in c(5:1)){
  for(j in c(5:1)){
    if(i==j){
      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
      if(i==5){
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04, 
                col = cols_plot[1], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,
                col = cols_plot[2], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,
                col = cols_plot[3], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,
                col = cols_plot[4], border = NA)
        text(c(0.43,0.58,0.61,0.4), seq(0.8,0.14,-0.22),
             c("C-HP", "C-DCHP", "C-MMHP", "True"),
             cex=1.7)
      }
    }else{
      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
      PR <- c(KS_model1_array[,i,j], KS_model2_array[,i,j],
              KS_model3_array[,i,j], KS_true_array[,i,j])
      ### try pr scores instead
      # PR <- c(PR_model1_array[,i,j],PR_model2_array[,i,j],
      #         PR_model3_array[,i,j],PR_true_array[,i,j])
      Type <- c(rep(1,n_sim), rep(2,n_sim), rep(3,n_sim), rep(4,n_sim))
      boxplot(PR ~ Type,  
              col = cols_plot,
              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
              xlab="",ylab="",xaxt="n",yaxt="n")
      #names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
    }
  }
}
mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
      at=c(0:4)/5+0.1)
mtext(text=c(5:1), side=1, line=1, outer=TRUE, cex=2,
      at=c(0:4)/5+0.1)
mtext(text="Degree Corrected KS",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

#####
par(mfrow=c(5,5),mar=c(0.2,0.2,0.2,0.2),oma=c(2.4,2.4,2.9,0.5))
for(i in c(5:1)){
  for(j in c(5:1)){
    if(i==j){
      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
      if(i==5){
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04, 
                col = cols_plot[1], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,
                col = cols_plot[2], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,
                col = cols_plot[3], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,
                col = cols_plot[4], border = NA)
        text(c(0.43,0.58,0.61,0.4), seq(0.8,0.14,-0.22),
             c("C-HP", "C-DCHP", "C-MMHP", "True"),
             cex=1.7)
      }
    }else{
      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
      # PR <- c(KS_model1_array[,i,j], KS_model2_array[,i,j],
      #         KS_model3_array[,i,j], KS_true_array[,i,j])
      ### try pr scores instead
      PR <- c(PR_model1_array[,i,j],PR_model2_array[,i,j],
              PR_model3_array[,i,j],PR_true_array[,i,j])
      Type <- c(rep(1,n_sim), rep(2,n_sim), rep(3,n_sim), rep(4,n_sim))
      boxplot(PR ~ Type,  
              col = cols_plot,
              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
              xlab="",ylab="",xaxt="n",yaxt="n")
      #names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
    }
  }
}
mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
      at=c(0:4)/5+0.1)
mtext(text=c(5:1), side=1, line=1, outer=TRUE, cex=2,
      at=c(0:4)/5+0.1)
mtext(text="Degree Corrected PR",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

```

### Common rate model

```{r ks-pr-common-rate model}
complete_sims <- 1:n_sim
complete_sims <- complete_sims[-29]

N_array <- array(0, dim = c(n_sim, length(object_par$f_vec_1),
                         length(object_par$f_vec_1))) 
Lambda_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1))) 
Lambda_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1)))
Lambda_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1))) 
Lambda_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1))) 
PR_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
PR_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1))) 
PR_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
PR_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                               length(object_par$f_vec_1))) 
KS_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
KS_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
KS_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
KS_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                               length(object_par$f_vec_1)))
KS_p_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1)))
KS_p_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1)))
KS_p_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
KS_p_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))

## Iteration on 50 simulations
for(s in 30:n_sim){
  load(here(comm_sim_path, paste0("sim_model3_fit123_",s,".RData")))
  load(here(comm_sim_path, paste0("fit123_state_est_",s,".RData",sep='')))
  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data, 
                                        cut_off = cut_off,
                                        N = length(object_par$f_vec_1))

  N_array[s,,] <- clean_sim_data$N_count

  ## model 1
  #########
  model1_par_est <- list(lambda0 = mean(sim_model3_stan_sim1$lambda0),
                         eta_1 = mean(sim_model3_stan_sim1$eta_1),
                         eta_2 = mean(sim_model3_stan_sim1$eta_2),
                         eta_3 = mean(sim_model3_stan_sim1$eta_3),
                         beta = mean(sim_model3_stan_sim1$beta),
                         f = apply(sim_model3_stan_sim1$f, 2, mean))

  for(i in c(1:5)){
    for(j in c(1:5)[-i]){
      current_t <- sim_model3_data$mmhp_matrix[i,j][[1]]$tau
      m1_object <- list(lambda0 = model1_par_est$lambda0,
                        alpha = model1_fn$alpha.fun(model1_par_est$f[i],
                                                  model1_par_est$f[j],
                                                  model1_par_est$eta_1,
                                                  model1_par_est$eta_2,
                                                  model1_par_est$eta_3),
                        beta = model1_par_est$beta)
      Lambda_model1_array[s,i,j] <- 
        uniHawkesIntegralIntensity(object = m1_object, 
                                   events = current_t,
                                   termination = tail(current_t,1))
      Lambda_test <- uniHawkesCompensator(object = m1_object, 
                                          events = current_t)
      KS_model1_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$statistic
      KS_p_model1_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
      PR_model1_array[s,i,j] <- uniHawkesPearsonResidual(object = m1_object, 
                                                         events = current_t,
                                                         termination = 
                                                           tail(current_t,1))
    }
  }

  ## model2
  #############
  model2_par_est <- list(gamma = apply(sim_model3_stan_sim2$gamma, 2, mean),
                         zeta = apply(sim_model3_stan_sim2$zeta,2,mean),
                         eta_1 = mean(sim_model3_stan_sim2$eta_1),
                         eta_2 = mean(sim_model3_stan_sim2$eta_2),
                         eta_3 = mean(sim_model3_stan_sim2$eta_3),
                         beta = mean(sim_model3_stan_sim2$beta),
                         f = apply(sim_model3_stan_sim2$f, 2, mean))

  for(i in c(1:5)){
    for(j in c(1:5)[-i]){
      current_t <- sim_model3_data$mmhp_matrix[i,j][[1]]$tau
      m2_object <- list(lambda0 = model2_par_est$gamma[i] + 
                          model2_par_est$zeta[j],
                        alpha = model1_fn$alpha.fun(model2_par_est$f[i],
                                                    model2_par_est$f[j],
                                                    model2_par_est$eta_1,
                                                    model2_par_est$eta_2,
                                                    model2_par_est$eta_3),
                        beta = model2_par_est$beta)
      Lambda_model2_array[s,i,j] <-
        uniHawkesIntegralIntensity(object = m1_object, 
                                   events = current_t,
                                   termination = tail(current_t,1))
      Lambda_test <- uniHawkesCompensator(object = m2_object,
                                          events = current_t)
      KS_model2_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$statistic
      KS_p_model2_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
      PR_model2_array[s,i,j] <- 
        uniHawkesPearsonResidual(object = m2_object, 
                                 events = current_t,
                                 termination = tail(current_t,1))
    }
  }

  ## Model3 & true model
  ######
  # lambda_0_est <- apply(sim_model3_stan_sim3$lambda0, 2, mean)
  # lambda_1_est <- apply(sim_model3_stan_sim3$lambda1, 2, mean)
  # ## then put these into a matrix
  # lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
  #                        ncol = length(object_par$f_vec_1))
  # lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
  #                        ncol = length(object_par$f_vec_1))
  # for(i in seq_along(lambda_0_est)) {
  #   row_id <- clean_sim_data$I_fit[i]
  #   col_id <- clean_sim_data$J_fit[i]
  #   lam0_par_est[row_id, col_id] <- lambda_0_est[i]
  #   lam1_par_est[row_id, col_id] <- lambda_1_est[i]
  # }
  mmhp_par_est <- list(lambda0 = mean(sim_model3_stan_sim3$lambda0),
                       lambda1 = mean(sim_model3_stan_sim3$lambda1),
                       eta_1 = mean(sim_model3_stan_sim3$eta_1),
                       eta_2 = mean(sim_model3_stan_sim3$eta_2),
                       eta_3 = mean(sim_model3_stan_sim3$eta_3),
                       beta = mean(sim_model3_stan_sim3$beta),
                       f = apply(sim_model3_stan_sim3$f,2,mean))
  clean_sim_data <- cleanSimulationData(raw_data = sim_model3_data, 
                                        cut_off = cut_off,
                                        N = length(object_par$f_vec_1))

  for(i in c(1:5)){
    for(j in c(1:5)[-i]){
      test.mmhp <- sim_model3_data$mmhp_matrix[i,j][[1]]
      temp.t <- test.mmhp$tau
      current.n <- length(temp.t)-1
      time.segment <- seq(0,tail(temp.t,1),length.out=10000)

      object_hat <- list(lambda0=mmhp_par_est$lambda0,
                         lambda1=mmhp_par_est$lambda1,
                         alpha=model3_fn$alpha.fun(mmhp_par_est$f[i],
                                                   mmhp_par_est$f[j],
                                                   mmhp_par_est$eta_1,
                                                   mmhp_par_est$eta_2),
                         beta=mmhp_par_est$beta,
                         q1=model3_fn$q1.fun(mmhp_par_est$f[i],
                                             mmhp_par_est$f[j],
                                             mmhp_par_est$eta_3),
                         q2=model3_fn$q0.fun(mmhp_par_est$f[i],
                                             mmhp_par_est$f[j],
                                             mmhp_par_est$eta_3))

      object_true <- lapply(object_matrix,function(x) x[i,j])
      names(object_true) <- c("lambda0","lambda1","alpha","beta","q1","q2")

      ## est Lmabda and [R]
      Lambda.test <- mmhpCompensator(params = object_hat, 
                                     t = temp.t,
                                     pzt=2 - 
                                       event_state_est_lst[i,j][[1]]$zt_v,
                                     if.pzt = FALSE)
      KS_model3_array[s,i,j] <-  ks.test(Lambda.test,"pexp")$statistic
      KS_p_model3_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
      state.est.latent.mmhp <- interpolate_state_est_lst[i,j][[1]]
      step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,
                              2 - state.est.latent.mmhp$z.hat)
      est.intensity <- mmhpIntensityNumeric(params = object_hat,
                                            t = temp.t[-1],
                                            time.vec = time.segment,
                                            latent.vec = 
                                              step.fun.est(time.segment))
      est.intensity.events <- mmhpIntensityAtEvents(params=object_hat,
                                                    t = temp.t,
                                  latent_z = 
                                    event_state_est_lst[i,j][[1]]$zt_v)
      Lambda_model3_array[s,i,j] <-
        sum(est.intensity)*(time.segment[2]-time.segment[1])
      PR_model3_array[s,i,j] <- sum(1/sqrt(est.intensity.events))-
        sum(sqrt(est.intensity))*(time.segment[2]-time.segment[1])

      ## Under the true model
      Lambda.test.true <- mmhpCompensator(params = object_true,
                                          t = temp.t,
                                          pzt = 2 - 
                                            test.mmhp$zt[2:length(test.mmhp$zt)],
                                          if.pzt=FALSE)
      KS_true_array[s,i,j] <-  ks.test(Lambda.test.true,"pexp")$statistic
      KS_p_true_array[s,i,j] <-  ks.test(Lambda.test.true,"pexp")$p.value
      true.intensity <- 
        mmhpTrueIntensityNumeric(params = object_true,
                                                 t = temp.t,
                                 latent = list(x = 
                                                fixStateTransition(test.mmhp)$x,
                                               z = 
                                                fixStateTransition(test.mmhp)$z),
                                     time.vec = time.segment)
      true.intensity.events <- mmhpIntensityAtEvents(params = object_true,
                                                     t = temp.t, 
                                                     latent_z = test.mmhp$zt)
      Lambda_true_array[s,i,j] <- sum(true.intensity$lambda.t)*(time.segment[2]-time.segment[1])
      PR_true_array[s,i,j] <- sum(1/sqrt(true.intensity.events))-
        sum(sqrt(true.intensity$lambda.t))*(time.segment[2]-time.segment[1])
    }
  }
}

cols_plot <- viridis::viridis(4)
#load("../output/sim_model3_fit123_residuals.RData")
par(mfrow=c(5,5),mar=c(0.2,0.2,0.2,0.2),oma=c(2.4,2.4,2.9,0.5))
for(i in c(5:1)){
  for(j in c(5:1)){
    if(i==j){
      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
      if(i==5){
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04, 
                col = cols_plot[1], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,
                col = cols_plot[2], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,
                col = cols_plot[3], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,
                col = cols_plot[4], border = NA)
        text(c(0.43,0.58,0.61,0.4), seq(0.8,0.14,-0.22),
             c("C-HP", "C-DCHP", "C-MMHP", "True"),
             cex=1.7)
      }
    }else{
      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
      PR <- c(KS_model1_array[,i,j], KS_model2_array[,i,j],
              KS_model3_array[,i,j], KS_true_array[,i,j])
      ### try pr scores instead
      # PR <- c(PR_model1_array[,i,j],PR_model2_array[,i,j],
      #         PR_model3_array[,i,j],PR_true_array[,i,j])
      Type <- c(rep(1,n_sim), rep(2,n_sim), rep(3,n_sim), rep(4,n_sim))
      boxplot(PR ~ Type,  
              col = cols_plot,
              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
              xlab="",ylab="",xaxt="n",yaxt="n")
      #names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
    }
  }
}
mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
      at=c(0:4)/5+0.1)
mtext(text=c(5:1), side=1, line=1, outer=TRUE, cex=2,
      at=c(0:4)/5+0.1)
mtext(text="Common Rate KS",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

####
cols_plot <- viridis::viridis(4)
#load("../output/sim_model3_fit123_residuals.RData")
par(mfrow=c(5,5),mar=c(0.2,0.2,0.2,0.2),oma=c(2.4,2.4,2.9,0.5))
for(i in c(5:1)){
  for(j in c(5:1)){
    if(i==j){
      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
      if(i==5){
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04, 
                col = cols_plot[1], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,
                col = cols_plot[2], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,
                col = cols_plot[3], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,
                col = cols_plot[4], border = NA)
        text(c(0.43,0.58,0.61,0.4), seq(0.8,0.14,-0.22),
             c("C-HP", "C-DCHP", "C-MMHP", "True"),
             cex=1.7)
      }
    }else{
      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
      # PR <- c(KS_model1_array[,i,j], KS_model2_array[,i,j],
      #         KS_model3_array[,i,j], KS_true_array[,i,j])
      ### try pr scores instead
      PR <- c(PR_model1_array[,i,j],PR_model2_array[,i,j],
              PR_model3_array[,i,j],PR_true_array[,i,j])
      Type <- c(rep(1,n_sim), rep(2,n_sim), rep(3,n_sim), rep(4,n_sim))
      boxplot(PR ~ Type,  
              col = cols_plot,
              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
              xlab="",ylab="",xaxt="n",yaxt="n")
      #names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
    }
  }
}
mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
      at=c(0:4)/5+0.1)
mtext(text=c(5:1), side=1, line=1, outer=TRUE, cex=2,
      at=c(0:4)/5+0.1)
mtext(text="Common Rate PR",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

```

This indicates a similar predictive performance for both these models,
when correctly implemented.

## Rank Single Cohort

### Degree Corrected Model

```{r single cohort rank dc}
rank_cohort <- 5
current_cohort <- rank_cohort

load(paste(here("output", "/"),
           cohort_names[current_cohort],
           "/agg_rank_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(here("output", "/"),
           cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(here("output", "/"),
           cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(here("output", "/"),
           cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

no_method <- 4
plot_latent_df <- data.frame(Methods = rep(1:no_method,
                                           each = 1000*mice_number),
                             Mice = rep(rep(1:mice_number, each = 1000),
                                        no_method),
                             force = rep(0, 1000*mice_number*no_method))
## agg
plot_latent_df$force[(1:(1000*mice_number))] <-
  as.vector(sim_agg_rank$x[1001:2000,])

## M1
plot_latent_df$force[(1:(1000*mice_number)) + 
                       1000*mice_number] <- as.vector(sim_cohort_hp$f)

## M2
plot_latent_df$force[(1:(1000*mice_number)) + 
                       2000*mice_number] <- as.vector(sim_cohort_dchp$f)

## M3
plot_latent_df$force[(1:(1000*mice_number)) + 
                       3000*mice_number] <- as.vector(sim_cohort_mmhp$f)

plot_latent_df$Mice <- factor(plot_latent_df$Mice,
                              levels = expert_rank_10[[current_cohort]])
plot_latent_df$Method <- factor(plot_latent_df$Method,
                                labels =
                                  c("AggRanking","C-HP","C-DCHP","C-MMHP"))

p1 <- ggplot(plot_latent_df, 
             aes(x = Mice, y = force, fill = Method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(4)) +
  ggtitle("Degree Corrected") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 10),
        legend.position="none") +
  facet_grid(cols=vars(Method)) +
  xlab("Mice (ranked by I&SI method)") +
  ylab("Latent rank")
p1

```

### Common Rate Model

```{r single cohort rank common rate}
current_cohort <- rank_cohort

load(paste(here("output", "common_rate", "/"),
           cohort_names[current_cohort],
           "/agg_rank_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(here("output", "common_rate", "/"),
           cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(here("output", "common_rate", "/"),
           cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(here("output", "common_rate", "/"),
           cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

no_method <- 4
plot_latent_df <- data.frame(Methods = rep(1:no_method,
                                           each = 1000*mice_number),
                             Mice = rep(rep(1:mice_number, each = 1000),
                                        no_method),
                             force = rep(0, 1000*mice_number*no_method))
## agg
plot_latent_df$force[(1:(1000*mice_number))] <-
  as.vector(sim_agg_rank$x[1001:2000,])

## M1
plot_latent_df$force[(1:(1000*mice_number)) + 
                       1000*mice_number] <- as.vector(sim_cohort_hp$f)

## M2
plot_latent_df$force[(1:(1000*mice_number)) + 
                       2000*mice_number] <- as.vector(sim_cohort_dchp$f)

## M3
plot_latent_df$force[(1:(1000*mice_number)) + 
                       3000*mice_number] <- as.vector(sim_cohort_mmhp$f)

plot_latent_df$Mice <- factor(plot_latent_df$Mice,
                              levels = expert_rank_10[[current_cohort]])
plot_latent_df$Method <- factor(plot_latent_df$Method,
                                labels =
                                  c("AggRanking","C-HP","C-DCHP","C-MMHP"))

p1 <- ggplot(plot_latent_df, 
             aes(x = Mice, y = force, fill = Method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(4)) +
  ggtitle("Degree Corrected") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 10),
        legend.position="none") +
  facet_grid(cols=vars(Method)) +
  xlab("Mice (ranked by I&SI method)") +
  ylab("Latent rank")
p1
```

## Overall Rank

### Degree Corrected Model

```{r all cohorts dc}
load(here("output",
          "weighted_rank_data.RData"))
no_method <- 4
plot_cor_df <- data.frame(Method=rep(c(1:no_method),each=10),
                          cor=as.vector(spearman_df))
plot_cor_df$Method <- factor(plot_cor_df$Method,
                             labels = c("Agg-rank","C-HP","C-DCHP","C-MMHP"))
p2 <- ggplot(plot_cor_df, aes(x="", y = cor, fill = Method)) +
        geom_boxplot(alpha=0.7, width=0.5) +
        scale_fill_manual(values = viridis::viridis(4)) + 
        ggtitle("Degree Corrected Model") +
        ylim(0,1) +
        theme_bw() +
        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
              text = element_text(size = 20),
              axis.text.y =element_text(size = 11),
              legend.position="none",
              axis.title.x=element_blank()) +
        facet_grid(cols=vars(Method)) +
        ylab("Spearman rank correlation")
p2

```

### Common Rate Model

```{r all cohorts comm rate}
load(here("output", "common_rate",
          "weighted_rank_data.RData"))
no_method <- 4
plot_cor_df <- data.frame(Method=rep(c(1:no_method),each=10),
                          cor=as.vector(spearman_df))
plot_cor_df$Method <- factor(plot_cor_df$Method,
                             labels = c("Agg-rank","C-HP","C-DCHP","C-MMHP"))
p2 <- ggplot(plot_cor_df, aes(x="", y = cor, fill = Method)) +
        geom_boxplot(alpha=0.7, width=0.5) +
        scale_fill_manual(values = viridis::viridis(4)) + 
        ggtitle("Common Rate Model") +
        ylim(0,1) +
        theme_bw() +
        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
              text = element_text(size = 20),
              axis.text.y =element_text(size = 11),
              legend.position="none",
              axis.title.x=element_blank()) +
        facet_grid(cols=vars(Method)) +
        ylab("Spearman rank correlation")
p2
```

## Predicted Events Single Cohort

### Degree Corrected Model

```{r predict single cohort dc}
load(here("output","plot_N_predict.RData"))
current_cohort <- 5# cohort 1 looks worse than rest

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
p3 <- temp_plot_df %>%
  rowwise() %>%
  #mutate(norm = min(norm,60)) %>%
  # rename(Method = method) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 150) + # aren't infinite but >150 and <200
  NULL
p3 + labs(fill = "Method")
```

### Common Rate Model

```{r predict single cohort comm rate}
load(here("output", "common_rate", "plot_N_predict.RData"))
current_cohort <- 5# cohort 1 looks worse than rest

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
# width=600,height=300)
p3 <- temp_plot_df %>%
  rowwise() %>%
  #mutate(norm = min(norm,60)) %>%
  # rename(Method = method) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("Common Rate") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 100) + # aren't infinite but >150 and <200
  NULL
p3 + labs(fill = "Method")
```

## Predicted Events All Cohorts

### Degree Corrected Model

```{r all cohorts predict dc}
load(here("output",
          "plot_N_predict.RData"))

# median prediction for each cohort here

all_cohort_box <- all_cohort_norm_df

all_cohort_box$method <- factor(all_cohort_box$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL",
                                         "C-HP","C-DCHP",
                                         "C-MMHP"))
all_cohort_box$day <- factor(all_cohort_box$day)

all_cohort_box %>% 
  ggplot(aes(x=method,y=norm, fill = method)) +
  geom_boxplot() + 
  facet_grid(cols = vars(day)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("Degree Corrected") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  # guides(color=guide_legend(title="Method")) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  labs(fill = "Method") +
  # ylim(0, 80) +
  NULL
```

### Common Rate Model

```{r all cohort predict comm rate}
load(here("output",
          "common_rate",
          "plot_N_predict.RData"))

# median prediction for each cohort here

all_cohort_box <- all_cohort_norm_df

all_cohort_box$method <- factor(all_cohort_box$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL",
                                         "C-HP","C-DCHP",
                                         "C-MMHP"))
all_cohort_box$day <- factor(all_cohort_box$day)

all_cohort_box %>% 
  ggplot(aes(x=method,y=norm, fill = method)) +
  geom_boxplot() + 
  facet_grid(cols = vars(day)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("Common Rate") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  # guides(color=guide_legend(title="Method")) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  labs(fill = "Method") +
  # ylim(0, 80) +
  NULL

# all_sims <- do.call(rbind,predict_day_norm_df_lst)
# all_sims <- all_cohort_norm_df
# 
# all_sims$method <- factor(all_sims$method,
#                               levels = c("mmhp","dsnl","m1","m2","m3"),
#                               labels = c("I-MMHP","DSNL",
#                                          "C-HP","C-DCHP",
#                                          "C-MMHP"))
# 
# all_sims %>%
#   ggplot(aes(x = method, y = norm, fill = method)) +
#   geom_boxplot() +
#   facet_grid(cols = vars(day)) +
#   scale_fill_manual(values = viridis::viridis(5)) +
#    ggtitle("Common Rate") +
#   theme_bw() +
#   theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
#         text = element_text(size = 20),
#         axis.text.x=element_blank(),
#         axis.ticks.x = element_blank(),
#         legend.position="right") +
#   facet_grid(cols=vars(day)) +
#   # guides(color=guide_legend(title="Method")) +
#   xlab("Prediction horizon (day)") + 
#   ylab("Frobenius norm of error") +
#   labs(fill = "Method") +
#   ylim(0, 80) +
#   NULL

```

## Predicted Rank Single Cohort

### Degree Corrected Model

```{r pred rank single cohort degree corrected}
load(here("output", "plot_rank_predict.RData"))
current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP",
                                         "C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),
# width=600,height=300)
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #scale_fill_manual(values =
  # c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
  ggtitle("Degree Corrected") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank correlation") +
  # ylim(0, 1) +
  NULL
p5
```

### Common Rate Model

```{r rank predict single cohort common rate}
load(here("output", "common_rate", "plot_rank_predict.RData"))
current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP",
                                         "C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),
# width=600,height=300)
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #scale_fill_manual(values =
  # c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
  ggtitle("Common Rate") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank correlation") 
  # ylim(0, 1)
p5 + labs(fill = "Method")

```

## Predicted Rank All Cohorts

### Degree Corrected Model

```{r pred rank all cohorts degree corrected}
load(here("output", "plot_rank_predict.RData"))
# temp_plot_df <- all_cohort_rank_df %>% 
#   group_by(day, method) %>% 
#   summarize(avg=mean(spearman), n= n(), sd=sd(spearman))

all_cohort_rank_df$method <- factor(all_cohort_rank_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
all_cohort_rank_df$day <- factor(all_cohort_rank_df$day)

p6 <- ggplot(all_cohort_rank_df,
             aes(x=method, y=spearman, fill = method)) + 
  geom_boxplot(alpha = 0.7) +
  # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  # geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
  #               position=position_dodge(0.2)) +
  scale_color_manual(values = viridis::viridis(5)) +
  #scale_color_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
  ggtitle("Degree Corrected") +
  theme_bw() +
  facet_grid(cols = vars(day)) +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") + 
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank correlation") + 
  coord_cartesian(ylim=c(0,1)) + 
  guides(color=guide_legend(title="Model")) 
p6

```

### Common Rate Model

```{r pred rank all cohorts comm rate}
load(here("output", "common_rate", "plot_rank_predict.RData"))
# temp_plot_df <- all_cohort_rank_df %>% 
#   group_by(day, method) %>% 
#   summarize(avg=mean(spearman), n= n(), sd=sd(spearman))

all_cohort_rank_df$method <- factor(all_cohort_rank_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
all_cohort_rank_df$day <- factor(all_cohort_rank_df$day)

p6 <- ggplot(all_cohort_rank_df,
             aes(x=method, y=spearman, fill = method)) + 
  geom_boxplot(alpha = 0.7) +
  # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  # geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
  #               position=position_dodge(0.2)) +
  scale_color_manual(values = viridis::viridis(5)) +
  #scale_color_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
  ggtitle("Common Rate") +
  theme_bw() +
  facet_grid(cols = vars(day)) +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") + 
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank correlation") + 
  coord_cartesian(ylim=c(0,1)) + 
  guides(color=guide_legend(title="Model")) 
p6

```

## Pearson Residuals

### Degree Corrected Model

```{r dc pr matrix}
dc_cohort <- 5
current_cohort <- dc_cohort

source(here("lib", "matrixPlotParameter.R"))

m1_pr <- readRDS(paste(here("output", "/"),
                       cohort_names[current_cohort],
                   "/chp_pr_matrix_",cohort_names[current_cohort],
                   ".RDS",sep=''))

m2_pr <- readRDS(paste(here("output", "/"),
                       cohort_names[current_cohort],
                     "/dchp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

m3_pr <- readRDS(paste(here("output", "/"),
                       cohort_names[current_cohort],
                     "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

indep_pr <- readRDS(paste(here("output", "/"),
                          cohort_names[current_cohort],
                     "/immhp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

matrix_lst_plot <- list(
                        indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
#cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-80,max=80,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
                  )

```

### Common Rate Model

```{r PR matrix common rate}
comm_data_path <- "../output/common_rate/"
current_cohort <- dc_cohort

source(here("lib", "matrixPlotParameter.R"))

m1_pr <- readRDS(paste(here("output","common_rate","/"),
                       cohort_names[current_cohort],
                   "/chp_pr_matrix_",cohort_names[current_cohort],
                   ".RDS",sep=''))

m2_pr <- readRDS(paste(here("output","common_rate", "/"),
                       cohort_names[current_cohort],
                     "/dchp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

m3_pr <- readRDS(paste(here("output","common_rate", "/"),
                       cohort_names[current_cohort],
                     "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

indep_pr <- readRDS(paste(here("output", "common_rate", "/"),
                          cohort_names[current_cohort],
                     "/immhp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

matrix_lst_plot <- list(
                        indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
#cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-80,max=80,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
                  )

```

### 2020-12-01 run_scripts/comm_rate_run/c_mmhp.R
updates to run scripts

@@ -11,7 +11,7 @@ jobid <- as.numeric(jobid)
 cohort_id <- jobid
 #cohort_id <- 1
 ####
-save_data_path <- "output/common_rate_small/"  #"output_june30/"
+save_data_path <- "output/common_rate/"  #"output_june30/"
 
 ### specify the number of segments here
 no_segments <- 500

### 2020-12-01 run_scripts/diagnostics.R

@@ -13,7 +13,7 @@ jobid <- as.numeric(jobid)
 cohort_id <- jobid
 # cohort_id <- 1
 ####
-data_path <- "output/common_rate/"
+data_path <- "output/"
 
 
 # library(rstan)

### 2020-12-01 run_scripts/predict.R

@@ -10,7 +10,7 @@ jobid <- as.numeric(jobid)
 cohort_id <- jobid
 #cohort_id <- 1
 ####
-data_path <- "output/common_rate/"
+data_path <- "output/"
 
 
 library(rstan)

### 2020-12-01 run_scripts/sim_fits.R

@@ -4,7 +4,7 @@
 #### if running on cluster ####
 source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
 
-data_path <- "output/common_rate/sims_m3_sparse/"
+data_path <- "output/sims_m3_sparse/"
 
 library(rstan)
 options(mc.cores = parallel::detectCores())

### 2020-12-01 output_scripts/Paper_Plots.Rmd
update plots

@@
 ## Figure 4a Recover Latent Ranks
-```{r fig-4a, fig.height=4,fig.width=8}
+```{r fig-4a, fig.height=6,fig.width=8}
 sim_data_path <- "../output/sims/sims_m3_dc/"
@@
 
-```{r fig4b-recover-latent-states,fig.width=8,fig.height=4}
+```{r fig4b-recover-latent-states,fig.width=8,fig.height=5}
 y.ub <- c(15,15,15)#c(130,72,31)
-x_events <- 135#150
-#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
-layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
+x_events <- 190#135#150
 layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
-my.xlim <- 140#160#200#130
-my.long.x <- 140#205#134.5
-legend.x <- c(40,40,40)#c(135,135,135)
+my.xlim <- 200#160#200#130
+my.long.x <- 205#205#134.5
+legend.x <- c(150,150,150)#c(135,135,135)
 legend.y <- #c(34,32,32)
-legend.y <- c(10,10,10)#c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.y <- c(12,12,12)#c(15,12,15)#c(62,37,18)#c(22,22,22)
 legend.cex <- 1.5 #3
@@
 par(mar = c(0,0.3,0,0.1))
-plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,10), type="n",
+plot(0,0,xlim=c(0,my.xlim), ylim=c(-2,4), type="n",
      bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
@@
 
-legend(legend.x[2]-35,
+legend(legend.x[2]-45,
        legend.y[2]+2,c("State 0/1 events","State change point"),
@@
        lty = c(NA,NA), lwd=c(NA,4))
-points(8,legend.y[2] - 2, pch = 1, cex = 2, col = "blue")
-points(10,legend.y[2] - 2, pch = 16, cex = 2, col = "blue")
+points(110,legend.y[2] - 3, pch = 1, cex = 2, col = "blue")
+points(113,legend.y[2] - 3, pch = 16, cex = 2, col = "blue")
 
@@
 plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), 
-     ylim=c(-3,10), type="n",
+     ylim=c(-2,4), type="n",
      bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
@@
        col = model_colors[3],
-       y.intersp=0.88,x.intersp=0.1,bty = "n",
+       y.intersp=0.6,x.intersp=0.1,bty = "n",
        lty =1, lwd = 5,cex=legend.cex,seg.len=1)
@@
 
-legend(legend.x[3]-30,legend.y[3]+2, c("Overestimation","Underestimation"),
+legend(legend.x[3]-45,legend.y[3]+2, c("Overestimation","Underestimation"),
        col = c(positive.col,negative.col),
-       y.intersp=0.88,x.intersp=0.5,bty = "n",
+       y.intersp=0.6,x.intersp=0.5,bty = "n",
        lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)
@@
 par(mar = c(0,0.3,0,0.1))
-plot(0,0,xlim=c(0,my.xlim), ylim=c(-12,8), type="n",
+plot(0,0,xlim=c(0,my.xlim), ylim=c(-2,4), type="n",
      bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
@@
 mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.25)
+
 ```
@@
 
-```{r fig-7-prMatrix-Cohort5, fig.height=7}
-# current_cohort <- 5
+```{r fig-7-prMatrix-Cohort5, fig.width=7, fig.height=7}
+current_cohort <- 5
 
@@
                   )
-
-```
-
-```{r fig-matrix-structure-score}
+mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)
+
+```
+
+```{r fig-7b-matrix-structure-score, fig.width=7, fig.height=7}
 library(NMF)
@@
 
+box_cols <- col_df %>% 
+  filter(method %in% c("I-MMHP","C-HP","C-DCHP","C-MMHP")) %>%
+  pull(cols)
+
 struct_plot %>% 
-  ggplot(aes(Method,Score)) + geom_boxplot() +
-  facet_wrap(~Pos_Neg, scales = "free") + theme_minimal()
+  ggplot(aes(Method,Score, fill = Method)) + geom_boxplot() + 
+  scale_fill_manual(values = box_cols) +
+  ggtitle("(b)") +
+  facet_wrap(~Pos_Neg) + theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+              text = element_text(size = 20),
+              axis.text.y =element_text(size = 11),
+              axis.text.x = element_blank(),
+              axis.title.x=element_blank() )
 

### 2020-12-01 run_scripts/sim_fits.R

@@ -45,7 +45,7 @@ object_par <- list(sim_lambda_0 = 0.08,
                    sim_lambda_1 = 0.2,
                    sim_eta_1 = 2.5,
                    gamma_var = c(0.01, 0.02, 0.03, 0.06, 0.07),
-                   zeta_var = c(0.075, 0.06, 0.06, 0.03, 0.02),
+                   zeta_var = c(0.075, 0.06, 0.05, 0.03, 0.02),
                    sim_eta_2 = 0.6,
                    sim_eta_3 = 5,
                    sim_beta = 1.5,

### 2020-12-02 output_scripts/cmmhp_comparison/sim_comparison.Rmd
check the sparse models also

@@
 
-dc_sim_path <- here::here("output", "sims", "sims_m3_dc")
+dc_sim_path <- here::here("output", "sims_m3_sparse")
 comm_sim_path <- here::here("output", "common_rate", "sims_m3")
@@
                    gamma_var = c(0.01, 0.02, 0.03, 0.06, 0.07),
-                   zeta_var = c(0.075, 0.02, 0.03, 0.05, 0.08),
+                   zeta_var = c(0.075, 0.06, 0.05, 0.03, 0.02),
                    sim_eta_2 = 0.6,
@@
                                     length(object_par$f_vec_1)))
-
+current_sims <- 1:n_sim
+# 7,31,34,43,47,49
 ## Iteration on 50 simulations
-for(s in c(1:n_sim)){
+for(s in 44:n_sim){
   load(here(dc_sim_path,paste0("sim_model3_fit123_",s,".RData")))
@@
 complete_sims <- 1:n_sim
-complete_sims <- complete_sims[-29]
+#complete_sims <- complete_sims[-29]
 
@@
 ## Iteration on 50 simulations
-for(s in 30:n_sim){
+for(s in 1:n_sim){
   load(here(comm_sim_path, paste0("sim_model3_fit123_",s,".RData")))

### 2020-12-04 output_scripts/Paper_Plots.Rmd
update rank sim fits to include them in same simulation script.
also examining the structure score

@@
 
-```
-
-```{r load rankings,echo=FALSE,include=FALSE,results='hide',cache=TRUE}
-full_data <- readRDS("../data/mice.RData")
-# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
 cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
@@
 mice_number <- 12
+
+```
+
+```{r load rankings,echo=FALSE,include=FALSE,results='hide',cache=TRUE}
+full_data <- readRDS("../data/mice.RData")
+# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
 
@@
 ```{r fig-5b-spearman-sim, fig.height=7}
-sim_files <- list.files(here("output", "rank_sims",
+sim_files <- list.files(here("output", "sims_m3_update",
                              "sims_m3_dc_isi_sparse"))
@@
   }
-  if(current_cohort == 10) {
+  if(current_cohort %in% c(8,10)) {
     # one additional row
@@
   current_score$Cohort <- current_cohort
+  # current_score$resids <- list(m1 = m1_pr,
+  #                              m2 = m2_pr,
+  #                              m3 = m3_pr,
+  #                              ind = indep_pr)
   struct_scores <-struct_scores %>% bind_rows(current_score)
@@
   pivot_longer(cols = "C-HP":"I-MMHP",
-               names_to = "Method", values_to = "Score") %>%
-  filter(Score > 0) %>%
-  filter(!(Method == "I-MMHP" & Pos_Neg == "Positive"))
+               names_to = "Method", values_to = "Score") 
+  # filter(Score > 0) %>%
+  # filter(Score < 0.99) %>%
+  # filter(!(Method == "I-MMHP" & Pos_Neg == "Positive"))
   # mutate(Method = as.factor(Method, levels = c("I-MMHP","C-HP","C-DCHP",
@@
 
-box_cols <- col_df %>% 
-  filter(method %in% c("I-MMHP","C-HP","C-DCHP","C-MMHP")) %>%
-  pull(cols)
+# box_cols <- col_df %>% 
+#   filter(method %in% c("I-MMHP","C-HP","C-DCHP","C-MMHP")) %>%
+#   pull(cols)
 
@@
   ggplot(aes(Method,Score, fill = Method)) + geom_boxplot() + 
-  scale_fill_manual(values = box_cols) +
+  # scale_fill_manual(values = box_cols) +
   ggtitle("(b)") +
@@
 
-```{r fig-8a-frob-norm-cohort5, fig.width=8,fig.height=4}
+```{r fig-8a-frob-norm-cohort5, fig.width=8,fig.height=4,eval=FALSE}
 load("../output/plot_N_predict.RData")
@@
 
-```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4}
+```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4, eval=FALSE}
 load("../output/plot_N_predict.RData")
@@
 
-```{r fig-8b-frob-norm-boxplot, fig.width=8, fig.height=4}
+```{r fig-7-pred-all-cohorts-box, fig.width=8, fig.height=4}
 load("../output/plot_N_predict.RData")
@@
   scale_fill_manual(values = plot_cols_pred) +
-  ggtitle("(b)") +
+  ggtitle("(a)") +
   theme_bw() +
@@
 
-```{r fig-9a-spearman-rank-cohort1}
+```{r fig-9a-spearman-rank-cohort1, eval=FALSE}
 load(here("output","plot_rank_predict.RData"))
@@
 
-```{r fig-9b-spearman-rank-all-cohorts}
+```{r fig-7-pred-rank-spearman-all-cohorts}
 load("../output/plot_rank_predict.RData")

### 2020-12-04 output_scripts/cmmhp_comparison/sim_comparison.Rmd
update rank sim fits to include them in same simulation script.
also examining the structure score

--- 2020-12-01 output_scripts/cmmhp_comparison/sim_comparison.Rmd
@@
 
-dc_sim_path <- here::here("output", "sims", "sims_m3_dc")
+dc_sim_path <- here::here("output", "sims_m3_update")
 comm_sim_path <- here::here("output", "common_rate", "sims_m3")
@@
 ```{r ks-pr-computation-dc}
-object_par <- list(sim_lambda_0 = 0.08,
-                   sim_lambda_1 = 0.16,
+object_par <- list(sim_lambda_1 = 0.2,
                    sim_eta_1 = 2.5,
-                   gamma_var = c(0.01, 0.02, 0.03, 0.06, 0.07),
-                   zeta_var = c(0.075, 0.02, 0.03, 0.05, 0.08),
+                   gamma_var = c(0.05, 0.02, 0.03, 0.08, 0.01),
+                   zeta_var = c(0.075, 0.1, 0.05, 0.01, 0.02),
                    sim_eta_2 = 0.6,
@@
                                     length(object_par$f_vec_1)))
-
+current_sims <- 1:n_sim
+# 7,31,34,43,47,49
 ## Iteration on 50 simulations
-for(s in c(1:n_sim)){
+# 3,8,11,16,19,24,27,41,45,46,48
+for(s in 1:n_sim){
   load(here(dc_sim_path,paste0("sim_model3_fit123_",s,".RData")))

### 2020-12-04 run_scripts/sim_fits.R

@@ -8,6 +8,7 @@ data_path <- "output/sims_m3_update/"
 
 library(rstan)
 options(mc.cores = parallel::detectCores())
+rstan_options(auto_write = TRUE)
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
 sim_id <- jobid
@@ -136,11 +137,13 @@ print(paste(i,"model1"))
 ## Fit in model 1
 sim_model3_stan_fit1[[1]] <- sampling(model1, data=data_list, 
                                          iter=1000, chains=4)
+
 print("model2")
 ## Fit in model 2
 sim_model3_stan_fit2[[1]] <- sampling(model2,
                                          data=data_list,
                                          iter=1000, chains=4)
+
 print("model3")
 ## Fit in model 3
 sim_model3_stan_fit3[[1]] <- sampling(model3,
@@ -155,11 +158,14 @@ sim_model3_stan_fit3[[1]] <- sampling(model3,
 sim_model3_stan_sim1 <- list()
 sim_model3_stan_sim2 <- list()
 sim_model3_stan_sim3 <- list()
-# for(i in 1:n_sim){
-  sim_model3_stan_sim1 <- rstan::extract(sim_model3_stan_fit1[[1]])
-  sim_model3_stan_sim2 <- rstan::extract(sim_model3_stan_fit2[[1]])
-  sim_model3_stan_sim3 <- rstan::extract(sim_model3_stan_fit3[[1]])
-# }
+
+sim_model3_stan_sim1 <- rstan::extract(sim_model3_stan_fit1[[1]])
+sim_model3_stan_sim2 <- rstan::extract(sim_model3_stan_fit2[[1]])
+sim_model3_stan_sim3 <- rstan::extract(sim_model3_stan_fit3[[1]])
+
+m1_rank <- order(apply(sim_model3_stan_sim1$f, 2, mean))
+m2_rank <- order(apply(sim_model3_stan_sim2$f, 2, mean))
+m3_rank <- order(apply(sim_model3_stan_sim3$f, 2, mean))
 
 ## Save the output
 save(object_fn, object_par, object_matrix, sim_model3_data,
@@ -243,3 +249,55 @@ for(cur_i in c(1:length(object_par$f_vec_1))){
 
 save(event_state_est_lst, interpolate_state_est_lst,
[…]

### 2020-12-04 run_scripts/sim_fits.R
make shorter so less events

@@ -28,7 +28,7 @@ source('lib/drawIntensity.R')
 # Define global variable
 n_sim <- 50
 cut_off <- 3
-obs_time <- 200
+obs_time <- 100
 
 model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
 
@@ -45,7 +45,7 @@ object_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*
 
 object_par <- list(sim_lambda_1 = 0.2,
                    sim_eta_1 = 2.5,
-                   gamma_var = c(0.05, 0.02, 0.03, 0.08, 0.01),
+                   gamma_var = c(0.05, 0.02, 0.03, 0.08, 0.02),
                    zeta_var = c(0.075, 0.1, 0.05, 0.01, 0.02),
                    sim_eta_2 = 0.6,
                    sim_eta_3 = 5,

### 2020-12-04 output_scripts/Paper_Plots.Rmd
move numbers for 5b further away from axis

@@
 ```{r fig-4a, fig.height=6,fig.width=8}
-sim_data_path <- "../output/sims/sims_m3_dc/"
+sim_data_path <- "../output/sims_m3_update/"
 
@@
 ```{r prepare data for 4b,cache=TRUE}
-plot.s <- 1#7#9
+plot.s <- 6#7#9
 plot.i <- 4
@@
 
-load(paste0(sim_data_path, "sim_model3_",
+load(paste0(sim_data_path,"/" ,"sim_model3_",
                                plot.s,
@@
 ## then need to load in the state estimate here
-load(paste0(sim_data_path, "fit123_state_est_", plot.s, ".RData"))
+load(paste0(sim_data_path,"/", "fit123_state_est_", plot.s, ".RData"))
 
@@
       at=c(0:4)/5+0.1)
-mtext(text=c(5:1), side=1, line=1, outer=TRUE, cex=2,
+mtext(text=c(5:1), side=1, line=1.5, outer=TRUE, cex=2,
       at=c(0:4)/5+0.1)

### 2020-12-04 output_scripts/Paper_Plots.Rmd
tidy up and adjust plots as needed

@@
 knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
-                      dev = 'png', fig.height = 4.5, fig.width = 7,
+                      dev = 'pdf', fig.height = 4.5, fig.width = 7,
                       warning = FALSE)
@@
 
-```{r fig-3b-rank-comparison}
+```{r fig-3b-rank-comparison, include=FALSE,eval=FALSE}
 # current_cohort <- 5
@@
 
-<!-- # Redone Figure 3 -->
-
-<!-- As discussed, it would be interesting to redo figure 3b -->
-<!-- to show the lack of fit in model 2 for one specific pair. This can be somewhat -->
-<!-- extracted from the diagnostics file. -->
-
-<!-- We actually want the empirical CDF plot here. -->
-
-<!-- ```{r fig_3b_update, fig.height=7, include=FALSE, eval=FALSE} -->
-<!-- # 2 -> 11 might be good here -->
-<!-- # current_cohort <- 5 -->
-<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
-<!-- return_df <- cleanObservationPeriod(current_cohort, clean_data) -->
-<!-- unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% -->
-<!--   dplyr::summarize(count=n(), -->
-<!--             observe=list(observe.id), -->
-<!--             observe.length=list(observe.time), -->
-<!--             no.events=list(no.events))  -->
-<!-- top_pairs <- unique_pairs_df %>% arrange(desc(count)) -->
-
-<!-- best_i <- top_pairs$initiator[8] -->
-<!-- best_j <- top_pairs$recipient[8] -->
-
-<!-- current_i <- best_i #8 -->
-<!-- current_j <- best_j #2 -->
-
-<!-- ### then plots #### -->
-<!-- # par(mfrow = c(1, 2), oma = c(1, 1, 1, 1), -->
-<!-- #      mar = c(2, 3, 2, 1), mgp = c(0.8,0,0)) -->
-<!-- # layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3)) -->
-<!-- anno.cex <- 1.3 -->
-<!-- title.cex <- 2.2 -->
-<!-- title.line <- 0.5 -->
-<!-- y.upper <- 20 -->
-<!-- #### then the corresponding QQ plot #### -->
-<!-- load(paste(data_path,cohort_names[current_cohort], -->
-<!--              "/real_diag_four_models_",cohort_names[current_cohort], -->
-<!--              ".RData",sep='')) -->
-<!-- Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]] -->
-
-<!-- p <- ppoints(length(Lambda.dc_hawkes.test)) -->
-<!-- # 100 equally spaced points on (0,1), excluding endpoints -->
-<!-- q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) -->
-<!-- # percentiles of the sample distribution -->
-<!-- plot(qexp(p),q, -->
-<!--      xlab="",ylab="",xaxt="n",yaxt="n", -->
-<!--      pch=1, cex=1, col=viridis::viridis(1), ylim=c(0,1), xlim=c(0,4.5)) -->
-<!-- mtext(side = 1, text = "Theoretical", line=1.6, cex=anno.cex) -->
-<!-- mtext(side = 2, text = "Empirical", line = 1.2, cex = anno.cex) -->
-<!-- mtext(side = 3, text = "(b)", line = 0.8, cex = 1.6, font = 2) -->
-<!-- # Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1) -->
-<!-- # Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:1),cex.axis=1,lwd=0,lwd.ticks=1) -->
-<!-- qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5) -->
-
-<!-- ### Empirical CDF #### -->
-
-<!-- plot(ecdf(Lambda.dc_hawkes.test), do.points = FALSE, -->
-<!--      verticals = TRUE, col = viridis::viridis(1), lwd = 2,  -->
-<!--      xlab = "", ylab = "", xaxt = "n", yaxt = "n", -->
-<!--      main = "", col.01line = NULL) -->
-<!-- curve(pexp(x,1/mean(Lambda.dc_hawkes.test)), -->
-<!--       min(Lambda.dc_hawkes.test), max(Lambda.dc_hawkes.test), -->
-<!--       ylab = "", xlab = "", -->
-<!--       add = TRUE, lwd = 2) -->
-
-<!-- ``` -->
-
-<!-- ```{r repeat entire fig2b for model 2, include=extra_plots, eval=extra_plots} -->
-<!-- # current_cohort <- 5 -->
-
-<!-- load(paste(data_path,cohort_names[current_cohort], -->
-<!--              "/real_diag_four_models_",cohort_names[current_cohort], -->
-<!--              ".RData",sep='')) -->
-
-<!-- load(paste(data_path,cohort_names[current_cohort], -->
-<!--            "/cohort_dchp_stan_result_",cohort_names[current_cohort], -->
-<!--            ".RData",sep='')) -->
-<!-- eta1_mean <- mean(sim_cohort_dchp$eta_1) -->
-<!-- eta2_mean <- mean(sim_cohort_dchp$eta_2) -->
-<!-- eta3_mean <- mean(sim_cohort_dchp$eta_3) -->
-<!-- f_est <- apply(sim_cohort_dchp$f,2,mean) -->
-<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
-<!-- return_df <- cleanObservationPeriod(current_cohort, clean_data) -->
-<!-- unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% -->
-<!--   dplyr::summarize(count=n(), -->
-<!--                    observe=list(observe.id), -->
-<!--                    observe.length=list(observe.time), -->
-<!--                    no.events=list(no.events)) -->
-<!-- unique_observe_win <- unique(return_df[,c("observe.id","observe.time")]) -->
-
-<!-- ks.stat.matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
-<!-- n_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
-<!-- Lambda_matrix <- matrix(list(),nrow=mice_number,ncol=mice_number) -->
-<!-- for(k in 1:mice_number){ -->
-<!--   for(l in c(1:mice_number)[-k]){ -->
-<!--     i<-expert_rank_10[[current_cohort]][k] -->
-<!--     j<-expert_rank_10[[current_cohort]][l] -->
-<!--     pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
-<!--     if(length(pair)>0){ -->
-<!--       param_mean <- list(lambda0=mean(sim_cohort_dchp$lambda0[,pair]), -->
-<!--                          alpha=model1_fn$alpha.fun(f_est[i], -->
-<!--                                                    f_est[j], -->
-<!--                                                    eta1_mean, -->
-<!--                                                    eta2_mean, -->
-<!--                                                    eta3_mean), -->
-<!--                          beta=mean(sim_cohort_dchp$beta)) -->
-<!--       current_window_vec <- unique_pairs_df$observe[[pair]] -->
-<!--       all_Lambda <- numeric(0) -->
-<!--       for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
-<!--         cur_win <- current_window_vec[cur] -->
-<!--         current_event_time <- return_df[return_df$initiator==i& -->
-<!--                                           return_df$recipient == j & -->
-<!--                             return_df$observe.id==cur_win,"event.times"][[1]] -->
-<!--         current_obs_time <- return_df[return_df$initiator==i& -->
-<!--                                         return_df$recipient==j& -->
-<!--                             return_df$observe.id==cur_win,"observe.time"] -->
-<!--         Lambda_vec <- uniHawkesCompensator(object = param_mean, -->
-<!--                               events = c(current_event_time, -->
-<!--                                          current_obs_time)) -->
-<!--         all_Lambda <- c(all_Lambda,Lambda_vec) -->
-<!--         n_matrix[i,j] <- n_matrix[i,j] + length(current_event_time) -->
-<!--       } -->
-<!--       if(length(all_Lambda)>0){ -->
-<!--         ks.stat.matrix[i,j] <-  ks.test(all_Lambda,"pexp", -->
-<!--                                         rate = 1/mean(all_Lambda))$statistic -->
-<!--         Lambda_matrix[i,j][[1]] <- all_Lambda -->
-<!--       } -->
-<!--     } -->
-<!--   } -->
-<!-- } -->
-
-<!-- m2_ks <- ks.stat.matrix -->
-
-<!-- # -------------- KS plot (stat) -->
-<!-- col.vec <- cRamp(as.vector(ks.stat.matrix)) -->
-<!-- ## need to do some sort of transformation between these here -->
-<!-- vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix)))) -->
-<!-- #order(as.vector(ks.stat.matrix),method = "") -->
-
-<!-- values <- as.vector(ks.stat.matrix) -->
-<!-- sorted_vals <- sort(ks.stat.matrix) -->
-<!-- #match(values,sorted_vals) -->
-<!-- col.vec.vir <- vir_cols[match(values,sorted_vals)] -->
-
-<!-- #### -->
-<!-- par(oma = c(6,4,4,1), mar=rep(0,4), -->
-<!--     mgp = c(0, .2, 0)) -->
-<!-- layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12,  -->
-<!--                     byrow = TRUE),rep(12*12+1,12)),  -->
-<!--        widths=c(rep(1,12),2), heights=rep(1,12)) -->
-<!-- for(i in expert_rank_10[[current_cohort]]){ -->
-<!--   for(j in expert_rank_10[[current_cohort]]){ -->
-<!--     if(ks.stat.matrix[i,j]==0){ -->
-<!--       plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="",  -->
-<!--            axes = FALSE, frame=TRUE) -->
-<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], -->
-<!--            border = 0, col = 'white') -->
-<!--     }else{ -->
-<!--       Lambda.test <- Lambda_matrix[i,j][[1]] -->
-<!--       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test), -->
-<!--             ylab="",xlab="",axes = FALSE, frame=TRUE) -->
-<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],  -->
-<!--            border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)]) -->
-<!--       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test), -->
-<!--             ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2) -->
-<!--       plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE, -->
-<!--            verticals = TRUE, col = "red", lwd = 2) -->
-<!--     } -->
-<!--   } -->
-<!-- } -->
-<!-- par(mar = c(0,2,0,3),mgp=c(0,0.8,0)) -->
-
-<!-- col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)), -->
-<!--                             length.out = 100), -->
-<!--                 col.vec = viridis(100)) -->
-
-<!-- temp <- cLegend(as.vector(ks.stat.matrix)) -->
-
-<!-- image(1, col_obj$x.vec, -->
-<!--       matrix(data=col_obj$x.vec,  -->
-<!--              ncol=length(col_obj$x.vec),nrow=1), -->
-<!--       col=col_obj$col.vec, -->
-<!--       xlab="",ylab="",axes=FALSE) -->
-<!-- axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1, -->
-<!--      cex.axis=2.4) -->
-
-<!-- mtext(text=expert_rank_10[[current_cohort]], side=1, -->
-<!--       line=1.8, outer=TRUE, cex=1.8, -->
-<!--       at=1/14*c(1:12)-1/22) -->
-<!-- mtext(text = expert_rank_10[[current_cohort]], -->
-<!--       side = 2, line = 0.5, outer = TRUE, cex = 1.8, -->
-<!--       at =1/12*c(12:1)-1/20, las = 2) -->
-<!-- mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE, -->
-<!--       cex = 2.2, -->
-<!--       at=0.45, font=2) -->
-
-<!-- ``` -->
-
-<!-- ```{r construct ks_diff} -->
-<!-- ks_diff <-  (m2_ks - m1_ks)/m1_ks -->
-<!-- ks_diff[is.nan(ks_diff)] <- 0 -->
-<!-- # -------------- KS plot (stat) -->
-<!-- col.vec <- cRamp(as.vector(ks_diff)) -->
-<!-- ## need to do some sort of transformation between these here -->
-<!-- vir_cols <- viridis::viridis(length((as.vector(ks_diff)))) -->
-<!-- #order(as.vector(ks.stat.matrix),method = "") -->
-
-<!-- values <- as.vector(ks_diff) -->
-<!-- sorted_vals <- sort(ks_diff) -->
-<!-- #match(values,sorted_vals) -->
-<!-- col.vec.vir <- vir_cols[match(values,sorted_vals)] -->
-
-<!-- #### -->
-<!-- par(oma = c(6,4,4,1), mar=rep(0,4), -->
-<!--     mgp = c(0, .2, 0)) -->
-<!-- layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12,  -->
-<!--                     byrow = TRUE),rep(12*12+1,12)),  -->
-<!--        widths=c(rep(1,12),2), heights=rep(1,12)) -->
-<!-- for(i in expert_rank_10[[current_cohort]]){ -->
-<!--   for(j in expert_rank_10[[current_cohort]]){ -->
-<!--     if(ks_diff[i,j]==0){ -->
-<!--       plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="",  -->
-<!--            axes = FALSE, frame=TRUE) -->
-<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], -->
-<!--            border = 0, col = 'white') -->
-<!--     }else{ -->
-<!--       Lambda.test <- Lambda_matrix[i,j][[1]] -->
-<!--       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test), -->
-<!--             ylab="",xlab="",axes = FALSE, frame=TRUE) -->
-<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], -->
-<!--            border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)]) -->
-
-<!--     } -->
-<!--   } -->
-<!-- } -->
-<!-- par(mar = c(0,2,0,3),mgp=c(0,0.8,0)) -->
-
-<!-- col_obj <- list(x.vec = seq(min(as.vector(ks_diff)),max(as.vector(ks_diff)), -->
-<!--                             length.out = 100), -->
-<!--                 col.vec = viridis(100)) -->
-
-<!-- # temp <- cLegend(as.vector(ks_diff)) -->
-
-<!-- image(1, col_obj$x.vec, -->
-<!--       matrix(data=col_obj$x.vec,  -->
-<!--              ncol=length(col_obj$x.vec),nrow=1), -->
-<!--       col=col_obj$col.vec, -->
-<!--       xlab="",ylab="") -->
-<!-- # axis(4, at=c(-0.2,0,0.2), labels=c(-0.2,0,0.2), las= HORIZONTAL<-1, -->
-<!-- #      cex.axis=2.4) -->
-
-<!-- mtext(text=expert_rank_10[[current_cohort]], side=1, -->
-<!--       line=1.8, outer=TRUE, cex=1.8, -->
-<!--       at=1/14*c(1:12)-1/22) -->
-<!-- mtext(text = expert_rank_10[[current_cohort]], -->
-<!--       side = 2, line = 0.5, outer = TRUE, cex = 1.8, -->
-<!--       at =1/12*c(12:1)-1/20, las = 2) -->
-<!-- mtext(text = "(M2 - M1)/M1", side = 3, line = 1.4, outer = TRUE, -->
-<!--       cex = 2.2, -->
-<!--       at=0.45, font=2) -->
-
-<!-- ``` -->
-
-<!-- ```{r construct ks diff normalised by num events} -->
-<!-- norm_diff <- (m2_ks - m1_ks)#/m1_ks -->
-<!-- norm_diff[is.nan(norm_diff)] <- 0 -->
-<!-- count_mat <- matrix(0, nrow = mice_number, ncol = mice_number) -->
-
-<!-- for(i in expert_rank_10[[current_cohort]]) { -->
-<!--   for(j in expert_rank_10[[current_cohort]]) { -->
-<!--     if( norm_diff[i,j] != 0 ) { -->
-<!--       num_events <- unique_pairs_df %>%  -->
-<!--       filter(initiator == i & recipient == j) %>% -->
-<!--       pull(count) -->
-<!--       # diff[i,j] <- diff[i,j] / num_events -->
-<!--       count_mat[i,j] <- num_events -->
-<!--     } -->
-<!--   } -->
-<!-- } -->
-
-<!-- tibble(diff_norm = as.vector(norm_diff), -->
-<!--        events = as.vector(count_mat)) %>% -->
-<!--   filter(events > 0 ) %>% -->
-<!--   ggplot(aes(events,diff_norm)) + geom_point() + -->
-<!--   ylab("M2-M1") + -->
-<!--   theme_minimal() -->
-
-<!-- tibble(diff_norm = as.vector(norm_diff), -->
-<!--        events = as.vector(count_mat)) %>% -->
-<!--   filter(events > 0) %>% -->
-<!--   ggplot(aes(diff_norm)) +  -->
-<!--   geom_histogram() + -->
-<!--   theme_minimal() -->
-
-<!-- ``` -->
-<!-- ```{r repeat for residuals} -->
-<!-- m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort], -->
-<!--                    "/chp_pr_matrix_",cohort_names[current_cohort], -->
-<!--                    ".RDS",sep='')) -->
-
-<!-- m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort], -->
-<!--                      "/dchp_pr_matrix_",cohort_names[current_cohort], -->
-<!--                      ".RDS",sep='')) -->
-
-<!-- tibble(m1pr = as.vector(m1_pr), -->
-<!--        m2pr = as.vector(m2_pr)) %>% -->
-<!--   mutate(diff = m2pr - m1pr) %>% -->
-<!--   ggplot(aes(diff)) +  -->
-<!--   geom_histogram() + -->
-<!--   labs(x = "M2 PR - M1 PR") + -->
-<!--   theme_minimal() -->
-
-<!-- ``` -->
-
-<!-- ```{r compute mean decrease in ks-score} -->
-<!-- summary(as.vector(m2_ks[m2_ks != 0])) -->
-<!-- summary(as.vector(m1_ks[m1_ks != 0])) -->
-
-<!-- t.test(as.vector(m2_ks[m2_ks != 0]), as.vector(m1_ks[m1_ks != 0])) -->
-
-<!-- diff <- as.vector(m2_ks[m2_ks != 0]) - as.vector(m1_ks[m1_ks != 0]) -->
-
-<!-- length(which(diff < 0))/length(diff) -->
-<!-- summary(diff) -->
-<!-- ``` -->
-
-<!-- This is good because it shows the most active animal, shows that individual -->
-<!-- out rate too large for this interaction. Just need to make this more -->
-<!-- like the plots in 2b. -->
-
 # Figure 4:
@@
 ## Figure 4a Recover Latent Ranks
-```{r fig-4a, fig.height=6,fig.width=8}
+```{r fig-4a, fig.height=3.5,fig.width=8}
 sim_data_path <- "../output/sims_m3_update/"
@@
 ```{r prepare data for 4b,cache=TRUE}
-plot.s <- 6#7#9
+plot.s <- 7#7 is pretty good
 plot.i <- 4
@@
 
-```{r fig4b-recover-latent-states,fig.width=8,fig.height=5}
-y.ub <- c(15,15,15)#c(130,72,31)
+```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4}
+y.ub <- c(35,35,35)#c(130,72,31)
 x_events <- 190#135#150
@@
 my.long.x <- 205#205#134.5
-legend.x <- c(150,150,150)#c(135,135,135)
+legend.x <- c(60,60,60)#c(135,135,135)
 legend.y <- #c(34,32,32)
-legend.y <- c(12,12,12)#c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.y <- c(23,23,23)#c(15,12,15)#c(62,37,18)#c(22,22,22)
 legend.cex <- 1.5 #3
@@
 line.wdth <- c(2,2.5)
-negative.col <- add.alpha('lightskyblue',0.6)
-positive.col <- add.alpha('tomato',0.6)
+negative.col <- add.alpha('lightskyblue')
+positive.col <- add.alpha('tomato')
 #negative.col <- viridis::viridis(5,alpha = 0.6)[1]
@@
        lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
-legend(legend.x[1]+18,legend.y[1],c("C-HP"),
+legend(legend.x[1]+22,legend.y[1],c("C-HP"),
        col = c(model_colors[1]),
@@
 par(mar = c(0,0.3,0,0.1))
-plot(0,0,xlim=c(0,my.xlim), ylim=c(-2,4), type="n",
+plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,4), type="n",
      bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
@@
 
-legend(legend.x[2]-45,
+legend(legend.x[2]-50,
        legend.y[2]+2,c("State 0/1 events","State change point"),
        col = c(NA,"red"),
-       y.intersp=0.85,x.intersp=-0.1, bty = "n",
+       y.intersp=0.85,x.intersp=-0.5, bty = "n",
        pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
-       lty = c(NA,NA), lwd=c(NA,4))
-points(110,legend.y[2] - 3, pch = 1, cex = 2, col = "blue")
-points(113,legend.y[2] - 3, pch = 16, cex = 2, col = "blue")
+       lty = c(NA,NA), lwd=c(NA,2))
+points(legend.x[2]-46,legend.y[2] - 4.5, pch = 1, cex = 2, col = "blue")
+points(legend.x[2]-44,legend.y[2] - 4.5, pch = 16, cex = 2, col = "blue")
 
@@
 plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), 
-     ylim=c(-2,4), type="n",
+     ylim=c(-4,4), type="n",
      bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
@@
 
-legend(legend.x[3]-45,legend.y[3]+2, c("Overestimation","Underestimation"),
+legend(legend.x[3]-50,legend.y[3]+2, c("Overestimation","Underestimation"),
        col = c(positive.col,negative.col),
-       y.intersp=0.6,x.intersp=0.5,bty = "n",
+       y.intersp=0.75,x.intersp=0.5,bty = "n",
        lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)
@@
 
-```{r fig5-residual-ks, fig.height=7}
+```{r fig5a-residual-ks, fig.height=7}
 # cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
@@
 ```{r fig-5b-spearman-sim, fig.height=7}
-sim_files <- list.files(here("output", "sims_m3_update",
-                             "sims_m3_dc_isi_sparse"))
+sim_files <- list.files(here("output", "sims_m3_update"), 
+                        pattern = "rank_sim")
 
@@
 for(i in seq_along(sim_files)) {
- single_fit <- readRDS(here("output", "rank_sims", 
-                            "sims_m3_dc_isi_sparse",
+ single_fit <- readRDS(here("output", "sims_m3_update",
                             sim_files[i]))
@@
 
-```{r fig-rank-slides, fig.height=3,include=slides_plots,eval=slides_plots}
-
-p2_slides <- plot_cor_df %>%
-  filter(Method != "Agg-rank") %>%      
-  ggplot(aes(x="", y = cor, fill = Method)) +
-        geom_boxplot(alpha=0.7, width=0.5) +
-        scale_fill_manual(values = viridis::viridis(3)) + 
-        #ggtitle("(b)") +
-        ylim(0,1) +
-        theme_bw() +
-        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
-              text = element_text(size = 20),
-              axis.text.y =element_text(size = 11),
-              legend.position="none",
-              axis.title.x=element_blank()) +
-        facet_grid(cols=vars(Method)) +
-        ylab("Rank correlation")
-p2_slides
-
-```
-
 # Figure 7: Pearson residual matrices
 
-```{r fig-7-prMatrix-Cohort5, fig.width=7, fig.height=7}
-current_cohort <- 5
+```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=7}
+current_cohort <- 3
+## 2 and 8 maybe look better
+## 3 probably looks the best
 
@@
                   )
-mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)
+# mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)
 
@@
               axis.title.x=element_blank() )
-
-```
-
-```{r fig_pr_slides, fig.height=3, fig.width=7, include=slides_plots,eval=slides_plots}
-# current_cohort <- 5
-
-m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                   "/chp_pr_matrix_",cohort_names[current_cohort],
-                   ".RDS",sep=''))
-
-m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                     "/dchp_pr_matrix_",cohort_names[current_cohort],
-                     ".RDS",sep=''))
-
-m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                     "/cmmhp_pr_matrix_",cohort_names[current_cohort],
-                     ".RDS",sep=''))
-
-indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                     "/immhp_pr_matrix_",cohort_names[current_cohort],
-                     ".RDS",sep=''))
-
-matrix_lst_plot <- list(
-                        #indep_pr[rev(expert_rank_10[[current_cohort]]),
-#                                                                   #expert_rank_10[[current_cohort]]],
-                        m1_pr[rev(expert_rank_10[[current_cohort]]),
-                                                                  expert_rank_10[[current_cohort]]],
-                        m2_pr[rev(expert_rank_10[[current_cohort]]),
-                                                                 expert_rank_10[[current_cohort]]],
-                        m3_pr[rev(expert_rank_10[[current_cohort]]),
-                                                                 expert_rank_10[[current_cohort]]]) 
-#cat("Cohort ",current_cohort,"\n",sep="")
-myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=3,n_row=1,
-                  xLabels=expert_rank_10[[current_cohort]],
-                  yLabels=rev(expert_rank_10[[current_cohort]]),
-                  min=-80,max=80,axis_cex=1,title_cex = 1.8,
-                  colorPalette="RdBu",if.emp=FALSE,
-                  #legend.mar=c(0.5,.5,0.5,0.5),
-                  title_lst=list("C-HP","C-DCHP","C-MMHP"), 
-                  #title_lst = list("I-MMHP"),
-                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
-                  matrix.mar=c(2.5,2.5,2.5,0.5)
-                  )
 
@@
 
-```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4, eval=FALSE}
+```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4.5, eval=FALSE}
 load("../output/plot_N_predict.RData")
@@
 
-```{r fig-7-pred-all-cohorts-box, fig.width=8, fig.height=4}
+```{r fig-7a-pred-all-cohorts-box}
 load("../output/plot_N_predict.RData")
@@
 all_cohort_box$day <- factor(all_cohort_box$day)
+
+plot_cols_pred <- col_df %>% 
+  filter(method %in% levels(all_cohort_box$method)) %>%
+   arrange(factor(method, levels = c("I-MMHP","DSNL",
+                                     "C-HP", "C-DCHP", "C-MMHP"))) %>%
+                    pull(cols)
 
@@
   theme_bw() +
-  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+  theme(plot.title = element_text(size = 22,
+                                  hjust = 0.5, face="bold"),
         text = element_text(size = 20),
@@
   NULL
-
-```
-
-```{r fig-slides-predict,include=slides_plots,eval=slides_plots,fig.height=3}
-load("../output/plot_N_predict.RData")
-temp_plot_df <- all_cohort_norm_df %>% 
-  group_by(day, method) %>% 
-  summarise(avg=mean(norm), n= n(), sd=sd(norm),
-            se = sd/sqrt(n))
-
-temp_plot_df$method <- factor(temp_plot_df$method,
-                              levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL","C-HP",
-                                         "C-DCHP","C-MMHP"))
-temp_plot_df$day <- factor(temp_plot_df$day)
-
-p4_slides <- ggplot(temp_plot_df, 
-                    aes(x=day, y=avg, group=method, color=method)) + 
-  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
-  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
-                 position=position_dodge(0.2)) +
-  scale_color_manual(values = viridis::viridis(5)) + 
-  #ggtitle("(b)") +
-  theme_bw() +
-  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
-        text = element_text(size = 20),
-        axis.text.x=element_text(size = 18)) +
-  xlab("Prediction horizon (day)") + 
-  ylab("Frobenius norm of error") + 
-  coord_cartesian(ylim=c(2.5,57.5)) + 
-  guides(color=guide_legend(title="Model")) 
-p4_slides
-
-```
-
-```{r, include=FALSE,eval=FALSE}
-
-all_sims <- do.call(rbind,predict_day_norm_df_lst)
-
-temp_plot_df <- all_sims %>% 
-  group_by(day, method) %>% 
-  summarise(avg=mean(norm), n= n(), sd=sd(norm),
-            se = sd/n)
-
-temp_plot_df$method <- factor(temp_plot_df$method,
-                              levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
-temp_plot_df$day <- factor(temp_plot_df$day)
-p4_slides <- temp_plot_df %>% #filter(method != "C-HP") %>% 
-  filter(method != "I-MMHP") %>%
-  ggplot(aes(x=day, y=avg, group=method, color=method)) + 
-  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
-  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
-                 position=position_dodge(0.2)) +
-  scale_color_manual(values = viridis::viridis(5)) + 
-  #ggtitle("(b)") +
-  theme_bw() +
-  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
-        text = element_text(size = 20),
-        axis.text.x=element_text(size = 18)) +
-  xlab("Prediction horizon (day)") + 
-  ylab("Frobenius norm of error") + 
-  coord_cartesian(ylim=c(2.5,57.5)) + 
-  guides(color=guide_legend(title="Model")) #+ ylim(c(0,1000))
-p4_slides
 
@@
 
-```{r fig-pred-cor, eval=slides_plots,include=slides_plots,fig.height=3}
+## Figure 9b: Predicted Spearman rank for all cohorts
+
+```{r fig-7b-pred-rank-spearman-all-cohorts}
 load("../output/plot_rank_predict.RData")
-current_cohort <- 5
-temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
-temp_plot_df$method <- factor(temp_plot_df$method,
-                              levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
-temp_plot_df$day <- factor(temp_plot_df$day)
-# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),width=600,height=300)
-temp_plot_df <- temp_plot_df %>%
-  filter(method != "I-MMHP") 
-p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
-  geom_boxplot(alpha=0.7) +
-  scale_fill_manual(values = viridis::viridis(5)) +
-  #scale_fill_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
-  #ggtitle("(a)") +
-  theme_bw() +
-  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
-        text = element_text(size = 20),
-        axis.text.x=element_blank(),
-        axis.ticks.x = element_blank(), 
-        legend.position="right") +
-  facet_grid(cols=vars(day)) +
-  xlab("Prediction horizon (day)") + 
-  ylab("Rank correlation") +
-  # ylim(0, 1) +
-  NULL
-p5
-```
-
-## Figure 9b: Predicted Spearman rank for all cohorts
-
-```{r fig-7-pred-rank-spearman-all-cohorts}
-load("../output/plot_rank_predict.RData")
-temp_plot_df <- all_cohort_rank_df %>% 
-  group_by(day, method) %>% 
-  summarize(avg=mean(spearman), n= n(), sd=sd(spearman))
-
-temp_plot_df$method <- factor(temp_plot_df$method,
-                              levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL","C-HP",
-                                         "C-DCHP","C-MMHP"))
-temp_plot_df$day <- factor(temp_plot_df$day)
-
-# png(paste(plot_path,"real_predict_rank_all_cohort.png",sep=""),width=600,height=300)
-p6 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
-  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
-  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
-                position=position_dodge(0.2)) +
-  scale_color_manual(values = plot_cols_pred) +
-  #scale_color_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
-  ggtitle("(b)") +
-  theme_bw() +
-  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
-        text = element_text(size = 20),
-        axis.text.x=element_text(size = 18)) +
-  xlab("Prediction horizon (day)") + 
-  ylab("Spearman rank correlation") + 
-  # coord_cartesian(ylim=c(0,1)) + 
-  guides(color=guide_legend(title="Method")) 
-p6
 
@@
   scale_fill_manual(values = plot_cols_pred) +
-  #scale_color_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
   ggtitle("(b)") +
@@
 
-```{r construct data for plot, results='hide',message=FALSE}
+```{r construct data for plot, results='hide',message=FALSE,cache=TRUE}
 library(PlayerRatings)
@@
 
-```{r process for state separation cohort5,eval=FALSE}
+```{r process for state separation cohort1,eval=FALSE}
 # only run this once and save the results
 # this doesn't need to be rerun ever, even if the stan fits change
-# current_cohort <- 5
+# current_cohort <- 1
 
@@
 
-```{r process data for plot 10b}
+```{r process data for plot 10b, cache=TRUE}
 library(PlayerRatings)
 # current_cohort <- 5
+current_cohort <- 1
 load(paste(data_path,cohort_names[current_cohort],

### 2020-12-04 output_scripts/fib4b_plot.R

@@ -1,11 +1,11 @@
-y.ub <- c(15,15,15)#c(130,72,31)
+y.ub <- c(35,35,35)#c(130,72,31)
 x_events <- 190#135#150
 layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
 my.xlim <- 200#160#200#130
 my.long.x <- 205#205#134.5
-legend.x <- c(150,150,150)#c(135,135,135)
+legend.x <- c(50,50,50)#c(135,135,135)
 legend.y <- #c(34,32,32)
-legend.y <- c(12,12,12)#c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.y <- c(20,20,20)#c(15,12,15)#c(62,37,18)#c(22,22,22)
 legend.cex <- 1.5 #3
 line.alpha <- c(0.9,0.6)
 line.wdth <- c(2,2.5)
@@ -65,7 +65,7 @@ legend(legend.x[1]+22,legend.y[1],c("C-HP"),
 
 ## delta lambda
 par(mar = c(0,0.3,0,0.1))
-plot(0,0,xlim=c(0,my.xlim), ylim=c(-2,4), type="n",
+plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,4), type="n",
      bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
 delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
 delta.positive <- delta.lambda
@@ -110,21 +110,21 @@ legend(legend.x[2],legend.y[2],"C-DCHP",
 axis(1,at=c(-2,my.long.x),col="gray35",
      line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
 
-legend(legend.x[2]-65,
+legend(legend.x[2]-50,
        legend.y[2]+2,c("State 0/1 events","State change point"),
        col = c(NA,"red"),
-       y.intersp=0.85,x.intersp=-0.1, bty = "n",
+       y.intersp=0.85,x.intersp=-0.5, bty = "n",
        pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
-       lty = c(NA,NA), lwd=c(NA,4))
-points(90,legend.y[2] - 1.5, pch = 1, cex = 2, col = "blue")
-points(93,legend.y[2] - 1.5, pch = 16, cex = 2, col = "blue")
[…]

### 2020-12-04 run_scripts/sim_fits.R

@@ -255,50 +255,50 @@ save(event_state_est_lst, interpolate_state_est_lst,
 
 #### Get Other Rankings
 
-count_data_dc <- get_wl_matrix(df = cbind(clean_sim_data$start, 
-                                          clean_sim_data$end))
-isi_dc.out <- compete::isi98(m = count_data_dc, random = TRUE)
-isi_rank_dc <- as.numeric(rev(isi_dc.out$best_order))
-
-
-agg_rank_data <- clean_sim_data_dc$N_count
-agg_rank_model <- stan_model(here("lib","latent_rank_agg_sim.stan"))
-
-agg_rank_fit <- rstan::sampling(agg_rank_model,
-                                data = list(n = 5,
-                                            n_matrix = agg_rank_data),
-                                iter = 1000,
-                                chains = 4)
-agg_sims <- rstan::extract(agg_rank_fit)
-
-agg_rank <- order(apply(agg_sims$x, 2, mean))
-
-
-
-### glicko ranking also ####
-glicko_data <- tibble(start = clean_sim_data$start,
-                      end = clean_sim_data$end)
-
-glicko_data <- glicko_data %>%
-  mutate(id = row_number(), score = 1) %>%
-  select(id, start, end, score)
-
-gl_train <- my_glicko(glicko_data, history=TRUE, cval=2)
-
-gl_train
-
-gl_ranks <- order(gl_train$ratings$Rating)
-
-## then save these
-
-output_rank <- tibble(truth = 1:5, 
-                      m1 = m1_rank,
-                      m2 = m2_rank,
-                      m3_dc = m3_dc_rank,
-                      isi = isi_rank_dc,
-                      agg = agg_rank,
-                      glicko = gl_ranks,
-                      sim = rep(sim_id,5))
-
-saveRDS(output_rank, 
-        file = paste(data_path,"rank_sim",sim_id,".RDS",sep=''))
+# count_data_dc <- get_wl_matrix(df = cbind(clean_sim_data$start, 
+#                                           clean_sim_data$end))
+# isi_dc.out <- compete::isi98(m = count_data_dc, random = TRUE)
+# isi_rank_dc <- as.numeric(rev(isi_dc.out$best_order))
+# 
+# 
+# agg_rank_data <- clean_sim_data_dc$N_count
+# agg_rank_model <- stan_model(here("lib","latent_rank_agg_sim.stan"))
+# 
+# agg_rank_fit <- rstan::sampling(agg_rank_model,
[…]

### 2020-12-10 output_scripts/Paper_Plots.Rmd
some final updates for plots

@@
 knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
-                      dev = 'pdf', fig.height = 4.5, fig.width = 7,
+                      dev = 'png', fig.height = 4.5, fig.width = 7,
                       warning = FALSE)
@@
 
-current_cohort <- 5
+current_cohort <- 7
+# 4 best so far, or 7
 
@@
 df1$event <- 1:nrow(df1)
-glick.df <- df1[, c("event","Actor","Recipient","score"), with = FALSE] #need event, actor, recipient, score
+glick.df <- df1[, c("event","Actor","Recipient","score"), with = FALSE]
+#need event, actor, recipient, score
 gl <- my_glicko(glick.df, history=TRUE, cval=2)
@@
   }else{
-    # this line makes no sense, and should likely never happen
     # try(
@@
 par(mar=c(3,5,3,1))
+testing_end <- testing_end - 1
 plot(1, type="n", xlab="", ylab="Glicko ranking", xlim=c(0,dim(gl$history)[2]),
@@
                               cut_off = 1)
-day_end_idx <- unlist(lapply(c(1:21),function(x) max(which(clean_data_all$day==x))))
+day_end_idx <- unlist(lapply(c(1:21),function(x) 
+  max(which(clean_data_all$day==x))))
 

### 2020-12-14 output_scripts/Slide_Plots.Rmd
add Rmd for slide plots

--- 2020-12-10 output_scripts/Paper_Plots.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
+knitr::opts_chunk$set(echo = TRUE, fig.path = "slide_figure/",
                       dev = 'png', fig.height = 4.5, fig.width = 7,
-                      warning = FALSE)
+                      warning = FALSE, eval = FALSE, include = FALSE)
 
@@
 
-```{r load rankings,echo=FALSE,include=FALSE,results='hide',cache=TRUE}
+```{r load rankings,echo=FALSE,eval=TRUE,results='hide',cache=TRUE}
 full_data <- readRDS("../data/mice.RData")
@@
 
-```{r define_functions}
+```{r define_functions,eval=TRUE}
 model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1 +
@@
 
-```{r creat colour df}
+```{r creat colour df,eval=TRUE}
 col_df <- tibble(method = c("I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
@@
 # Figure 5b: Simulation Spearman Rank
-```{r fig-5b-spearman-sim, fig.height=7}
+```{r fig-5b-spearman-sim, fig.height=3, fig.width=6, include=TRUE,eval=TRUE}
 sim_files <- list.files(here("output", "sims_m3_update"), 
@@
         axis.ticks.x = element_blank(),
-        legend.position="right") + ggtitle("(b)")
+        legend.position="right") #+ ggtitle("(b)")
 ```
@@
 
-```{r fig-6a-rank-vs-isi}
+```{r fig-6a-rank-vs-isi, include=TRUE, eval=TRUE}
 ### Rank Comparison for Single Cohort ####
@@
   geom_boxplot(alpha=0.7) +
-  scale_fill_manual(values = plot_cols)+
-  #scale_fill_manual(values = c("gray", "steelblue", "goldenrod2" , "firebrick2")) +
-  ggtitle("(a)") +
+  scale_fill_manual(values = plot_cols) +
+  # ggtitle("(a)") +
   theme_bw() +
@@
 
-```{r fig-6b-overall-rank-correlation}
+```{r fig-6b-overall-rank-correlation, include=TRUE, eval=TRUE}
 load("../output/weighted_rank_data.RData")
@@
         scale_fill_manual(values = plot_cols) + 
-        ggtitle("(b)") +
+        # ggtitle("(b)") +
         ylim(0,1) +
@@
 
-```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=7}
+```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=3, eval=TRUE, include=TRUE}
 current_cohort <- 3
@@
 matrix_lst_plot <- list(
-                        indep_pr[rev(expert_rank_10[[current_cohort]]),
-                                                                   expert_rank_10[[current_cohort]]],
+                        # indep_pr[rev(expert_rank_10[[current_cohort]]),
+                        #                                            expert_rank_10[[current_cohort]]],
                         m1_pr[rev(expert_rank_10[[current_cohort]]),
@@
 #cat("Cohort ",current_cohort,"\n",sep="")
-myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
-                  xLabels=expert_rank_10[[current_cohort]],
-                  yLabels=rev(expert_rank_10[[current_cohort]]),
-                  min=-80,max=80,axis_cex=2,title_cex = 1.8,
-                  colorPalette="RdBu",if.emp=FALSE,
+myMultiMatrixPlot(X=matrix_lst_plot,no_matrix = 3,n_row = 1,
+                  xLabels = expert_rank_10[[current_cohort]],
+                  yLabels = rev(expert_rank_10[[current_cohort]]),
+                  min = -80,max = 80,axis_cex = 2,
+                  title_cex = 1.8,
+                  colorPalette = "RdBu",if.emp = FALSE,
                   #legend.mar=c(0.5,.5,0.5,0.5),
-                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
+                  title_lst = list("C-HP","C-DCHP","C-MMHP"), 
                   #title_lst = list("I-MMHP"),
-                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
-                  matrix.mar=c(2.5,2.5,2.5,1)
+                  col_axis = c(-80,-40,0,40,80), fake_matrix=FALSE,
+                  matrix.mar = c(2.5,2.5,2.5,1)
                   )
@@
   scale_fill_manual(values = plot_cols_pred) +
-  ggtitle("(a)") +
+  # ggtitle("(a)") +
   theme_bw() +
@@
 
-```{r fig-7a-pred-all-cohorts-box}
+```{r fig-7a-pred-all-cohorts-box, include=TRUE, eval=TRUE, fig.width=7,fig.height=3}
 load("../output/plot_N_predict.RData")
@@
   xlab("Prediction horizon (day)") + 
-  ylab("Frobenius norm of error") +
+  ylab("Frob. norm of error") +
   labs(fill = "Method") +
@@
 
-```{r fig-7b-pred-rank-spearman-all-cohorts}
+```{r fig-7b-pred-rank-spearman-all-cohorts, include=TRUE, eval=TRUE, fig.width=7,fig.height=3}
 load("../output/plot_rank_predict.RData")
@@
   scale_fill_manual(values = plot_cols_pred) +
-  ggtitle("(b)") +
+  # ggtitle("(b)") +
   theme_bw() +
@@
 
-```{r construct data for plot, results='hide',message=FALSE,cache=TRUE}
+```{r construct data for plot, results='hide',message=FALSE,cache=TRUE,eval=TRUE}
 library(PlayerRatings)
@@
 
-```{r fig-10a-glicko-rating}
+```{r fig-10a-glicko-rating,include=TRUE,eval=TRUE}
 par(mar=c(3,5,3,1))
@@
 }
-mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
+# mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
 ```

### 2020-12-16 output_scripts/Paper_Plots.Rmd
add new fig4a and compete gist so all code in repo

@@
 ```
+```{r fig4a-new-hist, fig.height=3.5,fig.width=8}
+model_colors <- col_df %>% filter(method %in% c("C-HP",
+                                                "C-DCHP",
+                                                "C-MMHP"))
+
+model_colors <- model_colors %>% pull(cols)
+
+m1 <- sim_model3_stan_sim1_total %>%
+  map( ~apply(.x$f, 2, mean)  ) %>%
+  enframe() %>%
+  unnest(cols = value) %>%
+  mutate(node_id = rep(c("f1","f2","f3","f4","f5"), 50),
+         method = "C-HP")
+
+m2 <- sim_model3_stan_sim2_total %>%
+  map( ~apply(.x$f, 2, mean)  ) %>%
+  enframe() %>%
+  unnest(cols = value) %>%
+  mutate(node_id = rep(c("f1","f2","f3","f4","f5"), 50),
+         method = "C-DCHP")
+
+m3 <- sim_model3_stan_sim3_total %>%
+  map( ~apply(.x$f, 2, mean)  ) %>%
+  enframe() %>%
+  unnest(cols = value) %>%
+  mutate(node_id = rep(c("f1","f2","f3","f4","f5"), 50),
+         method = "C-MMHP")
+
+rank_means <- bind_rows(m1,m2,m3)
+
+# rank_means
+
+true_values <- tibble(
+  id = c("f1", "f2","f3","f4","f5"),
+  values = c(0.1,0.2,0.4,0.7,0.9),
+  val_names = c("   0.1","0.2","0.4","0.7","0.9")
+)
+
+rank_means %>% 
+  left_join(true_values, by = c("node_id" = "id")) %>%
+  ggplot(aes(value, fill = method)) + 
+  geom_histogram() + 
+  geom_vline(aes(xintercept = values), alpha = 0.6,
+             linetype = "dashed") +
+  ### add text here
+  geom_text(aes(values, 18, label = val_names),
+            size = 3, hjust = 1) +
+  scale_fill_manual(values = model_colors) +
+  facet_grid(cols = vars(node_id), rows = vars(method)) + 
+  theme_bw() + theme(
+    plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+    text = element_text(size = 12),
+    axis.text.x=element_blank(),
+    axis.ticks.x = element_blank(),
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank(),
+    legend.position = "none",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank()
+  ) +
+  labs(x = "", y = "")
+
+```
 
@@
 
-drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
+drawUniMMHPIntensityPaper(true.object,
+                          simulation = fixStateTransition(test.mmhp),
                           yupper=y.ub[1], 
@@
                           line.width=line.wdth[1],
-                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
+                          y.ratio=-0.05, min.y=-2,
+                          min.x=0, max.x=my.xlim,
                           title_name=paste(plot.i,"->",plot.j),

### 2020-12-16 lib/compete_gist.R

@@ -1,0 +1,234 @@
+### copy of https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R
+
+
+expandrows <- function(df){
+  
+  library(splitstackshape)  
+  library(data.table)  
+  
+  
+  temp <- cSplit(cSplit(cbind(id = 1:nrow(df), df),
+                        "Actor", ",", "long"), 
+                 "Recipient", ",", "long")
+  
+  
+  ## Convert "Actor" and "Recipient" to numeric
+  SD <- c("Actor", "Recipient")
+  temp[, (SD) := lapply(.SD, as.numeric), .SDcols = SD]
+  
+  
+  ## Sort Actors and Recipients, and check for duplicates and any points where Actors equal Recipients  
+  temp[, toDrop := duplicated(
+    paste(pmin(Actor, Recipient), pmax(Actor, Recipient))) |
+      Actor == Recipient, by = id]
+  
+  ## Create your "score" column
+  temp[, score := ifelse(any(toDrop), 0.5, 1), by = id]
+  
+  ## Subset and drop the irrelevant columns
+  out <- temp[!temp[, toDrop, with = TRUE]][, toDrop := NULL]
+  out$id<-NULL
+  return(out)
+}
+
+
+contests <- function(df,a,b){
+  df[(df$Actor==a & df$Recipient==b)|(df$Actor==b & df$Recipient==a),]
+}
+
+
+
+
+
+### Making Matrix Plots
+
+# takes wl matrix and order of id's and creates ggplot matrix.
+
+
+matrixplot <- function(m, mylevs=NULL, lowcolor="white",highcolor="red1"){
+  
+  library(ggplot2)
+  
+  #make the df we will use for plotting
+  m.dat <- reshape2::melt(m)
+  m.dat <- data.frame(m.dat)
+  m.dat <- m.dat[complete.cases(m.dat),] #removing NAs
+  
+  if(is.null(mylevs)) { mylevs = rownames(m)}
+  
+  #reorder the levels of the y-axis so plots properly
+  m.dat$Recipient <- factor(m.dat$Recipient, levels=mylevs)
+  m.dat$Actor <- factor(m.dat$Actor, levels = rev(mylevs))
+  m.dat[m.dat == 0] <- NA
+  
+  
+  #plot
[…]

### 2021-04-20 output_scripts/Slide_Plots.Rmd

@@
 
-plot_cols <- col_df %>% filter(method %in% levels(sim_data$name)) %>%
+plot_cols <- col_df %>%
+  filter(method %in% levels(sim_data$name)) %>%
   pull(cols)
 
+plot_cols_slide <- col_df %>%
+  filter(method %in% levels(sim_data$name)) %>%
+  filter(method != "AggRank") %>%
+  pull(cols)
+
 sim_data %>%
+  filter(name != "AggRank") %>%
   rename(Method = name, corr = value) %>%
@@
   geom_boxplot(aes(fill = Method), alpha = 0.7) +
-  scale_fill_manual(values = plot_cols) +
+  scale_fill_manual(values = plot_cols_slide) +
   labs(y = "Rank Correlation") + theme_bw() +
@@
 
-load(paste(data_path,cohort_names[current_cohort],
-           "/agg_rank_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
+# load(paste(data_path,cohort_names[current_cohort],
+#            "/agg_rank_stan_result_",cohort_names[current_cohort],
+#            ".RData",sep=''))
 load(paste(data_path,cohort_names[current_cohort],
@@
 
-no_method <- 4
-plot_latent_df <- data.frame(Methods=rep(1:no_method,each=1000*mice_number),
-                             Mice=rep(rep(1:mice_number,each=1000),no_method),
-                             force=rep(0,1000*mice_number*no_method))
-## agg
-plot_latent_df$force[(1:(1000*mice_number))] <- as.vector(sim_agg_rank$x[1001:2000,])
+no_method <- 3
+plot_latent_df <- data.frame(Methods = rep(1:no_method,
+                                         each=1000*mice_number),
+                             Mice = rep(rep(1:mice_number,each=1000),
+                                      no_method),
+                             force = rep(0,1000*mice_number*no_method))
+# ## agg
+# plot_latent_df$force[(1:(1000*mice_number))] <- as.vector(sim_agg_rank$x[1001:2000,])
 
 ## M1
-plot_latent_df$force[(1:(1000*mice_number))+1000*mice_number] <- as.vector(sim_cohort_hp$f)
+plot_latent_df$force[(1:(1000*mice_number))] <-
+  as.vector(sim_cohort_hp$f)
 
 ## M2
-plot_latent_df$force[(1:(1000*mice_number))+2000*mice_number] <- as.vector(sim_cohort_dchp$f)
+plot_latent_df$force[(1:(1000*mice_number)) + 
+                       1000*mice_number] <- as.vector(sim_cohort_dchp$f)
 
 ## M3
-plot_latent_df$force[(1:(1000*mice_number))+3000*mice_number] <- as.vector(sim_cohort_mmhp$f)
+plot_latent_df$force[(1:(1000*mice_number)) + 
+                       2000*mice_number] <- as.vector(sim_cohort_mmhp$f)
 
@@
 plot_latent_df$Method <- factor(plot_latent_df$Method,
-                                labels = c("AggRanking","C-HP","C-DCHP","C-MMHP"))
+                                labels = c("C-HP","C-DCHP","C-MMHP"))
 
 # png(paste(plot_path,"real_rank_one_cohort.png",sep=""),width=600,height=300)
-plot_cols <- col_df %>% filter(method %in% c("AggRank", "C-HP",
-                                "C-DCHP", "C-MMHP")) %>%
+plot_cols_slide <- col_df %>%
+  filter(method %in% c( "C-HP","C-DCHP", "C-MMHP")) %>%
   pull(cols)
@@
   geom_boxplot(alpha=0.7) +
-  scale_fill_manual(values = plot_cols) +
+  scale_fill_manual(values = plot_cols_slide) +
   # ggtitle("(a)") +
@@
                              labels = c("Agg-rank","C-HP","C-DCHP","C-MMHP"))
+
+cols_here <- col_df %>% 
+  filter(method %in% c("AggRank","C-HP","C-DCHP","C-MMHP")) %>%
+  pull(cols)
+
 p2 <- ggplot(plot_cor_df, aes(x="", y = cor, fill = Method)) +
         geom_boxplot(alpha=0.7, width=0.5) +
-        scale_fill_manual(values = plot_cols) + 
+        scale_fill_manual(values = cols_here) + 
         # ggtitle("(b)") +

### 2021-04-20 output_scripts/cmmhp_comparison/sim_comparison.Rmd

--- 2020-12-01 output_scripts/cmmhp_comparison/sim_comparison.Rmd
@@
                                     length(object_par$f_vec_1)))
-
+current_sims <- 1:n_sim
+# 7,31,34,43,47,49
 ## Iteration on 50 simulations
-for(s in c(1:n_sim)){
+# 8,11,19,27,32,42,43,46
+for(s in 47:n_sim){
   load(here(dc_sim_path,paste0("sim_model3_fit123_",s,".RData")))

### 2021-04-21 output_scripts/aug_updates.Rmd
add updates from aug to push to main

@@
   load(paste(data_path,cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",
+             cohort_names[current_cohort],
              ".RData",sep=''))
@@
   load(paste(data_path,cohort_names[current_cohort],
-             "/permute_cohort_mmhp_stan_result_",cohort_names[current_cohort],
+             "/permute_cohort_mmhp_stan_result_",
+             cohort_names[current_cohort],
              ".RData",sep=''))
@@
 
-  p <- mice_covars %>% ggplot(aes(true_rank,perm_rank)) + geom_point() +
+  p <- mice_covars %>% 
+    ggplot(aes(true_rank,perm_rank)) + 
+    geom_point() +
     ggtitle(paste("Cohort ",current_cohort,sep = ""))
 
-  q <- mice_covars %>% ggplot(aes(true_gam,perm_gam)) + geom_point()
+  q <- mice_covars %>% 
+    ggplot(aes(true_gam,perm_gam)) +
+    geom_point()
 
-  r <- mice_covars %>% ggplot(aes(true_zeta,perm_zeta)) + geom_point()
+  r <- mice_covars %>%
+    ggplot(aes(true_zeta,perm_zeta)) +
+    geom_point()
 
@@
 ```
+
 There does appear to be little to no structure in the estimated parameters 

### 2021-05-14 output_scripts/Paper_Plots.Rmd
reduce the base rates for simulations

@@
 
-temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
+temp_plot_df <- predict_day_mae_df_lst[[current_cohort]]
 temp_plot_df$method <- factor(temp_plot_df$method,
@@
 
-plot_cols_pred <- col_df %>% filter(method %in% levels(temp_plot_df$method)) %>%
+plot_cols_pred <- col_df %>% 
+  filter(method %in% levels(temp_plot_df$method)) %>%
    arrange(factor(method, levels = c("I-MMHP","DSNL",
@@
   # rename(Method = method) %>%
-  ggplot( aes(x = method, y = norm, fill = method)) +
+  ggplot( aes(x = method, y = mae, fill = method)) +
   geom_boxplot(alpha=0.7) +
@@
   xlab("Prediction horizon (day)") + 
-  ylab("Frobenius norm of error") +
-  ylim(0, 100) + # aren't infinite but >150 and <200
+  ylab("MAE") +
+  ylim(0, 8) + # aren't infinite but >150 and <200
   NULL
@@
   #mutate(norm = min(norm,100)) %>%
-  ggplot( aes(x = method, y = norm, fill = method)) +
+  ggplot( aes(x = method, y = mae, fill = method)) +
   geom_boxplot(alpha=0.7) +
@@
   ylab("Frobenius norm of error") +
-  ylim(0, 80) +
+  ylim(0, 10) +
   NULL
@@
 x.ttl <- ""; # blank x-axis label  
-y.ttl <- "rank corr. (expert rank)";  
+y.ttl <- "rank corr. (Glicko rank)";  
 ttl <- "(b)";  

### 2021-05-14 run_scripts/sim_fits.R

@@ -7,6 +7,7 @@ source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_set
 data_path <- "output/revisions/"
 
 library(rstan)
+library(R.utils)
 # library(compete)
 options(mc.cores = parallel::detectCores())
 rstan_options(auto_write = TRUE)
@@ -50,10 +51,10 @@ object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
 
 object_par <- list(sim_lambda_1 = 0.2,
                    sim_eta_1 = 2.5,
-                   gamma_var = runif(n = num_nodes, min = 0.01, max = 0.12),
-                   zeta_var = runif(n = num_nodes, min = 0.01, max = 0.12),
+                   gamma_var = runif(n = num_nodes, min = 0.01, max = 0.05),
+                   zeta_var = runif(n = num_nodes, min = 0.01, max = 0.05),
                    sim_eta_2 = 0.6,
-                   sim_eta_3 = 5,
+                   sim_eta_3 = 3,
                    sim_beta = 1.5,
                    f_vec_1 = seq(from = 0.05, to = 0.95,
                                  length.out = num_nodes))

### 2021-05-18 output_scripts/Paper_Plots.Rmd
start rmd for revisions

@@
 out <- captureOutput(for(curr_cohort in fit_cohorts){
-  naive_rank_10[[curr_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[curr_cohort]]])
-  expert_rank_10[[curr_cohort]] <- expertRankHierarchy(full_data[[cohort_names[curr_cohort]]])
+  naive_rank_10[[curr_cohort]] <-
+    naiveRankHierarchy(full_data[[cohort_names[curr_cohort]]])
+  expert_rank_10[[curr_cohort]] <-
+    expertRankHierarchy(full_data[[cohort_names[curr_cohort]]])
 })
@@
 
-mtext(text=expert_rank_10[[current_cohort]], side=1, line=1.8, outer=TRUE, cex=1.8,
+mtext(text=expert_rank_10[[current_cohort]],
+      side = 1, line = 1.8, outer = TRUE, cex = 1.8,
       at=1/14*c(1:12)-1/22)
@@
   ## bottom
-  mtext(text=expression(f[1],f[2],f[3],f[4],f[5]), side=1, line=2.4, outer=TRUE, 
-        at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
-        cex=2)
-  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.25,
-        at=0.5)
+  mtext(text = expression(f[1],f[2],f[3],f[4],f[5]), 
+        side = 1, line = 2.4, outer = TRUE, 
+        at = c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
+        cex = 2)
+  mtext(text = "Latent rank variables", side = 1,
+        line = 5.3,
+        outer = TRUE,
+        cex = 2.25,
+        at = 0.5)
   ## top
-  mtext(text="(a)", side=3, line=0, outer=TRUE, cex=2.5,
-        at=0.5, font=2)
+  mtext(text = "(a)", side = 3,
+        line = 0, 
+        outer = TRUE,
+        cex = 2.5,
+        at = 0.5, font = 2)
   ## left
@@
 model1_par_est <- list(lambda0 = mean(sim_model3_stan_sim1_total[[plot.s]]$lambda0),
-                       eta_1 = mean(sim_model3_stan_sim1_total[[plot.s]]$eta_1),
-                       eta_2 = mean(sim_model3_stan_sim1_total[[plot.s]]$eta_2),
-                       eta_3 = mean(sim_model3_stan_sim1_total[[plot.s]]$eta_3),
+                       eta_1 =
+                         mean(sim_model3_stan_sim1_total[[plot.s]]$eta_1),
+                       eta_2 =
+                         mean(sim_model3_stan_sim1_total[[plot.s]]$eta_2),
+                       eta_3 =
+                         mean(sim_model3_stan_sim1_total[[plot.s]]$eta_3),
                        beta = mean(sim_model3_stan_sim1_total[[plot.s]]$beta),

### 2021-05-18 output_scripts/revisions_may.Rmd
start rmd for revisions

---
title: "Comments on Latent Ranking"
author: "Owen G. Ward"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: FALSE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      # fig.path = "paper_figure/",
                      # dev = 'png',
                      # fig.height = 4.5,
                      # fig.width = 7,
                      warning = FALSE)

current_cohort <- 5

# don't write to this path
data_path <- "../output/"

func_dir <- "../lib/"

library(here)
library(rstan)
library(ppdiag)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(bayesplot)
library(viridis)
library(here)
library(compete)
library(colorspace)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source(paste(func_dir,'drawIntensity.R',sep =""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
```

## Run some longer/larger simulations

We can replace the simulation example with 5 nodes to one with
20 nodes.

```{r simulate_20_nodes}
num_nodes <- 20
cut_off <- 3
obs_time <- 200

model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
  return(eta1 * x * y * exp(-eta2 * abs(x-y))/(1 + exp(-eta3 *(x-y))))})

model3_fn <- list(alpha.fun = function(x, y, eta1, eta2){
  return(eta1*x*y*exp(-eta2*abs(x-y)))},
  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})

#### Save the simulation parameters ####

object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
  return(eta1*x*y*exp(-eta2*abs(x-y)))},
  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})

object_par <- list(sim_lambda_1 = 0.2,
                   sim_eta_1 = 1.5, # this has to be < beta
                   gamma_var = runif(n = num_nodes, min = 0.01, max = 0.05),
                   zeta_var = runif(n = num_nodes, min = 0.01, max = 0.05),
                   sim_eta_2 = 0.6,
                   sim_eta_3 = 3,
                   sim_beta = 2,
                   f_vec_1 = seq(from = 0.05, to = 0.95,
                                 length.out = num_nodes))

object_matrix <- list(lambda0_matrix=outer(object_par$gamma_var,
                                           object_par$zeta_var, "+"),
                      lambda1_matrix=matrix(object_par$sim_lambda_1,
                                            nrow=length(object_par$f_vec_1),
                                            ncol=length(object_par$f_vec_1)),
                      alpha_matrix=formMatrix(function(x,y)
                        object_fn$alpha.fun(x,y,object_par$sim_eta_1,
                                            object_par$sim_eta_2),
                        object_par$f_vec_1),
                      beta_matrix=matrix(object_par$sim_beta,
                                         nrow=length(object_par$f_vec_1),
                                         ncol=length(object_par$f_vec_1)),
                      q1_matrix=formMatrix(function(x,y)
                        object_fn$q1.fun(x, y,
                                         object_par$sim_eta_3),
                        object_par$f_vec_1),
                      q2_matrix=formMatrix(function(x,y)
                        object_fn$q0.fun(x, y,
                                         object_par$sim_eta_3),
                        object_par$f_vec_1))

## Simulate
sim_model3_data <- list()
N_array <- array(0, c(1, num_nodes, num_nodes))
# for(i in c(1:n_sim)){
sim_model3_data <- simulateLatentMMHP(lambda0_matrix =
                                        object_matrix$lambda0_matrix,
                                      lambda1_matrix =
                                        object_matrix$lambda1_matrix,
                                      alpha_matrix = object_matrix$alpha_matrix,
                                      beta_matrix = object_matrix$beta_matrix,
                                      q1_matrix = object_matrix$q1_matrix,
                                      q2_matrix = object_matrix$q2_matrix,
                                      horizon = obs_time)
clean_sim_data <- cleanSimulationData(raw_data = sim_model3_data,
                                      cut_off = cut_off,
                                      N = length(object_par$f_vec_1))
N_array <- clean_sim_data$N_count

```

We wish to confirm that this simulation study actually results
in sensible, such as whether the I&SI is consistent with
the true latent rankings.

We can also plot the MMHP fit for a single pair using `ppdiag`.

```{r plot_pair}
start <- 20
end <- 10

poss_start <- which(clean_sim_data$I_fit == start)
poss_end <- which(clean_sim_data$J_fit == end)

pair_id <- intersect(poss_start, poss_end)

events <- clean_sim_data$event_matrix[pair_id, ]
events <- events[events > 0]

q1 <- object_matrix$q1_matrix[start, end]
q2 <- object_matrix$q2_matrix[start, end]

obj <- pp_mmhp(lambda0 = object_matrix$lambda0_matrix[start, end],
        lambda1 = object_matrix$lambda1_matrix[start, end],
        alpha = object_matrix$alpha_matrix[start, end],
        beta = object_matrix$beta_matrix[start, end],
        Q = matrix(c(-q1, q1, q2, -q2), nrow = 2, ncol = 2, byrow = TRUE))

pp_residual(obj, events, end = obs_time)

# can't plot the mmhp unless you infer the latent process
### can use viterbi and such for now

```

```{r ranking_sim_data}
### i&si method
count_data_dc <- get_wl_matrix(df = cbind(clean_sim_data$start,
                                          clean_sim_data$end))
isi_dc.out <- compete::isi98(m = count_data_dc, random = TRUE)
isi_dc.out$best_order

### agg rank method
agg_rank_data <- clean_sim_data$N_count
agg_rank_model <- stan_model(here("lib","latent_rank_agg_sim.stan"))

agg_rank_fit <- rstan::sampling(agg_rank_model,
                                data = list(n = num_nodes,
                                            n_matrix = agg_rank_data),
                                iter = 1000,
                                chains = 4)
agg_sims <- rstan::extract(agg_rank_fit)

agg_rank <- order(apply(agg_sims$x, 2, mean))
agg_rank

### then glicko
glicko_data <- tibble(start = clean_sim_data$start,
                      end = clean_sim_data$end)

glicko_data <- glicko_data %>%
  mutate(id = row_number(), score = 1) %>%
  select(id, start, end, score)

library(PlayerRatings)
gl_train <- my_glicko(glicko_data, history=TRUE, cval=2)

gl_train

gl_ranks <- order(gl_train$ratings$Rating)
gl_ranks
```

So there is some structure in this data here that is perhaps 
best picked up by the I&SI method.

Similarly, we can confirm we get sensible fits by fitting the individual
MMHP model to each pair and showing the residuals.

```{r residuals-immhp-sim}
pr_matrix <- readRDS(here("output", "revisions", "pr_matrix_immhp.RDS"))
rr_matrix <- readRDS(here("output", "revisions", "rr_matrix_immhp.RDS"))
# image(pr_matrix)

matrix_lst_plot <- list()
matrix_lst_plot[[1]] <- rr_matrix
matrix_lst_plot[[2]] <- pr_matrix

myMultiMatrixPlot(X = matrix_lst_plot,
                  no_matrix = 2,
                  n_row = 1,
                  xLabels = 1:20,
                  yLabels = 20:1,
                  min = -30,
                  max = 30,
                  axis_cex = 2,
                  title_cex = 1.8,
                  colorPalette = "RdBu",
                  if.emp = FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst = list("Raw","Pearson"), 
                  #title_lst = list("I-MMHP"),
                  col_axis = c(-30,-15,0,15,30), 
                  fake_matrix = TRUE,
                  matrix.mar = c(2.5,2.5,2.5,1) )

```

### 2021-05-18 run_scripts/m3_immhp_sim.R

@@ -51,60 +51,60 @@ object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
   q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
   q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
 
-# object_par <- list(sim_lambda_1 = 0.2,
-#                    sim_eta_1 = 1.5, # this has to be < beta
-#                    gamma_var = runif(n = num_nodes, min = 0.01, max = 0.05),
-#                    zeta_var = runif(n = num_nodes, min = 0.01, max = 0.05),
-#                    sim_eta_2 = 0.6,
-#                    sim_eta_3 = 3,
-#                    sim_beta = 2,
-#                    f_vec_1 = seq(from = 0.05, to = 0.95,
-#                                  length.out = num_nodes))
-# 
-# object_matrix <- list(lambda0_matrix=outer(object_par$gamma_var,
-#                                            object_par$zeta_var, "+"),
-#                       lambda1_matrix=matrix(object_par$sim_lambda_1,
-#                                             nrow=length(object_par$f_vec_1),
-#                                             ncol=length(object_par$f_vec_1)),
-#                       alpha_matrix=formMatrix(function(x,y)
-#                         object_fn$alpha.fun(x,y,object_par$sim_eta_1,
-#                                             object_par$sim_eta_2),
-#                         object_par$f_vec_1),
-#                       beta_matrix=matrix(object_par$sim_beta,
-#                                          nrow=length(object_par$f_vec_1),
-#                                          ncol=length(object_par$f_vec_1)),
-#                       q1_matrix=formMatrix(function(x,y) 
-#                         object_fn$q1.fun(x, y,
-#                                          object_par$sim_eta_3),
-#                         object_par$f_vec_1),
-#                       q2_matrix=formMatrix(function(x,y) 
-#                         object_fn$q0.fun(x, y, 
-#                                          object_par$sim_eta_3),
-#                         object_par$f_vec_1))
-# 
-# 
-# ## Simulate
-# sim_model3_data <- list()
-# N_array <- array(0, c(1, num_nodes, num_nodes))
-# # for(i in c(1:n_sim)){
-# sim_model3_data <- simulateLatentMMHP(lambda0_matrix = object_matrix$lambda0_matrix,
-#                                       lambda1_matrix = object_matrix$lambda1_matrix,
-#                                       alpha_matrix = object_matrix$alpha_matrix,
[…]

### 2021-05-20 output_scripts/revisions_may.Rmd

@@
 
+obj$q1 <- q1
+obj$q2 <- q2
+
+ viterbi_result <- myViterbi(events = events, 
+                             param = obj,
+                             termination = obs_time)
+
+latent_inter <- interpolateLatentTrajectory(obj, 
+                                            events,
+                                            viterbi_result$zt_v,
+                                            initial.state =
+                                                 viterbi_result$initial_state,
+                                            termination.time = obs_time,
+                                            termination.state =
+                                              viterbi_result$termination_state)
+
+event_state <- ppdiag:::mmhp_event_state(params = obj, events = events)
+
+latent_state <- ppdiag:::interpolate_mmhp_latent(params = obj, events,
+                                                 zt = event_state$zt)
+
+mmhp_latent <- list()
+mmhp_latent$start <- 0
+mmhp_latent$end <- obs_time
+mmhp_latent$x <- c(0,latent_state$x.hat, obs_time)
+mmhp_latent$z <- c(viterbi_result$initial_state, latent_state$z.hat)
+mmhp_latent$events <- c(0, events)
+mmhp_latent$zt <- c(1, event_state$zt)
+ppdiag::drawUniMMHPIntensity(obj, mmhp_latent)
+
+# this plot is not correct for later Hawkes states...
+
 ```
@@
 isi_dc.out <- compete::isi98(m = count_data_dc, random = TRUE)
-isi_dc.out$best_order
+as.numeric(isi_dc.out$best_order) # from highest to lowest
 
@@
 agg_rank <- order(apply(agg_sims$x, 2, mean))
-agg_rank
+rev(agg_rank) # from highest to lowest
 
@@
 gl_ranks <- order(gl_train$ratings$Rating)
-gl_ranks
+gl_ranks #highest to lowest
 ```
@@
 Similarly, we can confirm we get sensible fits by fitting the individual
-MMHP model to each pair and showing the residuals.
+MMHP model to each pair and showing the residuals. This
+is consistent with what we see for real data, where the
+residual matrices show overall small positive values, indicating
+underestimation when we fit individual models.
 
@@
 ```
+
+## Explaining the g function
+
+```{r plot_g}
+alpha.fun <- function(x,y,eta1,eta2)
+  {
+   return( eta1 * x * y *exp(-eta2 * abs(x - y) ) )
+  }
+
+f_vec <- c(0.1, 0.2, 0.4, 0.8, 0.9)
+
+eta1 <- 6.6
+eta2 <- 0.37
+
+crossing(send = f_vec, rec = f_vec) %>% 
+  filter(send != rec) %>% 
+  mutate(alpha = alpha.fun(send, rec, eta1, eta2))
+
+```

### 2021-05-21 output_scripts/revisions_may.Rmd
styler rmd

--- 2021-05-18 output_scripts/revisions_may.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, 
+knitr::opts_chunk$set(
+  echo = TRUE,
   # fig.path = "paper_figure/",
@@
   # fig.width = 7,
-                      warning = FALSE)
+  warning = FALSE
+)
 
@@
 library(ppdiag)
-Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
+Sys.setenv(LOCAL_CPPFLAGS = "-march=corei7 -mtune=corei7")
 options(mc.cores = parallel::detectCores())
@@
 library(colorspace)
-source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
-source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
-source(paste(func_dir,'cleanData.R',sep = "")) 
-source(paste(func_dir,'prepareDataStan.R',sep = "")) 
-source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
-source(paste(func_dir,'plotUtil.R',sep = "")) 
-source(paste(func_dir,'mmhp.R',sep = ""))
-source(paste(func_dir,'uniHawkes.R',sep = ""))
-source(paste(func_dir,'simulatePrediction.R',sep = ""))
-source(paste(func_dir,'myGlicko.R',sep = ""))
-source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
-source(paste(func_dir,'residualStructureScore.R',sep = ""))
-source(paste(func_dir,'drawIntensity.R',sep =""))
+source(paste(func_dir, "naiveRankHierarchy.R", sep = ""))
+source(paste(func_dir, "expertRankHierarchy.R", sep = ""))
+source(paste(func_dir, "cleanData.R", sep = ""))
+source(paste(func_dir, "prepareDataStan.R", sep = ""))
+source(paste(func_dir, "inferLatentMmhp.R", sep = ""))
+source(paste(func_dir, "plotUtil.R", sep = ""))
+source(paste(func_dir, "mmhp.R", sep = ""))
+source(paste(func_dir, "uniHawkes.R", sep = ""))
+source(paste(func_dir, "simulatePrediction.R", sep = ""))
+source(paste(func_dir, "myGlicko.R", sep = ""))
+source(paste(func_dir, "matrixPlotParameter.R", sep = ""))
+source(paste(func_dir, "residualStructureScore.R", sep = ""))
+source(paste(func_dir, "drawIntensity.R", sep = ""))
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
@@
 
-model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
-  return(eta1 * x * y * exp(-eta2 * abs(x-y))/(1 + exp(-eta3 *(x-y))))})
+model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3) {
+  return(eta1 * x * y * exp(-eta2 * abs(x - y)) / (1 + exp(-eta3 * (x - y))))
+})
 
-model3_fn <- list(alpha.fun = function(x, y, eta1, eta2){
-  return(eta1*x*y*exp(-eta2*abs(x-y)))},
-  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
-  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
+model3_fn <- list(
+  alpha.fun = function(x, y, eta1, eta2) {
+    return(eta1 * x * y * exp(-eta2 * abs(x - y)))
+  },
+  q1.fun = function(x, y, eta3) {
+    return(exp(-eta3 * x))
+  },
+  q0.fun = function(x, y, eta3) {
+    return(exp(-eta3 * y))
+  }
+)
 
@@
 
-object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
-  return(eta1*x*y*exp(-eta2*abs(x-y)))},
-  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
-  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
+object_fn <- list(
+  alpha.fun = function(x, y, eta1, eta2) {
+    return(eta1 * x * y * exp(-eta2 * abs(x - y)))
+  },
+  q1.fun = function(x, y, eta3) {
+    return(exp(-eta3 * x))
+  },
+  q0.fun = function(x, y, eta3) {
+    return(exp(-eta3 * y))
+  }
+)
 
-object_par <- list(sim_lambda_1 = 0.2,
+object_par <- list(
+  sim_lambda_1 = 0.2,
   sim_eta_1 = 1.5, # this has to be < beta
@@
   sim_beta = 2,
-                   f_vec_1 = seq(from = 0.05, to = 0.95,
-                                 length.out = num_nodes))
+  f_vec_1 = seq(
+    from = 0.05, to = 0.95,
+    length.out = num_nodes
+  )
+)
 
-object_matrix <- list(lambda0_matrix=outer(object_par$gamma_var,
-                                           object_par$zeta_var, "+"),
-                      lambda1_matrix=matrix(object_par$sim_lambda_1,
-                                            nrow=length(object_par$f_vec_1),
-                                            ncol=length(object_par$f_vec_1)),
-                      alpha_matrix=formMatrix(function(x,y)
-                        object_fn$alpha.fun(x,y,object_par$sim_eta_1,
-                                            object_par$sim_eta_2),
-                        object_par$f_vec_1),
-                      beta_matrix=matrix(object_par$sim_beta,
-                                         nrow=length(object_par$f_vec_1),
-                                         ncol=length(object_par$f_vec_1)),
-                      q1_matrix=formMatrix(function(x,y)
-                        object_fn$q1.fun(x, y,
-                                         object_par$sim_eta_3),
-                        object_par$f_vec_1),
-                      q2_matrix=formMatrix(function(x,y)
-                        object_fn$q0.fun(x, y,
-                                         object_par$sim_eta_3),
-                        object_par$f_vec_1))
+object_matrix <- list(
+  lambda0_matrix = outer(
+    object_par$gamma_var,
+    object_par$zeta_var, "+"
+  ),
+  lambda1_matrix = matrix(object_par$sim_lambda_1,
+    nrow = length(object_par$f_vec_1),
+    ncol = length(object_par$f_vec_1)
+  ),
+  alpha_matrix = formMatrix(
+    function(x, y) {
+      object_fn$alpha.fun(
+        x, y, object_par$sim_eta_1,
+        object_par$sim_eta_2
+      )
+    },
+    object_par$f_vec_1
+  ),
+  beta_matrix = matrix(object_par$sim_beta,
+    nrow = length(object_par$f_vec_1),
+    ncol = length(object_par$f_vec_1)
+  ),
+  q1_matrix = formMatrix(
+    function(x, y) {
+      object_fn$q1.fun(
+        x, y,
+        object_par$sim_eta_3
+      )
+    },
+    object_par$f_vec_1
+  ),
+  q2_matrix = formMatrix(
+    function(x, y) {
+      object_fn$q0.fun(
+        x, y,
+        object_par$sim_eta_3
+      )
+    },
+    object_par$f_vec_1
+  )
+)
 
@@
 # for(i in c(1:n_sim)){
-sim_model3_data <- simulateLatentMMHP(lambda0_matrix =
+sim_model3_data <- simulateLatentMMHP(
+  lambda0_matrix =
     object_matrix$lambda0_matrix,
@@
   q2_matrix = object_matrix$q2_matrix,
-                                      horizon = obs_time)
-clean_sim_data <- cleanSimulationData(raw_data = sim_model3_data,
+  horizon = obs_time
+)
+clean_sim_data <- cleanSimulationData(
+  raw_data = sim_model3_data,
   cut_off = cut_off,
-                                      N = length(object_par$f_vec_1))
+  N = length(object_par$f_vec_1)
+)
 N_array <- clean_sim_data$N_count
-
 ```
@@
 
-obj <- pp_mmhp(lambda0 = object_matrix$lambda0_matrix[start, end],
+obj <- pp_mmhp(
+  lambda0 = object_matrix$lambda0_matrix[start, end],
   lambda1 = object_matrix$lambda1_matrix[start, end],
@@
   beta = object_matrix$beta_matrix[start, end],
-        Q = matrix(c(-q1, q1, q2, -q2), nrow = 2, ncol = 2, byrow = TRUE))
+  Q = matrix(c(-q1, q1, q2, -q2), nrow = 2, ncol = 2, byrow = TRUE)
+)
 
@@
 
+obj$q1 <- q1
+obj$q2 <- q2
+
+viterbi_result <- myViterbi(
+  events = events,
+  param = obj,
+  termination = obs_time
+)
+
+latent_inter <- interpolateLatentTrajectory(obj,
+  events,
+  viterbi_result$zt_v,
+  initial.state =
+    viterbi_result$initial_state,
+  termination.time = obs_time,
+  termination.state =
+    viterbi_result$termination_state
+)
+
+event_state <- ppdiag:::mmhp_event_state(params = obj, events = events)
+
+latent_state <- ppdiag:::interpolate_mmhp_latent(
+  params = obj, events,
+  zt = event_state$zt
+)
+
+mmhp_latent <- list()
+mmhp_latent$start <- 0
+mmhp_latent$end <- obs_time
+mmhp_latent$x <- c(0, latent_state$x.hat, obs_time)
+mmhp_latent$z <- c(viterbi_result$initial_state, latent_state$z.hat)
+mmhp_latent$events <- c(0, events)
+mmhp_latent$zt <- c(1, event_state$zt)
+ppdiag::drawUniMMHPIntensity(obj, mmhp_latent)
+
+# this plot is not correct for later Hawkes states...
 ```
@@
 ### i&si method
-count_data_dc <- get_wl_matrix(df = cbind(clean_sim_data$start,
-                                          clean_sim_data$end))
+count_data_dc <- get_wl_matrix(df = cbind(
+  clean_sim_data$start,
+  clean_sim_data$end
+))
 isi_dc.out <- compete::isi98(m = count_data_dc, random = TRUE)
-isi_dc.out$best_order
+as.numeric(isi_dc.out$best_order) # from highest to lowest
 
@@
 agg_rank_data <- clean_sim_data$N_count
-agg_rank_model <- stan_model(here("lib","latent_rank_agg_sim.stan"))
+agg_rank_model <- stan_model(here("lib", "latent_rank_agg_sim.stan"))
 
 agg_rank_fit <- rstan::sampling(agg_rank_model,
-                                data = list(n = num_nodes,
-                                            n_matrix = agg_rank_data),
+  data = list(
+    n = num_nodes,
+    n_matrix = agg_rank_data
+  ),
   iter = 1000,
-                                chains = 4)
+  chains = 4
+)
 agg_sims <- rstan::extract(agg_rank_fit)
@@
 agg_rank <- order(apply(agg_sims$x, 2, mean))
-agg_rank
+rev(agg_rank) # from highest to lowest
 
 ### then glicko
-glicko_data <- tibble(start = clean_sim_data$start,
-                      end = clean_sim_data$end)
+glicko_data <- tibble(
+  start = clean_sim_data$start,
+  end = clean_sim_data$end
+)
 
@@
 library(PlayerRatings)
-gl_train <- my_glicko(glicko_data, history=TRUE, cval=2)
+gl_train <- my_glicko(glicko_data, history = TRUE, cval = 2)
 
@@
 gl_ranks <- order(gl_train$ratings$Rating)
-gl_ranks
+gl_ranks # highest to lowest
 ```
@@
 
-myMultiMatrixPlot(X = matrix_lst_plot,
+myMultiMatrixPlot(
+  X = matrix_lst_plot,
   no_matrix = 2,
@@
   if.emp = FALSE,
-                  #legend.mar=c(0.5,.5,0.5,0.5),
-                  title_lst = list("Raw","Pearson"), 
-                  #title_lst = list("I-MMHP"),
-                  col_axis = c(-30,-15,0,15,30), 
+  # legend.mar=c(0.5,.5,0.5,0.5),
+  title_lst = list("Raw", "Pearson"),
+  # title_lst = list("I-MMHP"),
+  col_axis = c(-30, -15, 0, 15, 30),
   fake_matrix = TRUE,
-                  matrix.mar = c(2.5,2.5,2.5,1) )
+  matrix.mar = c(2.5, 2.5, 2.5, 1)
+)
+```
 
+## Explaining the g function
+
+```{r plot_g}
+alpha.fun <- function(x, y, eta1, eta2) {
+  return(eta1 * x * y * exp(-eta2 * abs(x - y)))
+}
+
+f_vec <- c(0.1, 0.2, 0.4, 0.8, 0.9)
+
+eta1 <- 6.6
+eta2 <- 0.37
+
+crossing(send = f_vec, rec = f_vec) %>%
+  filter(send != rec) %>%
+  mutate(alpha = alpha.fun(send, rec, eta1, eta2))
 ```
+
+## Community Structure Plot
+
+```{r recreate_jing_figure}
+load("../output/state_separation_plot.RData")
+for (current_cohort in c(3)) {
+  total_event_array <- total_event_array_lst[[current_cohort]]
+  active_event_array <- active_event_array_lst[[current_cohort]]
+  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+  return_df <- cleanObservationPeriod(current_cohort, clean_data)
+
+  start_win <- floor(max(return_df$observe.id) / 3) * (0:2) + 1
+  end_win <- floor(max(return_df$observe.id) / 3) * (1:3)
+  matrix1 <- apply(
+    total_event_array[, , start_win[1]:end_win[1]] -
+      active_event_array[, , start_win[1]:end_win[1]],
+    c(1, 2), sum
+  )
+  matrix2 <- apply(
+    total_event_array[, , start_win[2]:end_win[2]] -
+      active_event_array[, , start_win[2]:end_win[2]],
+    c(1, 2), sum
+  )
+  matrix3 <- apply(
+    total_event_array[, , start_win[3]:end_win[3]] -
+      active_event_array[, , start_win[3]:end_win[3]],
+    c(1, 2), sum
+  )
+
+  g_community1 <- graph_from_adjacency_matrix(matrix1, mode = "undirected")
+  lec1 <- cluster_leading_eigen(g_community1)
+
+  g_community2 <- graph_from_adjacency_matrix(matrix2, mode = "undirected")
+  lec2 <- cluster_leading_eigen(g_community2)
+
+  g_community3 <- graph_from_adjacency_matrix(matrix3, mode = "undirected")
+  lec3 <- cluster_leading_eigen(g_community3)
+
+  ### Make plot for t=1
+  png(paste(plot_path, "real_clustering_1.png", sep = ""), 
+      height = 600,
+      width = 600)
+  myCircularPlot(
+    cur.matrix = matrix1,
+    cur.order = c(1, 4, 10, 5, 11, 6, 7, 2, 8, 12, 9, 3),
+    cur.color = c(
+      colorRampPalette(brewer.pal(
+        name = "YlOrBr",
+        n =
+          8
+      ))(14)[c(
+        13,
+        9,
+        5
+      )],
+      colorRampPalette(brewer.pal(
+        name = "PuRd",
+        n =
+          8
+      ))(15)[c(
+        4,
+        6,
+        8,
+        10,
+        12,
+        14
+      )],
+      colorRampPalette(brewer.pal(
+        name = "Blues",
+        n =
+          8
+      ))(10)[c(
+        5,
+        7,
+        9
+      )]
+    ),
+    cur.gap = c(rep(5, 2), 30, rep(5, 5), 30, rep(5, 2), 30)
+  )
+  dev.off()
+
+  ### Make plot for t=2
+  png(paste(plot_path, "real_clustering_2.png", sep = ""),
+   height = 600,
+   width = 600
+ )
+ myCircularPlot(
+   cur.matrix = matrix2,
+   cur.order = c(1, 7, 8, 2, 3, 4, 5, 9, 10, 6, 11, 12),
+   cur.color = c(
+     colorRampPalette(brewer.pal(
+       name = "YlOrBr",
+       n = 8))(14)[c(13, 11, 9, 7, 5, 3)],
+     colorRampPalette(brewer.pal(
+       name = "Blues",
+       n = 8))(15)[c(4, 6, 8, 10, 12, 14)]
+   ),
+   cur.gap = c(rep(5, 5), 30, rep(5, 5), 30)
+ )
+ dev.off()
+
+  ### Make plot for t=3
+  png(paste(plot_path, "real_clustering_3.png", sep = ""),
+      height = 600,
+      width = 600)
+  myCircularPlot(
+    cur.matrix = matrix3[-3, -3],
+    cur.order = c(1, 10, 5, 2, 3, 6, 7, 8, 4, 11, 9),
+    cur.color = c(
+      colorRampPalette(
+        brewer.pal(name = "YlOrBr",
+                   n = 8))(14)[c(13, 9, 5, 3)],
+      colorRampPalette(brewer.pal(
+        name = "Blues",
+        n = 8))(16)[c(7, 9, 11, 13, 15)],
+      colorRampPalette(brewer.pal(
+        name = "PuRd",
+        n = 8))(15)[c(8, 12)]
+    ),
+    cur.gap = c(rep(5, 3), 30, rep(5, 4), 30, rep(5, 1), 30),
+    cur.ID = c(1:12)[-3]
+  )
+  dev.off()
+}
+```

### 2021-05-22 output_scripts/revisions_may.Rmd
styler on some more code

@@
 
+```{r construct_plot}
+state_types <- c("total", "utility", "social")
+metric_types <- c("dc", "ttri", "i")
+state_separation_result <- data.frame(array(0,
+                                            c(10 * 
+                                                length(state_types) *
+                                                length(metric_types),
+                                              4)))
+colnames(state_separation_result) <- c("cohort", "state", "metric", "value")
+
+total_event_array_lst <- list()
+active_event_array_lst <- list()
+for (current_cohort in c(2:10)) {
+  print(current_cohort)
+  load(paste(data_path, 
+             cohort_names[current_cohort],
+    "/mmhp_est_zt_",
+    cohort_names[current_cohort],
+    ".RData",
+    sep = ""
+  ))
+  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+  return_df <- cleanObservationPeriod(current_cohort, clean_data)
+  unique_pairs_df <- return_df %>%
+    group_by(initiator, recipient) %>%
+    dplyr::summarize(
+      count = n(),
+      observe = list(observe.id),
+      observe.length = list(observe.time),
+      no.events = list(no.events)
+    )
+  unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])
+
+  expert_rank <- expert_rank_10[[current_cohort]]
+
+  # ------------- Load the saved stan result, plot the inferred parameters and save
+  total_event_array_lst[[current_cohort]] <- 
+    array(0, dim = c(mice_number, mice_number, max(return_df$observe.id)))
+  active_event_array_lst[[current_cohort]] <-
+    array(0, dim = c(mice_number, mice_number, max(return_df$observe.id)))
+
+  for (i in 1:mice_number) {
+    for (j in 1:mice_number) {
+      pair <- which(unique_pairs_df$initiator == i & 
+                      unique_pairs_df$recipient == j)
+      if (length(pair) > 0) {
+        current_window_vec <- unique_pairs_df$observe[[pair]]
+        for (cur_win in current_window_vec) {
+          row_indicator <- (return_df$initiator == i) & 
+            (return_df$recipient == j) &
+            (return_df$observe.id == cur_win)
+          total_event_array_lst[[current_cohort]][i, j, cur_win] <-
+            length(return_df[row_indicator, "event.times"][[1]])
+          active_event_array_lst[[current_cohort]][i, j, cur_win] <- 
+            sum(apply(2 - state_array_list[[pair]][[cur_win]], 1, mean) > 0.5)
+        }
+      }
+    }
+  }
+
+  start_win <- floor(max(return_df$observe.id) / 2)
+  end_win <- max(return_df$observe.id)
+  matrix1 <- apply(
+    total_event_array_lst[[current_cohort]][, , start_win:end_win],
+    c(1, 2),
+    sum
+    )[expert_rank, expert_rank]
+  matrix2 <- apply(
+    active_event_array_lst[[current_cohort]][, , start_win:end_win],
+    c(1, 2),
+    sum
+    )[expert_rank, expert_rank]
+  matrix3 <- apply(
+    total_event_array_lst[[current_cohort]][, , start_win:end_win] -
+      active_event_array_lst[[current_cohort]][, , start_win:end_win],
+    c(1, 2),
+    sum
+    )[expert_rank, expert_rank]
+
+  # ------ compute metrics ------
+  state_separation_result$cohort[
+    ((current_cohort - 1) * 
+      length(metric_types) *
+      length(state_types) + 1):(current_cohort * length(metric_types) *
+                                  length(state_types))] <- cohort_names[current_cohort]
+  state_separation_result$metric[
+    ((current_cohort - 1) *
+       length(metric_types) *
+       length(state_types) + 1):(current_cohort * length(metric_types) *
+                                   length(state_types))] <- 
+    rep(c("dc", "ttri", "i"), length(state_types))
+
+  state_separation_result$state[
+    ((current_cohort - 1) *
+       length(metric_types) *
+       length(state_types) + 1):(current_cohort * length(metric_types) *
+                                   length(state_types) -
+                                   length(metric_types) * 2)] <- "total"
+  state_separation_result$value[
+    ((current_cohort - 1) *
+       length(metric_types) *
+       length(state_types) + 1):(current_cohort * length(metric_types) *
+                                   length(state_types) - 
+                                   length(metric_types) * 2)] <- 
+    c(dci(matrix1), ttri(matrix1)[[2]], iAndSI(matrix1)[1])
+
+  state_separation_result$state[
+    ((current_cohort - 1) *
+       length(metric_types) *
+       length(state_types) + 
+       length(metric_types) + 1):(current_cohort * 
+                                    length(metric_types) *
+                                    length(state_types) -
+                                    length(metric_types))] <-
+    "utility"
+  state_separation_result$value[
+    ((current_cohort - 1) *
+       length(metric_types) * 
+       length(state_types) + 
+       length(metric_types) + 1):(current_cohort * length(metric_types)
+                                  * length(state_types)
+                                  - length(metric_types))] <-
+    c(dci(matrix2), ttri(matrix2)[[2]], iAndSI(matrix2)[1])
+
+  state_separation_result$state[(current_cohort * length(metric_types) * length(state_types) - length(metric_types) + 1):(current_cohort * length(metric_types) * length(state_types))] <- "social"
+  state_separation_result$value[(current_cohort * length(metric_types) * length(state_types) - length(metric_types) + 1):(current_cohort * length(metric_types) * length(state_types))] <- c(dci(matrix3), ttri(matrix3)[[2]], iAndSI(matrix3)[1])
+}
+
+save(state_types, metric_types, state_separation_result,
+  total_event_array_lst, active_event_array_lst,
+  file = "../output/state_separation_plot.RData"
+)
+
+```
+
 ```{r recreate_jing_figure}

### 2021-05-26 output_scripts/revisions_may.Rmd
update rank sims for 20 nodes and setup for cmdstan also

@@
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
+
+cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cut_off <- 3
+mice_number <- 12
+
+full_data <- readRDS("../data/mice.RData")
+
+fit_cohorts <- c(1:10)
+naive_rank_10 <- list()
+expert_rank_10 <- list()
+out <- captureOutput(for(curr_cohort in fit_cohorts){
+  naive_rank_10[[curr_cohort]] <-
+    naiveRankHierarchy(full_data[[cohort_names[curr_cohort]]])
+  expert_rank_10[[curr_cohort]] <-
+    expertRankHierarchy(full_data[[cohort_names[curr_cohort]]])
+})
+
+theme_set(theme_minimal())
+
 ```
@@
 # this plot is not correct for later Hawkes states...
+## don't think the bug is with ppdiag
 ```
@@
 
+## Larger Simulation Study
+
+```{r load_in_large_sim}
+load(here("output", "revisions", "sim_model3_immhp_.RData"))
+load(here("output", "revisions", "sim_model3_fit_cmmhp_.RData"))
+
+post_rank <- post_draws %>% 
+  select(starts_with("f")) %>% 
+  ## rename the f cols first
+  rename_with(~gsub("[", "_", .x, fixed = TRUE)) %>% 
+  rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
+  pivot_longer(everything(),
+               names_to = "node",
+               values_to = "rank") 
+  # group_by(node) %>% 
+  # summarise(ave_rank = mean(rank), sd_rank = sd(rank)) %>%
+
+## order nodes
+# post_rank$node <- as.factor(post_rank$node)
+true_rank <- tibble(names = paste0("f_", 1:20),
+                    f_vec_1 = seq(from = 0.05,
+                                  to = 0.95,
+                                  length.out = 20))
+
+post_rank$node <- factor(post_rank$node, levels = paste0("f_", 1:20))
+
+post_mean <- post_rank %>%
+  group_by(node) %>% 
+  summarise(ave_rank = mean(rank))
+
+post_rank %>% 
+  ggplot(aes(node, rank)) + 
+  geom_boxplot() +
+  geom_point(data = true_rank,
+             mapping = aes(names, f_vec_1, shape = 16),
+             colour = "red") +
+  geom_point(data = post_mean,
+             mapping = aes(node, ave_rank, shape = 16),
+             colour = "blue") +
+  scale_shape_identity() +
+  labs(title = "Inferred Latent Ranking with Truth",
+       x = "Node", y = "Latent Ranking",
+       colour = "Summary")
+## blue is posterior mean, red is true value
+## can add legend to fix this
+```
+
+What else should we infer with a larger simulation example? How do we visualise 
+the results in this case?
+
+## Stability of Rankings over Time
+
+```{r load_cohort_rankings}
+for(cohort_id in 1:10){
+  start_rank <- readRDS(file = paste(data_path,
+                                 "/revisions/rank_stab/", "cohort_",
+                                 cohort_id, "start.RDS",
+                                 sep = ""))
+
+  end_rank <- readRDS(file = paste(data_path,
+                                   "/revisions/rank_stab/", "cohort_",
+                                   cohort_id, "end.RDS",
+                                   sep = ""))
+  ### plot both of these
+  init_ranks <- start_rank %>%
+    select(starts_with("f")) %>%
+    rename_with(~gsub("[", "_", .x, fixed = TRUE)) %>%
+    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>%
+    pivot_longer(everything(),
+                 names_to = "node",
+                 values_to = "rank")
+
+  final_ranks <- end_rank %>%
+    select(starts_with("f")) %>%
+    rename_with(~gsub("[", "_", .x, fixed = TRUE)) %>%
+    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>%
+    pivot_longer(everything(),
+                 names_to = "node",
+                 values_to = "rank")
+
+  init_ranks$node <- factor(init_ranks$node, levels = paste0("f_", 1:12))
+  final_ranks$node <- factor(final_ranks$node, levels = paste0("f_", 1:12))
+
+  init_ranks$when <- "first14"
+  final_ranks$when <- "last14"
+
+  init_ranks %>% 
+    ggplot(aes(node, rank)) + 
+    geom_boxplot() +
+    labs(title = "Ranking from first 14 Days")
+
+  final_ranks %>% 
+    ggplot(aes(node, rank)) + 
+    geom_boxplot() +
+    labs(title = "Ranking from final 14 Days")
+
+  all_ranks <- bind_rows(init_ranks, final_ranks)
+
+  coh_plot <- all_ranks %>% 
+    ggplot(aes(node, rank, fill = when)) +
+    geom_boxplot() +
+    labs(x = "Mouse",
+         y = "Latent Rank", 
+         fill = "Time Period",
+         title = "Agreement between initial and later ranking",
+         subtitle = "One Cohort")
+  print(coh_plot)
+}
+
+```
+
 ## Community Structure Plot
@@
 ```{r construct_plot}
+iAndSI <- function(M) {
+  n <- ncol(M)
+  result <- rep(0, 2)
+  k <- (M - t(M)) / 2
+  k[upper.tri(k)] <- 0
+  result[1] <- 0
+  a <- length(which(k > 0))
+  y <- which(k > 0) %% n
+  x <- (which(k > 0) - 1) %/% n + 1
+  y[y == 0] <- y[y == 0] + n
+  if (a > 0) {
+    result[1] <- a
+    result[2] <- sum(y - x)
+  }
+  return(result)
+}
+
 state_types <- c("total", "utility", "social")
@@
              cohort_names[current_cohort],
-    "/mmhp_est_zt_",
+    "/cmmhp_est_zt_",
     cohort_names[current_cohort],
@@
   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-  return_df <- cleanObservationPeriod(current_cohort, clean_data)
+  return_df <- cleanObservationPeriod(
+    current_cohort, 
+    raw_df =  full_data[[cohort_names[current_cohort]]],
+    clean_data)
   unique_pairs_df <- return_df %>%
@@
 
-  # ------------- Load the saved stan result, plot the inferred parameters and save
+  # -------- Load the saved stan result, 
+  # -------- plot the inferred parameters and save
   total_event_array_lst[[current_cohort]] <- 
@@
       length(state_types) + 1):(current_cohort * length(metric_types) *
-                                  length(state_types))] <- cohort_names[current_cohort]
+                                  length(state_types))] <-
+    cohort_names[current_cohort]
   state_separation_result$metric[
@@
                                    length(metric_types) * 2)] <- "total"
+
+  ## bug below here need to find iAndSI
   state_separation_result$value[
@@
 
-  state_separation_result$state[(current_cohort * length(metric_types) * length(state_types) - length(metric_types) + 1):(current_cohort * length(metric_types) * length(state_types))] <- "social"
-  state_separation_result$value[(current_cohort * length(metric_types) * length(state_types) - length(metric_types) + 1):(current_cohort * length(metric_types) * length(state_types))] <- c(dci(matrix3), ttri(matrix3)[[2]], iAndSI(matrix3)[1])
+  state_separation_result$state[(current_cohort * length(metric_types) *
+                                   length(state_types) - 
+                                   length(metric_types) + 1):(
+                                     current_cohort * length(metric_types) *
+                                       length(state_types))] <- "social"
+  state_separation_result$value[(current_cohort * length(metric_types) *
+                                   length(state_types) -
+                                   length(metric_types) + 1):(
+                                     current_cohort * length(metric_types) *
+                                       length(state_types))] <- 
+    c(dci(matrix3), ttri(matrix3)[[2]], iAndSI(matrix3)[1])
 }
@@
 load("../output/state_separation_plot.RData")
-for (current_cohort in c(3)) {
+for (current_cohort in c(2)) {
   total_event_array <- total_event_array_lst[[current_cohort]]
@@
   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-  return_df <- cleanObservationPeriod(current_cohort, clean_data)
+  return_df <- cleanObservationPeriod(current_cohort, 
+                                      full_data[[cohort_names[current_cohort]]],
+                                      clean_data)
 
@@
   )
-
+  ### work to here
   g_community1 <- graph_from_adjacency_matrix(matrix1, mode = "undirected")

### 2021-05-26 run_scripts/sim_rank_isi.R

@@ -1,9 +1,9 @@
 ##### compare inferred rank for simulated data using i&si method
 
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 
 
-data_path <- "output/rank_sims/sims_m3_dc_isi/sparse/"
+data_path <- "output/revisions/rank_sims"
 
 
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
@@ -12,7 +12,7 @@ sim_id <- jobid
 
 library(here)
 library(tidyverse)
-library(rstan)
+library(cmdstanr)
 library(compete)
 library(PlayerRatings)
 
@@ -28,6 +28,7 @@ source(here("lib",'myGlicko.R'))
 source(here("lib",'naiveRankHierarchy.R'))
 source(here("lib",'expertRankHierarchy.R'))
 cut_off <- 3
+num_nodes <- 20
 
 model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
   return(eta1 * x * y *exp(-eta2 * abs(x - y))/(1 + exp(-eta3 * (x - y) ) ) ) })
@@ -49,62 +50,64 @@ object_fn <- list(alpha.fun = function(x, y, eta1, eta2){
   q0.fun = function(x, y, eta3){
     return(exp(- eta3 * y) )})
 
-object_par <- list(sim_lambda_0 = 0.08,
-                   sim_lambda_1 = 0.15,
-                   sim_eta_1 = 2.5,
+object_par <- list(sim_lambda_1 = 0.2,
+                   sim_eta_1 = 1.5, # this has to be < beta
+                   gamma_var = runif(n = num_nodes, min = 0.01, max = 0.05),
+                   zeta_var = runif(n = num_nodes, min = 0.01, max = 0.05),
                    sim_eta_2 = 0.6,
-                   sim_eta_3 = 5,
-                   sim_beta = 1.5,
-                   f_vec_1=c(0.1, 0.2, 0.4, 0.7, 0.9))
+                   sim_eta_3 = 3,
+                   sim_beta = 2,
+                   f_vec_1 = seq(from = 0.05, to = 0.95,
+                                 length.out = num_nodes))
 
-object_matrix <- list(lambda0_matrix = matrix(object_par$sim_lambda_0,
-                                              nrow = length(object_par$f_vec_1),
[…]

### 2021-05-27 output_scripts/revisions_may.Rmd
update sim ks stats for the cluster

@@
 ```
+
+# Repeat Rank Simulations
+
+```{r rank-with-20-nodes}
+col_df <- tibble(method = c("I&SI",
+                            "AggRank",
+                            "DSNL",
+                            "Glicko",
+                            "I-MMHP",
+                            "C-HP",
+                            "C-DCHP",
+                            "True",
+                            "C-MMHP"),
+            cols = viridis(9))
+
+sim_files <- list.files(here("output", "revisions", "rank_sims"), 
+                        pattern = "rank_sim")
+
+all_sims <- list()
+for(i in seq_along(sim_files)) {
+ single_fit <- readRDS(here("output",
+                            "revisions",
+                            "rank_sims",
+                            sim_files[i]))
+ all_sims[[i]] <- single_fit
+}
+
+spear <- function(sim_data) {
+  truth <- sim_data$truth
+  sim_data %>%
+    select(m1:glicko) %>%
+    purrr::map( ~cor.test(truth, .x,
+                   method = "spearman")$estimate  ) %>%
+    enframe() %>%
+    unnest(cols = c(value))
+}
+
+sim_data <- map_dfr(all_sims, spear)
+
+name <- sim_data$name
+
+sim_data$name <- case_when(
+          name == "isi" ~ "I&SI",
+          name == "m1" ~ "C-HP",
+          name == "m2" ~ "C-DCHP",
+          name == "m3" ~ "C-MMHP",
+          name == "agg" ~ "AggRank",
+          name == "glicko" ~ "Glicko")
+
+sim_data$name <- factor(sim_data$name, levels = c("I&SI",
+                                                  "AggRank",
+                                                  "Glicko",
+                                                  "C-HP",
+                                                  "C-DCHP",
+                                                  "C-MMHP"))
+
+plot_cols <- col_df %>% filter(method %in% levels(sim_data$name)) %>%
+  pull(cols)
+
+sim_data %>%
+  rename(Method = name, corr = value) %>%
+  ggplot(aes(Method,corr)) + 
+  geom_boxplot(aes(fill = Method), alpha = 0.7) +
+  scale_fill_manual(values = plot_cols) +
+  labs(y = "Rank Correlation") + theme_bw() +
+  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+        text = element_text(size = 20),
+        axis.text.x=element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.position="right") + ggtitle("(b)")
+
+```

### 2021-05-27 run_scripts/sim_fits.R

@@ -4,13 +4,14 @@
 #### if running on cluster ####
 source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
 
-data_path <- "output/revisions/"
+data_path <- "output/revisions/sim_m3/"
 
-library(rstan)
+library(cmdstanr)
 library(R.utils)
+library(dplyr)
 # library(compete)
 options(mc.cores = parallel::detectCores())
-rstan_options(auto_write = TRUE)
+# rstan_options(auto_write = TRUE)
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
 sim_id <- jobid
@@ -118,9 +119,9 @@ sim_model3_stan_fit1 <- list()
 sim_model3_stan_fit2 <- list()
 sim_model3_stan_fit3 <- list()
 
-model1 <- stan_model("lib/sim_model1.stan")
-model2 <- stan_model("lib/sim_model2.stan")
-model3 <- stan_model("lib/sim_model3_dc.stan")
+model1 <- cmdstan_model("lib/sim_model1.stan")
+model2 <- cmdstan_model("lib/sim_model2.stan")
+model3 <- cmdstan_model("lib/sim_model3_dc.stan")
 
 # for(i in c(1:n_sim)){
 i <- sim_id
@@ -131,61 +132,71 @@ clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data,
 # these have different stan files because they're simulation models
 
 
-data_list <- list(max_Nm=max(clean_sim_data$N_count),
+data_list <- list(max_Nm = max(clean_sim_data$N_count),
                   N_til = length(clean_sim_data$I_fit),
-                  M=sum(clean_sim_data$N_count>=cut_off),
-                  N=length(object_par$f_vec_1),
+                  M = sum(clean_sim_data$N_count>=cut_off),
+                  N = length(object_par$f_vec_1),
                   I_fit = clean_sim_data$I_fit,
                   J_fit = clean_sim_data$J_fit,
                   T = tail(clean_sim_data$day_hour,1),
-                  Nm = as.vector(clean_sim_data$N_count[clean_sim_data$N_count>=cut_off]),
+                  Nm = as.vector(clean_sim_data$N_count[clean_sim_data$N_count>=
+                                                          cut_off]),
                   event_matrix = clean_sim_data$event_matrix,
[…]

### 2021-05-27 run_scripts/sim_rank_isi.R

@@ -3,7 +3,7 @@
 source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 
 
-data_path <- "output/revisions/rank_sims"
+data_path <- "output/revisions/rank_sims/"
 
 
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")

### 2021-05-27 output_scripts/revisions_may.Rmd
trying to make circular plot

@@
 library(here)
+library(igraph)
 library(compete)
+library(circlize)
 library(colorspace)
@@
 source(paste(func_dir, "drawIntensity.R", sep = ""))
+source(paste(func_dir, "circularPlot.R", sep = ""))
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
@@
 active_event_array_lst <- list()
-for (current_cohort in c(2:10)) {
+for (current_cohort in c(1:10)) {
   print(current_cohort)
@@
                       unique_pairs_df$recipient == j)
-      if (length(pair) > 0) {
+      if (length(pair) > 0 & i!=j) {
         current_window_vec <- unique_pairs_df$observe[[pair]]
@@
     c(dci(matrix3), ttri(matrix3)[[2]], iAndSI(matrix3)[1])
+  rm(interpolation_array_list)
+  rm(state_array_list)
 }
@@
   ### Make plot for t=1
-  png(paste(plot_path, "real_clustering_1.png", sep = ""), 
-      height = 600,
-      width = 600)
+  # png(paste(plot_path, "real_clustering_1.png", sep = ""), 
+  #     height = 600,
+  #     width = 600)
   myCircularPlot(
@@
   )
-  dev.off()
+  # dev.off()
 
   ### Make plot for t=2
-  png(paste(plot_path, "real_clustering_2.png", sep = ""),
-   height = 600,
-   width = 600
- )
+ #  png(paste(plot_path, "real_clustering_2.png", sep = ""),
+ #   height = 600,
+ #   width = 600
+ # )
+ # problems with these 2, possibly if no events from 11?
+ circos.par$cell.padding <- c(0,0,0,0)
  myCircularPlot(
@@
  )
- dev.off()
+ # dev.off()
 
   ### Make plot for t=3
-  png(paste(plot_path, "real_clustering_3.png", sep = ""),
-      height = 600,
-      width = 600)
+  # png(paste(plot_path, "real_clustering_3.png", sep = ""),
+  #     height = 600,
+  #     width = 600)
   myCircularPlot(
@@
   )
-  dev.off()
+  # dev.off()
 }

### 2021-06-01 output_scripts/revisions_may.Rmd
working on plots

@@
 
-```
-
-## Run some longer/larger simulations
-
-We can replace the simulation example with 5 nodes to one with
-20 nodes.
-
-```{r simulate_20_nodes}
-num_nodes <- 20
-cut_off <- 3
-obs_time <- 200
+col_df <- tibble(method = c("I&SI",
+                            "AggRank",
+                            "DSNL",
+                            "Glicko",
+                            "I-MMHP",
+                            "C-HP",
+                            "C-DCHP",
+                            "True",
+                            "C-MMHP"),
+            cols = viridis(9))
 
@@
 )
+
+```
+
+## Run some longer/larger simulations
+
+We can replace the simulation example with 5 nodes to one with
+20 nodes.
+
+```{r simulate_20_nodes}
+num_nodes <- 20
+cut_off <- 3
+obs_time <- 200
 
@@
 
-```{r ranking_sim_data}
+```{r ranking_sim_data, include=FALSE, eval=FALSE}
 ### i&si method
@@
 
-crossing(send = f_vec, rec = f_vec) %>%
+tidyr::crossing(send = f_vec, rec = f_vec) %>%
   filter(send != rec) %>%
@@
   ## rename the f cols first
-  rename_with(~gsub("[", "_", .x, fixed = TRUE)) %>% 
+  rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
   rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
@@
 # post_rank$node <- as.factor(post_rank$node)
-true_rank <- tibble(names = paste0("f_", 1:20),
-                    f_vec_1 = seq(from = 0.05,
+true_rank <- tibble(names = paste0("", 1:20),
+                    f_vec = seq(from = 0.05,
                                   to = 0.95,
-                                  length.out = 20))
-
-post_rank$node <- factor(post_rank$node, levels = paste0("f_", 1:20))
+                                  length.out = 20),
+                    value = "True Value")
+
+post_rank$node <- factor(post_rank$node, levels = paste0("", 1:20))
 
@@
   geom_point(data = true_rank,
-             mapping = aes(names, f_vec_1, shape = 16),
-             colour = "red") +
-  geom_point(data = post_mean,
-             mapping = aes(node, ave_rank, shape = 16),
-             colour = "blue") +
-  scale_shape_identity() +
+             mapping = aes(names, f_vec, colour = value)) +
+  # geom_point(data = post_mean,
+  #            mapping = aes(node, ave_rank, shape = 16),
+  #            colour = "blue") +
+  # scale_shape_identity() +
   labs(title = "Inferred Latent Ranking with Truth",
        x = "Node", y = "Latent Ranking",
-       colour = "Summary")
+       colour = "Summary") +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom")
 ## blue is posterior mean, red is true value
@@
 
-```{r construct_plot}
+```{r construct_plot, include=FALSE, eval=FALSE}
 iAndSI <- function(M) {
@@
 
-```{r recreate_jing_figure}
+```{r recreate_jing_figure, message=FALSE}
 load("../output/state_separation_plot.RData")
-for (current_cohort in c(2)) {
+# for (current_cohort in c(1)) {
+  current_cohort <- 9
   total_event_array <- total_event_array_lst[[current_cohort]]
@@
     cur.matrix = matrix1,
-    cur.order = c(1, 4, 10, 5, 11, 6, 7, 2, 8, 12, 9, 3),
+    ## is the ordering here for the nodes? need to make sure I get this right
+    ## working off this being the ordering from the clustering above
+    # cur.order = c(1, 4, 10, 5, 11, 6, 7, 2, 8, 12, 9, 3),
+    cur.order = order(lec1$membership),
     cur.color = c(
@@
         name = "YlOrBr",
-        n =
-          8
-      ))(14)[c(
-        13,
-        9,
-        5
-      )],
+        n = 8))(14)[c(13, 11, 9, 7)],
       colorRampPalette(brewer.pal(
         name = "PuRd",
-        n =
-          8
-      ))(15)[c(
-        4,
-        6,
-        8,
-        10,
-        12,
-        14
-      )],
+        n = 8))(13)[c(4, 6, 8, 10, 12)],
       colorRampPalette(brewer.pal(
         name = "Blues",
-        n =
-          8
-      ))(10)[c(
-        5,
-        7,
-        9
-      )]
-    ),
-    cur.gap = c(rep(5, 2), 30, rep(5, 5), 30, rep(5, 2), 30)
+        n = 8))(15)[c(4, 8, 12)]
+    ),
+    cur.gap = c(rep(5, 3), 30, rep(5, 4), 30, rep(5, 2), 30)
   )
@@
  myCircularPlot(
-   cur.matrix = matrix2,
-   cur.order = c(1, 7, 8, 2, 3, 4, 5, 9, 10, 6, 11, 12),
+   cur.matrix = matrix2[-11,-11],
+   cur.order = order(lec2$membership)[-6],
    cur.color = c(
@@
        name = "YlOrBr",
-       n = 8))(14)[c(13, 11, 9, 7, 5, 3)],
+       n = 8))(16)[c(15, 13, 11, 9, 7, 5)],
      colorRampPalette(brewer.pal(
        name = "Blues",
-       n = 8))(15)[c(4, 6, 8, 10, 12, 14)]
-   ),
-   cur.gap = c(rep(5, 5), 30, rep(5, 5), 30)
+       n = 8))(15)[c(6, 8, 10, 12, 14)]
+   ),
+   cur.gap = c(rep(5, 5), 30, rep(5, 4), 30),
+   cur.ID = c(1:12)[-11]
  )
@@
   myCircularPlot(
-    cur.matrix = matrix3[-3, -3],
-    cur.order = c(1, 10, 5, 2, 3, 6, 7, 8, 4, 11, 9),
+    cur.matrix = matrix3[-11, -11],
+    cur.order = order(lec3$membership)[-4],
     cur.color = c(
@@
         name = "Blues",
-        n = 8))(16)[c(7, 9, 11, 13, 15)],
+        n = 8))(16)[c(9, 11, 13, 15)],
       colorRampPalette(brewer.pal(
         name = "PuRd",
-        n = 8))(15)[c(8, 12)]
-    ),
-    cur.gap = c(rep(5, 3), 30, rep(5, 4), 30, rep(5, 1), 30),
-    cur.ID = c(1:12)[-3]
+        n = 8))(15)[c(4, 8, 12)]
+    ),
+    cur.gap = c(rep(5, 3), 30, rep(5, 3), 30, rep(5, 2), 30),
+    cur.ID = c(1:12)[-11]
   )
   # dev.off()
-}
+# }
 ```
@@
 ```{r rank-with-20-nodes}
-col_df <- tibble(method = c("I&SI",
-                            "AggRank",
-                            "DSNL",
-                            "Glicko",
-                            "I-MMHP",
-                            "C-HP",
-                            "C-DCHP",
-                            "True",
-                            "C-MMHP"),
-            cols = viridis(9))
-
 sim_files <- list.files(here("output", "revisions", "rank_sims"), 
@@
 ```
+
+# Improve Fig 4b
+
+Trying to write a better version of Figure 4b using these new larger
+simulated networks.
+
+```{r process-new-4b}
+plot.s <- 1 # 7 is pretty good
+plot.i <- 20
+plot.j <- 15
+
+cur_i <- plot.i
+cur_j <- plot.j
+
+load(paste0(here("output", "revisions", "sim_m3"),
+  "/", "sim_model3_fit123_",
+  plot.s,
+  ".RData"
+))
+
+test.mmhp <- sim_model3_data$mmhp_matrix[plot.i, plot.j][[1]]
+temp.t <- test.mmhp$tau
+current.n <- length(temp.t) - 1
+time.segment <- seq(0, tail(temp.t, 1), length.out = 5000)
+
+### Preprocess the model inference result
+## model 1
+#########
+
+## get f from cmdstan
+
+f_draws <- sim_model3_stan_sim1 %>% 
+  select(starts_with("f"))
+
+model1_par_est <- list(
+  lambda0 = mean(sim_model3_stan_sim1$lambda0),
+  eta_1 =
+    mean(sim_model3_stan_sim1$eta_1),
+  eta_2 =
+    mean(sim_model3_stan_sim1$eta_2),
+  eta_3 =
+    mean(sim_model3_stan_sim1$eta_3),
+  beta = mean(sim_model3_stan_sim1$beta),
+  f = apply(f_draws, 2, mean)
+)
+lambda.m1 <- uniHawkesIntensityNumeric(
+  object = list(
+    lambda0 =
+      model1_par_est$lambda0,
+    alpha =
+      model1_fn$alpha.fun(
+        model1_par_est$f[plot.i],
+        model1_par_est$f[plot.j],
+        model1_par_est$eta_1,
+        model1_par_est$eta_2,
+        model1_par_est$eta_3
+      ),
+    beta = model1_par_est$beta
+  ),
+  events = temp.t,
+  time.vec = time.segment
+)
+
+## model2
+#############
+gamma_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("gamma"))
+
+zeta_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("zeta"))
+
+f_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("f"))
+
+model2_par_est <- list(
+  gamma = apply(gamma_draws, 2, mean),
+  zeta = apply(zeta_draws, 2, mean),
+  eta_1 = mean(sim_model3_stan_sim2$eta_1),
+  eta_2 = mean(sim_model3_stan_sim2$eta_2),
+  eta_3 = mean(sim_model3_stan_sim2$eta_3),
+  beta = mean(sim_model3_stan_sim2$beta),
+  f = apply(f_draws, 2, mean)
+)
+
+lambda.m2 <- uniHawkesIntensityNumeric(
+  object = list(
+    lambda0 = model2_par_est$gamma[plot.i] +
+      model2_par_est$zeta[plot.j],
+    alpha = model1_fn$alpha.fun(
+      model2_par_est$f[plot.i],
+      model2_par_est$f[plot.j],
+      model2_par_est$eta_1,
+      model2_par_est$eta_2,
+      model2_par_est$eta_3
+    ),
+    beta = model2_par_est$beta
+  ),
+  events = temp.t,
+  time.vec = time.segment
+)
+
+## Model3
+###
+
+lam0_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("gamma"))
+
+lam1_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("zeta"))
+
+gamma_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("gamma"))
+
+zeta_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("zeta"))
+
+f_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("f"))
+
+lam0_vec <- apply(lam0_draws, 2, mean)
+lam1_vec <- apply(lam1_draws, 2, mean)
+lam0_par_est <- matrix(0,
+  nrow = length(object_par$f_vec_1),
+  ncol = length(object_par$f_vec_1)
+)
+lam1_par_est <- matrix(0,
+  nrow = length(object_par$f_vec_1),
+  ncol = length(object_par$f_vec_1)
+)
+
+clean_sim_data <- cleanSimulationData(
+  raw_data = sim_model3_data,
+  cut_off = cut_off,
+  N = length(object_par$f_vec_1)
+)
+
+for (i in seq_along(lam0_vec)) {
+  row_id <- clean_sim_data$I_fit[i]
+  col_id <- clean_sim_data$J_fit[i]
+  lam0_par_est[row_id, col_id] <- lam0_vec[i]
+  lam1_par_est[row_id, col_id] <- lam1_vec[i]
+}
+
+###
+
+#############
+mmhp_par_est <- list(
+  lambda0 = lam0_par_est,
+  lambda1 = lam1_par_est,
+  eta_1 = mean(sim_model3_stan_sim3$eta_1),
+  eta_2 = mean(sim_model3_stan_sim3$eta_2),
+  eta_3 = mean(sim_model3_stan_sim3$eta_3),
+  beta = mean(sim_model3_stan_sim3$beta),
+  f = apply(f_draws, 2, mean)
+)
+
+object_hat <- list(
+  lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
+  lambda1 = mmhp_par_est$lambda1[cur_i, cur_j],
+  alpha = model3_fn$alpha.fun(
+    mmhp_par_est$f[cur_i],
+    mmhp_par_est$f[cur_j],
+    mmhp_par_est$eta_1,
+    mmhp_par_est$eta_2
+  ),
+  beta = mmhp_par_est$beta,
+  q1 = model3_fn$q1.fun(
+    mmhp_par_est$f[cur_i],
+    mmhp_par_est$f[cur_j],
+    mmhp_par_est$eta_3
+  ),
+  q2 = model3_fn$q0.fun(
+    mmhp_par_est$f[cur_i],
+    mmhp_par_est$f[cur_j],
+    mmhp_par_est$eta_3
+  )
+)
+
+## then need to load in the state estimate here
+load(paste0(here("output", "revisions", "sim_m3"),
+  "/", "fit123_state_est_",
+  plot.s,
+  ".RData"
+))
+
+state.est.latent.mmhp <- interpolate_state_est_lst[plot.i, plot.j][[1]]
+state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
+  termination = 200
+)
+
+step.fun.est <- stepfun(
+  state.est.latent.mmhp$x.hat,
+  2 - state.est.latent.mmhp$z.hat
+)
+
+lambda.m3 <- mmhpIntensityNumeric(
+  params = object_hat,
+  t = temp.t[-1],
+  time.vec = time.segment,
+  latent.vec = step.fun.est(time.segment)
+)
+
+object_true <- lapply(object_matrix, function(x) x[plot.i, plot.j])
+names(object_true) <- c("lambda0", "lambda1", "alpha", "beta", "q1", "q2")
+
+lambda.true <- mmhpTrueIntensityNumeric(
+  params = object_true,
+  t = temp.t,
+  latent = list(
+    x = fixStateTransition(test.mmhp)$x,
+    z = fixStateTransition(test.mmhp)$z
+  ),
+  time.vec = time.segment
+)
+
+```
+
+```{r fig4b-redone}
+y.ub <- c(35,35,35)#c(130,72,31)
+x_events <- 190#135#150
+layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
+my.xlim <- 200#160#200#130
+my.long.x <- 205#205#134.5
+legend.x <- c(60,60,60)#c(135,135,135)
+legend.y <- #c(34,32,32)
+legend.y <- c(23,23,23)#c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.cex <- 1.5 #3
+line.alpha <- c(0.9,0.6)
+line.wdth <- c(2,2.5)
+negative.col <- add.alpha('lightskyblue')
+positive.col <- add.alpha('tomato')
+#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
+#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
+par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
+    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)
+
+model_colors <- col_df %>% filter(method %in% c("C-HP",
+                                                "C-DCHP",
+                                                "C-MMHP"))
+
+model_colors <- model_colors %>% pull(cols)
+
+# model1
+############
+true.object <- object_true
+
+drawUniMMHPIntensityPaper(true.object,
+                          simulation = fixStateTransition(test.mmhp),
+                          yupper=y.ub[1], 
+                          color=add.alpha("black", alpha=line.alpha[1]),
+                          line.width=line.wdth[1],
+                          y.ratio=-0.05, min.y=-2,
+                          min.x=0, max.x=my.xlim,
+                          title_name=paste(plot.i,"->",plot.j),
+                          title.cex = 2,
+                          box.type="n")
+drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
+                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
+                                                   model1_par_est$f[plot.j],
+                                                   model1_par_est$eta_1,
+                                                   model1_par_est$eta_2,
+                                                   model1_par_est$eta_3),
+                         beta=model1_par_est$beta,
+                         events=test.mmhp$tau,
+                         color=add.alpha(model_colors[1],
+                                         alpha=line.alpha[2]),
+                         line.width=line.wdth[2])
+
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+
+## add legend
+# changed 34 to 23, 25 to 18, -20 to -10
+# legend(10,legend.y[1],c("State 1/0 events","State change point"),
+#        col = c(NA,"red"),
+#        y.intersp=0.85,x.intersp=-0.1, bty = "n",
+#        pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
+#        lty = c(NA,NA), lwd=c(NA,4))
+# points(29,84,pch=1,cex=2,col="blue")
+# points(26,84,pch=16,cex=2,col="blue")
+legend(legend.x[1],legend.y[1],c("True"),
+       col = c("black"),
+       y.intersp=0.88,x.intersp=0.15,bty = "n",
+       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
+legend(legend.x[1]+22,legend.y[1],c("C-HP"),
+       col = c(model_colors[1]),
+       y.intersp=0.88,x.intersp=0.15,bty = "n",
+       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
+
+## delta lambda
+par(mar = c(0,0.3,0,0.1))
+plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,4), type="n",
+     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
+delta.positive <- delta.lambda
+delta.positive[delta.positive<0] <- 0
+delta.negative <- delta.lambda
+delta.negative[delta.negative>0] <- 0
+### hiding these for now ###
+polygon(c(0,lambda.true$time.vec,x_events),#200
+        c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events),#200
+        c(0,delta.positive,0),col=positive.col,border=NA)
+
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+# model2
+############
+drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
+                          yupper=y.ub[2], 
+                          color=add.alpha("black", alpha=line.alpha[1]),
+                          line.width=line.wdth[1],
+                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
+                          box.type="n")
+drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
+                           model2_par_est$zeta[plot.j],
+                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+                                                   model2_par_est$f[plot.j],
+                                                   model2_par_est$eta_1,
+                                                   model2_par_est$eta_2,
+                                                   model2_par_est$eta_3),
+                         beta=model2_par_est$beta,
+                         events=test.mmhp$tau,
+                         color=add.alpha(model_colors[2],
+                                         alpha=line.alpha[2]),
+                         line.width=line.wdth[2])
+legend(legend.x[2],legend.y[2],"C-DCHP",
+       col = model_colors[2],
+       y.intersp=0.88,x.intersp=0.1,bty = "n",
+       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)
+
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+
+legend(legend.x[2]-50,
+       legend.y[2]+2,c("State 0/1 events","State change point"),
+       col = c(NA,"red"),
+       y.intersp=0.85,x.intersp=-0.5, bty = "n",
+       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
+       lty = c(NA,NA), lwd=c(NA,2))
+points(legend.x[2]-46,legend.y[2] - 4.5, pch = 1, cex = 2, col = "blue")
+points(legend.x[2]-44,legend.y[2] - 4.5, pch = 16, cex = 2, col = "blue")
+
+## delta lambda
+par(mar = c(0,0.3,0,0.1))
+delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
+
+plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), 
+     ylim=c(-4,4), type="n",
+     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
+delta.positive <- delta.lambda
+delta.positive[delta.positive<0] <- 0
+delta.negative <- delta.lambda
+delta.negative[delta.negative>0] <- 0
+polygon(c(0,lambda.true$time.vec,x_events), #200
+        c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events), #200
+        c(0,delta.positive,0),col=positive.col,border=NA)
+# segments(0,0,my.xlim,0,col="gray45")
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+# model3
+########
+par(mar = c(0,0.3,1,0.1))
+drawUniMMHPIntensityPaper(true.object,
+                          simulation=fixStateTransition(test.mmhp),
+                          yupper=y.ub[3],
+                          color=add.alpha("black", alpha=line.alpha[1]),
+                          line.width=line.wdth[1],
+                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
+                          box.type="n")
+drawUniMMHPIntensityPaper(object_hat,
+                          simulation = list(
+                            x=state.est.latent.mmhp.new$x.hat,                                          
+                            z=state.est.latent.mmhp.new$z.hat,
+                            tau=test.mmhp$tau,zt=test.mmhp$zt,
+                            lambda.max=test.mmhp$lambda.max),
+                          yupper=y.ub,add=TRUE,
+                          color=add.alpha(model_colors[3],
+                                          alpha=line.alpha[2]),
+                          line.width=line.wdth[2])
+legend(legend.x[3],legend.y[3],"C-MMHP",
+       col = model_colors[3],
+       y.intersp=0.6,x.intersp=0.1,bty = "n",
+       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+
+legend(legend.x[3]-50,legend.y[3]+2, c("Overestimation","Underestimation"),
+       col = c(positive.col,negative.col),
+       y.intersp=0.75,x.intersp=0.5,bty = "n",
+       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)
+
+## delta lambda
+par(mar = c(0,0.3,0,0.1))
+plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,4), type="n",
+     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+delta.lambda <- lambda.m3-lambda.true$lambda.t
+delta.positive <- delta.lambda
+delta.positive[delta.positive<0] <- 0
+delta.negative <- delta.lambda
+delta.negative[delta.negative>0] <- 0
+### hiding these for now
+polygon(c(0,lambda.true$time.vec,x_events), # 200 
+        c(0,delta.negative,0),col=negative.col,border=NA)
+polygon(c(0,lambda.true$time.vec,x_events), # 200 
+        c(0,delta.positive,0),col=positive.col,border=NA)
+# segments(0,0,my.xlim,0,col="gray45")
+## draw box
+axis(1,at=c(-2,my.long.x),col="gray35",
+     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+
+## top
+mtext(text="(b)",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
+## bottom
+mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.25)
+## left
+mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.25)
+
+### just need to adjust the scales really!
+
+```

### 2021-06-07 output_scripts/Paper_Plots.Rmd
update overall predict to also save the median mae for all cohorts for second plot (fig7a in paper)
also tidying up and renaming some old stan files which aren't used to avoid any possible confusion

@@
 
-<!-- The remaining plot code seems to mostly be in `PaperPlots.R`. -->
-
 # Figure 8
 
-## Figure 8a: Frobenius norm of interaction predictions, single cohort
+## Figure 8a: MAE of interaction predictions, single cohort
 
@@
 
-```{r fig-pred-cohort-slides, include=slides_plots,eval=slides_plots, fig.height=3}
+## Figure 8b: Same plot aggregated for all cohorts
+
+```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4.5, eval=FALSE}
+### updated to mae
+
 load("../output/plot_N_predict.RData")
-# current_cohort <- 5# cohort 1 looks worse than rest
-# 3 looks nice
-
-temp_plot_df <- predict_day_mae_df_lst[[current_cohort]]
-temp_plot_df$method <- factor(temp_plot_df$method,
-                              levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
-temp_plot_df$day <- factor(temp_plot_df$day)
-#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
-# width=600,height=300)
-p3_slides <- temp_plot_df %>%
-  filter(method != "I-MMHP") %>%
-  rowwise() %>%
-  #mutate(norm = min(norm,100)) %>%
-  ggplot( aes(x = method, y = mae, fill = method)) +
-  geom_boxplot(alpha=0.7) +
-  scale_fill_manual(values = plot_cols_pred) +
-  #ggtitle("(a)") +
-  theme_bw() +
-  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
-        text = element_text(size = 20),
-        axis.text.x=element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.position="right") +
-  facet_grid(cols=vars(day)) +
-  xlab("Prediction horizon (day)") + 
-  ylab("Frobenius norm of error") +
-  ylim(0, 10) +
-  NULL
-p3_slides
-```
-
-## Figure 8b: Same plot aggregated for all cohorts
-
-```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4.5, eval=FALSE}
-load("../output/plot_N_predict.RData")
-temp_plot_df <- all_cohort_norm_df %>% 
+temp_plot_df <- all_cohort_mae_df %>% 
   group_by(day, method) %>% 
-  summarise(avg=mean(norm), n= n(), sd=sd(norm))
+  summarise(avg = mean(norm), n = n(), sd = sd(norm))
 
@@
      file = paste(data_path,cohort_names[current_cohort],
-                  "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
+                  "/dsnl_state_separation_stan_result_",
+                  cohort_names[current_cohort],
                   ".RData",sep=''))
@@
 ```{r fig-10b-rank-correlation}
-par(mar=c(3,5,3,1))
+par(mar=c(3, 5, 3, 1))
 cx <- 1.75  # cex for axis label text; 

### 2021-06-07 output_scripts/revisions_may.Rmd
update overall predict to also save the median mae for all cohorts for second plot (fig7a in paper)
also tidying up and renaming some old stan files which aren't used to avoid any possible confusion

@@
 
+```{r get-days-above-plot}
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(
+  current_cohort, 
+  raw_df =  full_data[[cohort_names[current_cohort]]],
+  clean_data)
+unique_pairs_df <- return_df %>%
+  group_by(initiator, recipient) %>%
+  dplyr::summarize(
+    count = n(),
+    observe = list(observe.id),
+    observe.length = list(observe.time),
+    no.events = list(no.events)
+  )
+unique_observe_days <- unique(return_df[, 
+                                       c("observe.id", "observe.time", "day")])
+
+unique_observe_days %>% 
+  filter(observe.id %in% start_win)
+
+unique_observe_days %>% 
+  filter(observe.id %in% end_win)
+
+```
+
 # Repeat Rank Simulations
@@
 ```{r fig4b-redone}
-y.ub <- c(35,35,35)#c(130,72,31)
-x_events <- 190#135#150
-layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
-my.xlim <- 200#160#200#130
-my.long.x <- 205#205#134.5
-legend.x <- c(60,60,60)#c(135,135,135)
-legend.y <- #c(34,32,32)
-legend.y <- c(23,23,23)#c(15,12,15)#c(62,37,18)#c(22,22,22)
-legend.cex <- 1.5 #3
-line.alpha <- c(0.9,0.6)
-line.wdth <- c(2,2.5)
-negative.col <- add.alpha('lightskyblue')
-positive.col <- add.alpha('tomato')
-#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
-#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
-par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
-    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)
-
-model_colors <- col_df %>% filter(method %in% c("C-HP",
+y.ub <- c(4, 5, 3) # c(130,72,31)
+x_events <- 190 # 135#150
+layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 2.5), 3))
+my.xlim <- 200 # 160#200#130
+my.long.x <- 205 # 205#134.5
+legend.x <- c(60, 60, 60) # c(135,135,135)
+legend.y <- # c(34,32,32)
+legend.y <- c(2, 2, 2) # c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.cex <- 1.5 # 3
+line.alpha <- c(0.9, 0.6)
+line.wdth <- c(2, 2.5)
+negative.col <- add.alpha("lightskyblue")
+positive.col <- add.alpha("tomato")
+
+par(
+  mar = c(0, 0.3, 0, 0.1), oma = c(0, 3.5, 4, 0),
+  tcl = 0.2, mgp = c(0.5, 0, 0), xpd = TRUE
+)
+
+model_colors <- col_df %>% filter(method %in% c(
+  "C-HP",
   "C-DCHP",
-                                                "C-MMHP"))
+  "C-MMHP"
+))
 
@@
   simulation = fixStateTransition(test.mmhp),
-                          yupper=y.ub[1], 
-                          color=add.alpha("black", alpha=line.alpha[1]),
-                          line.width=line.wdth[1],
-                          y.ratio=-0.05, min.y=-2,
-                          min.x=0, max.x=my.xlim,
-                          title_name=paste(plot.i,"->",plot.j),
+  yupper = y.ub[1],
+  color = add.alpha("black", alpha = line.alpha[1]),
+  line.width = line.wdth[1],
+  y.ratio = -0.05, min.y = -0.5,
+  min.x = 0, max.x = my.xlim,
+  title_name = paste(plot.i, "->", plot.j),
   title.cex = 2,
-                          box.type="n")
-drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
-                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
+  box.type = "n"
+)
+drawHawkesIntensityPaper(
+  lambda0 = model1_par_est$lambda0,
+  alpha = model1_fn$alpha.fun(
+    model1_par_est$f[plot.i],
     model1_par_est$f[plot.j],
@@
     model1_par_est$eta_2,
-                                                   model1_par_est$eta_3),
-                         beta=model1_par_est$beta,
-                         events=test.mmhp$tau,
-                         color=add.alpha(model_colors[1],
-                                         alpha=line.alpha[2]),
-                         line.width=line.wdth[2])
-
-## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+    model1_par_est$eta_3
+  ),
+  beta = model1_par_est$beta,
+  events = test.mmhp$tau,
+  color = add.alpha(model_colors[1],
+    alpha = line.alpha[2]
+  ),
+  line.width = line.wdth[2]
+)
+
+# draw box
+axis(1,
+  at = c(-2, my.long.x),
+  col = "gray35",
+  line = 0.5,
+  tick = T,
+  labels = rep("", 2),
+  lwd = 0.5,
+  lwd.ticks = 0,
+  lty = 3
+)
 
@@
 # points(26,84,pch=16,cex=2,col="blue")
-legend(legend.x[1],legend.y[1],c("True"),
-       col = c("black"),
-       y.intersp=0.88,x.intersp=0.15,bty = "n",
-       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
-legend(legend.x[1]+22,legend.y[1],c("C-HP"),
-       col = c(model_colors[1]),
-       y.intersp=0.88,x.intersp=0.15,bty = "n",
-       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
+
+#### more legend
+# legend(legend.x[1], legend.y[1], c("True"),
+#   col = c("black"),
+#   y.intersp = 0.88, x.intersp = 0.15, bty = "n",
+#   lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
+# )
+# legend(legend.x[1] + 22, legend.y[1], c("C-HP"),
+#   col = c(model_colors[1]),
+#   y.intersp = 0.88, x.intersp = 0.15, bty = "n",
+#   lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
+# )
 
 ## delta lambda
-par(mar = c(0,0.3,0,0.1))
-plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,4), type="n",
-     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
-delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
+par(mar = c(0, 0.3, 0, 0.1))
+plot(0, 0,
+  xlim = c(0, my.xlim), 
+  ylim = c(-1, 1),
+  type = "n",
+  bty = "n",
+  xlab = "",
+  ylab = "",
+  xaxt = "n",
+  yaxt = "n",
+  axes = FALSE
+)
+delta.lambda <- lambda.m1$lambda.t - lambda.true$lambda.t
 delta.positive <- delta.lambda
-delta.positive[delta.positive<0] <- 0
+delta.positive[delta.positive < 0] <- 0
 delta.negative <- delta.lambda
-delta.negative[delta.negative>0] <- 0
+delta.negative[delta.negative > 0] <- 0
 ### hiding these for now ###
-polygon(c(0,lambda.true$time.vec,x_events),#200
-        c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,x_events),#200
-        c(0,delta.positive,0),col=positive.col,border=NA)
-
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.negative, 0),
+  col = negative.col, border = NA
+)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.positive, 0),
+  col = positive.col, border = NA
+)
+
+axis(1,
+  at = c(-1, my.long.x), 
+  col = "gray35",
+  line = 0, tick = T, 
+  labels = rep("", 2),
+  lwd = 0.7,
+  lwd.ticks = 0
+)
 
@@
 ############
-drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
-                          yupper=y.ub[2], 
-                          color=add.alpha("black", alpha=line.alpha[1]),
-                          line.width=line.wdth[1],
-                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
-                          box.type="n")
-drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
+drawUniMMHPIntensityPaper(true.object,
+  simulation = fixStateTransition(test.mmhp),
+  yupper = y.ub[2],
+  color = add.alpha("black", alpha = line.alpha[1]),
+  line.width = line.wdth[1],
+  y.ratio = -0.05,
+  min.y = -0.5,
+  min.x = 0,
+  max.x = my.xlim,
+  box.type = "n"
+)
+drawHawkesIntensityPaper(
+  lambda0 = model2_par_est$gamma[plot.i] +
     model2_par_est$zeta[plot.j],
-                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+  alpha = model1_fn$alpha.fun(
+    model2_par_est$f[plot.i],
     model2_par_est$f[plot.j],
@@
     model2_par_est$eta_2,
-                                                   model2_par_est$eta_3),
-                         beta=model2_par_est$beta,
-                         events=test.mmhp$tau,
-                         color=add.alpha(model_colors[2],
-                                         alpha=line.alpha[2]),
-                         line.width=line.wdth[2])
-legend(legend.x[2],legend.y[2],"C-DCHP",
-       col = model_colors[2],
-       y.intersp=0.88,x.intersp=0.1,bty = "n",
-       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)
-
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
-
-legend(legend.x[2]-50,
-       legend.y[2]+2,c("State 0/1 events","State change point"),
-       col = c(NA,"red"),
-       y.intersp=0.85,x.intersp=-0.5, bty = "n",
-       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
-       lty = c(NA,NA), lwd=c(NA,2))
-points(legend.x[2]-46,legend.y[2] - 4.5, pch = 1, cex = 2, col = "blue")
-points(legend.x[2]-44,legend.y[2] - 4.5, pch = 16, cex = 2, col = "blue")
+    model2_par_est$eta_3
+  ),
+  beta = model2_par_est$beta,
+  events = test.mmhp$tau,
+  color = add.alpha(model_colors[2],
+    alpha = line.alpha[2]
+  ),
+  line.width = line.wdth[2]
+)
+
+### used legend
+# legend(legend.x[2], legend.y[2], "C-DCHP",
+#   col = model_colors[2],
+#   y.intersp = 0.88,
+#   x.intersp = 0.1,
+#   bty = "n",
+#   lty = 1,
+#   lwd = 5,
+#   cex = legend.cex,
+#   seg.len = 1
+# )
+
+axis(1,
+  at = c(-2, my.long.x),
+  col = "gray35",
+  line = 0.5,
+  tick = T,
+  labels = rep("", 2),
+  lwd = 0.5,
+  lwd.ticks = 0,
+  lty = 3
+)
+
+## location of legend
+# legend(legend.x[2] - 50,
+#   legend.y[2] + 1, c("State 0/1 events", "State change point"),
+#   col = c(NA, "red"),
+#   y.intersp = 0.85, x.intersp = -0.5, bty = "n",
+#   pch = c(NA, 4), pt.cex = c(NA, 2), cex = legend.cex,
+#   lty = c(NA, NA), lwd = c(NA, 2)
+# )
+# points(legend.x[2] - 46, legend.y[2] - .5, pch = 1, cex = 2, col = "blue")
+# points(legend.x[2] - 44, legend.y[2] - .5, pch = 16, cex = 2, col = "blue")
 
 ## delta lambda
-par(mar = c(0,0.3,0,0.1))
-delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
-
-plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), 
-     ylim=c(-4,4), type="n",
-     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
-delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
+par(mar = c(0, 0.3, 0, 0.1))
+delta.lambda <- lambda.m2$lambda.t - lambda.true$lambda.t
+
+plot(lambda.true$time.vec, delta.lambda,
+  xlim = c(0, my.xlim),
+  ylim = c(-1, 1.5), type = "n",
+  bty = "n",
+  xlab = "",
+  ylab = "",
+  xaxt = "n",
+  yaxt = "n",
+  axes = FALSE
+)
+delta.lambda <- lambda.m2$lambda.t - lambda.true$lambda.t
 delta.positive <- delta.lambda
-delta.positive[delta.positive<0] <- 0
+delta.positive[delta.positive < 0] <- 0
 delta.negative <- delta.lambda
-delta.negative[delta.negative>0] <- 0
-polygon(c(0,lambda.true$time.vec,x_events), #200
-        c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,x_events), #200
-        c(0,delta.positive,0),col=positive.col,border=NA)
+delta.negative[delta.negative > 0] <- 0
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.negative, 0),
+  col = negative.col, border = NA
+)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.positive, 0),
+  col = positive.col, border = NA
+)
 # segments(0,0,my.xlim,0,col="gray45")
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+axis(1,
+  at = c(-2, my.long.x), col = "gray35",
+  line = 0, tick = T, labels = rep("", 2), lwd = 0.7, lwd.ticks = 0
+)
 
@@
 ########
-par(mar = c(0,0.3,1,0.1))
+par(mar = c(0, 0.3, 1, 0.1))
 drawUniMMHPIntensityPaper(true.object,
-                          simulation=fixStateTransition(test.mmhp),
-                          yupper=y.ub[3],
-                          color=add.alpha("black", alpha=line.alpha[1]),
-                          line.width=line.wdth[1],
-                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
-                          box.type="n")
+  simulation = fixStateTransition(test.mmhp),
+  yupper = y.ub[3],
+  color = add.alpha("black", alpha = line.alpha[1]),
+  line.width = line.wdth[1],
+  y.ratio = -0.05, min.y = -0.5, min.x = 0, max.x = my.xlim,
+  box.type = "n"
+)
 drawUniMMHPIntensityPaper(object_hat,
   simulation = list(
-                            x=state.est.latent.mmhp.new$x.hat,                                          
-                            z=state.est.latent.mmhp.new$z.hat,
-                            tau=test.mmhp$tau,zt=test.mmhp$zt,
-                            lambda.max=test.mmhp$lambda.max),
-                          yupper=y.ub,add=TRUE,
-                          color=add.alpha(model_colors[3],
-                                          alpha=line.alpha[2]),
-                          line.width=line.wdth[2])
-legend(legend.x[3],legend.y[3],"C-MMHP",
-       col = model_colors[3],
-       y.intersp=0.6,x.intersp=0.1,bty = "n",
-       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
+    x = state.est.latent.mmhp.new$x.hat,
+    z = state.est.latent.mmhp.new$z.hat,
+    tau = test.mmhp$tau, zt = test.mmhp$zt,
+    lambda.max = test.mmhp$lambda.max
+  ),
+  yupper = y.ub, add = TRUE,
+  color = add.alpha(model_colors[3],
+    alpha = line.alpha[2]
+  ),
+  line.width = line.wdth[2]
+)
+# legend(legend.x[3], legend.y[3], "C-MMHP",
+#   col = model_colors[3],
+#   y.intersp = 0.6,
+#   x.intersp = 0.1,
+#   bty = "n",
+#   lty = 1,
+#   lwd = 5,
+#   cex = legend.cex,
+#   seg.len = 1
+# )
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
-
-legend(legend.x[3]-50,legend.y[3]+2, c("Overestimation","Underestimation"),
-       col = c(positive.col,negative.col),
-       y.intersp=0.75,x.intersp=0.5,bty = "n",
-       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)
+axis(1,
+  at = c(-2, my.long.x),
+  col = "gray35",
+  line = 0.5,
+  tick = T,
+  labels = rep("", 2), 
+  lwd = 0.5,
+  lwd.ticks = 0, lty = 3
+)
+
+# legend(legend.x[3] - 50, legend.y[3] + 2,
+#        c("Overestimation", "Underestimation"),
+#   col = c(positive.col, negative.col),
+#   y.intersp = 0.75, x.intersp = 0.5, bty = "n",
+#   lty = c(1, 1), lwd = c(10, 10), cex = legend.cex, seg.len = 0.8
+# )
 
 ## delta lambda
-par(mar = c(0,0.3,0,0.1))
-plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,4), type="n",
-     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
-delta.lambda <- lambda.m3-lambda.true$lambda.t
+par(mar = c(0, 0.3, 0, 0.1))
+plot(0, 0,
+  xlim = c(0, my.xlim), ylim = c(-1, 1.5), type = "n",
+  bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
+)
+delta.lambda <- lambda.m3 - lambda.true$lambda.t
 delta.positive <- delta.lambda
-delta.positive[delta.positive<0] <- 0
+delta.positive[delta.positive < 0] <- 0
 delta.negative <- delta.lambda
-delta.negative[delta.negative>0] <- 0
+delta.negative[delta.negative > 0] <- 0
 ### hiding these for now
-polygon(c(0,lambda.true$time.vec,x_events), # 200 
-        c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,x_events), # 200 
-        c(0,delta.positive,0),col=positive.col,border=NA)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.negative, 0),
+  col = negative.col, border = NA
+)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.positive, 0),
+  col = positive.col, border = NA
+)
 # segments(0,0,my.xlim,0,col="gray45")
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
-
-## top
-mtext(text="(b)",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
-## bottom
-mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.25)
-## left
-mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.25)
-
-### just need to adjust the scales really!
+axis(1,
+  at = c(-2, my.long.x), col = "gray35",
+  line = 0, tick = T, labels = rep("", 2), lwd = 0.7, lwd.ticks = 0
+)
+
+# ## top
+# mtext(text = "(b)", side = 3, line = 0.8, outer = TRUE, cex = 2.5, font = 2)
+# ## bottom
+# mtext(text = "Time", side = 1, line = 2, outer = TRUE, cex = 2.25)
+# ## left
+# mtext(text = "Intensity", side = 2, line = 0.6, outer = TRUE, cex = 2.25)
 

### 2021-06-07 run_scripts/c_mmhp_dc.R

@@ -9,9 +9,9 @@ source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_set
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
 cohort_id <- jobid
-#cohort_id <- 1
+# cohort_id <- 1
 ####
-save_data_path <- "output/"  #"output_june30/"
+save_data_path <- "output/revision/" # "output_june30/"
 
 ### specify the number of segments here
 no_segments <- 500
@@ -21,29 +21,29 @@ options(mc.cores = parallel::detectCores())
 
 
 library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
+# library(RColorBrewer)
+# library(Hmisc)
+# library(wCorr)
+# library(tidyverse)
 library(dplyr)
-#library(R.utils)
-#library(fields)
+# library(R.utils)
+# library(fields)
 
 
 
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
+source("lib/naiveRankHierarchy.R")
+source("lib/expertRankHierarchy.R")
+source("lib/cleanData.R")
+source("lib/prepareDataStan.R")
+source("lib/inferLatentMmhp.R")
+source("lib/plotUtil.R")
+source("lib/mmhp.R")
+source("lib/uniHawkes.R")
+source("lib/simulatePrediction.R")
+source("lib/myGlicko.R")
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
+source("lib/matrixPlotParameter.R")
+source("lib/residualStructureScore.R")
 
 
 
@@ -52,23 +52,33 @@ source('lib/residualStructureScore.R')
 #### load the data ####
[…]

### 2021-06-07 run_scripts/overall_predict.R

@@ -17,29 +17,29 @@ options(mc.cores = parallel::detectCores())
 
 library(PlayerRatings)
 library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
+# library(RColorBrewer)
+# library(Hmisc)
 library(wCorr)
-#library(tidyverse)
+# library(tidyverse)
 library(dplyr)
-#library(R.utils)
-#library(fields)
+# library(R.utils)
+# library(fields)
 
 
 
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
+source("lib/naiveRankHierarchy.R")
+source("lib/expertRankHierarchy.R")
+source("lib/cleanData.R")
+source("lib/prepareDataStan.R")
+source("lib/inferLatentMmhp.R")
+source("lib/plotUtil.R")
+source("lib/mmhp.R")
+source("lib/uniHawkes.R")
+source("lib/simulatePrediction.R")
+source("lib/myGlicko.R")
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
+source("lib/matrixPlotParameter.R")
+source("lib/residualStructureScore.R")
 
 
 
@@ -50,28 +50,34 @@ source('lib/residualStructureScore.R')
 
 full_data <- readRDS("data/mice.RData")
 # A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
-cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cohort_names <- paste("cohort", c(9, 10, 12, 15, 16, 17, 18, 37, 38, 45), sep = "")
[…]

### 2021-06-18 output_scripts/Paper_Plots.Rmd
update save path for overall predict, remove old paper plots, add option to draw intensity to draw dashed line add instructions to readme

@@
 
-```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4.5, eval=FALSE}
-### updated to mae
-
-load("../output/plot_N_predict.RData")
-temp_plot_df <- all_cohort_mae_df %>% 
-  group_by(day, method) %>% 
-  summarise(avg = mean(norm), n = n(), sd = sd(norm))
-
-temp_plot_df$method <- factor(temp_plot_df$method,
-                              levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL",
-                                         "C-HP","C-DCHP",
-                                         "C-MMHP"))
-temp_plot_df$day <- factor(temp_plot_df$day)
-
-#png(paste(plot_path,"real_predict_N_all_cohort.png",
-# sep=""),width=600,height=300)
-p4 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
-  geom_line(#aes(linetype = method),
-            size=1.2, alpha=0.8, position=position_dodge(0.2)) +
-  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
-                 position=position_dodge(0.2)) +
-  scale_color_manual(values = plot_cols_pred) + 
-  ggtitle("(b)") +
-  theme_bw() +
-  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
-        text = element_text(size = 20),
-        axis.text.x=element_text(size = 18)) +
-  xlab("Prediction horizon (day)") + 
-  ylab("Frobenius norm of error") + 
-  coord_cartesian(ylim=c(2.5,57.5)) + 
-  guides(color=guide_legend(title="Model")) +
-  guides(linetype = FALSE)
-p4
-```
-
 ```{r fig-7a-pred-all-cohorts-box}
-load("../output/plot_N_predict.RData")
-
-all_cohort_box <- all_cohort_norm_df
+### updated to revision
+load("../output/plot_N_predict_revision.RData")
+
+all_cohort_box <- all_cohort_mae_df
 

### 2021-06-18 output_scripts/revisions_may.Rmd
update save path for overall predict, remove old paper plots, add option to draw intensity to draw dashed line add instructions to readme

@@
          title = "Agreement between initial and later ranking",
-         subtitle = "One Cohort")
+         subtitle = paste0("Cohort ", cohort_id))
   print(coh_plot)
@@
 
+### Get within/between cluster fights for this
+
 # Repeat Rank Simulations
@@
 ```{r process-new-4b}
-plot.s <- 1 # 7 is pretty good
-plot.i <- 20
-plot.j <- 15
+plot.s <- 2 # 7 is pretty good, prev 1
+plot.i <- 20  ## prev 20
+plot.j <- 16  ## prev 15
 
@@
 ```{r fig4b-redone}
-y.ub <- c(4, 5, 3) # c(130,72,31)
+mmhp_lty <- 1
+
+y.ub <- c(8, 8, 8) # c(130,72,31)
 x_events <- 190 # 135#150
-layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 2.5), 3))
 my.xlim <- 200 # 160#200#130
 my.long.x <- 205 # 205#134.5
-legend.x <- c(60, 60, 60) # c(135,135,135)
+legend.x <- c(100, 100, 100) # c(135,135,135)
 legend.y <- # c(34,32,32)
-legend.y <- c(2, 2, 2) # c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.y <- c(6, 6, 6) # c(15,12,15)#c(62,37,18)#c(22,22,22)
 legend.cex <- 1.5 # 3
-line.alpha <- c(0.9, 0.6)
-line.wdth <- c(2, 2.5)
+line.alpha <- c(0.4, 0.6)
+line.wdth <- c(1.5, 2)
 negative.col <- add.alpha("lightskyblue")
 positive.col <- add.alpha("tomato")
-
-par(
-  mar = c(0, 0.3, 0, 0.1), oma = c(0, 3.5, 4, 0),
-  tcl = 0.2, mgp = c(0.5, 0, 0), xpd = TRUE
-)
 
@@
 
+```
+
+```{r actual-plot}
+layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 2.5), 3))
+par(
+  mar = c(0, 0.3, 0, 0.1), oma = c(0, 3.5, 4, 0),
+  tcl = 0.2, mgp = c(0.5, 0, 0), xpd = TRUE
+)
+
+mmhp_est <- fixStateTransition(test.mmhp)
+
 drawUniMMHPIntensityPaper(true.object,
-  simulation = fixStateTransition(test.mmhp),
+                          simulation = mmhp_est,
                           yupper = y.ub[1],
@@
                           title.cex = 2,
-  box.type = "n"
+                          box.type = "n",
+                          line_type = mmhp_lty
 )
@@
 #### more legend
-# legend(legend.x[1], legend.y[1], c("True"),
-#   col = c("black"),
-#   y.intersp = 0.88, x.intersp = 0.15, bty = "n",
-#   lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
-# )
-# legend(legend.x[1] + 22, legend.y[1], c("C-HP"),
-#   col = c(model_colors[1]),
-#   y.intersp = 0.88, x.intersp = 0.15, bty = "n",
-#   lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
-# )
+legend(legend.x[1], legend.y[1] + 1, c("True"),
+       col = c("black"),
+       y.intersp = 0.88, x.intersp = 0.15, bty = "n",
+       lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
+)
+legend(legend.x[1] + 22, legend.y[1] + 1, c("C-HP"),
+       col = c(model_colors[1]),
+       y.intersp = 0.88, x.intersp = 0.15, bty = "n",
+       lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
+)
 
@@
      xlim = c(0, my.xlim), 
-  ylim = c(-1, 1),
+     ylim = c(-0.5, 4),
      type = "n",
@@
 drawUniMMHPIntensityPaper(true.object,
-  simulation = fixStateTransition(test.mmhp),
+                          simulation = mmhp_est,
+                          ### these points aren't consistent?
                           yupper = y.ub[2],
-  color = add.alpha("black", alpha = line.alpha[1]),
+                          color = add.alpha("black",
+                                            alpha = line.alpha[1]),
                           line.width = line.wdth[1],
@@
                           max.x = my.xlim,
-  box.type = "n"
+                          box.type = "n",
+                          line_type = mmhp_lty
 )
@@
 ### used legend
-# legend(legend.x[2], legend.y[2], "C-DCHP",
-#   col = model_colors[2],
-#   y.intersp = 0.88,
-#   x.intersp = 0.1,
-#   bty = "n",
-#   lty = 1,
-#   lwd = 5,
-#   cex = legend.cex,
-#   seg.len = 1
-# )
+legend(legend.x[2], legend.y[2] + 1, c("True"),
+       col = c("black"),
+       y.intersp = 0.88, x.intersp = 0.15, bty = "n",
+       lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
+)
+legend(legend.x[2] + 22, legend.y[2] + 1, "C-DCHP",
+       col = model_colors[2],
+       y.intersp = 0.88,
+       x.intersp = 0.1,
+       bty = "n",
+       lty = 1,
+       lwd = 5,
+       cex = legend.cex,
+       seg.len = 1
+)
 
@@
 ## location of legend
-# legend(legend.x[2] - 50,
-#   legend.y[2] + 1, c("State 0/1 events", "State change point"),
-#   col = c(NA, "red"),
-#   y.intersp = 0.85, x.intersp = -0.5, bty = "n",
-#   pch = c(NA, 4), pt.cex = c(NA, 2), cex = legend.cex,
-#   lty = c(NA, NA), lwd = c(NA, 2)
-# )
-# points(legend.x[2] - 46, legend.y[2] - .5, pch = 1, cex = 2, col = "blue")
-# points(legend.x[2] - 44, legend.y[2] - .5, pch = 16, cex = 2, col = "blue")
+legend(legend.x[2] - 80,
+       legend.y[2] + 2, c("State 0/1 events", "State change point"),
+       col = c(NA, "red"),
+       y.intersp = 0.85,
+       x.intersp = -0,
+       bty = "n",
+       pch = c(NA, 4), pt.cex = c(NA, 2), cex = legend.cex,
+       lty = c(NA, NA), lwd = c(NA, 2)
+)
+points(legend.x[2] - 73, legend.y[2] - 0.5, 
+       pch = 1, cex = 2, col = "blue")
+points(legend.x[2] - 69, legend.y[2] - 0.5,
+       pch = 16, cex = 2, col = "blue")
 
@@
      xlim = c(0, my.xlim),
-  ylim = c(-1, 1.5), type = "n",
+     ylim = c(-0.5, 4), type = "n",
      bty = "n",
@@
 drawUniMMHPIntensityPaper(true.object,
-  simulation = fixStateTransition(test.mmhp),
+                          simulation = mmhp_est,
                           yupper = y.ub[3],
@@
                           y.ratio = -0.05, min.y = -0.5, min.x = 0, max.x = my.xlim,
-  box.type = "n"
+                          box.type = "n", line_type = mmhp_lty
 )
@@
 )
-# legend(legend.x[3], legend.y[3], "C-MMHP",
-#   col = model_colors[3],
-#   y.intersp = 0.6,
-#   x.intersp = 0.1,
-#   bty = "n",
-#   lty = 1,
-#   lwd = 5,
-#   cex = legend.cex,
-#   seg.len = 1
-# )
+legend(legend.x[3], legend.y[3] + 1, c("True"),
+       col = c("black"),
+       y.intersp = 0.88, x.intersp = 0.15, bty = "n",
+       lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
+)
+
+legend(legend.x[3] + 22, legend.y[3] + 1, "C-MMHP",
+       col = model_colors[3],
+       y.intersp = 0.6,
+       x.intersp = 0.1,
+       bty = "n",
+       lty = 1,
+       lwd = 5,
+       cex = legend.cex,
+       seg.len = 1
+)
 ## draw box
@@
 
-# legend(legend.x[3] - 50, legend.y[3] + 2,
-#        c("Overestimation", "Underestimation"),
-#   col = c(positive.col, negative.col),
-#   y.intersp = 0.75, x.intersp = 0.5, bty = "n",
-#   lty = c(1, 1), lwd = c(10, 10), cex = legend.cex, seg.len = 0.8
-# )
+legend(legend.x[3] - 80, legend.y[3] + 2,
+       c("Overestimation", "Underestimation"),
+       col = c(positive.col, negative.col),
+       y.intersp = 0.75, x.intersp = 0.5, bty = "n",
+       lty = c(1, 1), lwd = c(10, 10), cex = legend.cex, seg.len = 0.8
+)
 
@@
 plot(0, 0,
-  xlim = c(0, my.xlim), ylim = c(-1, 1.5), type = "n",
-  bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
+     xlim = c(0, my.xlim), 
+     ylim = c(-0.5, 4), type = "n",
+     bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n",
+     axes = FALSE
 )
@@
 
-# ## top
-# mtext(text = "(b)", side = 3, line = 0.8, outer = TRUE, cex = 2.5, font = 2)
-# ## bottom
-# mtext(text = "Time", side = 1, line = 2, outer = TRUE, cex = 2.25)
-# ## left
-# mtext(text = "Intensity", side = 2, line = 0.6, outer = TRUE, cex = 2.25)
-
+## top
+mtext(text = "(b)", side = 3, line = 0.8,
+      outer = TRUE, cex = 2.5, font = 2)
+## bottom
+mtext(text = "Time", side = 1, line = 2,
+      outer = TRUE, cex = 2.25)
+## left
+mtext(text = "Intensity", side = 2,
+      line = 0.6, outer = TRUE, cex = 2.25)
 ```
+
+Let's try find the best pairs
+```{r identify-best-fig4b}
+plot.s <- 2 # 7 is pretty good
+
+load(paste0(here("output", "revisions", "sim_m3"),
+  "/", "sim_model3_fit123_",
+  plot.s,
+  ".RData"
+))
+
+# 
+# plot.i <- 19  ## prev 20
+# plot.j <- 15  ## prev 15
+# 
+# cur_i <- plot.i
+# cur_j <- plot.j
+
+for(plot.i in 20:15){
+  for(plot.j in 20:15){
+    if(plot.i != plot.j) {
+      cat("i is ", plot.i, ", j is ", plot.j, " \n")
+      test.mmhp <- sim_model3_data$mmhp_matrix[plot.i, plot.j][[1]]
+      temp.t <- test.mmhp$tau
+      current.n <- length(temp.t) - 1
+      time.segment <- seq(0, tail(temp.t, 1), length.out = 5000)
+
+      ### Preprocess the model inference result
+      ## model 1
+      #########
+
+      ## get f from cmdstan
+
+      f_draws <- sim_model3_stan_sim1 %>% 
+        select(starts_with("f"))
+
+      model1_par_est <- list(
+        lambda0 = mean(sim_model3_stan_sim1$lambda0),
+        eta_1 =
+          mean(sim_model3_stan_sim1$eta_1),
+        eta_2 =
+          mean(sim_model3_stan_sim1$eta_2),
+        eta_3 =
+          mean(sim_model3_stan_sim1$eta_3),
+        beta = mean(sim_model3_stan_sim1$beta),
+        f = apply(f_draws, 2, mean)
+      )
+      lambda.m1 <- uniHawkesIntensityNumeric(
+        object = list(
+          lambda0 =
+            model1_par_est$lambda0,
+          alpha =
+            model1_fn$alpha.fun(
+              model1_par_est$f[plot.i],
+              model1_par_est$f[plot.j],
+              model1_par_est$eta_1,
+              model1_par_est$eta_2,
+              model1_par_est$eta_3
+            ),
+          beta = model1_par_est$beta
+        ),
+        events = temp.t,
+        time.vec = time.segment
+      )
+
+      ## model2
+      #############
+      gamma_draws <- sim_model3_stan_sim2 %>% 
+        select(starts_with("gamma"))
+
+      zeta_draws <- sim_model3_stan_sim2 %>% 
+        select(starts_with("zeta"))
+
+      f_draws <- sim_model3_stan_sim2 %>% 
+        select(starts_with("f"))
+
+      model2_par_est <- list(
+        gamma = apply(gamma_draws, 2, mean),
+        zeta = apply(zeta_draws, 2, mean),
+        eta_1 = mean(sim_model3_stan_sim2$eta_1),
+        eta_2 = mean(sim_model3_stan_sim2$eta_2),
+        eta_3 = mean(sim_model3_stan_sim2$eta_3),
+        beta = mean(sim_model3_stan_sim2$beta),
+        f = apply(f_draws, 2, mean)
+      )
+
+      lambda.m2 <- uniHawkesIntensityNumeric(
+        object = list(
+          lambda0 = model2_par_est$gamma[plot.i] +
+            model2_par_est$zeta[plot.j],
+          alpha = model1_fn$alpha.fun(
+            model2_par_est$f[plot.i],
+            model2_par_est$f[plot.j],
+            model2_par_est$eta_1,
+            model2_par_est$eta_2,
+            model2_par_est$eta_3
+          ),
+          beta = model2_par_est$beta
+        ),
+        events = temp.t,
+        time.vec = time.segment
+      )
+
+      ## Model3
+      ###
+
+      lam0_draws <- sim_model3_stan_sim3 %>% 
+        select(starts_with("gamma"))
+
+      lam1_draws <- sim_model3_stan_sim3 %>% 
+        select(starts_with("zeta"))
+
+      gamma_draws <- sim_model3_stan_sim3 %>% 
+        select(starts_with("gamma"))
+
+      zeta_draws <- sim_model3_stan_sim3 %>% 
+        select(starts_with("zeta"))
+
+      f_draws <- sim_model3_stan_sim2 %>% 
+        select(starts_with("f"))
+
+      lam0_vec <- apply(lam0_draws, 2, mean)
+      lam1_vec <- apply(lam1_draws, 2, mean)
+      lam0_par_est <- matrix(0,
+        nrow = length(object_par$f_vec_1),
+        ncol = length(object_par$f_vec_1)
+      )
+      lam1_par_est <- matrix(0,
+        nrow = length(object_par$f_vec_1),
+        ncol = length(object_par$f_vec_1)
+      )
+
+      clean_sim_data <- cleanSimulationData(
+        raw_data = sim_model3_data,
+        cut_off = cut_off,
+        N = length(object_par$f_vec_1)
+      )
+
+      for (i in seq_along(lam0_vec)) {
+        row_id <- clean_sim_data$I_fit[i]
+        col_id <- clean_sim_data$J_fit[i]
+        lam0_par_est[row_id, col_id] <- lam0_vec[i]
+        lam1_par_est[row_id, col_id] <- lam1_vec[i]
+      }
+
+      ###
+
+      #############
+      mmhp_par_est <- list(
+        lambda0 = lam0_par_est,
+        lambda1 = lam1_par_est,
+        eta_1 = mean(sim_model3_stan_sim3$eta_1),
+        eta_2 = mean(sim_model3_stan_sim3$eta_2),
+        eta_3 = mean(sim_model3_stan_sim3$eta_3),
+        beta = mean(sim_model3_stan_sim3$beta),
+        f = apply(f_draws, 2, mean)
+      )
+
+      object_hat <- list(
+        lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
+        lambda1 = mmhp_par_est$lambda1[cur_i, cur_j],
+        alpha = model3_fn$alpha.fun(
+          mmhp_par_est$f[cur_i],
+          mmhp_par_est$f[cur_j],
+          mmhp_par_est$eta_1,
+          mmhp_par_est$eta_2
+        ),
+        beta = mmhp_par_est$beta,
+        q1 = model3_fn$q1.fun(
+          mmhp_par_est$f[cur_i],
+          mmhp_par_est$f[cur_j],
+          mmhp_par_est$eta_3
+        ),
+        q2 = model3_fn$q0.fun(
+          mmhp_par_est$f[cur_i],
+          mmhp_par_est$f[cur_j],
+          mmhp_par_est$eta_3
+        )
+      )
+
+      ## then need to load in the state estimate here
+      load(paste0(here("output", "revisions", "sim_m3"),
+        "/", "fit123_state_est_",
+        plot.s,
+        ".RData"
+      ))
+
+      state.est.latent.mmhp <- interpolate_state_est_lst[plot.i, plot.j][[1]]
+      state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
+        termination = 200
+      )
+
+      step.fun.est <- stepfun(
+        state.est.latent.mmhp$x.hat,
+        2 - state.est.latent.mmhp$z.hat
+      )
+
+      lambda.m3 <- mmhpIntensityNumeric(
+        params = object_hat,
+        t = temp.t[-1],
+        time.vec = time.segment,
+        latent.vec = step.fun.est(time.segment)
+      )
+
+      object_true <- lapply(object_matrix, function(x) x[plot.i, plot.j])
+      names(object_true) <- c("lambda0", "lambda1", "alpha", "beta", "q1", "q2")
+
+      lambda.true <- mmhpTrueIntensityNumeric(
+        params = object_true,
+        t = temp.t,
+        latent = list(
+          x = fixStateTransition(test.mmhp)$x,
+          z = fixStateTransition(test.mmhp)$z
+        ),
+        time.vec = time.segment
+      )
+
+      print(range(lambda.m1$lambda.t - lambda.true$lambda.t))
+      cat("M1 ----- \n")
+      print(range(lambda.m2$lambda.t - lambda.true$lambda.t))
+      cat("M2 ----- \n")
+      print(range(lambda.m3 - lambda.true$lambda.t))
+      cat("M3 ----- \n")
+
+    }
+  }
+}
+```
+
+# Redo 5a
+
+```{r process_sims_5a}
+sim_data_path <- "../output/revisions/sim_m3/"
+
+n_sim <- 50
+
+num_nodes <- 20
+
+object_par <- list(sim_lambda_1 = 0.2,
+                   sim_eta_1 = 1.5,
+                   gamma_var = runif(n = num_nodes, min = 0.01, max = 0.05),
+                   zeta_var = runif(n = num_nodes, min = 0.01, max = 0.05),
+                   sim_eta_2 = 0.6,
+                   sim_eta_3 = 3,
+                   sim_beta = 2,
+                   f_vec_1 = seq(from = 0.05, to = 0.95,
+                                 length.out = num_nodes))
+
+## Initialize
+N_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+Lambda_model3_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+Lambda_model1_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+Lambda_model2_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+Lambda_true_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+PR_model1_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+PR_model2_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+PR_model3_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+PR_true_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_model1_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_model2_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_model3_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_true_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_p_model1_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_p_model2_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_p_model3_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_p_true_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+
+## Iteration on 50 simulations
+for (s in c(1:n_sim)) {
+  print(s)
+  load(paste0(sim_data_path, "sim_model3_fit123_", s, ".RData"))
+  load(paste(sim_data_path, "fit123_state_est_", s, ".RData", sep = ""))
+  clean_sim_data <- cleanSimulationData(
+    raw_data = sim_model3_data,
+    cut_off = cut_off,
+    N = length(object_par$f_vec_1)
+  )
+
+  N_array[s, , ] <- clean_sim_data$N_count
+
+  ## model 1
+  #########
+  ### transform from cmdstan here
+  f_draws <- sim_model3_stan_sim1 %>% 
+  select(starts_with("f"))
+
+  ###
+  model1_par_est <- list(
+    lambda0 = mean(sim_model3_stan_sim1$lambda0),
+    eta_1 = mean(sim_model3_stan_sim1$eta_1),
+    eta_2 = mean(sim_model3_stan_sim1$eta_2),
+    eta_3 = mean(sim_model3_stan_sim1$eta_3),
+    beta = mean(sim_model3_stan_sim1$beta),
+    f = apply(f_draws, 2, mean)
+  )
+
+  for (i in c(1:num_nodes)) {
+    for (j in c(1:num_nodes)[-i]) {
+      current_t <- sim_model3_data$mmhp_matrix[i, j][[1]]$tau
+      m1_object <- list(
+        lambda0 = model1_par_est$lambda0,
+        alpha = model1_fn$alpha.fun(
+          model1_par_est$f[i],
+          model1_par_est$f[j],
+          model1_par_est$eta_1,
+          model1_par_est$eta_2,
+          model1_par_est$eta_3
+        ),
+        beta = model1_par_est$beta
+      )
+      Lambda_model1_array[s, i, j] <-
+        uniHawkesIntegralIntensity(
+          object = m1_object,
+          events = current_t,
+          termination = tail(current_t, 1)
+        )
+      Lambda_test <- uniHawkesCompensator(
+        object = m1_object,
+        events = current_t
+      )
+      KS_model1_array[s, i, j] <- ks.test(Lambda_test, "pexp")$statistic
+      KS_p_model1_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
+      PR_model1_array[s, i, j] <- uniHawkesPearsonResidual(
+        object = m1_object,
+        events = current_t,
+        termination =
+          tail(current_t, 1)
+      )
+    }
+  }
+
+  ## model2
+  #############
+  ### convert to cmdstan
+  gamma_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("gamma"))
+  zeta_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("zeta"))
+  f_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("f"))
+
+  model2_par_est <- list(
+    gamma = apply(gamma_draws, 2, mean),
+    zeta = apply(zeta_draws, 2, mean),
+    eta_1 = mean(sim_model3_stan_sim2$eta_1),
+    eta_2 = mean(sim_model3_stan_sim2$eta_2),
+    eta_3 = mean(sim_model3_stan_sim2$eta_3),
+    beta = mean(sim_model3_stan_sim2$beta),
+    f = apply(f_draws, 2, mean)
+  )
+
+  for (i in c(1:num_nodes)) {
+    for (j in c(1:num_nodes)[-i]) {
+      current_t <- sim_model3_data$mmhp_matrix[i, j][[1]]$tau
+      m2_object <- list(
+        lambda0 = model2_par_est$gamma[i] +
+          model2_par_est$zeta[j],
+        alpha = model1_fn$alpha.fun(
+          model2_par_est$f[i],
+          model2_par_est$f[j],
+          model2_par_est$eta_1,
+          model2_par_est$eta_2,
+          model2_par_est$eta_3
+        ),
+        beta = model2_par_est$beta
+      )
+      Lambda_model2_array[s, i, j] <-
+        uniHawkesIntegralIntensity(
+          object = m1_object,
+          events = current_t,
+          termination = tail(current_t, 1)
+        )
+      Lambda_test <- uniHawkesCompensator(
+        object = m2_object,
+        events = current_t
+      )
+      KS_model2_array[s, i, j] <- ks.test(Lambda_test, "pexp")$statistic
+      KS_p_model2_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
+      PR_model2_array[s, i, j] <-
+        uniHawkesPearsonResidual(
+          object = m2_object,
+          events = current_t,
+          termination = tail(current_t, 1)
+        )
+    }
+  }
+
+  ## Model3 & true model
+  ######
+  ### cmdstan part
+  lam0_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("lambda0"))
+  lam1_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("lambda1"))
+  f_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("f"))
+
+  lambda_0_est <- apply(lam0_draws, 2, mean)
+  lambda_1_est <- apply(lam1_draws, 2, mean)
+  ## then put these into a matrix
+  lam0_par_est <- matrix(0,
+    nrow = length(object_par$f_vec_1),
+    ncol = length(object_par$f_vec_1)
+  )
+  lam1_par_est <- matrix(0,
+    nrow = length(object_par$f_vec_1),
+    ncol = length(object_par$f_vec_1)
+  )
+  for (i in seq_along(lambda_0_est)) {
+    row_id <- clean_sim_data$I_fit[i]
+    col_id <- clean_sim_data$J_fit[i]
+    lam0_par_est[row_id, col_id] <- lambda_0_est[i]
+    lam1_par_est[row_id, col_id] <- lambda_1_est[i]
+  }
+  mmhp_par_est <- list(
+    lambda0 = lam0_par_est,
+    lambda1 = lam1_par_est,
+    eta_1 = mean(sim_model3_stan_sim3$eta_1),
+    eta_2 = mean(sim_model3_stan_sim3$eta_2),
+    eta_3 = mean(sim_model3_stan_sim3$eta_3),
+    beta = mean(sim_model3_stan_sim3$beta),
+    f = apply(f_draws, 2, mean)
+  )
+  clean_sim_data <- cleanSimulationData(
+    raw_data = sim_model3_data,
+    cut_off = cut_off,
+    N = length(object_par$f_vec_1)
+  )
+
+  for (i in c(1:num_nodes)) {
+    for (j in c(1:num_nodes)[-i]) {
+      test.mmhp <- sim_model3_data$mmhp_matrix[i, j][[1]]
+      temp.t <- test.mmhp$tau
+      current.n <- length(temp.t) - 1
+      time.segment <- seq(0, tail(temp.t, 1), length.out = 10000)
+
+      object_hat <- list(
+        lambda0 = mmhp_par_est$lambda0[i, j],
+        lambda1 = mmhp_par_est$lambda1[i, j],
+        alpha = model3_fn$alpha.fun(
+          mmhp_par_est$f[i],
+          mmhp_par_est$f[j],
+          mmhp_par_est$eta_1,
+          mmhp_par_est$eta_2
+        ),
+        beta = mmhp_par_est$beta,
+        q1 = model3_fn$q1.fun(
+          mmhp_par_est$f[i],
+          mmhp_par_est$f[j],
+          mmhp_par_est$eta_3
+        ),
+        q2 = model3_fn$q0.fun(
+          mmhp_par_est$f[i],
+          mmhp_par_est$f[j],
+          mmhp_par_est$eta_3
+        )
+      )
+
+      object_true <- lapply(object_matrix, function(x) x[i, j])
+      names(object_true) <- c("lambda0", "lambda1",
+                              "alpha", "beta", "q1", "q2")
+
+      ## est Lmabda and [R]
+      Lambda.test <- mmhpCompensator(
+        params = object_hat,
+        t = temp.t,
+        pzt = 2 -
+          event_state_est_lst[i, j][[1]]$zt_v,
+        if.pzt = FALSE
+      )
+      KS_model3_array[s, i, j] <- ks.test(Lambda.test, "pexp")$statistic
+      KS_p_model3_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
+      state.est.latent.mmhp <- interpolate_state_est_lst[i, j][[1]]
+      step.fun.est <- stepfun(
+        state.est.latent.mmhp$x.hat,
+        2 - state.est.latent.mmhp$z.hat
+      )
+      est.intensity <- mmhpIntensityNumeric(
+        params = object_hat,
+        t = temp.t[-1],
+        time.vec = time.segment,
+        latent.vec =
+          step.fun.est(time.segment)
+      )
+      est.intensity.events <- mmhpIntensityAtEvents(
+        params = object_hat,
+        t = temp.t,
+        latent_z =
+          event_state_est_lst[i, j][[1]]$zt_v
+      )
+      Lambda_model3_array[s, i, j] <-
+        sum(est.intensity) * (time.segment[2] - time.segment[1])
+      PR_model3_array[s, i, j] <- sum(1 / sqrt(est.intensity.events)) -
+        sum(sqrt(est.intensity)) * (time.segment[2] - time.segment[1])
+
+      ## Under the true model
+      Lambda.test.true <- mmhpCompensator(
+        params = object_true,
+        t = temp.t,
+        pzt = 2 -
+          test.mmhp$zt[2:length(test.mmhp$zt)],
+        if.pzt = FALSE
+      )
+      KS_true_array[s, i, j] <- ks.test(Lambda.test.true, "pexp")$statistic
+      KS_p_true_array[s, i, j] <- ks.test(Lambda.test.true, "pexp")$p.value
+      true.intensity <-
+        mmhpTrueIntensityNumeric(
+          params = object_true,
+          t = temp.t,
+          latent = list(
+            x =
+              fixStateTransition(test.mmhp)$x,
+            z =
+              fixStateTransition(test.mmhp)$z
+          ),
+          time.vec = time.segment
+        )
+      true.intensity.events <- mmhpIntensityAtEvents(
+        params = object_true,
+        t = temp.t,
+        latent_z = test.mmhp$zt
+      )
+      Lambda_true_array[s, i, j] <- sum(true.intensity$lambda.t) * (time.segment[2] - time.segment[1])
+      PR_true_array[s, i, j] <- sum(1 / sqrt(true.intensity.events)) -
+        sum(sqrt(true.intensity$lambda.t)) * (time.segment[2] - time.segment[1])
+    }
+  }
+}
+
+```
+
+```{r curr_fig5a}
+cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
+                                 "True")) %>%
+  arrange(factor(method, levels = c("C-HP","C-DCHP","C-MMHP","True"))) %>%
+  pull(cols)
+#load("../output/sim_model3_fit123_residuals.RData")
+par(mfrow=c(5,5),mar=c(0.2,0.2,0.2,0.2),oma=c(2.4,2.4,2.9,0.5))
+for(i in c(5:1)){
+  for(j in c(5:1)){
+    if(i==j){
+      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
+           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+      if(i==5){
+        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04, 
+                col = cols_plot[1], border = NA)
+        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,
+                col = cols_plot[2], border = NA)
+        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,
+                col = cols_plot[3], border = NA)
+        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,
+                col = cols_plot[4], border = NA)
+        text(c(0.43,0.58,0.61,0.4), seq(0.8,0.14,-0.22),
+             c("C-HP", "C-DCHP", "C-MMHP", "True"),
+             cex=1.7)
+      }
+    }else{
+      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
+      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
+      PR <- c(KS_model1_array[,i,j], KS_model2_array[,i,j],
+              KS_model3_array[,i,j], KS_true_array[,i,j])
+      ### try pr scores instead
+      # PR <- c(PR_model1_array[,i,j],PR_model2_array[,i,j],
+      #         PR_model3_array[,i,j],PR_true_array[,i,j])
+      Type <- c(rep(1,n_sim), rep(2,n_sim), rep(3,n_sim), rep(4,n_sim))
+      boxplot(PR ~ Type,  
+              col = cols_plot,
+              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
+              xlab="",ylab="",xaxt="n",yaxt="n")
+      #names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
+    }
+  }
+}
+# mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
+#       at=c(0:4)/5+0.1)
+# mtext(text=c(5:1), side=1, line=1.5, outer=TRUE, cex=2,
+#       at=c(0:4)/5+0.1)
+# mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)
+
+```
+
+```{r new-5a}
+cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
+                                 "True")) %>%
+  arrange(factor(method, levels = c("C-HP","C-DCHP","C-MMHP","True"))) %>%
+  pull(cols)
+
+m1_ks <- tibble(Method = "C-HP",
+       ks = as.vector(KS_model1_array))
+
+m2_ks <- tibble(Method = "C-DCHP",
+       ks = as.vector(KS_model2_array))
+
+m3_ks <- tibble(Method = "C-MMHP",
+       ks = as.vector(KS_model3_array))
+
+true_ks <- tibble(Method = "True",
+                  ks = as.vector(KS_true_array))
+
+all_ks <- m1_ks %>% 
+  bind_rows(m2_ks) %>% 
+  bind_rows(m3_ks) %>% 
+  bind_rows(true_ks)
+
+all_ks$Method <- factor(all_ks$Method, levels = c("C-HP",
+                                                "C-DCHP",
+                                                "C-MMHP",
+                                                "True") )
+
+all_ks %>% 
+  ggplot(aes(Method, ks)) + 
+  geom_boxplot(aes(fill = Method)) +
+  scale_fill_manual(values = cols_plot) +
+  labs(y = "KS Statistic")
+
+m1_pr <- tibble(Method = "C-HP",
+       pr = as.vector(PR_model1_array))
+
+m2_pr <- tibble(Method = "C-DCHP",
+       pr = as.vector(PR_model2_array))
+
+m3_pr <- tibble(Method = "C-MMHP",
+       pr = as.vector(PR_model3_array))
+
+true_pr <- tibble(Method = "True",
+                  pr = as.vector(PR_true_array))
+
+all_pr <- m1_pr %>% 
+  bind_rows(m2_pr) %>% 
+  bind_rows(m3_pr) %>% 
+  bind_rows(true_pr)
+
+all_pr$Method<- factor(all_pr$Method, levels = c("C-HP",
+                                                "C-DCHP",
+                                                "C-MMHP",
+                                                "True") )
+all_pr %>% 
+  ggplot(aes(Method, pr)) + 
+  geom_boxplot(aes(fill = Method)) +
+  scale_fill_manual(values = cols_plot) +
+  labs(y = "Pearson Residual")
+```
+
+```{r take-mean-ks/pr}
+m1_ks <- tibble(Method = "C-HP",
+       ks = as.vector(apply(KS_model1_array, c(2,3), mean)))
+
+m2_ks <- tibble(Method = "C-DCHP",
+       ks = as.vector(apply(KS_model2_array, c(2,3), mean)))
+
+m3_ks <- tibble(Method = "C-MMHP",
+       ks = as.vector(apply(KS_model3_array, c(2,3), mean)))
+
+true_ks <- tibble(Method = "True",
+                  ks = as.vector(apply(KS_true_array, c(2,3), mean)))
+
+all_ks <- m1_ks %>% 
+  bind_rows(m2_ks) %>% 
+  bind_rows(m3_ks) %>% 
+  bind_rows(true_ks)
+
+all_ks$Method <- factor(all_ks$Method, levels = c("C-HP",
+                                                "C-DCHP",
+                                                "C-MMHP",
+                                                "True") )
+
+all_ks %>% 
+  ggplot(aes(Method, ks)) + 
+  geom_boxplot(aes(fill = Method)) +
+  scale_fill_manual(values = cols_plot) +
+  labs(y = "KS Statistic", title = "Average per Node Pair")
+
+####
+m1_pr <- tibble(Method = "C-HP",
+       pr = as.vector(apply(PR_model1_array, c(2,3), mean)))
+
+m2_pr <- tibble(Method = "C-DCHP",
+       pr = as.vector(apply(PR_model2_array, c(2,3), mean)))
+
+m3_pr <- tibble(Method = "C-MMHP",
+       pr = as.vector(apply(PR_model3_array, c(2,3), mean)))
+
+true_pr <- tibble(Method = "True",
+                  pr = as.vector(apply(PR_true_array, c(2,3), mean)))
+
+all_pr <- m1_pr %>% 
+  bind_rows(m2_pr) %>% 
+  bind_rows(m3_pr) %>% 
+  bind_rows(true_pr)
+
+all_pr$Method<- factor(all_pr$Method, levels = c("C-HP",
+                                                "C-DCHP",
+                                                "C-MMHP",
+                                                "True") )
+all_pr %>% 
+  ggplot(aes(Method, pr)) + 
+  geom_boxplot(aes(fill = Method)) +
+  scale_fill_manual(values = cols_plot) +
+  labs(y = "Pearson Residual", title = "Average Residual per Node Pair")
+```

### 2021-06-18 lib/drawIntensity.R

@@ -1,70 +1,122 @@
 ################################################################################################
-#This R file is source code to generate intensity figure for the latex file
-#There are two functions in this source code: drawUniMMHPIntensityPaper and drawHPIntensityPaper
-#Function 'drawHPIntensityPaper' is used to assist main function 'drawUniMMHPIntensityPaper'
+# This R file is source code to generate intensity figure for the latex file
+# There are two functions in this source code: drawUniMMHPIntensityPaper and drawHPIntensityPaper
+# Function 'drawHPIntensityPaper' is used to assist main function 'drawUniMMHPIntensityPaper'
 ################################################################################################
 
-drawUniMMHPIntensityPaper<-function(object,simulation,yupper=10,add=FALSE,color=1,line.width=1,
-                                    title_name="",title.cex=9, y.ratio=0, min.y=NULL, min.x=0, max.x=NULL, 
-                                    annotate.time=FALSE, event.cex=1, box.type="l", box.col="gray40", title.line=0.5){
+drawUniMMHPIntensityPaper <- function(object, simulation,
+                                      yupper = 10,
+                                      add = FALSE,
+                                      color = 1,
+                                      line.width = 1,
+                                      title_name = "",
+                                      title.cex = 9,
+                                      y.ratio = 0,
+                                      min.y = NULL,
+                                      min.x = 0,
+                                      max.x = NULL,
+                                      annotate.time = FALSE,
+                                      event.cex = 1,
+                                      box.type = "l",
+                                      box.col = "gray40",
+                                      title.line = 0.5,
+                                      line_type = 1) {
   # input object: the parameter list used for generating mmhp
-  #       simulation: simulation result from simulate.mmhp 
-  
[…]

### 2021-06-18 run_scripts/overall_predict.R

@@ -352,7 +352,7 @@ save(predict_day_norm_df_lst,
   est_array_m3,
   est_array_mmhp,
   est_array_dsnl,
-  file = paste(data_path, "plot_N_predict.RData", sep = "")
+  file = paste(data_path, "plot_N_predict_revision.RData", sep = "")
 )
 
 

### 2021-06-18 output_scripts/revisions_may.Rmd
modify sim fits for a simpler simulation scenario with easier gamma, fixed common zeta, shorter sim

@@
 
-unique_observe_days %>% 
+start_winds <- unique_observe_days %>% 
   filter(observe.id %in% start_win)
 
-unique_observe_days %>% 
+end_winds <-unique_observe_days %>% 
   filter(observe.id %in% end_win)
@@
 ### Get within/between cluster fights for this
+
+```{r extract-from-previons}
+wind1_memb <- tibble(id = 1:12, memb = lec1$membership)
+
+return_df %>% 
+  filter(observe.id >= start_winds$observe.id[1]) %>% 
+  filter(observe.id <= end_winds$observe.id[1]) %>% 
+  ### join with wind1_memb, tally
+  left_join(wind1_memb, by = c("initiator" = "id"))
+
+# length(lec2$membership)
+# 
+# length(lec3$membership)
+
+```
 
@@
 legend.cex <- 1.5 # 3
-line.alpha <- c(0.4, 0.6)
+line.alpha <- c(1, 0.5)
 line.wdth <- c(1.5, 2)
@@
 #### more legend
-legend(legend.x[1], legend.y[1] + 1, c("True"),
+legend(legend.x[1] - 2, legend.y[1] + 1, c("True"),
        col = c("black"),
-       y.intersp = 0.88, x.intersp = 0.15, bty = "n",
+       y.intersp = 0.88, x.intersp = 0.65, bty = "n",
        lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
@@
        col = c(model_colors[1]),
-       y.intersp = 0.88, x.intersp = 0.15, bty = "n",
+       y.intersp = 0.88, x.intersp = 0.65, bty = "n",
        lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
@@
 ### used legend
-legend(legend.x[2], legend.y[2] + 1, c("True"),
+legend(legend.x[2] - 2, legend.y[2] + 1, c("True"),
        col = c("black"),
-       y.intersp = 0.88, x.intersp = 0.15, bty = "n",
+       y.intersp = 0.88, x.intersp = 0.65, bty = "n",
        lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
@@
        y.intersp = 0.88,
-       x.intersp = 0.1,
+       x.intersp = 0.65,
        bty = "n",
@@
 ## location of legend
-legend(legend.x[2] - 80,
+legend(legend.x[2] - 95,
        legend.y[2] + 2, c("State 0/1 events", "State change point"),
@@
 )
-points(legend.x[2] - 73, legend.y[2] - 0.5, 
+points(legend.x[2] - 89, legend.y[2], 
        pch = 1, cex = 2, col = "blue")
-points(legend.x[2] - 69, legend.y[2] - 0.5,
+points(legend.x[2] - 85, legend.y[2],
        pch = 16, cex = 2, col = "blue")
@@
                           line.width = line.wdth[1],
-                          y.ratio = -0.05, min.y = -0.5, min.x = 0, max.x = my.xlim,
+                          y.ratio = -0.05, min.y = -0.5,
+                          min.x = 0, max.x = my.xlim,
                           box.type = "n", line_type = mmhp_lty
@@
 )
-legend(legend.x[3], legend.y[3] + 1, c("True"),
+legend(legend.x[3] - 2, legend.y[3] + 1, c("True"),
        col = c("black"),
-       y.intersp = 0.88, x.intersp = 0.15, bty = "n",
+       y.intersp = 0.88, x.intersp = 0.65, bty = "n",
        lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
@@
        col = model_colors[3],
-       y.intersp = 0.6,
-       x.intersp = 0.1,
+       y.intersp = 0.88,
+       x.intersp = .65,
        bty = "n",
@@
 
-legend(legend.x[3] - 80, legend.y[3] + 2,
+legend(legend.x[3] - 95, legend.y[3] + 2,
        c("Overestimation", "Underestimation"),
@@
           latent = list(
-            x =
-              fixStateTransition(test.mmhp)$x,
-            z =
-              fixStateTransition(test.mmhp)$z
+            ## these are the truth
+            x = fixStateTransition(test.mmhp)$x,
+            z = fixStateTransition(test.mmhp)$z
           ),
@@
       )
-      Lambda_true_array[s, i, j] <- sum(true.intensity$lambda.t) * (time.segment[2] - time.segment[1])
+      Lambda_true_array[s, i, j] <- sum(true.intensity$lambda.t) *
+        (time.segment[2] - time.segment[1])
       PR_true_array[s, i, j] <- sum(1 / sqrt(true.intensity.events)) -
@@
   }
+  rm(sim_model3_data)
 }
@@
 
-```{r curr_fig5a}
+```{r old_fig5a}
 cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
@@
               col = cols_plot,
-              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
-              xlab="",ylab="",xaxt="n",yaxt="n")
+              xlab="", ylab="",xaxt="n",yaxt="n")
       #names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
@@
 ```{r new-5a}
-cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
-                                 "True")) %>%
-  arrange(factor(method, levels = c("C-HP","C-DCHP","C-MMHP","True"))) %>%
+cols_plot <- col_df %>% 
+  filter(method %in% c("C-HP","C-DCHP","C-MMHP", "True")) %>%
+  arrange(factor(method, levels = c("C-HP", "C-DCHP", "C-MMHP", "True"))) %>%
   pull(cols)

### 2021-06-18 run_scripts/sim_fits.R

@@ -4,7 +4,7 @@
 #### if running on cluster ####
 source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 
-data_path <- "output/revisions/sim_m3/"
+data_path <- "output/revisions/sim_m3/june_18/"
 
 library(cmdstanr)
 library(R.utils)
@@ -33,7 +33,7 @@ source('lib/drawIntensity.R')
 n_sim <- 1
 num_nodes <- 20
 cut_off <- 3
-obs_time <- 200
+obs_time <- 50
 
 model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
   return(eta1 * x * y * exp(-eta2 * abs(x-y))/(1 + exp(-eta3 *(x-y))))})
@@ -51,63 +51,63 @@ object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
                   q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
                   q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
 
-# object_par <- list(sim_lambda_1 = 0.2,
-#                    sim_eta_1 = 1.5,
-#                    gamma_var = runif(n = num_nodes, min = 0.01, max = 0.05),
-#                    zeta_var = runif(n = num_nodes, min = 0.01, max = 0.05),
-#                    sim_eta_2 = 0.6,
-#                    sim_eta_3 = 3,
-#                    sim_beta = 2,
-#                    f_vec_1 = seq(from = 0.05, to = 0.95,
-#                                  length.out = num_nodes))
-# 
-# object_matrix <- list(lambda0_matrix=outer(object_par$gamma_var,
-#                                            object_par$zeta_var, "+"),
-#                       lambda1_matrix=matrix(object_par$sim_lambda_1,
-#                                             nrow=length(object_par$f_vec_1),
-#                                             ncol=length(object_par$f_vec_1)),
-#                       alpha_matrix=formMatrix(function(x,y)
-#                         object_fn$alpha.fun(x,y,object_par$sim_eta_1,
-#                                             object_par$sim_eta_2),
-#                         object_par$f_vec_1),
-#                       beta_matrix=matrix(object_par$sim_beta,
-#                                          nrow=length(object_par$f_vec_1),
-#                                          ncol=length(object_par$f_vec_1)),
-#                       q1_matrix=formMatrix(function(x,y) 
-#                         object_fn$q1.fun(x, y,
[…]

### 2021-06-23 output_scripts/revisions_may.Rmd
look at further stability components, set sim fits to small examples

@@
 
+  init_ranking <- all_ranks %>% filter(when == "first14") %>% 
+  group_by(node) %>% 
+  summarise(med = median(rank)) %>% 
+  arrange(-med) %>% 
+  pull(node)
+
+  ### then set the levels off this
+  all_ranks$node <- factor(all_ranks$node, 
+                           levels = as.character(init_ranking))
+
   coh_plot <- all_ranks %>% 
@@
 }
+
+```
+
+### Further Stability Questions
+
+To further investigate the stability of these rankings we 
+can do multiple things, including comparing the I&SI scores for both time
+periods to see the correlation across time.
+
+```{r compute start-end-isi}
+isi_data <- tibble()
+
+for(current_cohort in 1:10) {
+  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+  return_df <- cleanObservationPeriod(current_cohort, 
+                                    full_data[[cohort_names[current_cohort]]],
+                                      clean_data)
+  start_events <- return_df %>% filter(day <= 14)
+  wl_start <- get_wl_matrix(start_events[, c(3, 4)])
+  isi_start <- isi98(wl_start)
+  start_inf <- tibble(score = isi_start$I + isi_start$SI,
+                      order = list(isi_start$best_order),
+                      cohort = current_cohort,
+                      time = "Start")
+  isi_data <- isi_data %>% bind_rows(start_inf)
+  end_events <- return_df %>% filter(day > 7)
+  wl_end <- get_wl_matrix(end_events[, c(3, 4)])
+  isi_end <- isi98(wl_end)
+  end_inf <- tibble(score = isi_end$I + isi_end$SI,
+                      order = list(isi_end$best_order),
+                      cohort = current_cohort,
+                      time = "End")
+  isi_data <- isi_data %>% 
+    bind_rows(end_inf)
+}
+
+```
+
+```{r plot_output}
+isi_data %>% ggplot(aes(cohort, score, colour = time)) +
+  geom_point(alpha = 0.5, show.guide = FALSE) + 
+  scale_x_continuous(breaks = 1:10)
+
+### want one row for each cohort
+isi_data %>% 
+  select(-order) %>% 
+  pivot_wider(names_from = time, values_from = score) %>% 
+  summarise(correlation = cor(Start, End))
 
@@
   ### join with wind1_memb, tally
-  left_join(wind1_memb, by = c("initiator" = "id"))
-
-# length(lec2$membership)
-# 
-# length(lec3$membership)
+  left_join(wind1_memb, by = c("initiator" = "id")) %>% 
+  left_join(wind1_memb, by = c("recipient" = "id")) %>% 
+  rename(send_clust = memb.x, 
+         rec_clust = memb.y) %>% 
+  group_by(send_clust, rec_clust) %>% 
+  summarise(num_events = sum(no.events)) %>% 
+  mutate(clust = if_else(send_clust == rec_clust, "internal", "external")) %>% 
+  group_by(clust) %>% 
+  summarise(events = sum(num_events)) %>% 
+  ungroup() %>% 
+  mutate(prop = events/sum(events))
+
+wind2_memb <- tibble(id = 1:12, memb = lec2$membership)
+
+return_df %>% 
+  filter(observe.id >= start_winds$observe.id[2]) %>% 
+  filter(observe.id <= end_winds$observe.id[2]) %>% 
+  ### join with wind1_memb, tally
+  left_join(wind2_memb, by = c("initiator" = "id")) %>% 
+  left_join(wind2_memb, by = c("recipient" = "id")) %>% 
+  rename(send_clust = memb.x, 
+         rec_clust = memb.y) %>% 
+  group_by(send_clust, rec_clust) %>% 
+  summarise(num_events = sum(no.events)) %>% 
+  mutate(clust = if_else(send_clust == rec_clust, "internal", "external")) %>% 
+  group_by(clust) %>% 
+  summarise(events = sum(num_events)) %>% 
+  ungroup() %>% 
+  mutate(prop = events/sum(events))
+
+wind3_memb <- tibble(id = 1:12, memb = lec3$membership)
+
+return_df %>% 
+  filter(observe.id >= start_winds$observe.id[3]) %>% 
+  filter(observe.id <= end_winds$observe.id[3]) %>% 
+  ### join with wind1_memb, tally
+  left_join(wind3_memb, by = c("initiator" = "id")) %>% 
+  left_join(wind3_memb, by = c("recipient" = "id")) %>% 
+  rename(send_clust = memb.x, 
+         rec_clust = memb.y) %>% 
+  group_by(send_clust, rec_clust) %>% 
+  summarise(num_events = sum(no.events)) %>% 
+  mutate(clust = if_else(send_clust == rec_clust, "internal", "external")) %>% 
+  group_by(clust) %>% 
+  summarise(events = sum(num_events)) %>% 
+  ungroup() %>% 
+  mutate(prop = events/sum(events))
+
+```
+
+```{r repeat-all-cohorts}
+
+get_inter_ext_events <- function(current_cohort) {
+  total_event_array <- total_event_array_lst[[current_cohort]]
+  active_event_array <- active_event_array_lst[[current_cohort]]
+  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+  return_df <- cleanObservationPeriod(current_cohort, 
+                                    full_data[[cohort_names[current_cohort]]],
+                                      clean_data)
+
+  start_win <- floor(max(return_df$observe.id) / 3) * (0:2) + 1
+  end_win <- floor(max(return_df$observe.id) / 3) * (1:3)
+  matrix1 <- apply(
+    total_event_array[, , start_win[1]:end_win[1]] -
+      active_event_array[, , start_win[1]:end_win[1]],
+    c(1, 2), sum
+  )
+  matrix2 <- apply(
+    total_event_array[, , start_win[2]:end_win[2]] -
+      active_event_array[, , start_win[2]:end_win[2]],
+    c(1, 2), sum
+  )
+  matrix3 <- apply(
+    total_event_array[, , start_win[3]:end_win[3]] -
+      active_event_array[, , start_win[3]:end_win[3]],
+    c(1, 2), sum
+  )
+
+  g_community1 <- graph_from_adjacency_matrix(matrix1, mode = "undirected")
+  lec1 <- cluster_leading_eigen(g_community1)
+
+  g_community2 <- graph_from_adjacency_matrix(matrix2, mode = "undirected")
+  lec2 <- cluster_leading_eigen(g_community2)
+
+  g_community3 <- graph_from_adjacency_matrix(matrix3, mode = "undirected")
+  lec3 <- cluster_leading_eigen(g_community3)
+
+  wind1_memb <- tibble(id = 1:12, memb = lec1$membership)
+
+  return_df %>% 
+    filter(observe.id >= start_winds$observe.id[1]) %>% 
+    filter(observe.id <= end_winds$observe.id[1]) %>% 
+    ### join with wind1_memb, tally
+    left_join(wind1_memb, by = c("initiator" = "id")) %>% 
+    left_join(wind1_memb, by = c("recipient" = "id")) %>% 
+    rename(send_clust = memb.x, 
+           rec_clust = memb.y) %>% 
+    group_by(send_clust, rec_clust) %>% 
+    summarise(num_events = sum(no.events)) %>% 
+    mutate(clust = if_else(send_clust == rec_clust, "internal", "external")) %>% 
+    group_by(clust) %>% 
+    summarise(events = sum(num_events)) %>% 
+    ungroup() %>% 
+    mutate(prop = events/sum(events))
+
+  wind2_memb <- tibble(id = 1:12, memb = lec2$membership)
+
+  return_df %>% 
+    filter(observe.id >= start_winds$observe.id[2]) %>% 
+    filter(observe.id <= end_winds$observe.id[2]) %>% 
+    ### join with wind1_memb, tally
+    left_join(wind2_memb, by = c("initiator" = "id")) %>% 
+    left_join(wind2_memb, by = c("recipient" = "id")) %>% 
+    rename(send_clust = memb.x, 
+           rec_clust = memb.y) %>% 
+    group_by(send_clust, rec_clust) %>% 
+    summarise(num_events = sum(no.events)) %>% 
+    mutate(clust = if_else(send_clust == rec_clust, "internal", "external")) %>% 
+    group_by(clust) %>% 
+    summarise(events = sum(num_events)) %>% 
+    ungroup() %>% 
+    mutate(prop = events/sum(events))
+
+  wind3_memb <- tibble(id = 1:12, memb = lec3$membership)
+
+  return_df %>% 
+    filter(observe.id >= start_winds$observe.id[3]) %>% 
+    filter(observe.id <= end_winds$observe.id[3]) %>% 
+    ### join with wind1_memb, tally
+    left_join(wind3_memb, by = c("initiator" = "id")) %>% 
+    left_join(wind3_memb, by = c("recipient" = "id")) %>% 
+    rename(send_clust = memb.x, 
+           rec_clust = memb.y) %>% 
+    group_by(send_clust, rec_clust) %>% 
+    summarise(num_events = sum(no.events)) %>% 
+    mutate(clust = if_else(send_clust == rec_clust, "internal", "external")) %>% 
+    group_by(clust) %>% 
+    summarise(events = sum(num_events)) %>% 
+    ungroup() %>% 
+    mutate(prop = events/sum(events))
+
+}
+
+get_inter_ext_events(current_cohort = 2)
 
@@
                    sim_eta_1 = 1.5,
-                   gamma_var = runif(n = num_nodes, min = 0.01, max = 0.05),
-                   zeta_var = runif(n = num_nodes, min = 0.01, max = 0.05),
+                   gamma_var = runif(n = num_nodes,
+                                     min = 0.01, max = 0.05),
+                   zeta_var = runif(n = num_nodes,
+                                    min = 0.01, max = 0.05),
                    sim_eta_2 = 0.6,
@@
 
+  if(ncol(lam0_draws) != sum(clean_sim_data$N_count >2)) {
+    stop("Mismatch between params and event pairs")
+  }
+
   lambda_0_est <- apply(lam0_draws, 2, mean)
@@
 m1_ks <- tibble(Method = "C-HP",
-       ks = as.vector(KS_model1_array))
+       ks = as.vector(KS_model1_array[sims, ,]))
 
 m2_ks <- tibble(Method = "C-DCHP",
-       ks = as.vector(KS_model2_array))
+       ks = as.vector(KS_model2_array[sims, ,]))
 
 m3_ks <- tibble(Method = "C-MMHP",
-       ks = as.vector(KS_model3_array))
+       ks = as.vector(KS_model3_array[sims, ,]))
 
 true_ks <- tibble(Method = "True",
-       ks = as.vector(KS_true_array))
+       ks = as.vector(KS_true_array[sims, ,]))
 
@@
 m1_pr <- tibble(Method = "C-HP",
-       pr = as.vector(PR_model1_array))
+       pr = as.vector(PR_model1_array[sims, ,]))
 
 m2_pr <- tibble(Method = "C-DCHP",
-       pr = as.vector(PR_model2_array))
+       pr = as.vector(PR_model2_array[sims, ,]))
 
 m3_pr <- tibble(Method = "C-MMHP",
-       pr = as.vector(PR_model3_array))
+       pr = as.vector(PR_model3_array[sims, ,]))
 
 true_pr <- tibble(Method = "True",
-                  pr = as.vector(PR_true_array))
+      pr = as.vector(PR_true_array[sims, ,]))
 

### 2021-06-23 run_scripts/sim_fits.R

@@ -30,9 +30,9 @@ source('lib/drawIntensity.R')
 #source('lib/cleanData.R')
 # Define global variable
 n_sim <- 1
-num_nodes <- 10
+num_nodes <- 5
 cut_off <- 3
-obs_time <- 100
+obs_time <- 50
 
 model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
   return(eta1 * x * y * exp(-eta2 * abs(x-y))/(1 + exp(-eta3 *(x-y))))})
@@ -194,13 +194,17 @@ print("model3")
 ## Fit in model 3
 start_time <- Sys.time()
 sim_model3_stan_fit3 <- model3$sample(data = data_list,
+                                      iter_warmup = 500,
                                       iter_sampling = 1000,
                                       chains = 4,
-                                      refresh = 100)
+                                      refresh = 50)
 m3_time <- Sys.time() - start_time
 
 sim_model3_fit_3 <- sim_model3_stan_fit3$draws()
 sim_model3_fit3_draws <- posterior::as_draws_df(sim_model3_fit_3)
+
+# save the summary
+stan_fit3_summ <- sim_model3_stan_fit3$summary()
 
 # }
 

### 2021-06-25 output_scripts/revisions_may.Rmd
fix a very important bug with the ks statistics for m3

@@
 ```{r load_cohort_rankings}
-for(cohort_id in 1:10){
+# for(cohort_id in 1:10){
+cohort_id <- 5
   start_rank <- readRDS(file = paste(data_path,
@@
          fill = "Time Period",
-         title = "Agreement between initial and later ranking",
-         subtitle = paste0("Cohort ", cohort_id))
+         title = "Agreement between Initial and Final Ranking",
+         subtitle = paste0("Cohort ", cohort_id)) +
+    scale_fill_discrete(labels = c("First 14 Days", "Final 14 Days"))
   print(coh_plot)
-}
+# }
 
@@
       KS_model3_array[s, i, j] <- ks.test(Lambda.test, "pexp")$statistic
-      KS_p_model3_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
+      KS_p_model3_array[s, i, j] <- ks.test(Lambda.test, "pexp")$p.value
       state.est.latent.mmhp <- interpolate_state_est_lst[i, j][[1]]
@@
 
+```{r ks-p-value}
+
+m1_ks_p <- tibble(Method = "C-HP",
+       ks = as.vector(KS_p_model1_array[sims, ,]))
+
+m2_ks_p <- tibble(Method = "C-DCHP",
+       ks = as.vector(KS_p_model2_array[sims, ,]))
+
+m3_ks_p <- tibble(Method = "C-MMHP",
+       ks = as.vector(KS_p_model3_array[sims, ,]))
+
+true_ks_p <- tibble(Method = "True",
+       ks = as.vector(KS_p_true_array[sims, ,]))
+
+all_ks_p <- m1_ks_p %>% 
+  bind_rows(m2_ks_p) %>% 
+  bind_rows(m3_ks_p) %>% 
+  bind_rows(true_ks_p)
+
+all_ks_p$Method <- factor(all_ks_p$Method, levels = c("C-HP",
+                                                "C-DCHP",
+                                                "C-MMHP",
+                                                "True") )
+
+all_ks_p %>% 
+  filter(ks != 0) %>% 
+  mutate(log_p = -log(ks)) %>% 
+  ggplot(aes(log_p)) + 
+  geom_histogram(aes(fill = Method)) +
+  scale_fill_manual(values = cols_plot) +
+  labs(y = "Negative Log KS Statistic P Value") +
+  facet_wrap(~Method)
+
+```
+
 ```{r take-mean-ks/pr}

### 2021-06-25 output_scripts/revisions_may.Rmd
update to also plot p values, try design better simulation study

@@
 
+all_ks_p %>% ggplot(aes(Method, ks)) +
+  geom_boxplot(aes(fill = Method)) +
+  scale_fill_manual(values = cols_plot) +
+  labs(y = "P Value", title = "All Simulations")
+
 all_ks_p %>% 
   filter(ks != 0) %>% 
-  mutate(log_p = -log(ks)) %>% 
+  # mutate(log_p = -log(ks)) %>% 
   ggplot(aes(log_p)) + 
@@
   facet_wrap(~Method)
+
+### repeat for 1 simulation
+sims <- 12
+m1_ks_p <- tibble(Method = "C-HP",
+       ks = as.vector(KS_p_model1_array[sims, ,]))
+
+m2_ks_p <- tibble(Method = "C-DCHP",
+       ks = as.vector(KS_p_model2_array[sims, ,]))
+
+m3_ks_p <- tibble(Method = "C-MMHP",
+       ks = as.vector(KS_p_model3_array[sims, ,]))
+
+true_ks_p <- tibble(Method = "True",
+       ks = as.vector(KS_p_true_array[sims, ,]))
+
+all_ks_p <- m1_ks_p %>% 
+  bind_rows(m2_ks_p) %>% 
+  bind_rows(m3_ks_p) %>% 
+  bind_rows(true_ks_p)
+
+all_ks_p$Method <- factor(all_ks_p$Method, levels = c("C-HP",
+                                                "C-DCHP",
+                                                "C-MMHP",
+                                                "True") )
+
+all_ks_p %>% ggplot(aes(Method, ks)) +
+  geom_boxplot(aes(fill = Method)) +
+  scale_fill_manual(values = cols_plot) +
+  labs(y = "P Value", title = "single simulation")
 

### 2021-06-25 sim_design/simulation_design.R

@@ -27,9 +27,9 @@ source('lib/drawIntensity.R')
 #source('lib/cleanData.R')
 # Define global variable
 n_sim <- 1
-num_nodes <- 10
+num_nodes <- 5
 cut_off <- 3
-obs_time <- 100
+obs_time <- 50
 
 model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
   return(eta1 * x * y * exp(-eta2 * abs(x-y))/(1 + exp(-eta3 *(x-y))))})
@@ -48,10 +48,10 @@ object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
   q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
 
 object_par <- list(sim_lambda_1 = 0.4,
-                   gamma_var = rep(0.15, num_nodes),
-                   zeta_var = rep(0.15, num_nodes),
+                   gamma_var = seq(from = 0.01, to = 0.2, length.out = num_nodes),
+                   zeta_var = rep(0.1, num_nodes),
                    sim_eta_1 = 1.5, # from 3.5
-                   sim_eta_2 = 1.5, # from 2.6
+                   sim_eta_2 = 0,#1.5, # from 2.6
                    sim_eta_3 = 2, # this seems better
                    #sim_eta_3 = 7.5,
                    sim_beta = 1.5, # from 2

### 2021-06-25 run_scripts/sim_fits.R
testing and debugging the simulation fits

@@ -51,14 +51,17 @@ object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
                   q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
 
 object_par <- list(sim_lambda_1 = 0.4,
-                   gamma_var = seq(from = 0.01, to = .2, length.out = num_nodes),
+                   gamma_var = seq(from = 0.01,
+                                    to = .2,
+                                   length.out = num_nodes),
                    zeta_var = rep(0.1, num_nodes),
                    sim_eta_1 = 1.5, # from 3.5
                    sim_eta_2 = 1.5, # from 2.6
                    sim_eta_3 = 2, # this seems better
                    #sim_eta_3 = 7.5,
                    sim_beta = 1.5, # from 2
-                   f_vec_1 = seq(from = 0.05, to = 0.95,
+                   f_vec_1 = seq(from = 0.10,
+                                 to = 0.9,
                                  length.out = num_nodes))
 
 

### 2021-06-25 sim_design/check_sims.R

@@ -16,10 +16,20 @@ sim_data_path <- here("output", "revisions", "sim_design", "/")
 #                    f_vec_1 = seq(from = 0.05, to = 0.95,
 #                                  length.out = num_nodes))
 
-sim_id <- 9
+sim_id <- 10
 load(paste(sim_data_path,"sim_model3_sim123_",
                   sim_id,
                   ".RData",sep=''))
+
+sim_fit1_draws <- sim_model3_stan_sim1
+sim_fit2_draws <- sim_model3_stan_sim2
+sim_fit3_draws <- sim_model3_stan_sim3
+
+
+# sim_model3_stan_sim1 <- sim_fit1_draws
+# sim_model3_stan_sim2 <- sim_fit2_draws
+# sim_model3_stan_sim3 <- sim_fit3_draws
+
 
 
 ####

### 2021-06-28 output_scripts/Paper_Plots.Rmd
working on redoing the paper plots

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
-                      dev = 'png', fig.height = 4.5, fig.width = 7,
-                      warning = FALSE)
+knitr::opts_chunk$set(
+  echo = TRUE, fig.path = "paper_figure/",
+  dev = "png", fig.height = 4.5, fig.width = 7,
+  warning = FALSE
+)
 
@@
 extra_plots <- FALSE
+
+revision_plots <- TRUE
+original_plots <- FALSE
+### original plots for plots which are no longer needed, 
+### revision plots are what required
+
 current_cohort <- 5
@@
 library(rstan)
-Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
+Sys.setenv(LOCAL_CPPFLAGS = "-march=corei7 -mtune=corei7")
 options(mc.cores = parallel::detectCores())
@@
 library(colorspace)
-source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
-source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
-source(paste(func_dir,'cleanData.R',sep = "")) 
-source(paste(func_dir,'prepareDataStan.R',sep = "")) 
-source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
-source(paste(func_dir,'plotUtil.R',sep = "")) 
-source(paste(func_dir,'mmhp.R',sep = ""))
-source(paste(func_dir,'uniHawkes.R',sep = ""))
-source(paste(func_dir,'simulatePrediction.R',sep = ""))
-source(paste(func_dir,'myGlicko.R',sep = ""))
-source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
-source(paste(func_dir,'residualStructureScore.R',sep = ""))
-source(paste(func_dir,'drawIntensity.R',sep =""))
+source(paste(func_dir, "naiveRankHierarchy.R", sep = ""))
+source(paste(func_dir, "expertRankHierarchy.R", sep = ""))
+source(paste(func_dir, "cleanData.R", sep = ""))
+source(paste(func_dir, "prepareDataStan.R", sep = ""))
+source(paste(func_dir, "inferLatentMmhp.R", sep = ""))
+source(paste(func_dir, "plotUtil.R", sep = ""))
+source(paste(func_dir, "mmhp.R", sep = ""))
+source(paste(func_dir, "uniHawkes.R", sep = ""))
+source(paste(func_dir, "simulatePrediction.R", sep = ""))
+source(paste(func_dir, "myGlicko.R", sep = ""))
+source(paste(func_dir, "matrixPlotParameter.R", sep = ""))
+source(paste(func_dir, "residualStructureScore.R", sep = ""))
+source(paste(func_dir, "drawIntensity.R", sep = ""))
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
 
-cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cohort_names <- paste("cohort", c(9, 10, 12, 15, 16, 17, 18, 37, 38, 45),
+                      sep = "")
+cohort_short_names <- paste("C", c(9, 10, 12, 15, 16, 17, 18, 37, 38, 45),
+                            sep = "")
 cut_off <- 3
 mice_number <- 12
-
-```
-
-```{r load rankings,echo=FALSE,include=FALSE,results='hide',cache=TRUE}
+```
+
+```{r load rankings, echo=FALSE, include=FALSE, results='hide', cache=TRUE}
 full_data <- readRDS("../data/mice.RData")
@@
 expert_rank_10 <- list()
-out <- captureOutput(for(curr_cohort in fit_cohorts){
+out <- captureOutput(for (curr_cohort in fit_cohorts) {
   naive_rank_10[[curr_cohort]] <-
@@
 })
-
-```
-
-```{r define_functions}
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1 +
-                                                        exp(-eta3*(x-y))))})
-
-model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
-                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
-                  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
-
-```
-
-```{r creat colour df}
-col_df <- tibble(method = c("I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
-            "C-HP", "C-DCHP", "True", "C-MMHP"),
-            cols = viridis(9))
-
+```
+
+```{r define_functions, eval=revision_plots, include=FALSE}
+model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3) {
+  return(eta1 * x * y * exp(-eta2 * abs(x - y)) / (1 +
+    exp(-eta3 * (x - y))))
+})
+
+model3_fn <- list(
+  alpha.fun = function(x, y, eta1, eta2) {
+    return(eta1 * x * y * exp(-eta2 * abs(x - y)))
+  },
+  q1.fun = function(x, y, eta3) {
+    return(exp(-eta3 * x))
+  },
+  q0.fun = function(x, y, eta3) {
+    return(exp(-eta3 * y))
+  }
+)
+```
+
+```{r creat colour df, eval=revision_plots, include=FALSE}
+col_df <- tibble(
+  method = c(
+    "I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
+    "C-HP", "C-DCHP", "True", "C-MMHP"
+  ),
+  cols = viridis(9)
+)
 ```
@@
 
-```{r fig-2a-contour-plot}
+```{r fig-2a-contour-plot, eval=revision_plots}
 current_cohort <- 5
-#png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
-load(paste(data_path,cohort_names[current_cohort],
-           "/cohort_hp_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
+# png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
+load(paste(data_path, cohort_names[current_cohort],
+  "/cohort_hp_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
 eta1_mean <- mean(sim_cohort_hp$eta_1)
@@
 eta3_mean <- mean(sim_cohort_hp$eta_3)
-z.func <- function(x,y){
-  return(x*y*eta1_mean*exp(-eta2_mean*abs(x-y))/(1+exp(-eta3_mean*(y-x))))
+z.func <- function(x, y) {
+  return(x * y * eta1_mean *
+           exp(-eta2_mean * abs(x - y)) / (1 + exp(-eta3_mean * (y - x))))
   # this is because axes are flipped that we have y-x in last term
-  #return(x*y*eta1_mean/(1+exp(eta2_mean*abs(x-y)-eta3_mean*(y-x))))
-}
-z_plot <- outer(seq(1,0,-0.01),  
-                seq(0,1,0.01), 
-                z.func)
-my.image.plot(seq(0,1,0.01), seq(0,1,0.01), z_plot,
-              xlab=expression(f[j]),ylab=expression(f[i]),
-              my.main="(a)", cex.main=2.3, 
-              cex.lab=2.5, xLabels=c(1,0), yLabels=c(0,1))
-
+  # return(x*y*eta1_mean/(1+exp(eta2_mean*abs(x-y)-eta3_mean*(y-x))))
+}
+z_plot <- outer(
+  seq(1, 0, -0.01),
+  seq(0, 1, 0.01),
+  z.func
+)
+my.image.plot(seq(0, 1, 0.01), seq(0, 1, 0.01), z_plot,
+  xlab = expression(f[j]), ylab = expression(f[i]),
+  my.main = "(a)", cex.main = 2.3,
+  cex.lab = 2.5, xLabels = c(1, 0), yLabels = c(0, 1)
+)
 ```
@@
 
-```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE}
+```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE, eval=revision_plots}
 # current_cohort <- 5
 
-load(paste(data_path,cohort_names[current_cohort],
-           "/cohort_hp_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
+load(paste(data_path, cohort_names[current_cohort],
+  "/cohort_hp_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
 eta1_mean <- mean(sim_cohort_hp$eta_1)
@@
 eta3_mean <- mean(sim_cohort_hp$eta_3)
-f_est <- apply(sim_cohort_hp$f,2,mean)
+f_est <- apply(sim_cohort_hp$f, 2, mean)
 clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-return_df <- cleanObservationPeriod(current_cohort, clean_data)
-unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
-  dplyr::summarize(count=n(),
-                   observe=list(observe.id),
-                   observe.length=list(observe.time),
-                   no.events=list(no.events))
-unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
-
-ks.stat.matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
-n_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
-Lambda_matrix <- matrix(list(),nrow=mice_number,ncol=mice_number)
-for(k in 1:mice_number){
-  for(l in c(1:mice_number)[-k]){
-    i<-expert_rank_10[[current_cohort]][k]
-    j<-expert_rank_10[[current_cohort]][l]
-    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
-    if(length(pair)>0){
-      param_mean <- list(lambda0=mean(sim_cohort_hp$lambda0),
-                         alpha=model1_fn$alpha.fun(f_est[i],
+return_df <- cleanObservationPeriod(current_cohort,
+  raw_df =
+    full_data[[cohort_names[current_cohort]]],
+  clean_data
+)
+unique_pairs_df <- return_df %>%
+  group_by(initiator, recipient) %>%
+  dplyr::summarize(
+    count = n(),
+    observe = list(observe.id),
+    observe.length = list(observe.time),
+    no.events = list(no.events)
+  )
+unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])
+
+ks.stat.matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
+n_matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
+Lambda_matrix <- matrix(list(), nrow = mice_number, ncol = mice_number)
+for (k in 1:mice_number) {
+  for (l in c(1:mice_number)[-k]) {
+    i <- expert_rank_10[[current_cohort]][k]
+    j <- expert_rank_10[[current_cohort]][l]
+    pair <- which(unique_pairs_df$initiator == i & 
+                    unique_pairs_df$recipient == j)
+    if (length(pair) > 0) {
+      param_mean <- list(
+        lambda0 = mean(sim_cohort_hp$lambda0),
+        alpha = model1_fn$alpha.fun(
+          f_est[i],
           f_est[j],
@@
           eta2_mean,
-                                                   eta3_mean),
-                         beta=mean(sim_cohort_hp$beta))
+          eta3_mean
+        ),
+        beta = mean(sim_cohort_hp$beta)
+      )
       current_window_vec <- unique_pairs_df$observe[[pair]]
       all_Lambda <- numeric(0)
-      for(cur in c(1:length(current_window_vec))){ ## check length > 2
+      for (cur in c(1:length(current_window_vec))) { ## check length > 2
         cur_win <- current_window_vec[cur]
-        current_event_time <- return_df[return_df$initiator==i&
+        current_event_time <- return_df[return_df$initiator == i &
           return_df$recipient == j &
-                            return_df$observe.id==cur_win,"event.times"][[1]]
-        current_obs_time <- return_df[return_df$initiator==i&
-                                        return_df$recipient==j&
-                            return_df$observe.id==cur_win,"observe.time"]
-        Lambda_vec <- uniHawkesCompensator(object = param_mean,
-                              events = c(current_event_time,
-                                         current_obs_time))
-        all_Lambda <- c(all_Lambda,Lambda_vec)
-        n_matrix[i,j] <- n_matrix[i,j] + length(current_event_time)
-      }
-      if(length(all_Lambda)>0){
-        ks.stat.matrix[i,j] <-  ks.test(all_Lambda,"pexp",
-                                        rate = 1/mean(all_Lambda))$statistic
-        Lambda_matrix[i,j][[1]] <- all_Lambda
-      }
-    }
-  }
-}
-
-# png(paste(plot_path,"/diagonsis_model1_",cohort_names[current_cohort],".png",sep=''),
+          return_df$observe.id == cur_win, "event.times"][[1]]
+        current_obs_time <- return_df[return_df$initiator == i &
+          return_df$recipient == j &
+          return_df$observe.id == cur_win, "observe.time"]
+        Lambda_vec <- uniHawkesCompensator(
+          object = param_mean,
+          events = c(
+            current_event_time,
+            current_obs_time
+          )
+        )
+        all_Lambda <- c(all_Lambda, Lambda_vec)
+        n_matrix[i, j] <- n_matrix[i, j] + length(current_event_time)
+      }
+      if (length(all_Lambda) > 0) {
+        ks.stat.matrix[i, j] <- ks.test(all_Lambda, "pexp",
+          rate = 1 / mean(all_Lambda)
+        )$statistic
+        Lambda_matrix[i, j][[1]] <- all_Lambda
+      }
+    }
+  }
+}
+#
+# png(paste(plot_path,
+#           "/diagonsis_model1_",
+#           cohort_names[current_cohort],
+#           ".png",
+#           sep = ''),
 #     width=480,height=480)
@@
 col.vec <- cRamp(as.vector(ks.stat.matrix))
-## need to do some sort of transformation between these here
+# need to do some sort of transformation between these here
 vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
-#order(as.vector(ks.stat.matrix),method = "")
+# order(as.vector(ks.stat.matrix),method = "")
 
@@
 sorted_vals <- sort(ks.stat.matrix)
-#match(values,sorted_vals)
-col.vec.vir <- vir_cols[match(values,sorted_vals)]
+# match(values,sorted_vals)
+col.vec.vir <- vir_cols[match(values, sorted_vals)]
 
 ####
-par(oma = c(6,4,4,1), mar=rep(0,4),
-    mgp = c(0, .2, 0))
-layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
-                    byrow = TRUE),rep(12*12+1,12)), 
-       widths=c(rep(1,12),2), heights=rep(1,12))
-for(i in expert_rank_10[[current_cohort]]){
-  for(j in expert_rank_10[[current_cohort]]){
-    if(ks.stat.matrix[i,j]==0){
-      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
-           axes = FALSE, frame=TRUE)
-      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
-           border = 0, col = 'white')
-    }else{
-      Lambda.test <- Lambda_matrix[i,j][[1]]
-      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
-            ylab="",xlab="",axes = FALSE, frame=TRUE)
-      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], 
-           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
-      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
-            ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
-      plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
-           verticals = TRUE, col = "red", lwd = 2)
-    }
-  }
-}
-par(mar = c(0,2,0,3),mgp=c(0,0.8,0))
+par(
+  oma = c(6, 4, 4, 1), mar = rep(0, 4),
+  mgp = c(0, .2, 0)
+)
+layout(cbind(matrix(
+  data = c(1:(12 * 12)), nrow = 12, ncol = 12,
+  byrow = TRUE
+), rep(12 * 12 + 1, 12)),
+widths = c(rep(1, 12), 2), heights = rep(1, 12)
+)
+for (i in expert_rank_10[[current_cohort]]) {
+  for (j in expert_rank_10[[current_cohort]]) {
+    if (ks.stat.matrix[i, j] == 0) {
+      plot(0, 0,
+        xlim = c(0, 5), ylim = c(0, 5), type = "n", xlab = "", ylab = "",
+        axes = FALSE, frame = TRUE
+      )
+      rect(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[4],
+        border = 0, col = "white"
+      )
+    } else {
+      Lambda.test <- Lambda_matrix[i, j][[1]]
+      curve(pexp(x, 1 / mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
+        ylab = "", xlab = "", axes = FALSE, frame = TRUE
+      )
+      rect(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[4],
+        border = 0, col = col.vec.vir[matrixToVecIdx(i, j, mice_number)]
+      )
+      curve(pexp(x, 1 / mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
+        ylab = "", xlab = "", axes = FALSE, frame = TRUE, add = TRUE, lwd = 2
+      )
+      plot(ecdf(Lambda.test),
+        add = TRUE, do.points = FALSE,
+        verticals = TRUE, col = "red", lwd = 2
+      )
+    }
+  }
+}
+par(mar = c(0, 2, 0, 3), mgp = c(0, 0.8, 0))
 m1_ks <- ks.stat.matrix
-col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)),length.out = 100),
-                col.vec = viridis(100))
+col_obj <- list(
+  x.vec = seq(0, max(as.vector(ks.stat.matrix)), length.out = 100),
+  col.vec = viridis(100)
+)
 
 temp <- cLegend(as.vector(ks.stat.matrix))
-#which(temp$x.vec == as.vector(ks.stat.matrix))
+# which(temp$x.vec == as.vector(ks.stat.matrix))
 ## need to adjust this for the legend also.
@@
 image(1, col_obj$x.vec,
-      matrix(data=col_obj$x.vec, 
-             ncol=length(col_obj$x.vec),nrow=1),
-      col=col_obj$col.vec,
-      xlab="",ylab="", axes = FALSE)
-axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1,
-     cex.axis=2.4)
-
-mtext(text=expert_rank_10[[current_cohort]],
+  matrix(
+    data = col_obj$x.vec,
+    ncol = length(col_obj$x.vec), nrow = 1
+  ),
+  col = col_obj$col.vec,
+  xlab = "", ylab = "", axes = FALSE
+)
+axis(4,
+  at = c(0, 0.3, 0.6), labels = c(0, 0.3, 0.6), las = HORIZONTAL <- 1,
+  cex.axis = 2.4
+)
+
+mtext(
+  text = expert_rank_10[[current_cohort]],
   side = 1, line = 1.8, outer = TRUE, cex = 1.8,
-      at=1/14*c(1:12)-1/22)
-mtext(text = expert_rank_10[[current_cohort]],
+  at = 1 / 14 * c(1:12) - 1 / 22
+)
+mtext(
+  text = expert_rank_10[[current_cohort]],
   side = 2, line = 0.5, outer = TRUE, cex = 1.8,
-      at =1/12*c(12:1)-1/20, las = 2)
-mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE,
+  at = 1 / 12 * c(12:1) - 1 / 20, las = 2
+)
+mtext(
+  text = "(b)", side = 3, line = 1.4, outer = TRUE,
   cex = 2.2,
-      at=0.45, font=2)
-#dev.off()
+  at = 0.45, font = 2
+)
+# dev.off()
 ```
@@
 
-```{r fig-3a-baseline-rate}
+```{r fig-3a-baseline-rate, eval=revision_plots}
 # current_cohort <- 5
 
-load(paste(data_path,cohort_names[current_cohort],
-           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
-gamma_mean <- apply(sim_cohort_dchp$gamma,2,mean)
-zeta_mean <- apply(sim_cohort_dchp$zeta,2,mean)
+load(paste(data_path, cohort_names[current_cohort],
+  "/cohort_dchp_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+gamma_mean <- apply(sim_cohort_dchp$gamma, 2, mean)
+zeta_mean <- apply(sim_cohort_dchp$zeta, 2, mean)
 
@@
 latent_social_matrix <- gamma_mean %*%
-  t(rep(1,mice_number)) + rep(1,mice_number) %*% t(zeta_mean)
+  t(rep(1, mice_number)) + rep(1, mice_number) %*% t(zeta_mean)
 
@@
   rev(expert_rank_10[[current_cohort]]),
-                                         expert_rank_10[[current_cohort]]],
-                    xLabels=expert_rank_10[[current_cohort]],
-                    yLabels=rev(expert_rank_10[[current_cohort]]) )
+  expert_rank_10[[current_cohort]]
+],
+xLabels = expert_rank_10[[current_cohort]],
+yLabels = rev(expert_rank_10[[current_cohort]])
+)
 # title = "(a)" )
@@
 #       at=1/17.8*seq(2,12,2)+0.09)
-#dev.off()
-```
+# dev.off()
+```
+
 ## Figure 3b: Ranking Comparison
 
-```{r fig-3b-rank-comparison, include=FALSE,eval=FALSE}
+```{r fig-3b-rank-comparison, include=FALSE,eval=original_plots}
 # current_cohort <- 5
-
-colors_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP")) %>%
+colors_plot <- col_df %>%
+  filter(method %in% c("C-HP", "C-DCHP")) %>%
   pull(cols)
-load(paste(data_path,cohort_names[current_cohort],
-           "/cohort_hp_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
-load(paste(data_path,cohort_names[current_cohort],
-           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
+load(paste(data_path,
+  cohort_names[current_cohort],
+  "/cohort_hp_stan_result_",
+  cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+load(paste(data_path,
+  cohort_names[current_cohort],
+  "/cohort_dchp_stan_result_",
+  cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
 # png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
 #     width=400, height=300)
-par(oma = c(0,0,2,0), mar = c(3,4,1,1),mgp=c(0,0.5,0))
+par(oma = c(0, 0, 2, 0), mar = c(3, 4, 1, 1), mgp = c(0, 0.5, 0))
 plot(order(expert_rank_10[[current_cohort]]),
-     apply(sim_cohort_hp$f,2,mean),pch=16,cex=1.2,
-     #col= "steelblue",
+  apply(sim_cohort_hp$f, 2, mean),
+  pch = 16, cex = 1.2,
+  # col= "steelblue",
   col = colors_plot[1],
-     ylab="",xlab="",
-     xlim=c(1,12.5),ylim=c(0,1), xaxt="n", yaxt="n")
+  ylab = "", xlab = "",
+  xlim = c(1, 12.5), ylim = c(0, 1),
+  xaxt = "n", yaxt = "n"
+)
 segments(order(expert_rank_10[[current_cohort]]),
-         apply(sim_cohort_hp$f,2,mean)-apply(sim_cohort_hp$f,2,sd),
+  apply(sim_cohort_hp$f, 2, mean) -
+    apply(sim_cohort_hp$f, 2, sd),
   order(expert_rank_10[[current_cohort]]),
-         apply(sim_cohort_hp$f,2,mean)+apply(sim_cohort_hp$f,2,sd),
-         #col= add.alpha("steelblue",0.8),lwd=2)
-         col = add.alpha(colors_plot[1],0.8), lwd =2)
-points(order(expert_rank_10[[current_cohort]])+0.2,
-       apply(sim_cohort_dchp$f,2,mean),
-       pch=16,cex=1.2,
-       col=colors_plot[2])
-       #col="goldenrod2")
-segments(order(expert_rank_10[[current_cohort]])+0.2,
-         apply(sim_cohort_dchp$f,2,mean)-apply(sim_cohort_dchp$f,2,sd),
-         order(expert_rank_10[[current_cohort]])+0.2,
-         apply(sim_cohort_dchp$f,2,mean)+apply(sim_cohort_dchp$f,2,sd),
-         col= add.alpha(colors_plot[2],0.8),lwd=2)
-         #col= add.alpha("goldenrod2",0.8),lwd=2)
-
-axis(BELOW<-1, at=1:12, labels=expert_rank_10[[current_cohort]], cex.axis=1.3, tck=-0.015)
-#mtext(text=11, side=1, line=0.5, cex=1.3, at=6)
-
-axis(LEFT <-2, at=seq(0,1,0.2), labels=seq(0,1,0.2), las= HORIZONTAL<-1,
-     cex.axis=1.3, tck=-0.015)
-mtext(side=1, text="I&SI rank", line=1.8, cex=1.5)
-mtext(side=2, text="Latent rank", line=2.4, cex=1.6)
-mtext(side=3, text="(b)", line=0.8, cex=1.6, font=2)
-legend('bottomleft', legend = c("C-HP", "C-DCHP"),
-       pch = c(16, 16), lty = c(1, 1), lwd=c(2,2),
-       #col=c("steelblue","goldenrod"),
-       col=c(colors_plot[1],colors_plot[2]),
-       cex=1.5)
-#dev.off()
+  apply(sim_cohort_hp$f, 2, mean) +
+    apply(sim_cohort_hp$f, 2, sd),
+  # col= add.alpha("steelblue",0.8),lwd=2)
+  col = add.alpha(colors_plot[1], 0.8), lwd = 2
+)
+points(order(expert_rank_10[[current_cohort]]) + 0.2,
+  apply(sim_cohort_dchp$f, 2, mean),
+  pch = 16,
+  cex = 1.2,
+  col = colors_plot[2]
+)
+# col="goldenrod2")
+segments(order(expert_rank_10[[current_cohort]]) + 0.2,
+  apply(sim_cohort_dchp$f, 2, mean) - apply(sim_cohort_dchp$f, 2, sd),
+  order(expert_rank_10[[current_cohort]]) + 0.2,
+  apply(sim_cohort_dchp$f, 2, mean) + apply(sim_cohort_dchp$f, 2, sd),
+  col = add.alpha(colors_plot[2], 0.8), lwd = 2
+)
+# col= add.alpha("goldenrod2",0.8),lwd=2)
+
+axis(BELOW <- 1, at = 1:12, 
+     labels = expert_rank_10[[current_cohort]],
+     cex.axis = 1.3,
+     tck = -0.015)
+# mtext(text=11, side=1, line=0.5, cex=1.3, at=6)
+
+axis(LEFT <- 2,
+  at = seq(0, 1, 0.2), labels = seq(0, 1, 0.2), las = HORIZONTAL <- 1,
+  cex.axis = 1.3, tck = -0.015
+)
+mtext(side = 1, text = "I&SI rank", line = 1.8, cex = 1.5)
+mtext(side = 2, text = "Latent rank", line = 2.4, cex = 1.6)
+mtext(side = 3, text = "(b)", line = 0.8, cex = 1.6, font = 2)
+legend("bottomleft",
+  legend = c("C-HP", "C-DCHP"),
+  pch = c(16, 16), lty = c(1, 1), lwd = c(2, 2),
+  # col=c("steelblue","goldenrod"),
+  col = c(colors_plot[1], colors_plot[2]),
+  cex = 1.5
+)
+# dev.off()
 ```
@@
 ```{r, eval=FALSE, include=FALSE}
-par(mar=c(3,3,1,1))
-plot(as.vector(n_matrix[n_matrix>0]), as.vector(ks.stat.matrix[n_matrix>0]),
-     xlab="", ylab="", pch=16, col="gray", cex= 0.8, xaxt="n", yaxt="n",
-     ylim=c(0,0.65))
-mtext("Number of events", cex=1.5, side=1, line=1.8)
-mtext("K-S statistics", cex=1.5, side=2, line=1.5)
-mgp.axis(1,mgp=c(0,0.3,0),at=seq(0,120,10),cex.axis=1,lwd=0,lwd.ticks=0.1)
-mgp.axis(2,mgp=c(0,0.1,0),at=seq(-0.2,0.6,0.2),cex.axis=1,lwd=0,lwd.ticks=0.8)
+## need Hmisc for this
+
+par(mar = c(3, 3, 1, 1))
+plot(as.vector(n_matrix[n_matrix > 0]),
+     as.vector(ks.stat.matrix[n_matrix > 0]),
+     xlab = "",
+     ylab = "",
+     pch = 16,
+     col = "gray",
+     cex = 0.8,
+     xaxt = "n",
+     yaxt = "n",
+  ylim = c(0, 0.65)
+)
+mtext("Number of events", cex = 1.5, side = 1, line = 1.8)
+mtext("K-S statistics", cex = 1.5, side = 2, line = 1.5)
+mgp.axis(1, mgp = c(0, 0.3, 0),
+         at = seq(0, 120, 10),
+         cex.axis = 1,
+         lwd = 0,
+         lwd.ticks = 0.1)
+mgp.axis(2, mgp = c(0, 0.1, 0),
+         at = seq(-0.2, 0.6, 0.2),
+         cex.axis = 1,
+         lwd = 0,
+         lwd.ticks = 0.8)
 ```
@@
 ## Figure 4a Recover Latent Ranks
-```{r fig-4a, fig.height=3.5,fig.width=8}
+```{r fig-4a, fig.height=3.5, fig.width=8, eval=original_plots}
 sim_data_path <- "../output/sims_m3_update/"
@@
 m3_files <- list.files(sim_data_path, pattern = "sim_model3_fit*")
-#m1_files
+# m1_files
 
@@
 
-for(i in seq_along(m3_files)) {
-  load(paste0(sim_data_path,m3_files[i]))
+for (i in seq_along(m3_files)) {
+  load(paste0(sim_data_path, m3_files[i]))
   sim_model3_stan_sim1_total[[i]] <- sim_model3_stan_sim1
@@
   sim_model3_stan_sim3_total[[i]] <- sim_model3_stan_sim3
-
 }
@@
 
-#png(paste(plot_path,"sim_latent_recover.png",sep=""), height=500, width=900)
-par(mfrow=c(3, length(object_par$f_vec_1)),
-    mar=c(0,0,1,0),
-    oma=c(6.5,11,3.5,1))
-
-y.ub <- c(12,12,12,12,12)
-text.y <- c(rep(8,4),8)
-text.x <- c(0.1,0.2,0.4,0.7,0.9)
-text.x.adj <- c(0.3,0.4,0.6,0.5,0.8)
-
-model_colors <- col_df %>% filter(method %in% c("C-HP",
-                                                "C-DCHP", "C-MMHP")) %>%
+# png(paste(plot_path,"sim_latent_recover.png",sep=""), height=500, width=900)
+par(
+  mfrow = c(3, length(object_par$f_vec_1)),
+  mar = c(0, 0, 1, 0),
+  oma = c(6.5, 11, 3.5, 1)
+)
+
+y.ub <- c(12, 12, 12, 12, 12)
+text.y <- c(rep(8, 4), 8)
+text.x <- c(0.1, 0.2, 0.4, 0.7, 0.9)
+text.x.adj <- c(0.3, 0.4, 0.6, 0.5, 0.8)
+
+model_colors <- col_df %>%
+  filter(method %in% c(
+    "C-HP",
+    "C-DCHP", "C-MMHP"
+  )) %>%
   pull(cols)
 
-for(m in c(1:3)){
-  for(j in c(1:length(object_par$f_vec_1))){
-    plot(1,4,xlim=c(0,1),ylim=c(0,y.ub[j]),
-         type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+for (m in c(1:3)) {
+  for (j in c(1:length(object_par$f_vec_1))) {
+    plot(1, 4,
+      xlim = c(0, 1), ylim = c(0, y.ub[j]),
+      type = "n", xlab = "",
+      ylab = "", xaxt = "n",
+      yaxt = "n", axes = FALSE
+    )
 
@@
     # current_result <- eval(parse(text=paste("sim_model3_stan_sim",m,sep="")))
-    current_result <- eval(parse(text=paste("sim_model3_stan_sim",
+    current_result <- eval(parse(text = paste("sim_model3_stan_sim",
       m,
       "_total",
-                                            sep="")))
-    for(i in c(1:n_sim)){
-      lines(density(current_result[[i]]$f[,j]),
-            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
+      sep = ""
+    )))
+    for (i in c(1:n_sim)) {
+      lines(density(current_result[[i]]$f[, j]),
+        col = add.alpha(model_colors[m], alpha = 0.8), cex = 0.6, lwd = 0.8
+      )
     }
@@
     ## plot true value
-    abline(v=object_par$f_vec_1[j],lwd=1.8,lty=2,col="gray30")
+    abline(v = object_par$f_vec_1[j], lwd = 1.8, lty = 2, col = "gray30")
 
@@
     box.col <- "black"
-    box(lty = 'solid',col=box.col,lwd=0.7)
-
-    if(m==3){
-      text(text.x.adj[j],text.y[j],text.x[j],cex=2.4)
+    box(lty = "solid", col = box.col, lwd = 0.7)
+
+    if (m == 3) {
+      text(text.x.adj[j], text.y[j], text.x[j], cex = 2.4)
     }
@@
   ## bottom
-  mtext(text = expression(f[1],f[2],f[3],f[4],f[5]), 
+  mtext(
+    text = expression(f[1], f[2], f[3], f[4], f[5]),
     side = 1, line = 2.4, outer = TRUE,
-        at = c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
-        cex = 2)
-  mtext(text = "Latent rank variables", side = 1,
+    at = c(1:length(object_par$f_vec_1)) / length(object_par$f_vec_1) - 0.1,
+    cex = 2
+  )
+  mtext(
+    text = "Latent rank variables", side = 1,
     line = 5.3,
@@
     cex = 2.25,
-        at = 0.5)
+    at = 0.5
+  )
   ## top
-  mtext(text = "(a)", side = 3,
+  mtext(
+    text = "(a)", side = 3,
     line = 0,
@@
     cex = 2.5,
-        at = 0.5, font = 2)
+    at = 0.5, font = 2
+  )
   ## left
-  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5, outer=TRUE, 
-        at=c(0:2)/3+0.15,
-        cex=1.75, las=2)
-}
-
-```
-```{r fig4a-new-hist, fig.height=3.5,fig.width=8}
-model_colors <- col_df %>% filter(method %in% c("C-HP",
+  mtext(
+    text = rev(c("C-HP  ", "C-DCHP", "C-MMHP")),
+    side = 2,
+    line = 0.5,
+    outer = TRUE,
+    at = c(0:2) / 3 + 0.15,
+    cex = 1.75, las = 2
+  )
+}
+```
+
+```{r fig4a-new-hist, fig.height=3.5, fig.width=8, eval=original_plots}
+model_colors <- col_df %>% filter(method %in% c(
+  "C-HP",
   "C-DCHP",
-                                                "C-MMHP"))
+  "C-MMHP"
+))
 
@@
 m1 <- sim_model3_stan_sim1_total %>%
-  map( ~apply(.x$f, 2, mean)  ) %>%
+  map(~ apply(.x$f, 2, mean)) %>%
   enframe() %>%
   unnest(cols = value) %>%
-  mutate(node_id = rep(c("f1","f2","f3","f4","f5"), 50),
-         method = "C-HP")
+  mutate(
+    node_id = rep(c("f1", "f2", "f3", "f4", "f5"), 50),
+    method = "C-HP"
+  )
 
 m2 <- sim_model3_stan_sim2_total %>%
-  map( ~apply(.x$f, 2, mean)  ) %>%
+  map(~ apply(.x$f, 2, mean)) %>%
   enframe() %>%
   unnest(cols = value) %>%
-  mutate(node_id = rep(c("f1","f2","f3","f4","f5"), 50),
-         method = "C-DCHP")
+  mutate(
+    node_id = rep(c("f1", "f2", "f3", "f4", "f5"), 50),
+    method = "C-DCHP"
+  )
 
 m3 <- sim_model3_stan_sim3_total %>%
-  map( ~apply(.x$f, 2, mean)  ) %>%
+  map(~ apply(.x$f, 2, mean)) %>%
   enframe() %>%
   unnest(cols = value) %>%
-  mutate(node_id = rep(c("f1","f2","f3","f4","f5"), 50),
-         method = "C-MMHP")
-
-rank_means <- bind_rows(m1,m2,m3)
+  mutate(
+    node_id = rep(c("f1", "f2", "f3", "f4", "f5"), 50),
+    method = "C-MMHP"
+  )
+
+rank_means <- bind_rows(m1, m2, m3)
 
@@
 true_values <- tibble(
-  id = c("f1", "f2","f3","f4","f5"),
-  values = c(0.1,0.2,0.4,0.7,0.9),
-  val_names = c("   0.1","0.2","0.4","0.7","0.9")
+  id = c("f1", "f2", "f3", "f4", "f5"),
+  values = c(0.1, 0.2, 0.4, 0.7, 0.9),
+  val_names = c("   0.1", "0.2", "0.4", "0.7", "0.9")
 )
@@
   geom_histogram() +
-  geom_vline(aes(xintercept = values), alpha = 0.6,
-             linetype = "dashed") +
+  geom_vline(aes(xintercept = values),
+    alpha = 0.6,
+    linetype = "dashed"
+  ) +
   ### add text here
   geom_text(aes(values, 18, label = val_names),
-            size = 3, hjust = 1) +
+    size = 3, hjust = 1
+  ) +
   scale_fill_manual(values = model_colors) +
   facet_grid(cols = vars(node_id), rows = vars(method)) +
-  theme_bw() + theme(
-    plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
     text = element_text(size = 12),
-    axis.text.x=element_blank(),
+    axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
@@
   labs(x = "", y = "")
-
+```
+
+## Modified Figure 4a
+
+Reformatting this to boxplots for each of the 3 models, with the true
+ranking values included for each.
+
+Will need to update this with full final simulations.
+
+```{r new-fig-4a, eval = revision_plots}
+sim_data_path <- here("output", "revisions", "sim_m3", "june_18", "/")
+
+num_nodes <- 10
+
+f_vec <- seq(from = 0.10,
+               to = 0.9,
+               length.out = num_nodes)
+
+sim_ranks_mean <- tibble()
+sim_ranks <- tibble()
+
+sims_id <- 1:50
+sims_id <- sims_id[c(-22,-23, -24, -33, -34, -36, -39, -40, -41, -45)]
+
+for(curr_sim in sims_id) {
+  load(paste0(sim_data_path,
+              "sim_model3_fit123_",
+              curr_sim,
+              ".RData"))
+
+  f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
+  m1_ranks <- apply(f_m1, 2, mean)
+
+  f_m1_sims <- f_m1 %>% 
+    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
+    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
+    pivot_longer(everything(),
+                 names_to = "node",
+                 values_to = "rank")
+  f_m1_sims$model <- "C-HP"
+
+  f_m2 <- sim_model3_stan_sim2 %>% select(starts_with("f"))
+  m2_ranks <- apply(f_m2, 2, mean)
+
+  f_m2_sims <- f_m2 %>% 
+    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
+    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
+    pivot_longer(everything(),
+                 names_to = "node",
+                 values_to = "rank")
+
+  f_m2_sims$model <- "C-DCHP"
+
+  f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
+  m3_ranks <- apply(f_m1, 2, mean)
+
+  f_m3_sims <- f_m3 %>% 
+    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
+    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
+    pivot_longer(everything(),
+                 names_to = "node",
+                 values_to = "rank")
+
+  f_m3_sims$model <- "C-MMHP"
+
+  curr_mean_ranks <- tibble(model = c(rep("C-HP", num_nodes),
+                                 rep("C-DCHP", num_nodes),
+                                 rep("C-MMHP", num_nodes)),
+                       ranks = c(m1_ranks,
+                                 m2_ranks,
+                                 m3_ranks),
+                       node = rep(1:num_nodes, 3),
+                       true_rank = rep(f_vec, 3),
+                       sim_id = curr_sim)
+  sim_ranks_mean <- sim_ranks_mean %>% 
+    bind_rows(curr_mean_ranks)
+
+  sim_ranks <- sim_ranks %>% 
+    bind_rows(f_m1_sims, f_m2_sims, f_m3_sims)
+
+}
+
+sim_ranks$node <- factor(sim_ranks$node, levels = 1:num_nodes)
+sim_ranks_mean$node <- factor(sim_ranks_mean$node, levels = 1:num_nodes)
+
+# sim_ranks$node
+
+sim_ranks_mean %>% 
+  # filter(model == "C-MMHP") %>% 
+  ggplot(aes(node, ranks)) + 
+  geom_boxplot() +
+  facet_wrap(~model) +
+  geom_point(aes(node, true_rank, colour = "red"),
+             show.legend = FALSE) +
+  labs(title = "Mean rank from each simulation")
+
+## this is just the mean from each simulation, not the posterior draws
+
+true_ranks <- tibble(node = 1:num_nodes, true_rank = f_vec)
+true_ranks$node <- factor(true_ranks$node, levels = 1:num_nodes)
+
+sim_ranks %>% 
+  ggplot(aes(node, rank)) +
+  geom_boxplot() +
+  facet_wrap(~model) +
+  geom_point(data = true_ranks, aes(node, true_rank, colour = "red"),
+             show.legend = FALSE) +
+  labs(title = "All Posterior Draws")
 ```
@@
 
-```{r prepare data for 4b,cache=TRUE}
-plot.s <- 7#7 is pretty good
+Need to redo this after finally correctly formulating the 
+simulations.
+
+```{r prepare data for 4b,cache=TRUE, eval=revision_plots}
+plot.s <- 7 # 7 is pretty good
 plot.i <- 4
@@
 
-load(paste0(sim_data_path,"/" ,"sim_model3_",
+sim_data_path <- here("output", "revisions", "sim_m3", "june_18", "/")
+
+load(paste0(
+  sim_data_path, "/", "sim_model3_",
   plot.s,
-                              ".RData"))
-test.mmhp <- sim_model3_data$mmhp_matrix[plot.i,plot.j][[1]]
+  ".RData"
+))
+test.mmhp <- sim_model3_data$mmhp_matrix[plot.i, plot.j][[1]]
 temp.t <- test.mmhp$tau
-current.n <- length(temp.t)-1
-time.segment <- seq(0, tail(temp.t,1), length.out = 5000)
+current.n <- length(temp.t) - 1
+time.segment <- seq(0, tail(temp.t, 1), length.out = 5000)
 
@@
 #########
-model1_par_est <- list(lambda0 = mean(sim_model3_stan_sim1_total[[plot.s]]$lambda0),
-                       eta_1 =
-                         mean(sim_model3_stan_sim1_total[[plot.s]]$eta_1),
-                       eta_2 =
-                         mean(sim_model3_stan_sim1_total[[plot.s]]$eta_2),
-                       eta_3 =
-                         mean(sim_model3_stan_sim1_total[[plot.s]]$eta_3),
-                       beta = mean(sim_model3_stan_sim1_total[[plot.s]]$beta),
-                       f = apply(sim_model3_stan_sim1_total[[plot.s]]$f, 2, mean))
-lambda.m1<-uniHawkesIntensityNumeric(object = list(lambda0 = 
+
+## get f from cmdstan
+
+f_draws <- sim_model3_stan_sim1 %>% 
+  select(starts_with("f"))
+
+model1_par_est <- list(
+  lambda0 = mean(sim_model3_stan_sim1$lambda0),
+  eta_1 = mean(sim_model3_stan_sim1$eta_1),
+  eta_2 = mean(sim_model3_stan_sim1$eta_2),
+  eta_3 = mean(sim_model3_stan_sim1$eta_3),
+  beta = mean(sim_model3_stan_sim1$beta),
+  f = apply(f_draws, 2, mean)
+)
+lambda.m1 <- uniHawkesIntensityNumeric(
+  object = list(
+    lambda0 =
       model1_par_est$lambda0,
     alpha =
-                                      model1_fn$alpha.fun(model1_par_est$f[plot.i],
+      model1_fn$alpha.fun(
+        model1_par_est$f[plot.i],
         model1_par_est$f[plot.j],
@@
         model1_par_est$eta_2,
-                                    model1_par_est$eta_3),
-                                    beta = model1_par_est$beta),
+        model1_par_est$eta_3
+      ),
+    beta = model1_par_est$beta
+  ),
   events = temp.t,
-                                     time.vec = time.segment)
+  time.vec = time.segment
+)
 
@@
 #############
-model2_par_est <- list(gamma = apply(sim_model3_stan_sim2_total[[plot.s]]$gamma,
-                                     2, mean),
-                    zeta = apply(sim_model3_stan_sim2_total[[plot.s]]$zeta, 2, mean),
-                    eta_1 = mean(sim_model3_stan_sim2_total[[plot.s]]$eta_1),
-                    eta_2 = mean(sim_model3_stan_sim2_total[[plot.s]]$eta_2),
-                    eta_3 = mean(sim_model3_stan_sim2_total[[plot.s]]$eta_3),
-                    beta = mean(sim_model3_stan_sim2_total[[plot.s]]$beta),
-                    f = apply(sim_model3_stan_sim2_total[[plot.s]]$f, 2, mean))
-
-lambda.m2 <- uniHawkesIntensityNumeric(object=list(
-  lambda0 = model2_par_est$gamma[plot.i]+
+gamma_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("gamma"))
+
+zeta_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("zeta"))
+
+f_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("f"))
+
+model2_par_est <- list(
+  gamma = apply(gamma_draws, 2, mean),
+  zeta = apply(zeta_draws, 2, mean),
+  eta_1 = mean(sim_model3_stan_sim2$eta_1),
+  eta_2 = mean(sim_model3_stan_sim2$eta_2),
+  eta_3 = mean(sim_model3_stan_sim2$eta_3),
+  beta = mean(sim_model3_stan_sim2$beta),
+  f = apply(f_draws, 2, mean)
+)
+
+lambda.m2 <- uniHawkesIntensityNumeric(
+  object = list(
+    lambda0 = model2_par_est$gamma[plot.i] +
       model2_par_est$zeta[plot.j],
-  alpha = model1_fn$alpha.fun(model2_par_est$f[plot.i],
+    alpha = model1_fn$alpha.fun(
+      model2_par_est$f[plot.i],
       model2_par_est$f[plot.j],
@@
       model2_par_est$eta_2,
-                            model2_par_est$eta_3),
-                beta = model2_par_est$beta),
+      model2_par_est$eta_3
+    ),
+    beta = model2_par_est$beta
+  ),
   events = temp.t,
-                time.vec = time.segment)
+  time.vec = time.segment
+)
 
@@
 ###
-lam0_vec <- apply(sim_model3_stan_sim3_total[[plot.s]]$lambda0, 2, mean)
-lam1_vec <- apply(sim_model3_stan_sim3_total[[plot.s]]$lambda1, 2, mean)
-lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
-                       ncol = length(object_par$f_vec_1))
-lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
-                       ncol = length(object_par$f_vec_1))
-
-clean_sim_data <- cleanSimulationData(raw_data = sim_model3_data, 
+
+lam0_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("gamma"))
+
+lam1_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("zeta"))
+
+gamma_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("gamma"))
+
+zeta_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("zeta"))
+
+f_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("f"))
+
+lam0_vec <- apply(lam0_draws, 2, mean)
+lam1_vec <- apply(lam1_draws, 2, mean)
+lam0_par_est <- matrix(0,
+  nrow = length(object_par$f_vec_1),
+  ncol = length(object_par$f_vec_1)
+)
+lam1_par_est <- matrix(0,
+  nrow = length(object_par$f_vec_1),
+  ncol = length(object_par$f_vec_1)
+)
+
+clean_sim_data <- cleanSimulationData(
+  raw_data = sim_model3_data,
   cut_off = cut_off,
-                                      N = length(object_par$f_vec_1))
-
-for(i in seq_along(lam0_vec)) {
+  N = length(object_par$f_vec_1)
+)
+
+### TO DO
+### need to check this here for pairs with less than cut off events
+
+for (i in seq_along(lam0_vec)) {
   row_id <- clean_sim_data$I_fit[i]
@@
 #############
-mmhp_par_est <- list(lambda0 = lam0_par_est,
+mmhp_par_est <- list(
+  lambda0 = lam0_par_est,
   lambda1 = lam1_par_est,
-                     eta_1 = mean(sim_model3_stan_sim3_total[[plot.s]]$eta_1),
-                     eta_2 = mean(sim_model3_stan_sim3_total[[plot.s]]$eta_2),
-                     eta_3 = mean(sim_model3_stan_sim3_total[[plot.s]]$eta_3),
-                     beta = mean(sim_model3_stan_sim3_total[[plot.s]]$beta),
-                     f = apply(sim_model3_stan_sim3_total[[plot.s]]$f,2,mean))
-
-object_hat <- list(lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
+  eta_1 = mean(sim_model3_stan_sim3$eta_1),
+  eta_2 = mean(sim_model3_stan_sim3$eta_2),
+  eta_3 = mean(sim_model3_stan_sim3$eta_3),
+  beta = mean(sim_model3_stan_sim3$beta),
+  f = apply(f_draws, 2, mean)
+)
+
+object_hat <- list(
+  lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
   lambda1 = mmhp_par_est$lambda1[cur_i, cur_j],
-                   alpha = model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
+  alpha = model3_fn$alpha.fun(
+    mmhp_par_est$f[cur_i],
     mmhp_par_est$f[cur_j],
     mmhp_par_est$eta_1,
-                                             mmhp_par_est$eta_2),
+    mmhp_par_est$eta_2
+  ),
   beta = mmhp_par_est$beta,
-                   q1 = model3_fn$q1.fun(mmhp_par_est$f[cur_i],
+  q1 = model3_fn$q1.fun(
+    mmhp_par_est$f[cur_i],
     mmhp_par_est$f[cur_j],
-                                       mmhp_par_est$eta_3),
-                   q2=model3_fn$q0.fun(mmhp_par_est$f[cur_i],
+    mmhp_par_est$eta_3
+  ),
+  q2 = model3_fn$q0.fun(
+    mmhp_par_est$f[cur_i],
     mmhp_par_est$f[cur_j],
-                                       mmhp_par_est$eta_3))
+    mmhp_par_est$eta_3
+  )
+)
 
 ## then need to load in the state estimate here
-load(paste0(sim_data_path,"/", "fit123_state_est_", plot.s, ".RData"))
-
-state.est.latent.mmhp <- interpolate_state_est_lst[plot.i,plot.j][[1]]
+load(paste0(here("output", "revisions", "sim_m3"),
+  "/", "fit123_state_est_",
+  plot.s,
+  ".RData"
+))
+
+state.est.latent.mmhp <- interpolate_state_est_lst[plot.i, plot.j][[1]]
 state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
-                                                 termination=200)
-
-step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,
-                        2 - state.est.latent.mmhp$z.hat)
-
-lambda.m3 <- mmhpIntensityNumeric(params = object_hat,
+  termination = 200
+)
+
+step.fun.est <- stepfun(
+  state.est.latent.mmhp$x.hat,
+  2 - state.est.latent.mmhp$z.hat
+)
+
+lambda.m3 <- mmhpIntensityNumeric(
+  params = object_hat,
   t = temp.t[-1],
   time.vec = time.segment,
-                                  latent.vec = step.fun.est(time.segment))
-
-object_true <- lapply(object_matrix,function(x) x[plot.i,plot.j])
-names(object_true) <- c("lambda0","lambda1","alpha","beta","q1","q2")
-
-lambda.true <- mmhpTrueIntensityNumeric(params = object_true,
+  latent.vec = step.fun.est(time.segment)
+)
+
+object_true <- lapply(object_matrix, function(x) x[plot.i, plot.j])
+names(object_true) <- c("lambda0", "lambda1", "alpha", "beta", "q1", "q2")
+
+lambda.true <- mmhpTrueIntensityNumeric(
+  params = object_true,
   t = temp.t,
-                       latent = list(x = fixStateTransition(test.mmhp)$x,
-                                     z = fixStateTransition(test.mmhp)$z),
-                                     time.vec = time.segment)
+  latent = list(
+    x = fixStateTransition(test.mmhp)$x,
+    z = fixStateTransition(test.mmhp)$z
+  ),
+  time.vec = time.segment
+)
 
@@
 ```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4}
-y.ub <- c(35,35,35)#c(130,72,31)
-x_events <- 190#135#150
-layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
-my.xlim <- 200#160#200#130
-my.long.x <- 205#205#134.5
-legend.x <- c(60,60,60)#c(135,135,135)
-legend.y <- #c(34,32,32)
-legend.y <- c(23,23,23)#c(15,12,15)#c(62,37,18)#c(22,22,22)
-legend.cex <- 1.5 #3
-line.alpha <- c(0.9,0.6)
-line.wdth <- c(2,2.5)
-negative.col <- add.alpha('lightskyblue')
-positive.col <- add.alpha('tomato')
-#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
-#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
-par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
-    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)
+mmhp_lty <- 1
+
+y.ub <- c(8, 8, 8) # c(130,72,31)
+x_events <- 190 # 135#150
+my.xlim <- 200 # 160#200#130
+my.long.x <- 205 # 205#134.5
+legend.x <- c(100, 100, 100) # c(135,135,135)
+legend.y <- # c(34,32,32)
+legend.y <- c(6, 6, 6) # c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.cex <- 1.5 # 3
+line.alpha <- c(1, 0.5)
+line.wdth <- c(1.5, 2)
+negative.col <- add.alpha("lightskyblue")
+positive.col <- add.alpha("tomato")
+
+model_colors <- col_df %>% filter(method %in% c(
+  "C-HP",
+  "C-DCHP",
+  "C-MMHP"
+))
+
+model_colors <- model_colors %>% pull(cols)
 
@@
 
+```
+
+```{r actual-plot}
+layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 2.5), 3))
+par(
+  mar = c(0, 0.3, 0, 0.1), oma = c(0, 3.5, 4, 0),
+  tcl = 0.2, mgp = c(0.5, 0, 0), xpd = TRUE
+)
+
+mmhp_est <- fixStateTransition(test.mmhp)
+
 drawUniMMHPIntensityPaper(true.object,
-                          simulation = fixStateTransition(test.mmhp),
-                          yupper=y.ub[1], 
-                          color=add.alpha("black", alpha=line.alpha[1]),
-                          line.width=line.wdth[1],
-                          y.ratio=-0.05, min.y=-2,
-                          min.x=0, max.x=my.xlim,
-                          title_name=paste(plot.i,"->",plot.j),
+                          simulation = mmhp_est,
+                          yupper = y.ub[1],
+                          color = add.alpha("black", alpha = line.alpha[1]),
+                          line.width = line.wdth[1],
+                          y.ratio = -0.05, min.y = -0.5,
+                          min.x = 0, max.x = my.xlim,
+                          title_name = paste(plot.i, "->", plot.j),
                           title.cex = 2,
-                          box.type="n")
-drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
-                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
+                          box.type = "n",
+                          line_type = mmhp_lty
+)
+drawHawkesIntensityPaper(
+  lambda0 = model1_par_est$lambda0,
+  alpha = model1_fn$alpha.fun(
+    model1_par_est$f[plot.i],
     model1_par_est$f[plot.j],
@@
     model1_par_est$eta_2,
-                                                   model1_par_est$eta_3),
-                         beta=model1_par_est$beta,
-                         events=test.mmhp$tau,
-                         color=add.alpha(model_colors[1],
-                                         alpha=line.alpha[2]),
-                         line.width=line.wdth[2])
-
-## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
+    model1_par_est$eta_3
+  ),
+  beta = model1_par_est$beta,
+  events = test.mmhp$tau,
+  color = add.alpha(model_colors[1],
+                    alpha = line.alpha[2]
+  ),
+  line.width = line.wdth[2]
+)
+
+# draw box
+axis(1,
+     at = c(-2, my.long.x),
+     col = "gray35",
+     line = 0.5,
+     tick = T,
+     labels = rep("", 2),
+     lwd = 0.5,
+     lwd.ticks = 0,
+     lty = 3
+)
 
@@
 # points(26,84,pch=16,cex=2,col="blue")
-legend(legend.x[1],legend.y[1],c("True"),
+
+#### more legend
+legend(legend.x[1] - 2, legend.y[1] + 1, c("True"),
        col = c("black"),
-       y.intersp=0.88,x.intersp=0.15,bty = "n",
-       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
-legend(legend.x[1]+22,legend.y[1],c("C-HP"),
+       y.intersp = 0.88, x.intersp = 0.65, bty = "n",
+       lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
+)
+legend(legend.x[1] + 22, legend.y[1] + 1, c("C-HP"),
        col = c(model_colors[1]),
-       y.intersp=0.88,x.intersp=0.15,bty = "n",
-       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
+       y.intersp = 0.88, x.intersp = 0.65, bty = "n",
+       lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
+)
 
 ## delta lambda
-par(mar = c(0,0.3,0,0.1))
-plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,4), type="n",
-     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
-delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
+par(mar = c(0, 0.3, 0, 0.1))
+plot(0, 0,
+     xlim = c(0, my.xlim), 
+     ylim = c(-0.5, 4),
+     type = "n",
+     bty = "n",
+     xlab = "",
+     ylab = "",
+     xaxt = "n",
+     yaxt = "n",
+     axes = FALSE
+)
+delta.lambda <- lambda.m1$lambda.t - lambda.true$lambda.t
 delta.positive <- delta.lambda
-delta.positive[delta.positive<0] <- 0
+delta.positive[delta.positive < 0] <- 0
 delta.negative <- delta.lambda
-delta.negative[delta.negative>0] <- 0
+delta.negative[delta.negative > 0] <- 0
 ### hiding these for now ###
-polygon(c(0,lambda.true$time.vec,x_events),#200
-        c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,x_events),#200
-        c(0,delta.positive,0),col=positive.col,border=NA)
-
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+        c(0, delta.negative, 0),
+        col = negative.col, border = NA
+)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+        c(0, delta.positive, 0),
+        col = positive.col, border = NA
+)
+
+axis(1,
+     at = c(-1, my.long.x), 
+     col = "gray35",
+     line = 0, tick = T, 
+     labels = rep("", 2),
+     lwd = 0.7,
+     lwd.ticks = 0
+)
 
@@
 ############
-drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
-                          yupper=y.ub[2], 
-                          color=add.alpha("black", alpha=line.alpha[1]),
-                          line.width=line.wdth[1],
-                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
-                          box.type="n")
-drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
+drawUniMMHPIntensityPaper(true.object,
+                          simulation = mmhp_est,
+                          ### these points aren't consistent?
+                          yupper = y.ub[2],
+                          color = add.alpha("black",
+                                            alpha = line.alpha[1]),
+                          line.width = line.wdth[1],
+                          y.ratio = -0.05,
+                          min.y = -0.5,
+                          min.x = 0,
+                          max.x = my.xlim,
+                          box.type = "n",
+                          line_type = mmhp_lty
+)
+drawHawkesIntensityPaper(
+  lambda0 = model2_par_est$gamma[plot.i] +
     model2_par_est$zeta[plot.j],
-                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+  alpha = model1_fn$alpha.fun(
+    model2_par_est$f[plot.i],
     model2_par_est$f[plot.j],
@@
     model2_par_est$eta_2,
-                                                   model2_par_est$eta_3),
-                         beta=model2_par_est$beta,
-                         events=test.mmhp$tau,
-                         color=add.alpha(model_colors[2],
-                                         alpha=line.alpha[2]),
-                         line.width=line.wdth[2])
-legend(legend.x[2],legend.y[2],"C-DCHP",
+    model2_par_est$eta_3
+  ),
+  beta = model2_par_est$beta,
+  events = test.mmhp$tau,
+  color = add.alpha(model_colors[2],
+                    alpha = line.alpha[2]
+  ),
+  line.width = line.wdth[2]
+)
+
+### used legend
+legend(legend.x[2] - 2, legend.y[2] + 1, c("True"),
+       col = c("black"),
+       y.intersp = 0.88, x.intersp = 0.65, bty = "n",
+       lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
+)
+legend(legend.x[2] + 22, legend.y[2] + 1, "C-DCHP",
        col = model_colors[2],
-       y.intersp=0.88,x.intersp=0.1,bty = "n",
-       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)
-
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
-
-legend(legend.x[2]-50,
-       legend.y[2]+2,c("State 0/1 events","State change point"),
-       col = c(NA,"red"),
-       y.intersp=0.85,x.intersp=-0.5, bty = "n",
-       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
-       lty = c(NA,NA), lwd=c(NA,2))
-points(legend.x[2]-46,legend.y[2] - 4.5, pch = 1, cex = 2, col = "blue")
-points(legend.x[2]-44,legend.y[2] - 4.5, pch = 16, cex = 2, col = "blue")
+       y.intersp = 0.88,
+       x.intersp = 0.65,
+       bty = "n",
+       lty = 1,
+       lwd = 5,
+       cex = legend.cex,
+       seg.len = 1
+)
+
+axis(1,
+     at = c(-2, my.long.x),
+     col = "gray35",
+     line = 0.5,
+     tick = T,
+     labels = rep("", 2),
+     lwd = 0.5,
+     lwd.ticks = 0,
+     lty = 3
+)
+
+## location of legend
+legend(legend.x[2] - 95,
+       legend.y[2] + 2, c("State 0/1 events", "State change point"),
+       col = c(NA, "red"),
+       y.intersp = 0.85,
+       x.intersp = -0,
+       bty = "n",
+       pch = c(NA, 4), pt.cex = c(NA, 2), cex = legend.cex,
+       lty = c(NA, NA), lwd = c(NA, 2)
+)
+points(legend.x[2] - 89, legend.y[2], 
+       pch = 1, cex = 2, col = "blue")
+points(legend.x[2] - 85, legend.y[2],
+       pch = 16, cex = 2, col = "blue")
 
 ## delta lambda
-par(mar = c(0,0.3,0,0.1))
-delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
-
-plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), 
-     ylim=c(-4,4), type="n",
-     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
-delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
+par(mar = c(0, 0.3, 0, 0.1))
+delta.lambda <- lambda.m2$lambda.t - lambda.true$lambda.t
+
+plot(lambda.true$time.vec, delta.lambda,
+     xlim = c(0, my.xlim),
+     ylim = c(-0.5, 4), type = "n",
+     bty = "n",
+     xlab = "",
+     ylab = "",
+     xaxt = "n",
+     yaxt = "n",
+     axes = FALSE
+)
+delta.lambda <- lambda.m2$lambda.t - lambda.true$lambda.t
 delta.positive <- delta.lambda
-delta.positive[delta.positive<0] <- 0
+delta.positive[delta.positive < 0] <- 0
 delta.negative <- delta.lambda
-delta.negative[delta.negative>0] <- 0
-polygon(c(0,lambda.true$time.vec,x_events), #200
-        c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,x_events), #200
-        c(0,delta.positive,0),col=positive.col,border=NA)
+delta.negative[delta.negative > 0] <- 0
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+        c(0, delta.negative, 0),
+        col = negative.col, border = NA
+)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+        c(0, delta.positive, 0),
+        col = positive.col, border = NA
+)
 # segments(0,0,my.xlim,0,col="gray45")
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+axis(1,
+     at = c(-2, my.long.x), col = "gray35",
+     line = 0, tick = T, labels = rep("", 2), lwd = 0.7, lwd.ticks = 0
+)
 
@@
 ########
-par(mar = c(0,0.3,1,0.1))
+par(mar = c(0, 0.3, 1, 0.1))
 drawUniMMHPIntensityPaper(true.object,
-                          simulation=fixStateTransition(test.mmhp),
-                          yupper=y.ub[3],
-                          color=add.alpha("black", alpha=line.alpha[1]),
-                          line.width=line.wdth[1],
-                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
-                          box.type="n")
+                          simulation = mmhp_est,
+                          yupper = y.ub[3],
+                          color = add.alpha("black", alpha = line.alpha[1]),
+                          line.width = line.wdth[1],
+                          y.ratio = -0.05, min.y = -0.5,
+                          min.x = 0, max.x = my.xlim,
+                          box.type = "n", line_type = mmhp_lty
+)
 drawUniMMHPIntensityPaper(object_hat,
                           simulation = list(
-                            x=state.est.latent.mmhp.new$x.hat,                                          
-                            z=state.est.latent.mmhp.new$z.hat,
-                            tau=test.mmhp$tau,zt=test.mmhp$zt,
-                            lambda.max=test.mmhp$lambda.max),
-                          yupper=y.ub,add=TRUE,
-                          color=add.alpha(model_colors[3],
-                                          alpha=line.alpha[2]),
-                          line.width=line.wdth[2])
-legend(legend.x[3],legend.y[3],"C-MMHP",
+                            x = state.est.latent.mmhp.new$x.hat,
+                            z = state.est.latent.mmhp.new$z.hat,
+                            tau = test.mmhp$tau, zt = test.mmhp$zt,
+                            lambda.max = test.mmhp$lambda.max
+                          ),
+                          yupper = y.ub, add = TRUE,
+                          color = add.alpha(model_colors[3],
+                                            alpha = line.alpha[2]
+                          ),
+                          line.width = line.wdth[2]
+)
+legend(legend.x[3] - 2, legend.y[3] + 1, c("True"),
+       col = c("black"),
+       y.intersp = 0.88, x.intersp = 0.65, bty = "n",
+       lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
+)
+
+legend(legend.x[3] + 22, legend.y[3] + 1, "C-MMHP",
        col = model_colors[3],
-       y.intersp=0.6,x.intersp=0.1,bty = "n",
-       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
+       y.intersp = 0.88,
+       x.intersp = .65,
+       bty = "n",
+       lty = 1,
+       lwd = 5,
+       cex = legend.cex,
+       seg.len = 1
+)
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
-
-legend(legend.x[3]-50,legend.y[3]+2, c("Overestimation","Underestimation"),
-       col = c(positive.col,negative.col),
-       y.intersp=0.75,x.intersp=0.5,bty = "n",
-       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)
+axis(1,
+     at = c(-2, my.long.x),
+     col = "gray35",
+     line = 0.5,
+     tick = T,
+     labels = rep("", 2), 
+     lwd = 0.5,
+     lwd.ticks = 0, lty = 3
+)
+
+legend(legend.x[3] - 95, legend.y[3] + 2,
+       c("Overestimation", "Underestimation"),
+       col = c(positive.col, negative.col),
+       y.intersp = 0.75, x.intersp = 0.5, bty = "n",
+       lty = c(1, 1), lwd = c(10, 10), cex = legend.cex, seg.len = 0.8
+)
 
 ## delta lambda
-par(mar = c(0,0.3,0,0.1))
-plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,4), type="n",
-     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
-delta.lambda <- lambda.m3-lambda.true$lambda.t
+par(mar = c(0, 0.3, 0, 0.1))
+plot(0, 0,
+     xlim = c(0, my.xlim), 
+     ylim = c(-0.5, 4), type = "n",
+     bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n",
+     axes = FALSE
+)
+delta.lambda <- lambda.m3 - lambda.true$lambda.t
 delta.positive <- delta.lambda
-delta.positive[delta.positive<0] <- 0
+delta.positive[delta.positive < 0] <- 0
 delta.negative <- delta.lambda
-delta.negative[delta.negative>0] <- 0
+delta.negative[delta.negative > 0] <- 0
 ### hiding these for now
-polygon(c(0,lambda.true$time.vec,x_events), # 200 
-        c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,x_events), # 200 
-        c(0,delta.positive,0),col=positive.col,border=NA)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+        c(0, delta.negative, 0),
+        col = negative.col, border = NA
+)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+        c(0, delta.positive, 0),
+        col = positive.col, border = NA
+)
 # segments(0,0,my.xlim,0,col="gray45")
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+axis(1,
+     at = c(-2, my.long.x), col = "gray35",
+     line = 0, tick = T, labels = rep("", 2), lwd = 0.7, lwd.ticks = 0
+)
 
 ## top
-mtext(text="(b)",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
+mtext(text = "(b)", side = 3, line = 0.8,
+      outer = TRUE, cex = 2.5, font = 2)
 ## bottom
-mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.25)
+mtext(text = "Time", side = 1, line = 2,
+      outer = TRUE, cex = 2.25)
 ## left
-mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.25)
+mtext(text = "Intensity", side = 2,
+      line = 0.6, outer = TRUE, cex = 2.25)
 
@@
 m1_files <- list.files(m1_path, pattern = "sim_model1_fit*")
-#m1_files
+# m1_files
 
@@
 
-for(i in seq_along(m1_files)) {
-  load(paste0(m1_path,m1_files[i]))
+for (i in seq_along(m1_files)) {
+  load(paste0(m1_path, m1_files[i]))
   sim_model1_stan_sim1_total[[i]] <- sim_model1_stan_sim1
@@
   sim_model1_stan_sim3_total[[i]] <- sim_model1_stan_sim3
-
 }
@@
 m2_files <- list.files(m2_path, pattern = "sim_model2_fit*")
-#m1_files
+# m1_files
 
@@
 
-for(i in seq_along(m2_files)) {
-  load(paste0(m2_path,m2_files[i]))
+for (i in seq_along(m2_files)) {
+  load(paste0(m2_path, m2_files[i]))
   sim_model2_stan_sim1_total[[i]] <- sim_model2_stan_sim1
@@
   sim_model2_stan_sim3_total[[i]] <- sim_model2_stan_sim3
-
-}
-
+}
 ```
@@
 
-#png(paste(plot_path,"sim_latent_recover.png",sep=""), height=500, width=900)
-par(mfrow=c(3, length(object_par$f_vec_1)),
-    mar=c(0,0,1,0),
-    oma=c(6.5,11,3.5,1))
-
-y.ub <- c(12,12,12,12,12)
-text.y <- c(rep(8,4),8)
-text.x <- c(0.1,0.2,0.4,0.7,0.9)
-text.x.adj <- c(0.3,0.4,0.6,0.5,0.8)
+# png(paste(plot_path,"sim_latent_recover.png",sep=""), height=500, width=900)
+par(
+  mfrow = c(3, length(object_par$f_vec_1)),
+  mar = c(0, 0, 1, 0),
+  oma = c(6.5, 11, 3.5, 1)
+)
+
+y.ub <- c(12, 12, 12, 12, 12)
+text.y <- c(rep(8, 4), 8)
+text.x <- c(0.1, 0.2, 0.4, 0.7, 0.9)
+text.x.adj <- c(0.3, 0.4, 0.6, 0.5, 0.8)
 model_colors <- c("steelblue", "goldenrod2", "firebrick2")
@@
 
-for(m in c(1:3)){
-  for(j in c(1:length(object_par$f_vec_1))){
-    plot(1,4,xlim=c(0,1),ylim=c(0,y.ub[j]),
-         type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+for (m in c(1:3)) {
+  for (j in c(1:length(object_par$f_vec_1))) {
+    plot(1, 4,
+      xlim = c(0, 1), ylim = c(0, y.ub[j]),
+      type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
+    )
 
     ## Posterior density
-    current_result <- eval(parse(text=paste("sim_model1_stan_sim",
+    current_result <- eval(parse(text = paste("sim_model1_stan_sim",
       m,
       "_total",
-                                            sep="")))
-    for(i in c(1:n_sim)){
-      lines(density(current_result[[i]]$f[,j]),
-            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
+      sep = ""
+    )))
+    for (i in c(1:n_sim)) {
+      lines(density(current_result[[i]]$f[, j]),
+        col = add.alpha(model_colors[m], alpha = 0.8), cex = 0.6, lwd = 0.8
+      )
     }
@@
   ## bottom
-  mtext(text=expression(f[1],f[2],f[3],f[4],f[5]), side=1, line=2.4, outer=TRUE, 
-        at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
-        cex=2.4)
-  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.7,
-        at=0.5)
+  mtext(
+    text = expression(f[1], f[2], f[3], f[4], f[5]), side = 1, line = 2.4, outer = TRUE,
+    at = c(1:length(object_par$f_vec_1)) / length(object_par$f_vec_1) - 0.1,
+    cex = 2.4
+  )
+  mtext(
+    text = "Latent rank variables", side = 1, line = 5.3, outer = TRUE, cex = 2.7,
+    at = 0.5
+  )
   ## top
-  mtext(text="Simulated from M1", side=3, line=0, outer=TRUE, cex=3,
-        at=0.5, font=2)
+  mtext(
+    text = "Simulated from M1", side = 3, line = 0, outer = TRUE, cex = 3,
+    at = 0.5, font = 2
+  )
   ## left
-  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5, outer=TRUE, 
-        at=c(0:2)/3+0.15,
-        cex=2, las=2)
-}
-
-for(m in c(1:3)){
-  for(j in c(1:length(object_par$f_vec_1))){
-    plot(1,4,xlim=c(0,1),ylim=c(0,y.ub[j]),
-         type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
+  mtext(
+    text = rev(c("C-HP  ", "C-DCHP", "C-MMHP")), side = 2, line = 0.5, outer = TRUE,
+    at = c(0:2) / 3 + 0.15,
+    cex = 2, las = 2
+  )
+}
+
+for (m in c(1:3)) {
+  for (j in c(1:length(object_par$f_vec_1))) {
+    plot(1, 4,
+      xlim = c(0, 1), ylim = c(0, y.ub[j]),
+      type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
+    )
 
     ## Posterior density
-    current_result <- eval(parse(text=paste("sim_model2_stan_sim",
+    current_result <- eval(parse(text = paste("sim_model2_stan_sim",
       m,
       "_total",
-                                            sep="")))
-    for(i in c(1:n_sim)){
-      lines(density(current_result[[i]]$f[,j]),
-            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
+      sep = ""
+    )))
+    for (i in c(1:n_sim)) {
+      lines(density(current_result[[i]]$f[, j]),
+        col = add.alpha(model_colors[m], alpha = 0.8), cex = 0.6, lwd = 0.8
+      )
     }
@@
   ## bottom
-  mtext(text=expression(f[1],f[2],f[3],f[4],f[5]), side=1, line=2.4, outer=TRUE, 
-        at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
-        cex=2.4)
-  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.7,
-        at=0.5)
+  mtext(
+    text = expression(f[1], f[2], f[3], f[4], f[5]), side = 1, line = 2.4, outer = TRUE,
+    at = c(1:length(object_par$f_vec_1)) / length(object_par$f_vec_1) - 0.1,
+    cex = 2.4
+  )
+  mtext(
+    text = "Latent rank variables", side = 1, line = 5.3, outer = TRUE, cex = 2.7,
+    at = 0.5
+  )
   ## top
-  mtext(text="Simulated from M2", side=3, line=0, outer=TRUE, cex=3,
-        at=0.5, font=2)
+  mtext(
+    text = "Simulated from M2", side = 3, line = 0, outer = TRUE, cex = 3,
+    at = 0.5, font = 2
+  )
   ## left
-  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5, outer=TRUE, 
-        at=c(0:2)/3+0.15,
-        cex=2, las=2)
+  mtext(
+    text = rev(c("C-HP  ", "C-DCHP", "C-MMHP")), side = 2, line = 0.5, outer = TRUE,
+    at = c(0:2) / 3 + 0.15,
+    cex = 2, las = 2
+  )
 }
@@
 ```{r process m1 for fig4b, include=extra_plots, eval=extra_plots}
-plot.s <- 1#7#9
+plot.s <- 1 # 7#9
 plot.i <- 4
@@
 
-load(paste0(m1_path,m1_files[plot.s]))
-clean_sim_data_m1 <- cleanSimulationData(raw_data = sim_model1_data[[1]], 
+load(paste0(m1_path, m1_files[plot.s]))
+clean_sim_data_m1 <- cleanSimulationData(
+  raw_data = sim_model1_data[[1]],
   cut_off = cut_off,
-                                      N = length(object_par$f_vec_1))
+  N = length(object_par$f_vec_1)
+)
 # this loads in sim data too
 
-temp.t <- sim_model1_data[[1]]$day_hour[ which(sim_model1_data[[1]]$start == cur_i & 
+temp.t <- sim_model1_data[[1]]$day_hour[which(sim_model1_data[[1]]$start == cur_i &
   sim_model1_data[[1]]$end == cur_j)]
 # temp.t <- test.mmhp$tau
-current.n <- length(temp.t)-1
-time.segment <- seq(0,tail(temp.t,1),length.out=5000)
+current.n <- length(temp.t) - 1
+time.segment <- seq(0, tail(temp.t, 1), length.out = 5000)
 
@@
 #########
-model1_par_est <- list(lambda0 = 
+model1_par_est <- list(
+  lambda0 =
     mean(sim_model1_stan_sim1_total[[plot.s]]$lambda0),
@@
   beta = mean(sim_model1_stan_sim1_total[[plot.s]]$beta),
-                   f = apply(sim_model1_stan_sim1_total[[plot.s]]$f,2,mean))
-lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
+  f = apply(sim_model1_stan_sim1_total[[plot.s]]$f, 2, mean)
+)
+lambda.m1 <- uniHawkesIntensityNumeric(
+  object = list(
+    lambda0 =
       model1_par_est$lambda0,
     alpha =
-                                    model1_fn$alpha.fun(model1_par_est$f[plot.i],
+      model1_fn$alpha.fun(
+        model1_par_est$f[plot.i],
         model1_par_est$f[plot.j],
@@
         model1_par_est$eta_2,
-                                    model1_par_est$eta_3),
-                                    beta=model1_par_est$beta),
-                                    events=temp.t,
-                                    time.vec=time.segment)
+        model1_par_est$eta_3
+      ),
+    beta = model1_par_est$beta
+  ),
+  events = temp.t,
+  time.vec = time.segment
+)
 
@@
 #############
-model2_par_est <- list(gamma = apply(sim_model1_stan_sim2_total[[plot.s]]$gamma,
-                                   2,mean),
-                       zeta = apply(sim_model1_stan_sim2_total[[plot.s]]$zeta,
-                                  2, mean),
+model2_par_est <- list(
+  gamma = apply(
+    sim_model1_stan_sim2_total[[plot.s]]$gamma,
+    2, mean
+  ),
+  zeta = apply(
+    sim_model1_stan_sim2_total[[plot.s]]$zeta,
+    2, mean
+  ),
   eta_1 = mean(sim_model1_stan_sim2_total[[plot.s]]$eta_1),
@@
   beta = mean(sim_model1_stan_sim2_total[[plot.s]]$beta),
-                     f = apply(sim_model1_stan_sim2_total[[plot.s]]$f, 
-                             2, mean))
-
-lambda.m2 <- uniHawkesIntensityNumeric(object=list(
-  lambda0=model2_par_est$gamma[plot.i]+
+  f = apply(
+    sim_model1_stan_sim2_total[[plot.s]]$f,
+    2, mean
+  )
+)
+
+lambda.m2 <- uniHawkesIntensityNumeric(
+  object = list(
+    lambda0 = model2_par_est$gamma[plot.i] +
       model2_par_est$zeta[plot.j],
-  alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+    alpha = model1_fn$alpha.fun(
+      model2_par_est$f[plot.i],
       model2_par_est$f[plot.j],
@@
       model2_par_est$eta_2,
-                            model2_par_est$eta_3),
-                beta=model2_par_est$beta),
-                events=temp.t,
-                time.vec=time.segment)
+      model2_par_est$eta_3
+    ),
+    beta = model2_par_est$beta
+  ),
+  events = temp.t,
+  time.vec = time.segment
+)
 
@@
 lam1_vec <- apply(sim_model1_stan_sim3_total[[plot.s]]$lambda1, 2, mean)
-lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
-                       ncol = length(object_par$f_vec_1))
-lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
-                       ncol = length(object_par$f_vec_1))
+lam0_par_est <- matrix(0,
+  nrow = length(object_par$f_vec_1),
+  ncol = length(object_par$f_vec_1)
+)
+lam1_par_est <- matrix(0,
+  nrow = length(object_par$f_vec_1),
+  ncol = length(object_par$f_vec_1)
+)
 
@@
 
-for(i in seq_along(lam0_vec)) {
+for (i in seq_along(lam0_vec)) {
   row_id <- clean_sim_data_m1$I_fit[i]
@@
 ####
-mmhp_par_est <- list(lambda0 = lam0_par_est,
+mmhp_par_est <- list(
+  lambda0 = lam0_par_est,
   lambda1 = lam1_par_est,
@@
   beta = mean(sim_model1_stan_sim3_total[[plot.s]]$beta),
-                     f = apply(sim_model1_stan_sim3_total[[plot.s]]$f, 2, mean))
-
-object_hat <- list(lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
+  f = apply(sim_model1_stan_sim3_total[[plot.s]]$f, 2, mean)
+)
+
+object_hat <- list(
+  lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
   lambda1 = mmhp_par_est$lambda1[cur_i, cur_j],
-                   alpha = model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
+  alpha = model3_fn$alpha.fun(
+    mmhp_par_est$f[cur_i],
     mmhp_par_est$f[cur_j],
     mmhp_par_est$eta_1,
-                                             mmhp_par_est$eta_2),
+    mmhp_par_est$eta_2
+  ),
   beta = mmhp_par_est$beta,
-                   q1 = model3_fn$q1.fun(mmhp_par_est$f[cur_i],
+  q1 = model3_fn$q1.fun(
+    mmhp_par_est$f[cur_i],
     mmhp_par_est$f[cur_j],
-                                       mmhp_par_est$eta_3),
-                   q2 = model3_fn$q0.fun(mmhp_par_est$f[cur_i],
+    mmhp_par_est$eta_3
+  ),
+  q2 = model3_fn$q0.fun(
+    mmhp_par_est$f[cur_i],
     mmhp_par_est$f[cur_j],
-                                       mmhp_par_est$eta_3))
+    mmhp_par_est$eta_3
+  )
+)
 
 state_est_fits <- list.files(m1_path, pattern = "fit123_state_est_M1*")
-load(paste0(m1_path,state_est_fits[plot.s]))
-
-state.est.latent.mmhp <- interpolate_state_est_lst[plot.i,plot.j][[1]]
+load(paste0(m1_path, state_est_fits[plot.s]))
+
+state.est.latent.mmhp <- interpolate_state_est_lst[plot.i, plot.j][[1]]
 state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
-                                                 termination = 200)
-
-step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,
-                        2-state.est.latent.mmhp$z.hat)
-
-lambda.m3 <- mmhpIntensityNumeric(params=object_hat,
-                                  t=temp.t,
-                                  time.vec=time.segment,
-                                  latent.vec=step.fun.est(time.segment))
-
-object_true <- lapply(object_matrix,function(x) x[plot.i,plot.j])
-names(object_true) <- c("lambda0","lambda1","alpha","beta")
-
-lambda.true <- uniHawkesIntensityNumeric(object = object_true,
-                                        events =temp.t,
-                                        time.vec = time.segment)
+  termination = 200
+)
+
+step.fun.est <- stepfun(
+  state.est.latent.mmhp$x.hat,
+  2 - state.est.latent.mmhp$z.hat
+)
+
+lambda.m3 <- mmhpIntensityNumeric(
+  params = object_hat,
+  t = temp.t,
+  time.vec = time.segment,
+  latent.vec = step.fun.est(time.segment)
+)
+
+object_true <- lapply(object_matrix, function(x) x[plot.i, plot.j])
+names(object_true) <- c("lambda0", "lambda1", "alpha", "beta")
+
+lambda.true <- uniHawkesIntensityNumeric(
+  object = object_true,
+  events = temp.t,
+  time.vec = time.segment
+)
 ```
@@
 ```{r fig 4b M1 sim, include=extra_plots, eval=extra_plots}
-source(here("lib","mod_drawHawkesIntensityPaper.R"))
-y.ub <- c(27,27,27)#c(130,72,31)
-x_events <- 135#150
-#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
+source(here("lib", "mod_drawHawkesIntensityPaper.R"))
+y.ub <- c(27, 27, 27) # c(130,72,31)
+x_events <- 135 # 150
+# model_colors <- c("steelblue", "goldenrod2", "firebrick2")
 model_colors <- viridis::viridis(3)
-layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
-layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
-my.xlim <- 140#160#200#130
-my.long.x <- 140#205#134.5
-legend.x <- c(110,110,110)#c(135,135,135)
-legend.y <- #c(34,32,32)
-legend.y <- c(20,20,20)#c(62,37,18)#c(22,22,22)
-legend.cex <- 1.5 #3
-line.alpha <- c(0.9,0.6)
-line.wdth <- c(2,2.5)
-negative.col <- add.alpha('lightskyblue',0.6)
-positive.col <- add.alpha('tomato',0.6)
-#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
-#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
-par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
-    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)
+layout(matrix(c(1:6), 6, 1), heights = rep(c(2.5, 1), 3))
+layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 1), 3))
+my.xlim <- 140 # 160#200#130
+my.long.x <- 140 # 205#134.5
+legend.x <- c(110, 110, 110) # c(135,135,135)
+legend.y <- # c(34,32,32)
+  legend.y <- c(20, 20, 20) # c(62,37,18)#c(22,22,22)
+legend.cex <- 1.5 # 3
+line.alpha <- c(0.9, 0.6)
+line.wdth <- c(2, 2.5)
+negative.col <- add.alpha("lightskyblue", 0.6)
+positive.col <- add.alpha("tomato", 0.6)
+# negative.col <- viridis::viridis(5,alpha = 0.6)[1]
+# positive.col <- viridis::viridis(5,alpha = 0.6)[4]
+par(
+  mar = c(0, 0.3, 0, 0.1), oma = c(3, 3.5, 4, 0),
+  tcl = 0.2, mgp = c(0.5, 0, 0), xpd = TRUE
+)
 
@@
 
-mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
+mod_drawHawkesIntensityPaper(
+  lambda0 = true.object$lambda0,
   alpha = true.object$alpha,
@@
   add = FALSE,
-                            yupper=y.ub[1],
-                            color=add.alpha("black", alpha=line.alpha[1]),
-                            line.width=line.wdth[1],
-                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
-                            title_name=paste(plot.i,"->",plot.j),
+  yupper = y.ub[1],
+  color = add.alpha("black", alpha = line.alpha[1]),
+  line.width = line.wdth[1],
+  y.ratio = -0.05, min.y = -2, min.x = 0, max.x = my.xlim,
+  title_name = paste(plot.i, "->", plot.j),
   title.cex = 2,
-                            box.type="n")
-drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
-                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
+  box.type = "n"
+)
+drawHawkesIntensityPaper(
+  lambda0 = model1_par_est$lambda0,
+  alpha = model1_fn$alpha.fun(
+    model1_par_est$f[plot.i],
     model1_par_est$f[plot.j],
@@
     model1_par_est$eta_2,
-                                                   model1_par_est$eta_3),
-                         beta=model1_par_est$beta,
-                         events=temp.t,
-                         color=add.alpha(model_colors[1],
-                                         alpha=line.alpha[2]),
-                         line.width=line.wdth[2])
+    model1_par_est$eta_3
+  ),
+  beta = model1_par_est$beta,
+  events = temp.t,
+  color = add.alpha(model_colors[1],
+    alpha = line.alpha[2]
+  ),
+  line.width = line.wdth[2]
+)
 
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
-
-legend(legend.x[1],legend.y[1],c("True"),
+axis(1,
+  at = c(-2, my.long.x), col = "gray35",
+  line = 0.5, tick = T, labels = rep("", 2), lwd = 0.5, lwd.ticks = 0, lty = 3
+)
+
+legend(legend.x[1], legend.y[1], c("True"),
   col = c("black"),
-       y.intersp=0.88,x.intersp=0.15,bty = "n",
-       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
-legend(legend.x[1]+18,legend.y[1],c("C-HP"),
+  y.intersp = 0.88, x.intersp = 0.15, bty = "n",
+  lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
+)
+legend(legend.x[1] + 18, legend.y[1], c("C-HP"),
   col = c(model_colors[1]),
-       y.intersp=0.88,x.intersp=0.15,bty = "n",
-       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
+  y.intersp = 0.88, x.intersp = 0.15, bty = "n",
+  lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
+)
 
 ## delta lambda
-par(mar = c(0,0.3,0,0.1))
-plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,10), type="n",
-     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
-delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
+par(mar = c(0, 0.3, 0, 0.1))
+plot(0, 0,
+  xlim = c(0, my.xlim), ylim = c(-4, 10), type = "n",
+  bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
+)
+delta.lambda <- lambda.m1$lambda.t - lambda.true$lambda.t
 delta.positive <- delta.lambda
-delta.positive[delta.positive<0] <- 0
+delta.positive[delta.positive < 0] <- 0
 delta.negative <- delta.lambda
-delta.negative[delta.negative>0] <- 0
+delta.negative[delta.negative > 0] <- 0
 ### hiding these for now ###
-polygon(c(0,lambda.true$time.vec,x_events),#200
-        c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,x_events),#200
-        c(0,delta.positive,0),col=positive.col,border=NA)
-
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.negative, 0),
+  col = negative.col, border = NA
+)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.positive, 0),
+  col = positive.col, border = NA
+)
+
+axis(1,
+  at = c(-2, my.long.x), col = "gray35",
+  line = 0, tick = T, labels = rep("", 2), lwd = 0.7, lwd.ticks = 0
+)
 
@@
 ############
-mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
+mod_drawHawkesIntensityPaper(
+  lambda0 = true.object$lambda0,
   alpha = true.object$alpha,
@@
   add = FALSE,
-                            yupper=y.ub[1],
-                            color=add.alpha("black", alpha=line.alpha[1]),
-                            line.width=line.wdth[1],
-                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
-                            title_name=paste(plot.i,"->",plot.j),
+  yupper = y.ub[1],
+  color = add.alpha("black", alpha = line.alpha[1]),
+  line.width = line.wdth[1],
+  y.ratio = -0.05, min.y = -2, min.x = 0, max.x = my.xlim,
+  title_name = paste(plot.i, "->", plot.j),
   title.cex = 2,
-                            box.type="n")
-drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
+  box.type = "n"
+)
+drawHawkesIntensityPaper(
+  lambda0 = model2_par_est$gamma[plot.i] +
     model2_par_est$zeta[plot.j],
-                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
+  alpha = model1_fn$alpha.fun(
+    model2_par_est$f[plot.i],
     model2_par_est$f[plot.j],
@@
     model2_par_est$eta_2,
-                                                   model2_par_est$eta_3),
-                         beta=model2_par_est$beta,
-                         events=temp.t,
-                         color=add.alpha(model_colors[2],
-                                         alpha=line.alpha[2]),
-                         line.width=line.wdth[2])
-legend(legend.x[2],legend.y[2],"C-DCHP",
+    model2_par_est$eta_3
+  ),
+  beta = model2_par_est$beta,
+  events = temp.t,
+  color = add.alpha(model_colors[2],
+    alpha = line.alpha[2]
+  ),
+  line.width = line.wdth[2]
+)
+legend(legend.x[2], legend.y[2], "C-DCHP",
   col = model_colors[2],
-       y.intersp=0.88,x.intersp=0.1,bty = "n",
-       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)
-
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
-
-legend(legend.x[2]-40,
-       legend.y[2]+2,c("State 0/1 events","State change point"),
-       col = c(NA,"red"),
-       y.intersp=0.85,x.intersp=-0.1, bty = "n",
-       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
-       lty = c(NA,NA), lwd=c(NA,4))
-points(legend.x[2]-35,16,pch=1,cex=2,col="blue")
-points(legend.x[2]-34,16,pch=16,cex=2,col="blue")
+  y.intersp = 0.88, x.intersp = 0.1, bty = "n",
+  lty = 1, lwd = 5, cex = legend.cex, seg.len = 1
+)
+
+axis(1,
+  at = c(-2, my.long.x), col = "gray35",
+  line = 0.5, tick = T, labels = rep("", 2), lwd = 0.5, lwd.ticks = 0, lty = 3
+)
+
+legend(legend.x[2] - 40,
+  legend.y[2] + 2, c("State 0/1 events", "State change point"),
+  col = c(NA, "red"),
+  y.intersp = 0.85, x.intersp = -0.1, bty = "n",
+  pch = c(NA, 4), pt.cex = c(NA, 2), cex = legend.cex,
+  lty = c(NA, NA), lwd = c(NA, 4)
+)
+points(legend.x[2] - 35, 16, pch = 1, cex = 2, col = "blue")
+points(legend.x[2] - 34, 16, pch = 16, cex = 2, col = "blue")
 
 ## delta lambda
-par(mar = c(0,0.3,0,0.1))
-delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
-
-plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), ylim=c(-3,10), type="n",
-     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
-delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
+par(mar = c(0, 0.3, 0, 0.1))
+delta.lambda <- lambda.m2$lambda.t - lambda.true$lambda.t
+
+plot(lambda.true$time.vec, delta.lambda,
+  xlim = c(0, my.xlim), ylim = c(-3, 10), type = "n",
+  bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
+)
+delta.lambda <- lambda.m2$lambda.t - lambda.true$lambda.t
 delta.positive <- delta.lambda
-delta.positive[delta.positive<0] <- 0
+delta.positive[delta.positive < 0] <- 0
 delta.negative <- delta.lambda
-delta.negative[delta.negative>0] <- 0
-polygon(c(0,lambda.true$time.vec,x_events), #200
-        c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,x_events), #200
-        c(0,delta.positive,0),col=positive.col,border=NA)
+delta.negative[delta.negative > 0] <- 0
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.negative, 0),
+  col = negative.col, border = NA
+)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.positive, 0),
+  col = positive.col, border = NA
+)
 # segments(0,0,my.xlim,0,col="gray45")
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+axis(1,
+  at = c(-2, my.long.x), col = "gray35",
+  line = 0, tick = T, labels = rep("", 2), lwd = 0.7, lwd.ticks = 0
+)
 
@@
 ########
-par(mar = c(0,0.3,1,0.1))
-mod_drawHawkesIntensityPaper(lambda0 = true.object$lambda0,
+par(mar = c(0, 0.3, 1, 0.1))
+mod_drawHawkesIntensityPaper(
+  lambda0 = true.object$lambda0,
   alpha = true.object$alpha,
@@
   add = FALSE,
-                            yupper=y.ub[1],
-                            color=add.alpha("black", alpha=line.alpha[1]),
-                            line.width=line.wdth[1],
-                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
-                            title_name=paste(plot.i,"->",plot.j),
+  yupper = y.ub[1],
+  color = add.alpha("black", alpha = line.alpha[1]),
+  line.width = line.wdth[1],
+  y.ratio = -0.05, min.y = -2, min.x = 0, max.x = my.xlim,
+  title_name = paste(plot.i, "->", plot.j),
   title.cex = 2,
-                            box.type="n")
+  box.type = "n"
+)
 drawUniMMHPIntensityPaper(object_hat,
   simulation = list(
-  x=state.est.latent.mmhp.new$x.hat,                                          
-  z=state.est.latent.mmhp.new$z.hat,
-  tau=temp.t,
-  lambda.max=max(lambda.m3)),
-                          yupper=y.ub,add=TRUE,
-                          color=add.alpha(model_colors[3],
-                                      alpha=line.alpha[2]),
-  line.width=line.wdth[2])
-legend(legend.x[3],legend.y[3],"C-MMHP",
+    x = state.est.latent.mmhp.new$x.hat,
+    z = state.est.latent.mmhp.new$z.hat,
+    tau = temp.t,
+    lambda.max = max(lambda.m3)
+  ),
+  yupper = y.ub, add = TRUE,
+  color = add.alpha(model_colors[3],
+    alpha = line.alpha[2]
+  ),
+  line.width = line.wdth[2]
+)
+legend(legend.x[3], legend.y[3], "C-MMHP",
   col = model_colors[3],
-       y.intersp=0.88,x.intersp=0.1,bty = "n",
-       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
+  y.intersp = 0.88, x.intersp = 0.1, bty = "n",
+  lty = 1, lwd = 5, cex = legend.cex, seg.len = 1
+)
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
-
-legend(legend.x[3]-40,
-       legend.y[3],c("Overestimation","Underestimation"),
-       col = c(positive.col,negative.col),
-       y.intersp=0.88,x.intersp=0.5,bty = "n",
-       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)
+axis(1,
+  at = c(-2, my.long.x), col = "gray35",
+  line = 0.5, tick = T, labels = rep("", 2), lwd = 0.5, lwd.ticks = 0, lty = 3
+)
+
+legend(legend.x[3] - 40,
+  legend.y[3], c("Overestimation", "Underestimation"),
+  col = c(positive.col, negative.col),
+  y.intersp = 0.88, x.intersp = 0.5, bty = "n",
+  lty = c(1, 1), lwd = c(10, 10), cex = legend.cex, seg.len = 0.8
+)
 
 ## delta lambda
-par(mar = c(0,0.3,0,0.1))
-plot(0,0,xlim=c(0,my.xlim), ylim=c(-12,8), type="n",
-     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
-delta.lambda <- lambda.m3-lambda.true$lambda.t
+par(mar = c(0, 0.3, 0, 0.1))
+plot(0, 0,
+  xlim = c(0, my.xlim), ylim = c(-12, 8), type = "n",
+  bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
+)
+delta.lambda <- lambda.m3 - lambda.true$lambda.t
 delta.positive <- delta.lambda
-delta.positive[delta.positive<0] <- 0
+delta.positive[delta.positive < 0] <- 0
 delta.negative <- delta.lambda
-delta.negative[delta.negative>0] <- 0
+delta.negative[delta.negative > 0] <- 0
 ### hiding these for now
-polygon(c(0,lambda.true$time.vec,x_events), # 200 
-        c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,x_events), # 200 
-        c(0,delta.positive,0),col=positive.col,border=NA)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.negative, 0),
+  col = negative.col, border = NA
+)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.positive, 0),
+  col = positive.col, border = NA
+)
 # segments(0,0,my.xlim,0,col="gray45")
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+axis(1,
+  at = c(-2, my.long.x), col = "gray35",
+  line = 0, tick = T, labels = rep("", 2), lwd = 0.7, lwd.ticks = 0
+)
 
 ## top
-mtext(text="M1 Sim",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
+mtext(text = "M1 Sim", side = 3, line = 0.8, outer = TRUE, cex = 2.5, font = 2)
 ## bottom
-mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.5)
+mtext(text = "Time", side = 1, line = 2, outer = TRUE, cex = 2.5)
 ## left
-mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.5)
-
+mtext(text = "Intensity", side = 2, line = 0.6, outer = TRUE, cex = 2.5)
 ```
@@
 ```{r process m2 for fig4b, include=extra_plots, eval=extra_plots}
-plot.s <- 1#7#9
+plot.s <- 1 # 7#9
 plot.i <- 4
@@
 
-load(paste0(m2_path,m2_files[plot.s]))
-clean_sim_data_m2 <- cleanSimulationData(raw_data = sim_model2_data[[1]], 
+load(paste0(m2_path, m2_files[plot.s]))
+clean_sim_data_m2 <- cleanSimulationData(
+  raw_data = sim_model2_data[[1]],
   cut_off = cut_off,
-                                      N = length(object_par$f_vec_1))
-
-temp.t <- sim_model2_data[[1]]$day_hour[ which(sim_model2_data[[1]]$start == cur_i & 
+  N = length(object_par$f_vec_1)
+)
+
+temp.t <- sim_model2_data[[1]]$day_hour[which(sim_model2_data[[1]]$start == cur_i &
   sim_model2_data[[1]]$end == cur_j)]
 # temp.t <- test.mmhp$tau
-current.n <- length(temp.t)-1
-time.segment <- seq(0,tail(temp.t,1),length.out=5000)
+current.n <- length(temp.t) - 1
+time.segment <- seq(0, tail(temp.t, 1), length.out = 5000)
 
@@
 #########
-model1_par_est <- list(lambda0 = mean(sim_model2_stan_sim1_total[[plot.s]]$lambda0),
+model1_par_est <- list(
+  lambda0 = mean(sim_model2_stan_sim1_total[[plot.s]]$lambda0),
   eta_1 = mean(sim_model2_stan_sim1_total[[plot.s]]$eta_1),
@@
   beta = mean(sim_model2_stan_sim1_total[[plot.s]]$beta),
-                       f = apply(sim_model2_stan_sim1_total[[plot.s]]$f,2,mean))
-lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
+  f = apply(sim_model2_stan_sim1_total[[plot.s]]$f, 2, mean)
+)
+lambda.m1 <- uniHawkesIntensityNumeric(
+  object = list(
+    lambda0 =
       model1_par_est$lambda0,
     alpha =
-                                      model1_fn$alpha.fun(model1_par_est$f[plot.i],
+      model1_fn$alpha.fun(
+        model1_par_est$f[plot.i],
         model1_par_est$f[plot.j],
@@
         model1_par_est$eta_2,
-                                    model1_par_est$eta_3),
-                                    beta=model1_par_est$beta),
-                                     events=temp.t,
-                                     time.vec=time.segment)
+        model1_par_est$eta_3
+      ),
+    beta = model1_par_est$beta
+  ),
+  events = temp.t,
+  time.vec = time.segment
+)
 
@@
 #############
-model2_par_est <- list(gamma = apply(sim_model2_stan_sim2_total[[plot.s]]$gamma,
-                                   2,mean),
-                    zeta = apply(sim_model2_stan_sim2_total[[plot.s]]$zeta,2,mean),
+model2_par_est <- list(
+  gamma = apply(
+    sim_model2_stan_sim2_total[[plot.s]]$gamma,
+    2, mean
+  ),
+  zeta = apply(sim_model2_stan_sim2_total[[plot.s]]$zeta, 2, mean),
   eta_1 = mean(sim_model2_stan_sim2_total[[plot.s]]$eta_1),
@@
   beta = mean(sim_model2_stan_sim2_total[[plot.s]]$beta),
-                    f = apply(sim_model2_stan_sim2_total[[plot.s]]$f, 2, mean))
-
-lambda.m2 <- uniHawkesIntensityNumeric(object=list(
-  lambda0 = model2_par_est$gamma[plot.i]+
+  f = apply(sim_model2_stan_sim2_total[[plot.s]]$f, 2, mean)
+)
+
+lambda.m2 <- uniHawkesIntensityNumeric(
+  object = list(
+    lambda0 = model2_par_est$gamma[plot.i] +
       model2_par_est$zeta[plot.j],
-  alpha = model1_fn$alpha.fun(model2_par_est$f[plot.i],
+    alpha = model1_fn$alpha.fun(
+      model2_par_est$f[plot.i],
       model2_par_est$f[plot.j],
@@
 
-lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
-                       ncol = length(object_par$f_vec_1))
-lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
-                       ncol = length(object_par$f_vec_1))
-
-for(i in seq_along(lam0_vec)) {
+lam0_par_est <- matrix(0,
+  nrow = length(object_par$f_vec_1),
+  ncol = length(object_par$f_vec_1)
+)
+lam1_par_est <- matrix(0,
+  nrow = length(object_par$f_vec_1),
+  ncol = length(object_par$f_vec_1)
+)
+
+for (i in seq_along(lam0_vec)) {
   row_id <- clean_sim_data_m2$I_fit
@@
 
-mmhp_par_est <- list(lambda0 = lam0_par_est,
+mmhp_par_est <- list(
+  lambda0 = lam0_par_est,
   lambda1 = lam1_par_est,
@@
   beta = mean(sim_model2_stan_sim3_total[[plot.s]]$beta),
-                     f = apply(sim_model2_stan_sim3_total[[plot.s]]$f,2,mean))
-
-object_hat <- list(lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
+  f = apply(sim_model2_stan_sim3_total[[plot.s]]$f, 2, mean)
+)
+
+object_hat <- list(
+  lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
   lambda1 = mmhp_par_est$lambda1[cur_i, cur_j],
-                   alpha = model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
+  alpha = model3_fn$alpha.fun(
+    mmhp_par_est$f[cur_i],
     mmhp_par_est$f[cur_j],
     mmhp_par_est$eta_1,
-                                             mmhp_par_est$eta_2),
-                   beta=mmhp_par_est$beta,
-                   q1=model3_fn$q1.fun(mmhp_par_est$f[cur_i],
+    mmhp_par_est$eta_2
+  ),
+  beta = mmhp_par_est$beta,
+  q1 = model3_fn$q1.fun(
+    mmhp_par_est$f[cur_i],
     mmhp_par_est$f[cur_j],
-                                       mmhp_par_est$eta_3),
-                   q2=model3_fn$q0.fun(mmhp_par_est$f[cur_i],
+    mmhp_par_est$eta_3
+  ),
+  q2 = model3_fn$q0.fun(
+    mmhp_par_est$f[cur_i],
     mmhp_par_est$f[cur_j],
-                                       mmhp_par_est$eta_3))
+    mmhp_par_est$eta_3
+  )
+)
 
 state_est_fits <- list.files(m2_path, pattern = "fit123_state_est_M2*")
-load(paste0(m2_path,state_est_fits[plot.s]))
-
-state.est.latent.mmhp <- interpolate_state_est_lst[plot.i,plot.j][[1]]
+load(paste0(m2_path, state_est_fits[plot.s]))
+
+state.est.latent.mmhp <- interpolate_state_est_lst[plot.i, plot.j][[1]]
 state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
-                                                 termination=200)
-
-step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,
-                        2-state.est.latent.mmhp$z.hat)
-
-lambda.m3 <- mmhpIntensityNumeric(params = object_hat,
+  termination = 200
+)
+
+step.fun.est <- stepfun(
+  state.est.latent.mmhp$x.hat,
+  2 - state.est.latent.mmhp$z.hat
+)
+
+lambda.m3 <- mmhpIntensityNumeric(
+  params = object_hat,
   t = temp.t,
   time.vec = time.segment,
-                                  latent.vec = step.fun.est(time.segment))
-
-object_true <- lapply(object_matrix,function(x) x[plot.i,plot.j])
-names(object_true) <- c("lambda0","lambda1","alpha","beta")
-
-lambda.true <- uniHawkesIntensityNumeric(object = object_true,
-                                        events =temp.t,
-                                        time.vec = time.segment)
+  latent.vec = step.fun.est(time.segment)
+)
+
+object_true <- lapply(object_matrix, function(x) x[plot.i, plot.j])
+names(object_true) <- c("lambda0", "lambda1", "alpha", "beta")
+
+lambda.true <- uniHawkesIntensityNumeric(
+  object = object_true,
+  events = temp.t,
+  time.vec = time.segment
+)
 ```
@@
 ```{r fig 4b M2 sim, include=extra_plots, eval=extra_plots}
-source(here("lib","mod_drawHawkesIntensityPaper.R"))
-y.ub <- c(17,17,17)#c(130,72,31)
-x_events <- 135#150
-#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
+source(here("lib", "mod_drawHawkesIntensityPaper.R"))
+y.ub <- c(17, 17, 17) # c(130,72,31)
+x_events <- 135 # 150
+# model_colors <- c("steelblue", "goldenrod2", "firebrick2")
 model_colors <- viridis::viridis(3)
-layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
-layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
-my.xlim <- 140#160#200#130
-my.long.x <- 140#205#134.5
-legend.x <- c(50,50,50)#c(135,135,135)
-legend.y <- #c(34,32,32)
-legend.y <- c(15,12,15)#c(62,37,18)#c(22,22,22)
-legend.cex <- 1.5 #3
-line.alpha <- c(0.9,0.6)
-line.wdth <- c(2,2.5)
-negative.col <- add.alpha('lightskyblue',0.6)
-positive.col <- add.alpha('tomato',0.6)
-#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
-#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
-par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
-    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)
+layout(matrix(c(1:6), 6, 1), heights = rep(c(2.5, 1), 3))
+layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 1), 3))
+my.xlim <- 140 # 160#200#130
+my.long.x <- 140 # 205#134.5
+legend.x <- c(50, 50, 50) # c(135,135,135)
+legend.y <- # c(34,32,32)
+  legend.y <- c(15, 12, 15) # c(62,37,18)#c(22,22,22)
+legend.cex <- 1.5 # 3
+line.alpha <- c(0.9, 0.6)
+line.wdth <- c(2, 2.5)
+negative.col <- add.alpha("lightskyblue", 0.6)
+positive.col <- add.alpha("tomato", 0.6)
+# negative.col <- viridis::viridis(5,alpha = 0.6)[1]
+# positive.col <- viridis::viridis(5,alpha = 0.6)[4]
+par(
+  mar = c(0, 0.3, 0, 0.1), oma = c(3, 3.5, 4, 0),
+  tcl = 0.2, mgp = c(0.5, 0, 0), xpd = TRUE
+)
 
@@
     model2_par_est$eta_2,
-                                                   model2_par_est$eta_3),
-                         beta=model2_par_est$beta,
-                         events=temp.t,
-                         color=add.alpha(model_colors[2],
-                                         alpha=line.alpha[2]),
-                         line.width=line.wdth[2])
-legend(legend.x[2],legend.y[2],"C-DCHP",
+    model2_par_est$eta_3
+  ),
+  beta = model2_par_est$beta,
+  events = temp.t,
+  color = add.alpha(model_colors[2],
+    alpha = line.alpha[2]
+  ),
+  line.width = line.wdth[2]
+)
+legend(legend.x[2], legend.y[2], "C-DCHP",
   col = model_colors[2],
-       y.intersp=0.88,x.intersp=0.1,bty = "n",
-       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)
-
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
-
-legend(10,legend.y[2]+2,c("State 0/1 events","State change point"),
-       col = c(NA,"red"),
-       y.intersp=0.85,x.intersp=-0.1, bty = "n",
-       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
-       lty = c(NA,NA), lwd=c(NA,4))
-points(14,8+2,pch=1,cex=2,col="blue")
-points(16,8+2,pch=16,cex=2,col="blue")
+  y.intersp = 0.88, x.intersp = 0.1, bty = "n",
+  lty = 1, lwd = 5, cex = legend.cex, seg.len = 1
+)
+
+axis(1,
+  at = c(-2, my.long.x), col = "gray35",
+  line = 0.5, tick = T, labels = rep("", 2), lwd = 0.5, lwd.ticks = 0, lty = 3
+)
+
+legend(10, legend.y[2] + 2, c("State 0/1 events", "State change point"),
+  col = c(NA, "red"),
+  y.intersp = 0.85, x.intersp = -0.1, bty = "n",
+  pch = c(NA, 4), pt.cex = c(NA, 2), cex = legend.cex,
+  lty = c(NA, NA), lwd = c(NA, 4)
+)
+points(14, 8 + 2, pch = 1, cex = 2, col = "blue")
+points(16, 8 + 2, pch = 16, cex = 2, col = "blue")
 
 ## delta lambda
-par(mar = c(0,0.3,0,0.1))
-delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
-
-plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), ylim=c(-3,10), type="n",
-     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
-delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
+par(mar = c(0, 0.3, 0, 0.1))
+delta.lambda <- lambda.m2$lambda.t - lambda.true$lambda.t
+
+plot(lambda.true$time.vec, delta.lambda,
+  xlim = c(0, my.xlim), ylim = c(-3, 10), type = "n",
+  bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
+)
+delta.lambda <- lambda.m2$lambda.t - lambda.true$lambda.t
 delta.positive <- delta.lambda
-delta.positive[delta.positive<0] <- 0
+delta.positive[delta.positive < 0] <- 0
 delta.negative <- delta.lambda
-delta.negative[delta.negative>0] <- 0
-polygon(c(0,lambda.true$time.vec,x_events), #200
-        c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,x_events), #200
-        c(0,delta.positive,0),col=positive.col,border=NA)
+delta.negative[delta.negative > 0] <- 0
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.negative, 0),
+  col = negative.col, border = NA
+)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.positive, 0),
+  col = positive.col, border = NA
+)
 # segments(0,0,my.xlim,0,col="gray45")
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+axis(1,
+  at = c(-2, my.long.x), col = "gray35",
+  line = 0, tick = T, labels = rep("", 2), lwd = 0.7, lwd.ticks = 0
+)
 
@@
   add = FALSE,
-                            yupper=y.ub[1],
-                            color=add.alpha("black", alpha=line.alpha[1]),
-                            line.width=line.wdth[1],
-                            y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
-                            title_name=paste(plot.i,"->",plot.j),
+  yupper = y.ub[1],
+  color = add.alpha("black", alpha = line.alpha[1]),
+  line.width = line.wdth[1],
+  y.ratio = -0.05, min.y = -2, min.x = 0, max.x = my.xlim,
+  title_name = paste(plot.i, "->", plot.j),
   title.cex = 2,
-                            box.type="n")
+  box.type = "n"
+)
 drawUniMMHPIntensityPaper(object_hat,
   simulation = list(
-  x=state.est.latent.mmhp.new$x.hat,                                          
-  z=state.est.latent.mmhp.new$z.hat,
-  tau=temp.t,
-  lambda.max=max(lambda.m3)),
-                          yupper=y.ub,add=TRUE,
-                          color=add.alpha(model_colors[3],
-                                      alpha=line.alpha[2]),
-  line.width=line.wdth[2])
-legend(legend.x[3],legend.y[3],"C-MMHP",
+    x = state.est.latent.mmhp.new$x.hat,
+    z = state.est.latent.mmhp.new$z.hat,
+    tau = temp.t,
+    lambda.max = max(lambda.m3)
+  ),
+  yupper = y.ub, add = TRUE,
+  color = add.alpha(model_colors[3],
+    alpha = line.alpha[2]
+  ),
+  line.width = line.wdth[2]
+)
+legend(legend.x[3], legend.y[3], "C-MMHP",
   col = model_colors[3],
-       y.intersp=0.88,x.intersp=0.1,bty = "n",
-       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
+  y.intersp = 0.88, x.intersp = 0.1, bty = "n",
+  lty = 1, lwd = 5, cex = legend.cex, seg.len = 1
+)
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
-
-legend(10,legend.y[3],c("Overestimation","Underestimation"),
-       col = c(positive.col,negative.col),
-       y.intersp=0.88,x.intersp=0.5,bty = "n",
-       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)
+axis(1,
+  at = c(-2, my.long.x), col = "gray35",
+  line = 0.5, tick = T, labels = rep("", 2), lwd = 0.5, lwd.ticks = 0, lty = 3
+)
+
+legend(10, legend.y[3], c("Overestimation", "Underestimation"),
+  col = c(positive.col, negative.col),
+  y.intersp = 0.88, x.intersp = 0.5, bty = "n",
+  lty = c(1, 1), lwd = c(10, 10), cex = legend.cex, seg.len = 0.8
+)
 
 ## delta lambda
-par(mar = c(0,0.3,0,0.1))
-plot(0,0,xlim=c(0,my.xlim), ylim=c(-12,8), type="n",
-     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
-delta.lambda <- lambda.m3-lambda.true$lambda.t
+par(mar = c(0, 0.3, 0, 0.1))
+plot(0, 0,
+  xlim = c(0, my.xlim), ylim = c(-12, 8), type = "n",
+  bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
+)
+delta.lambda <- lambda.m3 - lambda.true$lambda.t
 delta.positive <- delta.lambda
-delta.positive[delta.positive<0] <- 0
+delta.positive[delta.positive < 0] <- 0
 delta.negative <- delta.lambda
-delta.negative[delta.negative>0] <- 0
+delta.negative[delta.negative > 0] <- 0
 ### hiding these for now
-polygon(c(0,lambda.true$time.vec,x_events), # 200 
-        c(0,delta.negative,0),col=negative.col,border=NA)
-polygon(c(0,lambda.true$time.vec,x_events), # 200 
-        c(0,delta.positive,0),col=positive.col,border=NA)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.negative, 0),
+  col = negative.col, border = NA
+)
+polygon(c(0, lambda.true$time.vec, x_events), # 200
+  c(0, delta.positive, 0),
+  col = positive.col, border = NA
+)
 # segments(0,0,my.xlim,0,col="gray45")
 ## draw box
-axis(1,at=c(-2,my.long.x),col="gray35",
-     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
+axis(1,
+  at = c(-2, my.long.x), col = "gray35",
+  line = 0, tick = T, labels = rep("", 2), lwd = 0.7, lwd.ticks = 0
+)
 
 ## top
-mtext(text="M2 Sim",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
+mtext(text = "M2 Sim", side = 3, line = 0.8, outer = TRUE, cex = 2.5, font = 2)
 ## bottom
-mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.5)
+mtext(text = "Time", side = 1, line = 2, outer = TRUE, cex = 2.5)
 ## left
-mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.5)
-
+mtext(text = "Intensity", side = 2, line = 0.6, outer = TRUE, cex = 2.5)
 ```
@@
 # Figure 5:
+
+To be updated!
+
 ```{r data for fig 5,cache=TRUE}
@@
 ## Initialize
-N_array <- array(0, dim = c(n_sim, length(object_par$f_vec_1),
-                         length(object_par$f_vec_1))) 
-Lambda_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                     length(object_par$f_vec_1))) 
-Lambda_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                     length(object_par$f_vec_1)))
-Lambda_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                     length(object_par$f_vec_1))) 
-Lambda_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                   length(object_par$f_vec_1))) 
-PR_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                 length(object_par$f_vec_1)))
-PR_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                 length(object_par$f_vec_1))) 
-PR_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                 length(object_par$f_vec_1)))
-PR_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                               length(object_par$f_vec_1))) 
-KS_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                 length(object_par$f_vec_1)))
-KS_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                 length(object_par$f_vec_1)))
-KS_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                    length(object_par$f_vec_1)))
-KS_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                               length(object_par$f_vec_1)))
-KS_p_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                   length(object_par$f_vec_1)))
-KS_p_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                   length(object_par$f_vec_1)))
-KS_p_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                    length(object_par$f_vec_1)))
-KS_p_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
-                                    length(object_par$f_vec_1)))
+N_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+Lambda_model3_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+Lambda_model1_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+Lambda_model2_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+Lambda_true_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+PR_model1_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+PR_model2_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+PR_model3_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+PR_true_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_model1_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_model2_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_model3_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_true_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_p_model1_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_p_model2_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_p_model3_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
+KS_p_true_array <- array(0, dim = c(
+  n_sim, length(object_par$f_vec_1),
+  length(object_par$f_vec_1)
+))
 
 ## Iteration on 50 simulations
-for(s in c(1:n_sim)){
-  load(paste0(sim_data_path,"sim_model3_fit123_",s,".RData"))
-  load(paste(sim_data_path,"fit123_state_est_",s,".RData",sep=''))
-  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data, 
+for (s in c(1:n_sim)) {
+  load(paste0(sim_data_path, "sim_model3_fit123_", s, ".RData"))
+  load(paste(sim_data_path, "fit123_state_est_", s, ".RData", sep = ""))
+  clean_sim_data <- cleanSimulationData(
+    raw_data = sim_model3_data,
     cut_off = cut_off,
-                                        N = length(object_par$f_vec_1))
-
-  N_array[s,,] <- clean_sim_data$N_count
+    N = length(object_par$f_vec_1)
+  )
+
+  N_array[s, , ] <- clean_sim_data$N_count
 
@@
   #########
-  model1_par_est <- list(lambda0 = mean(sim_model3_stan_sim1$lambda0),
+  model1_par_est <- list(
+    lambda0 = mean(sim_model3_stan_sim1$lambda0),
     eta_1 = mean(sim_model3_stan_sim1$eta_1),
@@
     beta = mean(sim_model3_stan_sim1$beta),
-                         f = apply(sim_model3_stan_sim1$f, 2, mean))
-
-  for(i in c(1:5)){
-    for(j in c(1:5)[-i]){
-      current_t <- sim_model3_data$mmhp_matrix[i,j][[1]]$tau
-      m1_object <- list(lambda0 = model1_par_est$lambda0,
-                        alpha = model1_fn$alpha.fun(model1_par_est$f[i],
+
+    ### TO DO
+    f = apply(sim_model3_stan_sim1$f, 2, mean)
+  )
+
+  for (i in c(1:5)) {
+    for (j in c(1:5)[-i]) {
+      current_t <- sim_model3_data$mmhp_matrix[i, j][[1]]$tau
+      m1_object <- list(
+        lambda0 = model1_par_est$lambda0,
+        alpha = model1_fn$alpha.fun(
+          model1_par_est$f[i],
           model1_par_est$f[j],
@@
           model1_par_est$eta_2,
-                                                  model1_par_est$eta_3),
-                        beta = model1_par_est$beta)
-      Lambda_model1_array[s,i,j] <- 
-        uniHawkesIntegralIntensity(object = m1_object, 
+          model1_par_est$eta_3
+        ),
+        beta = model1_par_est$beta
+      )
+      Lambda_model1_array[s, i, j] <-
+        uniHawkesIntegralIntensity(
+          object = m1_object,
           events = current_t,
-                                   termination = tail(current_t,1))
-      Lambda_test <- uniHawkesCompensator(object = m1_object, 
-                                          events = current_t)
-      KS_model1_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$statistic
-      KS_p_model1_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
-      PR_model1_array[s,i,j] <- uniHawkesPearsonResidual(object = m1_object, 
+          termination = tail(current_t, 1)
+        )
+      Lambda_test <- uniHawkesCompensator(
+        object = m1_object,
+        events = current_t
+      )
+      KS_model1_array[s, i, j] <- ks.test(Lambda_test, "pexp")$statistic
+      KS_p_model1_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
+      PR_model1_array[s, i, j] <- uniHawkesPearsonResidual(
+        object = m1_object,
         events = current_t,
         termination =
-                                                           tail(current_t,1))
+          tail(current_t, 1)
+      )
     }
@@
   #############
-  model2_par_est <- list(gamma = apply(sim_model3_stan_sim2$gamma, 2, mean),
-                         zeta = apply(sim_model3_stan_sim2$zeta,2,mean),
+  model2_par_est <- list(
+
+    ### TO DO
+    gamma = apply(sim_model3_stan_sim2$gamma, 2, mean),
+    zeta = apply(sim_model3_stan_sim2$zeta, 2, mean),
     eta_1 = mean(sim_model3_stan_sim2$eta_1),
@@
     beta = mean(sim_model3_stan_sim2$beta),
-                         f = apply(sim_model3_stan_sim2$f, 2, mean))
-
-  for(i in c(1:5)){
-    for(j in c(1:5)[-i]){
-      current_t <- sim_model3_data$mmhp_matrix[i,j][[1]]$tau
-      m2_object <- list(lambda0 = model2_par_est$gamma[i] + 
+    f = apply(sim_model3_stan_sim2$f, 2, mean)
+  )
+
+  for (i in c(1:5)) {
+    for (j in c(1:5)[-i]) {
+      current_t <- sim_model3_data$mmhp_matrix[i, j][[1]]$tau
+      m2_object <- list(
+        lambda0 = model2_par_est$gamma[i] +
           model2_par_est$zeta[j],
-                        alpha = model1_fn$alpha.fun(model2_par_est$f[i],
+        alpha = model1_fn$alpha.fun(
+          model2_par_est$f[i],
           model2_par_est$f[j],
@@
           model2_par_est$eta_2,
-                                                    model2_par_est$eta_3),
-                        beta = model2_par_est$beta)
-      Lambda_model2_array[s,i,j] <-
-        uniHawkesIntegralIntensity(object = m1_object, 
+          model2_par_est$eta_3
+        ),
+        beta = model2_par_est$beta
+      )
+      Lambda_model2_array[s, i, j] <-
+        uniHawkesIntegralIntensity(
+          object = m1_object,
           events = current_t,
-                                   termination = tail(current_t,1))
-      Lambda_test <- uniHawkesCompensator(object = m2_object,
-                                          events = current_t)
-      KS_model2_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$statistic
-      KS_p_model2_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
-      PR_model2_array[s,i,j] <- 
-        uniHawkesPearsonResidual(object = m2_object, 
+          termination = tail(current_t, 1)
+        )
+      Lambda_test <- uniHawkesCompensator(
+        object = m2_object,
+        events = current_t
+      )
+      KS_model2_array[s, i, j] <- ks.test(Lambda_test, "pexp")$statistic
+      KS_p_model2_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
+      PR_model2_array[s, i, j] <-
+        uniHawkesPearsonResidual(
+          object = m2_object,
           events = current_t,
-                                 termination = tail(current_t,1))
+          termination = tail(current_t, 1)
+        )
     }
@@
   ## then put these into a matrix
-  lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
-                         ncol = length(object_par$f_vec_1))
-  lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
-                         ncol = length(object_par$f_vec_1))
-  for(i in seq_along(lambda_0_est)) {
+  lam0_par_est <- matrix(0,
+    nrow = length(object_par$f_vec_1),
+    ncol = length(object_par$f_vec_1)
+  )
+  lam1_par_est <- matrix(0,
+    nrow = length(object_par$f_vec_1),
+    ncol = length(object_par$f_vec_1)
+  )
+  for (i in seq_along(lambda_0_est)) {
     row_id <- clean_sim_data$I_fit[i]
     col_id <- clean_sim_data$J_fit[i]
+    ### TO DO
     lam0_par_est[row_id, col_id] <- lambda_0_est[i]
@@
   }
-  mmhp_par_est <- list(lambda0 = lam0_par_est,
+  mmhp_par_est <- list(
+    lambda0 = lam0_par_est,
     lambda1 = lam1_par_est,
@@
     beta = mean(sim_model3_stan_sim3$beta),
-                       f = apply(sim_model3_stan_sim3$f,2,mean))
-  clean_sim_data <- cleanSimulationData(raw_data = sim_model3_data, 
+    f = apply(sim_model3_stan_sim3$f, 2, mean)
+  )
+  clean_sim_data <- cleanSimulationData(
+    raw_data = sim_model3_data,
     cut_off = cut_off,
-                                        N = length(object_par$f_vec_1))
-
-  for(i in c(1:5)){
-    for(j in c(1:5)[-i]){
-      test.mmhp <- sim_model3_data$mmhp_matrix[i,j][[1]]
+    N = length(object_par$f_vec_1)
+  )
+
+  for (i in c(1:5)) {
+    for (j in c(1:5)[-i]) {
+      test.mmhp <- sim_model3_data$mmhp_matrix[i, j][[1]]
       temp.t <- test.mmhp$tau
-      current.n <- length(temp.t)-1
-      time.segment <- seq(0,tail(temp.t,1),length.out=10000)
-
-      object_hat <- list(lambda0=mmhp_par_est$lambda0[i,j],
-                         lambda1=mmhp_par_est$lambda1[i,j],
-                         alpha=model3_fn$alpha.fun(mmhp_par_est$f[i],
+      current.n <- length(temp.t) - 1
+      time.segment <- seq(0, tail(temp.t, 1), length.out = 10000)
+
+      object_hat <- list(
+        lambda0 = mmhp_par_est$lambda0[i, j],
+        lambda1 = mmhp_par_est$lambda1[i, j],
+        alpha = model3_fn$alpha.fun(
+          mmhp_par_est$f[i],
           mmhp_par_est$f[j],
           mmhp_par_est$eta_1,
-                                                   mmhp_par_est$eta_2),
-                         beta=mmhp_par_est$beta,
-                         q1=model3_fn$q1.fun(mmhp_par_est$f[i],
+          mmhp_par_est$eta_2
+        ),
+        beta = mmhp_par_est$beta,
+        q1 = model3_fn$q1.fun(
+          mmhp_par_est$f[i],
           mmhp_par_est$f[j],
-                                             mmhp_par_est$eta_3),
-                         q2=model3_fn$q0.fun(mmhp_par_est$f[i],
+          mmhp_par_est$eta_3
+        ),
+        q2 = model3_fn$q0.fun(
+          mmhp_par_est$f[i],
           mmhp_par_est$f[j],
-                                             mmhp_par_est$eta_3))
-
-      object_true <- lapply(object_matrix,function(x) x[i,j])
-      names(object_true) <- c("lambda0","lambda1","alpha","beta","q1","q2")
+          mmhp_par_est$eta_3
+        )
+      )
+
+      object_true <- lapply(object_matrix, function(x) x[i, j])
+      names(object_true) <- c("lambda0", "lambda1",
+                              "alpha", "beta", "q1", "q2")
 
       ## est Lmabda and [R]
-      Lambda.test <- mmhpCompensator(params = object_hat, 
+      Lambda.test <- mmhpCompensator(
+        params = object_hat,
         t = temp.t,
-                                     pzt=2 - 
-                                       event_state_est_lst[i,j][[1]]$zt_v,
-                                     if.pzt = FALSE)
-      KS_model3_array[s,i,j] <-  ks.test(Lambda.test,"pexp")$statistic
-      KS_p_model3_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
-      state.est.latent.mmhp <- interpolate_state_est_lst[i,j][[1]]
-      step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,
-                              2 - state.est.latent.mmhp$z.hat)
-      est.intensity <- mmhpIntensityNumeric(params = object_hat,
+        pzt = 2 -
+          event_state_est_lst[i, j][[1]]$zt_v,
+        if.pzt = FALSE
+      )
+      KS_model3_array[s, i, j] <- ks.test(Lambda.test, "pexp")$statistic
+      KS_p_model3_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
+      state.est.latent.mmhp <- interpolate_state_est_lst[i, j][[1]]
+      step.fun.est <- stepfun(
+        state.est.latent.mmhp$x.hat,
+        2 - state.est.latent.mmhp$z.hat
+      )
+      est.intensity <- mmhpIntensityNumeric(
+        params = object_hat,
         t = temp.t[-1],
@@
         latent.vec =
-                                              step.fun.est(time.segment))
-      est.intensity.events <- mmhpIntensityAtEvents(params=object_hat,
+          step.fun.est(time.segment)
+      )
+      est.intensity.events <- mmhpIntensityAtEvents(
+        params = object_hat,
         t = temp.t,
         latent_z =
-                                    event_state_est_lst[i,j][[1]]$zt_v)
-      Lambda_model3_array[s,i,j] <-
-        sum(est.intensity)*(time.segment[2]-time.segment[1])
-      PR_model3_array[s,i,j] <- sum(1/sqrt(est.intensity.events))-
-        sum(sqrt(est.intensity))*(time.segment[2]-time.segment[1])
+          event_state_est_lst[i, j][[1]]$zt_v
+      )
+      Lambda_model3_array[s, i, j] <-
+        sum(est.intensity) * (time.segment[2] - time.segment[1])
+      PR_model3_array[s, i, j] <- sum(1 / sqrt(est.intensity.events)) -
+        sum(sqrt(est.intensity)) * (time.segment[2] - time.segment[1])
 
       ## Under the true model
-      Lambda.test.true <- mmhpCompensator(params = object_true,
+      Lambda.test.true <- mmhpCompensator(
+        params = object_true,
         t = temp.t,
@@
           test.mmhp$zt[2:length(test.mmhp$zt)],
-                                          if.pzt=FALSE)
-      KS_true_array[s,i,j] <-  ks.test(Lambda.test.true,"pexp")$statistic
-      KS_p_true_array[s,i,j] <-  ks.test(Lambda.test.true,"pexp")$p.value
+        if.pzt = FALSE
+      )
+      KS_true_array[s, i, j] <- ks.test(Lambda.test.true, "pexp")$statistic
+      KS_p_true_array[s, i, j] <- ks.test(Lambda.test.true, "pexp")$p.value
       true.intensity <-
-        mmhpTrueIntensityNumeric(params = object_true,
+        mmhpTrueIntensityNumeric(
+          params = object_true,
           t = temp.t,
-                                 latent = list(x = 
+          latent = list(
+            x =
               fixStateTransition(test.mmhp)$x,
             z =
-                                                fixStateTransition(test.mmhp)$z),
-                                     time.vec = time.segment)
-      true.intensity.events <- mmhpIntensityAtEvents(params = object_true,
+              fixStateTransition(test.mmhp)$z
+          ),
+          time.vec = time.segment
+        )
+      true.intensity.events <- mmhpIntensityAtEvents(
+        params = object_true,
         t = temp.t,
-                                                     latent_z = test.mmhp$zt)
-      Lambda_true_array[s,i,j] <- sum(true.intensity$lambda.t)*(time.segment[2]-time.segment[1])
-      PR_true_array[s,i,j] <- sum(1/sqrt(true.intensity.events))-
-        sum(sqrt(true.intensity$lambda.t))*(time.segment[2]-time.segment[1])
-    }
-  }
-}
-
+        latent_z = test.mmhp$zt
+      )
+      Lambda_true_array[s, i, j] <- sum(true.intensity$lambda.t) *
+        (time.segment[2] - time.segment[1])
+      PR_true_array[s, i, j] <- sum(1 / sqrt(true.intensity.events)) -
+        sum(sqrt(true.intensity$lambda.t)) *
+        (time.segment[2] - time.segment[1])
+    }
+  }
+}
 ```
@@
 
-cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
-                                 "True")) %>%
-  arrange(factor(method, levels = c("C-HP","C-DCHP","C-MMHP","True"))) %>%
+cols_plot <- col_df %>%
+  filter(method %in% c(
+    "C-HP", "C-DCHP", "C-MMHP",
+    "True"
+  )) %>%
+  arrange(factor(method, levels = c("C-HP", "C-DCHP", "C-MMHP", "True"))) %>%
   pull(cols)
-#load("../output/sim_model3_fit123_residuals.RData")
-par(mfrow=c(5,5),mar=c(0.2,0.2,0.2,0.2),oma=c(2.4,2.4,2.9,0.5))
-for(i in c(5:1)){
-  for(j in c(5:1)){
-    if(i==j){
-      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
-           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
-      if(i==5){
-        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04, 
-                col = cols_plot[1], border = NA)
-        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,
-                col = cols_plot[2], border = NA)
-        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,
-                col = cols_plot[3], border = NA)
-        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,
-                col = cols_plot[4], border = NA)
-        text(c(0.43,0.58,0.61,0.4), seq(0.8,0.14,-0.22),
+# load("../output/sim_model3_fit123_residuals.RData")
+par(mfrow = c(5, 5), mar = c(0.2, 0.2, 0.2, 0.2), oma = c(2.4, 2.4, 2.9, 0.5))
+for (i in c(5:1)) {
+  for (j in c(5:1)) {
+    if (i == j) {
+      plot(1, 1,
+        type = "n", xlim = c(0, 1), ylim = c(0, 1),
+        bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
+      )
+      if (i == 5) {
+        polygon(c(0, 0, 0.15, 0.15), c(0.72, 0.8, 0.8, 0.72) + 0.04,
+          col = cols_plot[1], border = NA
+        )
+        polygon(c(0, 0, 0.15, 0.15), c(0.72, 0.8, 0.8, 0.72) + 0.04 - 0.22,
+          col = cols_plot[2], border = NA
+        )
+        polygon(c(0, 0, 0.15, 0.15), c(0.72, 0.8, 0.8, 0.72) + 0.04 - 0.44,
+          col = cols_plot[3], border = NA
+        )
+        polygon(c(0, 0, 0.15, 0.15), c(0.72, 0.8, 0.8, 0.72) + 0.04 - 0.66,
+          col = cols_plot[4], border = NA
+        )
+        text(c(0.43, 0.58, 0.61, 0.4), seq(0.8, 0.14, -0.22),
           c("C-HP", "C-DCHP", "C-MMHP", "True"),
-             cex=1.7)
-      }
-    }else{
+          cex = 1.7
+        )
+      }
+    } else {
       # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
       #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
-      PR <- c(KS_model1_array[,i,j], KS_model2_array[,i,j],
-              KS_model3_array[,i,j], KS_true_array[,i,j])
+      PR <- c(
+        KS_model1_array[, i, j], KS_model2_array[, i, j],
+        KS_model3_array[, i, j], KS_true_array[, i, j]
+      )
       ### try pr scores instead
@@
       #         PR_model3_array[,i,j],PR_true_array[,i,j])
-      Type <- c(rep(1,n_sim), rep(2,n_sim), rep(3,n_sim), rep(4,n_sim))
+      Type <- c(rep(1, n_sim), rep(2, n_sim), rep(3, n_sim), rep(4, n_sim))
       boxplot(PR ~ Type,
         col = cols_plot,
-              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
-              xlab="",ylab="",xaxt="n",yaxt="n")
-      #names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
-    }
-  }
-}
-mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
-      at=c(0:4)/5+0.1)
-mtext(text=c(5:1), side=1, line=1.5, outer=TRUE, cex=2,
-      at=c(0:4)/5+0.1)
-mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)
-
+        # col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),
+        xlab = "", ylab = "", xaxt = "n", yaxt = "n"
+      )
+      # names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
+    }
+  }
+}
+mtext(
+  text = c(1:5), side = 2, line = 0.5, outer = TRUE, cex = 2, las = 2,
+  at = c(0:4) / 5 + 0.1
+)
+mtext(
+  text = c(5:1), side = 1, line = 1.5, outer = TRUE, cex = 2,
+  at = c(0:4) / 5 + 0.1
+)
+mtext(text = "(a)", side = 3, line = 0.5, outer = TRUE, cex = 2.5, font = 2)
 ```
@@
 sim_files <- list.files(here("output", "sims_m3_update"),
-                        pattern = "rank_sim")
+  pattern = "rank_sim"
+)
 
 all_sims <- list()
-for(i in seq_along(sim_files)) {
- single_fit <- readRDS(here("output", "sims_m3_update",
-                            sim_files[i]))
+for (i in seq_along(sim_files)) {
+  single_fit <- readRDS(here(
+    "output", "sims_m3_update",
+    sim_files[i]
+  ))
   all_sims[[i]] <- single_fit
@@
     select(m1:glicko) %>%
-    purrr::map( ~cor.test(truth, .x,
-                   method = "spearman")$estimate  ) %>%
+    purrr::map(~ cor.test(truth, .x,
+      method = "spearman"
+    )$estimate) %>%
     enframe() %>%
@@
   name == "agg" ~ "AggRank",
-          name == "glicko" ~ "Glicko")
-
-sim_data$name <- factor(sim_data$name, levels = c("I&SI",
+  name == "glicko" ~ "Glicko"
+)
+
+sim_data$name <- factor(sim_data$name, levels = c(
+  "I&SI",
   "AggRank",
@@
   "C-DCHP",
-                                                  "C-MMHP"))
-
-plot_cols <- col_df %>% filter(method %in% levels(sim_data$name)) %>%
+  "C-MMHP"
+))
+
+plot_cols <- col_df %>%
+  filter(method %in% levels(sim_data$name)) %>%
   pull(cols)
@@
   rename(Method = name, corr = value) %>%
-  ggplot(aes(Method,corr)) + 
+  ggplot(aes(Method, corr)) +
   geom_boxplot(aes(fill = Method), alpha = 0.7) +
   scale_fill_manual(values = plot_cols) +
-  labs(y = "Rank Correlation") + theme_bw() +
-  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+  labs(y = "Rank Correlation") +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
     text = element_text(size = 20),
-        axis.text.x=element_blank(),
+    axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
-        legend.position="right") + ggtitle("(b)")
+    legend.position = "right"
+  ) +
+  ggtitle("(b)")
 ```
@@
 
-load(paste(data_path,cohort_names[current_cohort],
-           "/agg_rank_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
-load(paste(data_path,cohort_names[current_cohort],
-           "/cohort_hp_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
-load(paste(data_path,cohort_names[current_cohort],
-           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
-load(paste(data_path,cohort_names[current_cohort],
-           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
+load(paste(data_path, cohort_names[current_cohort],
+  "/agg_rank_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+load(paste(data_path, cohort_names[current_cohort],
+  "/cohort_hp_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+load(paste(data_path, cohort_names[current_cohort],
+  "/cohort_dchp_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+load(paste(data_path, cohort_names[current_cohort],
+  "/cohort_mmhp_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
 
 no_method <- 4
-plot_latent_df <- data.frame(Methods=rep(1:no_method,each=1000*mice_number),
-                             Mice=rep(rep(1:mice_number,each=1000),no_method),
-                             force=rep(0,1000*mice_number*no_method))
+plot_latent_df <- data.frame(
+  Methods = rep(1:no_method, each = 1000 * mice_number),
+  Mice = rep(rep(1:mice_number, each = 1000), no_method),
+  force = rep(0, 1000 * mice_number * no_method)
+)
 ## agg
-plot_latent_df$force[(1:(1000*mice_number))] <- as.vector(sim_agg_rank$x[1001:2000,])
+plot_latent_df$force[(1:(1000 * mice_number))] <- as.vector(sim_agg_rank$x[1001:2000, ])
 
 ## M1
-plot_latent_df$force[(1:(1000*mice_number))+1000*mice_number] <- as.vector(sim_cohort_hp$f)
+plot_latent_df$force[(1:(1000 * mice_number)) + 1000 * mice_number] <- as.vector(sim_cohort_hp$f)
 
 ## M2
-plot_latent_df$force[(1:(1000*mice_number))+2000*mice_number] <- as.vector(sim_cohort_dchp$f)
+plot_latent_df$force[(1:(1000 * mice_number)) + 2000 * mice_number] <- as.vector(sim_cohort_dchp$f)
 
 ## M3
-plot_latent_df$force[(1:(1000*mice_number))+3000*mice_number] <- as.vector(sim_cohort_mmhp$f)
+plot_latent_df$force[(1:(1000 * mice_number)) + 3000 * mice_number] <- as.vector(sim_cohort_mmhp$f)
 
 plot_latent_df$Mice <- factor(plot_latent_df$Mice,
-                              levels = expert_rank_10[[current_cohort]])
+  levels = expert_rank_10[[current_cohort]]
+)
 plot_latent_df$Method <- factor(plot_latent_df$Method,
-                                labels = c("AggRanking","C-HP","C-DCHP","C-MMHP"))
+  labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP")
+)
 
 # png(paste(plot_path,"real_rank_one_cohort.png",sep=""),width=600,height=300)
-plot_cols <- col_df %>% filter(method %in% c("AggRank", "C-HP",
-                                "C-DCHP", "C-MMHP")) %>%
+plot_cols <- col_df %>%
+  filter(method %in% c(
+    "AggRank", "C-HP",
+    "C-DCHP", "C-MMHP"
+  )) %>%
   pull(cols)
 
-p1 <- ggplot(plot_latent_df, 
-             aes(x = Mice, y = force, fill = Method)) +
-  geom_boxplot(alpha=0.7) +
-  scale_fill_manual(values = plot_cols)+
-  #scale_fill_manual(values = c("gray", "steelblue", "goldenrod2" , "firebrick2")) +
+p1 <- ggplot(
+  plot_latent_df,
+  aes(x = Mice, y = force, fill = Method)
+) +
+  geom_boxplot(alpha = 0.7) +
+  scale_fill_manual(values = plot_cols) +
+  # scale_fill_manual(values = c("gray", "steelblue", "goldenrod2" , "firebrick2")) +
   ggtitle("(a)") +
   theme_bw() +
-  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+  theme(
+    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
     text = element_text(size = 20),
-        axis.text.x=element_text(size = 10),
-        legend.position="none") +
-  facet_grid(cols=vars(Method)) +
+    axis.text.x = element_text(size = 10),
+    legend.position = "none"
+  ) +
+  facet_grid(cols = vars(Method)) +
   xlab("Mice (ranked by I&SI method)") +
@@
 p1
-#dev.off()
-
+# dev.off()
 ```
@@
 load("../output/weighted_rank_data.RData")
-#png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
+# png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
 no_method <- 4
-plot_cor_df <- data.frame(Method=rep(c(1:no_method),each=10),
-                          cor=as.vector(spearman_df))
+plot_cor_df <- data.frame(
+  Method = rep(c(1:no_method), each = 10),
+  cor = as.vector(spearman_df)
+)
 plot_cor_df$Method <- factor(plot_cor_df$Method,
-                             labels = c("Agg-rank","C-HP","C-DCHP","C-MMHP"))
-p2 <- ggplot(plot_cor_df, aes(x="", y = cor, fill = Method)) +
-        geom_boxplot(alpha=0.7, width=0.5) +
+  labels = c("Agg-rank", "C-HP", "C-DCHP", "C-MMHP")
+)
+p2 <- ggplot(plot_cor_df, aes(x = "", y = cor, fill = Method)) +
+  geom_boxplot(alpha = 0.7, width = 0.5) +
   scale_fill_manual(values = plot_cols) +
   ggtitle("(b)") +
-        ylim(0,1) +
+  ylim(0, 1) +
   theme_bw() +
-        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+  theme(
+    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
     text = element_text(size = 20),
-              axis.text.y =element_text(size = 11),
-              legend.position="none",
-              axis.title.x=element_blank()) +
-        facet_grid(cols=vars(Method)) +
+    axis.text.y = element_text(size = 11),
+    legend.position = "none",
+    axis.title.x = element_blank()
+  ) +
+  facet_grid(cols = vars(Method)) +
   ylab("Spearman rank correlation")
 p2
-
 ```
@@
 
-m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                   "/chp_pr_matrix_",cohort_names[current_cohort],
-                   ".RDS",sep=''))
-
-m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                     "/dchp_pr_matrix_",cohort_names[current_cohort],
-                     ".RDS",sep=''))
-
-m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                     "/cmmhp_pr_matrix_",cohort_names[current_cohort],
-                     ".RDS",sep=''))
-
-indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                     "/immhp_pr_matrix_",cohort_names[current_cohort],
-                     ".RDS",sep=''))
+m1_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+  "/chp_pr_matrix_", cohort_names[current_cohort],
+  ".RDS",
+  sep = ""
+))
+
+m2_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+  "/dchp_pr_matrix_", cohort_names[current_cohort],
+  ".RDS",
+  sep = ""
+))
+
+m3_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+  "/cmmhp_pr_matrix_", cohort_names[current_cohort],
+  ".RDS",
+  sep = ""
+))
+
+indep_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+  "/immhp_pr_matrix_", cohort_names[current_cohort],
+  ".RDS",
+  sep = ""
+))
 
 matrix_lst_plot <- list(
-                        indep_pr[rev(expert_rank_10[[current_cohort]]),
-                                                                   expert_rank_10[[current_cohort]]],
-                        m1_pr[rev(expert_rank_10[[current_cohort]]),
-                                                                 expert_rank_10[[current_cohort]]],
-                        m2_pr[rev(expert_rank_10[[current_cohort]]),
-                                                                 expert_rank_10[[current_cohort]]],
-                        m3_pr[rev(expert_rank_10[[current_cohort]]),
-                                                                 expert_rank_10[[current_cohort]]]) 
-#cat("Cohort ",current_cohort,"\n",sep="")
-myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
-                  xLabels=expert_rank_10[[current_cohort]],
-                  yLabels=rev(expert_rank_10[[current_cohort]]),
-                  min=-80,max=80,axis_cex=2,title_cex = 1.8,
-                  colorPalette="RdBu",if.emp=FALSE,
-                  #legend.mar=c(0.5,.5,0.5,0.5),
-                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
-                  #title_lst = list("I-MMHP"),
-                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
-                  matrix.mar=c(2.5,2.5,2.5,1)
+  indep_pr[
+    rev(expert_rank_10[[current_cohort]]),
+    expert_rank_10[[current_cohort]]
+  ],
+  m1_pr[
+    rev(expert_rank_10[[current_cohort]]),
+    expert_rank_10[[current_cohort]]
+  ],
+  m2_pr[
+    rev(expert_rank_10[[current_cohort]]),
+    expert_rank_10[[current_cohort]]
+  ],
+  m3_pr[
+    rev(expert_rank_10[[current_cohort]]),
+    expert_rank_10[[current_cohort]]
+  ]
+)
+# cat("Cohort ",current_cohort,"\n",sep="")
+myMultiMatrixPlot(
+  X = matrix_lst_plot, no_matrix = 4, n_row = 2,
+  xLabels = expert_rank_10[[current_cohort]],
+  yLabels = rev(expert_rank_10[[current_cohort]]),
+  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
+  colorPalette = "RdBu", if.emp = FALSE,
+  # legend.mar=c(0.5,.5,0.5,0.5),
+  title_lst = list("I-MMHP", "C-HP", "C-DCHP", "C-MMHP"),
+  # title_lst = list("I-MMHP"),
+  col_axis = c(-80, -40, 0, 40, 80), fake_matrix = FALSE,
+  matrix.mar = c(2.5, 2.5, 2.5, 1)
 )
 # mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)
-
 ```
@@
 library(NMF)
-source(here("lib","residualStructureScore.R"))
+source(here("lib", "residualStructureScore.R"))
 
 struct_scores <- tibble()
-for(current_cohort in 1:10) {
-  m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                   "/chp_pr_matrix_",cohort_names[current_cohort],
-                   ".RDS",sep=''))
+for (current_cohort in 1:10) {
+  m1_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+    "/chp_pr_matrix_", cohort_names[current_cohort],
+    ".RDS",
+    sep = ""
+  ))
   ##
@@
   prob_id <- NA
-  prob_id <- c(prob_row,prob_col)
+  prob_id <- c(prob_row, prob_col)
   # print(prob_id)
-  if(length(prob_id) != 0) {
-    m1_pr <- m1_pr[-prob_id,-prob_id]
+  if (length(prob_id) != 0) {
+    m1_pr <- m1_pr[-prob_id, -prob_id]
   }
@@
   ##
-  m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                       "/dchp_pr_matrix_",cohort_names[current_cohort],
-                       ".RDS",sep=''))
-  if(length(prob_id) != 0) {
-    m2_pr <- m2_pr[-prob_id,-prob_id]
-  }
-
-  m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
-                       ".RDS",sep=''))
-  if(length(prob_id) != 0) {
-    m3_pr <- m3_pr[-prob_id,-prob_id]
-  }
-  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
-                       "/immhp_pr_matrix_",cohort_names[current_cohort],
-                       ".RDS",sep=''))
+  m2_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+    "/dchp_pr_matrix_", cohort_names[current_cohort],
+    ".RDS",
+    sep = ""
+  ))
+  if (length(prob_id) != 0) {
+    m2_pr <- m2_pr[-prob_id, -prob_id]
+  }
+
+  m3_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+    "/cmmhp_pr_matrix_", cohort_names[current_cohort],
+    ".RDS",
+    sep = ""
+  ))
+  if (length(prob_id) != 0) {
+    m3_pr <- m3_pr[-prob_id, -prob_id]
+  }
+  indep_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+    "/immhp_pr_matrix_", cohort_names[current_cohort],
+    ".RDS",
+    sep = ""
+  ))
   # print(range(as.vector(indep_pr)))
-  if(length(prob_id) != 0) {
-    indep_pr <- indep_pr[-prob_id,-prob_id]
-  }
-  if(current_cohort %in% c(8,10)) {
+  if (length(prob_id) != 0) {
+    indep_pr <- indep_pr[-prob_id, -prob_id]
+  }
+  if (current_cohort %in% c(8, 10)) {
     # one additional row
@@
     new_prob_col <- which(colSums(m1_pr) == 0)
-    prob_id <- c(new_prob_row,new_prob_col) 
-    if(length(prob_id) != 0) {
+    prob_id <- c(new_prob_row, new_prob_col)
+    if (length(prob_id) != 0) {
       m1_pr <- m1_pr[-prob_id, -prob_id]
@@
 
-  m1_score <-positiveNegativeApproxError(m1_pr)
+  m1_score <- positiveNegativeApproxError(m1_pr)
   m2_score <- positiveNegativeApproxError(m2_pr)
@@
   current_score <- tibble(m1_score, m2_score, m3_score, ind_score)
-  names(current_score) <- c("C-HP","C-DCHP","C-MMHP","I-MMHP")
-  current_score$type <- c("Positive Residuals","Negative Residuals")
+  names(current_score) <- c("C-HP", "C-DCHP", "C-MMHP", "I-MMHP")
+  current_score$type <- c("Positive Residuals", "Negative Residuals")
   current_score$Cohort <- current_cohort
@@
   #                              ind = indep_pr)
-  struct_scores <-struct_scores %>% bind_rows(current_score)
+  struct_scores <- struct_scores %>% bind_rows(current_score)
 }
@@
   rename(Pos_Neg = type) %>%
-  pivot_longer(cols = "C-HP":"I-MMHP",
-               names_to = "Method", values_to = "Score") 
+  pivot_longer(
+    cols = "C-HP":"I-MMHP",
+    names_to = "Method", values_to = "Score"
+  )
 # filter(Score > 0) %>%
@@
 #                                              "C-MMHP"))) %>%
-struct_plot$Method <- factor(struct_plot$Method, levels = c("I-MMHP","C-HP","C-DCHP",
-                                               "C-MMHP") )
+struct_plot$Method <- factor(struct_plot$Method, levels = c(
+  "I-MMHP", "C-HP", "C-DCHP",
+  "C-MMHP"
+))
 
@@
 struct_plot %>%
-  ggplot(aes(Method,Score, fill = Method)) + geom_boxplot() + 
+  ggplot(aes(Method, Score, fill = Method)) +
+  geom_boxplot() +
   # scale_fill_manual(values = box_cols) +
   ggtitle("(b)") +
-  facet_wrap(~Pos_Neg) + theme_bw() +
-  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+  facet_wrap(~Pos_Neg) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
     text = element_text(size = 20),
-              axis.text.y =element_text(size = 11),
+    axis.text.y = element_text(size = 11),
     axis.text.x = element_blank(),
-              axis.title.x=element_blank() )
-
+    axis.title.x = element_blank()
+  )
 ```
@@
 load("../output/plot_N_predict.RData")
-current_cohort <- 5# cohort 1 looks worse than rest
+current_cohort <- 5 # cohort 1 looks worse than rest
 
@@
 temp_plot_df$method <- factor(temp_plot_df$method,
-                              levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
+  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
+  labels = c("I-MMHP", "DSNL", "C-HP", "C-DCHP", "C-MMHP")
+)
 temp_plot_df$day <- factor(temp_plot_df$day)
-#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
+# png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
 # width=600,height=300)
@@
   filter(method %in% levels(temp_plot_df$method)) %>%
-   arrange(factor(method, levels = c("I-MMHP","DSNL",
-                                     "C-HP", "C-DCHP", "C-MMHP"))) %>%
+  arrange(factor(method, levels = c(
+    "I-MMHP", "DSNL",
+    "C-HP", "C-DCHP", "C-MMHP"
+  ))) %>%
   pull(cols)
@@
   rowwise() %>%
-  #mutate(norm = min(norm,60)) %>%
+  # mutate(norm = min(norm,60)) %>%
   # rename(Method = method) %>%
-  ggplot( aes(x = method, y = mae, fill = method)) +
-  geom_boxplot(alpha=0.7) +
+  ggplot(aes(x = method, y = mae, fill = method)) +
+  geom_boxplot(alpha = 0.7) +
   scale_fill_manual(values = plot_cols_pred) +
@@
   theme_bw() +
-  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+  theme(
+    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
     text = element_text(size = 20),
-        axis.text.x=element_blank(),
+    axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
-        legend.position="right") +
-  facet_grid(cols=vars(day)) +
+    legend.position = "right"
+  ) +
+  facet_grid(cols = vars(day)) +
   xlab("Prediction horizon (day)") +
@@
 
-```{r fig-7a-pred-all-cohorts-box}
+```{r fig-7a-pred-all-cohorts-box-mae}
 ### updated to revision
@@
 all_cohort_box$method <- factor(all_cohort_box$method,
-                              levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL",
-                                         "C-HP","C-DCHP",
-                                         "C-MMHP"))
+  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
+  labels = c(
+    "I-MMHP", "DSNL",
+    "C-HP", "C-DCHP",
+    "C-MMHP"
+  )
+)
 all_cohort_box$day <- factor(all_cohort_box$day)
@@
   filter(method %in% levels(all_cohort_box$method)) %>%
-   arrange(factor(method, levels = c("I-MMHP","DSNL",
-                                     "C-HP", "C-DCHP", "C-MMHP"))) %>%
+  arrange(factor(method, levels = c(
+    "I-MMHP", "DSNL",
+    "C-HP", "C-DCHP", "C-MMHP"
+  ))) %>%
   pull(cols)
@@
 all_cohort_box %>%
-  ggplot(aes(x=method,y=norm, fill = method)) +
+  ggplot(aes(x = method, y = norm, fill = method)) +
   # facet_grid(cols = vars(day)) +
-  geom_boxplot(alpha=0.7) +
+  geom_boxplot(alpha = 0.7) +
   scale_fill_manual(values = plot_cols_pred) +
@@
   theme_bw() +
-  theme(plot.title = element_text(size = 22,
-                                  hjust = 0.5, face="bold"),
+  theme(
+    plot.title = element_text(
+      size = 22,
+      hjust = 0.5, face = "bold"
+    ),
     text = element_text(size = 20),
-        axis.text.x=element_blank(),
+    axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
-        legend.position="right") +
-  facet_grid(cols=vars(day)) +
+    legend.position = "right"
+  ) +
+  facet_grid(cols = vars(day)) +
   # guides(color=guide_legend(title="Method")) +
@@
   NULL
-
 ```
@@
 ```{r fig-9a-spearman-rank-cohort1, eval=FALSE}
-load(here("output","plot_rank_predict.RData"))
+load(here("output", "plot_rank_predict.RData"))
 # current_cohort <- 5
@@
 temp_plot_df$method <- factor(temp_plot_df$method,
-                              levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL","C-HP",
-                                         "C-DCHP","C-MMHP"))
+  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
+  labels = c(
+    "I-MMHP", "DSNL", "C-HP",
+    "C-DCHP", "C-MMHP"
+  )
+)
 temp_plot_df$day <- factor(temp_plot_df$day)
@@
 p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
-  geom_boxplot(alpha=0.7) +
+  geom_boxplot(alpha = 0.7) +
   scale_fill_manual(values = plot_cols_pred) +
-  #scale_fill_manual(values =
+  # scale_fill_manual(values =
   # c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
@@
 all_cohort_rank_df$method <- factor(all_cohort_rank_df$method,
-                              levels = c("mmhp","dsnl","m1","m2","m3"),
-                              labels = c("I-MMHP","DSNL","C-HP",
-                                         "C-DCHP","C-MMHP"))
-
-p7 <- ggplot(all_cohort_rank_df,
-       aes(x=method, y=spearman, fill=method)) + 
+  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
+  labels = c(
+    "I-MMHP", "DSNL", "C-HP",
+    "C-DCHP", "C-MMHP"
+  )
+)
+
+p7 <- ggplot(
+  all_cohort_rank_df,
+  aes(x = method, y = spearman, fill = method)
+) +
   # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
@@
   theme_bw() +
-  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
+  theme(
+    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
     text = element_text(size = 20),
-        axis.text.x=element_blank(),
+    axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
-        legend.position="right") +
+    legend.position = "right"
+  ) +
   facet_grid(cols = vars(day)) +
@@
 p7
-
 ```
@@
 
-load(paste(data_path,cohort_names[current_cohort],
-           "/predict_simulation_",cohort_names[current_cohort],
-           ".RData",sep=''))
+load(paste(data_path, cohort_names[current_cohort],
+  "/predict_simulation_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
 clean_data <- cleanData(full_data[[cohort_names[current_cohort]]],
-                        cut_off = 1)
+  cut_off = 1
+)
 
 df <- full_data[[cohort_names[current_cohort]]]
-df <- df[df$Actor!="Start"&df$Actor!="End",]
+df <- df[df$Actor != "Start" & df$Actor != "End", ]
 df1 <- expandrows(df)
-df1 <- df1[order(df1$Timestamp),] #ensure in date order
+df1 <- df1[order(df1$Timestamp), ] # ensure in date order
 df1$event <- 1:nrow(df1)
-glick.df <- df1[, c("event","Actor","Recipient","score"), with = FALSE]
-#need event, actor, recipient, score
-gl <- my_glicko(glick.df, history=TRUE, cval=2)
+glick.df <- df1[, c("event", "Actor", "Recipient", "score"), with = FALSE]
+# need event, actor, recipient, score
+gl <- my_glicko(glick.df, history = TRUE, cval = 2)
 
 # ------------------- period
-training_end <- nrow(df[df$day<=18,])
-testing_end <- nrow(df)-1#1077 #929 for cohort 5
+training_end <- nrow(df[df$day <= 18, ])
+testing_end <- nrow(df) - 1 # 1077 #929 for cohort 5
 newx <- c(training_end:testing_end)
@@
 col_vec <- colorRampPalette(my_col)(mice_number)
-ltypes_vec <- rep(1,mice_number) #c(1,2,3,1,2,3,1,2,3,1,2,3)
+ltypes_vec <- rep(1, mice_number) # c(1,2,3,1,2,3,1,2,3,1,2,3)
 history_width <- 3
 sim_width <- 0.3
-shade_vec <- makeTransparent(col_vec,0.2)
-less_shade_vec <- makeTransparent(col_vec,0.7)
+shade_vec <- makeTransparent(col_vec, 0.2)
+less_shade_vec <- makeTransparent(col_vec, 0.7)
 
 # ---------------- simulation mean and sd
-sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,1000))
-for(s in 1:1000){
+sim_gl_array <- array(NA, dim = c(12, testing_end - training_end + 1, 1000))
+for (s in 1:1000) {
   print(s)
   temp_gl <- glickoScoreSimulationWithWindowsReturnAll(
-    predict.sim = m3_predict_sim[5:8,s], #7 for c 2 and 10
-    history.df = glick.df[1:training_end,])
-  history_matrix <- temp_gl$history[,,1]
-
-  if(testing_end>ncol(temp_gl$history[,,1])){
-    history_matrix <- cbind(history_matrix,
-                            t(matrix(rep(history_matrix[,ncol(history_matrix)],
-                                         testing_end-ncol(temp_gl$history[,,1])),
-                                     nrow=testing_end-ncol(temp_gl$history[,,1]),
-                                     byrow=TRUE)))
-  }else{
+    predict.sim = m3_predict_sim[5:8, s], # 7 for c 2 and 10
+    history.df = glick.df[1:training_end, ]
+  )
+  history_matrix <- temp_gl$history[, , 1]
+
+  if (testing_end > ncol(temp_gl$history[, , 1])) {
+    history_matrix <- cbind(
+      history_matrix,
+      t(matrix(rep(
+        history_matrix[, ncol(history_matrix)],
+        testing_end - ncol(temp_gl$history[, , 1])
+      ),
+      nrow = testing_end - ncol(temp_gl$history[, , 1]),
+      byrow = TRUE
+      ))
+    )
+  } else {
     # try(
-    history_matrix <- history_matrix[,1:testing_end]#temp_gl$history[,1:testing_end]
+    history_matrix <- history_matrix[, 1:testing_end] # temp_gl$history[,1:testing_end]
     # )
   }
-  sim_gl_array[,,s] <- history_matrix[,training_end:testing_end]
+  sim_gl_array[, , s] <- history_matrix[, training_end:testing_end]
 }
@@
 ```{r fig-10a-glicko-rating}
-par(mar=c(3,5,3,1))
+par(mar = c(3, 5, 3, 1))
 testing_end <- testing_end - 1
-plot(1, type="n", xlab="", ylab="Glicko ranking", xlim=c(0,dim(gl$history)[2]),
-     ylim=c(min(gl$history[,,1]),max(gl$history[,,1])),
-     cex.axis=2, cex.lab=2)
-for(m in c(1:mice_number)){
-  #history
-  lines(gl$history[m,1:training_end,1],
-        cex=0.6, col=col_vec[m],lwd=history_width,lty=ltypes_vec[m])
-  lines(c(rep(NA,training_end), gl$history[m,(training_end+1):testing_end,1]),
-        cex=0.6, col=shade_vec[m],lwd=history_width,lty=ltypes_vec[m])
-
-  #simulation
+plot(1,
+  type = "n", xlab = "", ylab = "Glicko ranking", xlim = c(0, dim(gl$history)[2]),
+  ylim = c(min(gl$history[, , 1]), max(gl$history[, , 1])),
+  cex.axis = 2, cex.lab = 2
+)
+for (m in c(1:mice_number)) {
+  # history
+  lines(gl$history[m, 1:training_end, 1],
+    cex = 0.6, col = col_vec[m], lwd = history_width, lty = ltypes_vec[m]
+  )
+  lines(c(rep(NA, training_end), gl$history[m, (training_end + 1):testing_end, 1]),
+    cex = 0.6, col = shade_vec[m], lwd = history_width, lty = ltypes_vec[m]
+  )
+
+  # simulation
   cur_end <- testing_end
-  mean_vec <- apply(sim_gl_array[m,,],1,function(x) mean(na.omit(x)))
-  sd_vec <- apply(sim_gl_array[m,,],1,function(x) sd(na.omit(x)))
-  polygon(c(newx, rev(newx)), c(mean_vec-sd_vec,rev(mean_vec+sd_vec)),col = shade_vec[m], border = NA)
-  #polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
-  lines(c(rep(NA,training_end),mean_vec),
-        cex=0.6, col=col_vec[m],lwd=1,lty=2)
+  mean_vec <- apply(sim_gl_array[m, , ], 1, function(x) mean(na.omit(x)))
+  sd_vec <- apply(sim_gl_array[m, , ], 1, function(x) sd(na.omit(x)))
+  polygon(c(newx, rev(newx)), c(mean_vec - sd_vec, rev(mean_vec + sd_vec)), col = shade_vec[m], border = NA)
+  # polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
+  lines(c(rep(NA, training_end), mean_vec),
+    cex = 0.6, col = col_vec[m], lwd = 1, lty = 2
+  )
 }
@@
 # annotate the days
-for(d in c(19:21)){
-  abline(v = nrow(df[df$day<=(d-1),]),lty=2,lwd=0.4)
-  text(x=nrow(df[df$day<=(d-1),]),y=2600,d)
-}
-mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
+for (d in c(19:21)) {
+  abline(v = nrow(df[df$day <= (d - 1), ]), lty = 2, lwd = 0.4)
+  text(x = nrow(df[df$day <= (d - 1), ]), y = 2600, d)
+}
+mtext(text = "(a)", side = 3, line = -2.3, outer = TRUE, cex = 2.8, at = 0.5, font = 2)
 ```
@@
 ```{r fig-glicko-pred-slides,eval=slides_plots,include=slides_plots}
-par(mar=c(3,5,3,1))
-plot(1, type="n", xlab="", ylab="Glicko ranking", xlim=c(0,dim(gl$history)[2]),
-     ylim=c(min(gl$history[,,1]),max(gl$history[,,1])),
-     cex.axis=2, cex.lab=2)
-for(m in c(1:mice_number)){
-  #history
-  lines(gl$history[m,1:training_end,1],
-        cex=0.6, col=col_vec[m],lwd=history_width,lty=ltypes_vec[m])
-  lines(c(rep(NA,training_end), gl$history[m,(training_end+1):testing_end,1]),
-        cex=0.6, col=shade_vec[m],lwd=history_width,lty=ltypes_vec[m])
-
-  #simulation
+par(mar = c(3, 5, 3, 1))
+plot(1,
+  type = "n", xlab = "", ylab = "Glicko ranking", xlim = c(0, dim(gl$history)[2]),
+  ylim = c(min(gl$history[, , 1]), max(gl$history[, , 1])),
+  cex.axis = 2, cex.lab = 2
+)
+for (m in c(1:mice_number)) {
+  # history
+  lines(gl$history[m, 1:training_end, 1],
+    cex = 0.6, col = col_vec[m], lwd = history_width, lty = ltypes_vec[m]
+  )
+  lines(c(rep(NA, training_end), gl$history[m, (training_end + 1):testing_end, 1]),
+    cex = 0.6, col = shade_vec[m], lwd = history_width, lty = ltypes_vec[m]
+  )
+
+  # simulation
   cur_end <- testing_end
-  mean_vec <- apply(sim_gl_array[m,,],1,function(x) mean(na.omit(x)))
-  sd_vec <- apply(sim_gl_array[m,,],1,function(x) sd(na.omit(x)))
-  polygon(c(newx, rev(newx)), c(mean_vec-sd_vec,rev(mean_vec+sd_vec)),
-          col = shade_vec[m], border = NA)
-  #polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
-  lines(c(rep(NA,training_end),mean_vec),
-        cex=0.6, col=col_vec[m],lwd=1,lty=2)
+  mean_vec <- apply(sim_gl_array[m, , ], 1, function(x) mean(na.omit(x)))
+  sd_vec <- apply(sim_gl_array[m, , ], 1, function(x) sd(na.omit(x)))
+  polygon(c(newx, rev(newx)), c(mean_vec - sd_vec, rev(mean_vec + sd_vec)),
+    col = shade_vec[m], border = NA
+  )
+  # polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
+  lines(c(rep(NA, training_end), mean_vec),
+    cex = 0.6, col = col_vec[m], lwd = 1, lty = 2
+  )
 }
@@
 # annotate the days
-for(d in c(19:21)){
-  abline(v = nrow(df[df$day<=(d-1),]),lty=2,lwd=0.4)
-  text(x=nrow(df[df$day<=(d-1),]),y=2600,d)
-}
-#mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
+for (d in c(19:21)) {
+  abline(v = nrow(df[df$day <= (d - 1), ]), lty = 2, lwd = 0.4)
+  text(x = nrow(df[df$day <= (d - 1), ]), y = 2600, d)
+}
+# mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
 ```
@@
 # also removing stan fits as they can cause issues in the next chunk
-
 ```
@@
 
-load(paste(data_path,cohort_names[current_cohort],
-             "/cmmhp_est_zt_",cohort_names[current_cohort],
-             ".RData",sep=''))
+load(paste(data_path, cohort_names[current_cohort],
+  "/cmmhp_est_zt_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
 clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
 return_df <- cleanObservationPeriod(current_cohort, clean_data)
-unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
-  dplyr::summarize(count=n(),
-                   observe=list(observe.id),
-                   observe.length=list(observe.time),
-                   no.events=list(no.events))
-unique_observe_win <- unique(return_df[,c("day","observe.id","observe.time")])
+unique_pairs_df <- return_df %>%
+  group_by(initiator, recipient) %>%
+  dplyr::summarize(
+    count = n(),
+    observe = list(observe.id),
+    observe.length = list(observe.time),
+    no.events = list(no.events)
+  )
+unique_observe_win <- unique(return_df[, c("day", "observe.id", "observe.time")])
 
@@
 print(".......state separation plot........")
-total_event_array <- array(0,dim = c(mice_number, mice_number,
-                                   max(return_df$observe.id)))
-active_event_array <- array(0,dim = c(mice_number, mice_number,
-                                    max(return_df$observe.id)))
-
-for(i in 1:mice_number){
-  for(j in c(1:mice_number)[-i]){
-    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
-    if(length(pair)>0){
+total_event_array <- array(0, dim = c(
+  mice_number, mice_number,
+  max(return_df$observe.id)
+))
+active_event_array <- array(0, dim = c(
+  mice_number, mice_number,
+  max(return_df$observe.id)
+))
+
+for (i in 1:mice_number) {
+  for (j in c(1:mice_number)[-i]) {
+    pair <- which(unique_pairs_df$initiator == i & unique_pairs_df$recipient == j)
+    if (length(pair) > 0) {
       current_window_vec <- unique_pairs_df$observe[[pair]]
-      for(cur_win in current_window_vec){
-        row_indicator <- return_df$initiator==i&return_df$recipient==j&return_df$observe.id==cur_win
-        total_event_array[i,j,cur_win] <- length(return_df[row_indicator,"event.times"][[1]])
-        active_event_array[i,j,cur_win] <- sum(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5)
-      }
-    }
-  }
-}
-
-utility_state_day <- array(0,dim=c(21,mice_number,mice_number))
-social_state_day <- array(0,dim=c(21,mice_number,mice_number))
-for(cur_day in c(1:21)){
-  cur_wins <- which(unique_observe_win$day==cur_day)
-  utility_state_day[cur_day,,] <- apply(active_event_array[,,cur_wins],
-                                        c(1, 2), sum)
-  social_state_day[cur_day,,] <- apply(total_event_array[,,cur_wins], 
-                                       c(1, 2), sum) - 
-    utility_state_day[cur_day,,]
+      for (cur_win in current_window_vec) {
+        row_indicator <- return_df$initiator == i & return_df$recipient == j & return_df$observe.id == cur_win
+        total_event_array[i, j, cur_win] <- length(return_df[row_indicator, "event.times"][[1]])
+        active_event_array[i, j, cur_win] <- sum(apply(2 - state_array_list[[pair]][[cur_win]], 1, mean) > 0.5)
+      }
+    }
+  }
+}
+
+utility_state_day <- array(0, dim = c(21, mice_number, mice_number))
+social_state_day <- array(0, dim = c(21, mice_number, mice_number))
+for (cur_day in c(1:21)) {
+  cur_wins <- which(unique_observe_win$day == cur_day)
+  utility_state_day[cur_day, , ] <- apply(
+    active_event_array[, , cur_wins],
+    c(1, 2), sum
+  )
+  social_state_day[cur_day, , ] <- apply(
+    total_event_array[, , cur_wins],
+    c(1, 2), sum
+  ) -
+    utility_state_day[cur_day, , ]
 }
@@
 fit_dsnl_active <- stan("../lib/dsnl_poisson.stan",
-                         data=list(day=21,
-                                   Gt=utility_state_day,
-                                   c=1,
-                                   sigma=0.5),
-                         iter=1000, chains=4, control=list(adapt_delta=0.99))
-print(fit_dsnl_active,pars=c("x"))
+  data = list(
+    day = 21,
+    Gt = utility_state_day,
+    c = 1,
+    sigma = 0.5
+  ),
+  iter = 1000, chains = 4, control = list(adapt_delta = 0.99)
+)
+print(fit_dsnl_active, pars = c("x"))
 sim_dsnl_active <- rstan::extract(fit_dsnl_active)
@@
 fit_dsnl_inactive <- stan("../lib/dsnl_poisson.stan",
-                           data=list(day=21,
-                                     Gt=social_state_day,
-                                     c=1,
-                                     sigma=1),
-                           iter=1000, chains=4, control=list(adapt_delta=0.99))
-print(fit_dsnl_inactive,pars=c("x"))
+  data = list(
+    day = 21,
+    Gt = social_state_day,
+    c = 1,
+    sigma = 1
+  ),
+  iter = 1000, chains = 4, control = list(adapt_delta = 0.99)
+)
+print(fit_dsnl_inactive, pars = c("x"))
 sim_dsnl_inactive <- rstan::extract(fit_dsnl_inactive)
@@
   sim_dsnl_inactive, fit_dsnl_inactive, social_state_day,
-     file = paste(data_path,cohort_names[current_cohort],
+  file = paste(data_path, cohort_names[current_cohort],
     "/dsnl_state_separation_stan_result_",
     cohort_names[current_cohort],
-                  ".RData",sep=''))
+    ".RData",
+    sep = ""
+  )
+)
 rm(interpolation_array_list)
@@
 current_cohort <- 1
-load(paste(data_path,cohort_names[current_cohort],
-           "/dsnl_poisson_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
-load(paste(data_path,cohort_names[current_cohort],
-           "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
-           ".RData",sep=''))
-sub.types <- c("All", "Active", "Inactive"); # three methods
-task.types <- paste0("day", 1:21);
-
-data.tbl <- data.frame(array(NA, c(2000*3*21, 3)))
+load(paste(data_path, cohort_names[current_cohort],
+  "/dsnl_poisson_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+load(paste(data_path, cohort_names[current_cohort],
+  "/dsnl_state_separation_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+sub.types <- c("All", "Active", "Inactive")
+# three methods
+task.types <- paste0("day", 1:21)
+data.tbl <- data.frame(array(NA, c(2000 * 3 * 21, 3)))
 colnames(data.tbl) <- c("sub.type", "task.type", "data.value")
-source('../lib/myGlicko.R')
+source("../lib/myGlicko.R")
 #------------ gl score
 df <- full_data[[cohort_names[current_cohort]]]
-df <- df[df$Actor!="Start"&df$Actor!="End",]
+df <- df[df$Actor != "Start" & df$Actor != "End", ]
 df1 <- expandrows(df)
-df1 <- df1[order(df1$Timestamp),] #ensure in date order
+df1 <- df1[order(df1$Timestamp), ] # ensure in date order
 df1$event <- 1:nrow(df1)
-glick.df <- df1[, c("event","Actor","Recipient","score"), with = FALSE] #need event, actor, recipient, score
-real.gl <- my_glicko(glick.df, history=TRUE, cval=2)
+glick.df <- df1[, c("event", "Actor", "Recipient", "score"), with = FALSE] # need event, actor, recipient, score
+real.gl <- my_glicko(glick.df, history = TRUE, cval = 2)
 clean_data_all <- cleanData(full_data[[cohort_names[current_cohort]]],
-                              cut_off = 1)
-day_end_idx <- unlist(lapply(c(1:21),function(x) 
-  max(which(clean_data_all$day==x))))
+  cut_off = 1
+)
+day_end_idx <- unlist(lapply(c(1:21), function(x) {
+  max(which(clean_data_all$day == x))
+}))
 
 ## All aggregate
-for (t in 1:length(task.types)){
-  temp_vec <- rep(NA,2000)
-  cur_real_rank <- real.gl$history[,day_end_idx[t],1]
-  for(s in c(1:2000)){
-    temp_result <- cor.test(sim_dsnl$x[s,t,], cur_real_rank,
-                            method = "spearman")
+for (t in 1:length(task.types)) {
+  temp_vec <- rep(NA, 2000)
+  cur_real_rank <- real.gl$history[, day_end_idx[t], 1]
+  for (s in c(1:2000)) {
+    temp_result <- cor.test(sim_dsnl$x[s, t, ], cur_real_rank,
+      method = "spearman"
+    )
     temp_vec[s] <- temp_result$estimate
   }
-  data.tbl$sub.type[(1:2000)+(t-1)*2000] <- sub.types[1]  
-  data.tbl$task.type[(1:2000)+(t-1)*2000] <- task.types[t];  
-  data.tbl$data.value[(1:2000)+(t-1)*2000] <- temp_vec
+  data.tbl$sub.type[(1:2000) + (t - 1) * 2000] <- sub.types[1]
+  data.tbl$task.type[(1:2000) + (t - 1) * 2000] <- task.types[t]
+  data.tbl$data.value[(1:2000) + (t - 1) * 2000] <- temp_vec
 }
@@
 ## Utility aggregate
-for (t in 1:length(task.types)){
-  temp_vec <- rep(NA,2000)
-  cur_real_rank <- real.gl$history[,day_end_idx[t],1]
-  for(s in c(1:2000)){
-    temp_result <- cor.test(-sim_dsnl_active$x[s,t,], cur_real_rank, method = "spearman")
+for (t in 1:length(task.types)) {
+  temp_vec <- rep(NA, 2000)
+  cur_real_rank <- real.gl$history[, day_end_idx[t], 1]
+  for (s in c(1:2000)) {
+    temp_result <- cor.test(-sim_dsnl_active$x[s, t, ], cur_real_rank, method = "spearman")
     temp_vec[s] <- temp_result$estimate
   }
-  data.tbl$sub.type[(1:2000)+(t-1)*2000+42000] <- sub.types[2]  
-  data.tbl$task.type[(1:2000)+(t-1)*2000+42000] <- task.types[t];  
-  data.tbl$data.value[(1:2000)+(t-1)*2000+42000] <- temp_vec
+  data.tbl$sub.type[(1:2000) + (t - 1) * 2000 + 42000] <- sub.types[2]
+  data.tbl$task.type[(1:2000) + (t - 1) * 2000 + 42000] <- task.types[t]
+  data.tbl$data.value[(1:2000) + (t - 1) * 2000 + 42000] <- temp_vec
 }
@@
 ## Social aggregate
-for (t in 1:length(task.types)){
-  temp_vec <- rep(NA,2000)
-  cur_real_rank <- real.gl$history[,day_end_idx[t],1]
-  for(s in c(1:2000)){
-    temp_result <- cor.test(sim_dsnl_inactive$x[s,t,], 
-                            cur_real_rank, method = "spearman")
+for (t in 1:length(task.types)) {
+  temp_vec <- rep(NA, 2000)
+  cur_real_rank <- real.gl$history[, day_end_idx[t], 1]
+  for (s in c(1:2000)) {
+    temp_result <- cor.test(sim_dsnl_inactive$x[s, t, ],
+      cur_real_rank,
+      method = "spearman"
+    )
     temp_vec[s] <- temp_result$estimate
   }
-  data.tbl$sub.type[(1:2000)+(t-1)*2000+42000*2] <- sub.types[3]  
-  data.tbl$task.type[(1:2000)+(t-1)*2000+42000*2] <- task.types[t];  
-  data.tbl$data.value[(1:2000)+(t-1)*2000+42000*2] <- temp_vec
-}
-
-data.tbl$sub.type <- factor(data.tbl$sub.type);  
-data.tbl$task.type <- factor(data.tbl$task.type);
+  data.tbl$sub.type[(1:2000) + (t - 1) * 2000 + 42000 * 2] <- sub.types[3]
+  data.tbl$task.type[(1:2000) + (t - 1) * 2000 + 42000 * 2] <- task.types[t]
+  data.tbl$data.value[(1:2000) + (t - 1) * 2000 + 42000 * 2] <- temp_vec
+}
+
+data.tbl$sub.type <- factor(data.tbl$sub.type)
+data.tbl$task.type <- factor(data.tbl$task.type)
 ```
@@
 ```{r fig-10b-rank-correlation}
-par(mar=c(3, 5, 3, 1))
+par(mar = c(3, 5, 3, 1))
 cx <- 1.75 # cex for axis label text;
 # default is 1. bigger numbers make the text bigger, smaller, smaller.
-x.ttl <- ""; # blank x-axis label  
-y.ttl <- "rank corr. (Glicko rank)";  
-ttl <- "(b)";  
-#y.lim <- c(min(data.tbl$data.value), max(data.tbl$data.value)+.5);
+x.ttl <- ""
+# blank x-axis label
+y.ttl <- "rank corr. (Glicko rank)"
+ttl <- "(b)"
+# y.lim <- c(min(data.tbl$data.value), max(data.tbl$data.value)+.5);
 # y-axis limits. +2 at top to give room for legend
-y.lim <- c(-1,1.2)    
+y.lim <- c(-1, 1.2)
 x.lim <- c(0.5, (length(task.types)))
-cols <- c('paleturquoise4', 'lightgreen', 'cornsilk')
+cols <- c("paleturquoise4", "lightgreen", "cornsilk")
 shifts <- c(-0.25, 0, 0.25)
 
-plot(x = 0, y = 0, xlim = x.lim, ylim = y.lim, xaxt='n',
-     col = 'white', xlab = x.ttl,
+plot(
+  x = 0, y = 0, xlim = x.lim, ylim = y.lim, xaxt = "n",
+  col = "white", xlab = x.ttl,
   ylab = y.ttl, main = ttl,
-     cex.main = cx*1.3, cex.axis = cx, cex.lab = cx); 
-axis(side = 1, at = 1:length(task.types), labels = task.types,
-     cex.axis=cx, cex.lab=cx)  # put on the x-axis labels  
-grid(nx=NA, ny=NULL, col='darkgrey');  
-lines(x=c(-1,100), y=c(0,0), col='darkgrey');  
+  cex.main = cx * 1.3, cex.axis = cx, cex.lab = cx
+)
+axis(
+  side = 1, at = 1:length(task.types), labels = task.types,
+  cex.axis = cx, cex.lab = cx
+) # put on the x-axis labels
+grid(nx = NA, ny = NULL, col = "darkgrey")
+lines(x = c(-1, 100), y = c(0, 0), col = "darkgrey")
 for (t.id in 1:length(task.types)) {
@@
       data.tbl$task.type == task.types[t.id])
-   boxplot(data.tbl$data.value[inds], at=t.id+shifts[i],
-           col=cols[i], add=TRUE, 
-           xaxt='n', yaxt='n', bty='n', boxwex=0.35,
-           outpch = 20, outcex = 0.5) 
-  }  
-}  
-legend(x='top', legend = sub.types, fill=cols,
-       horiz = TRUE, cex = cx, bg = 'white', bty = 'n')  
+    boxplot(data.tbl$data.value[inds],
+      at = t.id + shifts[i],
+      col = cols[i], add = TRUE,
+      xaxt = "n", yaxt = "n", bty = "n", boxwex = 0.35,
+      outpch = 20, outcex = 0.5
+    )
+  }
+}
+legend(
+  x = "top", legend = sub.types, fill = cols,
+  horiz = TRUE, cex = cx, bg = "white", bty = "n"
+)
 box()

### 2021-06-28 sim_design/check_sims.R
trying some additional simulation settings

@@ -1,8 +1,8 @@
 library(ggplot2)
 library(bayesplot)
-library(ggplot2)
 library(posterior)
 library(here)
+library(tidyverse)
 
 sim_data_path <- here("output", "revisions", "sim_design", "/")
 
@@ -16,14 +16,14 @@ sim_data_path <- here("output", "revisions", "sim_design", "/")
 #                    f_vec_1 = seq(from = 0.05, to = 0.95,
 #                                  length.out = num_nodes))
 
-sim_id <- 10
-load(paste(sim_data_path,"sim_model3_sim123_",
-                  sim_id,
-                  ".RData",sep=''))
+# sim_id <- 10
+# load(paste(sim_data_path,"sim_model3_sim123_",
+#                   sim_id,
+#                   ".RData",sep=''))
 
-sim_fit1_draws <- sim_model3_stan_sim1
-sim_fit2_draws <- sim_model3_stan_sim2
-sim_fit3_draws <- sim_model3_stan_sim3
+# sim_fit1_draws <- sim_model3_stan_sim1
+# sim_fit2_draws <- sim_model3_stan_sim2
+# sim_fit3_draws <- sim_model3_stan_sim3
 
 
 # sim_model3_stan_sim1 <- sim_fit1_draws
@@ -71,6 +71,22 @@ mcmc_trace(sim_fit1_draws, pars = "beta") +
 
 ####
 
+true_ranks <- tibble(node = 1:num_nodes,
+                     rank = object_par$f_vec_1)
+
+sim_fit1_draws %>% 
+  select(starts_with("f")) %>% 
+  rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
+  rename_with(~gsub("]", "", .x, fixed = TRUE)) %>%
+  pivot_longer(everything(),
+               names_to = "node",
+               values_to = "rank") %>% 
+  mutate(node = factor(node, levels = 1:num_nodes)) %>% 
+  ggplot(aes(node, rank)) + 
+  geom_boxplot() +
+  geom_point(data = true_ranks, aes(node, rank), colour = "red")
+
+
 mcmc_trace(sim_fit2_draws, pars =
              c("f[1]", "f[2]", "f[3]", "f[4]", "f[5]",
                "f[6]", "f[7]", "f[8]", "f[9]", "f[10]"))
@@ -104,6 +120,18 @@ mcmc_trace(sim_fit2_draws, pars = "f[5]") +
[…]

### 2021-06-28 sim_design/simulation_design.R

@@ -27,7 +27,7 @@ source('lib/drawIntensity.R')
 #source('lib/cleanData.R')
 # Define global variable
 n_sim <- 1
-num_nodes <- 5
+num_nodes <- 10
 cut_off <- 3
 obs_time <- 50
 
@@ -47,15 +47,16 @@ object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
   q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
   q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
 
-object_par <- list(sim_lambda_1 = 0.4,
-                   gamma_var = seq(from = 0.01, to = 0.2, length.out = num_nodes),
-                   zeta_var = rep(0.1, num_nodes),
-                   sim_eta_1 = 1.5, # from 3.5
-                   sim_eta_2 = 0,#1.5, # from 2.6
-                   sim_eta_3 = 2, # this seems better
+object_par <- list(sim_lambda_1 = 0.6,
+                   gamma_var = seq(from = 0.01, to = 0.2,
+                                   length.out = num_nodes),
+                   zeta_var = rep(0.05, num_nodes),
+                   sim_eta_1 = 3.5, # from 3.5
+                   sim_eta_2 = 2,#1.5, # from 2.6
+                   sim_eta_3 = 3, # this seems better
                    #sim_eta_3 = 7.5,
                    sim_beta = 1.5, # from 2
-                   f_vec_1 = seq(from = 0.05, to = 0.95,
+                   f_vec_1 = seq(from = 0.25, to = 0.85,
                                  length.out = num_nodes))
 
 object_matrix <- list(
@@ -167,16 +168,16 @@ sim_fit1_draws <- posterior::as_draws_df(sim_fit1)
 # # m1_time <- Sys.time() - start_time
 
 ## save the stan object
-dir.create(sim_data_path, recursive = TRUE, showWarnings = FALSE)
-sim_fit1_summ <- sim_stan_fit1$summary()
-# sim_stan_fit1$save_object(file = paste0(sim_data_path,
-#                                         "stan_fit_1_sim_",
-#                                         sim_id,
-#                                         ".RDS"))
-saveRDS(sim_fit1_summ, file = paste0(sim_data_path,
-                                     "stan_fit_1_summ_",
-                                     sim_id,
-                                     ".RDS"))
[…]

### 2021-07-06 run_scripts/c_dchp.R
update chp for cmdstan also

@@ -106,8 +106,8 @@ stan_train_input_lst <- prepareDataStanTrain(current_cohort)
 stan_train_input_lst$scale <- 0.1
 
 fit_cohort_dchp <- model2$sample(data = stan_train_input_lst,
-                                 iter_warmup = 2000,
-                                 iter_sampling = 3000,
+                                 iter_warmup = 1000,
+                                 iter_sampling = 1000,
                                  thin = 4,
                                  chains = 4,
                                  adapt_delta=0.95,

### 2021-07-06 run_scripts/c_hp.R

@@ -2,7 +2,7 @@
 
 ### code ####
 # #run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 # ### set cohort_id based on job num
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
@@ -10,9 +10,9 @@ cohort_id <- jobid
 #cohort_id <- 1
 #####
 
-save_data_path <- "output/common_rate/"
+save_data_path <- "output/revision/"
 
-library(rstan)
+library(cmdstanr)
 options(mc.cores = parallel::detectCores())
 
 
@@ -78,7 +78,7 @@ print(paste("Cohort",current_cohort))
 
 
 # then fit C-HP here for each cohort
-
+model1 <- cmdstan_model("lib/model1.stan")
 
 #### fit stan model ####
 print(paste("Cohort",current_cohort))
@@ -86,126 +86,185 @@ stan_input_lst <- prepareDataStan(current_cohort)
 stan_input_lst$alpha_id <- expert_rank_10[[current_cohort]][1]
 stan_input_lst$delta_1 <- rep(0.5,stan_input_lst$N_til)
 
-fit_cohort_hp <- stan("lib/model1.stan", 
-                      data = stan_input_lst,
-                      warmup = 1000, iter = 2000, chains = 4, thin=4,
-                      control=list(adapt_delta=0.98))
-sim_cohort_hp <- rstan::extract(fit_cohort_hp)
-dir.create(paste(save_data_path, cohort_names[current_cohort],sep=''), recursive = TRUE, showWarnings = FALSE)
+
+
+
+fit_cohort_hp <- model1$sample(data = stan_input_lst,
+                               iter_warmup = 1000,
+                               iter_sampling = 2000,
+                               chains = 4,
+                               thin = 4,
+                               adapt_delta=0.98,
+                               refresh = 200)
+
+chp_fit <- fit_cohort_hp$draws()
+sim_cohort_hp <- posterior::as_draws_df(chp_fit)
+
+dir.create(paste(save_data_path,
+                 cohort_names[current_cohort],sep=''),
+           recursive = TRUE,
+           showWarnings = FALSE)
 save(sim_cohort_hp, fit_cohort_hp,
-     file = paste(save_data_path,cohort_names[current_cohort],
[…]

### 2021-07-06 output_scripts/Paper_Plots.Rmd
just general tidying

@@
   dev = "png", fig.height = 4.5, fig.width = 7,
-  warning = FALSE
+  warning = FALSE, cache = TRUE
 )
@@
 # current_cohort <- 5
+current_cohort <- 5
 
@@
 ks.stat.matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
+ks_pval_chp <- matrix(0, nrow = mice_number, ncol = mice_number)
 n_matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
@@
         )$statistic
+        ks_pval_chp[i, j] <- ks.test(all_Lambda, "pexp",
+          rate = 1 / mean(all_Lambda)
+        )$p.value
         Lambda_matrix[i, j][[1]] <- all_Lambda
@@
 # dev.off()
+ks_chp <- ks.stat.matrix
+
 ```
@@
 ```{r fig-3a-baseline-rate, eval=revision_plots}
-# current_cohort <- 5
+current_cohort <- 5
+# current_cohort <- 6 # 3 is maybe ok, 6/7 is interesting
 
@@
 
+## New Fig
+
+KS Plot for C-DCHP
+
+```{r ks-c-dchp, eval=FALSE, warning=FALSE}
+ks.stat.matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
+ks_pval_dchp <- matrix(0, ncol = mice_number, nrow = mice_number)
+n_matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
+Lambda_matrix <- matrix(list(), nrow = mice_number, ncol = mice_number)
+
+gamma_mean <- apply(sim_cohort_dchp$gamma, 2, mean)
+zeta_mean <- apply(sim_cohort_dchp$zeta, 2, mean)
+eta1_mean <- mean(sim_cohort_dchp$eta_1)
+eta2_mean <- mean(sim_cohort_dchp$eta_2)
+eta3_mean <- mean(sim_cohort_dchp$eta_3)
+
+for (k in 1:mice_number) {
+  for (l in c(1:mice_number)[-k]) {
+    i <- expert_rank_10[[current_cohort]][k]
+    j <- expert_rank_10[[current_cohort]][l]
+    pair <- which(unique_pairs_df$initiator == i & 
+                    unique_pairs_df$recipient == j)
+    if (length(pair) > 0) {
+      param_mean <- list(
+        lambda0 = gamma_mean[i] + zeta_mean[j],
+        ## need to modify this
+        # lambda0 <- mean(sim_cohort_dchp$gamma)
+        alpha = model1_fn$alpha.fun(
+          f_est[i],
+          f_est[j],
+          eta1_mean,
+          eta2_mean,
+          eta3_mean
+        ),
+        beta = mean(sim_cohort_dchp$beta)
+      )
+      current_window_vec <- unique_pairs_df$observe[[pair]]
+      all_Lambda <- numeric(0)
+      for (cur in c(1:length(current_window_vec))) { ## check length > 2
+        cur_win <- current_window_vec[cur]
+        current_event_time <- return_df[return_df$initiator == i &
+          return_df$recipient == j &
+          return_df$observe.id == cur_win, "event.times"][[1]]
+        current_obs_time <- return_df[return_df$initiator == i &
+          return_df$recipient == j &
+          return_df$observe.id == cur_win, "observe.time"]
+        Lambda_vec <- uniHawkesCompensator(
+          object = param_mean,
+          events = c(
+            current_event_time,
+            current_obs_time
+          )
+        )
+        all_Lambda <- c(all_Lambda, Lambda_vec)
+        n_matrix[i, j] <- n_matrix[i, j] + length(current_event_time)
+      }
+      if (length(all_Lambda) > 0) {
+        ks.stat.matrix[i, j] <- ks.test(all_Lambda, "pexp",
+          rate = 1 / mean(all_Lambda)
+        )$statistic
+        ks_pval_dchp[i, j] <- ks.test(all_Lambda, "pexp",
+          rate = 1 / mean(all_Lambda)
+        )$p.value
+        Lambda_matrix[i, j][[1]] <- all_Lambda
+      }
+    }
+  }
+}
+col.vec <- cRamp(as.vector(ks.stat.matrix))
+# need to do some sort of transformation between these here
+vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
+# order(as.vector(ks.stat.matrix),method = "")
+
+values <- as.vector(ks.stat.matrix)
+sorted_vals <- sort(ks.stat.matrix)
+# match(values,sorted_vals)
+col.vec.vir <- vir_cols[match(values, sorted_vals)]
+
+####
+par(
+  oma = c(6, 4, 4, 1), mar = rep(0, 4),
+  mgp = c(0, .2, 0)
+)
+layout(cbind(matrix(
+  data = c(1:(12 * 12)), nrow = 12, ncol = 12,
+  byrow = TRUE
+), rep(12 * 12 + 1, 12)),
+widths = c(rep(1, 12), 2), heights = rep(1, 12)
+)
+for (i in expert_rank_10[[current_cohort]]) {
+  for (j in expert_rank_10[[current_cohort]]) {
+    if (ks.stat.matrix[i, j] == 0) {
+      plot(0, 0,
+        xlim = c(0, 5), ylim = c(0, 5), type = "n", xlab = "", ylab = "",
+        axes = FALSE, frame = TRUE
+      )
+      rect(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[4],
+        border = 0, col = "white"
+      )
+    } else {
+      Lambda.test <- Lambda_matrix[i, j][[1]]
+      curve(pexp(x, 1 / mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
+        ylab = "", xlab = "", axes = FALSE, frame = TRUE
+      )
+      rect(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[4],
+        border = 0, col = col.vec.vir[matrixToVecIdx(i, j, mice_number)]
+      )
+      curve(pexp(x, 1 / mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
+        ylab = "", xlab = "", axes = FALSE, frame = TRUE, add = TRUE, lwd = 2
+      )
+      plot(ecdf(Lambda.test),
+        add = TRUE, do.points = FALSE,
+        verticals = TRUE, col = "red", lwd = 2
+      )
+    }
+  }
+}
+par(mar = c(0, 2, 0, 3), mgp = c(0, 0.8, 0))
+m1_ks <- ks.stat.matrix
+col_obj <- list(
+  x.vec = seq(0, max(as.vector(ks.stat.matrix)), length.out = 100),
+  col.vec = viridis(100)
+)
+
+temp <- cLegend(as.vector(ks.stat.matrix))
+image(1, col_obj$x.vec,
+  matrix(
+    data = col_obj$x.vec,
+    ncol = length(col_obj$x.vec), nrow = 1
+  ),
+  col = col_obj$col.vec,
+  xlab = "", ylab = "", axes = FALSE
+)
+axis(4,
+  at = c(0, 0.3, 0.6), labels = c(0, 0.3, 0.6), las = HORIZONTAL <- 1,
+  cex.axis = 2.4
+)
+
+mtext(
+  text = expert_rank_10[[current_cohort]],
+  side = 1, line = 1.8, outer = TRUE, cex = 1.8,
+  at = 1 / 14 * c(1:12) - 1 / 22
+)
+mtext(
+  text = expert_rank_10[[current_cohort]],
+  side = 2, line = 0.5, outer = TRUE, cex = 1.8,
+  at = 1 / 12 * c(12:1) - 1 / 20, las = 2
+)
+mtext(
+  text = "C-DCHP", side = 3, line = 1.4, outer = TRUE,
+  cex = 2.2,
+  at = 0.45, font = 2
+)
+# dev.off()
+
+ks_dchp <- ks.stat.matrix
+
+```
+
+Plot the negative log of the p values here.
+
+```{r potential-fig3-diag, eval=FALSE}
+M1_ks_p <- tibble(ks_p = as.vector(ks_chp), method = "C-HP")
+
+M2_ks_p <- tibble(ks_p = as.vector(ks_dchp), 
+                  method = "C-DCHP")
+
+ks_p <- bind_rows(M1_ks_p, M2_ks_p) %>% 
+  left_join(col_df, by = "method")
+
+cols_plot <- col_df %>%
+  filter(method %in% c("C-HP", "C-DCHP")) %>% 
+  pull(cols)
+
+exp_fcn <- function(x) exp(-x)
+
+ks_p$method <- factor(ks_p$method, levels = c("C-HP", "C-DCHP"))
+
+ks_p %>% 
+  filter(ks_p != 0) %>% 
+  mutate(log_p = -log(ks_p)) %>% 
+  ggplot(aes(x = log_p)) + 
+  # geom_freqpoly(binwidth = 20) +
+  geom_histogram(aes(y = ..density.., fill = method), bins = 50) +
+  scale_fill_manual(values = cols_plot) +
+  labs(y = "Negative Log KS Statistic P Value") +
+  stat_function(fun = exp_fcn, colour = "red") +
+  facet_wrap(~method) +
+  labs(fill = "Method") +
+  theme_minimal()
+
+```
+
+Could repeat this across all cohorts?
+
+```{r above across all_cohorts, eval=FALSE}
+
+ks_chp_array <- array(0, dim = c(10, mice_number, mice_number))
+ks_dchp_array <- array(0, dim = c(10, mice_number, mice_number))
+
+for(current_cohort in 1:10) {
+  load(paste(data_path, cohort_names[current_cohort],
+    "/cohort_hp_stan_result_", cohort_names[current_cohort],
+    ".RData",
+    sep = ""
+  ))
+  load(paste(data_path, cohort_names[current_cohort],
+    "/cohort_dchp_stan_result_", cohort_names[current_cohort],
+    ".RData",
+    sep = ""
+  ))
+  eta1_mean <- mean(sim_cohort_hp$eta_1)
+  eta2_mean <- mean(sim_cohort_hp$eta_2)
+  eta3_mean <- mean(sim_cohort_hp$eta_3)
+  f_est <- apply(sim_cohort_hp$f, 2, mean)
+  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+  return_df <- cleanObservationPeriod(current_cohort,
+    raw_df =
+      full_data[[cohort_names[current_cohort]]],
+    clean_data
+  )
+  unique_pairs_df <- return_df %>%
+    group_by(initiator, recipient) %>%
+    dplyr::summarize(
+      count = n(),
+      observe = list(observe.id),
+      observe.length = list(observe.time),
+      no.events = list(no.events)
+    )
+  unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])
+
+  ks.stat.matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
+  ks_pval_chp <- matrix(0, nrow = mice_number, ncol = mice_number)
+  n_matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
+  Lambda_matrix <- matrix(list(), nrow = mice_number, ncol = mice_number)
+  for (k in 1:mice_number) {
+    for (l in c(1:mice_number)[-k]) {
+      i <- expert_rank_10[[current_cohort]][k]
+      j <- expert_rank_10[[current_cohort]][l]
+      pair <- which(unique_pairs_df$initiator == i & 
+                      unique_pairs_df$recipient == j)
+      if (length(pair) > 0) {
+        param_mean <- list(
+          lambda0 = mean(sim_cohort_hp$lambda0),
+          alpha = model1_fn$alpha.fun(
+            f_est[i],
+            f_est[j],
+            eta1_mean,
+            eta2_mean,
+            eta3_mean
+          ),
+          beta = mean(sim_cohort_hp$beta)
+        )
+        current_window_vec <- unique_pairs_df$observe[[pair]]
+        all_Lambda <- numeric(0)
+        for (cur in c(1:length(current_window_vec))) { ## check length > 2
+          cur_win <- current_window_vec[cur]
+          current_event_time <- return_df[return_df$initiator == i &
+            return_df$recipient == j &
+            return_df$observe.id == cur_win, "event.times"][[1]]
+          current_obs_time <- return_df[return_df$initiator == i &
+            return_df$recipient == j &
+            return_df$observe.id == cur_win, "observe.time"]
+          Lambda_vec <- uniHawkesCompensator(
+            object = param_mean,
+            events = c(
+              current_event_time,
+              current_obs_time
+            )
+          )
+          all_Lambda <- c(all_Lambda, Lambda_vec)
+          n_matrix[i, j] <- n_matrix[i, j] + length(current_event_time)
+        }
+        if (length(all_Lambda) > 0) {
+          ks.stat.matrix[i, j] <- ks.test(all_Lambda, "pexp",
+            rate = 1 / mean(all_Lambda)
+          )$statistic
+          ks_chp_array[current_cohort, i, j] <- ks.test(all_Lambda,
+                                                        "pexp",
+            rate = 1 / mean(all_Lambda)
+          )$p.value
+          Lambda_matrix[i, j][[1]] <- all_Lambda
+        }
+      }
+    }
+  }
+
+  ### c-dchp
+  gamma_mean <- apply(sim_cohort_dchp$gamma, 2, mean)
+  zeta_mean <- apply(sim_cohort_dchp$zeta, 2, mean)
+  eta1_mean <- mean(sim_cohort_dchp$eta_1)
+  eta2_mean <- mean(sim_cohort_dchp$eta_2)
+  eta3_mean <- mean(sim_cohort_dchp$eta_3)
+
+  for (k in 1:mice_number) {
+    for (l in c(1:mice_number)[-k]) {
+      i <- expert_rank_10[[current_cohort]][k]
+      j <- expert_rank_10[[current_cohort]][l]
+      pair <- which(unique_pairs_df$initiator == i & 
+                      unique_pairs_df$recipient == j)
+      if (length(pair) > 0) {
+        param_mean <- list(
+          lambda0 = gamma_mean[i] + zeta_mean[j],
+          ## need to modify this
+          # lambda0 <- mean(sim_cohort_dchp$gamma)
+          alpha = model1_fn$alpha.fun(
+            f_est[i],
+            f_est[j],
+            eta1_mean,
+            eta2_mean,
+            eta3_mean
+          ),
+          beta = mean(sim_cohort_dchp$beta)
+        )
+        current_window_vec <- unique_pairs_df$observe[[pair]]
+        all_Lambda <- numeric(0)
+        for (cur in c(1:length(current_window_vec))) { ## check length > 2
+          cur_win <- current_window_vec[cur]
+          current_event_time <- return_df[return_df$initiator == i &
+            return_df$recipient == j &
+            return_df$observe.id == cur_win, "event.times"][[1]]
+          current_obs_time <- return_df[return_df$initiator == i &
+            return_df$recipient == j &
+            return_df$observe.id == cur_win, "observe.time"]
+          Lambda_vec <- uniHawkesCompensator(
+            object = param_mean,
+            events = c(
+              current_event_time,
+              current_obs_time
+            )
+          )
+          all_Lambda <- c(all_Lambda, Lambda_vec)
+          n_matrix[i, j] <- n_matrix[i, j] + length(current_event_time)
+        }
+        if (length(all_Lambda) > 0) {
+          ks.stat.matrix[i, j] <- ks.test(all_Lambda, "pexp",
+            rate = 1 / mean(all_Lambda)
+          )$statistic
+          ks_dchp_array[current_cohort, i, j] <- ks.test(all_Lambda, "pexp",
+            rate = 1 / mean(all_Lambda)
+          )$p.value
+          Lambda_matrix[i, j][[1]] <- all_Lambda
+        }
+      }
+    }
+  }
+}
+
+```
+
+```{r plot-all-cohorts, eval=FALSE}
+M1_ks_p <- tibble(ks_p = as.vector(ks_chp_array), method = "C-HP")
+
+M2_ks_p <- tibble(ks_p = as.vector(ks_dchp_array), 
+                  method = "C-DCHP")
+
+ks_p <- bind_rows(M1_ks_p, M2_ks_p) %>% 
+  left_join(col_df, by = "method")
+
+cols_plot <- col_df %>%
+  filter(method %in% c("C-HP", "C-DCHP")) %>% 
+  pull(cols)
+
+exp_fcn <- function(x) exp(-x)
+
+ks_p$method <- factor(ks_p$method, levels = c("C-HP", "C-DCHP"))
+
+ks_p %>% 
+  filter(ks_p != 0) %>% 
+  mutate(log_p = -log(ks_p)) %>% 
+  ggplot(aes(x = log_p)) + 
+  # geom_freqpoly(binwidth = 20) +
+  geom_histogram(aes(y = ..density.., fill = method), bins = 50) +
+  scale_fill_manual(values = cols_plot) +
+  labs(y = "Negative Log KS Statistic P Value") +
+  stat_function(fun = exp_fcn, colour = "red") +
+  facet_wrap(~method) +
+  labs(fill = "Method") +
+  theme_minimal()
+
+```
+
 ## Figure 3b: Ranking Comparison
@@
 ```{r fig-3b-rank-comparison, include=FALSE,eval=original_plots}
-# current_cohort <- 5
+current_cohort <- 5
 colors_plot <- col_df %>%
@@
 ## need Hmisc for this
+library(Hmisc)
 
@@
 
-Will need to update this with full final simulations.
+Will need to update this with full final simulations but fully set up now.
 
 ```{r new-fig-4a, eval = revision_plots}
-sim_data_path <- here("output", "revisions", "sim_m3", "june_18", "/")
+sim_data_path <- here("output", "revisions", "sim_m3", "sim_3", "/")
 
@@
 
-f_vec <- seq(from = 0.10,
+f_vec <- seq(from = 0.2,
                to = 0.9,
@@
 
-sims_id <- 1:50
-sims_id <- sims_id[c(-22,-23, -24, -33, -34, -36, -39, -40, -41, -45)]
-
-for(curr_sim in sims_id) {
+model_colors <- col_df %>%
+  filter(method %in% c(
+    "C-HP",
+    "C-DCHP", "C-MMHP"
+  )) %>%
+  pull(cols)
+
+sims <- 1:20
+sims <- sims[c(-9, -13)]
+
+for(curr_sim in sims) {
   load(paste0(sim_data_path,
@@
   f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
-  m3_ranks <- apply(f_m1, 2, mean)
+  m3_ranks <- apply(f_m3, 2, mean)
 
@@
 
-sim_ranks_mean %>% 
+sim_ranks_mean$model <- factor(sim_ranks_mean$model, 
+                               levels = c( "C-HP", "C-DCHP", "C-MMHP"))
+
+mean_sims <- sim_ranks_mean %>% 
+  left_join(col_df, by = c("model" = "method"))
+
+mean_sims$model <- factor(mean_sims$model, levels = c("C-HP", "C-DCHP",
+                                                      "C-MMHP"))
+
+true_ranks <- tibble(node = rep(1:num_nodes,3),
+                     true_rank = rep(f_vec,3),
+                     model = c(rep("C-HP", 10),rep("C-DCHP", 10),
+                               rep("C-MMHP", 10)))
+true_ranks$node <- factor(true_ranks$node, levels = 1:num_nodes)
+
+true_ranks$model <- factor(true_ranks$model, 
+                           levels = c("C-HP", "C-DCHP","C-MMHP"))
+
+mean_sims %>% 
   # filter(model == "C-MMHP") %>% 
-  ggplot(aes(node, ranks)) + 
-  geom_boxplot() +
+  ggplot(aes(node, ranks, fill = model)) + 
+  geom_boxplot(show.legend = FALSE) +
+  scale_fill_manual(values = model_colors, guide = FALSE) +
+  # geom_point(aes(node, true_rank, colour = "red")) +
+  ylim(c(0,1)) +
+  labs(title = "(a)",
+       subtitle = "Mean rank from each simulation", 
+       y = "Posterior Mean Rank", x = "Node") +
   facet_wrap(~model) +
-  geom_point(aes(node, true_rank, colour = "red"),
-             show.legend = FALSE) +
-  labs(title = "Mean rank from each simulation")
+  geom_point(data = true_ranks,
+             aes(node, true_rank, colour = "True Value")) +
+  scale_shape_discrete(name = "True Value") +
+  theme_minimal() +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom",
+        plot.title = element_text(hjust = 0.5, size = 26),
+        text = element_text(size = 18),
+        legend.text = element_text(size = 18))
 
@@
 
-true_ranks <- tibble(node = 1:num_nodes, true_rank = f_vec)
-true_ranks$node <- factor(true_ranks$node, levels = 1:num_nodes)
-
-sim_ranks %>% 
-  ggplot(aes(node, rank)) +
-  geom_boxplot() +
-  facet_wrap(~model) +
-  geom_point(data = true_ranks, aes(node, true_rank, colour = "red"),
-             show.legend = FALSE) +
-  labs(title = "All Posterior Draws")
+# sim_ranks %>%
+#   ggplot(aes(node, rank)) +
+#   geom_boxplot() +
+#   facet_wrap(~model) +
+#   geom_point(data = true_ranks, aes(node, true_rank, colour = "red"),
+#              show.legend = FALSE) +
+#   labs(title = "All Posterior Draws")
 ```
@@
 
-Need to redo this after finally correctly formulating the 
+Need to modify this after finally correctly formulating the 
 simulations.
 
-```{r prepare data for 4b,cache=TRUE, eval=revision_plots}
+```{r prepare data for 4b,cache=TRUE, eval=FALSE}
 plot.s <- 7 # 7 is pretty good
@@
 ## then need to load in the state estimate here
-load(paste0(here("output", "revisions", "sim_m3"),
-  "/", "fit123_state_est_",
+# load(paste0(here("output", "revisions", "sim_m3"),
+#   "/", "fit123_state_est_",
+#   plot.s,
+#   ".RData"
+# ))
+
+load(paste0(
+  sim_data_path, "/", "fit123_state_est_",
   plot.s,
@@
 state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
-  termination = 200
+  termination = 50 
+  ### TO DO update for longer sims
 )
@@
 
-```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4}
+```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4, eval=FALSE}
 mmhp_lty <- 1
@@
 
-```{r actual-plot}
+```{r actual-plot, eval=FALSE}
 layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 2.5), 3))
@@
 
-For completeness, we also wish to repeat the above two plots using data generated 
+For completeness, we also wish to repeat the
+above two plots using data generated 
 from M1 and M2.
@@
 
-```{r data for fig 5,cache=TRUE}
-# load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
-# load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
-####
-#### load new format
+```{r data for fig 5,cache=TRUE, eval=revision_plots}
+n_sim <- 25
+
+num_nodes <- 10
+
+object_par <- list(f_vec_1 = seq(from = 0.1, to = 0.9,
+                                 length.out = num_nodes))
+### TO DO
+
+sim_data_path <- here("output", "revisions", "sim_m3", "june_18", "/")
 
@@
 ## Iteration on 50 simulations
-for (s in c(1:n_sim)) {
+sims <- 1:25
+sims <- sims[c(-12, -22, -23, -24)]
+
+for (s in sims) {
+  print(s)
   load(paste0(sim_data_path, "sim_model3_fit123_", s, ".RData"))
@@
   #########
+  ### transform from cmdstan here
+  f_draws <- sim_model3_stan_sim1 %>% 
+  select(starts_with("f"))
+
+  ###
   model1_par_est <- list(
@@
     beta = mean(sim_model3_stan_sim1$beta),
-
-    ### TO DO
-    f = apply(sim_model3_stan_sim1$f, 2, mean)
-  )
-
-  for (i in c(1:5)) {
-    for (j in c(1:5)[-i]) {
+    f = apply(f_draws, 2, mean)
+  )
+
+  for (i in c(1:num_nodes)) {
+    for (j in c(1:num_nodes)[-i]) {
       current_t <- sim_model3_data$mmhp_matrix[i, j][[1]]$tau
@@
   #############
+  ### convert to cmdstan
+  gamma_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("gamma"))
+  zeta_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("zeta"))
+  f_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("f"))
+
   model2_par_est <- list(
-
-    ### TO DO
-    gamma = apply(sim_model3_stan_sim2$gamma, 2, mean),
-    zeta = apply(sim_model3_stan_sim2$zeta, 2, mean),
+    gamma = apply(gamma_draws, 2, mean),
+    zeta = apply(zeta_draws, 2, mean),
     eta_1 = mean(sim_model3_stan_sim2$eta_1),
@@
     beta = mean(sim_model3_stan_sim2$beta),
-    f = apply(sim_model3_stan_sim2$f, 2, mean)
-  )
-
-  for (i in c(1:5)) {
-    for (j in c(1:5)[-i]) {
+    f = apply(f_draws, 2, mean)
+  )
+
+  for (i in c(1:num_nodes)) {
+    for (j in c(1:num_nodes)[-i]) {
       current_t <- sim_model3_data$mmhp_matrix[i, j][[1]]$tau
@@
   ######
-  lambda_0_est <- apply(sim_model3_stan_sim3$lambda0, 2, mean)
-  lambda_1_est <- apply(sim_model3_stan_sim3$lambda1, 2, mean)
+  ### cmdstan part
+  lam0_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("lambda0"))
+  lam1_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("lambda1"))
+  f_draws <- sim_model3_stan_sim3 %>% 
+  select(starts_with("f"))
+
+  if(ncol(lam0_draws) != sum(clean_sim_data$N_count >2)) {
+    stop("Mismatch between params and event pairs")
+  }
+
+  lambda_0_est <- apply(lam0_draws, 2, mean)
+  lambda_1_est <- apply(lam1_draws, 2, mean)
   ## then put these into a matrix
@@
     col_id <- clean_sim_data$J_fit[i]
-    ### TO DO
     lam0_par_est[row_id, col_id] <- lambda_0_est[i]
@@
     beta = mean(sim_model3_stan_sim3$beta),
-    f = apply(sim_model3_stan_sim3$f, 2, mean)
+    f = apply(f_draws, 2, mean)
   )
@@
 
-  for (i in c(1:5)) {
-    for (j in c(1:5)[-i]) {
+  for (i in c(1:num_nodes)) {
+    for (j in c(1:num_nodes)[-i]) {
       test.mmhp <- sim_model3_data$mmhp_matrix[i, j][[1]]
@@
   }
-}
-```
-
-```{r fig5a-residual-ks, fig.height=7}
+  rm(sim_model3_data)
+}
+
+```
+
+```{r fig5a-residual-ks, fig.height=7, eval=original_plots}
 # cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
@@
 
+New potential Figure 5a plots.
+
+```{r log-p-value}
+cols_plot <- col_df %>% 
+  filter(method %in% c("C-HP","C-DCHP","C-MMHP", "True")) %>%
+  arrange(factor(method, levels = c("C-HP", "C-DCHP", "C-MMHP", "True"))) %>%
+  pull(cols)
+
+m1_ks_p <- tibble(Method = "C-HP",
+                  ks = as.vector(KS_p_model1_array[sims, ,]))
+
+m2_ks_p <- tibble(Method = "C-DCHP",
+                  ks = as.vector(KS_p_model2_array[sims, ,]))
+
+m3_ks_p <- tibble(Method = "C-MMHP",
+                  ks = as.vector(KS_p_model3_array[sims, ,]))
+
+true_ks_p <- tibble(Method = "True",
+                    ks = as.vector(KS_p_true_array[sims, ,]))
+
+all_ks_p <- m1_ks_p %>% 
+  bind_rows(m2_ks_p) %>% 
+  bind_rows(m3_ks_p) %>% 
+  bind_rows(true_ks_p)
+
+all_ks_p$Method <- factor(all_ks_p$Method, levels = c("C-HP",
+                                                      "C-DCHP",
+                                                      "C-MMHP",
+                                                      "True") )
+
+exp_fcn <- function(x) exp(-x)
+
+all_ks_p %>% 
+  filter(ks != 0) %>% 
+  mutate(log_p = -log(ks)) %>% 
+  ggplot(aes(x = log_p)) + 
+  # geom_freqpoly(binwidth = 20) +
+  geom_histogram(aes(y = ..density.., fill = Method), bins = 50) +
+  scale_fill_manual(values = cols_plot) +
+  labs(y = "Negative Log KS Statistic P Value") +
+  stat_function(fun = exp_fcn, colour = "red") +
+  facet_wrap(~Method) +
+  theme_minimal()
+
+```
+
+Inferred ranking boxplots against true rankings.
+
+```{r posterior-mean-ranks}
+sim_data_path <- here("output", "revisions", "sim_m3", "june_18", "/")
+
+num_nodes <- 10
+
+# object_par$f_vec_1
+
+sim_ranks_mean <- tibble()
+sim_ranks <- tibble()
+
+for(curr_sim in sims) {
+  load(paste0(sim_data_path,
+              "sim_model3_fit123_",
+              curr_sim,
+              ".RData"))
+
+  f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
+  m1_ranks <- apply(f_m1, 2, mean)
+
+  f_m1_sims <- f_m1 %>% 
+    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
+    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
+    pivot_longer(everything(),
+                 names_to = "node",
+                 values_to = "rank")
+  f_m1_sims$model <- "C-HP"
+
+  f_m2 <- sim_model3_stan_sim2 %>% select(starts_with("f"))
+  m2_ranks <- apply(f_m2, 2, mean)
+
+  f_m2_sims <- f_m2 %>% 
+    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
+    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
+    pivot_longer(everything(),
+                 names_to = "node",
+                 values_to = "rank")
+
+  f_m2_sims$model <- "C-DCHP"
+
+  f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
+  m3_ranks <- apply(f_m3, 2, mean)
+
+  f_m3_sims <- f_m3 %>% 
+    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
+    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
+    pivot_longer(everything(),
+                 names_to = "node",
+                 values_to = "rank")
+
+  f_m3_sims$model <- "C-MMHP"
+
+  curr_mean_ranks <- tibble(model = c(rep("C-HP", num_nodes),
+                                 rep("C-DCHP", num_nodes),
+                                 rep("C-MMHP", num_nodes)),
+                       ranks = c(m1_ranks,
+                                 m2_ranks,
+                                 m3_ranks),
+                       node = rep(1:num_nodes, 3),
+                       true_rank = rep(object_par$f_vec_1, 3),
+                       sim_id = curr_sim)
+  sim_ranks_mean <- sim_ranks_mean %>% 
+    bind_rows(curr_mean_ranks)
+
+  sim_ranks <- sim_ranks %>% 
+    bind_rows(f_m1_sims, f_m2_sims, f_m3_sims)
+
+}
+
+sim_ranks$node <- factor(sim_ranks$node, levels = 1:num_nodes)
+sim_ranks_mean$node <- factor(sim_ranks_mean$node, levels = 1:num_nodes)
+
+# sim_ranks$node
+
+sim_ranks_mean$model <- factor(sim_ranks_mean$model,
+                               levels = c("C-HP", "C-DCHP", "C-MMHP"))
+
+sim_ranks_mean %>% 
+  # filter(model == "C-MMHP") %>% 
+  ggplot(aes(node, ranks, fill = model)) + 
+  geom_boxplot() +
+  scale_fill_manual(values = cols_plot, guide = 'none') +
+  facet_wrap(~model) +
+  geom_point(aes(node, true_rank, colour = "True Value"),
+             show.legend = TRUE) +
+  labs(title = "Mean rank from each simulation") +
+  theme_minimal() +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom")
+
+```
+
 # Figure 5b: Simulation Spearman Rank
+
+Need to update this again for the final simulation parameter setting.
+
 ```{r fig-5b-spearman-sim, fig.height=7}
-sim_files <- list.files(here("output", "sims_m3_update"),
-  pattern = "rank_sim"
-)
+sim_files <- list.files(here("output", "revisions", "rank_sims/"), 
+                        pattern = "rank_sim")
 
@@
   single_fit <- readRDS(here(
-    "output", "sims_m3_update",
+    "output", "revisions", "rank_sims",
     sim_files[i]
@@
   name == "m2" ~ "C-DCHP",
-  name == "m3_dc" ~ "C-MMHP",
+  name == "m3" ~ "C-MMHP",
   name == "agg" ~ "AggRank",
@@
 ## agg
-plot_latent_df$force[(1:(1000 * mice_number))] <- as.vector(sim_agg_rank$x[1001:2000, ])
+plot_latent_df$force[(1:(1000 * mice_number))] <-
+  as.vector(sim_agg_rank$x[1001:2000, ])
 
 ## M1
-plot_latent_df$force[(1:(1000 * mice_number)) + 1000 * mice_number] <- as.vector(sim_cohort_hp$f)
+plot_latent_df$force[(1:(1000 * mice_number)) +
+                       1000 * mice_number] <- as.vector(sim_cohort_hp$f)
 
 ## M2
-plot_latent_df$force[(1:(1000 * mice_number)) + 2000 * mice_number] <- as.vector(sim_cohort_dchp$f)
+plot_latent_df$force[(1:(1000 * mice_number)) + 
+                       2000 * mice_number] <- as.vector(sim_cohort_dchp$f)
 
 ## M3
-plot_latent_df$force[(1:(1000 * mice_number)) + 3000 * mice_number] <- as.vector(sim_cohort_mmhp$f)
+plot_latent_df$force[(1:(1000 * mice_number)) + 
+                       3000 * mice_number] <- as.vector(sim_cohort_mmhp$f)
 
@@
   plot_latent_df,
-  aes(x = Mice, y = force, fill = Method)
-) +
+  aes(x = Mice, y = force, fill = Method)) +
   geom_boxplot(alpha = 0.7) +
   scale_fill_manual(values = plot_cols) +
-  # scale_fill_manual(values = c("gray", "steelblue", "goldenrod2" , "firebrick2")) +
   ggtitle("(a)") +
@@
 ```
+
 ## Figure 6b: Spearman rank correlation
@@
   m2_score <- positiveNegativeApproxError(m2_pr)
-  m3_score <- positiveNegativeApproxError(m3_pr) ## smallest value which is good
+  m3_score <- positiveNegativeApproxError(m3_pr) 
+  ## smallest value which is good
   ind_score <- positiveNegativeApproxError(indep_pr)
@@
 
-```{r fig-8a-frob-norm-cohort5, fig.width=8,fig.height=4,eval=FALSE}
+```{r fig-8a-frob-norm-cohort5, fig.width=8,fig.height=4,eval=TRUE}
 load("../output/plot_N_predict.RData")
@@
   NULL
-p3 + labs(fill = "Method")
+p3 + labs(fill = "Method", title = "Single Cohort")
 ```
@@
   xlab("Prediction horizon (day)") +
-  ylab("Frobenius norm of error") +
+  ylab("MAE") +
   labs(fill = "Method") +
@@
     # try(
-    history_matrix <- history_matrix[, 1:testing_end] # temp_gl$history[,1:testing_end]
+    history_matrix <- history_matrix[, 1:testing_end] 
+    # temp_gl$history[,1:testing_end]
     # )
@@
 plot(1,
-  type = "n", xlab = "", ylab = "Glicko ranking", xlim = c(0, dim(gl$history)[2]),
+  type = "n", xlab = "",
+  ylab = "Glicko ranking", xlim = c(0, dim(gl$history)[2]),
   ylim = c(min(gl$history[, , 1]), max(gl$history[, , 1])),
@@
   )
-  lines(c(rep(NA, training_end), gl$history[m, (training_end + 1):testing_end, 1]),
+  lines(c(rep(NA, training_end),
+          gl$history[m, (training_end + 1):testing_end, 1]),
     cex = 0.6, col = shade_vec[m], lwd = history_width, lty = ltypes_vec[m]
@@
   sd_vec <- apply(sim_gl_array[m, , ], 1, function(x) sd(na.omit(x)))
-  polygon(c(newx, rev(newx)), c(mean_vec - sd_vec, rev(mean_vec + sd_vec)), col = shade_vec[m], border = NA)
+  polygon(c(newx, rev(newx)),
+          c(mean_vec - sd_vec, rev(mean_vec + sd_vec)),
+          col = shade_vec[m], border = NA)
   # polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
@@
 }
-mtext(text = "(a)", side = 3, line = -2.3, outer = TRUE, cex = 2.8, at = 0.5, font = 2)
+mtext(text = "(a)", side = 3, line = -2.3,
+      outer = TRUE, cex = 2.8, at = 0.5, font = 2)
 ```
@@
   )
-  lines(c(rep(NA, training_end), gl$history[m, (training_end + 1):testing_end, 1]),
+  lines(c(rep(NA, training_end), 
+          gl$history[m, (training_end + 1):testing_end, 1]),
     cex = 0.6, col = shade_vec[m], lwd = history_width, lty = ltypes_vec[m]
@@
   )
-unique_observe_win <- unique(return_df[, c("day", "observe.id", "observe.time")])
+unique_observe_win <- unique(return_df[,
+                                       c("day", "observe.id", "observe.time")])
 
@@
   for (j in c(1:mice_number)[-i]) {
-    pair <- which(unique_pairs_df$initiator == i & unique_pairs_df$recipient == j)
+    pair <- which(unique_pairs_df$initiator == i & 
+                    unique_pairs_df$recipient == j)
     if (length(pair) > 0) {
@@
       for (cur_win in current_window_vec) {
-        row_indicator <- return_df$initiator == i & return_df$recipient == j & return_df$observe.id == cur_win
-        total_event_array[i, j, cur_win] <- length(return_df[row_indicator, "event.times"][[1]])
-        active_event_array[i, j, cur_win] <- sum(apply(2 - state_array_list[[pair]][[cur_win]], 1, mean) > 0.5)
+        row_indicator <- return_df$initiator == i & 
+          return_df$recipient == j & return_df$observe.id == cur_win
+        total_event_array[i, j, cur_win] <- length(return_df[
+          row_indicator, "event.times"][[1]])
+        active_event_array[i, j, cur_win] <- 
+          sum(apply(2 - state_array_list[[pair]][[cur_win]], 1, mean) > 0.5)
       }
@@
 df1$event <- 1:nrow(df1)
-glick.df <- df1[, c("event", "Actor", "Recipient", "score"), with = FALSE] # need event, actor, recipient, score
+glick.df <- df1[, c("event", "Actor", "Recipient", "score"),
+                with = FALSE] # need event, actor, recipient, score
 real.gl <- my_glicko(glick.df, history = TRUE, cval = 2)
@@
   for (s in c(1:2000)) {
-    temp_result <- cor.test(-sim_dsnl_active$x[s, t, ], cur_real_rank, method = "spearman")
+    temp_result <- cor.test(-sim_dsnl_active$x[s, t, ], cur_real_rank,
+                            method = "spearman")
     temp_vec[s] <- temp_result$estimate

### 2021-07-06 sim_design/check_sims.R

@@ -36,6 +36,7 @@ sim_data_path <- here("output", "revisions", "sim_design", "/")
 mcmc_trace(sim_fit1_draws, pars =
              c("f[1]", "f[2]", "f[3]", "f[4]", "f[5]", "f[6]", "f[7]",
                "f[8]", "f[9]", "f[10]"))
+
 mcmc_trace(sim_fit1_draws, pars =
              c("eta_1", "eta_2", "eta_3", "beta", "lp__"))
 
@@ -138,6 +139,7 @@ sim_fit2_draws %>%
 mcmc_trace(sim_fit3_draws, pars =
              c("f[1]", "f[2]", "f[3]", "f[4]", "f[5]", "f[6]",
                "f[7]", "f[8]", "f[9]", "f[10]"))
+
 mcmc_trace(sim_fit3_draws, pars =
              c("eta_1", "eta_2", "eta_3", "beta", "lp__"))
 

### 2021-07-06 sim_design/simulation_design.R

@@ -50,13 +50,13 @@ object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
 object_par <- list(sim_lambda_1 = 0.6,
                    gamma_var = seq(from = 0.01, to = 0.2,
                                    length.out = num_nodes),
-                   zeta_var = rep(0.05, num_nodes),
-                   sim_eta_1 = 3.5, # from 3.5
+                   zeta_var = c(rep(0.05, num_nodes/2), rep(0.1, num_nodes/2)),
+                   sim_eta_1 = 1, # from 3.5
                    sim_eta_2 = 2,#1.5, # from 2.6
                    sim_eta_3 = 3, # this seems better
                    #sim_eta_3 = 7.5,
                    sim_beta = 1.5, # from 2
-                   f_vec_1 = seq(from = 0.25, to = 0.85,
+                   f_vec_1 = seq(from = 0.2, to = 0.9,
                                  length.out = num_nodes))
 
 object_matrix <- list(
@@ -64,9 +64,13 @@ object_matrix <- list(
     object_par$gamma_var,
     object_par$zeta_var, "+"
   ),
-  lambda1_matrix = matrix(object_par$sim_lambda_1,
-                          nrow = length(object_par$f_vec_1),
-                          ncol = length(object_par$f_vec_1)
+  # lambda1_matrix = matrix(object_par$sim_lambda_1,
+  #                         nrow = length(object_par$f_vec_1),
+  #                         ncol = length(object_par$f_vec_1)
+  # ),
+  lambda1_matrix = 1.5 * outer(
+    object_par$gamma_var,
+    object_par$zeta_var, "+"
   ),
   alpha_matrix = formMatrix(
     function(x, y) {
@@ -245,11 +249,11 @@ data_list$alpha_id <- top_rank
 
 # start_time <- Sys.time()
 sim_stan_fit3 <- model3$sample(data = data_list,
-                               iter_warmup = 50,
-                               iter_sampling = 100,
+                               iter_warmup = 20,
+                               iter_sampling = 200,
                                # adapt_delta = 0.9,
-                               chains = 4,
-                               refresh = 25)
+                               chains = 1,
+                               refresh = 10)
 
 
 # m3_time <- Sys.time() - start_time

### 2021-07-11 output_scripts/Paper_Plots.Rmd
tidy up stan code, reformat prediction and diagnostics to account for cmdstan output, also correcting multiple places where the incorrect pair wise base rates were being used. this should make a difference to the results which will be interesting to see. corresponding updates to paperplots to use the revised output

@@
 
+data_path <- "../output/revisions/"
+
 load(paste(data_path, cohort_names[current_cohort],
@@
 ))
+
 eta1_mean <- mean(sim_cohort_hp$eta_1)
@@
 eta3_mean <- mean(sim_cohort_hp$eta_3)
-f_est <- apply(sim_cohort_hp$f, 2, mean)
+
+f_draws <- sim_cohort_hp %>% select(starts_with("f"))
+
+f_est <- apply(f_draws, 2, mean)
 clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
@@
 ))
-gamma_mean <- apply(sim_cohort_dchp$gamma, 2, mean)
-zeta_mean <- apply(sim_cohort_dchp$zeta, 2, mean)
+
+gamma_draws <- sim_cohort_dchp %>% select(starts_with("gamma"))
+zeta_draws <- sim_cohort_dchp %>% select(starts_with("zeta"))
+
+gamma_mean <- apply(gamma_draws, 2, mean)
+zeta_mean <- apply(zeta_draws, 2, mean)
 
@@
 
-gamma_mean <- apply(sim_cohort_dchp$gamma, 2, mean)
-zeta_mean <- apply(sim_cohort_dchp$zeta, 2, mean)
+gamma_mean <- apply(gamma_draws, 2, mean)
+zeta_mean <- apply(zeta_draws, 2, mean)
 eta1_mean <- mean(sim_cohort_dchp$eta_1)
@@
 
+What is `data_path` here?
+
 ```{r above across all_cohorts, eval=FALSE}
@@
   eta3_mean <- mean(sim_cohort_hp$eta_3)
-  f_est <- apply(sim_cohort_hp$f, 2, mean)
+  f_draws <- sim_cohort_hp %>% select(starts_with("f"))
+
+  f_est <- apply(f_draws, 2, mean)
   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
@@
   ### c-dchp
-  gamma_mean <- apply(sim_cohort_dchp$gamma, 2, mean)
-  zeta_mean <- apply(sim_cohort_dchp$zeta, 2, mean)
+  gamma_draws <- sim_cohort_dchp %>% select(starts_with("gamma"))
+  zeta_draws <- sim_cohort_dchp %>% select(starts_with("zeta"))
+  gamma_mean <- apply(gamma_draws, 2, mean)
+  zeta_mean <- apply(zeta_draws, 2, mean)
   eta1_mean <- mean(sim_cohort_dchp$eta_1)
@@
   labs(fill = "Method") +
+  theme_minimal()
+
+```
+
+Further diagnostic plots for C-HP vs C-DCHP
+
+```{r plot-pvalues-m1-m2-here}
+ks_p %>% filter(ks_p != 0) %>%
+  select(-cols) %>% 
+  mutate(id = row_number()) %>% 
+  pivot_wider(names_from = method, values_from = ks_p)
+
+bind_cols(M1_ks_p, M2_ks_p) %>% 
+  rename(chp_p = ks_p...1, cdchp_p = ks_p...3) %>% 
+  filter(chp_p != 0) %>% 
+  ggplot(aes(chp_p, cdchp_p)) + geom_point() +
+  labs(x = "C-HP p Value", y = "C-DCHP p Value",
+       title = "p Value for C-HP and C-DCHP") +
   theme_minimal()
@@
 
-```{r new-fig-4a, eval = revision_plots}
-sim_data_path <- here("output", "revisions", "sim_m3", "sim_3", "/")
+```{r new-fig-4a, eval = revision_plots, message=FALSE, warning=FALSE}
+sim_data_path <- here("output", "revisions", "sim_m3", "sim_2", "/")
 
@@
 
-sims <- 1:20
-sims <- sims[c(-9, -13)]
+sims <- 1:50
+sims <- sims[c(-18)]
 
@@
                      true_rank = rep(f_vec,3),
-                     model = c(rep("C-HP", 10),rep("C-DCHP", 10),
+                     model = c(rep("C-HP", 10), rep("C-DCHP", 10),
                                rep("C-MMHP", 10)))
@@
 
-### TO DO
-### need to check this here for pairs with less than cut off events
-
 for (i in seq_along(lam0_vec)) {
@@
 }
-
 ###
-
 #############
@@
 ```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=7}
-current_cohort <- 3
+current_cohort <- 5
+data_path <- "../output/"
 ## 2 and 8 maybe look better
@@
 # mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)
+```
+
+```{r m1-m2-pr, fig.width=6}
+current_cohort <- 5
+m1_m2_plot <- list(m1_pr[
+    rev(expert_rank_10[[current_cohort]]),
+    expert_rank_10[[current_cohort]]
+  ],
+  m2_pr[
+    rev(expert_rank_10[[current_cohort]]),
+    expert_rank_10[[current_cohort]]
+  ])
+
+myMultiMatrixPlot(
+  X = m1_m2_plot, no_matrix = 2, n_row = 1,
+  xLabels = expert_rank_10[[current_cohort]],
+  yLabels = rev(expert_rank_10[[current_cohort]]),
+  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
+  colorPalette = "RdBu", if.emp = FALSE,
+  # legend.mar=c(0.5,.5,0.5,0.5),
+  title_lst = list("C-HP", "C-DCHP"),
+  # title_lst = list("I-MMHP"),
+  col_axis = c(-80, -40, 0, 40, 80), fake_matrix = TRUE,
+  matrix.mar = c(2.5, 2.5, 2.5, 1)
+)
 ```

### 2021-07-11 lib/simulatePrediction.R

@@ -51,8 +51,8 @@ simulateLatentMMHP <- function(lambda0_matrix,
   mmhp_matrix <- matrix(rep(list(), N*N),nrow = N, ncol =N) 
   for(i in c(1:N)){
     for(j in c(1:N)[-i]){
-      #print(paste(i,"->",j))
-      if(alpha_matrix[i,j]>0){
+      # print(paste(i,"->",j))
+      if(alpha_matrix[i,j]>0 & lambda0_matrix[i,j] > 0){
         sim_mmhp_object <- list(lambda0=lambda0_matrix[i,j],
                                 lambda1=lambda1_matrix[i,j],
                                 alpha=alpha_matrix[i,j],
@@ -62,11 +62,14 @@ simulateLatentMMHP <- function(lambda0_matrix,
         if(sim_mmhp_object$alpha>sim_mmhp_object$beta){
           sim.cur.result <- NULL
           while(is.null(sim.cur.result)){
-            sim.cur.result <- tryCatch(expr = {withTimeout(simulate.mmhp(object = sim_mmhp_object, 
-                                                                         termination=horizon,
-                                                                         if.prefer.active=if.prefer.active),
-                                                           timeout = 15)},
-                                       TimeoutException = function(ex) cat("Timeout. Skipping.\n"))
+            sim.cur.result <- tryCatch(
+              expr = {withTimeout(simulate.mmhp(object = sim_mmhp_object, 
+                                                termination = horizon,
+                                                if.prefer.active = 
+                                                  if.prefer.active),
+                                                timeout = 15)},
+                                       TimeoutException = function(ex) cat(
+                                         "Timeout. Skipping.\n"))
           }
           temp_mmhp <- sim.cur.result
         }else{

### 2021-07-11 run_scripts/diagnostics.R

@@ -6,7 +6,7 @@
 
 ### code ###
 ## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 ### set cohort_id based on job num
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
@@ -48,8 +48,6 @@ source('lib/residualStructureScore.R')
 
 
 
-
-
 #### then load in the data ####
 
 full_data <- readRDS("data/mice.RData")
@@ -60,9 +58,11 @@ cut_off <- 3
 mice_number <- 12
 
 
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
+model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){
+  return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
 
-model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
+model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){
+  return(eta1*x*y*exp(-eta2*abs(x-y)))},
                   q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
                   q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
 
@@ -81,13 +81,15 @@ current_cohort <- cohort_id
 print(paste("Cohort",current_cohort))
 
 clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-return_df <- cleanObservationPeriod(current_cohort, clean_data)
+return_df <- cleanObservationPeriod(current_cohort,
+                                    full_data[[cohort_names[current_cohort]]],
+                                    clean_data)
 unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
-  summarize(count=n(),
-            observe=list(observe.id),
-            observe.length=list(observe.time),
-            no.events=list(no.events))
-unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])
+  summarize(count = n(),
[…]

### 2021-07-11 run_scripts/overall_predict.R

@@ -110,24 +110,31 @@ for (current_cohort in 1:10) {
     ".RData",
     sep = ""
   ))
-  f_result_list[[current_cohort]][2, ] <- apply(sim_cohort_hp$f, 2, median)
-  f_sd_list[[current_cohort]][2, ] <- apply(sim_cohort_hp$f, 2, sd)
+  f_draws <- sim_cohort_hp %>% select(starts_with("f"))
+  f_result_list[[current_cohort]][2, ] <- apply(f_draws, 2, median)
+  f_sd_list[[current_cohort]][2, ] <- apply(f_draws, 2, sd)
   ## M2
-  load(paste(data_path, cohort_names[current_cohort],
-    "/cohort_dchp_stan_result_", cohort_names[current_cohort],
-    ".RData",
-    sep = ""
+  load(paste(data_path, 
+             cohort_names[current_cohort],
+             "/cohort_dchp_stan_result_",
+             cohort_names[current_cohort],
+             ".RData",
+             sep = ""
   ))
-  f_result_list[[current_cohort]][3, ] <- apply(sim_cohort_dchp$f, 2, median)
-  f_sd_list[[current_cohort]][3, ] <- apply(sim_cohort_dchp$f, 2, sd)
+  f_draws <- sim_cohort_dchp %>% select(starts_with("f"))
+  f_result_list[[current_cohort]][3, ] <- apply(f_draws, 2, median)
+  f_sd_list[[current_cohort]][3, ] <- apply(f_draws, 2, sd)
   ## M3
-  load(paste(data_path, cohort_names[current_cohort],
-    "/cohort_mmhp_stan_result_", cohort_names[current_cohort],
-    ".RData",
-    sep = ""
+  load(paste(data_path, 
+             cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",
+             cohort_names[current_cohort],
+             ".RData",
+             sep = ""
   ))
-  f_result_list[[current_cohort]][4, ] <- apply(sim_cohort_mmhp$f, 2, median)
-  f_sd_list[[current_cohort]][4, ] <- apply(sim_cohort_mmhp$f, 2, sd)
+  f_draws <- sim_cohort_mmhp %>% select(starts_with("f"))
+  f_result_list[[current_cohort]][4, ] <- apply(f_draws, 2, median)
+  f_sd_list[[current_cohort]][4, ] <- apply(f_draws, 2, sd)
 }
[…]

### 2021-07-11 run_scripts/predict.R

@@ -8,39 +8,39 @@ source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
 cohort_id <- jobid
-#cohort_id <- 1
+# cohort_id <- 1
 ####
 data_path <- "output/revisions/"
 
 
-library(rstan)
+library(cmdstanr)
 options(mc.cores = parallel::detectCores())
 
 
 library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
+# library(RColorBrewer)
+# library(Hmisc)
+# library(wCorr)
+# library(tidyverse)
 library(dplyr)
 library(R.utils)
-#library(fields)
+# library(fields)
 
 
 
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
+source("lib/naiveRankHierarchy.R")
+source("lib/expertRankHierarchy.R")
+source("lib/cleanData.R")
+source("lib/prepareDataStan.R")
+source("lib/inferLatentMmhp.R")
+source("lib/plotUtil.R")
+source("lib/mmhp.R")
+source("lib/uniHawkes.R")
+source("lib/simulatePrediction.R")
+source("lib/myGlicko.R")
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
+source("lib/matrixPlotParameter.R")
+source("lib/residualStructureScore.R")
 
 
 
@@ -51,214 +51,328 @@ source('lib/residualStructureScore.R')
 
 full_data <- readRDS("data/mice.RData")
 # A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
[…]

### 2021-07-13 sim_design/sim_design.Rmd
add sim design rmd file

---
title: "Better Designed Simulations"
author: "Owen G. Ward"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: FALSE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE
)

func_dir <- "../lib/"
Sys.setenv(LOCAL_CPPFLAGS = "-march=corei7 -mtune=corei7")
options(mc.cores = parallel::detectCores())

library(here)
library(cmdstanr)
library(ppdiag)
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(bayesplot)
library(posterior)
library(viridis)
library(here)
library(compete)
source(paste(func_dir, "naiveRankHierarchy.R", sep = ""))
source(paste(func_dir, "expertRankHierarchy.R", sep = ""))
source(paste(func_dir, "cleanData.R", sep = ""))
source(paste(func_dir, "prepareDataStan.R", sep = ""))
source(paste(func_dir, "inferLatentMmhp.R", sep = ""))
source(paste(func_dir, "plotUtil.R", sep = ""))
source(paste(func_dir, "mmhp.R", sep = ""))
source(paste(func_dir, "uniHawkes.R", sep = ""))
source(paste(func_dir, "simulatePrediction.R", sep = ""))
source(paste(func_dir, "myGlicko.R", sep = ""))
source(paste(func_dir, "matrixPlotParameter.R", sep = ""))
source(paste(func_dir, "residualStructureScore.R", sep = ""))
source(paste(func_dir, "drawIntensity.R", sep = ""))
source(paste(func_dir, "circularPlot.R", sep = ""))

theme_set(theme_minimal())

col_df <- tibble(method = c("I&SI",
                            "AggRank",
                            "DSNL",
                            "Glicko",
                            "I-MMHP",
                            "C-HP",
                            "C-DCHP",
                            "True",
                            "C-MMHP"),
            cols = viridis(9))

model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3) {
  return(eta1 * x * y * exp(-eta2 * abs(x - y)) / (1 + exp(-eta3 * (x - y))))
})

model3_fn <- list(
  alpha.fun = function(x, y, eta1, eta2) {
    return(eta1 * x * y * exp(-eta2 * abs(x - y)))
  },
  q1.fun = function(x, y, eta3) {
    return(exp(-eta3 * x))
  },
  q0.fun = function(x, y, eta3) {
    return(exp(-eta3 * y))
  }
)

sim_data_path <- here("output", "revisions", "sim_m3", "sim_3", "/")

```

In this document we want to better develop the properties of
the proposed latent ranking models for animal interactions, leading to
better designed and more robust simulation studies.

# Parameters of the Simulation Model

We specify the following parameters for our simulation model.

```{r specify-pars}
num_nodes <- 10 #20
cut_off <- 3
obs_time <- 100#50 #100

object_par <- list(sim_lambda_1 = 0.6,
                   gamma_var = seq(from = 0.01, to = 0.2,
                                   length.out = num_nodes),
                   zeta_var = rep(0.1, num_nodes),
                   sim_eta_1 = 1, # from 3.5
                   sim_eta_2 = 2,#1.5, # from 2.6
                   sim_eta_3 = 3, # this seems better
                   #sim_eta_3 = 7.5,
                   sim_beta = 1.5, # from 2
                   f_vec_1 = seq(from = 0.2, to = 0.9,
                                 length.out = num_nodes))

object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
  return(eta1*x*y*exp(-eta2*abs(x-y)))},
                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
                  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})

```

# Fitting the Simulated Models

We fit each of the 3 proposed models to this simulated data.

# Evaluating the Fit of the Simulated Models

We can explore the fit of a given model by visualizing the 
posterior trace plots for each parameter first, to confirm our
Bayesian model correctly sampled from the posterior.

```{r load-specific-stan-fit}
current_cohort <- 1

print(current_cohort)
### currently 13,14,17 completed

load(paste0(sim_data_path, "sim_model3_fit123_", current_cohort, ".RData"))
load(paste(sim_data_path, "fit123_state_est_", current_cohort,
           ".RData", sep = ""))
clean_sim_data <- cleanSimulationData(
    raw_data = sim_model3_data,
    cut_off = cut_off,
    N = length(object_par$f_vec_1)
  )

```

## Model 1

```{r examine-m1-stan}
mcmc_trace(sim_model3_stan_sim1, pars = c("eta_1", "eta_2", "eta_3"))

mcmc_trace(sim_model3_stan_sim1, pars = c("f[1]",
                                          "f[5]",
                                          "f[10]"))

mcmc_dens(sim_model3_stan_sim1, pars = c("eta_1", "eta_2", "eta_3"))

mcmc_dens(sim_model3_stan_sim1, pars = c("f[1]",
                                          "f[5]",
                                          "f[10]"))

mcmc_dens(sim_model3_stan_sim1, pars = c("lp__", "lambda0", "beta"))

```

## Model 2

```{r examine-m2-stan}
mcmc_trace(sim_model3_stan_sim2, pars = c("eta_1", "eta_2", "eta_3"))

mcmc_trace(sim_model3_stan_sim2, pars = c("f[1]",
                                          "f[5]",
                                          "f[10]"))

mcmc_dens(sim_model3_stan_sim2, pars = c("eta_1", "eta_2", "eta_3"))

mcmc_dens(sim_model3_stan_sim2, pars = c("f[1]",
                                          "f[5]",
                                          "f[10]"))

mcmc_dens(sim_model3_stan_sim2, pars = c("lp__", "beta"))

```

## Model 3

```{r examine-m3-stan}
mcmc_trace(sim_model3_stan_sim3, pars = c("eta_1", "eta_2", "eta_3"))

mcmc_trace(sim_model3_stan_sim3, pars = c("f[1]",
                                          "f[5]",
                                          "f[10]"))

mcmc_dens(sim_model3_stan_sim3, pars = c("eta_1", "eta_2", "eta_3"))

mcmc_dens(sim_model3_stan_sim3, pars = c("f[1]",
                                          "f[5]",
                                          "f[10]"))

mcmc_dens(sim_model3_stan_sim3, pars = c("lp__", "beta"))

```

These traceplots indicate that M1 has identifiability issues, struggling
with multimodality for multiple parameters, which is not the case in
M2 and M3. Similarly, M3 seems to better recover the model parameters
than M2.

## Model Diagnostics

We can then evaluate the fit of each model further, by 
computing the compensators of the point process.

```{r init-diags}
n_sim <- 1

N_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
Lambda_model3_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
Lambda_model1_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
Lambda_model2_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
Lambda_true_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
PR_model1_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
PR_model2_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
PR_model3_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
PR_true_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_model1_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_model2_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_model3_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_true_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_p_model1_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_p_model2_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_p_model3_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_p_true_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))

```

```{r compute-diagnostics}
s <- 1
### transform from cmdstan here
f_draws <- sim_model3_stan_sim1 %>% 
select(starts_with("f"))
###
model1_par_est <- list(
  lambda0 = mean(sim_model3_stan_sim1$lambda0),
  eta_1 = mean(sim_model3_stan_sim1$eta_1),
  eta_2 = mean(sim_model3_stan_sim1$eta_2),
  eta_3 = mean(sim_model3_stan_sim1$eta_3),
  beta = mean(sim_model3_stan_sim1$beta),
  f = apply(f_draws, 2, mean)
)

for (i in c(1:num_nodes)) {
  for (j in c(1:num_nodes)[-i]) {
    current_t <- sim_model3_data$mmhp_matrix[i, j][[1]]$tau
    m1_object <- list(
      lambda0 = model1_par_est$lambda0,
      alpha = model1_fn$alpha.fun(
        model1_par_est$f[i],
        model1_par_est$f[j],
        model1_par_est$eta_1,
        model1_par_est$eta_2,
        model1_par_est$eta_3
      ),
      beta = model1_par_est$beta
    )
    Lambda_model1_array[s, i, j] <-
      uniHawkesIntegralIntensity(
        object = m1_object,
        events = current_t,
        termination = tail(current_t, 1)
      )
    Lambda_test <- uniHawkesCompensator(
      object = m1_object,
      events = current_t
    )
    KS_model1_array[s, i, j] <- ks.test(Lambda_test, "pexp")$statistic
    KS_p_model1_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
    PR_model1_array[s, i, j] <- uniHawkesPearsonResidual(
      object = m1_object,
      events = current_t,
      termination =
        tail(current_t, 1)
    )
  }
}

## model2
#############
### convert to cmdstan
gamma_draws <- sim_model3_stan_sim2 %>% 
select(starts_with("gamma"))
zeta_draws <- sim_model3_stan_sim2 %>% 
select(starts_with("zeta"))
f_draws <- sim_model3_stan_sim2 %>% 
select(starts_with("f"))

model2_par_est <- list(
  gamma = apply(gamma_draws, 2, mean),
  zeta = apply(zeta_draws, 2, mean),
  eta_1 = mean(sim_model3_stan_sim2$eta_1),
  eta_2 = mean(sim_model3_stan_sim2$eta_2),
  eta_3 = mean(sim_model3_stan_sim2$eta_3),
  beta = mean(sim_model3_stan_sim2$beta),
  f = apply(f_draws, 2, mean)
)

for (i in c(1:num_nodes)) {
  for (j in c(1:num_nodes)[-i]) {
    current_t <- sim_model3_data$mmhp_matrix[i, j][[1]]$tau
    m2_object <- list(
      lambda0 = model2_par_est$gamma[i] +
        model2_par_est$zeta[j],
      alpha = model1_fn$alpha.fun(
        model2_par_est$f[i],
        model2_par_est$f[j],
        model2_par_est$eta_1,
        model2_par_est$eta_2,
        model2_par_est$eta_3
      ),
      beta = model2_par_est$beta
    )
    Lambda_model2_array[s, i, j] <-
      uniHawkesIntegralIntensity(
        object = m1_object,
        events = current_t,
        termination = tail(current_t, 1)
      )
    Lambda_test <- uniHawkesCompensator(
      object = m2_object,
      events = current_t
    )
    KS_model2_array[s, i, j] <- ks.test(Lambda_test, "pexp")$statistic
    KS_p_model2_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
    PR_model2_array[s, i, j] <-
      uniHawkesPearsonResidual(
        object = m2_object,
        events = current_t,
        termination = tail(current_t, 1)
      )
  }
}

```

We can then briefly look at some of these fits.

```{r m1-m2-diags}
# hist(as.vector(-log(KS_p_model1_array)))
# hist(as.vector(-log(KS_p_model2_array)))
# 
# hist(as.vector(PR_model1_array))
# hist(as.vector(PR_model2_array))

exp_fcn <- function(x) exp(-x)

tibble(ks = as.vector(KS_p_model1_array)) %>% 
  filter(ks != 0) %>% 
  mutate(log_p = -log(ks)) %>% 
  ggplot(aes(x = log_p)) + 
  # geom_freqpoly(binwidth = 20) +
  geom_histogram(aes(y = ..density..)) +
  # scale_fill_manual(values = cols_plot) +
  labs(y = "Negative Log KS Statistic P Value", title = "C-HP") +
  stat_function(fun = exp_fcn, colour = "red")

tibble(ks = as.vector(KS_p_model2_array)) %>% 
  filter(ks != 0) %>% 
  mutate(log_p = -log(ks)) %>% 
  ggplot(aes(x = log_p)) + 
  # geom_freqpoly(binwidth = 20) +
  geom_histogram(aes(y = ..density..)) +
  # scale_fill_manual(values = cols_plot) +
  labs(y = "Negative Log KS Statistic P Value", title = "C-DCHP") +
  stat_function(fun = exp_fcn, colour = "red")

```

```{r}
## Model3 & true model
######
### cmdstan part
lam0_draws <- sim_model3_stan_sim3 %>% 
select(starts_with("lambda0"))
lam1_draws <- sim_model3_stan_sim3 %>% 
select(starts_with("lambda1"))
f_draws <- sim_model3_stan_sim3 %>% 
select(starts_with("f"))

lambda_0_est <- apply(lam0_draws, 2, mean)
lambda_1_est <- apply(lam1_draws, 2, mean)
## then put these into a matrix
lam0_par_est <- matrix(0,
  nrow = length(object_par$f_vec_1),
  ncol = length(object_par$f_vec_1)
)
lam1_par_est <- matrix(0,
  nrow = length(object_par$f_vec_1),
  ncol = length(object_par$f_vec_1)
)
for (i in seq_along(lambda_0_est)) {
  row_id <- clean_sim_data$I_fit[i]
  col_id <- clean_sim_data$J_fit[i]
  if(clean_sim_data$N_count[row_id, col_id ] >= cut_off) {
    lam0_par_est[row_id, col_id] <- lambda_0_est[i]
    lam1_par_est[row_id, col_id] <- lambda_1_est[i]
  }

}
mmhp_par_est <- list(
  lambda0 = lam0_par_est,
  lambda1 = lam1_par_est,
  eta_1 = mean(sim_model3_stan_sim3$eta_1),
  eta_2 = mean(sim_model3_stan_sim3$eta_2),
  eta_3 = mean(sim_model3_stan_sim3$eta_3),
  beta = mean(sim_model3_stan_sim3$beta),
  f = apply(f_draws, 2, mean)
)
clean_sim_data <- cleanSimulationData(
  raw_data = sim_model3_data,
  cut_off = cut_off,
  N = length(object_par$f_vec_1)
)

for (i in c(1:num_nodes)) {
  for (j in c(1:num_nodes)[-i]) {
    test.mmhp <- sim_model3_data$mmhp_matrix[i, j][[1]]
    temp.t <- test.mmhp$tau
    current.n <- length(temp.t) - 1
    time.segment <- seq(0, tail(temp.t, 1), length.out = 10000)

    object_hat <- list(
      lambda0 = mmhp_par_est$lambda0[i, j],
      lambda1 = mmhp_par_est$lambda1[i, j],
      alpha = model3_fn$alpha.fun(
        mmhp_par_est$f[i],
        mmhp_par_est$f[j],
        mmhp_par_est$eta_1,
        mmhp_par_est$eta_2
      ),
      beta = mmhp_par_est$beta,
      q1 = model3_fn$q1.fun(
        mmhp_par_est$f[i],
        mmhp_par_est$f[j],
        mmhp_par_est$eta_3
      ),
      q2 = model3_fn$q0.fun(
        mmhp_par_est$f[i],
        mmhp_par_est$f[j],
        mmhp_par_est$eta_3
      )
    )

    object_true <- lapply(object_matrix, function(x) x[i, j])
    names(object_true) <- c("lambda0", "lambda1",
                            "alpha", "beta", "q1", "q2")

    ## est Lambda and [R]
    if(length(temp.t) > 2){
      Lambda.test <- mmhpCompensator(
        params = object_hat,
        t = temp.t,
        pzt = 2 -
          event_state_est_lst[i, j][[1]]$zt_v,
        if.pzt = FALSE
      )
      KS_model3_array[s, i, j] <- ks.test(Lambda.test, "pexp")$statistic
      KS_p_model3_array[s, i, j] <- ks.test(Lambda.test, "pexp")$p.value
      state.est.latent.mmhp <- interpolate_state_est_lst[i, j][[1]]
      step.fun.est <- stepfun(
        state.est.latent.mmhp$x.hat,
        2 - state.est.latent.mmhp$z.hat
      )
      est.intensity <- mmhpIntensityNumeric(
        params = object_hat,
        t = temp.t[-1],
        time.vec = time.segment,
        latent.vec =
          step.fun.est(time.segment)
      )
      est.intensity.events <- mmhpIntensityAtEvents(
        params = object_hat,
        t = temp.t,
        latent_z =
          event_state_est_lst[i, j][[1]]$zt_v
      )
    Lambda_model3_array[s, i, j] <-
      sum(est.intensity) * (time.segment[2] - time.segment[1])

    }
    if(clean_sim_data$N_count[i,j] < cut_off) {
      PR_model3_array[s, i, j] <- 0
    }
    else {
     PR_model3_array[s, i, j] <- sum(1 / sqrt(est.intensity.events)) -
      sum(sqrt(est.intensity)) * (time.segment[2] - time.segment[1]) 
    }

    ## Under the true model
    if(length(temp.t) > 2) {
      Lambda.test.true <- mmhpCompensator(
        params = object_true,
        t = temp.t,
        pzt = 2 -
          test.mmhp$zt[2:length(test.mmhp$zt)],
        if.pzt = FALSE
      )
      KS_true_array[s, i, j] <- ks.test(Lambda.test.true, "pexp")$statistic
      KS_p_true_array[s, i, j] <- ks.test(Lambda.test.true, "pexp")$p.value
      true.intensity <-
        mmhpTrueIntensityNumeric(
          params = object_true,
          t = temp.t,
          latent = list(
            ## these are the truth
            x = fixStateTransition(test.mmhp)$x,
            z = fixStateTransition(test.mmhp)$z
          ),
          time.vec = time.segment
        )
      true.intensity.events <- mmhpIntensityAtEvents(
        params = object_true,
        t = temp.t,
        latent_z = test.mmhp$zt
      )
      Lambda_true_array[s, i, j] <- sum(true.intensity$lambda.t) *
        (time.segment[2] - time.segment[1])
    }

    if(clean_sim_data$N_count[i,j] < cut_off) {
      PR_true_array[s, i, j] <- 0
    }
    else{
      PR_true_array[s, i, j] <- sum(1 / sqrt(true.intensity.events)) -
      sum(sqrt(true.intensity$lambda.t)) * (time.segment[2] - time.segment[1])
    }
  }
}
```

```{r diag-m3}

tibble(ks = as.vector(KS_p_model3_array)) %>% 
  filter(ks != 0) %>% 
  mutate(log_p = -log(ks)) %>% 
  ggplot(aes(x = log_p)) + 
  # geom_freqpoly(binwidth = 20) +
  geom_histogram(aes(y = ..density..)) +
  # scale_fill_manual(values = cols_plot) +
  labs(y = "Negative Log KS Statistic P Value", title = "C-MMHP") +
  stat_function(fun = exp_fcn, colour = "red")

tibble(ks = as.vector(KS_p_true_array)) %>% 
  filter(ks != 0) %>% 
  mutate(log_p = -log(ks)) %>% 
  ggplot(aes(x = log_p)) + 
  # geom_freqpoly(binwidth = 20) +
  geom_histogram(aes(y = ..density..)) +
  # scale_fill_manual(values = cols_plot) +
  labs(y = "Negative Log KS Statistic P Value", title = "True Parameters") +
  stat_function(fun = exp_fcn, colour = "red")

```

```{r pr-histograms}
hist(as.vector(PR_model1_array))
hist(as.vector(PR_model2_array))
hist(as.vector(PR_model3_array))
hist(as.vector(PR_true_array))

summary(as.vector(PR_model1_array))
summary(as.vector(PR_model2_array))
summary(as.vector(PR_model3_array))
summary(as.vector(PR_true_array))
```

## Inferred against True Ranks

```{r sim-ranks-plot}
f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
m1_ranks <- apply(f_m1, 2, mean)

f_m1_sims <- f_m1 %>% 
  rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
  rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
  pivot_longer(everything(),
               names_to = "node",
               values_to = "rank")
f_m1_sims$model <- "C-HP"

f_m2 <- sim_model3_stan_sim2 %>% select(starts_with("f"))
m2_ranks <- apply(f_m2, 2, mean)

f_m2_sims <- f_m2 %>% 
  rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
  rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
  pivot_longer(everything(),
               names_to = "node",
               values_to = "rank")

f_m2_sims$model <- "C-DCHP"

f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
m3_ranks <- apply(f_m1, 2, mean)

f_m3_sims <- f_m3 %>% 
  rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
  rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
  pivot_longer(everything(),
               names_to = "node",
               values_to = "rank")

f_m3_sims$model <- "C-MMHP"

sim_ranks <- bind_rows(f_m1_sims, f_m2_sims, f_m3_sims)

sim_ranks$node <- factor(sim_ranks$node, levels = 1:num_nodes)
sim_ranks$model <- factor(sim_ranks$model, levels = c("C-HP", 
                                                      "C-DCHP",
                                                      "C-MMHP"))

true_ranks <- tibble(node = 1:num_nodes, true_rank = object_par$f_vec_1)

sim_ranks %>% 
  ggplot(aes(node, rank)) +
  geom_boxplot() +
  facet_wrap(~model) +
  geom_point(data = true_ranks, aes(node, true_rank, colour = "red"),
             show.legend = FALSE)

```

# Diagnostics for all sims

```{r all-diags}
# sim_data_path <- here("output", "revisions", )

n_sim <- 20

num_nodes <- 10 #20
cut_off <- 3
obs_time <- 100 #100

# object_par <- list(sim_lambda_1 = 0.4,
#                    gamma_var = seq(from = 0.01,
#                                     to = .2,
#                                    length.out = num_nodes),
#                    zeta_var = rep(0.1, num_nodes),
#                    sim_eta_1 = 1, # from 3.5
#                    sim_eta_2 = 2, # from 2.6
#                    sim_eta_3 = 3, # this seems better
#                    #sim_eta_3 = 7.5,
#                    sim_beta = 1.5, # from 2
#                    f_vec_1 = seq(from = 0.10,
#                                  to = 0.9,
#                                  length.out = num_nodes))

## Initialize
N_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
Lambda_model3_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
Lambda_model1_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
Lambda_model2_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
Lambda_true_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
PR_model1_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
PR_model2_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
PR_model3_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
PR_true_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_model1_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_model2_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_model3_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_true_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_p_model1_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_p_model2_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_p_model3_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))
KS_p_true_array <- array(0, dim = c(
  n_sim, length(object_par$f_vec_1),
  length(object_par$f_vec_1)
))

```

```{r}
## Iteration on 50 simulations

sims <- 1:20
sims <- sims[c(-9,-13,-19,-20)]

for (s in sims) {
  print(s)
  load(paste0(sim_data_path, "sim_model3_fit123_", s, ".RData"))
  load(paste(sim_data_path, "fit123_state_est_", s, ".RData", sep = ""))
  clean_sim_data <- cleanSimulationData(
    raw_data = sim_model3_data,
    cut_off = cut_off,
    N = length(object_par$f_vec_1)
  )

  N_array[s, , ] <- clean_sim_data$N_count

  ## model 1
  #########
  ### transform from cmdstan here
  f_draws <- sim_model3_stan_sim1 %>% 
  select(starts_with("f"))

  ###
  model1_par_est <- list(
    lambda0 = mean(sim_model3_stan_sim1$lambda0),
    eta_1 = mean(sim_model3_stan_sim1$eta_1),
    eta_2 = mean(sim_model3_stan_sim1$eta_2),
    eta_3 = mean(sim_model3_stan_sim1$eta_3),
    beta = mean(sim_model3_stan_sim1$beta),
    f = apply(f_draws, 2, mean)
  )

  for (i in c(1:num_nodes)) {
    for (j in c(1:num_nodes)[-i]) {
      current_t <- sim_model3_data$mmhp_matrix[i, j][[1]]$tau
      m1_object <- list(
        lambda0 = model1_par_est$lambda0,
        alpha = model1_fn$alpha.fun(
          model1_par_est$f[i],
          model1_par_est$f[j],
          model1_par_est$eta_1,
          model1_par_est$eta_2,
          model1_par_est$eta_3
        ),
        beta = model1_par_est$beta
      )
      Lambda_model1_array[s, i, j] <-
        uniHawkesIntegralIntensity(
          object = m1_object,
          events = current_t,
          termination = tail(current_t, 1)
        )
      Lambda_test <- uniHawkesCompensator(
        object = m1_object,
        events = current_t
      )
      KS_model1_array[s, i, j] <- ks.test(Lambda_test, "pexp")$statistic
      KS_p_model1_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
      PR_model1_array[s, i, j] <- uniHawkesPearsonResidual(
        object = m1_object,
        events = current_t,
        termination =
          tail(current_t, 1)
      )
    }
  }

  ## model2
  #############
  ### convert to cmdstan
  gamma_draws <- sim_model3_stan_sim2 %>% 
  select(starts_with("gamma"))
  zeta_draws <- sim_model3_stan_sim2 %>% 
  select(starts_with("zeta"))
  f_draws <- sim_model3_stan_sim2 %>% 
  select(starts_with("f"))

  model2_par_est <- list(
    gamma = apply(gamma_draws, 2, mean),
    zeta = apply(zeta_draws, 2, mean),
    eta_1 = mean(sim_model3_stan_sim2$eta_1),
    eta_2 = mean(sim_model3_stan_sim2$eta_2),
    eta_3 = mean(sim_model3_stan_sim2$eta_3),
    beta = mean(sim_model3_stan_sim2$beta),
    f = apply(f_draws, 2, mean)
  )

  for (i in c(1:num_nodes)) {
    for (j in c(1:num_nodes)[-i]) {
      current_t <- sim_model3_data$mmhp_matrix[i, j][[1]]$tau
      m2_object <- list(
        lambda0 = model2_par_est$gamma[i] +
          model2_par_est$zeta[j],
        alpha = model1_fn$alpha.fun(
          model2_par_est$f[i],
          model2_par_est$f[j],
          model2_par_est$eta_1,
          model2_par_est$eta_2,
          model2_par_est$eta_3
        ),
        beta = model2_par_est$beta
      )
      Lambda_model2_array[s, i, j] <-
        uniHawkesIntegralIntensity(
          object = m1_object,
          events = current_t,
          termination = tail(current_t, 1)
        )
      Lambda_test <- uniHawkesCompensator(
        object = m2_object,
        events = current_t
      )
      KS_model2_array[s, i, j] <- ks.test(Lambda_test, "pexp")$statistic
      KS_p_model2_array[s, i, j] <- ks.test(Lambda_test, "pexp")$p.value
      PR_model2_array[s, i, j] <-
        uniHawkesPearsonResidual(
          object = m2_object,
          events = current_t,
          termination = tail(current_t, 1)
        )
    }
  }

  ## Model3 & true model
  ######
  ### cmdstan part
  lam0_draws <- sim_model3_stan_sim3 %>% 
  select(starts_with("lambda0"))
  lam1_draws <- sim_model3_stan_sim3 %>% 
  select(starts_with("lambda1"))
  f_draws <- sim_model3_stan_sim3 %>% 
  select(starts_with("f"))

  if(ncol(lam0_draws) != sum(clean_sim_data$N_count >2)) {
    stop("Mismatch between params and event pairs")
  }

  lambda_0_est <- apply(lam0_draws, 2, mean)
  lambda_1_est <- apply(lam1_draws, 2, mean)
  ## then put these into a matrix
  lam0_par_est <- matrix(0,
    nrow = length(object_par$f_vec_1),
    ncol = length(object_par$f_vec_1)
  )
  lam1_par_est <- matrix(0,
    nrow = length(object_par$f_vec_1),
    ncol = length(object_par$f_vec_1)
  )
  for (i in seq_along(lambda_0_est)) {
    row_id <- clean_sim_data$I_fit[i]
    col_id <- clean_sim_data$J_fit[i]
    lam0_par_est[row_id, col_id] <- lambda_0_est[i]
    lam1_par_est[row_id, col_id] <- lambda_1_est[i]
  }
  mmhp_par_est <- list(
    lambda0 = lam0_par_est,
    lambda1 = lam1_par_est,
    eta_1 = mean(sim_model3_stan_sim3$eta_1),
    eta_2 = mean(sim_model3_stan_sim3$eta_2),
    eta_3 = mean(sim_model3_stan_sim3$eta_3),
    beta = mean(sim_model3_stan_sim3$beta),
    f = apply(f_draws, 2, mean)
  )
  clean_sim_data <- cleanSimulationData(
    raw_data = sim_model3_data,
    cut_off = cut_off,
    N = length(object_par$f_vec_1)
  )

  for (i in c(1:num_nodes)) {
    for (j in c(1:num_nodes)[-i]) {
      test.mmhp <- sim_model3_data$mmhp_matrix[i, j][[1]]
      temp.t <- test.mmhp$tau
      current.n <- length(temp.t) - 1
      time.segment <- seq(0, tail(temp.t, 1), length.out = 10000)

      object_hat <- list(
        lambda0 = mmhp_par_est$lambda0[i, j],
        lambda1 = mmhp_par_est$lambda1[i, j],
        alpha = model3_fn$alpha.fun(
          mmhp_par_est$f[i],
          mmhp_par_est$f[j],
          mmhp_par_est$eta_1,
          mmhp_par_est$eta_2
        ),
        beta = mmhp_par_est$beta,
        q1 = model3_fn$q1.fun(
          mmhp_par_est$f[i],
          mmhp_par_est$f[j],
          mmhp_par_est$eta_3
        ),
        q2 = model3_fn$q0.fun(
          mmhp_par_est$f[i],
          mmhp_par_est$f[j],
          mmhp_par_est$eta_3
        )
      )

      object_true <- lapply(object_matrix, function(x) x[i, j])
      names(object_true) <- c("lambda0", "lambda1",
                              "alpha", "beta", "q1", "q2")

      ## est Lmabda and [R]
      if(length(temp.t) > 2 ) {
        Lambda.test <- mmhpCompensator(
        params = object_hat,
        t = temp.t,
        pzt = 2 -
          event_state_est_lst[i, j][[1]]$zt_v,
        if.pzt = FALSE
        )
        KS_model3_array[s, i, j] <- ks.test(Lambda.test, "pexp")$statistic
        KS_p_model3_array[s, i, j] <- ks.test(Lambda.test, "pexp")$p.value
        state.est.latent.mmhp <- interpolate_state_est_lst[i, j][[1]]
        step.fun.est <- stepfun(
          state.est.latent.mmhp$x.hat,
          2 - state.est.latent.mmhp$z.hat
        )
        est.intensity <- mmhpIntensityNumeric(
          params = object_hat,
          t = temp.t[-1],
          time.vec = time.segment,
          latent.vec =
            step.fun.est(time.segment)
        )
        est.intensity.events <- mmhpIntensityAtEvents(
          params = object_hat,
          t = temp.t,
          latent_z =
            event_state_est_lst[i, j][[1]]$zt_v
        )
        Lambda_model3_array[s, i, j] <-
          sum(est.intensity) * (time.segment[2] - time.segment[1])
        PR_model3_array[s, i, j] <- sum(1 / sqrt(est.intensity.events)) -
          sum(sqrt(est.intensity)) * (time.segment[2] - time.segment[1])
        }
      ## Under the true model
      if(length(temp.t) > 2 ) {
        Lambda.test.true <- mmhpCompensator(
        params = object_true,
        t = temp.t,
        pzt = 2 -
          test.mmhp$zt[2:length(test.mmhp$zt)],
        if.pzt = FALSE
        )
        KS_true_array[s, i, j] <- ks.test(Lambda.test.true, "pexp")$statistic
        KS_p_true_array[s, i, j] <- ks.test(Lambda.test.true, "pexp")$p.value
        true.intensity <-
          mmhpTrueIntensityNumeric(
            params = object_true,
            t = temp.t,
            latent = list(
              ## these are the truth
              x = fixStateTransition(test.mmhp)$x,
              z = fixStateTransition(test.mmhp)$z
            ),
            time.vec = time.segment
          )
        true.intensity.events <- mmhpIntensityAtEvents(
          params = object_true,
          t = temp.t,
          latent_z = test.mmhp$zt
        )
        Lambda_true_array[s, i, j] <- sum(true.intensity$lambda.t) *
          (time.segment[2] - time.segment[1])
        PR_true_array[s, i, j] <- sum(1 / sqrt(true.intensity.events)) -
          sum(sqrt(true.intensity$lambda.t)) * 
          (time.segment[2] - time.segment[1])
      }

    }
  }
  rm(sim_model3_data)
}
```

```{r plot-diag-output}
cols_plot <- col_df %>% 
  filter(method %in% c("C-HP","C-DCHP","C-MMHP", "True")) %>%
  arrange(factor(method, levels = c("C-HP", "C-DCHP", "C-MMHP", "True"))) %>%
  pull(cols)

m1_ks_p <- tibble(Method = "C-HP",
                  ks = as.vector(KS_p_model1_array[sims, ,]))

m2_ks_p <- tibble(Method = "C-DCHP",
                  ks = as.vector(KS_p_model2_array[sims, ,]))

m3_ks_p <- tibble(Method = "C-MMHP",
                  ks = as.vector(KS_p_model3_array[sims, ,]))

true_ks_p <- tibble(Method = "True",
                    ks = as.vector(KS_p_true_array[sims, ,]))

all_ks_p <- m1_ks_p %>% 
  bind_rows(m2_ks_p) %>% 
  bind_rows(m3_ks_p) %>% 
  bind_rows(true_ks_p)

all_ks_p$Method <- factor(all_ks_p$Method, levels = c("C-HP",
                                                      "C-DCHP",
                                                      "C-MMHP",
                                                      "True") )

exp_fcn <- function(x) exp(-x)

all_ks_p %>% 
  filter(ks != 0) %>% 
  mutate(log_p = -log(ks)) %>% 
  ggplot(aes(x = log_p)) + 
  # geom_freqpoly(binwidth = 20) +
  geom_histogram(aes(y = ..density.., fill = Method), bins = 50) +
  scale_fill_manual(values = cols_plot) +
  labs(y = "Negative Log KS Statistic P Value") +
  stat_function(fun = exp_fcn, colour = "red") +
  facet_wrap(~Method)
```

```{r pr-summary}
summary(as.vector(PR_model1_array[sims, ,]))
summary(as.vector(PR_model2_array[sims, ,]))
summary(as.vector(PR_model3_array[sims, ,][is.finite(PR_model3_array[sims,
                                                                     ,])]))
summary(as.vector(PR_true_array[sims, ,]))
```

### Ranks from all Sims

```{r}
# sim_data_path <- here("output", "revisions", "sim_m3", "sim_2", "/")

num_nodes <- 10

object_par$f_vec_1

sim_ranks_mean <- tibble()
sim_ranks <- tibble()

for(curr_sim in sims) {
  load(paste0(sim_data_path,
              "sim_model3_fit123_",
              curr_sim,
              ".RData"))

  f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
  m1_ranks <- apply(f_m1, 2, mean)

  f_m1_sims <- f_m1 %>% 
    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
    pivot_longer(everything(),
                 names_to = "node",
                 values_to = "rank")
  f_m1_sims$model <- "C-HP"

  f_m2 <- sim_model3_stan_sim2 %>% select(starts_with("f"))
  m2_ranks <- apply(f_m2, 2, mean)

  f_m2_sims <- f_m2 %>% 
    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
    pivot_longer(everything(),
                 names_to = "node",
                 values_to = "rank")

  f_m2_sims$model <- "C-DCHP"

  f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
  m3_ranks <- apply(f_m3, 2, mean)

  f_m3_sims <- f_m3 %>% 
    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
    pivot_longer(everything(),
                 names_to = "node",
                 values_to = "rank")

  f_m3_sims$model <- "C-MMHP"

  curr_mean_ranks <- tibble(model = c(rep("C-HP", num_nodes),
                                 rep("C-DCHP", num_nodes),
                                 rep("C-MMHP", num_nodes)),
                       ranks = c(m1_ranks,
                                 m2_ranks,
                                 m3_ranks),
                       node = rep(1:num_nodes, 3),
                       true_rank = rep(object_par$f_vec_1, 3),
                       sim_id = curr_sim)
  sim_ranks_mean <- sim_ranks_mean %>% 
    bind_rows(curr_mean_ranks)

  sim_ranks <- sim_ranks %>% 
    bind_rows(f_m1_sims, f_m2_sims, f_m3_sims)

}

sim_ranks$node <- factor(sim_ranks$node, levels = 1:num_nodes)
sim_ranks_mean$node <- factor(sim_ranks_mean$node, levels = 1:num_nodes)
sim_ranks_mean$model <- factor(sim_ranks_mean$model, 
                               levels = c("C-HP", "C-DCHP", "C-MMHP"))
# sim_ranks$node

sim_ranks_mean %>% 
  # filter(model == "C-MMHP") %>% 
  ggplot(aes(node, ranks)) + 
  geom_boxplot() +
  facet_wrap(~model) +
  geom_point(aes(node, true_rank, colour = "red"),
             show.legend = FALSE) +
  labs(title = "Mean rank from each simulation")

## this is just the mean from each simulation, not the posterior draws

true_ranks <- tibble(node = 1:num_nodes, true_rank = object_par$f_vec_1)
true_ranks$node <- factor(true_ranks$node, levels = 1:num_nodes)

sim_ranks %>% 
  ggplot(aes(node, rank)) +
  geom_boxplot() +
  facet_wrap(~model) +
  geom_point(data = true_ranks, aes(node, true_rank, colour = "red"),
             show.legend = FALSE) +
  labs(title = "All Posterior Draws")

```

```{r other-code, include=FALSE}
col_df <- tibble(method = c("I&SI",
                            "AggRank",
                            "DSNL",
                            "Glicko",
                            "I-MMHP",
                            "C-HP",
                            "C-DCHP",
                            "True",
                            "C-MMHP"),
                 cols = viridis(9))

```

### 2021-07-14 output_scripts/Paper_Plots.Rmd
large revamp of paper rmd
remove old plot chunks, update with plots for reponse, etc

@@
 knitr::opts_chunk$set(
-  echo = TRUE, fig.path = "paper_figure/",
+  echo = TRUE, fig.path = "paper_figure/revision/",
   dev = "png", fig.height = 4.5, fig.width = 7,
@@
 # don't write to this path
-data_path <- "../output/"
+data_path <- "../output/revisions/"
 
@@
 
-## New Fig
+## Test figure (not used)
 
@@
 
-Plot the negative log of the p values here.
-
-```{r potential-fig3-diag, eval=FALSE}
-M1_ks_p <- tibble(ks_p = as.vector(ks_chp), method = "C-HP")
-
-M2_ks_p <- tibble(ks_p = as.vector(ks_dchp), 
-                  method = "C-DCHP")
-
-ks_p <- bind_rows(M1_ks_p, M2_ks_p) %>% 
-  left_join(col_df, by = "method")
-
-cols_plot <- col_df %>%
-  filter(method %in% c("C-HP", "C-DCHP")) %>% 
-  pull(cols)
-
-exp_fcn <- function(x) exp(-x)
-
-ks_p$method <- factor(ks_p$method, levels = c("C-HP", "C-DCHP"))
-
-ks_p %>% 
-  filter(ks_p != 0) %>% 
-  mutate(log_p = -log(ks_p)) %>% 
-  ggplot(aes(x = log_p)) + 
-  # geom_freqpoly(binwidth = 20) +
-  geom_histogram(aes(y = ..density.., fill = method), bins = 50) +
-  scale_fill_manual(values = cols_plot) +
-  labs(y = "Negative Log KS Statistic P Value") +
-  stat_function(fun = exp_fcn, colour = "red") +
-  facet_wrap(~method) +
-  labs(fill = "Method") +
-  theme_minimal()
-
-```
-
-Could repeat this across all cohorts?
-
-What is `data_path` here?
+Plot the negative log of the p values here for all cohorts.
 
@@
 
-```{r plot-pvalues-m1-m2-here}
-ks_p %>% filter(ks_p != 0) %>%
-  select(-cols) %>% 
-  mutate(id = row_number()) %>% 
-  pivot_wider(names_from = method, values_from = ks_p)
-
+```{r plot-pvalues-m1-m2-here, eval=FALSE}
 bind_cols(M1_ks_p, M2_ks_p) %>% 
@@
 
-## Figure 3b: Ranking Comparison
-
-```{r fig-3b-rank-comparison, include=FALSE,eval=original_plots}
+## Figure 3b: Residual Structure
+
+```{r fig-3b-residual-structure, include=TRUE, eval=revision_plots}
+### now to add Pearson residual matrices here for C-HP and C-DCHP from fig 7
 current_cohort <- 5
-colors_plot <- col_df %>%
-  filter(method %in% c("C-HP", "C-DCHP")) %>%
-  pull(cols)
-load(paste(data_path,
-  cohort_names[current_cohort],
-  "/cohort_hp_stan_result_",
-  cohort_names[current_cohort],
+data_path <- "../output/revisions/"
+## 2 and 8 maybe look better
+## 3 probably looks the best
+
+m1_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+  "/chp_pr_matrix_", cohort_names[current_cohort],
+  ".RDS",
+  sep = ""
+))
+
+m2_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+  "/dchp_pr_matrix_", cohort_names[current_cohort],
+  ".RDS",
+  sep = ""
+))
+
+m3_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+  "/cmmhp_pr_matrix_", cohort_names[current_cohort],
+  ".RDS",
+  sep = ""
+))
+
+indep_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+  "/immhp_pr_matrix_", cohort_names[current_cohort],
+  ".RDS",
+  sep = ""
+))
+
+matrix_lst_plot <- list(
+  m1_pr[
+    rev(expert_rank_10[[current_cohort]]),
+    expert_rank_10[[current_cohort]]
+  ],
+  m2_pr[
+    rev(expert_rank_10[[current_cohort]]),
+    expert_rank_10[[current_cohort]]
+  ]
+  # ,
+  # m3_pr[
+  #   rev(expert_rank_10[[current_cohort]]),
+  #   expert_rank_10[[current_cohort]]
+  # ]
+)
+# cat("Cohort ",current_cohort,"\n",sep="")
+myMultiMatrixPlot(
+  X = matrix_lst_plot, no_matrix = 2, n_row = 1,
+  xLabels = expert_rank_10[[current_cohort]],
+  yLabels = rev(expert_rank_10[[current_cohort]]),
+  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
+  colorPalette = "RdBu", if.emp = FALSE,
+  # legend.mar=c(0.5,.5,0.5,0.5),
+  title_lst = list("C-HP", "C-DCHP", "C-MMHP"),
+  # title_lst = list("I-MMHP"),
+  col_axis = c(-80, -40, 0, 40, 80), fake_matrix = TRUE,
+  matrix.mar = c(2.5, 2.5, 2.5, 1)
+)
+mtext(text="(b)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)
+
+```
+
+## Additional Cohort for Response
+
+Add this below figure to the response to show how different cohorts 
+result in different response.
+
+```{r fig3-cohort-response}
+current_cohort <- 6
+
+load(paste(data_path, cohort_names[current_cohort],
+  "/cohort_dchp_stan_result_", cohort_names[current_cohort],
   ".RData",
@@
 ))
-load(paste(data_path,
-  cohort_names[current_cohort],
-  "/cohort_dchp_stan_result_",
-  cohort_names[current_cohort],
-  ".RData",
-  sep = ""
-))
-# png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
+
+gamma_draws <- sim_cohort_dchp %>% select(starts_with("gamma"))
+zeta_draws <- sim_cohort_dchp %>% select(starts_with("zeta"))
+
+gamma_mean <- apply(gamma_draws, 2, mean)
+zeta_mean <- apply(zeta_draws, 2, mean)
+
+# social matrix plot
+latent_social_matrix <- gamma_mean %*%
+  t(rep(1, mice_number)) + rep(1, mice_number) %*% t(zeta_mean)
+
+# png(paste(plot_path,"/lambda0_",
+# cohort_names[current_cohort],".png",sep=''),
 #     width=400, height=300)
-par(oma = c(0, 0, 2, 0), mar = c(3, 4, 1, 1), mgp = c(0, 0.5, 0))
-plot(order(expert_rank_10[[current_cohort]]),
-  apply(sim_cohort_hp$f, 2, mean),
-  pch = 16, cex = 1.2,
-  # col= "steelblue",
-  col = colors_plot[1],
-  ylab = "", xlab = "",
-  xlim = c(1, 12.5), ylim = c(0, 1),
-  xaxt = "n", yaxt = "n"
-)
-segments(order(expert_rank_10[[current_cohort]]),
-  apply(sim_cohort_hp$f, 2, mean) -
-    apply(sim_cohort_hp$f, 2, sd),
-  order(expert_rank_10[[current_cohort]]),
-  apply(sim_cohort_hp$f, 2, mean) +
-    apply(sim_cohort_hp$f, 2, sd),
-  # col= add.alpha("steelblue",0.8),lwd=2)
-  col = add.alpha(colors_plot[1], 0.8), lwd = 2
-)
-points(order(expert_rank_10[[current_cohort]]) + 0.2,
-  apply(sim_cohort_dchp$f, 2, mean),
-  pch = 16,
-  cex = 1.2,
-  col = colors_plot[2]
-)
-# col="goldenrod2")
-segments(order(expert_rank_10[[current_cohort]]) + 0.2,
-  apply(sim_cohort_dchp$f, 2, mean) - apply(sim_cohort_dchp$f, 2, sd),
-  order(expert_rank_10[[current_cohort]]) + 0.2,
-  apply(sim_cohort_dchp$f, 2, mean) + apply(sim_cohort_dchp$f, 2, sd),
-  col = add.alpha(colors_plot[2], 0.8), lwd = 2
-)
-# col= add.alpha("goldenrod2",0.8),lwd=2)
-
-axis(BELOW <- 1, at = 1:12, 
-     labels = expert_rank_10[[current_cohort]],
-     cex.axis = 1.3,
-     tck = -0.015)
-# mtext(text=11, side=1, line=0.5, cex=1.3, at=6)
-
-axis(LEFT <- 2,
-  at = seq(0, 1, 0.2), labels = seq(0, 1, 0.2), las = HORIZONTAL <- 1,
-  cex.axis = 1.3, tck = -0.015
-)
-mtext(side = 1, text = "I&SI rank", line = 1.8, cex = 1.5)
-mtext(side = 2, text = "Latent rank", line = 2.4, cex = 1.6)
-mtext(side = 3, text = "(b)", line = 0.8, cex = 1.6, font = 2)
-legend("bottomleft",
-  legend = c("C-HP", "C-DCHP"),
-  pch = c(16, 16), lty = c(1, 1), lwd = c(2, 2),
-  # col=c("steelblue","goldenrod"),
-  col = c(colors_plot[1], colors_plot[2]),
-  cex = 1.5
-)
-# dev.off()
+matrixPlotParameter(latent_social_matrix[
+  rev(expert_rank_10[[current_cohort]]),
+  expert_rank_10[[current_cohort]]
+],
+xLabels = expert_rank_10[[current_cohort]],
+yLabels = rev(expert_rank_10[[current_cohort]])
+)
+
 ```
 
-```{r, eval=FALSE, include=FALSE}
-## need Hmisc for this
-library(Hmisc)
-
-par(mar = c(3, 3, 1, 1))
-plot(as.vector(n_matrix[n_matrix > 0]),
-     as.vector(ks.stat.matrix[n_matrix > 0]),
-     xlab = "",
-     ylab = "",
-     pch = 16,
-     col = "gray",
-     cex = 0.8,
-     xaxt = "n",
-     yaxt = "n",
-  ylim = c(0, 0.65)
-)
-mtext("Number of events", cex = 1.5, side = 1, line = 1.8)
-mtext("K-S statistics", cex = 1.5, side = 2, line = 1.5)
-mgp.axis(1, mgp = c(0, 0.3, 0),
-         at = seq(0, 120, 10),
-         cex.axis = 1,
-         lwd = 0,
-         lwd.ticks = 0.1)
-mgp.axis(2, mgp = c(0, 0.1, 0),
-         at = seq(-0.2, 0.6, 0.2),
-         cex.axis = 1,
-         lwd = 0,
-         lwd.ticks = 0.8)
-```
-
 # Figure 4:
-
-## Figure 4a Recover Latent Ranks
-```{r fig-4a, fig.height=3.5, fig.width=8, eval=original_plots}
-sim_data_path <- "../output/sims_m3_update/"
-
-# load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
-# load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
-#### need to edit here to account for separate files now
-
-m3_files <- list.files(sim_data_path, pattern = "sim_model3_fit*")
-# m1_files
-
-# load(paste0(m1_path,m1_files[1]))
-sim_model3_stan_sim1_total <- list()
-sim_model3_stan_sim2_total <- list()
-sim_model3_stan_sim3_total <- list()
-
-for (i in seq_along(m3_files)) {
-  load(paste0(sim_data_path, m3_files[i]))
-  sim_model3_stan_sim1_total[[i]] <- sim_model3_stan_sim1
-  sim_model3_stan_sim2_total[[i]] <- sim_model3_stan_sim2
-  sim_model3_stan_sim3_total[[i]] <- sim_model3_stan_sim3
-}
-
-n_sim <- 50
-
-# png(paste(plot_path,"sim_latent_recover.png",sep=""), height=500, width=900)
-par(
-  mfrow = c(3, length(object_par$f_vec_1)),
-  mar = c(0, 0, 1, 0),
-  oma = c(6.5, 11, 3.5, 1)
-)
-
-y.ub <- c(12, 12, 12, 12, 12)
-text.y <- c(rep(8, 4), 8)
-text.x <- c(0.1, 0.2, 0.4, 0.7, 0.9)
-text.x.adj <- c(0.3, 0.4, 0.6, 0.5, 0.8)
-
-model_colors <- col_df %>%
-  filter(method %in% c(
-    "C-HP",
-    "C-DCHP", "C-MMHP"
-  )) %>%
-  pull(cols)
-
-for (m in c(1:3)) {
-  for (j in c(1:length(object_par$f_vec_1))) {
-    plot(1, 4,
-      xlim = c(0, 1), ylim = c(0, y.ub[j]),
-      type = "n", xlab = "",
-      ylab = "", xaxt = "n",
-      yaxt = "n", axes = FALSE
-    )
-
-    ## Posterior density
-    # current_result <- eval(parse(text=paste("sim_model3_stan_sim",m,sep="")))
-    current_result <- eval(parse(text = paste("sim_model3_stan_sim",
-      m,
-      "_total",
-      sep = ""
-    )))
-    for (i in c(1:n_sim)) {
-      lines(density(current_result[[i]]$f[, j]),
-        col = add.alpha(model_colors[m], alpha = 0.8), cex = 0.6, lwd = 0.8
-      )
-    }
-
-    ## plot true value
-    abline(v = object_par$f_vec_1[j], lwd = 1.8, lty = 2, col = "gray30")
-
-    ## plot box
-    box.wdt <- 1.5
-    box.col <- "black"
-    box(lty = "solid", col = box.col, lwd = 0.7)
-
-    if (m == 3) {
-      text(text.x.adj[j], text.y[j], text.x[j], cex = 2.4)
-    }
-  }
-  ## bottom
-  mtext(
-    text = expression(f[1], f[2], f[3], f[4], f[5]),
-    side = 1, line = 2.4, outer = TRUE,
-    at = c(1:length(object_par$f_vec_1)) / length(object_par$f_vec_1) - 0.1,
-    cex = 2
-  )
-  mtext(
-    text = "Latent rank variables", side = 1,
-    line = 5.3,
-    outer = TRUE,
-    cex = 2.25,
-    at = 0.5
-  )
-  ## top
-  mtext(
-    text = "(a)", side = 3,
-    line = 0,
-    outer = TRUE,
-    cex = 2.5,
-    at = 0.5, font = 2
-  )
-  ## left
-  mtext(
-    text = rev(c("C-HP  ", "C-DCHP", "C-MMHP")),
-    side = 2,
-    line = 0.5,
-    outer = TRUE,
-    at = c(0:2) / 3 + 0.15,
-    cex = 1.75, las = 2
-  )
-}
-```
-
-```{r fig4a-new-hist, fig.height=3.5, fig.width=8, eval=original_plots}
-model_colors <- col_df %>% filter(method %in% c(
-  "C-HP",
-  "C-DCHP",
-  "C-MMHP"
-))
-
-model_colors <- model_colors %>% pull(cols)
-
-m1 <- sim_model3_stan_sim1_total %>%
-  map(~ apply(.x$f, 2, mean)) %>%
-  enframe() %>%
-  unnest(cols = value) %>%
-  mutate(
-    node_id = rep(c("f1", "f2", "f3", "f4", "f5"), 50),
-    method = "C-HP"
-  )
-
-m2 <- sim_model3_stan_sim2_total %>%
-  map(~ apply(.x$f, 2, mean)) %>%
-  enframe() %>%
-  unnest(cols = value) %>%
-  mutate(
-    node_id = rep(c("f1", "f2", "f3", "f4", "f5"), 50),
-    method = "C-DCHP"
-  )
-
-m3 <- sim_model3_stan_sim3_total %>%
-  map(~ apply(.x$f, 2, mean)) %>%
-  enframe() %>%
-  unnest(cols = value) %>%
-  mutate(
-    node_id = rep(c("f1", "f2", "f3", "f4", "f5"), 50),
-    method = "C-MMHP"
-  )
-
-rank_means <- bind_rows(m1, m2, m3)
-
-# rank_means
-
-true_values <- tibble(
-  id = c("f1", "f2", "f3", "f4", "f5"),
-  values = c(0.1, 0.2, 0.4, 0.7, 0.9),
-  val_names = c("   0.1", "0.2", "0.4", "0.7", "0.9")
-)
-
-rank_means %>%
-  left_join(true_values, by = c("node_id" = "id")) %>%
-  ggplot(aes(value, fill = method)) +
-  geom_histogram() +
-  geom_vline(aes(xintercept = values),
-    alpha = 0.6,
-    linetype = "dashed"
-  ) +
-  ### add text here
-  geom_text(aes(values, 18, label = val_names),
-    size = 3, hjust = 1
-  ) +
-  scale_fill_manual(values = model_colors) +
-  facet_grid(cols = vars(node_id), rows = vars(method)) +
-  theme_bw() +
-  theme(
-    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
-    text = element_text(size = 12),
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank(),
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    legend.position = "none",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank()
-  ) +
-  labs(x = "", y = "")
-```
 
@@
 
-```{r new-fig-4a, eval = revision_plots, message=FALSE, warning=FALSE}
+```{r fig-4a, eval = revision_plots, message=FALSE, warning=FALSE}
 sim_data_path <- here("output", "revisions", "sim_m3", "sim_2", "/")
@@
 ## this is just the mean from each simulation, not the posterior draws
-
-# sim_ranks %>%
-#   ggplot(aes(node, rank)) +
-#   geom_boxplot() +
-#   facet_wrap(~model) +
-#   geom_point(data = true_ranks, aes(node, true_rank, colour = "red"),
-#              show.legend = FALSE) +
-#   labs(title = "All Posterior Draws")
 ```
@@
 
-To be updated!
+To be updated with the correct paths, etc
 
 ```{r data for fig 5,cache=TRUE, eval=revision_plots}
-n_sim <- 25
-
+n_sim <- 50
 num_nodes <- 10
 
-object_par <- list(f_vec_1 = seq(from = 0.1, to = 0.9,
+object_par <- list(f_vec_1 = seq(from = 0.2, to = 0.9,
                                  length.out = num_nodes))
-### TO DO
-
-sim_data_path <- here("output", "revisions", "sim_m3", "june_18", "/")
+
+sim_data_path <- here("output", "revisions", "sim_m3", "sim_2", "/")
 
@@
 ## Iteration on 50 simulations
-sims <- 1:25
-sims <- sims[c(-12, -22, -23, -24)]
+sims <- 1:50
+sims <- sims[c(-18)]
 
@@
 
-```{r fig5a-residual-ks, fig.height=7, eval=original_plots}
-# cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
-#                                              "True"))
-
-cols_plot <- col_df %>%
-  filter(method %in% c(
-    "C-HP", "C-DCHP", "C-MMHP",
-    "True"
-  )) %>%
-  arrange(factor(method, levels = c("C-HP", "C-DCHP", "C-MMHP", "True"))) %>%
-  pull(cols)
-# load("../output/sim_model3_fit123_residuals.RData")
-par(mfrow = c(5, 5), mar = c(0.2, 0.2, 0.2, 0.2), oma = c(2.4, 2.4, 2.9, 0.5))
-for (i in c(5:1)) {
-  for (j in c(5:1)) {
-    if (i == j) {
-      plot(1, 1,
-        type = "n", xlim = c(0, 1), ylim = c(0, 1),
-        bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
-      )
-      if (i == 5) {
-        polygon(c(0, 0, 0.15, 0.15), c(0.72, 0.8, 0.8, 0.72) + 0.04,
-          col = cols_plot[1], border = NA
-        )
-        polygon(c(0, 0, 0.15, 0.15), c(0.72, 0.8, 0.8, 0.72) + 0.04 - 0.22,
-          col = cols_plot[2], border = NA
-        )
-        polygon(c(0, 0, 0.15, 0.15), c(0.72, 0.8, 0.8, 0.72) + 0.04 - 0.44,
-          col = cols_plot[3], border = NA
-        )
-        polygon(c(0, 0, 0.15, 0.15), c(0.72, 0.8, 0.8, 0.72) + 0.04 - 0.66,
-          col = cols_plot[4], border = NA
-        )
-        text(c(0.43, 0.58, 0.61, 0.4), seq(0.8, 0.14, -0.22),
-          c("C-HP", "C-DCHP", "C-MMHP", "True"),
-          cex = 1.7
-        )
-      }
-    } else {
-      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
-      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
-      PR <- c(
-        KS_model1_array[, i, j], KS_model2_array[, i, j],
-        KS_model3_array[, i, j], KS_true_array[, i, j]
-      )
-      ### try pr scores instead
-      # PR <- c(PR_model1_array[,i,j],PR_model2_array[,i,j],
-      #         PR_model3_array[,i,j],PR_true_array[,i,j])
-      Type <- c(rep(1, n_sim), rep(2, n_sim), rep(3, n_sim), rep(4, n_sim))
-      boxplot(PR ~ Type,
-        col = cols_plot,
-        # col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),
-        xlab = "", ylab = "", xaxt = "n", yaxt = "n"
-      )
-      # names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
-    }
-  }
-}
-mtext(
-  text = c(1:5), side = 2, line = 0.5, outer = TRUE, cex = 2, las = 2,
-  at = c(0:4) / 5 + 0.1
-)
-mtext(
-  text = c(5:1), side = 1, line = 1.5, outer = TRUE, cex = 2,
-  at = c(0:4) / 5 + 0.1
-)
-mtext(text = "(a)", side = 3, line = 0.5, outer = TRUE, cex = 2.5, font = 2)
-```
-
-New potential Figure 5a plots.
+New potential Figure 5a plots. Need to improve this figure based on the newly
+chosen simulation parameters above.
 
@@
 
+### boxplot of ks statistics
+m1_ks <- tibble(Method = "C-HP",
+                  ks = as.vector(KS_model1_array[sims, ,]))
+
+m2_ks <- tibble(Method = "C-DCHP",
+                  ks = as.vector(KS_model2_array[sims, ,]))
+
+m3_ks <- tibble(Method = "C-MMHP",
+                  ks = as.vector(KS_model3_array[sims, ,]))
+
+true_ks <- tibble(Method = "True",
+                    ks = as.vector(KS_true_array[sims, ,]))
+
+all_ks <- m1_ks %>% 
+  bind_rows(m2_ks) %>% 
+  bind_rows(m3_ks) %>% 
+  bind_rows(true_ks)
+
+all_ks$Method <- factor(all_ks$Method, levels = c("C-HP",
+                                                  "C-DCHP",
+                                                  "C-MMHP",
+                                                  "True") )
+
+all_ks %>% 
+  filter(ks != 0) %>% 
+  ggplot(aes(Method, ks, fill = Method)) + 
+  geom_boxplot() +
+  scale_fill_manual(values = cols_plot) +
+  labs(y = "KS Statistic") +
+  theme_minimal()
+
 ```
@@
 Inferred ranking boxplots against true rankings.
-
-```{r posterior-mean-ranks}
-sim_data_path <- here("output", "revisions", "sim_m3", "june_18", "/")
-
-num_nodes <- 10
-
-# object_par$f_vec_1
-
-sim_ranks_mean <- tibble()
-sim_ranks <- tibble()
-
-for(curr_sim in sims) {
-  load(paste0(sim_data_path,
-              "sim_model3_fit123_",
-              curr_sim,
-              ".RData"))
-
-  f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
-  m1_ranks <- apply(f_m1, 2, mean)
-
-  f_m1_sims <- f_m1 %>% 
-    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
-    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
-    pivot_longer(everything(),
-                 names_to = "node",
-                 values_to = "rank")
-  f_m1_sims$model <- "C-HP"
-
-  f_m2 <- sim_model3_stan_sim2 %>% select(starts_with("f"))
-  m2_ranks <- apply(f_m2, 2, mean)
-
-  f_m2_sims <- f_m2 %>% 
-    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
-    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
-    pivot_longer(everything(),
-                 names_to = "node",
-                 values_to = "rank")
-
-  f_m2_sims$model <- "C-DCHP"
-
-  f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
-  m3_ranks <- apply(f_m3, 2, mean)
-
-  f_m3_sims <- f_m3 %>% 
-    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
-    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
-    pivot_longer(everything(),
-                 names_to = "node",
-                 values_to = "rank")
-
-  f_m3_sims$model <- "C-MMHP"
-
-  curr_mean_ranks <- tibble(model = c(rep("C-HP", num_nodes),
-                                 rep("C-DCHP", num_nodes),
-                                 rep("C-MMHP", num_nodes)),
-                       ranks = c(m1_ranks,
-                                 m2_ranks,
-                                 m3_ranks),
-                       node = rep(1:num_nodes, 3),
-                       true_rank = rep(object_par$f_vec_1, 3),
-                       sim_id = curr_sim)
-  sim_ranks_mean <- sim_ranks_mean %>% 
-    bind_rows(curr_mean_ranks)
-
-  sim_ranks <- sim_ranks %>% 
-    bind_rows(f_m1_sims, f_m2_sims, f_m3_sims)
-
-}
-
-sim_ranks$node <- factor(sim_ranks$node, levels = 1:num_nodes)
-sim_ranks_mean$node <- factor(sim_ranks_mean$node, levels = 1:num_nodes)
-
-# sim_ranks$node
-
-sim_ranks_mean$model <- factor(sim_ranks_mean$model,
-                               levels = c("C-HP", "C-DCHP", "C-MMHP"))
-
-sim_ranks_mean %>% 
-  # filter(model == "C-MMHP") %>% 
-  ggplot(aes(node, ranks, fill = model)) + 
-  geom_boxplot() +
-  scale_fill_manual(values = cols_plot, guide = 'none') +
-  facet_wrap(~model) +
-  geom_point(aes(node, true_rank, colour = "True Value"),
-             show.legend = TRUE) +
-  labs(title = "Mean rank from each simulation") +
-  theme_minimal() +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom")
-
-```
 
@@
 ## agg
+x_draws <- sim_agg_rank %>% select(starts_with("x"))
 plot_latent_df$force[(1:(1000 * mice_number))] <-
-  as.vector(sim_agg_rank$x[1001:2000, ])
+  as.vector(as.matrix(x_draws))
 
 ## M1
+f_draws <- sim_cohort_hp %>% select(starts_with("f"))
 plot_latent_df$force[(1:(1000 * mice_number)) +
-                       1000 * mice_number] <- as.vector(sim_cohort_hp$f)
+                       1000 * mice_number] <- as.vector(as.matrix(f_draws))
 
 ## M2
+f_draws <- sim_cohort_dchp %>% select(starts_with("f"))
 plot_latent_df$force[(1:(1000 * mice_number)) + 
-                       2000 * mice_number] <- as.vector(sim_cohort_dchp$f)
+                       2000 * mice_number] <- as.vector(as.matrix(f_draws))
 
 ## M3
+f_draws <- sim_cohort_mmhp %>% select(starts_with("f"))
 plot_latent_df$force[(1:(1000 * mice_number)) + 
-                       3000 * mice_number] <- as.vector(sim_cohort_mmhp$f)
+                       3000 * mice_number] <- as.vector(as.matrix(f_draws))
 
@@
 
-p1 <- ggplot(
-  plot_latent_df,
-  aes(x = Mice, y = force, fill = Method)) +
+p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
   geom_boxplot(alpha = 0.7) +
@@
 ```{r fig-6b-overall-rank-correlation}
-load("../output/weighted_rank_data.RData")
+load("../output/revisions/weighted_rank_data.RData")
 # png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
@@
 
-# Figure 7: Pearson residual matrices
+# Previous Figure 7: Pearson residual matrices
+
+No longer including this figure in the paper
 
@@
 current_cohort <- 5
-data_path <- "../output/"
+data_path <- "../output/revisions/"
 ## 2 and 8 maybe look better
@@
 
-```{r m1-m2-pr, fig.width=6}
-current_cohort <- 5
-m1_m2_plot <- list(m1_pr[
-    rev(expert_rank_10[[current_cohort]]),
-    expert_rank_10[[current_cohort]]
-  ],
-  m2_pr[
-    rev(expert_rank_10[[current_cohort]]),
-    expert_rank_10[[current_cohort]]
-  ])
-
-myMultiMatrixPlot(
-  X = m1_m2_plot, no_matrix = 2, n_row = 1,
-  xLabels = expert_rank_10[[current_cohort]],
-  yLabels = rev(expert_rank_10[[current_cohort]]),
-  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
-  colorPalette = "RdBu", if.emp = FALSE,
-  # legend.mar=c(0.5,.5,0.5,0.5),
-  title_lst = list("C-HP", "C-DCHP"),
-  # title_lst = list("I-MMHP"),
-  col_axis = c(-80, -40, 0, 40, 80), fake_matrix = TRUE,
-  matrix.mar = c(2.5, 2.5, 2.5, 1)
-)
-```
-
 ```{r fig-7b-matrix-structure-score, fig.width=7, fig.height=7}
@@
 ```{r fig-8a-frob-norm-cohort5, fig.width=8,fig.height=4,eval=TRUE}
-load("../output/plot_N_predict.RData")
+load("../output/revisions/plot_N_predict_revision.RData")
 current_cohort <- 5 # cohort 1 looks worse than rest
@@
   ylab("MAE") +
-  ylim(0, 8) + # aren't infinite but >150 and <200
+  ylim(0, 5) + # aren't infinite but >150 and <200
   NULL
@@
 ### updated to revision
-load("../output/plot_N_predict_revision.RData")
+load("../output/revisions/plot_N_predict_revision.RData")
 
@@
 ## Figure 9a: Predicted Spearman rank for single cohort
+
+This has not finished for new simulation setting yet.
 
@@
 
-```{r fig-glicko-pred-slides,eval=slides_plots,include=slides_plots}
-par(mar = c(3, 5, 3, 1))
-plot(1,
-  type = "n", xlab = "",
-  ylab = "Glicko ranking", xlim = c(0, dim(gl$history)[2]),
-  ylim = c(min(gl$history[, , 1]), max(gl$history[, , 1])),
-  cex.axis = 2, cex.lab = 2
-)
-for (m in c(1:mice_number)) {
-  # history
-  lines(gl$history[m, 1:training_end, 1],
-    cex = 0.6, col = col_vec[m], lwd = history_width, lty = ltypes_vec[m]
-  )
-  lines(c(rep(NA, training_end), 
-          gl$history[m, (training_end + 1):testing_end, 1]),
-    cex = 0.6, col = shade_vec[m], lwd = history_width, lty = ltypes_vec[m]
-  )
-
-  # simulation
-  cur_end <- testing_end
-  mean_vec <- apply(sim_gl_array[m, , ], 1, function(x) mean(na.omit(x)))
-  sd_vec <- apply(sim_gl_array[m, , ], 1, function(x) sd(na.omit(x)))
-  polygon(c(newx, rev(newx)), c(mean_vec - sd_vec, rev(mean_vec + sd_vec)),
-    col = shade_vec[m], border = NA
-  )
-  # polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
-  lines(c(rep(NA, training_end), mean_vec),
-    cex = 0.6, col = col_vec[m], lwd = 1, lty = 2
-  )
-}
-
-# annotate the days
-for (d in c(19:21)) {
-  abline(v = nrow(df[df$day <= (d - 1), ]), lty = 2, lwd = 0.4)
-  text(x = nrow(df[df$day <= (d - 1), ]), y = 2600, d)
-}
-# mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
-```
-
 ```{r remove some objects, include=FALSE}
@@
 clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-return_df <- cleanObservationPeriod(current_cohort, clean_data)
+return_df <- cleanObservationPeriod(current_cohort,
+                                    full_data[[cohort_names[current_cohort]]],
+                                    clean_data)
 unique_pairs_df <- return_df %>%
@@
 
+dsnl_x_sims <- sim_dsnl %>% select(starts_with("x"))
+
+dsnl_arr <- array(as.matrix(dsnl_x_sims), dim = c(1000, 21, 12))
+
 ## All aggregate
 for (t in 1:length(task.types)) {
-  temp_vec <- rep(NA, 2000)
+  temp_vec <- rep(NA, 1000)
   cur_real_rank <- real.gl$history[, day_end_idx[t], 1]
-  for (s in c(1:2000)) {
-    temp_result <- cor.test(sim_dsnl$x[s, t, ], cur_real_rank,
+  for (s in c(1:1000)) {
+    temp_result <- cor.test(dsnl_arr[s, t, ], cur_real_rank,
       method = "spearman"
@@
   }
-  data.tbl$sub.type[(1:2000) + (t - 1) * 2000] <- sub.types[1]
-  data.tbl$task.type[(1:2000) + (t - 1) * 2000] <- task.types[t]
-  data.tbl$data.value[(1:2000) + (t - 1) * 2000] <- temp_vec
+  data.tbl$sub.type[(1:1000) + (t - 1) * 1000] <- sub.types[1]
+  data.tbl$task.type[(1:1000) + (t - 1) * 1000] <- task.types[t]
+  data.tbl$data.value[(1:1000) + (t - 1) * 1000] <- temp_vec
 }
@@
 for (t in 1:length(task.types)) {
-  temp_vec <- rep(NA, 2000)
+  temp_vec <- rep(NA, 1000)
   cur_real_rank <- real.gl$history[, day_end_idx[t], 1]
-  for (s in c(1:2000)) {
+  for (s in c(1:1000)) {
     temp_result <- cor.test(-sim_dsnl_active$x[s, t, ], cur_real_rank,
@@
   }
-  data.tbl$sub.type[(1:2000) + (t - 1) * 2000 + 42000] <- sub.types[2]
-  data.tbl$task.type[(1:2000) + (t - 1) * 2000 + 42000] <- task.types[t]
-  data.tbl$data.value[(1:2000) + (t - 1) * 2000 + 42000] <- temp_vec
+  data.tbl$sub.type[(1:1000) + (t - 1) * 1000 + 21000] <- sub.types[2]
+  data.tbl$task.type[(1:1000) + (t - 1) * 1000 + 21000] <- task.types[t]
+  data.tbl$data.value[(1:1000) + (t - 1) * 1000 + 21000] <- temp_vec
 }
@@
 for (t in 1:length(task.types)) {
-  temp_vec <- rep(NA, 2000)
+  temp_vec <- rep(NA, 1000)
   cur_real_rank <- real.gl$history[, day_end_idx[t], 1]
-  for (s in c(1:2000)) {
+  for (s in c(1:1000)) {
     temp_result <- cor.test(sim_dsnl_inactive$x[s, t, ],
@@
   }
-  data.tbl$sub.type[(1:2000) + (t - 1) * 2000 + 42000 * 2] <- sub.types[3]
-  data.tbl$task.type[(1:2000) + (t - 1) * 2000 + 42000 * 2] <- task.types[t]
-  data.tbl$data.value[(1:2000) + (t - 1) * 2000 + 42000 * 2] <- temp_vec
+  data.tbl$sub.type[(1:1000) + (t - 1) * 1000 + 21000 * 2] <- sub.types[3]
+  data.tbl$task.type[(1:1000) + (t - 1) * 1000 + 21000 * 2] <- task.types[t]
+  data.tbl$data.value[(1:1000) + (t - 1) * 1000 + 21000 * 2] <- temp_vec
 }

### 2021-07-23 output_scripts/Paper_Plots.Rmd
some final updates to the plots, etc

@@
 # don't write to this path
-data_path <- "../output/revisions/"
+data_path <- "../output/revisions/lapl_check/"
 
@@
 library(here)
-library(rstan)
+# library(rstan)
+library(cmdstanr)
 Sys.setenv(LOCAL_CPPFLAGS = "-march=corei7 -mtune=corei7")
@@
 mice_number <- 12
+col_df <- tibble(
+  method = c(
+    "I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
+    "C-HP", "C-DCHP", "True", "C-MMHP"
+  ),
+  cols = viridis(9)
+)
 ```
@@
 ```{r creat colour df, eval=revision_plots, include=FALSE}
-col_df <- tibble(
-  method = c(
-    "I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
-    "C-HP", "C-DCHP", "True", "C-MMHP"
-  ),
-  cols = viridis(9)
-)
+# col_df <- tibble(
+#   method = c(
+#     "I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
+#     "C-HP", "C-DCHP", "True", "C-MMHP"
+#   ),
+#   cols = viridis(9)
+# )
 ```
@@
 
-data_path <- "../output/revisions/"
+data_path <- "../output/revisions/lapl_check/"
 
@@
 xLabels = expert_rank_10[[current_cohort]],
-yLabels = rev(expert_rank_10[[current_cohort]])
-)
-# title = "(a)" )
+yLabels = rev(expert_rank_10[[current_cohort]]),
+title = "(a)" )
 # mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
@@
     )
-  unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])
+  unique_observe_win <- unique(return_df[,
+                                         c("observe.id", "observe.time")])
 
@@
 current_cohort <- 5
-data_path <- "../output/revisions/"
+data_path <- "../output/revisions/lapl_check/"
 ## 2 and 8 maybe look better
@@
 ```{r fig-4a, eval = revision_plots, message=FALSE, warning=FALSE}
-sim_data_path <- here("output", "revisions", "sim_m3", "sim_2", "/")
+sim_data_path <- here("output", "revisions", "lapl_check", "sim_lapl", "/")
 
@@
 sims <- 1:50
-sims <- sims[c(-18)]
+sims <- sims[c(-37,-45,-46, -50)]
 
@@
 
-```{r prepare data for 4b,cache=TRUE, eval=FALSE}
-plot.s <- 7 # 7 is pretty good
-plot.i <- 4
-plot.j <- 5
-
-cur_i <- 4
-cur_j <- 5
-
-sim_data_path <- here("output", "revisions", "sim_m3", "june_18", "/")
+```{r prepare data for 4b,cache=TRUE, eval=TRUE}
+plot.s <- 26 # 8 is pretty good
+plot.i <- 10
+plot.j <- 9
+
+# 29 10 -> 9 also decent
+# 26 10 -> 9 also decent
+#17 10 -> 9 decent
+#1, 10 -> 8 not too bad
+#8 10 -> 9 also
+
+### only going up to 100 now
+cur_i <- plot.i
+cur_j <- plot.j
+
+sim_data_path <- here("output", "revisions", "lapl_check", "sim_lapl", "/")
 
 load(paste0(
-  sim_data_path, "/", "sim_model3_",
+  sim_data_path, "/", "sim_model3_fit123_",
   plot.s,
@@
 
-## model2
-#############
+## model2 ####
 gamma_draws <- sim_model3_stan_sim2 %>% 
@@
 
-## Model3
-###
+## Model3 ####
 
 lam0_draws <- sim_model3_stan_sim3 %>% 
-  select(starts_with("gamma"))
+  select(starts_with("lambda0"))
 
 lam1_draws <- sim_model3_stan_sim3 %>% 
-  select(starts_with("zeta"))
+  select(starts_with("lambda1"))
 
@@
 ###
-#############
+### model 3 ####
 mmhp_par_est <- list(
@@
 state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
-  termination = 50 
-  ### TO DO update for longer sims
+                                                 termination = 100
 )
@@
 
-```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4, eval=FALSE}
+```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4, eval=TRUE}
 mmhp_lty <- 1
 
-y.ub <- c(8, 8, 8) # c(130,72,31)
-x_events <- 190 # 135#150
-my.xlim <- 200 # 160#200#130
-my.long.x <- 205 # 205#134.5
-legend.x <- c(100, 100, 100) # c(135,135,135)
+y.ub <- c(5, 5, 5) # c(130,72,31)
+x_events <- 90 # 135#150
+my.xlim <- 100 # 160#200#130
+my.long.x <- 100 # 205#134.5
+legend.x <- c(50, 50, 50) # c(135,135,135)
 legend.y <- # c(34,32,32)
-legend.y <- c(6, 6, 6) # c(15,12,15)#c(62,37,18)#c(22,22,22)
+legend.y <- c(3.5, 3.5, 3.5) # c(15,12,15)#c(62,37,18)#c(22,22,22)
 legend.cex <- 1.5 # 3
@@
 true.object <- object_true
-
 ```
 
-```{r actual-plot, eval=FALSE}
+```{r fig-4b, eval=TRUE}
 layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 2.5), 3))
 par(
-  mar = c(0, 0.3, 0, 0.1), oma = c(0, 3.5, 4, 0),
+  mar = c(0.2, 0.3, 0, 0.1), oma = c(3, 3.5, 4, 2),
   tcl = 0.2, mgp = c(0.5, 0, 0), xpd = TRUE
@@
 ## delta lambda
-par(mar = c(0, 0.3, 0, 0.1))
+par(mar = c(0.1, 0.3, 0, 0.1))
 plot(0, 0,
      xlim = c(0, my.xlim), 
-     ylim = c(-0.5, 4),
+     ylim = c(-1.5, 1.5),
      type = "n",
@@
 delta.lambda <- lambda.m1$lambda.t - lambda.true$lambda.t
+m1_diff <- delta.lambda
 delta.positive <- delta.lambda
@@
 ## location of legend
-legend(legend.x[2] - 95,
-       legend.y[2] + 2, c("State 0/1 events", "State change point"),
+legend(legend.x[2] - 35,
+       legend.y[2] + 1.75, c("State 0/1 events", "State change point"),
        col = c(NA, "red"),
-       y.intersp = 0.85,
+       y.intersp = 0.75,
        x.intersp = -0,
@@
 )
-points(legend.x[2] - 89, legend.y[2], 
+points(legend.x[2] - 33, legend.y[2] + 0.5, 
        pch = 1, cex = 2, col = "blue")
-points(legend.x[2] - 85, legend.y[2],
+points(legend.x[2] - 31, legend.y[2] + 0.5,
        pch = 16, cex = 2, col = "blue")
@@
 ## delta lambda
-par(mar = c(0, 0.3, 0, 0.1))
+par(mar = c(0.1, 0.3, 0, 0.1))
 delta.lambda <- lambda.m2$lambda.t - lambda.true$lambda.t
@@
      xlim = c(0, my.xlim),
-     ylim = c(-0.5, 4), type = "n",
+     ylim = c(-1.5, 1.5), type = "n",
      bty = "n",
@@
 delta.lambda <- lambda.m2$lambda.t - lambda.true$lambda.t
+m2_diff <- delta.lambda
 delta.positive <- delta.lambda
@@
 ########
-par(mar = c(0, 0.3, 1, 0.1))
+par(mar = c(0.1, 0.3, 1, 0.1))
 drawUniMMHPIntensityPaper(true.object,
@@
 )
-legend(legend.x[3] - 2, legend.y[3] + 1, c("True"),
+legend(legend.x[3] - 2, legend.y[3] + 1.75, c("True"),
        col = c("black"),
@@
 
-legend(legend.x[3] + 22, legend.y[3] + 1, "C-MMHP",
+legend(legend.x[3] + 22, legend.y[3] + 1.75, "C-MMHP",
        col = model_colors[3],
        y.intersp = 0.88,
-       x.intersp = .65,
+       x.intersp = .25,
        bty = "n",
@@
 
-legend(legend.x[3] - 95, legend.y[3] + 2,
+legend(legend.x[3] - 45, legend.y[3] + 2.5,
        c("Overestimation", "Underestimation"),
@@
 ## delta lambda
-par(mar = c(0, 0.3, 0, 0.1))
+par(mar = c(0.1, 0.3, 0, 0.1))
 plot(0, 0,
      xlim = c(0, my.xlim), 
-     ylim = c(-0.5, 4), type = "n",
+     ylim = c(-1.5, 1.5), type = "n",
      bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n",
@@
 delta.lambda <- lambda.m3 - lambda.true$lambda.t
+m3_diff <- delta.lambda
 delta.positive <- delta.lambda
@@
 ## top
-mtext(text = "(b)", side = 3, line = 0.8,
+mtext(text = "(b)", side = 3, line = 0.25,
       outer = TRUE, cex = 2.5, font = 2)
 ## bottom
-mtext(text = "Time", side = 1, line = 2,
+mtext(text = "Time", side = 1, line = 1.5,
       outer = TRUE, cex = 2.25)
@@
 
-sim_data_path <- here("output", "revisions", "sim_m3", "sim_2", "/")
+sim_data_path <- here("output", "revisions", "lapl_check", "sim_lapl", "/")
 
@@
 sims <- 1:50
-sims <- sims[c(-18)]
+# sims <- sims[c(-18)]
+sims <- sims[c(-37,-45,-46, -50)]
 
@@
 
-```{r fig-5b-spearman-sim, fig.height=7}
-sim_files <- list.files(here("output", "revisions", "rank_sims/"), 
+```{r fig-5b-spearman-sim, fig.height=5}
+sim_files <- list.files(here("output",
+                             "revisions",
+                             "lapl_check",
+                             "sim_rank/"), 
                         pattern = "rank_sim")
@@
 all_sims <- list()
+
 for (i in seq_along(sim_files)) {
   single_fit <- readRDS(here(
-    "output", "revisions", "rank_sims",
+    "output", "revisions", "lapl_check", "sim_rank",
     sim_files[i]
@@
   ) +
-  ggtitle("(b)")
+  # ggtitle("(b)")
+  NULL
 ```
@@
 # current_cohort <- 5
+# data_path
 
@@
 ```{r fig-6b-overall-rank-correlation}
-load("../output/revisions/weighted_rank_data.RData")
+load("../output/revisions/lapl_check/weighted_rank_data.RData")
 # png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
@@
 
-```{r fig-8a-frob-norm-cohort5, fig.width=8,fig.height=4,eval=TRUE}
-load("../output/revisions/plot_N_predict_revision.RData")
+```{r fig-8a-mae-norm-cohort5, fig.width=8,fig.height=4,eval=TRUE}
+load("../output/revisions/lapl_check/plot_N_predict_revision.RData")
 current_cohort <- 5 # cohort 1 looks worse than rest
@@
 
-```{r fig-7a-pred-all-cohorts-box-mae}
+```{r fig-7a-pred-all-cohorts-box-mae, fig.width=8,fig.height=4,eval=TRUE}
 ### updated to revision
-load("../output/revisions/plot_N_predict_revision.RData")
+load("../output/revisions/lapl_check/plot_N_predict_revision.RData")
 
@@
 ```{r fig-9a-spearman-rank-cohort1, eval=FALSE}
-load(here("output", "plot_rank_predict.RData"))
+load(here("output",
+          "revisions",
+          "lapl_check",
+          "plot_rank_predict.RData"))
 # current_cohort <- 5
@@
 ```{r fig-7b-pred-rank-spearman-all-cohorts}
-load("../output/plot_rank_predict.RData")
+load("../output/revisions/lapl_check/plot_rank_predict.RData")
 
@@
 
+No longer need to run this.
+
 ```{r process for state separation cohort1,eval=FALSE}
@@
                                     clean_data)
+
 unique_pairs_df <- return_df %>%
@@
   )
+
 unique_observe_win <- unique(return_df[,
-                                       c("day", "observe.id", "observe.time")])
+                                       c("day",
+                                         "observe.id",
+                                         "observe.time")])
 
@@
 social_state_day <- array(0, dim = c(21, mice_number, mice_number))
+
 for (cur_day in c(1:21)) {
@@
 
+dsnl_poisson <- cmdstan_model("../lib/dsnl_poisson.stan")
+
 ## utility dsnl
-fit_dsnl_active <- stan("../lib/dsnl_poisson.stan",
+fit_dsnl_active <- dsnl_poisson$sample(
   data = list(
@@
     c = 1,
-    sigma = 0.5
-  ),
-  iter = 1000, chains = 4, control = list(adapt_delta = 0.99)
-)
+    sigma = 1
+  ),
+  iter_sampling = 500,
+  iter_warmup = 500,
+  chains = 4,
+  adapt_delta = 0.95
+)
+
+active_fit <- fit_dsnl_active$draws()
+sim_dsnl_active <- posterior::as_draws_df(active_fit)
+
 print(fit_dsnl_active, pars = c("x"))
@@
 
+Need to update this to read in cmdstan results.
+
 ```{r process data for plot 10b, cache=TRUE}
 library(PlayerRatings)
-# current_cohort <- 5
-current_cohort <- 1
+current_cohort <- 5
+# current_cohort <- 1
 load(paste(data_path, cohort_names[current_cohort],
@@
 
+dsnl_act_sims <- sim_dsnl_active %>% select(starts_with("x"))
+dsnl_act_arr <- array(as.matrix(dsnl_act_sims), dim = c(1000, 21, 12))
+
 ## Utility aggregate
@@
   for (s in c(1:1000)) {
-    temp_result <- cor.test(-sim_dsnl_active$x[s, t, ], cur_real_rank,
+    temp_result <- cor.test(-dsnl_act_arr[s, t, ], cur_real_rank,
                             method = "spearman")
@@
 }
+
+dsnl_inac_sims <- sim_dsnl_inactive %>% select(starts_with("x"))
+dsnl_inac_arr <- array(as.matrix(dsnl_inac_sims), dim = c(1000, 21, 12))
 
@@
   for (s in c(1:1000)) {
-    temp_result <- cor.test(sim_dsnl_inactive$x[s, t, ],
+    temp_result <- cor.test(dsnl_inac_arr[s, t, ],
       cur_real_rank,

### 2021-07-23 run_scripts/agg_rank.R

@@ -101,7 +101,7 @@ fit_agg_rank <- agg_model$sample(
   data = list(n_matrix = clean_data$N_count),
   iter_sampling = 1000,
   chains = 4,
-  thin = 4,
+  # thin = 4,
   adapt_delta = 0.99
 )
 

### 2021-08-04 run_scripts/agg_rank.R
update agg rank to rerun

@@ -101,7 +101,7 @@ fit_agg_rank <- agg_model$sample(
   data = list(n_matrix = clean_data$N_count),
   iter_sampling = 1000,
   chains = 4,
-  # thin = 4,
+  thin = 4,
   adapt_delta = 0.99
 )
 

### 2021-08-04 output_scripts/Paper_Plots.Rmd

@@
   echo = TRUE, fig.path = "paper_figure/revision/",
-  dev = "png", fig.height = 4.5, fig.width = 7,
+  dev = "png", fig.height = 5, fig.width = 7,
   warning = FALSE, cache = TRUE
@@
 
-```{r fig-2a-contour-plot, eval=revision_plots}
+```{r fig-2a-contour-plot, eval=revision_plots, fig.width=6, fig.height=6}
 current_cohort <- 5
@@
 
-```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE, eval=revision_plots}
+```{r fig-2b-diag-plot-c5,echo=FALSE,warning=FALSE, eval=revision_plots, fig.width=6, fig.height=6}
 # current_cohort <- 5
@@
 ks_chp <- ks.stat.matrix
-
+current_cohort <- 6
 ```
@@
 
-```{r fig-3a-baseline-rate, eval=revision_plots}
+```{r fig-3a-baseline-rate, fig.width=5, fig.height=5, eval=revision_plots}
 current_cohort <- 5
+## this looks better
 # current_cohort <- 6 # 3 is maybe ok, 6/7 is interesting
@@
 
-```{r fig-3b-residual-structure, include=TRUE, eval=revision_plots}
+```{r fig-3b-residual-structure, include=TRUE, fig.width=10, fig.height=5, eval=revision_plots}
+### this looks better
 ### now to add Pearson residual matrices here for C-HP and C-DCHP from fig 7
@@
 
-```{r fig3-cohort-response}
+```{r fig3-cohort-response, fig.width=5, fig.height=5}
 current_cohort <- 6
+### this looks good
 
@@
 )
-
+current_cohort <- 5
 ```
@@
       line = 0.6, outer = TRUE, cex = 2.25)
+
+```
+
+## Fig 5 Param Recovery
+
+Confirm parameter recovery for some of the simulation settings, as 
+a potential figure 5a also.
+
+```{r param-recov}
+## param recovery for some lambda0, lambda1, alpha, beta,
+## eta1, eta2, eta3
+model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
+  return(eta1 * x * y * exp(-eta2 * abs(x-y))/(1 + exp(-eta3 *(x-y))))})
+
+model3_fn <- list(alpha.fun = function(x, y, eta1, eta2){
+  return(eta1*x*y*exp(-eta2*abs(x-y)))},
+                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
+                  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
+
+#### Save the simulation parameters ####
+
+object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
+  return(eta1*x*y*exp(-eta2*abs(x-y)))},
+                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
+                  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
+
+num_nodes <- 10
+object_par <- list(sim_lambda_1 = 0.6,
+                   gamma_var = seq(from = 0.01, to = 0.2,
+                                   length.out = num_nodes),
+                   zeta_var = rep(0.1, num_nodes),
+                   sim_eta_1 = 3, # from 3.5
+                   sim_eta_2 = 2,#1.5, # from 2.6
+                   sim_eta_3 = 2.5, # 
+                   #sim_eta_3 = 7.5,
+                   sim_beta = 1.5, # from 2
+                   f_vec_1 = seq(from = 0.2,
+                                 to = 0.9,
+                                 length.out = num_nodes))
+object_matrix <- list(
+  lambda0_matrix = outer(
+    object_par$gamma_var,
+    object_par$zeta_var, "+"
+  ),
+  lambda1_matrix = 1.5*outer(
+    object_par$gamma_var,
+    object_par$zeta_var, "+"
+  ),
+  alpha_matrix = formMatrix(
+    function(x, y) {
+      object_fn$alpha.fun(
+        x, y, object_par$sim_eta_1,
+        object_par$sim_eta_2
+      )
+    },
+    object_par$f_vec_1
+  ),
+  beta_matrix = matrix(object_par$sim_beta,
+    nrow = length(object_par$f_vec_1),
+    ncol = length(object_par$f_vec_1)
+  ),
+  q1_matrix = formMatrix(
+    function(x, y) {
+      object_fn$q1.fun(
+        x, y,
+        object_par$sim_eta_3
+      )
+    },
+    object_par$f_vec_1
+  ),
+  q2_matrix = formMatrix(
+    function(x, y) {
+      object_fn$q0.fun(
+        x, y,
+        object_par$sim_eta_3
+      )
+    },
+    object_par$f_vec_1
+  )
+)
+
+```
+
+```{r process-sims}
+### load in sims, take mean of each parameter from each simulation 
+### setting, add to tibble?
+sim_data_path <- here("output", "revisions", "lapl_check", "sim_lapl", "/")
+
+sim_files <- list.files(here("output",
+                             "revisions",
+                             "lapl_check",
+                             "sim_lapl",
+                             "/"), 
+                        pattern = "sim_model3_fit123_")
+
+par_ests <- tibble()
+
+for(i in seq_along(sim_files)) {
+  load(here(
+    "output",
+    "revisions", 
+    "lapl_check",
+    "sim_lapl",
+    sim_files[i]
+  ))
+  #then get the ests
+  m1_est <- sim_model3_stan_sim1 %>%
+    select(beta, eta_1, eta_2, eta_3) %>% 
+    summarise(across(.cols = everything(), median)) %>%
+    pivot_longer(cols = everything()) %>% 
+    mutate(sim_id = i, model = "C-HP")
+
+  m2_est <- sim_model3_stan_sim2 %>%
+    select(beta, eta_1, eta_2, eta_3,
+           starts_with("gamma"),
+           starts_with("zeta")) %>% 
+    summarise(across(.cols = everything(), median)) %>%
+    pivot_longer(cols = everything()) %>% 
+    mutate(sim_id = i, model = "C-DCHP")
+
+  m3_est <- sim_model3_stan_sim3 %>%
+    select(beta, eta_1, eta_2, eta_3, 
+           starts_with("gamma"),
+           starts_with("zeta")) %>% 
+    summarise(across(.cols = everything(), median)) %>%
+    # rename(w_lambda = r_lambda1) %>% 
+    pivot_longer(cols = everything()) %>% 
+    mutate(sim_id = i, model = "C-MMHP")
+  par_ests <- par_ests %>% bind_rows(m1_est, m2_est, m3_est)
+}
+
+par_ests
+
+true_pars <- tibble(name = c("beta", "eta_1", "eta_2", "eta_3",
+                             paste0("gamma[", 1:10, "]"),
+                             paste0("zeta[", 1:10, "]")),
+                    value = c(1.5, 3, 2, 2.5, seq(from = 0.01, to = 0.2,
+                                   length.out = num_nodes),
+                              rep(0.1, num_nodes)))
+
+par_ests %>% 
+  filter(name %in% c("beta", "eta_1", "eta_2", "eta_3")) %>% 
+  ggplot(aes(model, value)) + geom_boxplot() +
+  geom_hline(data = true_pars %>% 
+               filter(name %in% c("beta", "eta_1", "eta_2", "eta_3")),
+             aes(yintercept = value)) +
+  facet_wrap(vars(name), scales = "free")
+
+par_ests %>% 
+  filter(!name %in% c("beta", "eta_1", "eta_2", "eta_3")) %>% 
+  ggplot(aes(model, value)) + geom_boxplot() +
+  geom_hline(data = true_pars %>%
+               filter(!name %in% c("beta", "eta_1", "eta_2", "eta_3")),
+             aes(yintercept = value)) +
+  facet_wrap(vars(name), scales = "free")
 
@@
   single_fit <- readRDS(here(
-    "output", "revisions", "lapl_check", "sim_rank",
+    "output",
+    "revisions", 
+    "lapl_check",
+    "sim_rank",
     sim_files[i]
@@
 ### Rank Comparison for Single Cohort ####
-# current_cohort <- 5
+current_cohort <- 5
 # data_path
@@
 p2
+```
+
+# Further results on latent ranks
+
+Wish to investigate some further properties of the
+latent states for these animals, in the context of the above latent rank
+plot.
+
+```{r prop-active-inactive, eval=FALSE}
+### think need to run this
+current_cohort <- 6
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+return_df <- cleanObservationPeriod(current_cohort,
+  raw_df =
+    full_data[[cohort_names[current_cohort]]],
+  clean_data
+)
+unique_pairs_df <- return_df %>%
+  group_by(initiator, recipient) %>%
+  dplyr::summarize(
+    count = n(),
+    observe = list(observe.id),
+    observe.length = list(observe.time),
+    no.events = list(no.events)
+  )
+unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])
+
+load(paste(data_path, cohort_names[current_cohort],
+  "/cmmhp_est_zt_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+
+### then look at these pairwise
+length(interpolation_array_list)
+
+dim(interpolation_array_list[[1]][[1]]) # each column here is a simulation
+num_pairs <- length(interpolation_array_list)
+num_winds <- length(interpolation_array_list[[4]])
+
+## 500 for each window
+
+mean_state <- matrix(NA, nrow = num_pairs, ncol = num_winds)
+
+for(i in seq_along(1:num_pairs)) {
+  for(j in seq_along(1:num_winds)) {
+    if(i != 19) { # self directed event, remove
+      curr_mean_vec <- apply(interpolation_array_list[[i]][[j]],
+                                    1, mean)
+      mean_state[i,j] <- mean(curr_mean_vec)
+    }
+  }
+}
+# apply(interpolation_array_list[[i]][[j]], 1, mean)
+# dim(interpolation_array_list[[i]][[j]])
+
+# then just take mean state, multiply by length of the window...
+dim(unique_observe_win)
+
+### this is the expected amount of time in the active state?
+prop_active <- mean_state %*% 
+  unique_observe_win$observe.time# /sum(unique_observe_win$observe.time)
+
+prop_active[is.na(prop_active)] <- 0
+
+pairs_tibble <- unique_pairs_df
+pairs_tibble$prop_active <- prop_active
+
+init_act <- pairs_tibble %>% group_by(initiator) %>% 
+  summarise(mean_active = sum(prop_active)) %>% 
+  arrange(desc(mean_active))
+
+rec_act <- pairs_tibble %>% group_by(recipient) %>% 
+  summarise(mean_active = sum(prop_active)) %>% 
+  arrange(desc(mean_active))
+
+bind_rows(init_act %>% rename(start = initiator),
+          rec_act %>% rename(start = recipient)) %>% 
+  group_by(start) %>% 
+  summarise(total_active = sum(mean_active)) %>% 
+  arrange(total_active)
+
+```
+
+```{r rerun-isi, eval=FALSE}
+num_tries <- 100 
+result <- matrix(NA, nrow = num_tries, ncol = 12)
+for(i in 1:num_tries){
+  print(i)
+  raw_data <- full_data[[cohort_names[current_cohort]]]
+  win_lost_df <- raw_data[-which(raw_data[,
+                                        "Actor"]=="Start"|raw_data[,
+                                                              "Actor"]=="End"),
+                          c("Actor","Recipient")]
+  win_lost_matrix <- get_wl_matrix(win_lost_df)
+  sample
+  # problem is that the initial rank the same the whole time.
+  win_lost_matrix
+  out <- isi98(win_lost_matrix[gtools::permute(1:12), gtools::permute(1:12)])
+  a <- as.numeric(out$best_order)
+
+  result[i, ] <- a
+}
+
+result[ ,12]
+
+```
+
+```{r explore-cohort, eval=FALSE}
+unique_pairs_df %>% 
+  group_by(initiator) %>% 
+  summarise(start = sum(count)) %>% 
+  arrange(start)
+
+unique_pairs_df %>% 
+  group_by(recipient) %>% 
+  summarise(receive = sum(count)) %>% 
+  arrange(receive)
+
+### look at out degree estimates also
+sim_cohort_mmhp %>% 
+  select(starts_with("gamma")) %>% 
+  summarise(across(everything(), mean)) %>% 
+  pivot_longer(everything())
+
+sim_cohort_mmhp %>% 
+  select(starts_with("zeta")) %>% 
+  summarise(across(everything(), mean)) %>% 
+  pivot_longer(everything())
+
+### get sd for each of the 3 models
+
+m1 <- sim_cohort_hp %>% 
+  select(starts_with("f")) %>% 
+  summarise(across(everything(), sd)) %>% 
+  pivot_longer(everything()) %>% 
+  mutate(model = "C-HP")
+
+m2 <- sim_cohort_dchp %>% 
+  select(starts_with("f")) %>% 
+  summarise(across(everything(), sd)) %>% 
+  pivot_longer(everything()) %>% 
+  mutate(model = "C-DCHP")
+
+m3 <- sim_cohort_mmhp %>% 
+  select(starts_with("f")) %>% 
+  summarise(across(everything(), sd)) %>% 
+  pivot_longer(everything()) %>% 
+  mutate(model = "C-MMHP")
+
+bind_rows(m1, m2, m3) %>% 
+  left_join(m3, by = "name") %>% 
+  rename(mmhp_var = value.y, var = value.x) %>% 
+  select(-model.y) %>% 
+  group_by(name) %>%
+  summarise(per_var = var/mmhp_var, model = model.x) %>% 
+  filter(model != "C-MMHP") %>% 
+  # ungroup() %>% 
+  # pull(per_var)
+  mutate(per_var_cmmhp = scales::percent(per_var)) %>% 
+  select(-per_var)
+```
+
+## Further rank information
+
+```{r compute-isi-using-cmmhp-ranking, eval=FALSE}
+f_med <- sim_cohort_mmhp %>% 
+  select(starts_with("f")) %>% 
+  summarise(across(everything(), median)) %>% 
+  pivot_longer(everything())
+
+isi_ord <- order(f_med$value,decreasing = TRUE)
+
+df <- win_lost_df
+df[, 1] <- factor(df[, 1], levels = 1:12)
+df[, 2] <- factor(df[, 2], levels = 1:12)
+df$result <- 1
+m1 <- stats::xtabs(result ~ ., data = df)
+
+result <- isi98(m1[isi_ord,isi_ord])
+```
+
+```{r investigate-bursty, eval=FALSE}
+# inter_8_10 <-
+
+theme_set(theme_minimal())
+
+return_df %>% 
+  filter(initiator == 7) %>% 
+  select(initiator, 
+         recipient,
+         observe.id,
+         observe.start,
+         observe.end,
+         event.times) %>% 
+  unnest_longer(event.times) %>% 
+  group_by(observe.id, initiator) %>% 
+  arrange(event.times, .by_group = TRUE) %>% 
+  mutate(inter = event.times - lag(event.times, default = 0)) %>% 
+  ggplot(aes(inter)) + geom_histogram() +
+  labs(title = "Fights from animal 12")
+
+return_df %>% 
+  filter(recipient == 7) %>% 
+  select(initiator, 
+         recipient,
+         observe.id,
+         observe.start,
+         observe.end,
+         event.times) %>% 
+  unnest_longer(event.times) %>% 
+  group_by(observe.id, initiator) %>% 
+  arrange(event.times, .by_group = TRUE) %>% 
+  mutate(inter = event.times - lag(event.times, default = 0)) %>% 
+  ggplot(aes(inter)) + geom_histogram() +
+  labs(title = "Fights to animal 12")
+
+return_df %>% 
+  filter(initiator %in% c(3) | recipient == 3) %>% 
+  select(initiator, 
+         recipient,
+         observe.id,
+         observe.start,
+         observe.end,
+         event.times) %>% 
+  unnest_longer(event.times) %>% 
+  group_by(observe.id, initiator) %>% 
+  arrange(event.times, .by_group = TRUE) %>% 
+  mutate(inter = event.times - lag(event.times, default = 0)) %>% 
+  ggplot(aes(inter)) + geom_histogram() + 
+  labs(title = "Top Ranked Animals")
+
+```
+
+```{r investigate-animal-12, eval=FALSE}
+### want to try establish what proportion of its fights occur in inactive
+### periods compared to other animals, etc
+cur_node <- 12
+
+pairs <- unique_pairs_df %>% 
+  ungroup() %>% 
+  mutate(index = row_number()) %>% 
+  filter(initiator == cur_node) %>% 
+  select(index, initiator, recipient, observe) %>%
+  # observe gives the window its in
+  # unnest_wider(observe) %>%
+  pull(index)
+
+observe_winds <- unique_pairs_df %>% 
+  ungroup() %>% 
+  mutate(index = row_number()) %>% 
+  filter(initiator == cur_node) %>% 
+  select(index, initiator, recipient, observe)
+
+## need to somehow get the corresponding entries of the matrix 
+## for these
+for(i in seq_along(1:nrow(observe_winds))) {
+  curr_winds <- observe_winds$observe[[i]]
+  print(mean_state[pairs, ][i, curr_winds])
+}
+
+### how do these differ?
+
+###
+### this is the mean state across all observation windows, compared
+### to the mean state for windows where events are observed above
+apply(mean_state[pairs, ], 1, mean)
+
+###  
+act_vec <- mean_state %*% 
+  unique_observe_win$observe.time
+act_vec[pairs] /sum(unique_observe_win$observe.time)
+```
+
+### Explore Latent States
+
+Look at fights from/to a given animal and plot the inferred latent 
+states for each window.
+
+```{r plot-latent-given-animal, eval=FALSE}
+# dim(interpolation_array_list[[1]][[1]])
+# ### pair then window then segment times simulation
+# 
+# interpolation_array_list[[1]][[1]][1 , ] %>% 
+#   map_dbl(., mean)
+# 
+# ### need a function to take a given
+# 
+# ### this is what I want
+# dim(interpolation_array_list[[1]][[1]])
+# apply(interpolation_array_list[[1]][[1]], 1, mean) 
+# # want to do this for each pair
+
+mean_states <- function(df) {
+  return(apply(df, 1, mean))
+}
+
+pair_list <- unique_pairs_df %>% 
+  ungroup() %>% 
+  mutate(index = row_number()) %>% 
+  filter(initiator == 12) %>% 
+  pull(index)
+
+pair_list
+
+num_pairs <- nrow(unique_pairs_df)
+pair_result <- vector(mode = "list", length = num_pairs)
+
+for(i in seq_along(1:num_pairs)) {
+  if(i != 19) {
+    print(i)
+    pair_result[[i]] <- interpolation_array_list[[i]] %>% 
+    map(~mean_states((.x))) %>% 
+    set_names(paste0("window_", 1:34)) %>% 
+    as_tibble()
+  }
+}
+
+pair_result # has for each pair in each element
+saveRDS(pair_result, file = "pair_result.RDS")
+```
+
+Look at the output from this process, plot these, etc.
+
+```{r look-at-pair-result, eval=FALSE}
+pair_result <- readRDS("../pair_result.RDS")
+theme_set(theme_minimal())
+
+### need to get the event times within windows also...
+# return_df %>% 
+#   select(observe.id, initiator, recipient, event.times)
+# 
+# unique_observe_win
+# ## this is everything I need for the plots then...
+# unique_pairs_df %>% 
+#   ungroup() %>% 
+#   mutate(index = row_number()) %>% 
+#   filter(initiator == init & recipient == rec) %>% 
+#   pull(index)
+
+plot_window <- function(init, rec) {
+  res_state_tibb <- tibble()
+  res_event_tibb <- tibble()
+  pair <- unique_pairs_df %>% 
+            ungroup() %>% 
+            mutate(index = row_number()) %>% 
+            filter(initiator == init & recipient == rec) %>% 
+            pull(index)
+  if(length(pair) == 0) {
+    stop("No interactions")
+  }
+  for(window in 1:34) {
+    state_vec <- pair_result[[pair]][, window] 
+    state_vec <- state_vec %>% pull(names(state_vec))
+    length_wind <- unique_observe_win$observe.time[window]
+    init <- unique_pairs_df$initiator[pair]
+    rec <- unique_pairs_df$recipient[pair]
+    events <- return_df %>% 
+      filter(initiator == init) %>% 
+      filter(recipient == rec) %>% 
+      filter(observe.id == window) 
+    if(nrow(events) > 0 ) {
+      event_times <- unlist(events$event.times)
+      event_tibb <- tibble(x = event_times, y = 0, wind = window)
+      res_event_tibb <- res_event_tibb %>% 
+        bind_rows(event_tibb)
+
+      state_tibb <- tibble(x = seq(from = 0,
+                                   to = length_wind,
+                                   length.out = 500),
+                           mean_state = state_vec,
+                           wind = window)
+      res_state_tibb <- res_state_tibb %>% 
+      bind_rows(state_tibb)
+    } 
+  }
+  ### could do a facet wrap by window! 
+  plt <- res_state_tibb %>% 
+  ggplot(aes(x, mean_state)) +
+  geom_line(aes(colour = "Mean State")) +
+  geom_point(data = res_event_tibb, mapping = aes(x,y)) +
+  facet_wrap(~wind, scales = "free_x") +
+  scale_y_continuous(breaks = c(0, 1)) +
+  # scale_x_continuous(breaks = c(1, 2)) +
+  theme(legend.title = element_blank(), axis.text.x = element_blank()) +
+  labs(x = "Time", y = "Latent State",
+       title = paste("From", init, "to", rec))
+  print(plt)
+}
+
+```
+
+We can then look at some of these for some pairs of interest.
+
+```{r from-12, eval=FALSE}
+## make sure correct return_df loaded here
+plot_window(12, 1)
+plot_window(12, 2)
+plot_window(12, 3)
+plot_window(12, 4)
+plot_window(12, 5)
+plot_window(12, 6)
+plot_window(12, 7)
+plot_window(12, 8)
+plot_window(12, 9)
+plot_window(12, 10)
+plot_window(12, 11)
+```
+
+```{r to-animal-12, eval=FALSE}
+# plot_window(1, 12)
+# plot_window(2, 12)
+plot_window(3, 12)
+plot_window(4, 12)
+plot_window(5, 12)
+# plot_window(6, 12)
+# plot_window(7, 12)
+plot_window(8, 12)
+plot_window(9, 12)
+plot_window(10, 12)
+plot_window(11, 12)
+```
+
+Similarly, we can look at the breakdown of events that are classified as
+active as opposed to inactive.
+
+```{r classify-events, eval=FALSE}
+total_event_array <- array(0,
+                           dim = c(mice_number, mice_number,
+                                   max(return_df$observe.id)))
+active_event_array <- array(0,
+                            dim = c(mice_number, mice_number,
+                                    max(return_df$observe.id)))
+
+for (i in 1:mice_number) {
+  for (j in 1:mice_number) {
+    if(i != j) {
+      pair <- which(unique_pairs_df$initiator == i & 
+                      unique_pairs_df$recipient == j)
+      if (length(pair) > 0) {
+        current_window_vec <- unique_pairs_df$observe[[pair]]
+        for (cur_win in current_window_vec) {
+          row_indicator <- (return_df$initiator == i) &
+            (return_df$recipient == j) &
+            (return_df$observe.id == cur_win)
+          total_event_array[i, j, cur_win] <- length(return_df[row_indicator,
+                                                            "event.times"][[1]])
+          active_event_array[i, j, cur_win] <- sum(apply(2 -
+                                           state_array_list[[pair]][[cur_win]],
+                                           1, mean) > 0.5)
+        }
+      }
+    }
+  }
+}
+
+total_matrix <- apply(total_event_array, c(1,2), sum)
+active_matrix <- apply(active_event_array, c(1,2), sum)
+
+inact_matrix <- total_matrix - active_matrix
+
+### compute isi for each
+names(active_matrix) <- 1:12
+colnames(active_matrix) <- 1:12
+rownames(active_matrix) <- 1:12
+isi98(active_matrix)
+
+names(inact_matrix) <- 1:12
+colnames(inact_matrix) <- 1:12
+rownames(inact_matrix) <- 1:12
+isi98(inact_matrix)
 ```
@@
 
-```{r fig-7a-pred-all-cohorts-box-mae, fig.width=8,fig.height=4,eval=TRUE}
+```{r fig-7a-pred-all-cohorts-box-mae,eval=TRUE, fig.width=8, fig.height=4}
 ### updated to revision

### 2021-08-09 output_scripts/investigate_rankings.Rmd
file to investigate the rankings

---
title: "Ranking Stability"
author: "Owen G. Ward"
date: '`r Sys.Date()`'
output:
  html_document:
    # toc: true
    # toc_depth: 2
    # toc_float: true
    number_sections: FALSE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.height = 5, fig.width = 7,
  warning = FALSE, cache = TRUE
)

slides_plots <- FALSE
extra_plots <- FALSE

revision_plots <- TRUE
original_plots <- FALSE
### original plots for plots which are no longer needed, 
### revision plots are what required

current_cohort <- 5

# don't write to this path
data_path <- "../output/revisions/lapl_check/prior_check/"

func_dir <- "../lib/"

library(here)
# library(rstan)
library(cmdstanr)
Sys.setenv(LOCAL_CPPFLAGS = "-march=corei7 -mtune=corei7")
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(posterior)
library(bayesplot)
library(viridis)
library(here)
library(compete)
library(colorspace)
source(paste(func_dir, "naiveRankHierarchy.R", sep = ""))
source(paste(func_dir, "expertRankHierarchy.R", sep = ""))
source(paste(func_dir, "cleanData.R", sep = ""))
source(paste(func_dir, "prepareDataStan.R", sep = ""))
source(paste(func_dir, "inferLatentMmhp.R", sep = ""))
source(paste(func_dir, "plotUtil.R", sep = ""))
source(paste(func_dir, "mmhp.R", sep = ""))
source(paste(func_dir, "uniHawkes.R", sep = ""))
source(paste(func_dir, "simulatePrediction.R", sep = ""))
source(paste(func_dir, "myGlicko.R", sep = ""))
source(paste(func_dir, "matrixPlotParameter.R", sep = ""))
source(paste(func_dir, "residualStructureScore.R", sep = ""))
source(paste(func_dir, "drawIntensity.R", sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

cohort_names <- paste("cohort", c(9, 10, 12, 15, 16, 17, 18, 37, 38, 45),
                      sep = "")
cohort_short_names <- paste("C", c(9, 10, 12, 15, 16, 17, 18, 37, 38, 45),
                            sep = "")
cut_off <- 3
mice_number <- 12
col_df <- tibble(
  method = c(
    "I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
    "C-HP", "C-DCHP", "True", "C-MMHP"
  ),
  cols = viridis(9)
)
theme_set(theme_minimal())
```

```{r load rankings, echo=FALSE, include=FALSE, results='hide', cache=TRUE}
full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
out <- captureOutput(for (curr_cohort in fit_cohorts) {
  naive_rank_10[[curr_cohort]] <-
    naiveRankHierarchy(full_data[[cohort_names[curr_cohort]]])
  expert_rank_10[[curr_cohort]] <-
    expertRankHierarchy(full_data[[cohort_names[curr_cohort]]])
})
```

```{r define_functions, eval=revision_plots, include=FALSE}
model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3) {
  return(eta1 * x * y * exp(-eta2 * abs(x - y)) / (1 +
    exp(-eta3 * (x - y))))
})

model3_fn <- list(
  alpha.fun = function(x, y, eta1, eta2) {
    return(eta1 * x * y * exp(-eta2 * abs(x - y)))
  },
  q1.fun = function(x, y, eta3) {
    return(exp(-eta3 * x))
  },
  q0.fun = function(x, y, eta3) {
    return(exp(-eta3 * y))
  }
)
```

# Ranking and Events

We first modify the priors from the C-MMHP model which leads to
much improved MCMC performance.

We want to look at the relationship between the inferred variability
of the ranking and the number of interactions a given animal is involved in.

We plot the inferred ranks arranged by decreasing number 
of total interactions for all 4 of the comparison models, as in Fig6a.

```{r plot-rank-total-interactions, eval=FALSE}
for(current_cohort in 1:10) {
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
             ))
  total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count)
  f_ranks <- paste("f[", order(total_inter, decreasing = TRUE),
                   "]", sep = "")
  f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>% 
  pivot_longer(everything())
  f_draws$name <- factor(f_draws$name, levels = f_ranks)
  plot_f <- f_draws %>% 
  ggplot(aes(name, value)) +
  geom_boxplot() +
  labs(title = paste("Cohort ", current_cohort, sep = ""),
       subtitle = "Ordered by total interactions")
  print(plot_f)
}
```

```{r all-4-models, warning=FALSE}
for(current_cohort in 1:10) {
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
             ))
  load(paste(data_path, cohort_names[current_cohort],
    "/agg_rank_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_hp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_dchp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count)

  no_method <- 4
  plot_latent_df <- data.frame(
    Methods = rep(1:no_method, each = 1000 * mice_number),
    Mice = rep(rep(1:mice_number, each = 1000), no_method),
    force = rep(0, 1000 * mice_number * no_method)
  )
  ## agg
  x_draws <- sim_agg_rank %>% select(starts_with("x"))
  plot_latent_df$force[(1:(1000 * mice_number))] <-
    as.vector(as.matrix(x_draws))

  ## M1
  f_draws <- sim_cohort_hp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) +
                         1000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  ## M2
  f_draws <- sim_cohort_dchp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) + 
                         2000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  ## M3
  f_draws <- sim_cohort_mmhp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) + 
                         3000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  plot_latent_df$Mice <- factor(plot_latent_df$Mice,
    levels = order(total_inter, decreasing = TRUE)
  )
  plot_latent_df$Method <- factor(plot_latent_df$Method,
    labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP")
  )
  plot_cols <- col_df %>%
  filter(method %in% c(
    "AggRank", "C-HP",
    "C-DCHP", "C-MMHP"
  )) %>%
  pull(cols)

  p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
    geom_boxplot(alpha = 0.7) +
    scale_fill_manual(values = plot_cols) +
    ggtitle("(a)") +
    theme_bw() +
    theme(
      plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
      text = element_text(size = 20),
      axis.text.x = element_text(size = 10),
      legend.position = "none"
    ) +
    facet_grid(cols = vars(Method)) +
    xlab("Mice (ranked by total interactions)") +
    ylab("Latent rank") + 
    labs(title = paste("Cohort ", current_cohort, sep = ""))
  print(p1)
}

```

Similarly, here are the corresponding plots with the animals ranked by 
I&SI score instead.

```{r isi-ranks, warning=FALSE, eval=FALSE}
for(current_cohort in 1:10) {
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
             ))
  total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count)
  f_ranks <- paste("f[", expert_rank_10[[current_cohort]],
                   "]", sep = "")
  f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>% 
  pivot_longer(everything())
  f_draws$name <- factor(f_draws$name, levels = f_ranks)
  plot_f <- f_draws %>% 
  ggplot(aes(name, value)) +
  geom_boxplot() +
  labs(title = paste("Cohort ", current_cohort, sep = ""),
       subtitle = "Ordered by I&SI score")
  print(plot_f)
}

```

```{r ranked-by-isi}
for(current_cohort in 1:10) {
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
             ))
  load(paste(data_path, cohort_names[current_cohort],
    "/agg_rank_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_hp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_dchp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count)

  no_method <- 4
  plot_latent_df <- data.frame(
    Methods = rep(1:no_method, each = 1000 * mice_number),
    Mice = rep(rep(1:mice_number, each = 1000), no_method),
    force = rep(0, 1000 * mice_number * no_method)
  )
  ## agg
  x_draws <- sim_agg_rank %>% select(starts_with("x"))
  plot_latent_df$force[(1:(1000 * mice_number))] <-
    as.vector(as.matrix(x_draws))

  ## M1
  f_draws <- sim_cohort_hp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) +
                         1000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  ## M2
  f_draws <- sim_cohort_dchp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) + 
                         2000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  ## M3
  f_draws <- sim_cohort_mmhp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) + 
                         3000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  plot_latent_df$Mice <- factor(plot_latent_df$Mice,
    levels = expert_rank_10[[current_cohort]]
  )
  plot_latent_df$Method <- factor(plot_latent_df$Method,
    labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP")
  )
  plot_cols <- col_df %>%
  filter(method %in% c(
    "AggRank", "C-HP",
    "C-DCHP", "C-MMHP"
  )) %>%
  pull(cols)

  p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
    geom_boxplot(alpha = 0.7) +
    scale_fill_manual(values = plot_cols) +
    ggtitle("(a)") +
    theme_bw() +
    theme(
      plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
      text = element_text(size = 20),
      axis.text.x = element_text(size = 10),
      legend.position = "none"
    ) +
    facet_grid(cols = vars(Method)) +
    xlab("Mice (ranked by I&SI)") +
    ylab("Latent rank") + 
    labs(title = paste("Cohort ", current_cohort, sep = ""))
  print(p1)
}

```

Cohort 3 win loss

```{r c3-win-loss}
current_cohort <- 3
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])

clean_data$N_count

load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
             ))

gamma_draws <- sim_cohort_mmhp %>% 
  select(starts_with("gamma")) %>% 
  pivot_longer(everything())

gamma_draws$name <- factor(gamma_draws$name, 
                           levels = paste("gamma[", 1:12, "]", sep = ""))

gamma_draws %>% 
  ggplot(aes(name, value)) + 
  geom_boxplot()

zeta_draws <- sim_cohort_mmhp %>% 
  select(starts_with("zeta")) %>% 
  pivot_longer(everything())

zeta_draws$name <- factor(zeta_draws$name, 
                           levels = paste("zeta[", 1:12, "]", sep = ""))

zeta_draws %>% 
  ggplot(aes(name, value)) + 
  geom_boxplot()

f_draws <- sim_cohort_mmhp %>% 
  select(starts_with("f")) %>% 
  pivot_longer(everything()) %>% 
  group_by(name) %>% 
  summarise(med = median(value)) %>% 
  arrange(-med)

f_draws %>% pull(name)

cmmhp_ranks <- c(10, 12, 7, 6, 3, 8, 2, 4, 1, 9, 11, 5)
clean_data$N_count[cmmhp_ranks, cmmhp_ranks]

c3_count <- clean_data$N_count
names(c3_count) <- 1:12
rownames(c3_count) <- 1:12
colnames(c3_count) <- 1:12
isi98(c3_count)
isi98(c3_count[cmmhp_ranks, cmmhp_ranks])
```

## Plot Omega Lambda and f draws

```{r plot-omega-lambda, message=FALSE}
for(current_cohort in 1:10) {
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
             ))
  fit_draws <- as_draws_array(sim_cohort_mmhp)
  plot1 <- mcmc_hist(fit_draws, pars = "w_lambda") +
    labs(paste("Cohort ", current_cohort, sep = ""))
  print(plot1)
}
```

# Compare rankings with/without eta_3

```{r plot-rankings-both-models, message=FALSE}
# data_path
other_data_path <- "../output/revisions/lapl_check/ident_check/"

for(current_cohort in 1:10) {
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
             ))
  sim1 <- sim_cohort_mmhp
  load(paste(other_data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
             ))
  sim2 <- sim_cohort_mmhp

  all_data <- sim1 %>%
    select(starts_with("f")) %>% 
    pivot_longer(everything()) %>% 
    mutate(model = "with eta3") %>% 
    bind_rows(sim2 %>% select(starts_with("f")) %>% 
                pivot_longer(everything()) %>% 
                mutate(model = "without"))
  all_data$model <- factor(all_data$model)
  comp_plot <- ggplot(all_data, aes(name, value, fill = model)) +
    geom_boxplot() +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "Removing eta3",
         y = "Latent Rankings")
  print(comp_plot)

  all_data %>% group_by(name, model) %>% 
    summarise(model_mean = mean(value), 
              model_sd = sd(value))

  ## same for gamma,
  all_data <- sim1 %>%
    select(contains("eta") | starts_with("w_lam")) %>% 
    pivot_longer(everything()) %>% 
    mutate(model = "with eta1") %>% 
    bind_rows(sim2 %>% select(contains("eta") | starts_with("w_lam")) %>% 
                pivot_longer(everything()) %>% 
                mutate(model = "without"))
  all_data$model <- factor(all_data$model)
  comp_plot <- ggplot(all_data, aes(name, value, fill = model)) +
    geom_boxplot() +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "Comparison removing eta3", y = "Other params") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  print(comp_plot)

  ###
  all_data <- sim1 %>%
    select(starts_with("gamma")) %>% 
    pivot_longer(everything()) %>% 
    mutate(model = "with eta3") %>% 
    bind_rows(sim2 %>% select(starts_with("gamma")) %>% 
                pivot_longer(everything()) %>% 
                mutate(model = "without"))
  all_data$model <- factor(all_data$model)
  comp_plot <- ggplot(all_data, aes(name, value, fill = model)) +
    geom_boxplot() +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "Comparison removing eta3", y = "Out Degree") +
  print(comp_plot)

}

```

# Compare rankings with/without eta_1

```{r plot-rankings-both-models, message=FALSE}
# data_path
other_data_path <- "../output/revisions/lapl_check/ident_check_no_eta1/"

for(current_cohort in 1:10) {
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
             ))
  sim1 <- sim_cohort_mmhp
  load(paste(other_data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
             ))
  sim2 <- sim_cohort_mmhp

  all_data <- sim1 %>%
    select(starts_with("f")) %>% 
    pivot_longer(everything()) %>% 
    mutate(model = "with eta1") %>% 
    bind_rows(sim2 %>% select(starts_with("f")) %>% 
                pivot_longer(everything()) %>% 
                mutate(model = "without"))
  all_data$model <- factor(all_data$model)
  comp_plot <- ggplot(all_data, aes(name, value, fill = model)) +
    geom_boxplot() +
    labs("Rankings across models")
  print(comp_plot)

  all_data %>% group_by(name, model) %>% 
    summarise(model_mean = mean(value), 
              model_sd = sd(value))

  ## same for gamma,
  all_data <- sim1 %>%
    select(contains("eta") | starts_with("w_lam")) %>% 
    pivot_longer(everything()) %>% 
    mutate(model = "with eta1") %>% 
    bind_rows(sim2 %>% select(contains("eta") | starts_with("w_lam")) %>% 
                pivot_longer(everything()) %>% 
                mutate(model = "without"))
  all_data$model <- factor(all_data$model)
  comp_plot <- ggplot(all_data, aes(name, value, fill = model)) +
    geom_boxplot() +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "Comparison removing eta1", y = "Eta params") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  print(comp_plot)

  ###
  all_data <- sim1 %>%
    select(starts_with("gamma")) %>% 
    pivot_longer(everything()) %>% 
    mutate(model = "with eta1") %>% 
    bind_rows(sim2 %>% select(starts_with("gamma")) %>% 
                pivot_longer(everything()) %>% 
                mutate(model = "without"))
  all_data$model <- factor(all_data$model)
  comp_plot <- ggplot(all_data, aes(name, value, fill = model)) +
    geom_boxplot() +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "Comparison removing eta1", y = "Out Degree")
  print(comp_plot)

}

```

# Other Paper plots

```{r fig-3b}
current_cohort <- 5

m1_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
  "/chp_pr_matrix_", cohort_names[current_cohort],
  ".RDS",
  sep = ""
))

m2_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
  "/dchp_pr_matrix_", cohort_names[current_cohort],
  ".RDS",
  sep = ""
))

m3_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
  "/cmmhp_pr_matrix_", cohort_names[current_cohort],
  ".RDS",
  sep = ""
))

indep_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
  "/immhp_pr_matrix_", cohort_names[current_cohort],
  ".RDS",
  sep = ""
))

matrix_lst_plot <- list(
  m1_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ],
  m2_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ]
  ,
  m3_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ],
  indep_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ]
)
# cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(
  X = matrix_lst_plot, no_matrix = 4, n_row = 2,
  xLabels = expert_rank_10[[current_cohort]],
  yLabels = rev(expert_rank_10[[current_cohort]]),
  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
  colorPalette = "RdBu", if.emp = FALSE,
  # legend.mar=c(0.5,.5,0.5,0.5),
  title_lst = list("C-HP", "C-DCHP", "C-MMHP", "I-MMHP"),
  # title_lst = list("I-MMHP"),
  col_axis = c(-80, -40, 0, 40, 80), 
  fake_matrix = FALSE,
  matrix.mar = c(2.5, 2.5, 2.5, 1)
)
mtext(text = "(b)",
      side = 3,
      line = 0.5,
      outer = TRUE,
      cex = 2.5,
      font = 2)

```

```{r fig-7a}
load("../output/revisions/lapl_check/prior_check/plot_N_predict_revision.RData")
current_cohort <- 5 # cohort 1 looks worse than rest

temp_plot_df <- predict_day_mae_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
  labels = c("I-MMHP", "DSNL", "C-HP", "C-DCHP", "C-MMHP")
)
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
# width=600,height=300)

plot_cols_pred <- col_df %>%
  filter(method %in% levels(temp_plot_df$method)) %>%
  arrange(factor(method, levels = c(
    "I-MMHP", "DSNL",
    "C-HP", "C-DCHP", "C-MMHP"
  ))) %>%
  pull(cols)

p3 <- temp_plot_df %>%
  rowwise() %>%
  # mutate(norm = min(norm,60)) %>%
  # rename(Method = method) %>%
  ggplot(aes(x = method, y = mae, fill = method)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(a)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  facet_grid(cols = vars(day)) +
  xlab("Prediction horizon (day)") +
  ylab("MAE") +
  ylim(0, 5) + # aren't infinite but >150 and <200
  NULL
p3 + labs(fill = "Method", title = "Single Cohort")

```
```{r fig-7b}
load("../output/revisions/lapl_check/prior_check/plot_N_predict_revision.RData")

all_cohort_box <- all_cohort_mae_df

all_cohort_box$method <- factor(all_cohort_box$method,
  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
  labels = c(
    "I-MMHP", "DSNL",
    "C-HP", "C-DCHP",
    "C-MMHP"
  )
)
all_cohort_box$day <- factor(all_cohort_box$day)

plot_cols_pred <- col_df %>%
  filter(method %in% levels(all_cohort_box$method)) %>%
  arrange(factor(method, levels = c(
    "I-MMHP", "DSNL",
    "C-HP", "C-DCHP", "C-MMHP"
  ))) %>%
  pull(cols)

all_cohort_box %>%
  ggplot(aes(x = method, y = norm, fill = method)) +
  # facet_grid(cols = vars(day)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(a)") +
  theme_bw() +
  theme(
    plot.title = element_text(
      size = 22,
      hjust = 0.5, face = "bold"
    ),
    text = element_text(size = 20),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  facet_grid(cols = vars(day)) +
  # guides(color=guide_legend(title="Method")) +
  xlab("Prediction horizon (day)") +
  ylab("MAE") +
  labs(fill = "Method") +
  # ylim(0, 80) +
  NULL

```

# Look at the inferred latent states

```{r process-cohort}
current_cohort <- 3

clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort,
  raw_df =
    full_data[[cohort_names[current_cohort]]],
  clean_data
)
unique_pairs_df <- return_df %>%
  group_by(initiator, recipient) %>%
  dplyr::summarize(
    count = n(),
    observe = list(observe.id),
    observe.length = list(observe.time),
    no.events = list(no.events)
  )
unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])

mean_states <- function(df) {
  return(apply(df, 1, mean))
}

load(paste(data_path, cohort_names[current_cohort],
  "/cmmhp_est_zt_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))

num_pairs <- nrow(unique_pairs_df)
pair_result <- vector(mode = "list", length = num_pairs)

for(i in seq_along(1:num_pairs)) {
  # if(i != 19) {
    # print(i)
    pair_result[[i]] <- interpolation_array_list[[i]] %>%
    map(~mean_states((.x))) %>%
    set_names(paste0("window_", 1:nrow(unique_observe_win))) %>%
    as_tibble()
  # }
}

rm(interpolation_array_list)

```

```{r plot-function}
plot_window <- function(init, rec, unique_observe_win, pair_result) {
  res_state_tibb <- tibble()
  res_event_tibb <- tibble()
  pair <- unique_pairs_df %>%
            ungroup() %>%
            mutate(index = row_number()) %>%
            filter(initiator == init & recipient == rec) %>%
            pull(index)
  if(length(pair) == 0) {
    stop("No interactions")
  }
  for(window in 1:nrow(unique_observe_win)) {
    state_vec <- pair_result[[pair]][, window]
    state_vec <- state_vec %>% pull(names(state_vec))
    length_wind <- unique_observe_win$observe.time[window]
    init <- unique_pairs_df$initiator[pair]
    rec <- unique_pairs_df$recipient[pair]
    events <- return_df %>%
      filter(initiator == init) %>%
      filter(recipient == rec) %>%
      filter(observe.id == window)
    if(nrow(events) > 0 ) {
      event_times <- unlist(events$event.times)
      event_tibb <- tibble(x = event_times, y = 0, wind = window)
      res_event_tibb <- res_event_tibb %>%
        bind_rows(event_tibb)

      state_tibb <- tibble(x = seq(from = 0,
                                   to = length_wind,
                                   length.out = 500),
                           mean_state = state_vec,
                           wind = window)
      res_state_tibb <- res_state_tibb %>%
      bind_rows(state_tibb)
    }
  }
  ### could do a facet wrap by window!
  plt <- res_state_tibb %>%
  ggplot(aes(x, mean_state)) +
  geom_line(aes(colour = "Mean State")) +
  geom_point(data = res_event_tibb, mapping = aes(x,y)) +
  facet_wrap(~wind, scales = "free_x") +
  scale_y_continuous(breaks = c(0, 1)) +
  ylim(c(0,1)) +
  # scale_x_continuous(breaks = c(1, 2)) +
  theme(legend.title = element_blank(), axis.text.x = element_blank()) +
  labs(x = "Time", y = "Latent State",
       title = paste("From", init, "to", rec))
  print(plt)
}

```

Then we can plot some pairs from this cohort.

```{r plot-from-5, message=FALSE}
plot_window(5, 1, unique_observe_win, pair_result)
plot_window(5, 2, unique_observe_win, pair_result)
plot_window(5, 3, unique_observe_win, pair_result)
plot_window(5, 4, unique_observe_win, pair_result)
plot_window(5, 6, unique_observe_win, pair_result)
plot_window(5, 7, unique_observe_win, pair_result)
plot_window(5, 8, unique_observe_win, pair_result)
plot_window(5, 9, unique_observe_win, pair_result)
plot_window(5, 10, unique_observe_win, pair_result)
plot_window(5, 11, unique_observe_win, pair_result)
plot_window(5, 12, unique_observe_win, pair_result)
```

```{r to-5}
# plot_window(1, 5, unique_observe_win, pair_result)
plot_window(2, 5, unique_observe_win, pair_result)
plot_window(3, 5, unique_observe_win, pair_result)
plot_window(4, 5, unique_observe_win, pair_result)
plot_window(6, 5, unique_observe_win, pair_result)
plot_window(7, 5, unique_observe_win, pair_result)
plot_window(8, 5, unique_observe_win, pair_result)
# plot_window(9, 5, unique_observe_win, pair_result)
plot_window(10, 5, unique_observe_win, pair_result)
# plot_window(11, 5, unique_observe_win, pair_result)
# plot_window(12, 5, unique_observe_win, pair_result)
```

<!-- ```{r from-12, eval=FALSE} -->
<!-- ## make sure correct return_df loaded here -->
<!-- plot_window(8, 1) -->
<!-- plot_window(8, 2) -->
<!-- plot_window(8, 3) -->
<!-- plot_window(8, 4) -->
<!-- plot_window(8, 5) -->
<!-- plot_window(8, 6) -->
<!-- plot_window(8, 7) -->
<!-- # plot_window(8, 8) -->
<!-- plot_window(8, 9) -->
<!-- plot_window(8, 10) -->
<!-- plot_window(8, 11) -->
<!-- plot_window(8, 12) -->
<!-- ``` -->

<!-- ```{r to-animal-12, eval=FALSE} -->
<!-- # # plot_window(1, 12) -->
<!-- # # plot_window(2, 12) -->
<!-- # plot_window(3, 12) -->
<!-- # plot_window(4, 12) -->
<!-- # plot_window(5, 12) -->
<!-- # # plot_window(6, 12) -->
<!-- # # plot_window(7, 12) -->
<!-- # plot_window(8, 12) -->
<!-- # plot_window(9, 12) -->
<!-- # plot_window(10, 12) -->
<!-- # plot_window(11, 12) -->

<!-- plot_window(2, 9, unique_observe_win) -->
<!-- plot_window(2, 7, unique_observe_win) -->
<!-- plot_window(2, 8, unique_observe_win) -->
<!-- plot_window(7, 8, unique_observe_win) -->
<!-- ``` -->

<!-- ## Active/Inactive -->

<!-- ```{r compute-active-in, eval=FALSE} -->
<!-- current_cohort <- 6 -->
<!-- load(paste(data_path, cohort_names[current_cohort], -->
<!--   "/cmmhp_est_zt_", cohort_names[current_cohort], -->
<!--   ".RData", -->
<!--   sep = "" -->
<!-- )) -->

<!-- total_event_array <- array(0, -->
<!--                            dim = c(mice_number, mice_number, -->
<!--                                    max(return_df$observe.id))) -->
<!-- active_event_array <- array(0, -->
<!--                             dim = c(mice_number, mice_number, -->
<!--                                     max(return_df$observe.id))) -->

<!-- for (i in 1:mice_number) { -->
<!--   for (j in 1:mice_number) { -->
<!--     if(i != j) { -->
<!--       pair <- which(unique_pairs_df$initiator == i &  -->
<!--                       unique_pairs_df$recipient == j) -->
<!--       if (length(pair) > 0) { -->
<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
<!--         for (cur_win in current_window_vec) { -->
<!--           row_indicator <- (return_df$initiator == i) & -->
<!--             (return_df$recipient == j) & -->
<!--             (return_df$observe.id == cur_win) -->
<!--           total_event_array[i, j, cur_win] <- length(return_df[row_indicator, -->
<!--                                                             "event.times"][[1]]) -->
<!--           active_event_array[i, j, cur_win] <- sum(apply(2 - -->
<!--                                            state_array_list[[pair]][[cur_win]], -->
<!--                                            1, mean) > 0.5) -->
<!--         } -->
<!--       } -->
<!--     } -->
<!--   } -->
<!-- } -->

<!-- total_matrix <- apply(total_event_array, c(1,2), sum) -->
<!-- active_matrix <- apply(active_event_array, c(1,2), sum) -->

<!-- inact_matrix <- total_matrix - active_matrix -->

<!-- rm(interpolation_array_list) -->

<!-- ``` -->

<!-- ## Variance of f for no fights -->

<!-- ```{r var-f, eval=FALSE} -->
<!-- data_path <- "../output/revisions/lapl_check/" -->
<!-- current_cohort <- 6 -->
<!-- ## good for 4,8,9 -->
<!-- ## ok for 2 -->
<!-- ## bad for 1, 10 -->
<!-- load(paste(data_path, cohort_names[current_cohort], -->
<!--   "/cohort_mmhp_stan_result_", cohort_names[current_cohort], -->
<!--   ".RData", -->
<!--   sep = "" -->
<!-- )) -->

<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!-- return_df <- cleanObservationPeriod(current_cohort, -->
<!--       raw_df = full_data[[cohort_names[current_cohort]]], -->
<!--       clean_data) -->
<!-- sim_cohort_mmhp -->

<!-- sim_cohort_mmhp %>% select(starts_with("f")) %>%  -->
<!--   pivot_longer(everything()) %>%  -->
<!--   ggplot(aes(name, value)) + -->
<!--   geom_boxplot() -->

<!-- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->

<!-- sim_cohort_mmhp %>% select(starts_with("f")) %>%  -->
<!--   pivot_longer(everything()) %>%  -->
<!--   group_by(name) %>%  -->
<!--   summarise(sd = sd(value)) %>%  -->
<!--   arrange(desc(sd)) %>%  -->
<!--   print(n = 12) -->

<!-- ``` -->

<!-- ```{r investigate-stan-fits, eval=FALSE} -->
<!-- ## rerunning with ensuring that delta is not fixed. -->
<!-- pri_data_path <- "../output/revisions/lapl_check/prior/" -->
<!-- current_cohort <- 9 -->
<!-- ## good for 4,8,9 -->
<!-- ## ok for 2 -->
<!-- ## bad for 1, 10 -->
<!-- load(paste(pri_data_path, cohort_names[current_cohort], -->
<!--   "/cohort_mmhp_stan_result_", cohort_names[current_cohort], -->
<!--   ".RData", -->
<!--   sep = "" -->
<!-- )) -->

<!-- hist(sim_cohort_mmhp$w_lambda) -->
<!-- # table(sim_cohort_mmhp$w_lambda) -->

<!-- ### convert to "draws" object, compute rhats -->
<!-- fit_draws <- as_draws_array(sim_cohort_mmhp) -->

<!-- mcmc_trace(fit_draws, pars = c("w_lambda", "beta", "gamma[1]")) -->

<!-- rhat(fit_draws[ , ,"f[1]"]) -->

<!-- rhat_fit <- apply(fit_draws, 3, rhat) -->
<!-- summary(rhat_fit) -->
<!-- ``` -->

<!-- ### What is difference between cohort 4 and 5/6 -->

<!-- ```{r cohort-stats, eval=FALSE} -->
<!-- clean_data_2 <- cleanData(full_data[[cohort_names[2]]]) -->
<!-- clean_data_4 <- cleanData(full_data[[cohort_names[4]]]) -->
<!-- clean_data_6 <- cleanData(full_data[[cohort_names[6]]]) -->
<!-- clean_data_1 <- cleanData(full_data[[cohort_names[1]]]) -->
<!-- clean_data_10 <- cleanData(full_data[[cohort_names[10]]]) -->
<!-- ``` -->

<!-- ```{r, message=FALSE, eval=FALSE} -->
<!-- for(current_cohort in 1:10) { -->
<!--   print(current_cohort) -->
<!--    clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!--     return_df <- cleanObservationPeriod(current_cohort, -->
<!--       raw_df = -->
<!--         full_data[[cohort_names[current_cohort]]], -->
<!--       clean_data -->
<!--     ) -->
<!--     print(sum(clean_data$N_count)) -->
<!--     unique_pairs_df <- return_df %>% -->
<!--       group_by(initiator, recipient) %>% -->
<!--       dplyr::summarize( -->
<!--         count = n(), -->
<!--         observe = list(observe.id), -->
<!--         observe.length = list(observe.time), -->
<!--         no.events = list(no.events) -->
<!--       ) -->
<!--     unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")]) -->
<!--     print(nrow(unique_observe_win)) -->
<!--     print(sum(unique_observe_win$observe.time)) -->
<!--     print(summary(unique_pairs_df$count)) -->
<!--     cat("-------\n") -->
<!-- } -->
<!-- ``` -->

<!-- ## Bayesplot -->

<!-- ```{r specific-cohort, eval=FALSE} -->
<!-- current_cohort <- 4 -->
<!-- load(paste(pri_data_path, cohort_names[current_cohort], -->
<!--   "/cohort_mmhp_stan_result_", cohort_names[current_cohort], -->
<!--   ".RData", -->
<!--   sep = "" -->
<!-- )) -->

<!-- fit_draws <- as_draws_array(sim_cohort_mmhp) -->
<!-- ``` -->

<!-- ```{r, eval=FALSE} -->
<!-- mcmc_pairs(fit_draws, pars = c("eta_1", "eta_2", "eta_3", "beta")) -->

<!-- mcmc_trace(fit_draws, pars = c("eta_1", "eta_2", "eta_3", "beta")) -->

<!-- mcmc_pairs(fit_draws, pars = c("beta", "eta_3"),  -->
<!--              diag_fun = "dens", off_diag_fun = "hex", -->
<!--              condition = pairs_condition(chains = list(2, c(1,3,4)))) -->

<!-- ``` -->

<!-- ## Check Priors -->

<!-- ```{r normal-priors, eval=FALSE} -->

<!-- pri_data_path <- "../output/revisions/lapl_check/prior_check/" -->

<!-- for(current_cohort in 1:10) { -->
<!--   print(current_cohort) -->
<!--   load(paste(pri_data_path, cohort_names[current_cohort], -->
<!--   "/cohort_mmhp_stan_result_", cohort_names[current_cohort], -->
<!--   ".RData", -->
<!--   sep = "" -->
<!--   )) -->
<!--   fit_draws <- as_draws_array(sim_cohort_mmhp) -->
<!--   rhat_fit <- apply(fit_draws, 3, posterior::rhat) -->
<!--   print(summary(rhat_fit)) -->
<!--   print(mcmc_trace(fit_draws,  -->
<!--              pars = c("eta_1", "eta_2", "eta_3", "beta"))) -->
<!--   cat("-----\n") -->
<!-- } -->

<!-- mcmc_pairs(fit_draws, pars = c("eta_1", "eta_2", "eta_3", "beta")) -->

<!-- ``` -->

<!-- ## check rankings against isi score this data -->

<!-- ```{r label, eval=FALSE} -->
<!-- for(current_cohort in 1:10) { -->
<!--   print(current_cohort) -->
<!--   load(paste(pri_data_path, cohort_names[current_cohort], -->
<!--   "/cohort_mmhp_stan_result_", cohort_names[current_cohort], -->
<!--   ".RData", -->
<!--   sep = "" -->
<!--   )) -->
<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!--   fit_draws <- as_draws_array(sim_cohort_mmhp) -->
<!--   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>%  -->
<!--   pivot_longer(everything()) -->
<!--   f_draws$name <- factor(f_draws$name, levels = paste("f[", -->
<!--                                       expert_rank_10[[current_cohort]], -->
<!--                                       "]", sep = "")) -->
<!--   f_draws %>%  -->
<!--   ggplot(aes(name, value)) + -->
<!--   geom_boxplot() -->

<!--   rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->

<!--   sim_cohort_mmhp %>% select(starts_with("f")) %>%  -->
<!--     pivot_longer(everything()) %>%  -->
<!--     group_by(name) %>%  -->
<!--     summarise(sd = sd(value)) %>%  -->
<!--     arrange(desc(sd)) %>%  -->
<!--     print(n = 12) -->

<!--   cat("-----\n") -->
<!-- } -->
<!-- ``` -->

### 2021-08-10 output_scripts/Paper_Plots.Rmd
rerun all paper plots with half normal prior results for c-mmhp models

@@
 # don't write to this path
-data_path <- "../output/revisions/lapl_check/"
+data_path <- "../output/revisions/lapl_check/prior_check/"
 
@@
 for (s in sims) {
-  print(s)
+  # print(s)
   load(paste0(sim_data_path, "sim_model3_fit123_", s, ".RData"))
@@
 
-```{r log-p-value}
+```{r log-p-value, eval=FALSE}
 cols_plot <- col_df %>% 
@@
 current_cohort <- 5
+# want to update this now
 # data_path
@@
 ## Figure 9a: Predicted Spearman rank for single cohort
-
-This has not finished for new simulation setting yet.
 

### 2021-08-10 output_scripts/Paper_Plots.Rmd
formatting and tidying up results a bit

@@
   dev = "png", fig.height = 5, fig.width = 7,
-  warning = FALSE, cache = TRUE
+  warning = FALSE, cache = FALSE
 )

### 2021-08-10 output_scripts/investigate_rankings.Rmd
formatting and tidying up results a bit

@@
 
+# Interevents vs rankings
+
+```{r interevents, message=FALSE}
+for(current_cohort in 1:10) {
+  cat(paste("Cohort ", current_cohort, "\n", sep = ""))
+  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+  stan_input_lst <- prepareDataStan(current_cohort)
+
+  pair_events <- apply(stan_input_lst$Nm, 1, sum)
+
+  pair_matrix <- matrix(0, nrow = 12, ncol = 12)
+  for(i in seq_along(pair_events)) {
+    i_ind <- stan_input_lst$I_fit[i]
+    j_ind <- stan_input_lst$J_fit[i]
+    pair_matrix[i_ind, j_ind] <- pair_events[i]
+  }
+  # pair_matrix <- clean_data$N_count[expert_rank_10[[current_cohort]],
+  #                                   expert_rank_10[[current_cohort]]]
+  pair_matrix <- pair_matrix[expert_rank_10[[current_cohort]],
+                    expert_rank_10[[current_cohort]]]
+  colnames(pair_matrix) <- expert_rank_10[[current_cohort]]
+  rownames(pair_matrix) <- expert_rank_10[[current_cohort]]
+  print(pair_matrix)
+  cat("=====\n")
+
+}
+```
+
 # Ranking and Events
@@
 
-```{r all-4-models, warning=FALSE}
-for(current_cohort in 1:10) {
-  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-  load(paste(data_path,
-             cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",
-             cohort_names[current_cohort],
-             ".RData",
-             sep = ""
-             ))
-  load(paste(data_path, cohort_names[current_cohort],
-    "/agg_rank_stan_result_", cohort_names[current_cohort],
-    ".RData",
-    sep = ""
-  ))
-  load(paste(data_path, cohort_names[current_cohort],
-    "/cohort_hp_stan_result_", cohort_names[current_cohort],
-    ".RData",
-    sep = ""
-  ))
-  load(paste(data_path, cohort_names[current_cohort],
-    "/cohort_dchp_stan_result_", cohort_names[current_cohort],
-    ".RData",
-    sep = ""
-  ))
-  total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count)
-
-  no_method <- 4
-  plot_latent_df <- data.frame(
-    Methods = rep(1:no_method, each = 1000 * mice_number),
-    Mice = rep(rep(1:mice_number, each = 1000), no_method),
-    force = rep(0, 1000 * mice_number * no_method)
-  )
-  ## agg
-  x_draws <- sim_agg_rank %>% select(starts_with("x"))
-  plot_latent_df$force[(1:(1000 * mice_number))] <-
-    as.vector(as.matrix(x_draws))
-
-  ## M1
-  f_draws <- sim_cohort_hp %>% select(starts_with("f"))
-  plot_latent_df$force[(1:(1000 * mice_number)) +
-                         1000 * mice_number] <-
-    as.vector(as.matrix(f_draws))
-
-  ## M2
-  f_draws <- sim_cohort_dchp %>% select(starts_with("f"))
-  plot_latent_df$force[(1:(1000 * mice_number)) + 
-                         2000 * mice_number] <-
-    as.vector(as.matrix(f_draws))
-
-  ## M3
-  f_draws <- sim_cohort_mmhp %>% select(starts_with("f"))
-  plot_latent_df$force[(1:(1000 * mice_number)) + 
-                         3000 * mice_number] <-
-    as.vector(as.matrix(f_draws))
-
-  plot_latent_df$Mice <- factor(plot_latent_df$Mice,
-    levels = order(total_inter, decreasing = TRUE)
-  )
-  plot_latent_df$Method <- factor(plot_latent_df$Method,
-    labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP")
-  )
-  plot_cols <- col_df %>%
-  filter(method %in% c(
-    "AggRank", "C-HP",
-    "C-DCHP", "C-MMHP"
-  )) %>%
-  pull(cols)
-
-  p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
-    geom_boxplot(alpha = 0.7) +
-    scale_fill_manual(values = plot_cols) +
-    ggtitle("(a)") +
-    theme_bw() +
-    theme(
-      plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
-      text = element_text(size = 20),
-      axis.text.x = element_text(size = 10),
-      legend.position = "none"
-    ) +
-    facet_grid(cols = vars(Method)) +
-    xlab("Mice (ranked by total interactions)") +
-    ylab("Latent rank") + 
-    labs(title = paste("Cohort ", current_cohort, sep = ""))
-  print(p1)
-}
-
-```
-
-Similarly, here are the corresponding plots with the animals ranked by 
-I&SI score instead.
-
-```{r isi-ranks, warning=FALSE, eval=FALSE}
-for(current_cohort in 1:10) {
-  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-  load(paste(data_path,
-             cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",
-             cohort_names[current_cohort],
-             ".RData",
-             sep = ""
-             ))
-  total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count)
-  f_ranks <- paste("f[", expert_rank_10[[current_cohort]],
-                   "]", sep = "")
-  f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>% 
-  pivot_longer(everything())
-  f_draws$name <- factor(f_draws$name, levels = f_ranks)
-  plot_f <- f_draws %>% 
-  ggplot(aes(name, value)) +
-  geom_boxplot() +
-  labs(title = paste("Cohort ", current_cohort, sep = ""),
-       subtitle = "Ordered by I&SI score")
-  print(plot_f)
-}
-
-```
-
-```{r ranked-by-isi}
-for(current_cohort in 1:10) {
-  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-  load(paste(data_path,
-             cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",
-             cohort_names[current_cohort],
-             ".RData",
-             sep = ""
-             ))
-  load(paste(data_path, cohort_names[current_cohort],
-    "/agg_rank_stan_result_", cohort_names[current_cohort],
-    ".RData",
-    sep = ""
-  ))
-  load(paste(data_path, cohort_names[current_cohort],
-    "/cohort_hp_stan_result_", cohort_names[current_cohort],
-    ".RData",
-    sep = ""
-  ))
-  load(paste(data_path, cohort_names[current_cohort],
-    "/cohort_dchp_stan_result_", cohort_names[current_cohort],
-    ".RData",
-    sep = ""
-  ))
-  total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count)
-
-  no_method <- 4
-  plot_latent_df <- data.frame(
-    Methods = rep(1:no_method, each = 1000 * mice_number),
-    Mice = rep(rep(1:mice_number, each = 1000), no_method),
-    force = rep(0, 1000 * mice_number * no_method)
-  )
-  ## agg
-  x_draws <- sim_agg_rank %>% select(starts_with("x"))
-  plot_latent_df$force[(1:(1000 * mice_number))] <-
-    as.vector(as.matrix(x_draws))
-
-  ## M1
-  f_draws <- sim_cohort_hp %>% select(starts_with("f"))
-  plot_latent_df$force[(1:(1000 * mice_number)) +
-                         1000 * mice_number] <-
-    as.vector(as.matrix(f_draws))
-
-  ## M2
-  f_draws <- sim_cohort_dchp %>% select(starts_with("f"))
-  plot_latent_df$force[(1:(1000 * mice_number)) + 
-                         2000 * mice_number] <-
-    as.vector(as.matrix(f_draws))
-
-  ## M3
-  f_draws <- sim_cohort_mmhp %>% select(starts_with("f"))
-  plot_latent_df$force[(1:(1000 * mice_number)) + 
-                         3000 * mice_number] <-
-    as.vector(as.matrix(f_draws))
-
-  plot_latent_df$Mice <- factor(plot_latent_df$Mice,
-    levels = expert_rank_10[[current_cohort]]
-  )
-  plot_latent_df$Method <- factor(plot_latent_df$Method,
-    labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP")
-  )
-  plot_cols <- col_df %>%
-  filter(method %in% c(
-    "AggRank", "C-HP",
-    "C-DCHP", "C-MMHP"
-  )) %>%
-  pull(cols)
-
-  p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
-    geom_boxplot(alpha = 0.7) +
-    scale_fill_manual(values = plot_cols) +
-    ggtitle("(a)") +
-    theme_bw() +
-    theme(
-      plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
-      text = element_text(size = 20),
-      axis.text.x = element_text(size = 10),
-      legend.position = "none"
-    ) +
-    facet_grid(cols = vars(Method)) +
-    xlab("Mice (ranked by I&SI)") +
-    ylab("Latent rank") + 
-    labs(title = paste("Cohort ", current_cohort, sep = ""))
-  print(p1)
-}
-
-```
-
-Cohort 3 win loss
-
-```{r c3-win-loss}
-current_cohort <- 3
-clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-
-clean_data$N_count
-
-load(paste(data_path,
-             cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",
-             cohort_names[current_cohort],
-             ".RData",
-             sep = ""
-             ))
-
-gamma_draws <- sim_cohort_mmhp %>% 
-  select(starts_with("gamma")) %>% 
-  pivot_longer(everything())
-
-gamma_draws$name <- factor(gamma_draws$name, 
-                           levels = paste("gamma[", 1:12, "]", sep = ""))
-
-gamma_draws %>% 
-  ggplot(aes(name, value)) + 
-  geom_boxplot()
-
-zeta_draws <- sim_cohort_mmhp %>% 
-  select(starts_with("zeta")) %>% 
-  pivot_longer(everything())
-
-zeta_draws$name <- factor(zeta_draws$name, 
-                           levels = paste("zeta[", 1:12, "]", sep = ""))
-
-zeta_draws %>% 
-  ggplot(aes(name, value)) + 
-  geom_boxplot()
-
-f_draws <- sim_cohort_mmhp %>% 
-  select(starts_with("f")) %>% 
-  pivot_longer(everything()) %>% 
-  group_by(name) %>% 
-  summarise(med = median(value)) %>% 
-  arrange(-med)
-
-f_draws %>% pull(name)
-
-cmmhp_ranks <- c(10, 12, 7, 6, 3, 8, 2, 4, 1, 9, 11, 5)
-clean_data$N_count[cmmhp_ranks, cmmhp_ranks]
-
-c3_count <- clean_data$N_count
-names(c3_count) <- 1:12
-rownames(c3_count) <- 1:12
-colnames(c3_count) <- 1:12
-isi98(c3_count)
-isi98(c3_count[cmmhp_ranks, cmmhp_ranks])
-```
-
-## Plot Omega Lambda and f draws
-
-```{r plot-omega-lambda, message=FALSE}
-for(current_cohort in 1:10) {
-  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-  load(paste(data_path,
-             cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",
-             cohort_names[current_cohort],
-             ".RData",
-             sep = ""
-             ))
-  fit_draws <- as_draws_array(sim_cohort_mmhp)
-  plot1 <- mcmc_hist(fit_draws, pars = "w_lambda") +
-    labs(paste("Cohort ", current_cohort, sep = ""))
-  print(plot1)
-}
-```
-
-# Compare rankings with/without eta_3
-
-```{r plot-rankings-both-models, message=FALSE}
-# data_path
-other_data_path <- "../output/revisions/lapl_check/ident_check/"
-
-for(current_cohort in 1:10) {
-  load(paste(data_path,
-             cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",
-             cohort_names[current_cohort],
-             ".RData",
-             sep = ""
-             ))
-  sim1 <- sim_cohort_mmhp
-  load(paste(other_data_path,
-             cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",
-             cohort_names[current_cohort],
-             ".RData",
-             sep = ""
-             ))
-  sim2 <- sim_cohort_mmhp
-
-  all_data <- sim1 %>%
-    select(starts_with("f")) %>% 
-    pivot_longer(everything()) %>% 
-    mutate(model = "with eta3") %>% 
-    bind_rows(sim2 %>% select(starts_with("f")) %>% 
-                pivot_longer(everything()) %>% 
-                mutate(model = "without"))
-  all_data$model <- factor(all_data$model)
-  comp_plot <- ggplot(all_data, aes(name, value, fill = model)) +
-    geom_boxplot() +
-    labs(title = paste("Cohort ", current_cohort, sep = ""),
-         subtitle = "Removing eta3",
-         y = "Latent Rankings")
-  print(comp_plot)
-
-  all_data %>% group_by(name, model) %>% 
-    summarise(model_mean = mean(value), 
-              model_sd = sd(value))
-
-  ## same for gamma,
-  all_data <- sim1 %>%
-    select(contains("eta") | starts_with("w_lam")) %>% 
-    pivot_longer(everything()) %>% 
-    mutate(model = "with eta1") %>% 
-    bind_rows(sim2 %>% select(contains("eta") | starts_with("w_lam")) %>% 
-                pivot_longer(everything()) %>% 
-                mutate(model = "without"))
-  all_data$model <- factor(all_data$model)
-  comp_plot <- ggplot(all_data, aes(name, value, fill = model)) +
-    geom_boxplot() +
-    labs(title = paste("Cohort ", current_cohort, sep = ""),
-         subtitle = "Comparison removing eta3", y = "Other params") +
-    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
-  print(comp_plot)
-
-  ###
-  all_data <- sim1 %>%
-    select(starts_with("gamma")) %>% 
-    pivot_longer(everything()) %>% 
-    mutate(model = "with eta3") %>% 
-    bind_rows(sim2 %>% select(starts_with("gamma")) %>% 
-                pivot_longer(everything()) %>% 
-                mutate(model = "without"))
-  all_data$model <- factor(all_data$model)
-  comp_plot <- ggplot(all_data, aes(name, value, fill = model)) +
-    geom_boxplot() +
-    labs(title = paste("Cohort ", current_cohort, sep = ""),
-         subtitle = "Comparison removing eta3", y = "Out Degree") +
-  print(comp_plot)
-
-}
-
-```
-
-# Compare rankings with/without eta_1
-
-```{r plot-rankings-both-models, message=FALSE}
-# data_path
-other_data_path <- "../output/revisions/lapl_check/ident_check_no_eta1/"
-
-for(current_cohort in 1:10) {
-  load(paste(data_path,
-             cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",
-             cohort_names[current_cohort],
-             ".RData",
-             sep = ""
-             ))
-  sim1 <- sim_cohort_mmhp
-  load(paste(other_data_path,
-             cohort_names[current_cohort],
-             "/cohort_mmhp_stan_result_",
-             cohort_names[current_cohort],
-             ".RData",
-             sep = ""
-             ))
-  sim2 <- sim_cohort_mmhp
-
-  all_data <- sim1 %>%
-    select(starts_with("f")) %>% 
-    pivot_longer(everything()) %>% 
-    mutate(model = "with eta1") %>% 
-    bind_rows(sim2 %>% select(starts_with("f")) %>% 
-                pivot_longer(everything()) %>% 
-                mutate(model = "without"))
-  all_data$model <- factor(all_data$model)
-  comp_plot <- ggplot(all_data, aes(name, value, fill = model)) +
-    geom_boxplot() +
-    labs("Rankings across models")
-  print(comp_plot)
-
-  all_data %>% group_by(name, model) %>% 
-    summarise(model_mean = mean(value), 
-              model_sd = sd(value))
-
-  ## same for gamma,
-  all_data <- sim1 %>%
-    select(contains("eta") | starts_with("w_lam")) %>% 
-    pivot_longer(everything()) %>% 
-    mutate(model = "with eta1") %>% 
-    bind_rows(sim2 %>% select(contains("eta") | starts_with("w_lam")) %>% 
-                pivot_longer(everything()) %>% 
-                mutate(model = "without"))
-  all_data$model <- factor(all_data$model)
-  comp_plot <- ggplot(all_data, aes(name, value, fill = model)) +
-    geom_boxplot() +
-    labs(title = paste("Cohort ", current_cohort, sep = ""),
-         subtitle = "Comparison removing eta1", y = "Eta params") +
-    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
-  print(comp_plot)
-
-  ###
-  all_data <- sim1 %>%
-    select(starts_with("gamma")) %>% 
-    pivot_longer(everything()) %>% 
-    mutate(model = "with eta1") %>% 
-    bind_rows(sim2 %>% select(starts_with("gamma")) %>% 
-                pivot_longer(everything()) %>% 
-                mutate(model = "without"))
-  all_data$model <- factor(all_data$model)
-  comp_plot <- ggplot(all_data, aes(name, value, fill = model)) +
-    geom_boxplot() +
-    labs(title = paste("Cohort ", current_cohort, sep = ""),
-         subtitle = "Comparison removing eta1", y = "Out Degree")
-  print(comp_plot)
-
-}
-
-```
-
-# Other Paper plots
-
-```{r fig-3b}
-current_cohort <- 5
-
-m1_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
-  "/chp_pr_matrix_", cohort_names[current_cohort],
-  ".RDS",
-  sep = ""
-))
-
-m2_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
-  "/dchp_pr_matrix_", cohort_names[current_cohort],
-  ".RDS",
-  sep = ""
-))
-
-m3_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
-  "/cmmhp_pr_matrix_", cohort_names[current_cohort],
-  ".RDS",
-  sep = ""
-))
-
-indep_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
-  "/immhp_pr_matrix_", cohort_names[current_cohort],
-  ".RDS",
-  sep = ""
-))
-
-matrix_lst_plot <- list(
-  m1_pr[
-    rev(expert_rank_10[[current_cohort]]),
-    expert_rank_10[[current_cohort]]
-  ],
-  m2_pr[
-    rev(expert_rank_10[[current_cohort]]),
-    expert_rank_10[[current_cohort]]
-  ]
-  ,
-  m3_pr[
-    rev(expert_rank_10[[current_cohort]]),
-    expert_rank_10[[current_cohort]]
-  ],
-  indep_pr[
-    rev(expert_rank_10[[current_cohort]]),
-    expert_rank_10[[current_cohort]]
-  ]
-)
-# cat("Cohort ",current_cohort,"\n",sep="")
-myMultiMatrixPlot(
-  X = matrix_lst_plot, no_matrix = 4, n_row = 2,
-  xLabels = expert_rank_10[[current_cohort]],
-  yLabels = rev(expert_rank_10[[current_cohort]]),
-  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
-  colorPalette = "RdBu", if.emp = FALSE,
-  # legend.mar=c(0.5,.5,0.5,0.5),
-  title_lst = list("C-HP", "C-DCHP", "C-MMHP", "I-MMHP"),
-  # title_lst = list("I-MMHP"),
-  col_axis = c(-80, -40, 0, 40, 80), 
-  fake_matrix = FALSE,
-  matrix.mar = c(2.5, 2.5, 2.5, 1)
-)
-mtext(text = "(b)",
-      side = 3,
-      line = 0.5,
-      outer = TRUE,
-      cex = 2.5,
-      font = 2)
-
-```
-
-```{r fig-7a}
-load("../output/revisions/lapl_check/prior_check/plot_N_predict_revision.RData")
-current_cohort <- 5 # cohort 1 looks worse than rest
-
-temp_plot_df <- predict_day_mae_df_lst[[current_cohort]]
-temp_plot_df$method <- factor(temp_plot_df$method,
-  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
-  labels = c("I-MMHP", "DSNL", "C-HP", "C-DCHP", "C-MMHP")
-)
-temp_plot_df$day <- factor(temp_plot_df$day)
-# png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
-# width=600,height=300)
-
-plot_cols_pred <- col_df %>%
-  filter(method %in% levels(temp_plot_df$method)) %>%
-  arrange(factor(method, levels = c(
-    "I-MMHP", "DSNL",
-    "C-HP", "C-DCHP", "C-MMHP"
-  ))) %>%
-  pull(cols)
-
-p3 <- temp_plot_df %>%
-  rowwise() %>%
-  # mutate(norm = min(norm,60)) %>%
-  # rename(Method = method) %>%
-  ggplot(aes(x = method, y = mae, fill = method)) +
-  geom_boxplot(alpha = 0.7) +
-  scale_fill_manual(values = plot_cols_pred) +
-  ggtitle("(a)") +
-  theme_bw() +
-  theme(
-    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
-    text = element_text(size = 20),
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank(),
-    legend.position = "right"
-  ) +
-  facet_grid(cols = vars(day)) +
-  xlab("Prediction horizon (day)") +
-  ylab("MAE") +
-  ylim(0, 5) + # aren't infinite but >150 and <200
-  NULL
-p3 + labs(fill = "Method", title = "Single Cohort")
-
-```
-```{r fig-7b}
-load("../output/revisions/lapl_check/prior_check/plot_N_predict_revision.RData")
-
-all_cohort_box <- all_cohort_mae_df
-
-all_cohort_box$method <- factor(all_cohort_box$method,
-  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
-  labels = c(
-    "I-MMHP", "DSNL",
-    "C-HP", "C-DCHP",
-    "C-MMHP"
-  )
-)
-all_cohort_box$day <- factor(all_cohort_box$day)
-
-plot_cols_pred <- col_df %>%
-  filter(method %in% levels(all_cohort_box$method)) %>%
-  arrange(factor(method, levels = c(
-    "I-MMHP", "DSNL",
-    "C-HP", "C-DCHP", "C-MMHP"
-  ))) %>%
-  pull(cols)
-
-all_cohort_box %>%
-  ggplot(aes(x = method, y = norm, fill = method)) +
-  # facet_grid(cols = vars(day)) +
-  geom_boxplot(alpha = 0.7) +
-  scale_fill_manual(values = plot_cols_pred) +
-  ggtitle("(a)") +
-  theme_bw() +
-  theme(
-    plot.title = element_text(
-      size = 22,
-      hjust = 0.5, face = "bold"
-    ),
-    text = element_text(size = 20),
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank(),
-    legend.position = "right"
-  ) +
-  facet_grid(cols = vars(day)) +
-  # guides(color=guide_legend(title="Method")) +
-  xlab("Prediction horizon (day)") +
-  ylab("MAE") +
-  labs(fill = "Method") +
-  # ylim(0, 80) +
-  NULL
-
-```
-
-# Look at the inferred latent states
-
-```{r process-cohort}
-current_cohort <- 3
-
-clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-return_df <- cleanObservationPeriod(current_cohort,
-  raw_df =
-    full_data[[cohort_names[current_cohort]]],
-  clean_data
-)
-unique_pairs_df <- return_df %>%
-  group_by(initiator, recipient) %>%
-  dplyr::summarize(
-    count = n(),
-    observe = list(observe.id),
-    observe.length = list(observe.time),
-    no.events = list(no.events)
-  )
-unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])
-
-mean_states <- function(df) {
-  return(apply(df, 1, mean))
-}
-
-load(paste(data_path, cohort_names[current_cohort],
-  "/cmmhp_est_zt_", cohort_names[current_cohort],
-  ".RData",
-  sep = ""
-))
-
-num_pairs <- nrow(unique_pairs_df)
-pair_result <- vector(mode = "list", length = num_pairs)
-
-for(i in seq_along(1:num_pairs)) {
-  # if(i != 19) {
-    # print(i)
-    pair_result[[i]] <- interpolation_array_list[[i]] %>%
-    map(~mean_states((.x))) %>%
-    set_names(paste0("window_", 1:nrow(unique_observe_win))) %>%
-    as_tibble()
-  # }
-}
-
-rm(interpolation_array_list)
-
-```
-
-```{r plot-function}
-plot_window <- function(init, rec, unique_observe_win, pair_result) {
-  res_state_tibb <- tibble()
-  res_event_tibb <- tibble()
-  pair <- unique_pairs_df %>%
-            ungroup() %>%
-            mutate(index = row_number()) %>%
-            filter(initiator == init & recipient == rec) %>%
-            pull(index)
-  if(length(pair) == 0) {
-    stop("No interactions")
-  }
-  for(window in 1:nrow(unique_observe_win)) {
-    state_vec <- pair_result[[pair]][, window]
-    state_vec <- state_vec %>% pull(names(state_vec))
-    length_wind <- unique_observe_win$observe.time[window]
-    init <- unique_pairs_df$initiator[pair]
-    rec <- unique_pairs_df$recipient[pair]
-    events <- return_df %>%
-      filter(initiator == init) %>%
-      filter(recipient == rec) %>%
-      filter(observe.id == window)
-    if(nrow(events) > 0 ) {
-      event_times <- unlist(events$event.times)
-      event_tibb <- tibble(x = event_times, y = 0, wind = window)
-      res_event_tibb <- res_event_tibb %>%
-        bind_rows(event_tibb)
-
-      state_tibb <- tibble(x = seq(from = 0,
-                                   to = length_wind,
-                                   length.out = 500),
-                           mean_state = state_vec,
-                           wind = window)
-      res_state_tibb <- res_state_tibb %>%
-      bind_rows(state_tibb)
-    }
-  }
-  ### could do a facet wrap by window!
-  plt <- res_state_tibb %>%
-  ggplot(aes(x, mean_state)) +
-  geom_line(aes(colour = "Mean State")) +
-  geom_point(data = res_event_tibb, mapping = aes(x,y)) +
-  facet_wrap(~wind, scales = "free_x") +
-  scale_y_continuous(breaks = c(0, 1)) +
-  ylim(c(0,1)) +
-  # scale_x_continuous(breaks = c(1, 2)) +
-  theme(legend.title = element_blank(), axis.text.x = element_blank()) +
-  labs(x = "Time", y = "Latent State",
-       title = paste("From", init, "to", rec))
-  print(plt)
-}
-
-```
-
-Then we can plot some pairs from this cohort.
-
-```{r plot-from-5, message=FALSE}
-plot_window(5, 1, unique_observe_win, pair_result)
-plot_window(5, 2, unique_observe_win, pair_result)
-plot_window(5, 3, unique_observe_win, pair_result)
-plot_window(5, 4, unique_observe_win, pair_result)
-plot_window(5, 6, unique_observe_win, pair_result)
-plot_window(5, 7, unique_observe_win, pair_result)
-plot_window(5, 8, unique_observe_win, pair_result)
-plot_window(5, 9, unique_observe_win, pair_result)
-plot_window(5, 10, unique_observe_win, pair_result)
-plot_window(5, 11, unique_observe_win, pair_result)
-plot_window(5, 12, unique_observe_win, pair_result)
-```
-
-```{r to-5}
-# plot_window(1, 5, unique_observe_win, pair_result)
-plot_window(2, 5, unique_observe_win, pair_result)
-plot_window(3, 5, unique_observe_win, pair_result)
-plot_window(4, 5, unique_observe_win, pair_result)
-plot_window(6, 5, unique_observe_win, pair_result)
-plot_window(7, 5, unique_observe_win, pair_result)
-plot_window(8, 5, unique_observe_win, pair_result)
-# plot_window(9, 5, unique_observe_win, pair_result)
-plot_window(10, 5, unique_observe_win, pair_result)
-# plot_window(11, 5, unique_observe_win, pair_result)
-# plot_window(12, 5, unique_observe_win, pair_result)
-```
-
-<!-- ```{r from-12, eval=FALSE} -->
-<!-- ## make sure correct return_df loaded here -->
-<!-- plot_window(8, 1) -->
-<!-- plot_window(8, 2) -->
-<!-- plot_window(8, 3) -->
-<!-- plot_window(8, 4) -->
-<!-- plot_window(8, 5) -->
-<!-- plot_window(8, 6) -->
-<!-- plot_window(8, 7) -->
-<!-- # plot_window(8, 8) -->
-<!-- plot_window(8, 9) -->
-<!-- plot_window(8, 10) -->
-<!-- plot_window(8, 11) -->
-<!-- plot_window(8, 12) -->
-<!-- ``` -->
-
-<!-- ```{r to-animal-12, eval=FALSE} -->
-<!-- # # plot_window(1, 12) -->
-<!-- # # plot_window(2, 12) -->
-<!-- # plot_window(3, 12) -->
-<!-- # plot_window(4, 12) -->
-<!-- # plot_window(5, 12) -->
-<!-- # # plot_window(6, 12) -->
-<!-- # # plot_window(7, 12) -->
-<!-- # plot_window(8, 12) -->
-<!-- # plot_window(9, 12) -->
-<!-- # plot_window(10, 12) -->
-<!-- # plot_window(11, 12) -->
-
-<!-- plot_window(2, 9, unique_observe_win) -->
-<!-- plot_window(2, 7, unique_observe_win) -->
-<!-- plot_window(2, 8, unique_observe_win) -->
-<!-- plot_window(7, 8, unique_observe_win) -->
-<!-- ``` -->
-
-<!-- ## Active/Inactive -->
-
-<!-- ```{r compute-active-in, eval=FALSE} -->
-<!-- current_cohort <- 6 -->
+<!-- ```{r all-4-models, warning=FALSE} -->
+<!-- for(current_cohort in 1:10) { -->
+<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
+<!--   load(paste(data_path, -->
+<!--              cohort_names[current_cohort], -->
+<!--              "/cohort_mmhp_stan_result_", -->
+<!--              cohort_names[current_cohort], -->
+<!--              ".RData", -->
+<!--              sep = "" -->
+<!--              )) -->
 <!--   load(paste(data_path, cohort_names[current_cohort], -->
-<!--   "/cmmhp_est_zt_", cohort_names[current_cohort], -->
-<!--   ".RData", -->
-<!--   sep = "" -->
-<!-- )) -->
-
-<!-- total_event_array <- array(0, -->
-<!--                            dim = c(mice_number, mice_number, -->
-<!--                                    max(return_df$observe.id))) -->
-<!-- active_event_array <- array(0, -->
-<!--                             dim = c(mice_number, mice_number, -->
-<!--                                     max(return_df$observe.id))) -->
-
-<!-- for (i in 1:mice_number) { -->
-<!--   for (j in 1:mice_number) { -->
-<!--     if(i != j) { -->
-<!--       pair <- which(unique_pairs_df$initiator == i &  -->
-<!--                       unique_pairs_df$recipient == j) -->
-<!--       if (length(pair) > 0) { -->
-<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
-<!--         for (cur_win in current_window_vec) { -->
-<!--           row_indicator <- (return_df$initiator == i) & -->
-<!--             (return_df$recipient == j) & -->
-<!--             (return_df$observe.id == cur_win) -->
-<!--           total_event_array[i, j, cur_win] <- length(return_df[row_indicator, -->
-<!--                                                             "event.times"][[1]]) -->
-<!--           active_event_array[i, j, cur_win] <- sum(apply(2 - -->
-<!--                                            state_array_list[[pair]][[cur_win]], -->
-<!--                                            1, mean) > 0.5) -->
+<!--     "/agg_rank_stan_result_", cohort_names[current_cohort], -->
+<!--     ".RData", -->
+<!--     sep = "" -->
+<!--   )) -->
+<!--   load(paste(data_path, cohort_names[current_cohort], -->
+<!--     "/cohort_hp_stan_result_", cohort_names[current_cohort], -->
+<!--     ".RData", -->
+<!--     sep = "" -->
+<!--   )) -->
+<!--   load(paste(data_path, cohort_names[current_cohort], -->
+<!--     "/cohort_dchp_stan_result_", cohort_names[current_cohort], -->
+<!--     ".RData", -->
+<!--     sep = "" -->
+<!--   )) -->
+<!--   total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
+
+<!--   no_method <- 4 -->
+<!--   plot_latent_df <- data.frame( -->
+<!--     Methods = rep(1:no_method, each = 1000 * mice_number), -->
+<!--     Mice = rep(rep(1:mice_number, each = 1000), no_method), -->
+<!--     force = rep(0, 1000 * mice_number * no_method) -->
+<!--   ) -->
+<!--   ## agg -->
+<!--   x_draws <- sim_agg_rank %>% select(starts_with("x")) -->
+<!--   plot_latent_df$force[(1:(1000 * mice_number))] <- -->
+<!--     as.vector(as.matrix(x_draws)) -->
+
+<!--   ## M1 -->
+<!--   f_draws <- sim_cohort_hp %>% select(starts_with("f")) -->
+<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
+<!--                          1000 * mice_number] <- -->
+<!--     as.vector(as.matrix(f_draws)) -->
+
+<!--   ## M2 -->
+<!--   f_draws <- sim_cohort_dchp %>% select(starts_with("f")) -->
+<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
+<!--                          2000 * mice_number] <- -->
+<!--     as.vector(as.matrix(f_draws)) -->
+
+<!--   ## M3 -->
+<!--   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) -->
+<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
+<!--                          3000 * mice_number] <- -->
+<!--     as.vector(as.matrix(f_draws)) -->
+
+<!--   plot_latent_df$Mice <- factor(plot_latent_df$Mice, -->
+<!--     levels = order(total_inter, decreasing = TRUE) -->
+<!--   ) -->
+<!--   plot_latent_df$Method <- factor(plot_latent_df$Method, -->
+<!--     labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP") -->
+<!--   ) -->
+<!--   plot_cols <- col_df %>% -->
+<!--   filter(method %in% c( -->
+<!--     "AggRank", "C-HP", -->
+<!--     "C-DCHP", "C-MMHP" -->
+<!--   )) %>% -->
+<!--   pull(cols) -->
+
+<!--   p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) + -->
+<!--     geom_boxplot(alpha = 0.7) + -->
+<!--     scale_fill_manual(values = plot_cols) + -->
+<!--     ggtitle("(a)") + -->
+<!--     theme_bw() + -->
+<!--     theme( -->
+<!--       plot.title = element_text(size = 22, hjust = 0.5, face = "bold"), -->
+<!--       text = element_text(size = 20), -->
+<!--       axis.text.x = element_text(size = 10), -->
+<!--       legend.position = "none" -->
+<!--     ) + -->
+<!--     facet_grid(cols = vars(Method)) + -->
+<!--     xlab("Mice (ranked by total interactions)") + -->
+<!--     ylab("Latent rank") + -->
+<!--     labs(title = paste("Cohort ", current_cohort, sep = "")) -->
+<!--   print(p1) -->
 <!-- } -->
+
+<!-- ``` -->
+
+<!-- Similarly, here are the corresponding plots with the animals ranked by -->
+<!-- I&SI score instead. -->
+
+<!-- ```{r isi-ranks, warning=FALSE, eval=FALSE} -->
+<!-- for(current_cohort in 1:10) { -->
+<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
+<!--   load(paste(data_path, -->
+<!--              cohort_names[current_cohort], -->
+<!--              "/cohort_mmhp_stan_result_", -->
+<!--              cohort_names[current_cohort], -->
+<!--              ".RData", -->
+<!--              sep = "" -->
+<!--              )) -->
+<!--   total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
+<!--   f_ranks <- paste("f[", expert_rank_10[[current_cohort]], -->
+<!--                    "]", sep = "") -->
+<!--   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>% -->
+<!--   pivot_longer(everything()) -->
+<!--   f_draws$name <- factor(f_draws$name, levels = f_ranks) -->
+<!--   plot_f <- f_draws %>% -->
+<!--   ggplot(aes(name, value)) + -->
+<!--   geom_boxplot() + -->
+<!--   labs(title = paste("Cohort ", current_cohort, sep = ""), -->
+<!--        subtitle = "Ordered by I&SI score") -->
+<!--   print(plot_f) -->
 <!-- } -->
+
+<!-- ``` -->
+
+<!-- ```{r ranked-by-isi} -->
+<!-- for(current_cohort in 1:10) { -->
+<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
+<!--   load(paste(data_path, -->
+<!--              cohort_names[current_cohort], -->
+<!--              "/cohort_mmhp_stan_result_", -->
+<!--              cohort_names[current_cohort], -->
+<!--              ".RData", -->
+<!--              sep = "" -->
+<!--              )) -->
+<!--   load(paste(data_path, cohort_names[current_cohort], -->
+<!--     "/agg_rank_stan_result_", cohort_names[current_cohort], -->
+<!--     ".RData", -->
+<!--     sep = "" -->
+<!--   )) -->
+<!--   load(paste(data_path, cohort_names[current_cohort], -->
+<!--     "/cohort_hp_stan_result_", cohort_names[current_cohort], -->
+<!--     ".RData", -->
+<!--     sep = "" -->
+<!--   )) -->
+<!--   load(paste(data_path, cohort_names[current_cohort], -->
+<!--     "/cohort_dchp_stan_result_", cohort_names[current_cohort], -->
+<!--     ".RData", -->
+<!--     sep = "" -->
+<!--   )) -->
+<!--   total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
+
+<!--   no_method <- 4 -->
+<!--   plot_latent_df <- data.frame( -->
+<!--     Methods = rep(1:no_method, each = 1000 * mice_number), -->
+<!--     Mice = rep(rep(1:mice_number, each = 1000), no_method), -->
+<!--     force = rep(0, 1000 * mice_number * no_method) -->
+<!--   ) -->
+<!--   ## agg -->
+<!--   x_draws <- sim_agg_rank %>% select(starts_with("x")) -->
+<!--   plot_latent_df$force[(1:(1000 * mice_number))] <- -->
+<!--     as.vector(as.matrix(x_draws)) -->
+
+<!--   ## M1 -->
+<!--   f_draws <- sim_cohort_hp %>% select(starts_with("f")) -->
+<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
+<!--                          1000 * mice_number] <- -->
+<!--     as.vector(as.matrix(f_draws)) -->
+
+<!--   ## M2 -->
+<!--   f_draws <- sim_cohort_dchp %>% select(starts_with("f")) -->
+<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
+<!--                          2000 * mice_number] <- -->
+<!--     as.vector(as.matrix(f_draws)) -->
+
+<!--   ## M3 -->
+<!--   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) -->
+<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
+<!--                          3000 * mice_number] <- -->
+<!--     as.vector(as.matrix(f_draws)) -->
+
+<!--   plot_latent_df$Mice <- factor(plot_latent_df$Mice, -->
+<!--     levels = expert_rank_10[[current_cohort]] -->
+<!--   ) -->
+<!--   plot_latent_df$Method <- factor(plot_latent_df$Method, -->
+<!--     labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP") -->
+<!--   ) -->
+<!--   plot_cols <- col_df %>% -->
+<!--   filter(method %in% c( -->
+<!--     "AggRank", "C-HP", -->
+<!--     "C-DCHP", "C-MMHP" -->
+<!--   )) %>% -->
+<!--   pull(cols) -->
+
+<!--   p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) + -->
+<!--     geom_boxplot(alpha = 0.7) + -->
+<!--     scale_fill_manual(values = plot_cols) + -->
+<!--     ggtitle("(a)") + -->
+<!--     theme_bw() + -->
+<!--     theme( -->
+<!--       plot.title = element_text(size = 22, hjust = 0.5, face = "bold"), -->
+<!--       text = element_text(size = 20), -->
+<!--       axis.text.x = element_text(size = 10), -->
+<!--       legend.position = "none" -->
+<!--     ) + -->
+<!--     facet_grid(cols = vars(Method)) + -->
+<!--     xlab("Mice (ranked by I&SI)") + -->
+<!--     ylab("Latent rank") + -->
+<!--     labs(title = paste("Cohort ", current_cohort, sep = "")) -->
+<!--   print(p1) -->
 <!-- } -->
-<!--   } -->
-<!-- } -->
-
-<!-- total_matrix <- apply(total_event_array, c(1,2), sum) -->
-<!-- active_matrix <- apply(active_event_array, c(1,2), sum) -->
-
-<!-- inact_matrix <- total_matrix - active_matrix -->
-
-<!-- rm(interpolation_array_list) -->
-
-<!-- ``` -->
-
-<!-- ## Variance of f for no fights -->
-
-<!-- ```{r var-f, eval=FALSE} -->
-<!-- data_path <- "../output/revisions/lapl_check/" -->
-<!-- current_cohort <- 6 -->
-<!-- ## good for 4,8,9 -->
-<!-- ## ok for 2 -->
-<!-- ## bad for 1, 10 -->
-<!-- load(paste(data_path, cohort_names[current_cohort], -->
-<!--   "/cohort_mmhp_stan_result_", cohort_names[current_cohort], -->
-<!--   ".RData", -->
-<!--   sep = "" -->
-<!-- )) -->
-
+
+<!-- ``` -->
+
+<!-- Cohort 3 win loss -->
+
+<!-- ```{r c3-win-loss} -->
+<!-- current_cohort <- 3 -->
 <!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
-<!-- return_df <- cleanObservationPeriod(current_cohort, -->
-<!--       raw_df = full_data[[cohort_names[current_cohort]]], -->
-<!--       clean_data) -->
-<!-- sim_cohort_mmhp -->
-
-<!-- sim_cohort_mmhp %>% select(starts_with("f")) %>%  -->
-<!--   pivot_longer(everything()) %>%  -->
+
+<!-- clean_data$N_count -->
+
+<!-- load(paste(data_path, -->
+<!--              cohort_names[current_cohort], -->
+<!--              "/cohort_mmhp_stan_result_", -->
+<!--              cohort_names[current_cohort], -->
+<!--              ".RData", -->
+<!--              sep = "" -->
+<!--              )) -->
+
+<!-- gamma_draws <- sim_cohort_mmhp %>% -->
+<!--   select(starts_with("gamma")) %>% -->
+<!--   pivot_longer(everything()) -->
+
+<!-- gamma_draws$name <- factor(gamma_draws$name, -->
+<!--                            levels = paste("gamma[", 1:12, "]", sep = "")) -->
+
+<!-- gamma_draws %>% -->
 <!--   ggplot(aes(name, value)) + -->
@@
 
-<!-- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
-
-<!-- sim_cohort_mmhp %>% select(starts_with("f")) %>%  -->
-<!--   pivot_longer(everything()) %>%  -->
-<!--   group_by(name) %>%  -->
-<!--   summarise(sd = sd(value)) %>%  -->
-<!--   arrange(desc(sd)) %>%  -->
-<!--   print(n = 12) -->
-
-<!-- ``` -->
-
-<!-- ```{r investigate-stan-fits, eval=FALSE} -->
-<!-- ## rerunning with ensuring that delta is not fixed. -->
-<!-- pri_data_path <- "../output/revisions/lapl_check/prior/" -->
-<!-- current_cohort <- 9 -->
-<!-- ## good for 4,8,9 -->
-<!-- ## ok for 2 -->
-<!-- ## bad for 1, 10 -->
-<!-- load(paste(pri_data_path, cohort_names[current_cohort], -->
-<!--   "/cohort_mmhp_stan_result_", cohort_names[current_cohort], -->
-<!--   ".RData", -->
-<!--   sep = "" -->
-<!-- )) -->
-
-<!-- hist(sim_cohort_mmhp$w_lambda) -->
-<!-- # table(sim_cohort_mmhp$w_lambda) -->
-
-<!-- ### convert to "draws" object, compute rhats -->
-<!-- fit_draws <- as_draws_array(sim_cohort_mmhp) -->
-
-<!-- mcmc_trace(fit_draws, pars = c("w_lambda", "beta", "gamma[1]")) -->
-
-<!-- rhat(fit_draws[ , ,"f[1]"]) -->
-
-<!-- rhat_fit <- apply(fit_draws, 3, rhat) -->
-<!-- summary(rhat_fit) -->
-<!-- ``` -->
-
-<!-- ### What is difference between cohort 4 and 5/6 -->
-
-<!-- ```{r cohort-stats, eval=FALSE} -->
-<!-- clean_data_2 <- cleanData(full_data[[cohort_names[2]]]) -->
-<!-- clean_data_4 <- cleanData(full_data[[cohort_names[4]]]) -->
-<!-- clean_data_6 <- cleanData(full_data[[cohort_names[6]]]) -->
-<!-- clean_data_1 <- cleanData(full_data[[cohort_names[1]]]) -->
-<!-- clean_data_10 <- cleanData(full_data[[cohort_names[10]]]) -->
-<!-- ``` -->
-
-<!-- ```{r, message=FALSE, eval=FALSE} -->
-<!-- for(current_cohort in 1:10) { -->
-<!--   print(current_cohort) -->
-<!--    clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
-<!--     return_df <- cleanObservationPeriod(current_cohort, -->
-<!--       raw_df = -->
-<!--         full_data[[cohort_names[current_cohort]]], -->
-<!--       clean_data -->
-<!--     ) -->
-<!--     print(sum(clean_data$N_count)) -->
-<!--     unique_pairs_df <- return_df %>% -->
-<!--       group_by(initiator, recipient) %>% -->
-<!--       dplyr::summarize( -->
-<!--         count = n(), -->
-<!--         observe = list(observe.id), -->
-<!--         observe.length = list(observe.time), -->
-<!--         no.events = list(no.events) -->
-<!--       ) -->
-<!--     unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")]) -->
-<!--     print(nrow(unique_observe_win)) -->
-<!--     print(sum(unique_observe_win$observe.time)) -->
-<!--     print(summary(unique_pairs_df$count)) -->
-<!--     cat("-------\n") -->
-<!-- } -->
-<!-- ``` -->
-
-<!-- ## Bayesplot -->
-
-<!-- ```{r specific-cohort, eval=FALSE} -->
-<!-- current_cohort <- 4 -->
-<!-- load(paste(pri_data_path, cohort_names[current_cohort], -->
-<!--   "/cohort_mmhp_stan_result_", cohort_names[current_cohort], -->
-<!--   ".RData", -->
-<!--   sep = "" -->
-<!-- )) -->
-
-<!-- fit_draws <- as_draws_array(sim_cohort_mmhp) -->
-<!-- ``` -->
-
-<!-- ```{r, eval=FALSE} -->
-<!-- mcmc_pairs(fit_draws, pars = c("eta_1", "eta_2", "eta_3", "beta")) -->
-
-<!-- mcmc_trace(fit_draws, pars = c("eta_1", "eta_2", "eta_3", "beta")) -->
-
-<!-- mcmc_pairs(fit_draws, pars = c("beta", "eta_3"),  -->
-<!--              diag_fun = "dens", off_diag_fun = "hex", -->
-<!--              condition = pairs_condition(chains = list(2, c(1,3,4)))) -->
-
-<!-- ``` -->
-
-<!-- ## Check Priors -->
-
-<!-- ```{r normal-priors, eval=FALSE} -->
-
-<!-- pri_data_path <- "../output/revisions/lapl_check/prior_check/" -->
-
-<!-- for(current_cohort in 1:10) { -->
-<!--   print(current_cohort) -->
-<!--   load(paste(pri_data_path, cohort_names[current_cohort], -->
-<!--   "/cohort_mmhp_stan_result_", cohort_names[current_cohort], -->
-<!--   ".RData", -->
-<!--   sep = "" -->
-<!--   )) -->
-<!--   fit_draws <- as_draws_array(sim_cohort_mmhp) -->
-<!--   rhat_fit <- apply(fit_draws, 3, posterior::rhat) -->
-<!--   print(summary(rhat_fit)) -->
-<!--   print(mcmc_trace(fit_draws,  -->
-<!--              pars = c("eta_1", "eta_2", "eta_3", "beta"))) -->
-<!--   cat("-----\n") -->
-<!-- } -->
-
-<!-- mcmc_pairs(fit_draws, pars = c("eta_1", "eta_2", "eta_3", "beta")) -->
-
-<!-- ``` -->
-
-<!-- ## check rankings against isi score this data -->
-
-<!-- ```{r label, eval=FALSE} -->
-<!-- for(current_cohort in 1:10) { -->
-<!--   print(current_cohort) -->
-<!--   load(paste(pri_data_path, cohort_names[current_cohort], -->
-<!--   "/cohort_mmhp_stan_result_", cohort_names[current_cohort], -->
-<!--   ".RData", -->
-<!--   sep = "" -->
-<!--   )) -->
-<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
-<!--   fit_draws <- as_draws_array(sim_cohort_mmhp) -->
-<!--   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>%  -->
+<!-- zeta_draws <- sim_cohort_mmhp %>% -->
+<!--   select(starts_with("zeta")) %>% -->
 <!--   pivot_longer(everything()) -->
-<!--   f_draws$name <- factor(f_draws$name, levels = paste("f[", -->
-<!--                                       expert_rank_10[[current_cohort]], -->
-<!--                                       "]", sep = "")) -->
-<!--   f_draws %>%  -->
+
+<!-- zeta_draws$name <- factor(zeta_draws$name, -->
+<!--                            levels = paste("zeta[", 1:12, "]", sep = "")) -->
+
+<!-- zeta_draws %>% -->
 <!--   ggplot(aes(name, value)) + -->
@@
 
-<!--   rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
-
-<!--   sim_cohort_mmhp %>% select(starts_with("f")) %>%  -->
+<!-- f_draws <- sim_cohort_mmhp %>% -->
+<!--   select(starts_with("f")) %>% -->
 <!--   pivot_longer(everything()) %>% -->
 <!--   group_by(name) %>% -->
-<!--     summarise(sd = sd(value)) %>%  -->
-<!--     arrange(desc(sd)) %>%  -->
-<!--     print(n = 12) -->
-
-<!--   cat("-----\n") -->
+<!--   summarise(med = median(value)) %>% -->
+<!--   arrange(-med) -->
+
+<!-- f_draws %>% pull(name) -->
+
+<!-- cmmhp_ranks <- c(10, 12, 7, 6, 3, 8, 2, 4, 1, 9, 11, 5) -->
+<!-- clean_data$N_count[cmmhp_ranks, cmmhp_ranks] -->
+
+<!-- c3_count <- clean_data$N_count -->
+<!-- names(c3_count) <- 1:12 -->
+<!-- rownames(c3_count) <- 1:12 -->
+<!-- colnames(c3_count) <- 1:12 -->
+<!-- isi98(c3_count) -->
+<!-- isi98(c3_count[cmmhp_ranks, cmmhp_ranks]) -->
+<!-- ``` -->
+
+<!-- ## Plot Omega Lambda and f draws -->
+
+<!-- ```{r plot-omega-lambda, message=FALSE} -->
+<!-- for(current_cohort in 1:10) { -->
+<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
+<!--   load(paste(data_path, -->
+<!--              cohort_names[current_cohort], -->
+<!--              "/cohort_mmhp_stan_result_", -->
+<!--              cohort_names[current_cohort], -->
+<!--              ".RData", -->
+<!--              sep = "" -->
+<!--              )) -->
+<!--   fit_draws <- as_draws_array(sim_cohort_mmhp) -->
+<!--   plot1 <- mcmc_hist(fit_draws, pars = "w_lambda") + -->
+<!--     labs(paste("Cohort ", current_cohort, sep = "")) -->
+<!--   print(plot1) -->
 <!-- } -->
 <!-- ``` -->
+
+<!-- # Compare rankings with/without eta_3 -->
+
+<!-- ```{r plot-rankings-both-models-no-eta3, message=FALSE} -->
+<!-- # data_path -->
+<!-- other_data_path <- "../output/revisions/lapl_check/ident_check/" -->
+
+<!-- for(current_cohort in 1:10) { -->
+<!--   load(paste(data_path, -->
+<!--              cohort_names[current_cohort], -->
+<!--              "/cohort_mmhp_stan_result_", -->
+<!--              cohort_names[current_cohort], -->
+<!--              ".RData", -->
+<!--              sep = "" -->
+<!--              )) -->
+<!--   sim1 <- sim_cohort_mmhp -->
+<!--   load(paste(other_data_path, -->
+<!--              cohort_names[current_cohort], -->
+<!--              "/cohort_mmhp_stan_result_", -->
+<!--              cohort_names[current_cohort], -->
+<!--              ".RData", -->
+<!--              sep = "" -->
+<!--              )) -->
+<!--   sim2 <- sim_cohort_mmhp -->
+
+<!--   all_data <- sim1 %>% -->
+<!--     select(starts_with("f")) %>%  -->
+<!--     pivot_longer(everything()) %>%  -->
+<!--     mutate(model = "with eta3") %>%  -->
+<!--     bind_rows(sim2 %>% select(starts_with("f")) %>%  -->
+<!--                 pivot_longer(everything()) %>%  -->
+<!--                 mutate(model = "without")) -->
+
+<!--   f_ranks <- paste("f[", expert_rank_10[[current_cohort]], -->
+<!--                    "]", sep = "")  -->
+<!--   all_data$name <- factor(all_data$name, levels = f_ranks) -->
+
+<!--   all_data$model <- factor(all_data$model) -->
+<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
+<!--     geom_boxplot() + -->
+<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
+<!--          subtitle = "Removing eta3, ordered by ISI", -->
+<!--          y = "Latent Rankings") -->
+<!--   print(comp_plot) -->
+
+<!--   all_data %>% group_by(name, model) %>%  -->
+<!--     summarise(model_mean = mean(value),  -->
+<!--               model_sd = sd(value)) -->
+
+<!--   all_data <- sim1 %>% -->
+<!--     select(starts_with("eta") | starts_with("w_lam") | starts_with("beta")) %>%  -->
+<!--     pivot_longer(everything()) %>%  -->
+<!--     mutate(model = "with eta1") %>%  -->
+<!--     bind_rows(sim2 %>%  -->
+<!--                 select(starts_with("eta") |  -->
+<!--                          starts_with("w_lam") | -->
+<!--                          starts_with("beta")) %>%  -->
+<!--                 pivot_longer(everything()) %>%  -->
+<!--                 mutate(model = "without")) -->
+<!--   all_data$model <- factor(all_data$model) -->
+<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
+<!--     geom_boxplot() + -->
+<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
+<!--          subtitle = "Comparison removing eta3", y = "Eta params") + -->
+<!--     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) -->
+<!--   print(comp_plot) -->
+<!--   ### -->
+<!--   ## same for zeta, -->
+<!--   all_data <- sim1 %>% -->
+<!--     select(starts_with("zeta") ) %>%  -->
+<!--     pivot_longer(everything()) %>%  -->
+<!--     mutate(model = "with eta1") %>%  -->
+<!--     bind_rows(sim2 %>% select(starts_with("zeta")) %>%  -->
+<!--                 pivot_longer(everything()) %>%  -->
+<!--                 mutate(model = "without")) -->
+<!--   all_data$model <- factor(all_data$model) -->
+<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
+<!--     geom_boxplot() + -->
+<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
+<!--          subtitle = "Comparison removing eta3", y = "Zeta params") + -->
+<!--     theme(axis.text.x = element_blank()) + -->
+<!--     facet_wrap(~name, scales = "free") -->
+<!--   print(comp_plot) -->
+
+<!--   ### -->
+<!--   all_data <- sim1 %>% -->
+<!--     select(starts_with("gamma")) %>%  -->
+<!--     pivot_longer(everything()) %>%  -->
+<!--     mutate(model = "with eta3") %>%  -->
+<!--     bind_rows(sim2 %>% select(starts_with("gamma")) %>%  -->
+<!--                 pivot_longer(everything()) %>%  -->
+<!--                 mutate(model = "without")) -->
+<!--   all_data$model <- factor(all_data$model) -->
+<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
+<!--     geom_boxplot() + -->
+<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
+<!--          subtitle = "Comparison removing eta3", y = "Out Degree") + -->
+<!--     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) -->
+<!--   print(comp_plot) -->
+
+<!-- } -->
+
+<!-- ``` -->
+
+<!-- # Compare rankings with/without eta_1 -->
+
+<!-- ```{r plot-rankings-both-models-no-eta-1, message=FALSE} -->
+<!-- # data_path -->
+<!-- other_data_path <- "../output/revisions/lapl_check/ident_check_no_eta1/" -->
+
+<!-- for(current_cohort in 1:10) { -->
+<!--   load(paste(data_path, -->
+<!--              cohort_names[current_cohort], -->
+<!--              "/cohort_mmhp_stan_result_", -->
+<!--              cohort_names[current_cohort], -->
+<!--              ".RData", -->
+<!--              sep = "" -->
+<!--              )) -->
+<!--   sim1 <- sim_cohort_mmhp -->
+<!--   load(paste(other_data_path, -->
+<!--              cohort_names[current_cohort], -->
+<!--              "/cohort_mmhp_stan_result_", -->
+<!--              cohort_names[current_cohort], -->
+<!--              ".RData", -->
+<!--              sep = "" -->
+<!--              )) -->
+<!--   sim2 <- sim_cohort_mmhp -->
+
+<!--   all_data <- sim1 %>% -->
+<!--     select(starts_with("f")) %>%  -->
+<!--     pivot_longer(everything()) %>%  -->
+<!--     mutate(model = "with eta1") %>%  -->
+<!--     bind_rows(sim2 %>% select(starts_with("f")) %>%  -->
+<!--                 pivot_longer(everything()) %>%  -->
+<!--                 mutate(model = "without")) -->
+
+<!--   f_ranks <- paste("f[", expert_rank_10[[current_cohort]], -->
+<!--                    "]", sep = "")  -->
+<!--   all_data$name <- factor(all_data$name, levels = f_ranks) -->
+
+<!--   all_data$model <- factor(all_data$model) -->
+<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
+<!--     geom_boxplot() + -->
+<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
+<!--          subtitle = "Comparison removing eta1, ranked by ISI", -->
+<!--          y = "Latent Ranks") -->
+<!--   print(comp_plot) -->
+
+<!--   all_data %>% group_by(name, model) %>%  -->
+<!--     summarise(model_mean = mean(value),  -->
+<!--               model_sd = sd(value)) -->
+
+<!--   ## same for beta_etc, -->
+<!--   all_data <- sim1 %>% -->
+<!--     select(starts_with("eta") | starts_with("w_lam") | starts_with("beta")) %>%  -->
+<!--     pivot_longer(everything()) %>%  -->
+<!--     mutate(model = "with eta1") %>%  -->
+<!--     bind_rows(sim2 %>%  -->
+<!--                 select(starts_with("eta") |  -->
+<!--                          starts_with("w_lam") | -->
+<!--                          starts_with("beta")) %>%  -->
+<!--                 pivot_longer(everything()) %>%  -->
+<!--                 mutate(model = "without")) -->
+<!--   all_data$model <- factor(all_data$model) -->
+<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
+<!--     geom_boxplot() + -->
+<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
+<!--          subtitle = "Comparison removing eta1", y = "Eta params") + -->
+<!--     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) -->
+<!--   print(comp_plot) -->
+<!--   ### -->
+<!--   ## same for zeta, -->
+<!--   all_data <- sim1 %>% -->
+<!--     select(starts_with("zeta") ) %>%  -->
+<!--     pivot_longer(everything()) %>%  -->
+<!--     mutate(model = "with eta1") %>%  -->
+<!--     bind_rows(sim2 %>% select(starts_with("zeta")) %>%  -->
+<!--                 pivot_longer(everything()) %>%  -->
+<!--                 mutate(model = "without")) -->
+<!--   all_data$model <- factor(all_data$model) -->
+<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
+<!--     geom_boxplot() + -->
+<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
+<!--          subtitle = "Comparison removing eta1", y = "Zeta params") + -->
+<!--     theme(axis.text.x = element_blank()) + -->
+<!--     facet_wrap(~name, scales = "free") -->
+<!--   print(comp_plot) -->
+
+<!--   ### -->
+<!--   all_data <- sim1 %>% -->
+<!--     select(starts_with("gamma")) %>%  -->
+<!--     pivot_longer(everything()) %>%  -->
+<!--     mutate(model = "with eta1") %>%  -->
+<!--     bind_rows(sim2 %>% select(starts_with("gamma")) %>%  -->
+<!--                 pivot_longer(everything()) %>%  -->
+<!--                 mutate(model = "without")) -->
+<!--   all_data$model <- factor(all_data$model) -->
+<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
+<!--     geom_boxplot() + -->
+<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
+<!--          subtitle = "Comparison removing eta1", y = "Out Degree") + -->
+<!--     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) -->
+<!--   print(comp_plot) -->
+
+<!-- } -->
+
+<!-- ``` -->
+
+<!-- # Other Paper plots -->
+
+<!-- ```{r fig-3b} -->
+<!-- current_cohort <- 5 -->
+
+<!-- m1_pr <- readRDS(paste(data_path, cohort_names[current_cohort], -->
+<!--   "/chp_pr_matrix_", cohort_names[current_cohort], -->
+<!--   ".RDS", -->
+<!--   sep = "" -->
+<!-- )) -->
+
+<!-- m2_pr <- readRDS(paste(data_path, cohort_names[current_cohort], -->
+<!--   "/dchp_pr_matrix_", cohort_names[current_cohort], -->
+<!--   ".RDS", -->
+<!--   sep = "" -->
+<!-- )) -->
+
+<!-- m3_pr <- readRDS(paste(data_path, cohort_names[current_cohort], -->
+<!--   "/cmmhp_pr_matrix_", cohort_names[current_cohort], -->
+<!--   ".RDS", -->
+<!--   sep = "" -->
+<!-- )) -->
+
+<!-- indep_pr <- readRDS(paste(data_path, cohort_names[current_cohort], -->
+<!--   "/immhp_pr_matrix_", cohort_names[current_cohort], -->
+<!--   ".RDS", -->
+<!--   sep = "" -->
+<!-- )) -->
+
+<!-- matrix_lst_plot <- list( -->
+<!--   m1_pr[ -->
+<!--     rev(expert_rank_10[[current_cohort]]), -->
+<!--     expert_rank_10[[current_cohort]] -->
+<!--   ], -->
+<!--   m2_pr[ -->
+<!--     rev(expert_rank_10[[current_cohort]]), -->
+<!--     expert_rank_10[[current_cohort]] -->
+<!--   ] -->
+<!--   , -->
+<!--   m3_pr[ -->
+<!--     rev(expert_rank_10[[current_cohort]]), -->
+<!--     expert_rank_10[[current_cohort]] -->
+<!--   ], -->
+<!--   indep_pr[ -->
+<!--     rev(expert_rank_10[[current_cohort]]), -->
+<!--     expert_rank_10[[current_cohort]] -->
+<!--   ] -->
+<!-- ) -->
+<!-- # cat("Cohort ",current_cohort,"\n",sep="") -->
+<!-- myMultiMatrixPlot( -->
+<!--   X = matrix_lst_plot, no_matrix = 4, n_row = 2, -->
+<!--   xLabels = expert_rank_10[[current_cohort]], -->
+<!--   yLabels = rev(expert_rank_10[[current_cohort]]), -->
+<!--   min = -80, max = 80, axis_cex = 2, title_cex = 1.8, -->
+<!--   colorPalette = "RdBu", if.emp = FALSE, -->
+<!--   # legend.mar=c(0.5,.5,0.5,0.5), -->
+<!--   title_lst = list("C-HP", "C-DCHP", "C-MMHP", "I-MMHP"), -->
+<!--   # title_lst = list("I-MMHP"), -->
+<!--   col_axis = c(-80, -40, 0, 40, 80), -->
+<!--   fake_matrix = FALSE, -->
+<!--   matrix.mar = c(2.5, 2.5, 2.5, 1) -->
+<!-- ) -->
+<!-- mtext(text = "(b)", -->
+<!--       side = 3, -->
+<!--       line = 0.5, -->
+<!--       outer = TRUE, -->
+<!--       cex = 2.5, -->
+<!--       font = 2) -->
+
+<!-- ``` -->
+
+<!-- ```{r fig-7a} -->
+<!-- load("../output/revisions/lapl_check/prior_check/plot_N_predict_revision.RData") -->
+<!-- current_cohort <- 5 # cohort 1 looks worse than rest -->
+
+<!-- temp_plot_df <- predict_day_mae_df_lst[[current_cohort]] -->
+<!-- temp_plot_df$method <- factor(temp_plot_df$method, -->
+<!--   levels = c("mmhp", "dsnl", "m1", "m2", "m3"), -->
+<!--   labels = c("I-MMHP", "DSNL", "C-HP", "C-DCHP", "C-MMHP") -->
+<!-- ) -->
+<!-- temp_plot_df$day <- factor(temp_plot_df$day) -->
+<!-- # png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""), -->
+<!-- # width=600,height=300) -->
+
+<!-- plot_cols_pred <- col_df %>% -->
+<!--   filter(method %in% levels(temp_plot_df$method)) %>% -->
+<!--   arrange(factor(method, levels = c( -->
+<!--     "I-MMHP", "DSNL", -->
+<!--     "C-HP", "C-DCHP", "C-MMHP" -->
+<!--   ))) %>% -->
+<!--   pull(cols) -->
+
+<!-- p3 <- temp_plot_df %>% -->
+<!--   rowwise() %>% -->
+<!--   # mutate(norm = min(norm,60)) %>% -->
+<!--   # rename(Method = method) %>% -->
+<!--   ggplot(aes(x = method, y = mae, fill = method)) + -->
+<!--   geom_boxplot(alpha = 0.7) + -->
+<!--   scale_fill_manual(values = plot_cols_pred) + -->
+<!--   ggtitle("(a)") + -->
+<!--   theme_bw() + -->
+<!--   theme( -->
+<!--     plot.title = element_text(size = 22, hjust = 0.5, face = "bold"), -->
+<!--     text = element_text(size = 20), -->
+<!--     axis.text.x = element_blank(), -->
+<!--     axis.ticks.x = element_blank(), -->
+<!--     legend.position = "right" -->
+<!--   ) + -->
+<!--   facet_grid(cols = vars(day)) + -->
+<!--   xlab("Prediction horizon (day)") + -->
+<!--   ylab("MAE") + -->
+<!--   ylim(0, 5) + # aren't infinite but >150 and <200 -->
+<!--   NULL -->
+<!-- p3 + labs(fill = "Method", title = "Single Cohort") -->
+
+<!-- ``` -->
+
+<!-- ```{r fig-7b} -->
+<!-- load("../output/revisions/lapl_check/prior_check/plot_N_predict_revision.RData") -->
+
+<!-- all_cohort_box <- all_cohort_mae_df -->
+
+<!-- all_cohort_box$method <- factor(all_cohort_box$method, -->
+<!--   levels = c("mmhp", "dsnl", "m1", "m2", "m3"), -->
+<!--   labels = c( -->
+<!--     "I-MMHP", "DSNL", -->
+<!--     "C-HP", "C-DCHP", -->
+<!--     "C-MMHP" -->
+<!--   ) -->
+<!-- ) -->
+<!-- all_cohort_box$day <- factor(all_cohort_box$day) -->
+
+<!-- plot_cols_pred <- col_df %>% -->
+<!--   filter(method %in% levels(all_cohort_box$method)) %>% -->
+<!--   arrange(factor(method, levels = c( -->
+<!--     "I-MMHP", "DSNL", -->
+<!--     "C-HP", "C-DCHP", "C-MMHP" -->
+<!--   ))) %>% -->
+<!--   pull(cols) -->
+
+<!-- all_cohort_box %>% -->
+<!--   ggplot(aes(x = method, y = norm, fill = method)) + -->
+<!--   # facet_grid(cols = vars(day)) + -->
+<!--   geom_boxplot(alpha = 0.7) + -->
+<!--   scale_fill_manual(values = plot_cols_pred) + -->
+<!--   ggtitle("(a)") + -->
+<!--   theme_bw() + -->
+<!--   theme( -->
+<!--     plot.title = element_text( -->
+<!--       size = 22, -->
+<!--       hjust = 0.5, face = "bold" -->
+<!--     ), -->
+<!--     text = element_text(size = 20), -->
+<!--     axis.text.x = element_blank(), -->
+<!--     axis.ticks.x = element_blank(), -->
+<!--     legend.position = "right" -->
+<!--   ) + -->
+<!--   facet_grid(cols = vars(day)) + -->
+<!--   # guides(color=guide_legend(title="Method")) + -->
+<!--   xlab("Prediction horizon (day)") + -->
+<!--   ylab("MAE") + -->
+<!--   labs(fill = "Method") + -->
+<!--   # ylim(0, 80) + -->
+<!--   NULL -->
+
+<!-- ``` -->
+
+<!-- ```{r fig-7b-pred-rank-spearman-all-cohorts} -->
+<!-- load("../output/revisions/lapl_check/prior_check/plot_rank_predict.RData") -->
+
+<!-- all_cohort_rank_df$method <- factor(all_cohort_rank_df$method, -->
+<!--   levels = c("mmhp", "dsnl", "m1", "m2", "m3"), -->
+<!--   labels = c( -->
+<!--     "I-MMHP", "DSNL", "C-HP", -->
+<!--     "C-DCHP", "C-MMHP" -->
+<!--   ) -->
+<!-- ) -->
+
+<!-- p7 <- ggplot( -->
+<!--   all_cohort_rank_df, -->
+<!--   aes(x = method, y = spearman, fill = method) -->
+<!-- ) + -->
+<!--   # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) + -->
+<!--   geom_boxplot(alpha = 0.7) + -->
+<!--   scale_fill_manual(values = plot_cols_pred) + -->
+<!--   ggtitle("(b)") + -->
+<!--   theme_bw() + -->
+<!--   theme( -->
+<!--     plot.title = element_text(size = 22, hjust = 0.5, face = "bold"), -->
+<!--     text = element_text(size = 20), -->
+<!--     axis.text.x = element_blank(), -->
+<!--     axis.ticks.x = element_blank(), -->
+<!--     legend.position = "right" -->
+<!--   ) + -->
+<!--   facet_grid(cols = vars(day)) + -->
+<!--   xlab("Prediction horizon (day)") + -->
+<!--   ylab("Spearman rank corr.") + -->
+<!--   # coord_cartesian(ylim=c(0,1)) + -->
+<!--   labs(fill = "Method") -->
+
+<!-- p7 -->
+<!-- ``` -->
+
+<!-- ```{r construct data for plot, results='hide',message=FALSE,cache=TRUE} -->
+<!-- library(PlayerRatings) -->
+
+<!-- current_cohort <- 7 -->
+<!-- # 4 best so far, or 7 -->
+
+<!-- load(paste(data_path, cohort_names[current_cohort], -->
+<!--   "/predict_simulation_", cohort_names[current_cohort], -->
+<!--   ".RData", -->
+<!--   sep = "" -->
+<!-- )) -->
+<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]], -->
+<!--   cut_off = 1 -->
+<!-- ) -->
+
+<!-- df <- full_data[[cohort_names[current_cohort]]] -->
+<!-- df <- df[df$Actor != "Start" & df$Actor != "End", ] -->
+<!-- df1 <- expandrows(df) -->
+<!-- df1 <- df1[order(df1$Timestamp), ] # ensure in date order -->
+<!-- df1$event <- 1:nrow(df1) -->
+<!-- glick.df <- df1[, c("event", "Actor", "Recipient", "score"), with = FALSE] -->
+<!-- # need event, actor, recipient, score -->
+<!-- gl <- my_glicko(glick.df, history = TRUE, cval = 2) -->
+
+<!-- # ------------------- period -->
+<!-- training_end <- nrow(df[df$day <= 18, ]) -->
+<!-- testing_end <- nrow(df) - 1 # 1077 #929 for cohort 5 -->
+<!-- newx <- c(training_end:testing_end) -->
+
+<!-- # ----------------- set pars for plot -->
+<!-- my_col <- c("black", "grey", "orange", "red") -->
+<!-- col_vec <- colorRampPalette(my_col)(mice_number) -->
+<!-- ltypes_vec <- rep(1, mice_number) # c(1,2,3,1,2,3,1,2,3,1,2,3) -->
+<!-- history_width <- 3 -->
+<!-- sim_width <- 0.3 -->
+<!-- shade_vec <- makeTransparent(col_vec, 0.2) -->
+<!-- less_shade_vec <- makeTransparent(col_vec, 0.7) -->
+
+<!-- # ---------------- simulation mean and sd -->
+<!-- sim_gl_array <- array(NA, dim = c(12, testing_end - training_end + 1, 1000)) -->
+<!-- for (s in 1:1000) { -->
+<!--   print(s) -->
+<!--   temp_gl <- glickoScoreSimulationWithWindowsReturnAll( -->
+<!--     predict.sim = m3_predict_sim[5:8, s], # 7 for c 2 and 10 -->
+<!--     history.df = glick.df[1:training_end, ] -->
+<!--   ) -->
+<!--   history_matrix <- temp_gl$history[, , 1] -->
+
+<!--   if (testing_end > ncol(temp_gl$history[, , 1])) { -->
+<!--     history_matrix <- cbind( -->
+<!--       history_matrix, -->
+<!--       t(matrix(rep( -->
+<!--         history_matrix[, ncol(history_matrix)], -->
+<!--         testing_end - ncol(temp_gl$history[, , 1]) -->
+<!--       ), -->
+<!--       nrow = testing_end - ncol(temp_gl$history[, , 1]), -->
+<!--       byrow = TRUE -->
+<!--       )) -->
+<!--     ) -->
+<!--   } else { -->
+<!--     # try( -->
+<!--     history_matrix <- history_matrix[, 1:testing_end]  -->
+<!--     # temp_gl$history[,1:testing_end] -->
+<!--     # ) -->
+<!--   } -->
+<!--   sim_gl_array[, , s] <- history_matrix[, training_end:testing_end] -->
+<!-- } -->
+<!-- ``` -->
+
+<!-- ```{r fig-10a-glicko-rating} -->
+<!-- par(mar = c(3, 5, 3, 1)) -->
+<!-- testing_end <- testing_end - 1 -->
+<!-- plot(1, -->
+<!--   type = "n", xlab = "", -->
+<!--   ylab = "Glicko ranking", xlim = c(0, dim(gl$history)[2]), -->
+<!--   ylim = c(min(gl$history[, , 1]), max(gl$history[, , 1])), -->
+<!--   cex.axis = 2, cex.lab = 2 -->
+<!-- ) -->
+<!-- for (m in c(1:mice_number)) { -->
+<!--   # history -->
+<!--   lines(gl$history[m, 1:training_end, 1], -->
+<!--     cex = 0.6, col = col_vec[m], lwd = history_width, lty = ltypes_vec[m] -->
+<!--   ) -->
+<!--   lines(c(rep(NA, training_end), -->
+<!--           gl$history[m, (training_end + 1):testing_end, 1]), -->
+<!--     cex = 0.6, col = shade_vec[m], lwd = history_width, lty = ltypes_vec[m] -->
+<!--   ) -->
+
+<!--   # simulation -->
+<!--   cur_end <- testing_end -->
+<!--   mean_vec <- apply(sim_gl_array[m, , ], 1, function(x) mean(na.omit(x))) -->
+<!--   sd_vec <- apply(sim_gl_array[m, , ], 1, function(x) sd(na.omit(x))) -->
+<!--   polygon(c(newx, rev(newx)), -->
+<!--           c(mean_vec - sd_vec, rev(mean_vec + sd_vec)), -->
+<!--           col = shade_vec[m], border = NA) -->
+<!--   # polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA) -->
+<!--   lines(c(rep(NA, training_end), mean_vec), -->
+<!--     cex = 0.6, col = col_vec[m], lwd = 1, lty = 2 -->
+<!--   ) -->
+<!-- } -->
+
+<!-- # annotate the days -->
+<!-- for (d in c(19:21)) { -->
+<!--   abline(v = nrow(df[df$day <= (d - 1), ]), lty = 2, lwd = 0.4) -->
+<!--   text(x = nrow(df[df$day <= (d - 1), ]), y = 2600, d) -->
+<!-- } -->
+<!-- mtext(text = "(a)", side = 3, line = -2.3, -->
+<!--       outer = TRUE, cex = 2.8, at = 0.5, font = 2) -->
+<!-- ``` -->
+
+<!-- ```{r remove some objects, include=FALSE} -->
+<!-- rm(m3_predict_sim) -->
+<!-- rm(m2_predict_sim) -->
+<!-- rm(m1_predict_sim) -->
+<!-- rm(mmhp_predict_sim) -->
+<!-- rm(fit_agg_rank) -->
+<!-- rm(fit_cohort_hp) -->
+<!-- rm(fit_cohort_dchp) -->
+<!-- rm(fit_cohort_mmhp) -->
+
+<!-- # also removing stan fits as they can cause issues in the next chunk -->
+<!-- ``` -->

### 2021-08-10 lib/matrixPlotParameter.R

@@ -1,110 +1,121 @@
 # ----- Define a function for plotting a matrix ----- #
-matrixPlotParameter <- function(x, ...){
+matrixPlotParameter <- function(x, ...) {
   min <- min(x)
   max <- max(x)
-  #abs<-6.9
-  #min<--abs
-  #min<--0.78
-  #max<-20
-  #min<-0
-  #yLabels <- rownames(x)
-  #xLabels <- colnames(x)
-  title <-c()
+  # abs<-6.9
+  # min<--abs
+  # min<--0.78
+  # max<-20
+  # min<-0
+  # yLabels <- rownames(x)
+  # xLabels <- colnames(x)
+  title <- c()
   # check for additional function arguments
-  if( length(list(...)) ){
+  if (length(list(...))) {
     Lst <- list(...)
-    if( !is.null(Lst$zlim) ){
+    if (!is.null(Lst$zlim)) {
       min <- Lst$zlim[1]
       max <- Lst$zlim[2]
     }
-    if( !is.null(Lst$yLabels) ){
+    if (!is.null(Lst$yLabels)) {
       yLabels <- c(Lst$yLabels)
     }
-    if( !is.null(Lst$xLabels) ){
+    if (!is.null(Lst$xLabels)) {
       xLabels <- c(Lst$xLabels)
     }
-    if( !is.null(Lst$title) ){
+    if (!is.null(Lst$title)) {
       title <- Lst$title
     }
   }
   # check for null values
-  if( is.null(xLabels) ){
+  if (is.null(xLabels)) {
     xLabels <- c(1:ncol(x))
   }
-  if( is.null(yLabels) ){
+  if (is.null(yLabels)) {
     yLabels <- c(1:nrow(x))
   }
-  
-  par(oma = c(1,1,2,1))
-  layout(matrix(data=c(1,2), nrow=1, ncol=2), widths=c(5,1), heights=c(1,1))
-  
+
+  par(oma = c(1, 1, 2, 1))
+  layout(matrix(data = c(1, 2), nrow = 1, ncol = 2),
+         widths = c(5, 1),
+         heights = c(1, 1))
+
   # Red and green range from 0 to 1 while Blue ranges from 1 to 0
-  ColorRamp <- colorRampPalette(rev(brewer.pal(8,"RdBu")))(length(xLabels)*length(yLabels))
-  ColorRamp <- viridis::viridis(n = length(xLabels)*length(yLabels))
[…]

### 2021-08-10 run_scripts/c_mmhp_dc.R

@@ -11,7 +11,7 @@ jobid <- as.numeric(jobid)
 cohort_id <- jobid
 # cohort_id <- 1
 ####
-save_data_path <- "output/revisions/lapl_check/ident_check_no_eta1/"
+save_data_path <- "output/revisions/lapl_check/ident_check/" # "output_june30/"
 
 ### specify the number of segments here
 no_segments <- 500
@@ -102,7 +102,6 @@ print(paste("Cohort", current_cohort))
 # print(paste("Cohort", current_cohort))
 # 
 dc_model <- cmdstan_model("lib/model3_dc_lapl_ident.stan")
-model_code <- dc_model$print()
 # 
 stan_input_lst <- prepareDataStan(current_cohort)
 stan_input_lst$alpha_id <- expert_rank_10[[current_cohort]][1]
@@ -110,13 +109,13 @@ stan_input_lst$delta_1 <- rep(0.5, stan_input_lst$N_til)
 
 fit_cohort_mmhp <- dc_model$sample(
   data = stan_input_lst,
-  iter_warmup = 1000,
-  iter_sampling = 1000,
+  iter_warmup = 100,
+  iter_sampling = 200,
   chains = 4,
   thin = 4,
   # adapt_delta = 0.9,
   # max_treedepth = 15,
-  refresh = 100
+  refresh = 20
 )
 
 
@@ -139,7 +138,6 @@ dir.create(paste(save_data_path, cohort_names[current_cohort], sep = ""),
 
 save(sim_cohort_mmhp, fit_cohort_mmhp,
      sampler_diag,
-     model_code,
   file = paste(save_data_path,
     cohort_names[current_cohort],
     "/cohort_mmhp_stan_result_",
@@ -149,383 +147,382 @@ save(sim_cohort_mmhp, fit_cohort_mmhp,
   )
 )
 
-# 
-# #### Interpolate Latent States ####
-# 
-# print(current_cohort)
-# load(paste(save_data_path, cohort_names[current_cohort],
-#   "/cohort_mmhp_stan_result_", cohort_names[current_cohort],
-#   ".RData",
-#   sep = ""
-# ))
-# 
-# 
-# clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-# return_df <- cleanObservationPeriod(
-#   current_cohort,
-#   full_data[[cohort_names[current_cohort]]],
-#   clean_data
-# )
-# unique_pairs_df <- return_df %>%
-#   group_by(initiator, recipient) %>%
[…]

### 2021-08-10 output_scripts/investigate_rankings.Rmd
update sim ests being used

@@
 
-# Ranking and Events
-
-We first modify the priors from the C-MMHP model which leads to
-much improved MCMC performance.
-
-We want to look at the relationship between the inferred variability
-of the ranking and the number of interactions a given animal is involved in.
-
-We plot the inferred ranks arranged by decreasing number
-of total interactions for all 4 of the comparison models, as in Fig6a.
-
-```{r plot-rank-total-interactions, eval=FALSE}
- for(current_cohort in 1:10) {
-   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-   load(paste(data_path,
-              cohort_names[current_cohort],
-              "/cohort_mmhp_stan_result_",
-              cohort_names[current_cohort],
-              ".RData",
-              sep = ""
-              ))
-   total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count)
-   f_ranks <- paste("f[", order(total_inter, decreasing = TRUE),
-                    "]", sep = "")
-   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>%
-   pivot_longer(everything())
-   f_draws$name <- factor(f_draws$name, levels = f_ranks)
-   plot_f <- f_draws %>%
-   ggplot(aes(name, value)) +
-   geom_boxplot() +
-   labs(title = paste("Cohort ", current_cohort, sep = ""),
-        subtitle = "Ordered by total interactions")
-   print(plot_f)
- }
-```
+<!-- # Ranking and Events -->
+
+<!-- We first modify the priors from the C-MMHP model which leads to -->
+<!-- much improved MCMC performance. -->
+
+<!-- We want to look at the relationship between the inferred variability -->
+<!-- of the ranking and the number of interactions a given animal is involved in. -->
+
+<!-- We plot the inferred ranks arranged by decreasing number -->
+<!-- of total interactions for all 4 of the comparison models, as in Fig6a. -->
+
+<!-- ```{r plot-rank-total-interactions, eval=FALSE} -->
+<!--  for(current_cohort in 1:10) { -->
+<!--    clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
+<!--    load(paste(data_path, -->
+<!--               cohort_names[current_cohort], -->
+<!--               "/cohort_mmhp_stan_result_", -->
+<!--               cohort_names[current_cohort], -->
+<!--               ".RData", -->
+<!--               sep = "" -->
+<!--               )) -->
+<!--    total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
+<!--    f_ranks <- paste("f[", order(total_inter, decreasing = TRUE), -->
+<!--                     "]", sep = "") -->
+<!--    f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>% -->
+<!--    pivot_longer(everything()) -->
+<!--    f_draws$name <- factor(f_draws$name, levels = f_ranks) -->
+<!--    plot_f <- f_draws %>% -->
+<!--    ggplot(aes(name, value)) + -->
+<!--    geom_boxplot() + -->
+<!--    labs(title = paste("Cohort ", current_cohort, sep = ""), -->
+<!--         subtitle = "Ordered by total interactions") -->
+<!--    print(plot_f) -->
+<!--  } -->
+<!-- ``` -->
 
@@
 <!-- ``` -->
+
+# Examine new simulation results
+
+```{r inferred-rankings}
+sim_data_path <- here("output",
+                      "revisions",
+                      "lapl_check",
+                      "real_recov", "/")
+
+sim_files <- list.files(sim_data_path, pattern = "sim_model3_fit")
+
+num_nodes <- 12
+
+cohort_est <- readRDS(here("output", "sim_ests.RDS"))
+
+f_vec <- mean_values %>% 
+  pivot_wider(names_from = variable, values_from = mean) %>% 
+  select(starts_with("f")) %>% 
+  as.numeric()
+
+sim_ranks_mean <- tibble()
+sim_ranks <- tibble()
+
+model_colors <- col_df %>%
+  filter(method %in% c(
+    "C-HP",
+    "C-DCHP", "C-MMHP"
+  )) %>%
+  pull(cols)
+
+for(curr_sim in seq_along(sim_files)) {
+  load(paste0(sim_data_path,
+              sim_files[curr_sim]))
+
+  f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
+  m1_ranks <- apply(f_m1, 2, mean)
+
+  f_m1_sims <- f_m1 %>% 
+    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
+    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
+    pivot_longer(everything(),
+                 names_to = "node",
+                 values_to = "rank")
+  f_m1_sims$model <- "C-HP"
+
+  f_m2 <- sim_model3_stan_sim2 %>% select(starts_with("f"))
+  m2_ranks <- apply(f_m2, 2, mean)
+
+  f_m2_sims <- f_m2 %>% 
+    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
+    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
+    pivot_longer(everything(),
+                 names_to = "node",
+                 values_to = "rank")
+
+  f_m2_sims$model <- "C-DCHP"
+
+  f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
+  m3_ranks <- apply(f_m3, 2, mean)
+
+  f_m3_sims <- f_m3 %>% 
+    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
+    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
+    pivot_longer(everything(),
+                 names_to = "node",
+                 values_to = "rank")
+
+  f_m3_sims$model <- "C-MMHP"
+
+  curr_mean_ranks <- tibble(model = c(rep("C-HP", num_nodes),
+                                 rep("C-DCHP", num_nodes),
+                                 rep("C-MMHP", num_nodes)),
+                       ranks = c(m1_ranks,
+                                 m2_ranks,
+                                 m3_ranks),
+                       node = rep(1:num_nodes, 3),
+                       true_rank = rep(f_vec, 3),
+                       sim_id = curr_sim)
+  sim_ranks_mean <- sim_ranks_mean %>% 
+    bind_rows(curr_mean_ranks)
+
+  sim_ranks <- sim_ranks %>% 
+    bind_rows(f_m1_sims, f_m2_sims, f_m3_sims)
+
+}
+
+sim_ranks$node <- factor(sim_ranks$node, levels = 1:num_nodes)
+sim_ranks_mean$node <- factor(sim_ranks_mean$node, levels = 1:num_nodes)
+
+# sim_ranks$node
+
+sim_ranks_mean$model <- factor(sim_ranks_mean$model, 
+                               levels = c( "C-HP", "C-DCHP", "C-MMHP"))
+
+mean_sims <- sim_ranks_mean %>% 
+  left_join(col_df, by = c("model" = "method"))
+
+mean_sims$model <- factor(mean_sims$model, levels = c("C-HP", "C-DCHP",
+                                                      "C-MMHP"))
+
+true_ranks <- tibble(node = rep(1:num_nodes,3),
+                     true_rank = rep(f_vec,3),
+                     model = c(rep("C-HP", num_nodes),
+                               rep("C-DCHP", num_nodes),
+                               rep("C-MMHP", num_nodes)))
+true_ranks$node <- factor(true_ranks$node, levels = 1:num_nodes)
+
+true_ranks$model <- factor(true_ranks$model, 
+                           levels = c("C-HP", "C-DCHP","C-MMHP"))
+
+mean_sims %>% 
+  # filter(model == "C-MMHP") %>% 
+  ggplot(aes(node, ranks, fill = model)) + 
+  geom_boxplot(show.legend = FALSE) +
+  scale_fill_manual(values = model_colors, guide = FALSE) +
+  # geom_point(aes(node, true_rank, colour = "red")) +
+  ylim(c(0,1)) +
+  labs(title = "(a)",
+       subtitle = "Mean rank from each simulation", 
+       y = "Posterior Mean Rank", x = "Node") +
+  facet_wrap(~model) +
+  geom_point(data = true_ranks,
+             aes(node, true_rank, colour = "True Value")) +
+  scale_shape_discrete(name = "True Value") +
+  theme_minimal() +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom",
+        plot.title = element_text(hjust = 0.5, size = 26),
+        text = element_text(size = 18),
+        legend.text = element_text(size = 18))
+
+```
+
+What about the recovery of the other parameters?
+
+```{r eta_recovery}
+
+eta_ests <- tibble()
+
+for(curr_sim in seq_along(sim_files)) {
+  load(paste0(sim_data_path,
+              sim_files[curr_sim]))
+
+  eta_m1 <- sim_model3_stan_sim1 %>% 
+    select(starts_with("eta")) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise(mean_est = mean(value)) %>% 
+    mutate(model = "C-HP")
+
+  eta_m2 <- sim_model3_stan_sim2 %>%
+    select(starts_with("eta")) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise(mean_est = mean(value)) %>% 
+    mutate(model = "C-DCHP")
+
+  eta_m3 <- sim_model3_stan_sim3 %>%
+    select(starts_with("eta")) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise(mean_est = mean(value)) %>% 
+    mutate(model = "C-MMHP")
+
+  curr_sim_ests <- bind_rows(eta_m1,
+                             eta_m2,
+                             eta_m3)
+
+  eta_ests <- eta_ests %>% 
+    bind_rows(curr_sim_ests)
+
+}
+
+eta_ests$model <- factor(eta_ests$model, levels = c("C-HP",
+                                                    "C-DCHP",
+                                                    "C-MMHP"))
+
+tru_values <- tibble(name = c("eta_1", "eta_2", "eta_3"),
+                     mean_est = c(object_par$sim_eta_1,
+                                  object_par$sim_eta_2,
+                                  object_par$sim_eta_3))
+
+eta_ests %>% 
+  ggplot(aes(name, mean_est)) +
+  geom_boxplot(aes(fill = model)) +
+  geom_hline(mapping = aes(yintercept = mean_est),
+             tru_values, colour = "red") +
+  facet_wrap(~name)
+
+```

### 2021-08-11 output_scripts/investigate_rankings.Rmd
look at parameter recovery for simulation studies also

@@
 
+mean_values <- cohort_est %>% select(variable, mean)
+
 f_vec <- mean_values %>% 
@@
   as.numeric()
+
+f_vec <- seq(from = 0.2, to = 0.9, length.out = num_nodes)
 
@@
   f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
-  m1_ranks <- apply(f_m1, 2, mean)
+  m1_ranks <- apply(f_m1, 2, median)
 
@@
   f_m2 <- sim_model3_stan_sim2 %>% select(starts_with("f"))
-  m2_ranks <- apply(f_m2, 2, mean)
+  m2_ranks <- apply(f_m2, 2, median)
 
@@
   f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
-  m3_ranks <- apply(f_m3, 2, mean)
+  m3_ranks <- apply(f_m3, 2, median)
 
@@
 ```{r eta_recovery}
-
 eta_ests <- tibble()
@@
   eta_m1 <- sim_model3_stan_sim1 %>% 
-    select(starts_with("eta")) %>% 
+    select(starts_with("eta") | starts_with("beta") |
+             starts_with("r_lam")) %>% 
     pivot_longer(everything()) %>% 
     group_by(name) %>% 
-    summarise(mean_est = mean(value)) %>% 
-    mutate(model = "C-HP")
+    summarise(mean_est = median(value)) %>% 
+    mutate(model = "C-HP") %>% 
+    filter(name != "beta_delta")
 
   eta_m2 <- sim_model3_stan_sim2 %>%
-    select(starts_with("eta")) %>% 
+    select(starts_with("eta") | starts_with("beta") |
+             starts_with("r_lam")) %>% 
     pivot_longer(everything()) %>% 
     group_by(name) %>% 
-    summarise(mean_est = mean(value)) %>% 
-    mutate(model = "C-DCHP")
+    summarise(mean_est = median(value)) %>% 
+    mutate(model = "C-DCHP") %>% 
+    filter(name != "beta_delta")
 
   eta_m3 <- sim_model3_stan_sim3 %>%
-    select(starts_with("eta")) %>% 
+    select(starts_with("eta") | starts_with("beta") |
+             starts_with("r_lam")) %>% 
     pivot_longer(everything()) %>% 
     group_by(name) %>% 
-    summarise(mean_est = mean(value)) %>% 
-    mutate(model = "C-MMHP")
+    summarise(mean_est = median(value)) %>% 
+    mutate(model = "C-MMHP") %>% 
+    filter(name != "beta_delta")
 
@@
                              eta_m3)
-
   eta_ests <- eta_ests %>% 
     bind_rows(curr_sim_ests)
-
 }
@@
 
-tru_values <- tibble(name = c("eta_1", "eta_2", "eta_3"),
+tru_values <- tibble(name = c("eta_1", "eta_2", "eta_3",
+                              "r_lambda1", "beta"),
                      mean_est = c(object_par$sim_eta_1,
                                   object_par$sim_eta_2,
-                                  object_par$sim_eta_3))
+                                  object_par$sim_eta_3,
+                                  object_par$sim_w_lam,
+                                  object_par$sim_beta))
 
@@
              tru_values, colour = "red") +
-  facet_wrap(~name)
+  facet_wrap(~name, scales = "free")
 
 ```
+
+Similarly, we can check the degree parameters.
+
+```{r gamma-estimates}
+gamma_ests <- tibble()
+
+for(curr_sim in seq_along(sim_files)) {
+  load(paste0(sim_data_path,
+              sim_files[curr_sim]))
+
+  gamm_m2 <- sim_model3_stan_sim2 %>%
+    select(starts_with("gamma") ) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise(mean_est = median(value)) %>% 
+    mutate(model = "C-DCHP")
+
+  gamm_m3 <- sim_model3_stan_sim3 %>%
+    select(starts_with("gamma") ) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise(mean_est = median(value)) %>% 
+    mutate(model = "C-MMHP")
+
+  curr_sim_ests <- bind_rows(gamm_m2,
+                             gamm_m3)
+  gamma_ests <- gamma_ests %>% 
+    bind_rows(curr_sim_ests)
+}
+
+gamma_ests$model <- factor(gamma_ests$model, levels = c("C-HP",
+                                                    "C-DCHP",
+                                                    "C-MMHP"))
+
+tru_values <- tibble(name = paste0("gamma[", 1:num_nodes, "]"),
+                     mean_est = object_par$gamma_var)
+
+gamma_ests %>% 
+  ggplot(aes(name, mean_est)) +
+  geom_boxplot(aes(fill = model)) +
+  geom_hline(mapping = aes(yintercept = mean_est),
+             tru_values, colour = "red") +
+  facet_wrap(~name, scales = "free")
+```
+
+```{r gamma-estimates}
+zeta_ests <- tibble()
+
+for(curr_sim in seq_along(sim_files)) {
+  load(paste0(sim_data_path,
+              sim_files[curr_sim]))
+
+  zeta_m2 <- sim_model3_stan_sim2 %>%
+    select(starts_with("zeta") ) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise(mean_est = median(value)) %>% 
+    mutate(model = "C-DCHP")
+
+  zeta_m3 <- sim_model3_stan_sim3 %>%
+    select(starts_with("zeta") ) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise(mean_est = median(value)) %>% 
+    mutate(model = "C-MMHP")
+
+  curr_sim_ests <- bind_rows(zeta_m2,
+                             zeta_m3)
+  zeta_ests <- zeta_ests %>% 
+    bind_rows(curr_sim_ests)
+}
+
+zeta_ests$model <- factor(zeta_ests$model, levels = c("C-HP",
+                                                    "C-DCHP",
+                                                    "C-MMHP"))
+
+tru_values <- tibble(name = paste0("zeta[", 1:num_nodes, "]"),
+                     mean_est = object_par$zeta_var)
+
+zeta_ests %>% 
+  ggplot(aes(name, mean_est)) +
+  geom_boxplot(aes(fill = model)) +
+  geom_hline(mapping = aes(yintercept = mean_est),
+             tru_values, colour = "red") +
+  facet_wrap(~name, scales = "free")
+```

### 2021-08-13 output_scripts/Cohort_level_analysis.Rmd
first updates added for the first cohort

---
title: "Cohort Level Analysis"
author: "Owen G. Ward"
date: '`r Sys.Date()`'
output:
  html_document:
    # toc: true
    # toc_depth: 1
    number_sections: true
    # toc_float: true
    code_folding: hide
---

```{r setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.height = 5, fig.width = 7,
  warning = FALSE, cache = TRUE
)

slides_plots <- FALSE
extra_plots <- FALSE

revision_plots <- TRUE
original_plots <- FALSE
### original plots for plots which are no longer needed, 
### revision plots are what required

# current_cohort <- 5

# don't write to this path
data_path <- "../output/revisions/lapl_check/prior_check/"
no_eta_3_data_path <- "../output/revisions/lapl_check/ident_check/"
no_eta_1_data_path <- "../output/revisions/lapl_check/ident_check_no_eta1/"

func_dir <- "../lib/"

library(here)
# library(rstan)
library(cmdstanr)
Sys.setenv(LOCAL_CPPFLAGS = "-march=corei7 -mtune=corei7")
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(posterior)
library(bayesplot)
library(viridis)
library(here)
library(compete)
library(colorspace)
source(paste(func_dir, "naiveRankHierarchy.R", sep = ""))
source(paste(func_dir, "expertRankHierarchy.R", sep = ""))
source(paste(func_dir, "cleanData.R", sep = ""))
source(paste(func_dir, "prepareDataStan.R", sep = ""))
source(paste(func_dir, "inferLatentMmhp.R", sep = ""))
source(paste(func_dir, "plotUtil.R", sep = ""))
source(paste(func_dir, "mmhp.R", sep = ""))
source(paste(func_dir, "uniHawkes.R", sep = ""))
source(paste(func_dir, "simulatePrediction.R", sep = ""))
source(paste(func_dir, "myGlicko.R", sep = ""))
source(paste(func_dir, "matrixPlotParameter.R", sep = ""))
source(paste(func_dir, "residualStructureScore.R", sep = ""))
source(paste(func_dir, "drawIntensity.R", sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

cohort_names <- paste("cohort", c(9, 10, 12, 15, 16, 17, 18, 37, 38, 45),
                      sep = "")
cohort_short_names <- paste("C", c(9, 10, 12, 15, 16, 17, 18, 37, 38, 45),
                            sep = "")
cut_off <- 3
mice_number <- 12
col_df <- tibble(
  method = c(
    "I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
    "C-HP", "C-DCHP", "True", "C-MMHP"
  ),
  cols = viridis(9)
)
theme_set(theme_minimal())
```

```{r load rankings, echo=FALSE, results='hide', cache=TRUE}
full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
out <- captureOutput(for (curr_cohort in fit_cohorts) {
  naive_rank_10[[curr_cohort]] <-
    naiveRankHierarchy(full_data[[cohort_names[curr_cohort]]])
  expert_rank_10[[curr_cohort]] <-
    expertRankHierarchy(full_data[[cohort_names[curr_cohort]]])
})
```

```{r define_functions}
model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3) {
  return(eta1 * x * y * exp(-eta2 * abs(x - y)) / (1 +
    exp(-eta3 * (x - y))))
})

model3_fn <- list(
  alpha.fun = function(x, y, eta1, eta2) {
    return(eta1 * x * y * exp(-eta2 * abs(x - y)))
  },
  q1.fun = function(x, y, eta3) {
    return(exp(-eta3 * x))
  },
  q0.fun = function(x, y, eta3) {
    return(exp(-eta3 * y))
  }
)
```

```{r define_plot_functions}
print_total_events <- function(current_cohort) {
  cat(paste("Cohort ", current_cohort, "\n", sep = ""))
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  stan_input_lst <- prepareDataStan(current_cohort)

  pair_events <- apply(stan_input_lst$Nm, 1, sum)

  pair_matrix <- matrix(0, nrow = 12, ncol = 12)
  for(i in seq_along(pair_events)) {
    i_ind <- stan_input_lst$I_fit[i]
    j_ind <- stan_input_lst$J_fit[i]
    pair_matrix[i_ind, j_ind] <- pair_events[i]
  }
  # pair_matrix <- clean_data$N_count[expert_rank_10[[current_cohort]],
  #                                   expert_rank_10[[current_cohort]]]
  pair_matrix <- pair_matrix[expert_rank_10[[current_cohort]],
                    expert_rank_10[[current_cohort]]]
  colnames(pair_matrix) <- expert_rank_10[[current_cohort]]
  rownames(pair_matrix) <- expert_rank_10[[current_cohort]]
  print(pair_matrix)
}

total_events_active <- function(current_cohort) {
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  return_df <- cleanObservationPeriod(current_cohort,
                                      raw_df =
                     full_data[[cohort_names[current_cohort]]],
                                      clean_data
  )
  unique_pairs_df <- return_df %>%
    group_by(initiator, recipient) %>%
    dplyr::summarize(
      count = n(),
      observe = list(observe.id),
      observe.length = list(observe.time),
      no.events = list(no.events)
    )
  unique_observe_win <- unique(return_df[,
                                         c("observe.id", "observe.time")])
  load(paste(data_path, cohort_names[current_cohort],
             "/cmmhp_est_zt_", cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))
  total_event_array <- array(0,
                             dim = c(mice_number, mice_number,
                                     max(return_df$observe.id)))
  active_event_array <- array(0,
                              dim = c(mice_number, mice_number,
                                      max(return_df$observe.id)))

  for (i in 1:mice_number) {
    for (j in 1:mice_number) {
      if(i != j) {
        pair <- which(unique_pairs_df$initiator == i &
                        unique_pairs_df$recipient == j)
        if (length(pair) > 0) {
          current_window_vec <- unique_pairs_df$observe[[pair]]
          for (cur_win in current_window_vec) {
            row_indicator <- (return_df$initiator == i) &
              (return_df$recipient == j) &
              (return_df$observe.id == cur_win)
            total_event_array[i, j, cur_win] <-
              length(return_df[
                row_indicator,"event.times"][[1]])
            active_event_array[i, j, cur_win] <- sum(apply(2 -
                        state_array_list[[pair]][[cur_win]],
                                                           1, mean) > 0.5)
          }
        }
      }
    }
  }

  total_matrix <- apply(total_event_array, c(1,2), sum)
  active_matrix <- apply(active_event_array, c(1,2), sum)
  rm(interpolation_array_list)
  rm(initial_state_list)
  rm(termination_state_list)
  rm(state_array_list)
  return(active_matrix)
}

###
print_total_less_windows <- function(current_cohort) {
  cat(paste("Cohort ", current_cohort, "\n", sep = ""))
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  stan_input_lst <- prepareDataStan(current_cohort)

  pair_events <- apply(stan_input_lst$Nm, 1, sum) -
    rowSums(stan_input_lst$Nm != 0)

  pair_matrix <- matrix(0, nrow = 12, ncol = 12)
  for(i in seq_along(pair_events)) {
    i_ind <- stan_input_lst$I_fit[i]
    j_ind <- stan_input_lst$J_fit[i]
    pair_matrix[i_ind, j_ind] <- pair_events[i]
  }
  # pair_matrix <- clean_data$N_count[expert_rank_10[[current_cohort]],
  #                                   expert_rank_10[[current_cohort]]]
  pair_matrix <- pair_matrix[expert_rank_10[[current_cohort]],
                    expert_rank_10[[current_cohort]]]
  colnames(pair_matrix) <- expert_rank_10[[current_cohort]]
  rownames(pair_matrix) <- expert_rank_10[[current_cohort]]
  print(pair_matrix)
}

rankings_by_total <- function(current_cohort) {
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
             ))
  load(paste(data_path, cohort_names[current_cohort],
    "/agg_rank_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_hp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_dchp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count)

  no_method <- 4
  plot_latent_df <- data.frame(
    Methods = rep(1:no_method, each = 1000 * mice_number),
    Mice = rep(rep(1:mice_number, each = 1000), no_method),
    force = rep(0, 1000 * mice_number * no_method)
  )
  ## agg
  x_draws <- sim_agg_rank %>% select(starts_with("x"))
  plot_latent_df$force[(1:(1000 * mice_number))] <-
    as.vector(as.matrix(x_draws))

  ## M1
  f_draws <- sim_cohort_hp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) +
                         1000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  ## M2
  f_draws <- sim_cohort_dchp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) +
                         2000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  ## M3
  f_draws <- sim_cohort_mmhp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) +
                         3000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  plot_latent_df$Mice <- factor(plot_latent_df$Mice,
    levels = order(total_inter, decreasing = TRUE)
  )
  plot_latent_df$Method <- factor(plot_latent_df$Method,
    labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP")
  )
  plot_cols <- col_df %>%
  filter(method %in% c(
    "AggRank", "C-HP",
    "C-DCHP", "C-MMHP"
  )) %>%
  pull(cols)

  p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
    geom_boxplot(alpha = 0.7) +
    scale_fill_manual(values = plot_cols) +
    ggtitle("(a)") +
    theme_bw() +
    theme(
      plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
      text = element_text(size = 20),
      axis.text.x = element_text(size = 10),
      legend.position = "none"
    ) +
    facet_grid(cols = vars(Method)) +
    xlab("Mice (ranked by total interactions)") +
    ylab("Latent rank") +
    labs(title = paste("Cohort ", current_cohort, sep = ""))
  print(p1)
}

rankings_by_isi <- function(current_cohort){
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
             ))
  load(paste(data_path, cohort_names[current_cohort],
    "/agg_rank_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_hp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_dchp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count)

  no_method <- 4
  plot_latent_df <- data.frame(
    Methods = rep(1:no_method, each = 1000 * mice_number),
    Mice = rep(rep(1:mice_number, each = 1000), no_method),
    force = rep(0, 1000 * mice_number * no_method)
  )
  ## agg
  x_draws <- sim_agg_rank %>% select(starts_with("x"))
  plot_latent_df$force[(1:(1000 * mice_number))] <-
    as.vector(as.matrix(x_draws))

  ## M1
  f_draws <- sim_cohort_hp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) +
                         1000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  ## M2
  f_draws <- sim_cohort_dchp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) +
                         2000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  ## M3
  f_draws <- sim_cohort_mmhp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) +
                         3000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  plot_latent_df$Mice <- factor(plot_latent_df$Mice,
    levels = expert_rank_10[[current_cohort]]
  )
  plot_latent_df$Method <- factor(plot_latent_df$Method,
    labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP")
  )
  plot_cols <- col_df %>%
  filter(method %in% c(
    "AggRank", "C-HP",
    "C-DCHP", "C-MMHP"
  )) %>%
  pull(cols)

  p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
    geom_boxplot(alpha = 0.7) +
    scale_fill_manual(values = plot_cols) +
    ggtitle("(a)") +
    theme_bw() +
    theme(
      plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
      text = element_text(size = 20),
      axis.text.x = element_text(size = 10),
      legend.position = "none"
    ) +
    facet_grid(cols = vars(Method)) +
    xlab("Mice (ranked by I&SI)") +
    ylab("Latent rank") +
    labs(title = paste("Cohort ", current_cohort, sep = ""))
  print(p1)
}

rankings_by_cmmhp <- function(current_cohort) {
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
             "/agg_rank_stan_result_", cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
             "/cohort_hp_stan_result_", cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
             "/cohort_dchp_stan_result_", cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))
  total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count)

  no_method <- 4
  plot_latent_df <- data.frame(
    Methods = rep(1:no_method, each = 1000 * mice_number),
    Mice = rep(rep(1:mice_number, each = 1000), no_method),
    force = rep(0, 1000 * mice_number * no_method)
  )
  ## agg
  x_draws <- sim_agg_rank %>% select(starts_with("x"))
  plot_latent_df$force[(1:(1000 * mice_number))] <-
    as.vector(as.matrix(x_draws))

  ## M1
  f_draws <- sim_cohort_hp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) +
                         1000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  ## M2
  f_draws <- sim_cohort_dchp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) +
                         2000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  ## M3
  f_draws <- sim_cohort_mmhp %>% select(starts_with("f"))
  plot_latent_df$force[(1:(1000 * mice_number)) +
                         3000 * mice_number] <-
    as.vector(as.matrix(f_draws))

  ### get median from this
  cmmhp_rank <- f_draws %>% 
    pivot_longer(everything()) %>%
    group_by(name) %>%
    summarise(med_rank = median(value)) %>% 
    arrange(desc(med_rank)) %>% 
    pull(name)
  ## then just get the numbers
  m3_ranks <- str_extract(cmmhp_rank, pattern = "[:digit:]+")

  plot_latent_df$Mice <- factor(plot_latent_df$Mice,
                                levels = m3_ranks
  )
  plot_latent_df$Method <- factor(plot_latent_df$Method,
                                  labels = c("AggRanking",
                                             "C-HP",
                                             "C-DCHP",
                                             "C-MMHP")
  )
  plot_cols <- col_df %>%
    filter(method %in% c(
      "AggRank", "C-HP",
      "C-DCHP", "C-MMHP"
    )) %>%
    pull(cols)
  p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
    geom_boxplot(alpha = 0.7) +
    scale_fill_manual(values = plot_cols) +
    ggtitle("(a)") +
    theme_bw() +
    theme(
      plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
      text = element_text(size = 20),
      axis.text.x = element_text(size = 10),
      legend.position = "none"
    ) +
    facet_grid(cols = vars(Method)) +
    xlab("Mice (ranked by C-MMHP)") +
    ylab("Latent rank") +
    labs(title = paste("Cohort ", current_cohort, sep = ""))
  print(p1)
}

param_ests <- function(current_cohort){
  load(paste(data_path, cohort_names[current_cohort],
             "/cohort_hp_stan_result_", cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
             "/cohort_dchp_stan_result_", cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))

  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))
  plot_cols <- col_df %>%
    filter(method %in% c(
      "C-HP",
      "C-DCHP",
      "C-MMHP"
    )) %>%
    pull(cols)
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("eta") | starts_with("w_lam") |
             starts_with("beta")) %>%
    select(! ends_with("delta")) %>% 
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP") %>%
    bind_rows(sim_cohort_dchp %>%
                select(starts_with("eta") |
                         starts_with("w_lam") |
                         starts_with("beta")) %>%
                select(!ends_with("delta")) %>% 
                select(!ends_with("detla")) %>% 
                pivot_longer(everything()) %>%
                mutate(Model = "C-DCHP")) %>% 
    bind_rows(sim_cohort_hp %>%
                select(starts_with("eta") |
                         starts_with("w_lam") |
                         starts_with("beta")) %>%
                select(!ends_with("delta")) %>% 
                pivot_longer(everything()) %>%
                mutate(Model = "C-HP"))
  all_data$Model <- factor(all_data$Model,
                           levels = c("C-HP", "C-DCHP", "C-MMHP"))
  comp_plot <- ggplot(all_data, aes(name, value, fill = Model)) +
    geom_boxplot() +
    scale_fill_manual(values = plot_cols) +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "Estimated Model Parameters") +
    # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.text.x = element_blank()) +
    facet_wrap(~name, scales = "free")
  print(comp_plot)
  ###
  ## same for gamma
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("gamma")) %>%
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP") %>%
    bind_rows(sim_cohort_dchp %>%
                select(starts_with("gamma")) %>%
                pivot_longer(everything()) %>%
                mutate(Model = "C-DCHP"))
  all_data$Model <- factor(all_data$Model,
                           levels = c("C-HP", "C-DCHP", "C-MMHP"))
  all_data$name <- factor(all_data$name, 
                          levels = paste0("gamma[",1:12,"]"))
  comp_plot <- ggplot(all_data, aes(name, value, fill = Model)) +
    geom_boxplot() +
    scale_fill_manual(values = plot_cols[2:3]) +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "Out Degree Parameters", y = "Out Degree") +
    theme(axis.text.x = element_blank()) +
    facet_wrap(~name, scales = "free")
  print(comp_plot)
  ###
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("zeta") ) %>%
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP") %>%
    bind_rows(sim_cohort_dchp %>%
                select(starts_with("zeta")) %>%
                pivot_longer(everything()) %>%
                mutate(Model = "C-DCHP"))
  all_data$Model <- factor(all_data$Model,
                           levels = c("C-HP", "C-DCHP", "C-MMHP"))
  all_data$name <- factor(all_data$name, 
                          levels = paste0("zeta[",1:12,"]"))
  comp_plot <- ggplot(all_data, aes(name, value, fill = Model)) +
    geom_boxplot() +
    scale_fill_manual(values = plot_cols[2:3]) +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "In Degree Parameters", y = "In Degree") +
    facet_wrap(~name, scales = "free")
    # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  print(comp_plot)
}

```

# Results {.tabset .unnumbered #sec1}

## Cohort 1

```{r set_cohort}
current_cohort <- 1
```

### Total Events ordered by I&SI ranking

```{r total-events_1, message=FALSE}
print_total_events(current_cohort)
```

### Total Events less Number of Windows containing events ordered by I&SI

```{r total-events-less-active-windows, message=FALSE}
active_events <- total_events_active(current_cohort)
colnames(active_events) <- expert_rank_10[[current_cohort]]
rownames(active_events) <- expert_rank_10[[current_cohort]]
print(active_events)
```

### Correlation Matrices

### Inferred ranking ordered by I&SI score

```{r ranked-by-isi}
rankings_by_isi(current_cohort)
```

### Inferred ranking order by C-MMHP median ranking

```{r ranked-by-cmmhp}
rankings_by_cmmhp(current_cohort)
```

### Parameter Estimates

```{r param-ests, message=FALSE}
param_ests(current_cohort)
```

<!-- ## Cohort 2 -->

<!-- ```{r set_cohort-2} -->
<!-- current_cohort <- 2 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_2, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c2, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c2, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c2} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ## C 3  -->

<!-- ```{r set_cohort-3} -->
<!-- current_cohort <- 3 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_3, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c3, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c3, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c3} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3-c3, message=FALSE} -->
<!-- ests_without_eta_3(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1-c3, message=FALSE} -->
<!-- ests_without_eta_1(current_cohort) -->
<!-- ``` -->

<!-- ## C 4 -->

<!-- ```{r set_cohort-4} -->
<!-- current_cohort <- 4 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_4, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c4, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c4, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c4} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3-c4, message=FALSE} -->
<!-- ests_without_eta_3(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1-c4, message=FALSE} -->
<!-- ests_without_eta_1(current_cohort) -->
<!-- ``` -->

<!-- ## C 5 -->

<!-- ```{r set_cohort-5} -->
<!-- current_cohort <- 5 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_5, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c5, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c5, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c5} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3-c5, message=FALSE} -->
<!-- ests_without_eta_3(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1-c5, message=FALSE} -->
<!-- ests_without_eta_1(current_cohort) -->
<!-- ``` -->

<!-- ## C 6 -->

<!-- ```{r set_cohort-6} -->
<!-- current_cohort <- 6 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_6, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c6, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c6, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c6} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3-c6, message=FALSE} -->
<!-- ests_without_eta_3(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1-c6, message=FALSE} -->
<!-- ests_without_eta_1(current_cohort) -->
<!-- ``` -->

<!-- ## C 7 -->

<!-- ```{r set_cohort-7} -->
<!-- current_cohort <- 7 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_7, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c7, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c7, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c7} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3-c7, message=FALSE} -->
<!-- ests_without_eta_3(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1-c7, message=FALSE} -->
<!-- ests_without_eta_1(current_cohort) -->
<!-- ``` -->

<!-- ## C 8 -->

<!-- ```{r set_cohort-8} -->
<!-- current_cohort <- 8 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_8, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c8, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c8, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c8} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3-c8, message=FALSE} -->
<!-- ests_without_eta_3(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1-c8, message=FALSE} -->
<!-- ests_without_eta_1(current_cohort) -->
<!-- ``` -->

<!-- ## C 9 -->

<!-- ```{r set_cohort-9} -->
<!-- current_cohort <- 9 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_9, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c9, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c9, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c9} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3-c9, message=FALSE} -->
<!-- ests_without_eta_3(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1-c9, message=FALSE} -->
<!-- ests_without_eta_1(current_cohort) -->
<!-- ``` -->

<!-- ## C 10 -->

<!-- ```{r set_cohort-10} -->
<!-- current_cohort <- 10 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_10, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c10, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c10, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c10} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3-c10, message=FALSE} -->
<!-- ests_without_eta_3(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1-c10, message=FALSE} -->
<!-- ests_without_eta_1(current_cohort) -->
<!-- ``` -->

### 2021-08-18 output_scripts/Cohort_level_analysis.Rmd
current updates

@@
 
-slides_plots <- FALSE
-extra_plots <- FALSE
-
-revision_plots <- TRUE
-original_plots <- FALSE
-### original plots for plots which are no longer needed, 
-### revision plots are what required
-
-# current_cohort <- 5
+## cache_options for individual output types here? maybe?
+cache_table <- FALSE
+cache_corr <- FALSE
+cache_pars <- FALSE
 
 # don't write to this path
-data_path <- "../output/revisions/lapl_check/prior_check/"
-no_eta_3_data_path <- "../output/revisions/lapl_check/ident_check/"
-no_eta_1_data_path <- "../output/revisions/lapl_check/ident_check_no_eta1/"
+data_path <- "../output/revisions/aug_run/"
+
+options(digits = 3)
 
@@
 library(here)
+library(corrplot)
 library(compete)
+library(kableExtra)
 library(colorspace)
@@
 
-```{r load rankings, echo=FALSE, results='hide', cache=TRUE}
+```{css, echo=FALSE, cache=FALSE}
+.header-section-number {
+  display: none;
+}
+
+body {
+  counter-reset: counter-level-1;
+}
+
+h1:not(.title) {
+  counter-increment: counter-level-1;
+  counter-reset: counter-level-2;
+}
+
+h2 {
+  counter-increment: counter-level-1;
+  counter-increment: counter-level-2;
+  # counter-reset: counter-level-3;
+}
+
+h2::before {
+  counter-increment: counter-level-1;
+}
+
+h3 {
+  counter-increment: counter-level-3;
+  counter-increment: counter-level-2;
+}
+
+h3::before {
+  content: counter(counter-level-2) " ";
+}
+```
+
+```{r load rankings, echo=FALSE, results='hide'}
 full_data <- readRDS("../data/mice.RData")
@@
 
-###
 print_total_less_windows <- function(current_cohort) {
@@
                            levels = c("C-HP", "C-DCHP", "C-MMHP"))
+  w_lam_est <- all_data %>% 
+    filter(name == "w_lambda") %>% 
+    summarise(median(value)) %>% pull()
   comp_plot <- ggplot(all_data, aes(name, value, fill = Model)) +
@@
     pivot_longer(everything()) %>%
-    mutate(Model = "C-MMHP") %>%
+    mutate(Model = "C-MMHP",
+           value = value * w_lam_est) %>%
     bind_rows(sim_cohort_dchp %>%
@@
 
+fights_table <- function(current_cohort) {
+  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+  return_df <- cleanObservationPeriod(current_cohort,
+                                      raw_df =
+                                full_data[[cohort_names[current_cohort]]],
+                                      clean_data
+  )
+  total_events <- clean_data$N_count
+  active_events <- total_events_active(current_cohort)
+  active_out <- rowSums(active_events)
+  active_in <- colSums(active_events)
+  out_fights <- rowSums(total_events)
+  in_fights <- colSums(total_events)
+  fight_data <- tibble(node = 1:12,
+                       out_fights = out_fights,
+                       in_fights = in_fights,
+                       out_act_perc = active_out/out_fights,
+                       in_act_perc = active_in/in_fights)
+
+  isi_rank <- expert_rank_10[[current_cohort]]
+  # this orders from best to worst
+  ## load cmmhp rank
+  load(paste(data_path,
+             cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",
+             cohort_names[current_cohort],
+             ".RData",
+             sep = ""
+  ))
+  cmmhp_rank <- sim_cohort_mmhp %>% 
+    select(starts_with("f")) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise(cmmhp_rank = median(value))
+  out_degrees <- sim_cohort_mmhp %>% 
+    select(starts_with("gamma")) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise(out_degree = median(value)) %>% 
+    mutate(node = stringr::str_extract(name,
+                                       pattern = "[:digit:]+")) %>%
+    mutate(node = as.integer(node)) %>% 
+    select(node, out_degree)
+  in_degrees <- sim_cohort_mmhp %>% 
+    select(starts_with("zeta")) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise(in_degree = median(value)) %>% 
+    mutate(node = stringr::str_extract(name,
+                                       pattern = "[:digit:]+")) %>% 
+    mutate(node = as.integer(node)) %>% 
+    select(node, in_degree)
+  cmmhp_names <- stringr::str_extract(cmmhp_rank$name,
+                                      pattern = "[:digit:]+")
+  cmmhp_ranks <- tibble(node = cmmhp_names, 
+                        rank = cmmhp_rank$cmmhp_rank) %>% 
+    arrange(desc(rank)) %>% 
+    mutate(node = as.integer(node), num_rank_cmmhp = 1:12)
+  isi_ranks <- tibble(node = isi_rank, 
+                      num_rank_isi = 1:length(cmmhp_names))
+  ## don't need isi or cmmhp ranks here
+
+  summary_data <- fight_data %>% 
+    left_join(cmmhp_ranks, by = "node") %>% 
+    left_join(isi_ranks, by = "node") %>% 
+    left_join(out_degrees, by = "node") %>% 
+    left_join(in_degrees, by = "node") %>% 
+    # this will
+    mutate(isi_less_cmmhp = num_rank_isi - num_rank_cmmhp) %>% 
+    select(-c(rank,num_rank_isi, num_rank_cmmhp)) %>% 
+    pivot_longer(cols = out_fights:isi_less_cmmhp)
+
+  # knitr::kable(summary_data)
+  summary_data
+}
+
+corr_matrices <- function(current_cohort) {
+  load(paste(data_path,
+             cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",
+             cohort_names[current_cohort],
+             ".RData",
+             sep = ""
+  ))
+
+  m3_ranks <- sim_cohort_mmhp %>% 
+    select(starts_with("f")) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise("C-MMHP" = median(value))
+
+  load(paste(data_path,
+             cohort_names[current_cohort],
+             "/cohort_hp_stan_result_",
+             cohort_names[current_cohort],
+             ".RData",
+             sep = ""
+  ))
+
+  m1_ranks <- sim_cohort_hp %>% 
+    select(starts_with("f")) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise("C-HP" = median(value))
+
+  load(paste(data_path,
+             cohort_names[current_cohort],
+             "/cohort_dchp_stan_result_",
+             cohort_names[current_cohort],
+             ".RData",
+             sep = ""
+  ))
+
+  m2_ranks <- sim_cohort_dchp %>% 
+    select(starts_with("f")) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise("C-DCHP" = median(value))
+
+  ranks <- m1_ranks %>% 
+    left_join(m2_ranks, by = "name") %>% 
+    left_join(m3_ranks, by = "name")
+
+  cor_matrix <- cor(ranks[,2:4])
+  # col3 = colorRampPalette(c('red', 'white', 'blue'))
+  corrplot(cor_matrix,
+           type = "upper",
+           tl.col = "black",
+           col.lim = c(0,1),
+        title = "Pearson Correlation median ranks",
+        mar = c(0, 0, 1, 0), diag = FALSE)
+
+  ## same think for spearman rank correlation
+  m1_num <- m1_ranks %>% 
+    rename(value = "C-HP") %>% 
+    arrange(desc(value)) %>% 
+    mutate(chp = 1:12) %>% 
+    mutate(node = stringr::str_extract(name,
+                                       pattern = "[:digit:]+")) %>%
+    mutate(node = as.integer(node)) %>% 
+    select(node, chp)
+
+  m2_num <- m2_ranks %>% 
+    rename(value = "C-DCHP") %>% 
+    arrange(desc(value)) %>% 
+    mutate(cdchp = 1:12) %>% 
+    mutate(node = stringr::str_extract(name,
+                                       pattern = "[:digit:]+")) %>%
+    mutate(node = as.integer(node)) %>% 
+    select(node, cdchp)
+
+  m3_num <- m3_ranks %>% 
+    rename(value = "C-MMHP") %>% 
+    arrange(desc(value)) %>% 
+    mutate(cmmhp = 1:12) %>% 
+    mutate(node = stringr::str_extract(name,
+                                       pattern = "[:digit:]+")) %>%
+    mutate(node = as.integer(node)) %>% 
+    select(node, cmmhp)
+
+  isi_ranks <- tibble(node = expert_rank_10[[current_cohort]],
+                      isi = 1:12)
+  ###
+  rank_df <- m1_num %>% 
+    left_join(m2_num, by = "node") %>% 
+    left_join(m3_num, by = "node") %>% 
+    left_join(isi_ranks, by = "node")
+
+  spear_cor <- cor(rank_df[,2:5], method = "spearman")
+
+  corrplot(spear_cor,
+           type = "upper",
+           tl.col = "black",
+           col.lim = c(0,1),
+           title = "Spearman Rank Correlation",
+           mar = c(0, 0, 1, 0), diag = FALSE)
+}
 ```
@@
 
-## Cohort 1
+## Cohort 1 {-}
 
@@
 current_cohort <- 1
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+# the clean_data is handy for other intermediate analyses
 ```
@@
 
-### Total Events less Number of Windows containing events ordered by I&SI
+### Total Active Events ordered by I&SI
+
+Here all events which are classified as inactive by the C-MMHP model
+originate from the top ranked animal. As such there is strong
+agreement between the win/loss matrix of all events and
+those ocurring in active periods, with the 
+restriction to only active events
+slightly decreasing the 
+influence of the top ranked animal.
 
@@
 active_events <- total_events_active(current_cohort)
+active_events <- active_events[expert_rank_10[[current_cohort]],
+                               expert_rank_10[[current_cohort]]]
 colnames(active_events) <- expert_rank_10[[current_cohort]]
@@
 
+Examing the correlation matrices of both the median ranks for
+each of our cohort models and the Spearman rank correlations,
+we see that the C-HP most agrees with the I&SI ranking,
+with the C-DCHP and C-MMHP models showing progressively less agreement.
+
+```{r corr-plots, message=FALSE}
+corr_matrices(current_cohort)
+```
+
 ### Inferred ranking ordered by I&SI score
+
+We next plot the inferred posterior rank estimates from 
+each of our cohort models and the comparison AggRank model,
+where we order the animals by the estimated I&SI ranking.
 
@@
 
+Similarly, to show how this rank differs from that obtained by the C-MMHP
+model, we order the animals by the inferred ranking from that
+model.
+
 ```{r ranked-by-cmmhp}
@@
 
+For each of our three proposed models, we show the parameter
+estimates for the non rank parameters, including the in and
+out degree estimates for the models which incorporate degree
+corrections.
+
 ```{r param-ests, message=FALSE}
@@
 
-<!-- ## Cohort 2 -->
-
-<!-- ```{r set_cohort-2} -->
-<!-- current_cohort <- 2 -->
-<!-- ``` -->
-
-<!-- ### Total Events ordered by I&SI ranking -->
-
-<!-- ```{r total-events_2, message=FALSE} -->
-<!-- print_total_events(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->
-
-<!-- ```{r total-events-less-active-windows-c2, message=FALSE} -->
-<!-- print_total_less_windows(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Inferred ranking, ordered by total interactions -->
-
-<!-- ```{r all-4-models-c2, warning=FALSE} -->
-<!-- rankings_by_total(current_cohort) -->
-<!-- ``` -->
-
-<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
-<!-- <!-- I&SI score instead. -->
-
-<!-- ### Inferred ranking ordered by I&SI score -->
-
-<!-- ```{r ranked-by-isi-c2} -->
-<!-- rankings_by_isi(current_cohort) -->
-<!-- ``` -->
-
-<!-- ## C 3  -->
-
-<!-- ```{r set_cohort-3} -->
-<!-- current_cohort <- 3 -->
-<!-- ``` -->
-
-<!-- ### Total Events ordered by I&SI ranking -->
-
-<!-- ```{r total-events_3, message=FALSE} -->
-<!-- print_total_events(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->
-
-<!-- ```{r total-events-less-active-windows-c3, message=FALSE} -->
-<!-- print_total_less_windows(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Inferred ranking, ordered by total interactions -->
-
-<!-- ```{r all-4-models-c3, warning=FALSE} -->
-<!-- rankings_by_total(current_cohort) -->
-<!-- ``` -->
-
-<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
-<!-- <!-- I&SI score instead. -->
-
-<!-- ### Inferred ranking ordered by I&SI score -->
-
-<!-- ```{r ranked-by-isi-c3} -->
-<!-- rankings_by_isi(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_3 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta3-c3, message=FALSE} -->
-<!-- ests_without_eta_3(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_1 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta-1-c3, message=FALSE} -->
-<!-- ests_without_eta_1(current_cohort) -->
-<!-- ``` -->
-
-<!-- ## C 4 -->
-
-<!-- ```{r set_cohort-4} -->
-<!-- current_cohort <- 4 -->
-<!-- ``` -->
-
-<!-- ### Total Events ordered by I&SI ranking -->
-
-<!-- ```{r total-events_4, message=FALSE} -->
-<!-- print_total_events(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->
-
-<!-- ```{r total-events-less-active-windows-c4, message=FALSE} -->
-<!-- print_total_less_windows(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Inferred ranking, ordered by total interactions -->
-
-<!-- ```{r all-4-models-c4, warning=FALSE} -->
-<!-- rankings_by_total(current_cohort) -->
-<!-- ``` -->
-
-<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
-<!-- <!-- I&SI score instead. -->
-
-<!-- ### Inferred ranking ordered by I&SI score -->
-
-<!-- ```{r ranked-by-isi-c4} -->
-<!-- rankings_by_isi(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_3 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta3-c4, message=FALSE} -->
-<!-- ests_without_eta_3(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_1 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta-1-c4, message=FALSE} -->
-<!-- ests_without_eta_1(current_cohort) -->
-<!-- ``` -->
-
-<!-- ## C 5 -->
-
-<!-- ```{r set_cohort-5} -->
-<!-- current_cohort <- 5 -->
-<!-- ``` -->
-
-<!-- ### Total Events ordered by I&SI ranking -->
-
-<!-- ```{r total-events_5, message=FALSE} -->
-<!-- print_total_events(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->
-
-<!-- ```{r total-events-less-active-windows-c5, message=FALSE} -->
-<!-- print_total_less_windows(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Inferred ranking, ordered by total interactions -->
-
-<!-- ```{r all-4-models-c5, warning=FALSE} -->
-<!-- rankings_by_total(current_cohort) -->
-<!-- ``` -->
-
-<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
-<!-- <!-- I&SI score instead. -->
-
-<!-- ### Inferred ranking ordered by I&SI score -->
-
-<!-- ```{r ranked-by-isi-c5} -->
-<!-- rankings_by_isi(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_3 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta3-c5, message=FALSE} -->
-<!-- ests_without_eta_3(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_1 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta-1-c5, message=FALSE} -->
-<!-- ests_without_eta_1(current_cohort) -->
-<!-- ``` -->
-
-<!-- ## C 6 -->
-
-<!-- ```{r set_cohort-6} -->
-<!-- current_cohort <- 6 -->
-<!-- ``` -->
-
-<!-- ### Total Events ordered by I&SI ranking -->
-
-<!-- ```{r total-events_6, message=FALSE} -->
-<!-- print_total_events(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->
-
-<!-- ```{r total-events-less-active-windows-c6, message=FALSE} -->
-<!-- print_total_less_windows(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Inferred ranking, ordered by total interactions -->
-
-<!-- ```{r all-4-models-c6, warning=FALSE} -->
-<!-- rankings_by_total(current_cohort) -->
-<!-- ``` -->
-
-<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
-<!-- <!-- I&SI score instead. -->
-
-<!-- ### Inferred ranking ordered by I&SI score -->
-
-<!-- ```{r ranked-by-isi-c6} -->
-<!-- rankings_by_isi(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_3 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta3-c6, message=FALSE} -->
-<!-- ests_without_eta_3(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_1 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta-1-c6, message=FALSE} -->
-<!-- ests_without_eta_1(current_cohort) -->
-<!-- ``` -->
-
-<!-- ## C 7 -->
-
-<!-- ```{r set_cohort-7} -->
-<!-- current_cohort <- 7 -->
-<!-- ``` -->
-
-<!-- ### Total Events ordered by I&SI ranking -->
-
-<!-- ```{r total-events_7, message=FALSE} -->
-<!-- print_total_events(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->
-
-<!-- ```{r total-events-less-active-windows-c7, message=FALSE} -->
-<!-- print_total_less_windows(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Inferred ranking, ordered by total interactions -->
-
-<!-- ```{r all-4-models-c7, warning=FALSE} -->
-<!-- rankings_by_total(current_cohort) -->
-<!-- ``` -->
-
-<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
-<!-- <!-- I&SI score instead. -->
-
-<!-- ### Inferred ranking ordered by I&SI score -->
-
-<!-- ```{r ranked-by-isi-c7} -->
-<!-- rankings_by_isi(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_3 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta3-c7, message=FALSE} -->
-<!-- ests_without_eta_3(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_1 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta-1-c7, message=FALSE} -->
-<!-- ests_without_eta_1(current_cohort) -->
-<!-- ``` -->
-
-<!-- ## C 8 -->
-
-<!-- ```{r set_cohort-8} -->
-<!-- current_cohort <- 8 -->
-<!-- ``` -->
-
-<!-- ### Total Events ordered by I&SI ranking -->
-
-<!-- ```{r total-events_8, message=FALSE} -->
-<!-- print_total_events(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->
-
-<!-- ```{r total-events-less-active-windows-c8, message=FALSE} -->
-<!-- print_total_less_windows(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Inferred ranking, ordered by total interactions -->
-
-<!-- ```{r all-4-models-c8, warning=FALSE} -->
-<!-- rankings_by_total(current_cohort) -->
-<!-- ``` -->
-
-<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
-<!-- <!-- I&SI score instead. -->
-
-<!-- ### Inferred ranking ordered by I&SI score -->
-
-<!-- ```{r ranked-by-isi-c8} -->
-<!-- rankings_by_isi(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_3 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta3-c8, message=FALSE} -->
-<!-- ests_without_eta_3(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_1 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta-1-c8, message=FALSE} -->
-<!-- ests_without_eta_1(current_cohort) -->
-<!-- ``` -->
-
-<!-- ## C 9 -->
-
-<!-- ```{r set_cohort-9} -->
-<!-- current_cohort <- 9 -->
-<!-- ``` -->
-
-<!-- ### Total Events ordered by I&SI ranking -->
-
-<!-- ```{r total-events_9, message=FALSE} -->
-<!-- print_total_events(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->
-
-<!-- ```{r total-events-less-active-windows-c9, message=FALSE} -->
-<!-- print_total_less_windows(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Inferred ranking, ordered by total interactions -->
-
-<!-- ```{r all-4-models-c9, warning=FALSE} -->
-<!-- rankings_by_total(current_cohort) -->
-<!-- ``` -->
-
-<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
-<!-- <!-- I&SI score instead. -->
-
-<!-- ### Inferred ranking ordered by I&SI score -->
-
-<!-- ```{r ranked-by-isi-c9} -->
-<!-- rankings_by_isi(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_3 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta3-c9, message=FALSE} -->
-<!-- ests_without_eta_3(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_1 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta-1-c9, message=FALSE} -->
-<!-- ests_without_eta_1(current_cohort) -->
-<!-- ``` -->
-
-<!-- ## C 10 -->
-
-<!-- ```{r set_cohort-10} -->
-<!-- current_cohort <- 10 -->
-<!-- ``` -->
-
-<!-- ### Total Events ordered by I&SI ranking -->
-
-<!-- ```{r total-events_10, message=FALSE} -->
-<!-- print_total_events(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->
-
-<!-- ```{r total-events-less-active-windows-c10, message=FALSE} -->
-<!-- print_total_less_windows(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Inferred ranking, ordered by total interactions -->
-
-<!-- ```{r all-4-models-c10, warning=FALSE} -->
-<!-- rankings_by_total(current_cohort) -->
-<!-- ``` -->
-
-<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
-<!-- <!-- I&SI score instead. -->
-
-<!-- ### Inferred ranking ordered by I&SI score -->
-
-<!-- ```{r ranked-by-isi-c10} -->
-<!-- rankings_by_isi(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_3 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta3-c10, message=FALSE} -->
-<!-- ests_without_eta_3(current_cohort) -->
-<!-- ``` -->
-
-<!-- ### Compare parameter estimates with/without eta_1 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta-1-c10, message=FALSE} -->
-<!-- ests_without_eta_1(current_cohort) -->
-<!-- ``` -->
+### Summary Table
+
+Finally, for each animal in this cohort, we summarise
+
+```{r summ_tabls, message=FALSE}
+c1_summ <- fights_table(current_cohort)
+# c1_summ %>% 
+#   kbl() %>% 
+#   kable_styling()
+
+c1_summ %>% 
+  pivot_wider(id_cols = node) %>% 
+  rename(out_deg = out_degree, in_deg = in_degree,
+         "Out Events" = out_fights,
+         "In Events" = in_fights,
+         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
+         "Out Degree" = out_degree,
+         "In Degree" = in_degree,
+         "I&SI to C-MMHP change" = isi_less_cmmhp,
+         "Animal" = node) %>% 
+  kbl() %>% 
+  kable_styling()
+```
+
+## Cohort 2 {-}
+
+```{r set_cohort2}
+current_cohort <- 2
+```
+
+### Total Events ordered by I&SI ranking
+
+```{r total-events_2, message=FALSE}
+print_total_events(current_cohort)
+```
+
+### Total Active Events ordered by I&SI
+
+```{r total-events-less-active-windows2, message=FALSE}
+active_events <- total_events_active(current_cohort)
+active_events <- active_events[expert_rank_10[[current_cohort]],
+                               expert_rank_10[[current_cohort]]]
+colnames(active_events) <- expert_rank_10[[current_cohort]]
+rownames(active_events) <- expert_rank_10[[current_cohort]]
+print(active_events)
+```
+
+### Correlation Matrices
+
+```{r corr-plots2, message=FALSE}
+corr_matrices(current_cohort)
+```
+
+### Inferred ranking ordered by I&SI score
+
+```{r ranked-by-isi2}
+rankings_by_isi(current_cohort)
+```
+
+### Inferred ranking order by C-MMHP median ranking
+
+```{r ranked-by-cmmhp2}
+rankings_by_cmmhp(current_cohort)
+```
+
+### Parameter Estimates
+
+```{r param-ests2, message=FALSE}
+param_ests(current_cohort)
+```
+
+### Summary Table
+
+```{r summ_tabls2, message=FALSE}
+c2_summ <- fights_table(current_cohort)
+
+c2_summ %>% 
+  pivot_wider(id_cols = node) %>% 
+  rename(out_deg = out_degree, in_deg = in_degree,
+         "Out Events" = out_fights,
+         "In Events" = in_fights,
+         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
+         "Out Degree" = out_degree,
+         "In Degree" = in_degree,
+         "I&SI to C-MMHP change" = isi_less_cmmhp,
+         "Animal" = node) %>% 
+  kbl() %>% 
+  kable_styling()
+```
+
+## Cohort 3 {-}
+
+```{r set_cohort3}
+current_cohort <- 3
+```
+
+### Total Events ordered by I&SI ranking
+
+```{r total-events_3, message=FALSE}
+print_total_events(current_cohort)
+```
+
+### Total Active Events ordered by I&SI
+
+```{r total-events-less-active-windows3, message=FALSE}
+active_events <- total_events_active(current_cohort)
+active_events <- active_events[expert_rank_10[[current_cohort]],
+                               expert_rank_10[[current_cohort]]]
+colnames(active_events) <- expert_rank_10[[current_cohort]]
+rownames(active_events) <- expert_rank_10[[current_cohort]]
+print(active_events)
+```
+
+### Correlation Matrices
+
+```{r corr-plots3, message=FALSE}
+corr_matrices(current_cohort)
+```
+
+### Inferred ranking ordered by I&SI score
+
+```{r ranked-by-isi3}
+rankings_by_isi(current_cohort)
+```
+
+### Inferred ranking order by C-MMHP median ranking
+
+```{r ranked-by-cmmhp3}
+rankings_by_cmmhp(current_cohort)
+```
+
+### Parameter Estimates
+
+```{r param-ests3, message=FALSE}
+param_ests(current_cohort)
+```
+
+### Summary Table
+
+```{r summ_tabls3, message=FALSE}
+c3_summ <- fights_table(current_cohort)
+
+c3_summ %>% 
+  pivot_wider(id_cols = node) %>% 
+  rename(out_deg = out_degree, in_deg = in_degree,
+         "Out Events" = out_fights,
+         "In Events" = in_fights,
+         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
+         "Out Degree" = out_degree,
+         "In Degree" = in_degree,
+         "I&SI to C-MMHP change" = isi_less_cmmhp,
+         "Animal" = node) %>% 
+  kbl() %>% 
+  kable_styling()
+```
+
+## Cohort 4 {-}
+
+```{r set_cohort4}
+current_cohort <- 4
+```
+
+### Total Events ordered by I&SI ranking
+
+```{r total-events_4, message=FALSE}
+print_total_events(current_cohort)
+```
+
+### Total Active Events ordered by I&SI
+
+```{r total-events-less-active-windows4, message=FALSE}
+active_events <- total_events_active(current_cohort)
+active_events <- active_events[expert_rank_10[[current_cohort]],
+                               expert_rank_10[[current_cohort]]]
+colnames(active_events) <- expert_rank_10[[current_cohort]]
+rownames(active_events) <- expert_rank_10[[current_cohort]]
+print(active_events)
+```
+
+### Correlation Matrices
+
+```{r corr-plots4, message=FALSE}
+corr_matrices(current_cohort)
+```
+
+### Inferred ranking ordered by I&SI score
+
+```{r ranked-by-isi4}
+rankings_by_isi(current_cohort)
+```
+
+### Inferred ranking order by C-MMHP median ranking
+
+```{r ranked-by-cmmhp4}
+rankings_by_cmmhp(current_cohort)
+```
+
+### Parameter Estimates
+
+```{r param-ests4, message=FALSE}
+param_ests(current_cohort)
+```
+
+### Summary Table
+
+```{r summ_tabls4, message=FALSE}
+c4_summ <- fights_table(current_cohort)
+
+c4_summ %>% 
+  pivot_wider(id_cols = node) %>% 
+  rename(out_deg = out_degree, in_deg = in_degree,
+         "Out Events" = out_fights,
+         "In Events" = in_fights,
+         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
+         "Out Degree" = out_degree,
+         "In Degree" = in_degree,
+         "I&SI to C-MMHP change" = isi_less_cmmhp,
+         "Animal" = node) %>% 
+  kbl() %>% 
+  kable_styling()
+```
+
+## Cohort 5 {-}
+
+```{r set_cohort5}
+current_cohort <- 5
+```
+
+### Total Events ordered by I&SI ranking
+
+```{r total-events_5, message=FALSE}
+print_total_events(current_cohort)
+```
+
+### Total Active Events ordered by I&SI
+
+```{r total-events-less-active-windows5, message=FALSE}
+active_events <- total_events_active(current_cohort)
+active_events <- active_events[expert_rank_10[[current_cohort]],
+                               expert_rank_10[[current_cohort]]]
+
+colnames(active_events) <- expert_rank_10[[current_cohort]]
+rownames(active_events) <- expert_rank_10[[current_cohort]]
+print(active_events)
+```
+
+### Correlation Matrices
+
+```{r corr-plots5, message=FALSE}
+corr_matrices(current_cohort)
+```
+
+### Inferred ranking ordered by I&SI score
+
+```{r ranked-by-isi5}
+rankings_by_isi(current_cohort)
+```
+
+### Inferred ranking order by C-MMHP median ranking
+
+```{r ranked-by-cmmhp5}
+rankings_by_cmmhp(current_cohort)
+```
+
+### Parameter Estimates
+
+```{r param-ests5, message=FALSE}
+param_ests(current_cohort)
+```
+
+### Summary Table
+
+```{r summ_tabls5, message=FALSE}
+c5_summ <- fights_table(current_cohort)
+
+c5_summ %>% 
+  pivot_wider(id_cols = node) %>% 
+  rename(out_deg = out_degree, in_deg = in_degree,
+         "Out Events" = out_fights,
+         "In Events" = in_fights,
+         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
+         "Out Degree" = out_degree,
+         "In Degree" = in_degree,
+         "I&SI to C-MMHP change" = isi_less_cmmhp,
+         "Animal" = node) %>% 
+  kbl() %>% 
+  kable_styling()
+```
+
+## Cohort 6 {-}
+
+```{r set_cohort6}
+current_cohort <- 6
+```
+
+### Total Events ordered by I&SI ranking
+
+```{r total-events_6, message=FALSE}
+print_total_events(current_cohort)
+```
+
+### Total Active Events ordered by I&SI
+
+```{r total-events-less-active-windows6, message=FALSE}
+active_events <- total_events_active(current_cohort)
+active_events <- active_events[expert_rank_10[[current_cohort]],
+                               expert_rank_10[[current_cohort]]]
+
+colnames(active_events) <- expert_rank_10[[current_cohort]]
+rownames(active_events) <- expert_rank_10[[current_cohort]]
+print(active_events)
+```
+
+### Correlation Matrices
+
+```{r corr-plots6, message=FALSE}
+corr_matrices(current_cohort)
+```
+
+### Inferred ranking ordered by I&SI score
+
+```{r ranked-by-isi6}
+rankings_by_isi(current_cohort)
+```
+
+### Inferred ranking order by C-MMHP median ranking
+
+```{r ranked-by-cmmhp6}
+rankings_by_cmmhp(current_cohort)
+```
+
+### Parameter Estimates
+
+```{r param-ests6, message=FALSE}
+param_ests(current_cohort)
+```
+
+### Summary Table
+
+```{r summ_tabls6, message=FALSE}
+c6_summ <- fights_table(current_cohort)
+
+c6_summ %>% 
+  pivot_wider(id_cols = node) %>% 
+  rename(out_deg = out_degree, in_deg = in_degree,
+         "Out Events" = out_fights,
+         "In Events" = in_fights,
+         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
+         "Out Degree" = out_degree,
+         "In Degree" = in_degree,
+         "I&SI to C-MMHP change" = isi_less_cmmhp,
+         "Animal" = node) %>% 
+  kbl() %>% 
+  kable_styling()
+
+```
+
+## Cohort 7 {-}
+
+```{r set_cohort7}
+current_cohort <- 7
+```
+
+### Total Events ordered by I&SI ranking
+
+```{r total-events_7, message=FALSE}
+print_total_events(current_cohort)
+```
+
+### Total Active Events ordered by I&SI
+
+```{r total-events-less-active-windows7, message=FALSE}
+active_events <- total_events_active(current_cohort)
+active_events <- active_events[expert_rank_10[[current_cohort]],
+                               expert_rank_10[[current_cohort]]]
+
+colnames(active_events) <- expert_rank_10[[current_cohort]]
+rownames(active_events) <- expert_rank_10[[current_cohort]]
+print(active_events)
+```
+
+### Correlation Matrices
+
+```{r corr-plots7, message=FALSE}
+corr_matrices(current_cohort)
+```
+
+### Inferred ranking ordered by I&SI score
+
+```{r ranked-by-isi7}
+rankings_by_isi(current_cohort)
+```
+
+### Inferred ranking order by C-MMHP median ranking
+
+```{r ranked-by-cmmhp7}
+rankings_by_cmmhp(current_cohort)
+```
+
+### Parameter Estimates
+
+```{r param-ests7, message=FALSE}
+param_ests(current_cohort)
+```
+
+### Summary Table
+
+```{r summ_tabls7, message=FALSE}
+c7_summ <- fights_table(current_cohort)
+c7_summ %>% 
+  pivot_wider(id_cols = node) %>% 
+  rename(out_deg = out_degree, in_deg = in_degree,
+         "Out Events" = out_fights,
+         "In Events" = in_fights,
+         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
+         "Out Degree" = out_degree,
+         "In Degree" = in_degree,
+         "I&SI to C-MMHP change" = isi_less_cmmhp,
+         "Animal" = node) %>% 
+  kbl() %>% 
+  kable_styling()
+```
+
+## Cohort 8 {-}
+
+```{r set_cohort8}
+current_cohort <- 8
+```
+
+### Total Events ordered by I&SI ranking
+
+```{r total-events_8, message=FALSE}
+print_total_events(current_cohort)
+```
+
+### Total Active Events ordered by I&SI
+
+```{r total-events-less-active-windows8, message=FALSE}
+active_events <- total_events_active(current_cohort)
+active_events <- active_events[expert_rank_10[[current_cohort]],
+                               expert_rank_10[[current_cohort]]]
+
+colnames(active_events) <- expert_rank_10[[current_cohort]]
+rownames(active_events) <- expert_rank_10[[current_cohort]]
+print(active_events)
+```
+
+### Correlation Matrices
+
+```{r corr-plots8, message=FALSE}
+corr_matrices(current_cohort)
+```
+
+### Inferred ranking ordered by I&SI score
+
+```{r ranked-by-isi8}
+rankings_by_isi(current_cohort)
+```
+
+### Inferred ranking order by C-MMHP median ranking
+
+```{r ranked-by-cmmhp8}
+rankings_by_cmmhp(current_cohort)
+```
+
+### Parameter Estimates
+
+```{r param-ests8, message=FALSE}
+param_ests(current_cohort)
+```
+
+### Summary Table
+
+```{r summ_tabls8, message=FALSE}
+c8_summ <- fights_table(current_cohort)
+
+c8_summ %>% 
+  pivot_wider(id_cols = node) %>% 
+  rename(out_deg = out_degree, in_deg = in_degree,
+         "Out Events" = out_fights,
+         "In Events" = in_fights,
+         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
+         "Out Degree" = out_degree,
+         "In Degree" = in_degree,
+         "I&SI to C-MMHP change" = isi_less_cmmhp,
+         "Animal" = node) %>% 
+  kbl() %>% 
+  kable_styling()
+```
+
+## Cohort 9 {-}
+
+```{r set_cohort9}
+current_cohort <- 9
+```
+
+### Total Events ordered by I&SI ranking
+
+```{r total-events_9, message=FALSE}
+print_total_events(current_cohort)
+```
+
+### Total Active Events ordered by I&SI
+
+```{r total-events-less-active-windows9, message=FALSE}
+active_events <- total_events_active(current_cohort)
+active_events <- active_events[expert_rank_10[[current_cohort]],
+                               expert_rank_10[[current_cohort]]]
+
+colnames(active_events) <- expert_rank_10[[current_cohort]]
+rownames(active_events) <- expert_rank_10[[current_cohort]]
+print(active_events)
+```
+
+### Correlation Matrices
+
+```{r corr-plots9, message=FALSE}
+corr_matrices(current_cohort)
+```
+
+### Inferred ranking ordered by I&SI score
+
+```{r ranked-by-isi9}
+rankings_by_isi(current_cohort)
+```
+
+### Inferred ranking order by C-MMHP median ranking
+
+```{r ranked-by-cmmhp9}
+rankings_by_cmmhp(current_cohort)
+```
+
+### Parameter Estimates
+
+```{r param-ests9, message=FALSE}
+param_ests(current_cohort)
+```
+
+### Summary Table
+
+```{r summ_tabls9, message=FALSE}
+c9_summ <-fights_table(current_cohort)
+
+c9_summ %>% 
+  pivot_wider(id_cols = node) %>% 
+  rename(out_deg = out_degree, in_deg = in_degree,
+         "Out Events" = out_fights,
+         "In Events" = in_fights,
+         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
+         "Out Degree" = out_degree,
+         "In Degree" = in_degree,
+         "I&SI to C-MMHP change" = isi_less_cmmhp,
+         "Animal" = node) %>% 
+  kbl() %>% 
+  kable_styling()
+```
+
+## Cohort 10 {-}
+
+```{r set_cohort10}
+current_cohort <- 10
+```
+
+### Total Events ordered by I&SI ranking
+
+```{r total-events_10, message=FALSE}
+print_total_events(current_cohort)
+```
+
+### Total Active Events ordered by I&SI
+
+```{r total-events-less-active-windows10, message=FALSE}
+active_events <- total_events_active(current_cohort)
+active_events <- active_events[expert_rank_10[[current_cohort]],
+                               expert_rank_10[[current_cohort]]]
+
+colnames(active_events) <- expert_rank_10[[current_cohort]]
+rownames(active_events) <- expert_rank_10[[current_cohort]]
+print(active_events)
+```
+
+### Correlation Matrices
+
+```{r corr-plots10, message=FALSE}
+corr_matrices(current_cohort)
+```
+
+### Inferred ranking ordered by I&SI score
+
+```{r ranked-by-isi10}
+rankings_by_isi(current_cohort)
+```
+
+### Inferred ranking order by C-MMHP median ranking
+
+```{r ranked-by-cmmhp10}
+rankings_by_cmmhp(current_cohort)
+```
+
+### Parameter Estimates
+
+```{r param-ests10, message=FALSE}
+param_ests(current_cohort)
+```
+
+### Summary Table
+
+```{r summ_tabls10, message=FALSE}
+c10_summ <- fights_table(current_cohort)
+
+c10_summ %>% 
+  pivot_wider(id_cols = node) %>% 
+  rename(out_deg = out_degree, in_deg = in_degree,
+         "Out Events" = out_fights,
+         "In Events" = in_fights,
+         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
+         "Out Degree" = out_degree,
+         "In Degree" = in_degree,
+         "I&SI to C-MMHP change" = isi_less_cmmhp,
+         "Animal" = node) %>% 
+  kbl() %>% 
+  kable_styling()
+```
+
+## All Correlation Plots {-}
+
+```{r all-corr-plots}
+for(current_cohort in 1:10) {
+  cat(paste("Cohort", current_cohort, "\n", sep = " "))
+  cat("======== \n")
+  corr_matrices(current_cohort)
+}
+```
+
+## Summary Data {-}
+
+### Degree Parameters
+
+```{r get-all-cmmhp-degrees, message=FALSE}
+cmmhp_gamma <- tibble()
+cmmhp_zeta <- tibble()
+out_perc <- tibble()
+in_perc <- tibble()
+
+### there is something up with the cohorts here, not correct!
+
+for(current_cohort in 1:10) {
+  ### get perc for each one here
+  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+  out_fights <- tibble(name = paste0("gamma[",1:12,"]"),
+                       perc_out = rowSums(clean_data$N_count)/
+                         sum(clean_data$N_count)) %>% 
+    mutate(perc_out = round(perc_out, 2),
+           cohort = paste0("Cohort_", current_cohort))
+  in_fights <- tibble(name = paste0("zeta[",1:12,"]"),
+                       perc_in = colSums(clean_data$N_count)/
+                         sum(clean_data$N_count)) %>% 
+    mutate(perc_in = round(perc_in, 2),
+           cohort = paste0("Cohort_", current_cohort))
+  ###
+  load(paste(data_path,
+             cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",
+             cohort_names[current_cohort],
+             ".RData",
+             sep = ""
+  ))
+  # plot_cols <- col_df %>%
+  #   filter(method %in% c(
+  #     "C-HP",
+  #     "C-DCHP",
+  #     "C-MMHP"
+  #   )) %>%
+  #   pull(cols)
+  all_data <- sim_cohort_mmhp %>%
+    select(starts_with("gamma") ) %>% 
+    pivot_longer(everything()) %>%
+    mutate(Model = "C-MMHP", cohort = paste0("Cohort_", current_cohort)) 
+  out_perc <- out_perc %>% 
+    bind_rows(out_fights)
+  in_perc <- in_perc %>% 
+    bind_rows(in_fights)
+  cmmhp_gamma <- cmmhp_gamma %>% 
+    bind_rows(all_data)
+  all_data <- sim_cohort_mmhp %>%
+    select(starts_with("zeta") ) %>% 
+    pivot_longer(everything()) %>%
+    mutate(Model = "C-MMHP", cohort = paste0("Cohort_", current_cohort)) 
+  cmmhp_zeta <- cmmhp_zeta %>% 
+    bind_rows(all_data)
+}
+
+cmmhp_gamma$name <- stringr::str_extract(cmmhp_gamma$name, 
+                                         pattern = "[:digit:]+")
+cmmhp_zeta$name <- stringr::str_extract(cmmhp_zeta$name, 
+                                         pattern = "[:digit:]+")
+
+out_perc$name <- stringr::str_extract(out_perc$name, 
+                                         pattern = "[:digit:]+")
+in_perc$name <- stringr::str_extract(in_perc$name, 
+                                         pattern = "[:digit:]+")
+
+out_perc$name <- factor(out_perc$name,
+                           levels = as.character(1:12))
+in_perc$name <- factor(in_perc$name,
+                           levels = as.character(1:12))
+
+out_perc$Model <- "C-MMHP"
+in_perc$Model <- "C-MMHP"
+
+max_out <- cmmhp_gamma %>% 
+  group_by(name, cohort) %>% 
+  summarise(max_est = max(value))
+
+max_in <- cmmhp_zeta %>% 
+  group_by(name, cohort) %>% 
+  summarise(max_est = max(value))
+
+out_perc <- out_perc %>% 
+  left_join(max_out, by = c("name", "cohort"))
+
+in_perc <- in_perc %>% 
+  left_join(max_out, by = c("name", "cohort"))
+
+cmmhp_gamma$name <- factor(cmmhp_gamma$name,
+                           levels = as.character(1:12))
+cmmhp_zeta$name <- factor(cmmhp_zeta$name,
+                           levels = as.character(1:12))
+# plot_cols
+cmmhp_gamma$cohort <- factor(cmmhp_gamma$cohort, 
+                             levels = paste0("Cohort_", 1:10))
+cmmhp_zeta$cohort <- factor(cmmhp_zeta$cohort, 
+                             levels = paste0("Cohort_", 1:10))
+
+cmmhp_gamma %>% 
+  ggplot(aes(name, value, fill = Model)) +
+  geom_boxplot() +
+  scale_fill_manual(values = "#FDE725FF") +
+  facet_wrap(~cohort, scales = "free", ncol = 2) +
+  geom_text(data = out_perc, aes(name, max_est + 0.25, label = perc_out),
+            size = 2) +
+  # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
+  labs(y = "Out Degree", x = element_blank())
+
+cmmhp_zeta %>% 
+  ggplot(aes(name, value, fill = Model)) +
+  geom_boxplot() +
+  scale_fill_manual(values = "#FDE725FF") +
+  facet_wrap(~cohort, scales = "free", ncol = 2) +
+  geom_text(data = in_perc, aes(name, max_est + 0.25, label = perc_in),
+            size = 2) +
+  # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
+  labs(y = "In Degree", x = element_blank())
+
+```
+
+### Other Global Parameters
+
+```{r plot-cohort-level-params}
+cohort_pars <- tibble()
+for(current_cohort in 1:10) {
+  load(paste(data_path,
+             cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",
+             cohort_names[current_cohort],
+             ".RData",
+             sep = ""
+  ))
+  all_data <- sim_cohort_mmhp %>%
+    select(starts_with("eta") | starts_with("w_lam") |
+             starts_with("beta")) %>%
+    select(! ends_with("delta")) %>% 
+    pivot_longer(everything()) %>%
+    mutate(Model = "C-MMHP", cohort = paste0("C_", current_cohort))
+  cohort_pars <- cohort_pars %>% 
+    bind_rows(all_data)
+}
+
+cohort_pars$cohort <- factor(cohort_pars$cohort, 
+                             levels = paste0("C_",1:10))
+
+cohort_pars %>% 
+  ggplot(aes(cohort, value, fill = Model)) +
+  geom_boxplot() +
+  scale_fill_manual(values = "#FDE725FF") +
+  facet_wrap(~name, scales = "free") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
+
+```
+
+### Cohort Summaries
+
+```{r overall-fight-info}
+cohort_summ <- tibble()
+
+for(current_cohort in 1:10) {
+  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
+  total_events <- clean_data$N_count
+  active_events <- total_events_active(current_cohort)
+  total_fights <- sum(clean_data$N_count)
+  coh_tbl <- tibble(cohort = current_cohort,
+                    number_fights = total_fights,
+                    act_perc = sum(active_events)/sum(total_fights))
+  cohort_summ <- cohort_summ %>% 
+    bind_rows(coh_tbl)
+}
+
+cohort_summ %>% 
+  rename("Cohort" = cohort,
+         "Total Fights" = number_fights,
+         "% Active Fights" = act_perc) %>% 
+  kbl() %>% 
+  kable_styling()
+
+```

### 2021-08-18 output_scripts/Paper_Plots.Rmd
current updates

@@
 # don't write to this path
-data_path <- "../output/revisions/lapl_check/prior_check/"
+data_path <- "../output/revisions/aug_run/"
 
@@
 
+## change this to just list all files with a pattern
 sims <- 1:50
@@
 
-print(fit_dsnl_active, pars = c("x"))
-sim_dsnl_active <- rstan::extract(fit_dsnl_active)
+# 
+# print(fit_dsnl_active, pars = c("x"))
+# sim_dsnl_active <- rstan::extract(fit_dsnl_active)
 
 ## social dsnl
-fit_dsnl_inactive <- stan("../lib/dsnl_poisson.stan",
+fit_dsnl_inactive <- dsnl_poisson$sample(
   data = list(
@@
 )
-print(fit_dsnl_inactive, pars = c("x"))
+# print(fit_dsnl_inactive, pars = c("x"))
 sim_dsnl_inactive <- rstan::extract(fit_dsnl_inactive)

### 2021-08-18 output_scripts/investigate_rankings.Rmd
current updates

@@
   html_document:
-    # toc: true
-    # toc_depth: 2
-    # toc_float: true
+    toc: true
+    toc_depth: 2
+    toc_float: true
     number_sections: FALSE
@@
   echo = TRUE, fig.height = 5, fig.width = 7,
-  warning = FALSE, cache = TRUE
+  warning = FALSE, cache = TRUE, eval_paper = FALSE
 )
 
-slides_plots <- FALSE
-extra_plots <- FALSE
-
-revision_plots <- TRUE
-original_plots <- FALSE
-### original plots for plots which are no longer needed, 
-### revision plots are what required
+paper_plots <- FALSE
+# extra_plots <- FALSE
 
@@
 
-```{r define_functions, eval=revision_plots, include=FALSE}
+```{r define_functions, include=FALSE}
 model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3) {
@@
 
-# Interevents vs rankings
+# Other Paper plots
 
-```{r interevents, message=FALSE}
-for(current_cohort in 1:10) {
-  cat(paste("Cohort ", current_cohort, "\n", sep = ""))
-  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-  stan_input_lst <- prepareDataStan(current_cohort)
+```{r fig-3b, eval=paper_plots}
+current_cohort <- 5
 
-  pair_events <- apply(stan_input_lst$Nm, 1, sum)
+m1_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+  "/chp_pr_matrix_", cohort_names[current_cohort],
+  ".RDS",
+  sep = ""
+))
 
-  pair_matrix <- matrix(0, nrow = 12, ncol = 12)
-  for(i in seq_along(pair_events)) {
-    i_ind <- stan_input_lst$I_fit[i]
-    j_ind <- stan_input_lst$J_fit[i]
-    pair_matrix[i_ind, j_ind] <- pair_events[i]
+m2_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+  "/dchp_pr_matrix_", cohort_names[current_cohort],
+  ".RDS",
+  sep = ""
+))
+
+m3_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+  "/cmmhp_pr_matrix_", cohort_names[current_cohort],
+  ".RDS",
+  sep = ""
+))
+
+indep_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
+  "/immhp_pr_matrix_", cohort_names[current_cohort],
+  ".RDS",
+  sep = ""
+))
+
+matrix_lst_plot <- list(
+  m1_pr[
+    rev(expert_rank_10[[current_cohort]]),
+    expert_rank_10[[current_cohort]]
+  ],
+  m2_pr[
+    rev(expert_rank_10[[current_cohort]]),
+    expert_rank_10[[current_cohort]]
+  ]
+  ,
+  m3_pr[
+    rev(expert_rank_10[[current_cohort]]),
+    expert_rank_10[[current_cohort]]
+  ],
+  indep_pr[
+    rev(expert_rank_10[[current_cohort]]),
+    expert_rank_10[[current_cohort]]
+  ]
+)
+# cat("Cohort ",current_cohort,"\n",sep="")
+myMultiMatrixPlot(
+  X = matrix_lst_plot, no_matrix = 4, n_row = 2,
+  xLabels = expert_rank_10[[current_cohort]],
+  yLabels = rev(expert_rank_10[[current_cohort]]),
+  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
+  colorPalette = "RdBu", if.emp = FALSE,
+  # legend.mar=c(0.5,.5,0.5,0.5),
+  title_lst = list("C-HP", "C-DCHP", "C-MMHP", "I-MMHP"),
+  # title_lst = list("I-MMHP"),
+  col_axis = c(-80, -40, 0, 40, 80),
+  fake_matrix = FALSE,
+  matrix.mar = c(2.5, 2.5, 2.5, 1)
+)
+mtext(text = "(b)",
+      side = 3,
+      line = 0.5,
+      outer = TRUE,
+      cex = 2.5,
+      font = 2)
+
+```
+
+```{r fig-7a, eval=paper_plots}
+load("../output/revisions/lapl_check/prior_check/plot_N_predict_revision.RData")
+current_cohort <- 5 # cohort 1 looks worse than rest
+
+temp_plot_df <- predict_day_mae_df_lst[[current_cohort]]
+temp_plot_df$method <- factor(temp_plot_df$method,
+  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
+  labels = c("I-MMHP", "DSNL", "C-HP", "C-DCHP", "C-MMHP")
+)
+temp_plot_df$day <- factor(temp_plot_df$day)
+# png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
+# width=600,height=300)
+
+plot_cols_pred <- col_df %>%
+  filter(method %in% levels(temp_plot_df$method)) %>%
+  arrange(factor(method, levels = c(
+    "I-MMHP", "DSNL",
+    "C-HP", "C-DCHP", "C-MMHP"
+  ))) %>%
+  pull(cols)
+
+p3 <- temp_plot_df %>%
+  rowwise() %>%
+  # mutate(norm = min(norm,60)) %>%
+  # rename(Method = method) %>%
+  ggplot(aes(x = method, y = mae, fill = method)) +
+  geom_boxplot(alpha = 0.7) +
+  scale_fill_manual(values = plot_cols_pred) +
+  ggtitle("(a)") +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
+    text = element_text(size = 20),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    legend.position = "right"
+  ) +
+  facet_grid(cols = vars(day)) +
+  xlab("Prediction horizon (day)") +
+  ylab("MAE") +
+  ylim(0, 5) + # aren't infinite but >150 and <200
+  NULL
+p3 + labs(fill = "Method", title = "Single Cohort")
+
+```
+
+```{r fig-7b, eval=paper_plots}
+load("../output/revisions/lapl_check/prior_check/plot_N_predict_revision.RData")
+
+all_cohort_box <- all_cohort_mae_df
+
+all_cohort_box$method <- factor(all_cohort_box$method,
+  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
+  labels = c(
+    "I-MMHP", "DSNL",
+    "C-HP", "C-DCHP",
+    "C-MMHP"
+  )
+)
+all_cohort_box$day <- factor(all_cohort_box$day)
+
+plot_cols_pred <- col_df %>%
+  filter(method %in% levels(all_cohort_box$method)) %>%
+  arrange(factor(method, levels = c(
+    "I-MMHP", "DSNL",
+    "C-HP", "C-DCHP", "C-MMHP"
+  ))) %>%
+  pull(cols)
+
+all_cohort_box %>%
+  ggplot(aes(x = method, y = norm, fill = method)) +
+  # facet_grid(cols = vars(day)) +
+  geom_boxplot(alpha = 0.7) +
+  scale_fill_manual(values = plot_cols_pred) +
+  ggtitle("(a)") +
+  theme_bw() +
+  theme(
+    plot.title = element_text(
+      size = 22,
+      hjust = 0.5, face = "bold"
+    ),
+    text = element_text(size = 20),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    legend.position = "right"
+  ) +
+  facet_grid(cols = vars(day)) +
+  # guides(color=guide_legend(title="Method")) +
+  xlab("Prediction horizon (day)") +
+  ylab("MAE") +
+  labs(fill = "Method") +
+  # ylim(0, 80) +
+  NULL
+
+```
+
+```{r fig-7b-pred-rank-spearman-all-cohorts, eval=paper_plots}
+load("../output/revisions/lapl_check/prior_check/plot_rank_predict.RData")
+
+all_cohort_rank_df$method <- factor(all_cohort_rank_df$method,
+  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
+  labels = c(
+    "I-MMHP", "DSNL", "C-HP",
+    "C-DCHP", "C-MMHP"
+  )
+)
+
+p7 <- ggplot(
+  all_cohort_rank_df,
+  aes(x = method, y = spearman, fill = method)
+) +
+  # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
+  geom_boxplot(alpha = 0.7) +
+  scale_fill_manual(values = plot_cols_pred) +
+  ggtitle("(b)") +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
+    text = element_text(size = 20),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    legend.position = "right"
+  ) +
+  facet_grid(cols = vars(day)) +
+  xlab("Prediction horizon (day)") +
+  ylab("Spearman rank corr.") +
+  # coord_cartesian(ylim=c(0,1)) +
+  labs(fill = "Method")
+
+p7
+```
+
+```{r construct data for plot, results='hide',message=FALSE,cache=TRUE, eval=paper_plots}
+library(PlayerRatings)
+
+current_cohort <- 7
+# 4 best so far, or 7
+
+load(paste(data_path, cohort_names[current_cohort],
+  "/predict_simulation_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+clean_data <- cleanData(full_data[[cohort_names[current_cohort]]],
+  cut_off = 1
+)
+
+df <- full_data[[cohort_names[current_cohort]]]
+df <- df[df$Actor != "Start" & df$Actor != "End", ]
+df1 <- expandrows(df)
+df1 <- df1[order(df1$Timestamp), ] # ensure in date order
+df1$event <- 1:nrow(df1)
+glick.df <- df1[, c("event", "Actor", "Recipient", "score"), with = FALSE]
+# need event, actor, recipient, score
+gl <- my_glicko(glick.df, history = TRUE, cval = 2)
+
+# ------------------- period
+training_end <- nrow(df[df$day <= 18, ])
+testing_end <- nrow(df) - 1 # 1077 #929 for cohort 5
+newx <- c(training_end:testing_end)
+
+# ----------------- set pars for plot
+my_col <- c("black", "grey", "orange", "red")
+col_vec <- colorRampPalette(my_col)(mice_number)
+ltypes_vec <- rep(1, mice_number) # c(1,2,3,1,2,3,1,2,3,1,2,3)
+history_width <- 3
+sim_width <- 0.3
+shade_vec <- makeTransparent(col_vec, 0.2)
+less_shade_vec <- makeTransparent(col_vec, 0.7)
+
+# ---------------- simulation mean and sd
+sim_gl_array <- array(NA, dim = c(12, testing_end - training_end + 1, 1000))
+for (s in 1:1000) {
+  print(s)
+  temp_gl <- glickoScoreSimulationWithWindowsReturnAll(
+    predict.sim = m3_predict_sim[5:8, s], # 7 for c 2 and 10
+    history.df = glick.df[1:training_end, ]
+  )
+  history_matrix <- temp_gl$history[, , 1]
+
+  if (testing_end > ncol(temp_gl$history[, , 1])) {
+    history_matrix <- cbind(
+      history_matrix,
+      t(matrix(rep(
+        history_matrix[, ncol(history_matrix)],
+        testing_end - ncol(temp_gl$history[, , 1])
+      ),
+      nrow = testing_end - ncol(temp_gl$history[, , 1]),
+      byrow = TRUE
+      ))
+    )
+  } else {
+    # try(
+    history_matrix <- history_matrix[, 1:testing_end]
+    # temp_gl$history[,1:testing_end]
+    # )
   }
-  # pair_matrix <- clean_data$N_count[expert_rank_10[[current_cohort]],
-  #                                   expert_rank_10[[current_cohort]]]
-  pair_matrix <- pair_matrix[expert_rank_10[[current_cohort]],
-                    expert_rank_10[[current_cohort]]]
-  colnames(pair_matrix) <- expert_rank_10[[current_cohort]]
-  rownames(pair_matrix) <- expert_rank_10[[current_cohort]]
-  print(pair_matrix)
-  cat("=====\n")
-
+  sim_gl_array[, , s] <- history_matrix[, training_end:testing_end]
 }
@@
 
-<!-- # Ranking and Events -->
+```{r fig-10a-glicko-rating, eval=paper_plots}
+par(mar = c(3, 5, 3, 1))
+testing_end <- testing_end - 1
+plot(1,
+  type = "n", xlab = "",
+  ylab = "Glicko ranking", xlim = c(0, dim(gl$history)[2]),
+  ylim = c(min(gl$history[, , 1]), max(gl$history[, , 1])),
+  cex.axis = 2, cex.lab = 2
+)
+for (m in c(1:mice_number)) {
+  # history
+  lines(gl$history[m, 1:training_end, 1],
+    cex = 0.6, col = col_vec[m], lwd = history_width, lty = ltypes_vec[m]
+  )
+  lines(c(rep(NA, training_end),
+          gl$history[m, (training_end + 1):testing_end, 1]),
+    cex = 0.6, col = shade_vec[m], lwd = history_width, lty = ltypes_vec[m]
+  )
 
-<!-- We first modify the priors from the C-MMHP model which leads to -->
-<!-- much improved MCMC performance. -->
+  # simulation
+  cur_end <- testing_end
+  mean_vec <- apply(sim_gl_array[m, , ], 1, function(x) mean(na.omit(x)))
+  sd_vec <- apply(sim_gl_array[m, , ], 1, function(x) sd(na.omit(x)))
+  polygon(c(newx, rev(newx)),
+          c(mean_vec - sd_vec, rev(mean_vec + sd_vec)),
+          col = shade_vec[m], border = NA)
+  # polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
+  lines(c(rep(NA, training_end), mean_vec),
+    cex = 0.6, col = col_vec[m], lwd = 1, lty = 2
+  )
+}
 
-<!-- We want to look at the relationship between the inferred variability -->
-<!-- of the ranking and the number of interactions a given animal is involved in. -->
+# annotate the days
+for (d in c(19:21)) {
+  abline(v = nrow(df[df$day <= (d - 1), ]), lty = 2, lwd = 0.4)
+  text(x = nrow(df[df$day <= (d - 1), ]), y = 2600, d)
+}
+mtext(text = "(a)", side = 3, line = -2.3,
+      outer = TRUE, cex = 2.8, at = 0.5, font = 2)
+```
 
-<!-- We plot the inferred ranks arranged by decreasing number -->
-<!-- of total interactions for all 4 of the comparison models, as in Fig6a. -->
+```{r remove some objects, include=FALSE, eval=paper_plots}
+rm(m3_predict_sim)
+rm(m2_predict_sim)
+rm(m1_predict_sim)
+rm(mmhp_predict_sim)
+rm(fit_agg_rank)
+rm(fit_cohort_hp)
+rm(fit_cohort_dchp)
+rm(fit_cohort_mmhp)
 
-<!-- ```{r plot-rank-total-interactions, eval=FALSE} -->
-<!--  for(current_cohort in 1:10) { -->
-<!--    clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
-<!--    load(paste(data_path, -->
-<!--               cohort_names[current_cohort], -->
-<!--               "/cohort_mmhp_stan_result_", -->
-<!--               cohort_names[current_cohort], -->
-<!--               ".RData", -->
-<!--               sep = "" -->
-<!--               )) -->
-<!--    total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
-<!--    f_ranks <- paste("f[", order(total_inter, decreasing = TRUE), -->
-<!--                     "]", sep = "") -->
-<!--    f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>% -->
-<!--    pivot_longer(everything()) -->
-<!--    f_draws$name <- factor(f_draws$name, levels = f_ranks) -->
-<!--    plot_f <- f_draws %>% -->
-<!--    ggplot(aes(name, value)) + -->
-<!--    geom_boxplot() + -->
-<!--    labs(title = paste("Cohort ", current_cohort, sep = ""), -->
-<!--         subtitle = "Ordered by total interactions") -->
-<!--    print(plot_f) -->
-<!--  } -->
-<!-- ``` -->
-
-<!-- ```{r all-4-models, warning=FALSE} -->
-<!-- for(current_cohort in 1:10) { -->
-<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
-<!--   load(paste(data_path, -->
-<!--              cohort_names[current_cohort], -->
-<!--              "/cohort_mmhp_stan_result_", -->
-<!--              cohort_names[current_cohort], -->
-<!--              ".RData", -->
-<!--              sep = "" -->
-<!--              )) -->
-<!--   load(paste(data_path, cohort_names[current_cohort], -->
-<!--     "/agg_rank_stan_result_", cohort_names[current_cohort], -->
-<!--     ".RData", -->
-<!--     sep = "" -->
-<!--   )) -->
-<!--   load(paste(data_path, cohort_names[current_cohort], -->
-<!--     "/cohort_hp_stan_result_", cohort_names[current_cohort], -->
-<!--     ".RData", -->
-<!--     sep = "" -->
-<!--   )) -->
-<!--   load(paste(data_path, cohort_names[current_cohort], -->
-<!--     "/cohort_dchp_stan_result_", cohort_names[current_cohort], -->
-<!--     ".RData", -->
-<!--     sep = "" -->
-<!--   )) -->
-<!--   total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
-
-<!--   no_method <- 4 -->
-<!--   plot_latent_df <- data.frame( -->
-<!--     Methods = rep(1:no_method, each = 1000 * mice_number), -->
-<!--     Mice = rep(rep(1:mice_number, each = 1000), no_method), -->
-<!--     force = rep(0, 1000 * mice_number * no_method) -->
-<!--   ) -->
-<!--   ## agg -->
-<!--   x_draws <- sim_agg_rank %>% select(starts_with("x")) -->
-<!--   plot_latent_df$force[(1:(1000 * mice_number))] <- -->
-<!--     as.vector(as.matrix(x_draws)) -->
-
-<!--   ## M1 -->
-<!--   f_draws <- sim_cohort_hp %>% select(starts_with("f")) -->
-<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
-<!--                          1000 * mice_number] <- -->
-<!--     as.vector(as.matrix(f_draws)) -->
-
-<!--   ## M2 -->
-<!--   f_draws <- sim_cohort_dchp %>% select(starts_with("f")) -->
-<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
-<!--                          2000 * mice_number] <- -->
-<!--     as.vector(as.matrix(f_draws)) -->
-
-<!--   ## M3 -->
-<!--   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) -->
-<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
-<!--                          3000 * mice_number] <- -->
-<!--     as.vector(as.matrix(f_draws)) -->
-
-<!--   plot_latent_df$Mice <- factor(plot_latent_df$Mice, -->
-<!--     levels = order(total_inter, decreasing = TRUE) -->
-<!--   ) -->
-<!--   plot_latent_df$Method <- factor(plot_latent_df$Method, -->
-<!--     labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP") -->
-<!--   ) -->
-<!--   plot_cols <- col_df %>% -->
-<!--   filter(method %in% c( -->
-<!--     "AggRank", "C-HP", -->
-<!--     "C-DCHP", "C-MMHP" -->
-<!--   )) %>% -->
-<!--   pull(cols) -->
-
-<!--   p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) + -->
-<!--     geom_boxplot(alpha = 0.7) + -->
-<!--     scale_fill_manual(values = plot_cols) + -->
-<!--     ggtitle("(a)") + -->
-<!--     theme_bw() + -->
-<!--     theme( -->
-<!--       plot.title = element_text(size = 22, hjust = 0.5, face = "bold"), -->
-<!--       text = element_text(size = 20), -->
-<!--       axis.text.x = element_text(size = 10), -->
-<!--       legend.position = "none" -->
-<!--     ) + -->
-<!--     facet_grid(cols = vars(Method)) + -->
-<!--     xlab("Mice (ranked by total interactions)") + -->
-<!--     ylab("Latent rank") + -->
-<!--     labs(title = paste("Cohort ", current_cohort, sep = "")) -->
-<!--   print(p1) -->
-<!-- } -->
-
-<!-- ``` -->
-
-<!-- Similarly, here are the corresponding plots with the animals ranked by -->
-<!-- I&SI score instead. -->
-
-<!-- ```{r isi-ranks, warning=FALSE, eval=FALSE} -->
-<!-- for(current_cohort in 1:10) { -->
-<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
-<!--   load(paste(data_path, -->
-<!--              cohort_names[current_cohort], -->
-<!--              "/cohort_mmhp_stan_result_", -->
-<!--              cohort_names[current_cohort], -->
-<!--              ".RData", -->
-<!--              sep = "" -->
-<!--              )) -->
-<!--   total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
-<!--   f_ranks <- paste("f[", expert_rank_10[[current_cohort]], -->
-<!--                    "]", sep = "") -->
-<!--   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>% -->
-<!--   pivot_longer(everything()) -->
-<!--   f_draws$name <- factor(f_draws$name, levels = f_ranks) -->
-<!--   plot_f <- f_draws %>% -->
-<!--   ggplot(aes(name, value)) + -->
-<!--   geom_boxplot() + -->
-<!--   labs(title = paste("Cohort ", current_cohort, sep = ""), -->
-<!--        subtitle = "Ordered by I&SI score") -->
-<!--   print(plot_f) -->
-<!-- } -->
-
-<!-- ``` -->
-
-<!-- ```{r ranked-by-isi} -->
-<!-- for(current_cohort in 1:10) { -->
-<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
-<!--   load(paste(data_path, -->
-<!--              cohort_names[current_cohort], -->
-<!--              "/cohort_mmhp_stan_result_", -->
-<!--              cohort_names[current_cohort], -->
-<!--              ".RData", -->
-<!--              sep = "" -->
-<!--              )) -->
-<!--   load(paste(data_path, cohort_names[current_cohort], -->
-<!--     "/agg_rank_stan_result_", cohort_names[current_cohort], -->
-<!--     ".RData", -->
-<!--     sep = "" -->
-<!--   )) -->
-<!--   load(paste(data_path, cohort_names[current_cohort], -->
-<!--     "/cohort_hp_stan_result_", cohort_names[current_cohort], -->
-<!--     ".RData", -->
-<!--     sep = "" -->
-<!--   )) -->
-<!--   load(paste(data_path, cohort_names[current_cohort], -->
-<!--     "/cohort_dchp_stan_result_", cohort_names[current_cohort], -->
-<!--     ".RData", -->
-<!--     sep = "" -->
-<!--   )) -->
-<!--   total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
-
-<!--   no_method <- 4 -->
-<!--   plot_latent_df <- data.frame( -->
-<!--     Methods = rep(1:no_method, each = 1000 * mice_number), -->
-<!--     Mice = rep(rep(1:mice_number, each = 1000), no_method), -->
-<!--     force = rep(0, 1000 * mice_number * no_method) -->
-<!--   ) -->
-<!--   ## agg -->
-<!--   x_draws <- sim_agg_rank %>% select(starts_with("x")) -->
-<!--   plot_latent_df$force[(1:(1000 * mice_number))] <- -->
-<!--     as.vector(as.matrix(x_draws)) -->
-
-<!--   ## M1 -->
-<!--   f_draws <- sim_cohort_hp %>% select(starts_with("f")) -->
-<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
-<!--                          1000 * mice_number] <- -->
-<!--     as.vector(as.matrix(f_draws)) -->
-
-<!--   ## M2 -->
-<!--   f_draws <- sim_cohort_dchp %>% select(starts_with("f")) -->
-<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
-<!--                          2000 * mice_number] <- -->
-<!--     as.vector(as.matrix(f_draws)) -->
-
-<!--   ## M3 -->
-<!--   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) -->
-<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
-<!--                          3000 * mice_number] <- -->
-<!--     as.vector(as.matrix(f_draws)) -->
-
-<!--   plot_latent_df$Mice <- factor(plot_latent_df$Mice, -->
-<!--     levels = expert_rank_10[[current_cohort]] -->
-<!--   ) -->
-<!--   plot_latent_df$Method <- factor(plot_latent_df$Method, -->
-<!--     labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP") -->
-<!--   ) -->
-<!--   plot_cols <- col_df %>% -->
-<!--   filter(method %in% c( -->
-<!--     "AggRank", "C-HP", -->
-<!--     "C-DCHP", "C-MMHP" -->
-<!--   )) %>% -->
-<!--   pull(cols) -->
-
-<!--   p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) + -->
-<!--     geom_boxplot(alpha = 0.7) + -->
-<!--     scale_fill_manual(values = plot_cols) + -->
-<!--     ggtitle("(a)") + -->
-<!--     theme_bw() + -->
-<!--     theme( -->
-<!--       plot.title = element_text(size = 22, hjust = 0.5, face = "bold"), -->
-<!--       text = element_text(size = 20), -->
-<!--       axis.text.x = element_text(size = 10), -->
-<!--       legend.position = "none" -->
-<!--     ) + -->
-<!--     facet_grid(cols = vars(Method)) + -->
-<!--     xlab("Mice (ranked by I&SI)") + -->
-<!--     ylab("Latent rank") + -->
-<!--     labs(title = paste("Cohort ", current_cohort, sep = "")) -->
-<!--   print(p1) -->
-<!-- } -->
-
-<!-- ``` -->
-
-<!-- Cohort 3 win loss -->
-
-<!-- ```{r c3-win-loss} -->
-<!-- current_cohort <- 3 -->
-<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
-
-<!-- clean_data$N_count -->
-
-<!-- load(paste(data_path, -->
-<!--              cohort_names[current_cohort], -->
-<!--              "/cohort_mmhp_stan_result_", -->
-<!--              cohort_names[current_cohort], -->
-<!--              ".RData", -->
-<!--              sep = "" -->
-<!--              )) -->
-
-<!-- gamma_draws <- sim_cohort_mmhp %>% -->
-<!--   select(starts_with("gamma")) %>% -->
-<!--   pivot_longer(everything()) -->
-
-<!-- gamma_draws$name <- factor(gamma_draws$name, -->
-<!--                            levels = paste("gamma[", 1:12, "]", sep = "")) -->
-
-<!-- gamma_draws %>% -->
-<!--   ggplot(aes(name, value)) + -->
-<!--   geom_boxplot() -->
-
-<!-- zeta_draws <- sim_cohort_mmhp %>% -->
-<!--   select(starts_with("zeta")) %>% -->
-<!--   pivot_longer(everything()) -->
-
-<!-- zeta_draws$name <- factor(zeta_draws$name, -->
-<!--                            levels = paste("zeta[", 1:12, "]", sep = "")) -->
-
-<!-- zeta_draws %>% -->
-<!--   ggplot(aes(name, value)) + -->
-<!--   geom_boxplot() -->
-
-<!-- f_draws <- sim_cohort_mmhp %>% -->
-<!--   select(starts_with("f")) %>% -->
-<!--   pivot_longer(everything()) %>% -->
-<!--   group_by(name) %>% -->
-<!--   summarise(med = median(value)) %>% -->
-<!--   arrange(-med) -->
-
-<!-- f_draws %>% pull(name) -->
-
-<!-- cmmhp_ranks <- c(10, 12, 7, 6, 3, 8, 2, 4, 1, 9, 11, 5) -->
-<!-- clean_data$N_count[cmmhp_ranks, cmmhp_ranks] -->
-
-<!-- c3_count <- clean_data$N_count -->
-<!-- names(c3_count) <- 1:12 -->
-<!-- rownames(c3_count) <- 1:12 -->
-<!-- colnames(c3_count) <- 1:12 -->
-<!-- isi98(c3_count) -->
-<!-- isi98(c3_count[cmmhp_ranks, cmmhp_ranks]) -->
-<!-- ``` -->
-
-<!-- ## Plot Omega Lambda and f draws -->
-
-<!-- ```{r plot-omega-lambda, message=FALSE} -->
-<!-- for(current_cohort in 1:10) { -->
-<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
-<!--   load(paste(data_path, -->
-<!--              cohort_names[current_cohort], -->
-<!--              "/cohort_mmhp_stan_result_", -->
-<!--              cohort_names[current_cohort], -->
-<!--              ".RData", -->
-<!--              sep = "" -->
-<!--              )) -->
-<!--   fit_draws <- as_draws_array(sim_cohort_mmhp) -->
-<!--   plot1 <- mcmc_hist(fit_draws, pars = "w_lambda") + -->
-<!--     labs(paste("Cohort ", current_cohort, sep = "")) -->
-<!--   print(plot1) -->
-<!-- } -->
-<!-- ``` -->
-
-<!-- # Compare rankings with/without eta_3 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta3, message=FALSE} -->
-<!-- # data_path -->
-<!-- other_data_path <- "../output/revisions/lapl_check/ident_check/" -->
-
-<!-- for(current_cohort in 1:10) { -->
-<!--   load(paste(data_path, -->
-<!--              cohort_names[current_cohort], -->
-<!--              "/cohort_mmhp_stan_result_", -->
-<!--              cohort_names[current_cohort], -->
-<!--              ".RData", -->
-<!--              sep = "" -->
-<!--              )) -->
-<!--   sim1 <- sim_cohort_mmhp -->
-<!--   load(paste(other_data_path, -->
-<!--              cohort_names[current_cohort], -->
-<!--              "/cohort_mmhp_stan_result_", -->
-<!--              cohort_names[current_cohort], -->
-<!--              ".RData", -->
-<!--              sep = "" -->
-<!--              )) -->
-<!--   sim2 <- sim_cohort_mmhp -->
-
-<!--   all_data <- sim1 %>% -->
-<!--     select(starts_with("f")) %>%  -->
-<!--     pivot_longer(everything()) %>%  -->
-<!--     mutate(model = "with eta3") %>%  -->
-<!--     bind_rows(sim2 %>% select(starts_with("f")) %>%  -->
-<!--                 pivot_longer(everything()) %>%  -->
-<!--                 mutate(model = "without")) -->
-
-<!--   f_ranks <- paste("f[", expert_rank_10[[current_cohort]], -->
-<!--                    "]", sep = "")  -->
-<!--   all_data$name <- factor(all_data$name, levels = f_ranks) -->
-
-<!--   all_data$model <- factor(all_data$model) -->
-<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
-<!--     geom_boxplot() + -->
-<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
-<!--          subtitle = "Removing eta3, ordered by ISI", -->
-<!--          y = "Latent Rankings") -->
-<!--   print(comp_plot) -->
-
-<!--   all_data %>% group_by(name, model) %>%  -->
-<!--     summarise(model_mean = mean(value),  -->
-<!--               model_sd = sd(value)) -->
-
-<!--   all_data <- sim1 %>% -->
-<!--     select(starts_with("eta") | starts_with("w_lam") | starts_with("beta")) %>%  -->
-<!--     pivot_longer(everything()) %>%  -->
-<!--     mutate(model = "with eta1") %>%  -->
-<!--     bind_rows(sim2 %>%  -->
-<!--                 select(starts_with("eta") |  -->
-<!--                          starts_with("w_lam") | -->
-<!--                          starts_with("beta")) %>%  -->
-<!--                 pivot_longer(everything()) %>%  -->
-<!--                 mutate(model = "without")) -->
-<!--   all_data$model <- factor(all_data$model) -->
-<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
-<!--     geom_boxplot() + -->
-<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
-<!--          subtitle = "Comparison removing eta3", y = "Eta params") + -->
-<!--     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) -->
-<!--   print(comp_plot) -->
-<!--   ### -->
-<!--   ## same for zeta, -->
-<!--   all_data <- sim1 %>% -->
-<!--     select(starts_with("zeta") ) %>%  -->
-<!--     pivot_longer(everything()) %>%  -->
-<!--     mutate(model = "with eta1") %>%  -->
-<!--     bind_rows(sim2 %>% select(starts_with("zeta")) %>%  -->
-<!--                 pivot_longer(everything()) %>%  -->
-<!--                 mutate(model = "without")) -->
-<!--   all_data$model <- factor(all_data$model) -->
-<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
-<!--     geom_boxplot() + -->
-<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
-<!--          subtitle = "Comparison removing eta3", y = "Zeta params") + -->
-<!--     theme(axis.text.x = element_blank()) + -->
-<!--     facet_wrap(~name, scales = "free") -->
-<!--   print(comp_plot) -->
-
-<!--   ### -->
-<!--   all_data <- sim1 %>% -->
-<!--     select(starts_with("gamma")) %>%  -->
-<!--     pivot_longer(everything()) %>%  -->
-<!--     mutate(model = "with eta3") %>%  -->
-<!--     bind_rows(sim2 %>% select(starts_with("gamma")) %>%  -->
-<!--                 pivot_longer(everything()) %>%  -->
-<!--                 mutate(model = "without")) -->
-<!--   all_data$model <- factor(all_data$model) -->
-<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
-<!--     geom_boxplot() + -->
-<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
-<!--          subtitle = "Comparison removing eta3", y = "Out Degree") + -->
-<!--     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) -->
-<!--   print(comp_plot) -->
-
-<!-- } -->
-
-<!-- ``` -->
-
-<!-- # Compare rankings with/without eta_1 -->
-
-<!-- ```{r plot-rankings-both-models-no-eta-1, message=FALSE} -->
-<!-- # data_path -->
-<!-- other_data_path <- "../output/revisions/lapl_check/ident_check_no_eta1/" -->
-
-<!-- for(current_cohort in 1:10) { -->
-<!--   load(paste(data_path, -->
-<!--              cohort_names[current_cohort], -->
-<!--              "/cohort_mmhp_stan_result_", -->
-<!--              cohort_names[current_cohort], -->
-<!--              ".RData", -->
-<!--              sep = "" -->
-<!--              )) -->
-<!--   sim1 <- sim_cohort_mmhp -->
-<!--   load(paste(other_data_path, -->
-<!--              cohort_names[current_cohort], -->
-<!--              "/cohort_mmhp_stan_result_", -->
-<!--              cohort_names[current_cohort], -->
-<!--              ".RData", -->
-<!--              sep = "" -->
-<!--              )) -->
-<!--   sim2 <- sim_cohort_mmhp -->
-
-<!--   all_data <- sim1 %>% -->
-<!--     select(starts_with("f")) %>%  -->
-<!--     pivot_longer(everything()) %>%  -->
-<!--     mutate(model = "with eta1") %>%  -->
-<!--     bind_rows(sim2 %>% select(starts_with("f")) %>%  -->
-<!--                 pivot_longer(everything()) %>%  -->
-<!--                 mutate(model = "without")) -->
-
-<!--   f_ranks <- paste("f[", expert_rank_10[[current_cohort]], -->
-<!--                    "]", sep = "")  -->
-<!--   all_data$name <- factor(all_data$name, levels = f_ranks) -->
-
-<!--   all_data$model <- factor(all_data$model) -->
-<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
-<!--     geom_boxplot() + -->
-<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
-<!--          subtitle = "Comparison removing eta1, ranked by ISI", -->
-<!--          y = "Latent Ranks") -->
-<!--   print(comp_plot) -->
-
-<!--   all_data %>% group_by(name, model) %>%  -->
-<!--     summarise(model_mean = mean(value),  -->
-<!--               model_sd = sd(value)) -->
-
-<!--   ## same for beta_etc, -->
-<!--   all_data <- sim1 %>% -->
-<!--     select(starts_with("eta") | starts_with("w_lam") | starts_with("beta")) %>%  -->
-<!--     pivot_longer(everything()) %>%  -->
-<!--     mutate(model = "with eta1") %>%  -->
-<!--     bind_rows(sim2 %>%  -->
-<!--                 select(starts_with("eta") |  -->
-<!--                          starts_with("w_lam") | -->
-<!--                          starts_with("beta")) %>%  -->
-<!--                 pivot_longer(everything()) %>%  -->
-<!--                 mutate(model = "without")) -->
-<!--   all_data$model <- factor(all_data$model) -->
-<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
-<!--     geom_boxplot() + -->
-<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
-<!--          subtitle = "Comparison removing eta1", y = "Eta params") + -->
-<!--     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) -->
-<!--   print(comp_plot) -->
-<!--   ### -->
-<!--   ## same for zeta, -->
-<!--   all_data <- sim1 %>% -->
-<!--     select(starts_with("zeta") ) %>%  -->
-<!--     pivot_longer(everything()) %>%  -->
-<!--     mutate(model = "with eta1") %>%  -->
-<!--     bind_rows(sim2 %>% select(starts_with("zeta")) %>%  -->
-<!--                 pivot_longer(everything()) %>%  -->
-<!--                 mutate(model = "without")) -->
-<!--   all_data$model <- factor(all_data$model) -->
-<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
-<!--     geom_boxplot() + -->
-<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
-<!--          subtitle = "Comparison removing eta1", y = "Zeta params") + -->
-<!--     theme(axis.text.x = element_blank()) + -->
-<!--     facet_wrap(~name, scales = "free") -->
-<!--   print(comp_plot) -->
-
-<!--   ### -->
-<!--   all_data <- sim1 %>% -->
-<!--     select(starts_with("gamma")) %>%  -->
-<!--     pivot_longer(everything()) %>%  -->
-<!--     mutate(model = "with eta1") %>%  -->
-<!--     bind_rows(sim2 %>% select(starts_with("gamma")) %>%  -->
-<!--                 pivot_longer(everything()) %>%  -->
-<!--                 mutate(model = "without")) -->
-<!--   all_data$model <- factor(all_data$model) -->
-<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
-<!--     geom_boxplot() + -->
-<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
-<!--          subtitle = "Comparison removing eta1", y = "Out Degree") + -->
-<!--     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) -->
-<!--   print(comp_plot) -->
-
-<!-- } -->
-
-<!-- ``` -->
-
-<!-- # Other Paper plots -->
-
-<!-- ```{r fig-3b} -->
-<!-- current_cohort <- 5 -->
-
-<!-- m1_pr <- readRDS(paste(data_path, cohort_names[current_cohort], -->
-<!--   "/chp_pr_matrix_", cohort_names[current_cohort], -->
-<!--   ".RDS", -->
-<!--   sep = "" -->
-<!-- )) -->
-
-<!-- m2_pr <- readRDS(paste(data_path, cohort_names[current_cohort], -->
-<!--   "/dchp_pr_matrix_", cohort_names[current_cohort], -->
-<!--   ".RDS", -->
-<!--   sep = "" -->
-<!-- )) -->
-
-<!-- m3_pr <- readRDS(paste(data_path, cohort_names[current_cohort], -->
-<!--   "/cmmhp_pr_matrix_", cohort_names[current_cohort], -->
-<!--   ".RDS", -->
-<!--   sep = "" -->
-<!-- )) -->
-
-<!-- indep_pr <- readRDS(paste(data_path, cohort_names[current_cohort], -->
-<!--   "/immhp_pr_matrix_", cohort_names[current_cohort], -->
-<!--   ".RDS", -->
-<!--   sep = "" -->
-<!-- )) -->
-
-<!-- matrix_lst_plot <- list( -->
-<!--   m1_pr[ -->
-<!--     rev(expert_rank_10[[current_cohort]]), -->
-<!--     expert_rank_10[[current_cohort]] -->
-<!--   ], -->
-<!--   m2_pr[ -->
-<!--     rev(expert_rank_10[[current_cohort]]), -->
-<!--     expert_rank_10[[current_cohort]] -->
-<!--   ] -->
-<!--   , -->
-<!--   m3_pr[ -->
-<!--     rev(expert_rank_10[[current_cohort]]), -->
-<!--     expert_rank_10[[current_cohort]] -->
-<!--   ], -->
-<!--   indep_pr[ -->
-<!--     rev(expert_rank_10[[current_cohort]]), -->
-<!--     expert_rank_10[[current_cohort]] -->
-<!--   ] -->
-<!-- ) -->
-<!-- # cat("Cohort ",current_cohort,"\n",sep="") -->
-<!-- myMultiMatrixPlot( -->
-<!--   X = matrix_lst_plot, no_matrix = 4, n_row = 2, -->
-<!--   xLabels = expert_rank_10[[current_cohort]], -->
-<!--   yLabels = rev(expert_rank_10[[current_cohort]]), -->
-<!--   min = -80, max = 80, axis_cex = 2, title_cex = 1.8, -->
-<!--   colorPalette = "RdBu", if.emp = FALSE, -->
-<!--   # legend.mar=c(0.5,.5,0.5,0.5), -->
-<!--   title_lst = list("C-HP", "C-DCHP", "C-MMHP", "I-MMHP"), -->
-<!--   # title_lst = list("I-MMHP"), -->
-<!--   col_axis = c(-80, -40, 0, 40, 80), -->
-<!--   fake_matrix = FALSE, -->
-<!--   matrix.mar = c(2.5, 2.5, 2.5, 1) -->
-<!-- ) -->
-<!-- mtext(text = "(b)", -->
-<!--       side = 3, -->
-<!--       line = 0.5, -->
-<!--       outer = TRUE, -->
-<!--       cex = 2.5, -->
-<!--       font = 2) -->
-
-<!-- ``` -->
-
-<!-- ```{r fig-7a} -->
-<!-- load("../output/revisions/lapl_check/prior_check/plot_N_predict_revision.RData") -->
-<!-- current_cohort <- 5 # cohort 1 looks worse than rest -->
-
-<!-- temp_plot_df <- predict_day_mae_df_lst[[current_cohort]] -->
-<!-- temp_plot_df$method <- factor(temp_plot_df$method, -->
-<!--   levels = c("mmhp", "dsnl", "m1", "m2", "m3"), -->
-<!--   labels = c("I-MMHP", "DSNL", "C-HP", "C-DCHP", "C-MMHP") -->
-<!-- ) -->
-<!-- temp_plot_df$day <- factor(temp_plot_df$day) -->
-<!-- # png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""), -->
-<!-- # width=600,height=300) -->
-
-<!-- plot_cols_pred <- col_df %>% -->
-<!--   filter(method %in% levels(temp_plot_df$method)) %>% -->
-<!--   arrange(factor(method, levels = c( -->
-<!--     "I-MMHP", "DSNL", -->
-<!--     "C-HP", "C-DCHP", "C-MMHP" -->
-<!--   ))) %>% -->
-<!--   pull(cols) -->
-
-<!-- p3 <- temp_plot_df %>% -->
-<!--   rowwise() %>% -->
-<!--   # mutate(norm = min(norm,60)) %>% -->
-<!--   # rename(Method = method) %>% -->
-<!--   ggplot(aes(x = method, y = mae, fill = method)) + -->
-<!--   geom_boxplot(alpha = 0.7) + -->
-<!--   scale_fill_manual(values = plot_cols_pred) + -->
-<!--   ggtitle("(a)") + -->
-<!--   theme_bw() + -->
-<!--   theme( -->
-<!--     plot.title = element_text(size = 22, hjust = 0.5, face = "bold"), -->
-<!--     text = element_text(size = 20), -->
-<!--     axis.text.x = element_blank(), -->
-<!--     axis.ticks.x = element_blank(), -->
-<!--     legend.position = "right" -->
-<!--   ) + -->
-<!--   facet_grid(cols = vars(day)) + -->
-<!--   xlab("Prediction horizon (day)") + -->
-<!--   ylab("MAE") + -->
-<!--   ylim(0, 5) + # aren't infinite but >150 and <200 -->
-<!--   NULL -->
-<!-- p3 + labs(fill = "Method", title = "Single Cohort") -->
-
-<!-- ``` -->
-
-<!-- ```{r fig-7b} -->
-<!-- load("../output/revisions/lapl_check/prior_check/plot_N_predict_revision.RData") -->
-
-<!-- all_cohort_box <- all_cohort_mae_df -->
-
-<!-- all_cohort_box$method <- factor(all_cohort_box$method, -->
-<!--   levels = c("mmhp", "dsnl", "m1", "m2", "m3"), -->
-<!--   labels = c( -->
-<!--     "I-MMHP", "DSNL", -->
-<!--     "C-HP", "C-DCHP", -->
-<!--     "C-MMHP" -->
-<!--   ) -->
-<!-- ) -->
-<!-- all_cohort_box$day <- factor(all_cohort_box$day) -->
-
-<!-- plot_cols_pred <- col_df %>% -->
-<!--   filter(method %in% levels(all_cohort_box$method)) %>% -->
-<!--   arrange(factor(method, levels = c( -->
-<!--     "I-MMHP", "DSNL", -->
-<!--     "C-HP", "C-DCHP", "C-MMHP" -->
-<!--   ))) %>% -->
-<!--   pull(cols) -->
-
-<!-- all_cohort_box %>% -->
-<!--   ggplot(aes(x = method, y = norm, fill = method)) + -->
-<!--   # facet_grid(cols = vars(day)) + -->
-<!--   geom_boxplot(alpha = 0.7) + -->
-<!--   scale_fill_manual(values = plot_cols_pred) + -->
-<!--   ggtitle("(a)") + -->
-<!--   theme_bw() + -->
-<!--   theme( -->
-<!--     plot.title = element_text( -->
-<!--       size = 22, -->
-<!--       hjust = 0.5, face = "bold" -->
-<!--     ), -->
-<!--     text = element_text(size = 20), -->
-<!--     axis.text.x = element_blank(), -->
-<!--     axis.ticks.x = element_blank(), -->
-<!--     legend.position = "right" -->
-<!--   ) + -->
-<!--   facet_grid(cols = vars(day)) + -->
-<!--   # guides(color=guide_legend(title="Method")) + -->
-<!--   xlab("Prediction horizon (day)") + -->
-<!--   ylab("MAE") + -->
-<!--   labs(fill = "Method") + -->
-<!--   # ylim(0, 80) + -->
-<!--   NULL -->
-
-<!-- ``` -->
-
-<!-- ```{r fig-7b-pred-rank-spearman-all-cohorts} -->
-<!-- load("../output/revisions/lapl_check/prior_check/plot_rank_predict.RData") -->
-
-<!-- all_cohort_rank_df$method <- factor(all_cohort_rank_df$method, -->
-<!--   levels = c("mmhp", "dsnl", "m1", "m2", "m3"), -->
-<!--   labels = c( -->
-<!--     "I-MMHP", "DSNL", "C-HP", -->
-<!--     "C-DCHP", "C-MMHP" -->
-<!--   ) -->
-<!-- ) -->
-
-<!-- p7 <- ggplot( -->
-<!--   all_cohort_rank_df, -->
-<!--   aes(x = method, y = spearman, fill = method) -->
-<!-- ) + -->
-<!--   # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) + -->
-<!--   geom_boxplot(alpha = 0.7) + -->
-<!--   scale_fill_manual(values = plot_cols_pred) + -->
-<!--   ggtitle("(b)") + -->
-<!--   theme_bw() + -->
-<!--   theme( -->
-<!--     plot.title = element_text(size = 22, hjust = 0.5, face = "bold"), -->
-<!--     text = element_text(size = 20), -->
-<!--     axis.text.x = element_blank(), -->
-<!--     axis.ticks.x = element_blank(), -->
-<!--     legend.position = "right" -->
-<!--   ) + -->
-<!--   facet_grid(cols = vars(day)) + -->
-<!--   xlab("Prediction horizon (day)") + -->
-<!--   ylab("Spearman rank corr.") + -->
-<!--   # coord_cartesian(ylim=c(0,1)) + -->
-<!--   labs(fill = "Method") -->
-
-<!-- p7 -->
-<!-- ``` -->
-
-<!-- ```{r construct data for plot, results='hide',message=FALSE,cache=TRUE} -->
-<!-- library(PlayerRatings) -->
-
-<!-- current_cohort <- 7 -->
-<!-- # 4 best so far, or 7 -->
-
-<!-- load(paste(data_path, cohort_names[current_cohort], -->
-<!--   "/predict_simulation_", cohort_names[current_cohort], -->
-<!--   ".RData", -->
-<!--   sep = "" -->
-<!-- )) -->
-<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]], -->
-<!--   cut_off = 1 -->
-<!-- ) -->
-
-<!-- df <- full_data[[cohort_names[current_cohort]]] -->
-<!-- df <- df[df$Actor != "Start" & df$Actor != "End", ] -->
-<!-- df1 <- expandrows(df) -->
-<!-- df1 <- df1[order(df1$Timestamp), ] # ensure in date order -->
-<!-- df1$event <- 1:nrow(df1) -->
-<!-- glick.df <- df1[, c("event", "Actor", "Recipient", "score"), with = FALSE] -->
-<!-- # need event, actor, recipient, score -->
-<!-- gl <- my_glicko(glick.df, history = TRUE, cval = 2) -->
-
-<!-- # ------------------- period -->
-<!-- training_end <- nrow(df[df$day <= 18, ]) -->
-<!-- testing_end <- nrow(df) - 1 # 1077 #929 for cohort 5 -->
-<!-- newx <- c(training_end:testing_end) -->
-
-<!-- # ----------------- set pars for plot -->
-<!-- my_col <- c("black", "grey", "orange", "red") -->
-<!-- col_vec <- colorRampPalette(my_col)(mice_number) -->
-<!-- ltypes_vec <- rep(1, mice_number) # c(1,2,3,1,2,3,1,2,3,1,2,3) -->
-<!-- history_width <- 3 -->
-<!-- sim_width <- 0.3 -->
-<!-- shade_vec <- makeTransparent(col_vec, 0.2) -->
-<!-- less_shade_vec <- makeTransparent(col_vec, 0.7) -->
-
-<!-- # ---------------- simulation mean and sd -->
-<!-- sim_gl_array <- array(NA, dim = c(12, testing_end - training_end + 1, 1000)) -->
-<!-- for (s in 1:1000) { -->
-<!--   print(s) -->
-<!--   temp_gl <- glickoScoreSimulationWithWindowsReturnAll( -->
-<!--     predict.sim = m3_predict_sim[5:8, s], # 7 for c 2 and 10 -->
-<!--     history.df = glick.df[1:training_end, ] -->
-<!--   ) -->
-<!--   history_matrix <- temp_gl$history[, , 1] -->
-
-<!--   if (testing_end > ncol(temp_gl$history[, , 1])) { -->
-<!--     history_matrix <- cbind( -->
-<!--       history_matrix, -->
-<!--       t(matrix(rep( -->
-<!--         history_matrix[, ncol(history_matrix)], -->
-<!--         testing_end - ncol(temp_gl$history[, , 1]) -->
-<!--       ), -->
-<!--       nrow = testing_end - ncol(temp_gl$history[, , 1]), -->
-<!--       byrow = TRUE -->
-<!--       )) -->
-<!--     ) -->
-<!--   } else { -->
-<!--     # try( -->
-<!--     history_matrix <- history_matrix[, 1:testing_end]  -->
-<!--     # temp_gl$history[,1:testing_end] -->
-<!--     # ) -->
-<!--   } -->
-<!--   sim_gl_array[, , s] <- history_matrix[, training_end:testing_end] -->
-<!-- } -->
-<!-- ``` -->
-
-<!-- ```{r fig-10a-glicko-rating} -->
-<!-- par(mar = c(3, 5, 3, 1)) -->
-<!-- testing_end <- testing_end - 1 -->
-<!-- plot(1, -->
-<!--   type = "n", xlab = "", -->
-<!--   ylab = "Glicko ranking", xlim = c(0, dim(gl$history)[2]), -->
-<!--   ylim = c(min(gl$history[, , 1]), max(gl$history[, , 1])), -->
-<!--   cex.axis = 2, cex.lab = 2 -->
-<!-- ) -->
-<!-- for (m in c(1:mice_number)) { -->
-<!--   # history -->
-<!--   lines(gl$history[m, 1:training_end, 1], -->
-<!--     cex = 0.6, col = col_vec[m], lwd = history_width, lty = ltypes_vec[m] -->
-<!--   ) -->
-<!--   lines(c(rep(NA, training_end), -->
-<!--           gl$history[m, (training_end + 1):testing_end, 1]), -->
-<!--     cex = 0.6, col = shade_vec[m], lwd = history_width, lty = ltypes_vec[m] -->
-<!--   ) -->
-
-<!--   # simulation -->
-<!--   cur_end <- testing_end -->
-<!--   mean_vec <- apply(sim_gl_array[m, , ], 1, function(x) mean(na.omit(x))) -->
-<!--   sd_vec <- apply(sim_gl_array[m, , ], 1, function(x) sd(na.omit(x))) -->
-<!--   polygon(c(newx, rev(newx)), -->
-<!--           c(mean_vec - sd_vec, rev(mean_vec + sd_vec)), -->
-<!--           col = shade_vec[m], border = NA) -->
-<!--   # polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA) -->
-<!--   lines(c(rep(NA, training_end), mean_vec), -->
-<!--     cex = 0.6, col = col_vec[m], lwd = 1, lty = 2 -->
-<!--   ) -->
-<!-- } -->
-
-<!-- # annotate the days -->
-<!-- for (d in c(19:21)) { -->
-<!--   abline(v = nrow(df[df$day <= (d - 1), ]), lty = 2, lwd = 0.4) -->
-<!--   text(x = nrow(df[df$day <= (d - 1), ]), y = 2600, d) -->
-<!-- } -->
-<!-- mtext(text = "(a)", side = 3, line = -2.3, -->
-<!--       outer = TRUE, cex = 2.8, at = 0.5, font = 2) -->
-<!-- ``` -->
-
-<!-- ```{r remove some objects, include=FALSE} -->
-<!-- rm(m3_predict_sim) -->
-<!-- rm(m2_predict_sim) -->
-<!-- rm(m1_predict_sim) -->
-<!-- rm(mmhp_predict_sim) -->
-<!-- rm(fit_agg_rank) -->
-<!-- rm(fit_cohort_hp) -->
-<!-- rm(fit_cohort_dchp) -->
-<!-- rm(fit_cohort_mmhp) -->
-
-<!-- # also removing stan fits as they can cause issues in the next chunk -->
-<!-- ``` -->
+# also removing stan fits as they can cause issues in the next chunk
+```
 
@@
 
-```{r gamma-estimates}
+```{r zeta-estimates}
 zeta_ests <- tibble()

### 2021-09-20 output_scripts/Cohort_level_analysis.Rmd
Revisions apr 21 (#12)
Detailed updates corresponding to a thorough revision of both the simulation studies and analyses

@@
   ))
-  # plot_cols <- col_df %>%
-  #   filter(method %in% c(
-  #     "C-HP",
-  #     "C-DCHP",
-  #     "C-MMHP"
-  #   )) %>%
-  #   pull(cols)
   all_data <- sim_cohort_mmhp %>%
@@
 
+###
+
 cmmhp_gamma$name <- stringr::str_extract(cmmhp_gamma$name, 
@@
 in_perc <- in_perc %>% 
-  left_join(max_out, by = c("name", "cohort"))
+  left_join(max_in, by = c("name", "cohort"))
 
@@
                              levels = paste0("Cohort_", 1:10))
+in_perc$cohort <- factor(in_perc$cohort, 
+                        levels = paste0("Cohort_", 1:10))
+out_perc$cohort <- factor(out_perc$cohort,
+                         levels = paste0("Cohort_", 1:10))
 
@@
   scale_fill_manual(values = "#FDE725FF") +
+  geom_text(data = out_perc, aes(name, 2 * max_est + 1.5, label = perc_out),
+            size = 2) +
+  # scale_y_continuous(breaks = 3) +
   facet_wrap(~cohort, scales = "free", ncol = 2) +
-  geom_text(data = out_perc, aes(name, max_est + 0.25, label = perc_out),
-            size = 2) +
   # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
-  labs(y = "Out Degree", x = element_blank())
+  labs(y = "Out Degree", x = element_blank(),
+       subtitle = "Labels denote % total fights instigated")
 
@@
   scale_fill_manual(values = "#FDE725FF") +
+  # scale_y_continuous(breaks = 3) +
+  geom_text(data = in_perc, aes(name, 2 * max_est + 1.5, label = perc_in),
+            size = 2) +
   facet_wrap(~cohort, scales = "free", ncol = 2) +
-  geom_text(data = in_perc, aes(name, max_est + 0.25, label = perc_in),
-            size = 2) +
   # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
-  labs(y = "In Degree", x = element_blank())
+  labs(y = "In Degree", x = element_blank(),
+       subtitle = "Labels denote % total fights received")
 
@@
 
-```{r overall-fight-info}
+```{r overall-fight-info, message=FALSE, warning=FALSE}
 cohort_summ <- tibble()
@@
 ```
+### Relationship between active fights and difference in Spearman correlation
+
+```{r plot_percent_active_vs_spear_corr}
+# cohort_summ
+
+spear_corr_all <- tibble()
+
+for(current_cohort in 1:10) {
+  load(paste(data_path,
+             cohort_names[current_cohort],
+             "/cohort_mmhp_stan_result_",
+             cohort_names[current_cohort],
+             ".RData",
+             sep = ""
+  ))
+
+  m3_ranks <- sim_cohort_mmhp %>% 
+    select(starts_with("f")) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise("C-MMHP" = median(value))
+
+  load(paste(data_path,
+             cohort_names[current_cohort],
+             "/cohort_hp_stan_result_",
+             cohort_names[current_cohort],
+             ".RData",
+             sep = ""
+  ))
+
+  m1_ranks <- sim_cohort_hp %>% 
+    select(starts_with("f")) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise("C-HP" = median(value))
+
+  load(paste(data_path,
+             cohort_names[current_cohort],
+             "/cohort_dchp_stan_result_",
+             cohort_names[current_cohort],
+             ".RData",
+             sep = ""
+  ))
+
+  m2_ranks <- sim_cohort_dchp %>% 
+    select(starts_with("f")) %>% 
+    pivot_longer(everything()) %>% 
+    group_by(name) %>% 
+    summarise("C-DCHP" = median(value))
+
+  ranks <- m1_ranks %>% 
+    left_join(m2_ranks, by = "name") %>% 
+    left_join(m3_ranks, by = "name")
+  ## same think for spearman rank correlation
+  m1_num <- m1_ranks %>% 
+    rename(value = "C-HP") %>% 
+    arrange(desc(value)) %>% 
+    mutate(chp = 1:12) %>% 
+    mutate(node = stringr::str_extract(name,
+                                       pattern = "[:digit:]+")) %>%
+    mutate(node = as.integer(node)) %>% 
+    select(node, chp)
+
+  m2_num <- m2_ranks %>% 
+    rename(value = "C-DCHP") %>% 
+    arrange(desc(value)) %>% 
+    mutate(cdchp = 1:12) %>% 
+    mutate(node = stringr::str_extract(name,
+                                       pattern = "[:digit:]+")) %>%
+    mutate(node = as.integer(node)) %>% 
+    select(node, cdchp)
+
+  m3_num <- m3_ranks %>% 
+    rename(value = "C-MMHP") %>% 
+    arrange(desc(value)) %>% 
+    mutate(cmmhp = 1:12) %>% 
+    mutate(node = stringr::str_extract(name,
+                                       pattern = "[:digit:]+")) %>%
+    mutate(node = as.integer(node)) %>% 
+    select(node, cmmhp)
+
+  isi_ranks <- tibble(node = expert_rank_10[[current_cohort]],
+                      isi = 1:12)
+  ###
+  rank_df <- m1_num %>% 
+    left_join(m2_num, by = "node") %>% 
+    left_join(m3_num, by = "node") %>% 
+    left_join(isi_ranks, by = "node")
+
+  spear_cor <- cor(rank_df[,2:5], method = "spearman")
+  # spear_corr_list[[current_cohort]] <- spear_cor
+
+  curr_spear <- as_tibble(spear_cor) %>% 
+    mutate(first = c("chp", "cdchp", "cmmhp", "isi")) %>%
+    pivot_longer(cols = chp:isi)
+
+  spear_ind <- as_tibble(upper.tri(spear_cor)) %>% 
+    pivot_longer(everything())
+
+  curr_spear <- curr_spear %>% 
+    bind_cols(spear_ind %>% 
+                             rename(new_name = name, ind = value)) %>% 
+    filter(ind == TRUE) %>% 
+    select(first, name, value) %>% 
+    rename(second = name) %>% 
+    mutate(cohort = current_cohort)
+
+  # %>% 
+  # # filter(first != name) %>% 
+  # # this removes ones which are actually identical
+  # distinct(first, name, value, .keep_all = TRUE) %>% 
+  # rename(second = name) %>% 
+  # mutate(cohort = current_cohort)
+
+  spear_corr_all <- spear_corr_all %>% 
+    bind_rows(curr_spear)
+}
+
+spear_corr_all %>%
+  left_join(cohort_summ, by = "cohort") %>% 
+  filter(first == "chp") %>% 
+  filter(second %in% c("cdchp", "cmmhp")) %>% 
+  pivot_wider(id_cols = cohort, names_from = second, 
+              values_from = c(value, act_perc)) %>% 
+  select(cohort:act_perc_cdchp) %>% 
+  rename(act_perc = act_perc_cdchp) %>% 
+  mutate(corr_diff = value_cdchp - value_cmmhp) %>% 
+  select(cohort, corr_diff, act_perc) %>% 
+  ggplot(aes(corr_diff, act_perc)) +
+  geom_point() +
+  labs(y = "Percent fights Active", x = "Correlation Differernce",
+       subtitle = "Correlation difference between C-HP/C-DCHP and C-HP/C-MMHP")
+# then join this with cohort summ and do the plot
+```

### 2021-09-20 output_scripts/Paper_Plots.Rmd
Revisions apr 21 (#12)
Detailed updates corresponding to a thorough revision of both the simulation studies and analyses

@@
   dev = "png", fig.height = 5, fig.width = 7,
-  warning = FALSE, cache = FALSE
+  warning = FALSE, cache = TRUE
 )
@@
 ```{r fig-4a, eval = revision_plots, message=FALSE, warning=FALSE}
-sim_data_path <- here("output", "revisions", "lapl_check", "sim_lapl", "/")
+sim_data_path <- here("output", "revisions", "aug_run", "sims", "/")
 
@@
 ## change this to just list all files with a pattern
-sims <- 1:50
-sims <- sims[c(-37,-45,-46, -50)]
+sims <- list.files(sim_data_path, pattern = "sim_model3_fit123")
 
@@
   load(paste0(sim_data_path,
-              "sim_model3_fit123_",
-              curr_sim,
-              ".RData"))
+              curr_sim))
 
   f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
-  m1_ranks <- apply(f_m1, 2, mean)
+  m1_ranks <- apply(f_m1, 2, median)
 
@@
 
-## this is just the mean from each simulation, not the posterior draws
+## this is just the median from each simulation, not the posterior draws
 ```
@@
   ),
-  iter = 1000, chains = 4, control = list(adapt_delta = 0.99)
+  iter_warmup = 500,
+  iter_sampling = 500,
+  chains = 4,
+  adapt_delta = 0.95
 )
 # print(fit_dsnl_inactive, pars = c("x"))
-sim_dsnl_inactive <- rstan::extract(fit_dsnl_inactive)
-
-save(sim_dsnl_active, fit_dsnl_active, utility_state_day,
-  sim_dsnl_inactive, fit_dsnl_inactive, social_state_day,
-  file = paste(data_path, cohort_names[current_cohort],
+inactive_fit <- fit_dsnl_inactive$draws()
+sim_dsnl_inactive <- posterior::as_draws_df(inactive_fit)
+
+save(sim_dsnl_active,
+     fit_dsnl_active,
+     utility_state_day,
+     sim_dsnl_inactive,
+     fit_dsnl_inactive,
+     social_state_day,
+     file = paste(data_path,
+                  cohort_names[current_cohort],
                   "/dsnl_state_separation_stan_result_",
@@
 
-Need to update this to read in cmdstan results.
-
-```{r process data for plot 10b, cache=TRUE}
+```{r process data for plot 10b, cache=FALSE}
 library(PlayerRatings)
@@
 ```{r fig-10b-rank-correlation}
+print(current_cohort)
 par(mar = c(3, 5, 3, 1))

### 2021-09-20 output_scripts/aug_updates.Rmd
Revisions apr 21 (#12)
Detailed updates corresponding to a thorough revision of both the simulation studies and analyses

@@
 
-data_path <- "../output/"
+data_path <- "../output/revisions/lapl_check/"
 
@@
 
-  mean_latent_rank <- apply(sim_cohort_mmhp$f,2,mean)
+  mean_latent_rank <- apply(sim_cohort_mmhp %>% 
+                              select(starts_with("f")),2,mean)
 
-  out_degree <- apply(sim_cohort_mmhp$gamma,2,mean)
-  in_degree <- apply(sim_cohort_mmhp$zeta,2,mean)
+  out_degree <- apply(sim_cohort_mmhp %>% 
+                        select(starts_with("gamma")),2,mean)
+  in_degree <- apply(sim_cohort_mmhp %>% 
+                       select(starts_with("zeta")),2,mean)
+
+  degs <- tibble(expert = expert_rank_10[[current_cohort]],
+                  latent = mean_latent_rank,#[expert],
+                 out_deg = out_degree,#[expert],
+                 in_deg = in_degree)#[expert])
+
+  p <- ggplot(degs,aes(latent,out_deg)) + geom_point() + 
+    #scale_y_continuous(breaks = c(12:1), trans = "reverse") + 
+    ggtitle(paste("Out Degree vs Latent Cohort ", current_cohort,sep="")) + 
+    ylab("Out Degree (Gamma)") + xlab("Latent Rank")
+  #print(p)
+  q <- ggplot(degs,aes(latent,in_deg)) + geom_point() +
+    ggtitle(paste("In Degree vs Latent Cohort ",current_cohort,sep="")) +
+    ylab("In Degree (Zeta)") + xlab("Latent Rank")
+  #print(q)
+  grid.arrange(p,q, nrow = 1)
+}
+
+```
+
+```{r repeat-dchp}
+for(current_cohort in 1:10) {
+  #cat("Cohort ", current_cohort,"\n",sep="")
+  load(paste(data_path,cohort_names[current_cohort],
+             "/cohort_dchp_stan_result_",cohort_names[current_cohort],
+             ".RData",sep=''))
+
+  mean_latent_rank <- apply(sim_cohort_dchp %>% 
+                              select(starts_with("f")),2,mean)
+
+  out_degree <- apply(sim_cohort_dchp %>% 
+                        select(starts_with("gamma")),2,mean)
+  in_degree <- apply(sim_cohort_dchp %>% 
+                       select(starts_with("zeta")),2,mean)
 

### 2021-09-20 output_scripts/revisions_may.Rmd
Revisions apr 21 (#12)
Detailed updates corresponding to a thorough revision of both the simulation studies and analyses

@@
 
-```{r simulate_20_nodes}
+```{r simulate_20_nodes, eval=FALSE, include=FALSE}
 num_nodes <- 20
@@
 
-```{r plot_pair}
+```{r plot_pair, eval=FALSE, include=FALSE}
 start <- 20
@@
 
-```{r residuals-immhp-sim}
+```{r residuals-immhp-sim, eval=FALSE, include=FALSE}
 pr_matrix <- readRDS(here("output", "revisions", "pr_matrix_immhp.RDS"))
@@
 
-```{r repeat-all-cohorts}
+```{r repeat-all-cohorts, eval=FALSE, include=FALSE}
 
@@
 
-```{r take-mean-ks/pr}
+```{r take-mean-ks/pr, include=FALSE}
 m1_ks <- tibble(Method = "C-HP",

### 2021-09-20 lib/circularPlot.R

@@ -1,0 +1,129 @@
+addalpha <- function(colors, alpha=1.0) {
+  r <- col2rgb(colors, alpha=TRUE)
+  # Apply alpha
+  r[4,] <- alpha*255
+  r <- r/255.0
+  return(rgb(r[1,], r[2,], r[3,], r[4,]))
+}
+
+myCircularPlot <- function(cur.matrix, cur.order, cur.color,
+                           cur.gap, cur.ID = c(1:12)){
+  par(mfrow = c(1, 1),
+      mgp = c(0, 0, 0),
+      mar = c(1, 0, 0, 0),
+      oma = c(0, 0, 0, 0))
+  df1 <- data.frame(order = cur.order,
+                    ID = cur.ID,
+                    stringsAsFactors = FALSE)
+  if(length(cur.order)==12){
+    m <- cur.matrix
+    df1 <- data.frame(order = cur.order,
+                      ID = as.character(c(1:12)),
+                      stringsAsFactors = FALSE)
+    
+  }else{
+    m <- cur.matrix
+    df1 <- data.frame(order = cur.order,
+                      ID = cur.ID,
+                      stringsAsFactors = FALSE)
+  }
+  dimnames(m) <- list(orig = df1$ID, dest = df1$ID)
+  ### Sort order of data.frame and matrix for plotting in circos
+  df1 <- arrange(df1, order)
+  df1$ID <- factor(df1$ID, levels = df1$ID)
+  m <- m[levels(df1$ID), levels(df1$ID)]
+  ### Define ranges of circos sectors and their colors (both of the sectors and the links)
+  df1$xmin <- 0
+  df1$xmax <- rowSums(m) + colSums(m)
+  n <- nrow(df1)
+  
+  df1$rcol<- cur.color#rgb(df1$r, df1$g, df1$b, max = 255)
+  df1$lcol<- addalpha(df1$rcol, alpha = rep(0.5, n)) #rgb(df1$r, df1$g, df1$b, alpha=100, max = 255)
+  
+  ### Plot sectors (outer part)
+  circos.clear()
+  
+  ### Basic circos graphic parameters
+  circos.par(
+    cell.padding = c(0, 0, 0, 0), track.margin = c(0, 0.15),
+    start.degree = 90,
+    gap.degree = cur.gap
+  )
+
+  ### Sector details
+  circos.initialize(factors = df1$ID, xlim = cbind(df1$xmin, df1$xmax))
+  ### Plot sectors
+  circos.trackPlotRegion(
[…]

### 2021-09-20 lib/cleanData.R

@@ -87,11 +87,18 @@ cleanData <- function(raw_data, cut_off = 3, N = 12){
       max_interevent[i] <- 0
     }
   }
-  return(list(N_count = N_count, time_matrix = time_matrix, max_interevent = max_interevent,
-              I_fit = I_fit, J_fit = J_fit, day_hour = day_hour[1:M], 
+  return(list(N_count = N_count,
+              time_matrix = time_matrix,
+              max_interevent = max_interevent,
+              I_fit = I_fit,
+              J_fit = J_fit,
+              day_hour = day_hour[1:M], 
               indicator_each_pair = indicator_each_pair, M = M,
-              start = start[1:M], end = end[1:M],
-              day = day[1:M], new_observation = new_observation[1:M], time_stamp = time_stamp[1:M],
+              start = start[1:M],
+              end = end[1:M],
+              day = day[1:M],
+              new_observation = new_observation[1:M],
+              time_stamp = time_stamp[1:M],
               observation_change = observation_change/60))
 }
 

### 2021-09-20 lib/inferLatentMmhp.R

@@ -25,8 +25,12 @@ myViterbi <- function(events, param, termination = NULL, if.print = FALSE){
   
   ## --- Calculation for log probability of Markov transition logP_ij(t)
   for(n in 1:(N+1)){
-    probs_1_matrix[n,1] <- log(param$q2/(param$q1+param$q2)+param$q1/(param$q1+param$q2)*exp(-(param$q1+param$q2)*interevent[n])) # 1->1
-    probs_2_matrix[n,2] <- log(param$q1/(param$q1+param$q2)+param$q2/(param$q1+param$q2)*exp(-(param$q1+param$q2)*interevent[n])) # 2->2
+    probs_1_matrix[n,1] <- log(param$q2/(param$q1+param$q2) + 
+                                 param$q1/(param$q1+param$q2)*
+                                 exp(-(param$q1+param$q2)*interevent[n])) # 1->1
+    probs_2_matrix[n,2] <- log(param$q1/(param$q1+param$q2) + 
+                                 param$q2/(param$q1+param$q2)*
+                                 exp(-(param$q1+param$q2)*interevent[n])) # 2->2
     probs_1_matrix[n,2] <- log(1-exp(probs_2_matrix[n,2])) # 2->1
     probs_2_matrix[n,1] <- log(1-exp(probs_1_matrix[n,1])) # 1->2
   }

### 2021-09-20 lib/prepareDataStan.R

@@ -14,16 +14,32 @@
 ############################################################################
 prepareDataStan <- function(current_cohort){
   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-  return_df <- cleanObservationPeriod(current_cohort, full_data[[cohort_names[current_cohort]]], clean_data)
+  return_df <- cleanObservationPeriod(current_cohort,
+                                      full_data[[cohort_names[current_cohort]]],
+                                      clean_data)
   
-  unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% dplyr::summarize(count=n(), observe=list(observe.id))
-  unique_observe_win <- unique(return_df[,c("observe.id","observe.time","observe.start","observe.end")])
+  unique_pairs_df <- return_df %>% 
+    group_by(initiator, recipient) %>%
+    dplyr::summarize(count=n(), observe=list(observe.id))
+  unique_observe_win <- unique(return_df[,c("observe.id",
+                                            "observe.time",
+                                            "observe.start",
+                                            "observe.end")])
   
-  time_array <- array(0,dim=c(nrow(unique_pairs_df),max(return_df$observe.id),max(unlist(lapply(return_df$event.times,length)))+1))
-  event_array <- array(0,dim=c(nrow(unique_pairs_df),max(return_df$observe.id),max(unlist(lapply(return_df$event.times,length)))))
-  count_matrix <- matrix(0,nrow=nrow(unique_pairs_df),ncol=max(return_df$observe.id))
-  delta_window <- c(0,unique_observe_win$observe.start[-1]-unique_observe_win$observe.end[-nrow(unique_observe_win)])
-  finishing_time <- matrix(0,nrow=nrow(unique_pairs_df),ncol=max(return_df$observe.id))
+  time_array <- array(0, dim = c(nrow(unique_pairs_df),
+                              max(return_df$observe.id),
+                              max(unlist(lapply(return_df$event.times,length)))+1))
+  event_array <- array(0, dim = c(nrow(unique_pairs_df),
+                               max(return_df$observe.id),
+                               max(unlist(lapply(return_df$event.times,length)))))
+  count_matrix <- matrix(0, nrow = nrow(unique_pairs_df),
+                         ncol = max(return_df$observe.id))
+  delta_window <- c(0,
+                    unique_observe_win$observe.start[-1] - 
+                      unique_observe_win$observe.end[-nrow(unique_observe_win)])
+  finishing_time <- matrix(0,
[…]

### 2021-09-20 plot4.R

@@ -1,0 +1,595 @@
+# library(here)
+# library(tidyverse)
+
+plot.s <- 26 # 8 is pretty good
+plot.i <- 10
+plot.j <- 9
+
+# 29 10 -> 9 also decent
+# 26 10 -> 9 also decent
+#17 10 -> 9 decent
+#1, 10 -> 8 not too bad
+#8 10 -> 9 also
+
+### only going up to 100 now
+cur_i <- plot.i
+cur_j <- plot.j
+
+sim_data_path <- here("output", "revisions", "lapl_check", "sim_lapl", "/")
+
+load(paste0(
+  sim_data_path, "/", "sim_model3_fit123_",
+  plot.s,
+  ".RData"
+))
+test.mmhp <- sim_model3_data$mmhp_matrix[plot.i, plot.j][[1]]
+temp.t <- test.mmhp$tau
+current.n <- length(temp.t) - 1
+time.segment <- seq(0, tail(temp.t, 1), length.out = 5000)
+
+### Preprocess the model inference result
+## model 1
+#########
+
+## get f from cmdstan 
+
+f_draws <- sim_model3_stan_sim1 %>% 
+  select(starts_with("f"))
+
+model1_par_est <- list(
+  lambda0 = mean(sim_model3_stan_sim1$lambda0),
+  eta_1 = mean(sim_model3_stan_sim1$eta_1),
+  eta_2 = mean(sim_model3_stan_sim1$eta_2),
+  eta_3 = mean(sim_model3_stan_sim1$eta_3),
+  beta = mean(sim_model3_stan_sim1$beta),
+  f = apply(f_draws, 2, mean)
+)
+lambda.m1 <- uniHawkesIntensityNumeric(
+  object = list(
+    lambda0 =
+      model1_par_est$lambda0,
+    alpha =
+      model1_fn$alpha.fun(
+        model1_par_est$f[plot.i],
+        model1_par_est$f[plot.j],
+        model1_par_est$eta_1,
+        model1_par_est$eta_2,
+        model1_par_est$eta_3
+      ),
+    beta = model1_par_est$beta
+  ),
+  events = temp.t,
+  time.vec = time.segment
+)
+
+
+## model2 ####
+gamma_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("gamma"))
+
+zeta_draws <- sim_model3_stan_sim2 %>% 
+  select(starts_with("zeta"))
+
[…]

### 2021-09-20 run_scripts/active_dsnl.R

@@ -1,0 +1,205 @@
+
+### code ####
+# #run this if running on the cluster
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
+# ### set cohort_id based on job num
+jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+jobid <- as.numeric(jobid)
+cohort_id <- jobid
+#cohort_id <- 1
+#####
+
+data_path <- "output/revisions/lapl_check/"
+
+library(cmdstanr)
+options(mc.cores = parallel::detectCores())
+
+
+library(compete)
+#library(RColorBrewer)
+#library(Hmisc)
+#library(wCorr)
+#library(tidyverse)
+library(dplyr)
+#library(R.utils)
+#library(fields)
+
+
+
+source('lib/naiveRankHierarchy.R')
+source('lib/expertRankHierarchy.R')
+source('lib/cleanData.R') 
+source('lib/prepareDataStan.R') 
+source('lib/inferLatentMmhp.R')
+source('lib/plotUtil.R') 
+source('lib/mmhp.R')
+source('lib/uniHawkes.R')
+source('lib/simulatePrediction.R')
+source('lib/myGlicko.R')
+source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
+source('lib/matrixPlotParameter.R')
+source('lib/residualStructureScore.R')
+
+
+
+
+
+#### then load in the stan fit here ###
+
+full_data <- readRDS("data/mice.RData")
+# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
+cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cut_off <- 3
+mice_number <- 12
+
+
+model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
+
+model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
[…]

### 2021-09-20 run_scripts/agg_rank.R

@@ -5,45 +5,45 @@
 
 ### code ###
 ## run this section if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 # ### set cohort_id based on job num
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
 cohort_id <- jobid
-#cohort_id <- 1
+# cohort_id <- 1
 #####
 
-save_data_path <- "output/common_rate/"
+save_data_path <- "output/revisions/aug_run/"
 
 
-library(rstan)
+library(cmdstanr)
 options(mc.cores = parallel::detectCores())
 
 
 library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
+# library(RColorBrewer)
+# library(Hmisc)
+# library(wCorr)
+# library(tidyverse)
 library(dplyr)
-#library(R.utils)
-#library(fields)
+# library(R.utils)
+# library(fields)
 
 
 
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
+source("lib/naiveRankHierarchy.R")
+source("lib/expertRankHierarchy.R")
+source("lib/cleanData.R")
+source("lib/prepareDataStan.R")
+source("lib/inferLatentMmhp.R")
+source("lib/plotUtil.R")
+source("lib/mmhp.R")
+source("lib/uniHawkes.R")
+source("lib/simulatePrediction.R")
+source("lib/myGlicko.R")
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
+source("lib/matrixPlotParameter.R")
[…]

### 2021-09-20 run_scripts/c_dchp.R

@@ -2,14 +2,14 @@
 
 ### code ###
 # run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 # ### set cohort_id based on job num
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
 cohort_id <- jobid
 
-save_data_path <- "output/common_rate/"
-library(rstan)
+save_data_path <- "output/revisions/aug_run/"
+library(cmdstanr)
 options(mc.cores = parallel::detectCores())
 
 
@@ -74,18 +74,27 @@ print(paste("Cohort",current_cohort))
 
 
 # then fit DC C-HP here for each cohort
-
+model2 <- cmdstan_model("lib/model2.stan")
 
 #### fit the stan model ####
 print(current_cohort)
 stan_input_lst <- prepareDataStan(current_cohort)
 stan_input_lst$scale <- 0.1
-fit_cohort_dchp <- stan("lib/model2.stan",
-                        data = stan_input_lst,
-                        warmup = 2000, iter = 3000, thin = 4, chains = 4,
-                        control=list(adapt_delta=0.95))
-sim_cohort_dchp <- rstan::extract(fit_cohort_dchp)
-dir.create(paste(save_data_path, cohort_names[current_cohort],sep=''), recursive = TRUE, showWarnings = FALSE)
+fit_cohort_dchp <- model2$sample(data = stan_input_lst,
+                                 iter_warmup = 1000,
+                                 iter_sampling = 1000,
+                                 thin = 4,
+                                 chains = 4,
+                                 adapt_delta=0.95,
+                                 refresh = 100)
+
+
+dchp_fit <- fit_cohort_dchp$draws()
+sim_cohort_dchp <- posterior::as_draws_df(dchp_fit)
+
+# sim_cohort_dchp <- rstan::extract(fit_cohort_dchp)
+dir.create(paste(save_data_path, cohort_names[current_cohort],sep=''),
+           recursive = TRUE, showWarnings = FALSE)
 save(sim_cohort_dchp, fit_cohort_dchp,
      file = paste(save_data_path,cohort_names[current_cohort],
[…]

### 2021-09-20 run_scripts/c_hp.R

@@ -2,7 +2,7 @@
 
 ### code ####
 # #run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 # ### set cohort_id based on job num
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
@@ -10,9 +10,9 @@ cohort_id <- jobid
 #cohort_id <- 1
 #####
 
-save_data_path <- "output/common_rate/"
+save_data_path <- "output/revisions/aug_run/"
 
-library(rstan)
+library(cmdstanr)
 options(mc.cores = parallel::detectCores())
 
 
@@ -78,7 +78,7 @@ print(paste("Cohort",current_cohort))
 
 
 # then fit C-HP here for each cohort
-
+model1 <- cmdstan_model("lib/model1.stan")
 
 #### fit stan model ####
 print(paste("Cohort",current_cohort))
@@ -86,126 +86,185 @@ stan_input_lst <- prepareDataStan(current_cohort)
 stan_input_lst$alpha_id <- expert_rank_10[[current_cohort]][1]
 stan_input_lst$delta_1 <- rep(0.5,stan_input_lst$N_til)
 
-fit_cohort_hp <- stan("lib/model1.stan", 
-                      data = stan_input_lst,
-                      warmup = 1000, iter = 2000, chains = 4, thin=4,
-                      control=list(adapt_delta=0.98))
-sim_cohort_hp <- rstan::extract(fit_cohort_hp)
-dir.create(paste(save_data_path, cohort_names[current_cohort],sep=''), recursive = TRUE, showWarnings = FALSE)
+
+
+
+fit_cohort_hp <- model1$sample(data = stan_input_lst,
+                               iter_warmup = 1000,
+                               iter_sampling = 1000,
+                               chains = 4,
+                               thin = 4,
+                               adapt_delta=0.98,
+                               refresh = 200)
+
+chp_fit <- fit_cohort_hp$draws()
+sim_cohort_hp <- posterior::as_draws_df(chp_fit)
+
+dir.create(paste(save_data_path,
+                 cohort_names[current_cohort],sep=''),
+           recursive = TRUE,
+           showWarnings = FALSE)
 save(sim_cohort_hp, fit_cohort_hp,
[…]

### 2021-09-20 run_scripts/c_mmhp_dc.R

@@ -4,46 +4,48 @@
 
 ### code ###
 ## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 # ### set cohort_id based on job num
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
 cohort_id <- jobid
-#cohort_id <- 1
+# cohort_id <- 1
 ####
-save_data_path <- "output/"  #"output_june30/"
+save_data_path <- "output/revisions/aug_run/" # "output_june30/"
 
 ### specify the number of segments here
 no_segments <- 500
 
-library(rstan)
+# library(rstan)
+library(cmdstanr)
 options(mc.cores = parallel::detectCores())
 
 
 library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
+# library(RColorBrewer)
+# library(Hmisc)
+# library(wCorr)
+# library(tidyverse)
 library(dplyr)
-#library(R.utils)
-#library(fields)
+library(posterior)
+# library(R.utils)
+# library(fields)
 
 
 
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
+source("lib/naiveRankHierarchy.R")
+source("lib/expertRankHierarchy.R")
+source("lib/cleanData.R")
+source("lib/prepareDataStan.R")
+source("lib/inferLatentMmhp.R")
+source("lib/plotUtil.R")
+source("lib/mmhp.R")
+source("lib/uniHawkes.R")
+source("lib/simulatePrediction.R")
+source("lib/myGlicko.R")
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
[…]

### 2021-09-20 run_scripts/cluster_setup.R

@@ -1,6 +1,7 @@
 ### script to be sourced to run on the cluster
 
 
-.libPaths("/rigel/stats/users/ogw2103/rpackages")
-setwd("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/")
+.libPaths("/moto/stats/users/ogw2103/rpackages")
+setwd("/moto/stats/users/ogw2103/Code/MMHP_Latent/")
 library(here)
+library(R.utils)

### 2021-09-20 run_scripts/diagnostics.R

@@ -6,14 +6,14 @@
 
 ### code ###
 ## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 ### set cohort_id based on job num
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
 cohort_id <- jobid
 # cohort_id <- 1
 ####
-data_path <- "output/"
+data_path <- "output/revisions/aug_run/"
 
 
 # library(rstan)
@@ -48,8 +48,6 @@ source('lib/residualStructureScore.R')
 
 
 
-
-
 #### then load in the data ####
 
 full_data <- readRDS("data/mice.RData")
@@ -60,9 +58,11 @@ cut_off <- 3
 mice_number <- 12
 
 
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
+model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){
+  return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
 
-model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
+model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){
+  return(eta1*x*y*exp(-eta2*abs(x-y)))},
                   q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
                   q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
 
@@ -81,13 +81,15 @@ current_cohort <- cohort_id
 print(paste("Cohort",current_cohort))
 
 clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
-return_df <- cleanObservationPeriod(current_cohort, clean_data)
+return_df <- cleanObservationPeriod(current_cohort,
+                                    full_data[[cohort_names[current_cohort]]],
+                                    clean_data)
 unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
-  summarize(count=n(),
-            observe=list(observe.id),
-            observe.length=list(observe.time),
-            no.events=list(no.events))
[…]

### 2021-09-20 run_scripts/dsnl.R

@@ -3,43 +3,43 @@
 
 ### code ###
 ## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 # ### set cohort_id based on job num
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
 cohort_id <- jobid
 # cohort_id <- 1
 ####
-save_data_path <- "output/common_rate/"
+save_data_path <- "output/revisions/aug_run/"
 
-library(rstan)
+library(cmdstanr)
 options(mc.cores = parallel::detectCores())
 
 
 library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
+# library(RColorBrewer)
+# library(Hmisc)
+# library(wCorr)
+# library(tidyverse)
 library(dplyr)
-#library(R.utils)
-#library(fields)
+# library(R.utils)
+# library(fields)
 
 
 
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
+source("lib/naiveRankHierarchy.R")
+source("lib/expertRankHierarchy.R")
+source("lib/cleanData.R")
+source("lib/prepareDataStan.R")
+source("lib/inferLatentMmhp.R")
+source("lib/plotUtil.R")
+source("lib/mmhp.R")
+source("lib/uniHawkes.R")
+source("lib/simulatePrediction.R")
+source("lib/myGlicko.R")
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
+source("lib/matrixPlotParameter.R")
+source("lib/residualStructureScore.R")
 
 
 
[…]

### 2021-09-20 run_scripts/i_mmhp.R

@@ -4,7 +4,7 @@
 
 ### code ###
 ## run this section if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 source("run_scripts/cluster_setup.R")
 ### set cohort_id based on job num
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
@@ -13,11 +13,11 @@ cohort_id <- jobid
 #cohort_id <- 1
 #####
 
-save_data_path <- "output/common_rate/"
+save_data_path <- "output/revisions/aug_run/"
 
 no_segments <- 500
 
-library(rstan)
+library(cmdstanr)
 options(mc.cores = parallel::detectCores())
 
 
@@ -87,15 +87,31 @@ print(paste("Cohort",current_cohort))
 print(current_cohort)
 stan_input_lst <- prepareDataStanIMMHP(current_cohort)
 
-fit_mmhp_sep <- stan("lib/I-MMHP.stan",
-                     data=stan_input_lst,
-                     warmup = 2000, iter = 3000, thin = 4, chains = 4) 
-sim_mmhp_sep <- rstan::extract(fit_mmhp_sep)
-dir.create(paste(save_data_path, cohort_names[current_cohort],sep=''), recursive = TRUE, showWarnings = FALSE)
+immhp_model <- cmdstan_model("lib/I-MMHP.stan")
+
+fit_mmhp_sep <- immhp_model$sample(data = stan_input_lst,
+                                   iter_warmup = 1000,
+                                   iter_sampling = 1000,
+                                   thin = 4,
+                                   chains = 4) 
+
+# sim_mmhp_sep <- rstan::extract(fit_mmhp_sep)
+immhp_fit <- fit_mmhp_sep$draws()
+sim_mmhp_sep <- posterior::as_draws_df(immhp_fit)
+
+
+dir.create(paste(save_data_path,
+                 cohort_names[current_cohort],
+                 sep = ''),
+           recursive = TRUE,
+           showWarnings = FALSE)
 save(sim_mmhp_sep, fit_mmhp_sep,
-     file = paste(save_data_path,cohort_names[current_cohort],
-                  "/sep_mmhp_stan_result_",cohort_names[current_cohort],
-                  ".RData",sep=''))
+     file = paste(save_data_path,
+                  cohort_names[current_cohort],
[…]

### 2021-09-20 run_scripts/m3_immhp_sim.R

@@ -1,0 +1,253 @@
+#### Rerun the modified simulation fits based on the modified Stan models ####
+### Simulate Data from Model 3 and fit I-MMHP to each Pair
+
+#### if running on cluster ####
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
+
+data_path <- "output/revisions/"
+
+# library(rstan)
+library(cmdstanr)
+library(R.utils)
+library(ppdiag)
+# library(compete)
+options(mc.cores = parallel::detectCores())
+# rstan_options(auto_write = TRUE)
+jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+jobid <- as.numeric(jobid)
+sim_id <- jobid
+
+#Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
+
+
+#### Load source code from ../lib/ ####
+source('lib/uniHawkes.R')
+source('lib/mmhp.R')
+source('lib/simulatePrediction.R')
+source('lib/plotUtil.R')
+source('lib/inferLatentMmhp.R')
+source('lib/drawIntensity.R')
+#source('lib/prepareDataStan.R')
+#source('lib/cleanData.R')
+# Define global variable
+n_sim <- 1
+num_nodes <- 20
+cut_off <- 3
+obs_time <- 200
+
+model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
+  return(eta1 * x * y * exp(-eta2 * abs(x-y))/(1 + exp(-eta3 *(x-y))))})
+
+model3_fn <- list(alpha.fun = function(x, y, eta1, eta2){
+  return(eta1*x*y*exp(-eta2*abs(x-y)))},
+  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
+  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
+
+
+#### Save the simulation parameters ####
+
+object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
+  return(eta1*x*y*exp(-eta2*abs(x-y)))},
+  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
+  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
+
+object_par <- list(sim_lambda_1 = 0.2,
+                   sim_eta_1 = 1.5, # this has to be < beta
+                   gamma_var = runif(n = num_nodes, min = 0.01, max = 0.05),
[…]

### 2021-09-20 run_scripts/overall_predict.R

@@ -3,43 +3,45 @@
 
 ### code ###
 ## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 # ### set cohort_id based on job num
 # jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 # jobid <- as.numeric(jobid)
 # cohort_id <- jobid
 # cohort_id <- 1
 ####
-data_path <- "output/"
 
-library(rstan)
-options(mc.cores = parallel::detectCores())
+data_path <- "output/revisions/aug_run/"
+
+# library(rstan)
+# options(mc.cores = parallel::detectCores())
+options(dplyr.summarise.inform = FALSE)
 
 library(PlayerRatings)
 library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
+# library(RColorBrewer)
+# library(Hmisc)
 library(wCorr)
-#library(tidyverse)
+# library(tidyverse)
 library(dplyr)
-#library(R.utils)
-#library(fields)
+# library(R.utils)
+# library(fields)
 
 
 
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
+source("lib/naiveRankHierarchy.R")
+source("lib/expertRankHierarchy.R")
+source("lib/cleanData.R")
+source("lib/prepareDataStan.R")
+source("lib/inferLatentMmhp.R")
+source("lib/plotUtil.R")
+source("lib/mmhp.R")
+source("lib/uniHawkes.R")
+source("lib/simulatePrediction.R")
+source("lib/myGlicko.R")
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
+source("lib/matrixPlotParameter.R")
[…]

### 2021-09-20 run_scripts/predict.R

@@ -3,44 +3,44 @@
 
 ### code ###
 ## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 ### set cohort_id based on job num
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
 cohort_id <- jobid
-#cohort_id <- 1
+# cohort_id <- 1
 ####
-data_path <- "output/"
+data_path <- "output/revisions/aug_run/"
 
 
-library(rstan)
+library(cmdstanr)
 options(mc.cores = parallel::detectCores())
 
 
 library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
+# library(RColorBrewer)
+# library(Hmisc)
+# library(wCorr)
+# library(tidyverse)
 library(dplyr)
 library(R.utils)
-#library(fields)
+# library(fields)
 
 
 
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
+source("lib/naiveRankHierarchy.R")
+source("lib/expertRankHierarchy.R")
+source("lib/cleanData.R")
+source("lib/prepareDataStan.R")
+source("lib/inferLatentMmhp.R")
+source("lib/plotUtil.R")
+source("lib/mmhp.R")
+source("lib/uniHawkes.R")
+source("lib/simulatePrediction.R")
+source("lib/myGlicko.R")
 source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
+source("lib/matrixPlotParameter.R")
+source("lib/residualStructureScore.R")
 
 
 
[…]

### 2021-09-20 run_scripts/process_sims_immhp.R

@@ -1,0 +1,82 @@
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
+
+data_path <- "output/revisions/"
+
+# library(rstan)
+library(cmdstanr)
+library(R.utils)
+library(ppdiag)
+# library(compete)
+options(mc.cores = parallel::detectCores())
+# rstan_options(auto_write = TRUE)
+jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+jobid <- as.numeric(jobid)
+sim_id <- jobid
+
+#Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
+
+
+#### Load source code from ../lib/ ####
+source('lib/uniHawkes.R')
+source('lib/mmhp.R')
+source('lib/simulatePrediction.R')
+source('lib/plotUtil.R')
+source('lib/inferLatentMmhp.R')
+source('lib/drawIntensity.R')
+#source('lib/prepareDataStan.R')
+#source('lib/cleanData.R')
+# Define global variable
+n_sim <- 1
+num_nodes <- 20
+cut_off <- 3
+obs_time <- 200
+
+model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
+  return(eta1 * x * y * exp(-eta2 * abs(x-y))/(1 + exp(-eta3 *(x-y))))})
+
+model3_fn <- list(alpha.fun = function(x, y, eta1, eta2){
+  return(eta1*x*y*exp(-eta2*abs(x-y)))},
+  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
+  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
+
+
+#### Save the simulation parameters ####
+
+object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
+  return(eta1*x*y*exp(-eta2*abs(x-y)))},
+  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
+  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
+
+
+
+load(paste(data_path, "sim_model3_immhp_", ".RData", sep = ''))
+
+clean_sim_data <- cleanSimulationData(raw_data = sim_model3_data, 
+                                      cut_off = cut_off,
+                                      N = length(object_par$f_vec_1))
+
+
[…]

### 2021-09-20 run_scripts/rank_stability_exp.R

@@ -1,0 +1,127 @@
+##### fit each of our 3 models to the first 14 days of data
+##### compare to fitting to last 14 days
+
+
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
+# ### set cohort_id based on job num
+jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+jobid <- as.numeric(jobid)
+cohort_id <- jobid
+#cohort_id <- 1
+####
+save_data_path <- "output/revisions/rank_stab/"  #"output_june30/"
+
+### specify the number of segments here
+no_segments <- 500
+
+library(cmdstanr)
+options(mc.cores = parallel::detectCores())
+
+
+library(compete)
+#library(RColorBrewer)
+#library(Hmisc)
+#library(wCorr)
+#library(tidyverse)
+library(dplyr)
+#library(R.utils)
+#library(fields)
+
+
+
+source('lib/naiveRankHierarchy.R')
+source('lib/expertRankHierarchy.R')
+source('lib/cleanData.R') 
+source('lib/prepareDataStan.R') 
+source('lib/inferLatentMmhp.R')
+source('lib/plotUtil.R') 
+source('lib/mmhp.R')
+source('lib/uniHawkes.R')
+source('lib/simulatePrediction.R')
+source('lib/myGlicko.R')
+source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
+source('lib/matrixPlotParameter.R')
+source('lib/residualStructureScore.R')
+
+
+
+
+
+#### load the data ####
+full_data <- readRDS("data/mice.RData")
+# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
+cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
+cut_off <- 3
+mice_number <- 12
+
+
+model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
+
[…]

### 2021-09-20 run_scripts/sim_fits.R

@@ -1,15 +1,18 @@
 #### Rerun the modified simulation fits based on the modified Stan models ####
-
+### Simulate Data from Model 3 and fit each of the 3 models to this data
 
 #### if running on cluster ####
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 
-data_path <- "output/sims_m3_update/"
+data_path <- "output/revisions/aug_run/sims/"
 
-library(rstan)
-# library(compete)
+library(cmdstanr)
+library(R.utils)
+library(tidyr)
+library(dplyr)
+library(compete)
 options(mc.cores = parallel::detectCores())
-rstan_options(auto_write = TRUE)
+# rstan_options(auto_write = TRUE)
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
 sim_id <- jobid
@@ -27,52 +30,126 @@ source('lib/drawIntensity.R')
 #source('lib/prepareDataStan.R')
 #source('lib/cleanData.R')
 # Define global variable
-n_sim <- 50
+n_sim <- 1
+num_nodes <- 10
 cut_off <- 3
 obs_time <- 200
 
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
+# cohort_ests <- readRDS("output/sim_ests.RDS")
 
-model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
+model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
+  return(eta1 * x * y * exp(-eta2 * abs(x-y))/(1 + exp(-eta3 *(x-y))))})
+
+model3_fn <- list(alpha.fun = function(x, y, eta1, eta2){
+  return(eta1*x*y*exp(-eta2*abs(x-y)))},
                   q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
                   q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
 
 
 #### Save the simulation parameters ####
 
[…]

### 2021-09-20 run_scripts/sim_rank_isi.R

@@ -1,215 +1,288 @@
 ##### compare inferred rank for simulated data using i&si method
 
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
 
 
-data_path <- "output/rank_sims/sims_m3_dc_isi/sparse/"
-
+data_path <- "output/revisions/aug_run/sim_rank/"
+print(data_path)
 
 jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 jobid <- as.numeric(jobid)
 sim_id <- jobid
 
+print(paste(data_path, "rank_sim", sim_id, ".RDS", sep = ""))
 library(here)
 library(tidyverse)
-library(rstan)
+library(cmdstanr)
 library(compete)
 library(PlayerRatings)
+library(R.utils)
 
 options(mc.cores = parallel::detectCores())
 
-source(here("lib",'uniHawkes.R'))
-source(here("lib","mmhp.R"))
-source(here("lib",'simulatePrediction.R'))
-source(here("lib",'plotUtil.R'))
-source(here("lib",'inferLatentMmhp.R'))
-source(here("lib",'drawIntensity.R'))
-source(here("lib",'myGlicko.R'))
-source(here("lib",'naiveRankHierarchy.R'))
-source(here("lib",'expertRankHierarchy.R'))
+source(here("lib", "uniHawkes.R"))
+source(here("lib", "mmhp.R"))
+source(here("lib", "simulatePrediction.R"))
+source(here("lib", "plotUtil.R"))
+source(here("lib", "inferLatentMmhp.R"))
+source(here("lib", "drawIntensity.R"))
+source(here("lib", "myGlicko.R"))
+source(here("lib", "naiveRankHierarchy.R"))
+source(here("lib", "expertRankHierarchy.R"))
 cut_off <- 3
+num_nodes <- 10
 
-model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
-  return(eta1 * x * y *exp(-eta2 * abs(x - y))/(1 + exp(-eta3 * (x - y) ) ) ) })
+model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3) {
[…]

### 2021-09-20 run_scripts/submit.sh

@@ -1,21 +1,23 @@
 #!/bin/sh
 #
-#SBATCH -A tzsts
-#SBATCH -J cmmhp
+#SBATCH -A stats
+#SBATCH -J dsnl
 #SBATCH -c 4
-#SBATCH -t 720:00
+#SBATCH -t 320:00
 #SBATCH --mem-per-cpu 8gb
-#SBATCH -a 1,2,3
+#SBATCH -a 2-10
 #SBATCH --mail-user=ogw2103@columbia.edu
 #SBATCH --mail-type=ALL
 ##SBATCH -o cmmhp-%A.%a.out
 ##SBATCH --error=cmmhp-%A.%a.err 
 
-module load R
+module load R/4.0.1
 echo "Launching R"
 date
 
-R CMD BATCH --no-save --vanilla c_mmhp.R routput_cmmhp_$SLURM_ARRAY_TASK_ID
+##R CMD BATCH --no-save --vanilla overall_predict.R routput_ov_pred_long$SLURM_ARRAY_TASK_ID
+R CMD BATCH --no-save --vanilla active_dsnl.R routput_active_dsnl_$SLURM_ARRAY_TASK_ID
+echo "Completed"
 echo "Completed"
 date
 

### 2021-09-20 sim_design/check_sims.R

@@ -1,0 +1,218 @@
+library(ggplot2)
+library(bayesplot)
+library(posterior)
+library(here)
+library(tidyverse)
+
+sim_data_path <- here("output", "revisions", "sim_design", "/")
+
+# object_par <- list(sim_lambda_1 = 0.4,
+#                    gamma_var = rep(0.15, num_nodes),
+#                    zeta_var = rep(0.15, num_nodes),
+#                    sim_eta_1 = 3.5,
+#                    sim_eta_2 = 2.6,
+#                    sim_eta_3 = 7.5,
+#                    sim_beta = 2,
+#                    f_vec_1 = seq(from = 0.05, to = 0.95,
+#                                  length.out = num_nodes))
+
+# sim_id <- 10
+# load(paste(sim_data_path,"sim_model3_sim123_",
+#                   sim_id,
+#                   ".RData",sep=''))
+
+# sim_fit1_draws <- sim_model3_stan_sim1
+# sim_fit2_draws <- sim_model3_stan_sim2
+# sim_fit3_draws <- sim_model3_stan_sim3
+
+
+# sim_model3_stan_sim1 <- sim_fit1_draws
+# sim_model3_stan_sim2 <- sim_fit2_draws
+# sim_model3_stan_sim3 <- sim_fit3_draws
+
+
+
+####
+mcmc_trace(sim_fit1_draws, pars =
+             c("f[1]", "f[2]", "f[3]", "f[4]", "f[5]", "f[6]", "f[7]",
+               "f[8]", "f[9]", "f[10]"))
+
+mcmc_trace(sim_fit1_draws, pars =
+             c("eta_1", "eta_2", "eta_3", "beta", "lp__"))
+
+mcmc_trace(sim_fit1_draws, pars = "eta_1") +
+  geom_hline(yintercept = object_par$sim_eta_1)
+
+mcmc_trace(sim_fit1_draws, pars = "eta_2") +
+  geom_hline(yintercept = object_par$sim_eta_2)
+
+mcmc_trace(sim_fit1_draws, pars = "eta_3") +
+  geom_hline(yintercept = object_par$sim_eta_3)
+
+mcmc_trace(sim_fit1_draws, pars = "f[1]") +
+  geom_hline(yintercept = object_par$f_vec_1[1])
+
+mcmc_trace(sim_fit1_draws, pars = "f[2]") +
[…]

### 2021-09-20 sim_design/simulation_design.R

@@ -1,0 +1,310 @@
+### simulation
+source("/moto/stats/users/ogw2103/Code/MMHP_Latent/run_scripts/cluster_setup.R")
+
+jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+jobid <- as.numeric(jobid)
+sim_id <- jobid
+
+library(cmdstanr)
+library(here)
+##library(bayesplot)
+library(R.utils)
+library(dplyr)
+library(compete)
+options(mc.cores = parallel::detectCores())
+
+sim_data_path <- here("output", "revisions", "sim_design", "/")
+
+
+#### Load source code from ../lib/ ####
+source('lib/uniHawkes.R')
+source('lib/mmhp.R')
+source('lib/simulatePrediction.R')
+source('lib/plotUtil.R')
+source('lib/inferLatentMmhp.R')
+source('lib/drawIntensity.R')
+#source('lib/prepareDataStan.R')
+#source('lib/cleanData.R')
+# Define global variable
+n_sim <- 1
+num_nodes <- 10
+cut_off <- 3
+obs_time <- 50
+
+model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
+  return(eta1 * x * y * exp(-eta2 * abs(x-y))/(1 + exp(-eta3 *(x-y))))})
+
+model3_fn <- list(alpha.fun = function(x, y, eta1, eta2){
+  return(eta1*x*y*exp(-eta2*abs(x-y)))},
+  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
+  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
+
+
+#### Save the simulation parameters ####
+
+object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
+  return(eta1*x*y*exp(-eta2*abs(x-y)))},
+  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
+  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
+
+object_par <- list(sim_lambda_1 = 0.6,
+                   gamma_var = seq(from = 0.01, to = 0.2,
+                                   length.out = num_nodes),
+                   zeta_var = c(rep(0.05, num_nodes/2), rep(0.1, num_nodes/2)),
+                   sim_eta_1 = 1, # from 3.5
+                   sim_eta_2 = 2,#1.5, # from 2.6
+                   sim_eta_3 = 3, # this seems better
[…]

### 2021-09-25 output_scripts/Cohort_level_analysis.Rmd
tidying

@@
 ---
-title: "Cohort Level Analysis"
-author: "Owen G. Ward"
+title: "Supplement:Network Hawkes Process Models for Exploring Latent Hierarchy in Social Animal Interactions"
+author: 
 date: '`r Sys.Date()`'
 output:
-  html_document:
-    # toc: true
-    # toc_depth: 1
-    number_sections: true
-    # toc_float: true
-    code_folding: hide
+  # html_document:
+  #   # toc: true
+  #   # toc_depth: 1
+  #   number_sections: true
+  #   # toc_float: true
+  #   code_folding: hide
+  pdf_document
 ---
+
+Here we provide some summary analysis for each of the mice cohorts
+used in this paper. We include analyses for each cohort 
+separately, along with providing some further overall results.
 
@@
 knitr::opts_chunk$set(
-  echo = TRUE, fig.height = 5, fig.width = 7,
+  echo = FALSE, fig.height = 5, fig.width = 7,
   warning = FALSE, cache = TRUE
 )
+# knitr::opts_chunk$set(echo = FALSE) ### for pdf output
 
@@
 }
+
+cohort_mae <- function(current_cohort) {
+  load("../output/revisions/lapl_check/plot_N_predict_revision.RData")
+  temp_plot_df <- predict_day_mae_df_lst[[current_cohort]]
+  temp_plot_df$method <- factor(temp_plot_df$method,
+    levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
+    labels = c("I-MMHP", "DSNL", "C-HP", "C-DCHP", "C-MMHP")
+  )
+  temp_plot_df$day <- factor(temp_plot_df$day)
+  # png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
+  # width=600,height=300)
+
+  plot_cols_pred <- col_df %>%
+    filter(method %in% levels(temp_plot_df$method)) %>%
+    arrange(factor(method, levels = c(
+      "I-MMHP", "DSNL",
+      "C-HP", "C-DCHP", "C-MMHP"
+    ))) %>%
+    pull(cols)
+
+  p3 <- temp_plot_df %>%
+    rowwise() %>%
+    # mutate(norm = min(norm,60)) %>%
+    # rename(Method = method) %>%
+    ggplot(aes(x = method, y = mae, fill = method)) +
+    geom_boxplot(alpha = 0.7) +
+    scale_fill_manual(values = plot_cols_pred) +
+    ggtitle("(a)") +
+    theme_bw() +
+    theme(
+      plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
+      text = element_text(size = 20),
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      legend.position = "right"
+    ) +
+    facet_grid(cols = vars(day)) +
+    xlab("Prediction horizon (day)") +
+    ylab("MAE") +
+    ylim(0, 5) + # aren't infinite but >150 and <200
+    NULL
+  p3 + labs(fill = "Method", title = "Single Cohort",
+            subtitle = paste("Cohort", current_cohort, sep = " "))
+}
+
 ```
@@
 
-Here all events which are classified as inactive by the C-MMHP model
-originate from the top ranked animal. As such there is strong
-agreement between the win/loss matrix of all events and
-those ocurring in active periods, with the 
-restriction to only active events
-slightly decreasing the 
-influence of the top ranked animal.
+<!-- Here all events which are classified as inactive by the C-MMHP model -->
+<!-- originate from the top ranked animal. As such there is strong -->
+<!-- agreement between the win/loss matrix of all events and -->
+<!-- those ocurring in active periods, with the  -->
+<!-- restriction to only active events -->
+<!-- slightly decreasing the  -->
+<!-- influence of the top ranked animal. -->
 
@@
 
-Examing the correlation matrices of both the median ranks for
-each of our cohort models and the Spearman rank correlations,
-we see that the C-HP most agrees with the I&SI ranking,
-with the C-DCHP and C-MMHP models showing progressively less agreement.
+<!-- Examining the correlation matrices of both the median ranks for -->
+<!-- each of our cohort models and the Spearman rank correlations, -->
+<!-- we see that the C-HP most agrees with the I&SI ranking, -->
+<!-- with the C-DCHP and C-MMHP models showing progressively less agreement. -->
 
@@
 
-We next plot the inferred posterior rank estimates from 
-each of our cohort models and the comparison AggRank model,
-where we order the animals by the estimated I&SI ranking.
+<!-- We next plot the inferred posterior rank estimates from  -->
+<!-- each of our cohort models and the comparison AggRank model, -->
+<!-- where we order the animals by the estimated I&SI ranking. -->
 
@@
 
-Similarly, to show how this rank differs from that obtained by the C-MMHP
-model, we order the animals by the inferred ranking from that
-model.
+<!-- Similarly, to show how this rank differs from that obtained by the C-MMHP -->
+<!-- model, we order the animals by the inferred ranking from that -->
+<!-- model. -->
 
@@
 
-For each of our three proposed models, we show the parameter
-estimates for the non rank parameters, including the in and
-out degree estimates for the models which incorporate degree
-corrections.
+<!-- For each of our three proposed models, we show the parameter -->
+<!-- estimates for the non rank parameters, including the in and -->
+<!-- out degree estimates for the models which incorporate degree -->
+<!-- corrections. -->
 
@@
 ### Summary Table
-
-Finally, for each animal in this cohort, we summarise
 
@@
 ```
+
+<!-- ### Cohort MAE -->
+
+<!-- ```{r mae-cohort-1} -->
+<!-- cohort_mae(current_cohort) -->
+<!-- ``` -->
 
@@
   geom_point() +
-  labs(y = "Percent fights Active", x = "Correlation Differernce",
+  labs(y = "Percent fights Active", x = "Correlation Difference",
        subtitle = "Correlation difference between C-HP/C-DCHP and C-HP/C-MMHP")

### 2021-09-25 output_scripts/Paper_Plots.Rmd
tidying

@@
 extra_plots <- FALSE
+fig4 <- FALSE
 
@@
 
-data_path <- "../output/revisions/lapl_check/"
-
 load(paste(data_path, cohort_names[current_cohort],
@@
 
-```{r fig-3a-baseline-rate, fig.width=5, fig.height=5, eval=revision_plots}
+```{r fig-3a-baseline-rate, fig.width=5, fig.height=5}
 current_cohort <- 5
@@
 xLabels = expert_rank_10[[current_cohort]],
-yLabels = rev(expert_rank_10[[current_cohort]]),
-title = "(a)" )
+yLabels = rev(expert_rank_10[[current_cohort]]))
+mtext(text="(a)",
+      side = 3,
+      line = 0.5,
+      outer = TRUE,
+      cex = 2.5,
+      font = 2)
 # mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
@@
 current_cohort <- 5
-data_path <- "../output/revisions/lapl_check/"
 ## 2 and 8 maybe look better
@@
   yLabels = rev(expert_rank_10[[current_cohort]]),
-  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
+  min = -90, max = 90, axis_cex = 1.6, title_cex = 1.8,
   colorPalette = "RdBu", if.emp = FALSE,
@@
   # title_lst = list("I-MMHP"),
-  col_axis = c(-80, -40, 0, 40, 80), fake_matrix = TRUE,
+  col_axis = c(-90, -45, 0, 45, 90), fake_matrix = TRUE,
   matrix.mar = c(2.5, 2.5, 2.5, 1)
@@
 
-```{r fig-4a, eval = revision_plots, message=FALSE, warning=FALSE}
+```{r fig-4a, eval = fig4, message=FALSE, warning=FALSE}
 sim_data_path <- here("output", "revisions", "aug_run", "sims", "/")
@@
 
-```{r prepare data for 4b,cache=TRUE, eval=TRUE}
+```{r prepare data for 4b,cache=TRUE, eval=fig4}
 plot.s <- 26 # 8 is pretty good
@@
 
-```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4, eval=TRUE}
+```{r fig-4b-recover-latent-states,fig.width=8,fig.height=4, eval=fig4}
 mmhp_lty <- 1
@@
 
-```{r fig-4b, eval=TRUE}
+```{r fig-4b, eval=fig4}
 layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 2.5), 3))
@@
 
-```{r data for fig 5,cache=TRUE, eval=revision_plots}
+```{r data for fig 5,cache=TRUE, eval=FALSE}
 n_sim <- 50
@@
 
-sim_data_path <- here("output", "revisions", "lapl_check", "sim_lapl", "/")
+sim_data_path <- here("output", "revisions", "aug_run", "sims", "/")
 
@@
                              "revisions",
-                             "lapl_check",
+                             "aug_run",
                              "sim_rank/"), 
@@
     "revisions", 
-    "lapl_check",
+    "aug_run",
     "sim_rank",
@@
 
-## Figure 6a: Rank vs I&SI
-
-```{r fig-6a-rank-vs-isi}
+## Figure 6a: Rank vs I&SI Cohort 5
+
+```{r fig-6a-rank-vs-isi-cohort5}
 ### Rank Comparison for Single Cohort ####
@@
 
-## Figure 6b: Spearman rank correlation
-
-```{r fig-6b-overall-rank-correlation}
-load("../output/revisions/lapl_check/weighted_rank_data.RData")
+## Figure 6b: Rank vs I&SI Cohort 3
+
+```{r fig-6b-rank-vs-isi-cohort3}
+### Rank Comparison for Single Cohort ####
+current_cohort <- 3
+# want to update this now
+# data_path
+
+load(paste(data_path, cohort_names[current_cohort],
+  "/agg_rank_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+load(paste(data_path, cohort_names[current_cohort],
+  "/cohort_hp_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+load(paste(data_path, cohort_names[current_cohort],
+  "/cohort_dchp_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+load(paste(data_path, cohort_names[current_cohort],
+  "/cohort_mmhp_stan_result_", cohort_names[current_cohort],
+  ".RData",
+  sep = ""
+))
+
+no_method <- 4
+plot_latent_df <- data.frame(
+  Methods = rep(1:no_method, each = 1000 * mice_number),
+  Mice = rep(rep(1:mice_number, each = 1000), no_method),
+  force = rep(0, 1000 * mice_number * no_method)
+)
+## agg
+x_draws <- sim_agg_rank %>% select(starts_with("x"))
+plot_latent_df$force[(1:(1000 * mice_number))] <-
+  as.vector(as.matrix(x_draws))
+
+## M1
+f_draws <- sim_cohort_hp %>% select(starts_with("f"))
+plot_latent_df$force[(1:(1000 * mice_number)) +
+                       1000 * mice_number] <- as.vector(as.matrix(f_draws))
+
+## M2
+f_draws <- sim_cohort_dchp %>% select(starts_with("f"))
+plot_latent_df$force[(1:(1000 * mice_number)) + 
+                       2000 * mice_number] <- as.vector(as.matrix(f_draws))
+
+## M3
+f_draws <- sim_cohort_mmhp %>% select(starts_with("f"))
+plot_latent_df$force[(1:(1000 * mice_number)) + 
+                       3000 * mice_number] <- as.vector(as.matrix(f_draws))
+
+plot_latent_df$Mice <- factor(plot_latent_df$Mice,
+  levels = expert_rank_10[[current_cohort]]
+)
+plot_latent_df$Method <- factor(plot_latent_df$Method,
+  labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP")
+)
+
+# png(paste(plot_path,"real_rank_one_cohort.png",sep=""),width=600,height=300)
+plot_cols <- col_df %>%
+  filter(method %in% c(
+    "AggRank", "C-HP",
+    "C-DCHP", "C-MMHP"
+  )) %>%
+  pull(cols)
+
+p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
+  geom_boxplot(alpha = 0.7) +
+  scale_fill_manual(values = plot_cols) +
+  ggtitle("(a)") +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
+    text = element_text(size = 20),
+    axis.text.x = element_text(size = 10),
+    legend.position = "none"
+  ) +
+  facet_grid(cols = vars(Method)) +
+  xlab("Mice (ranked by I&SI method)") +
+  ylab("Latent rank")
+p1
+# dev.off()
+current_cohort <- 5
+```
+
+```{r fig-6b-overall-rank-correlation, eval=FALSE}
+load("../output/revisions/aug_run/weighted_rank_data.RData")
 # png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
@@
 
-```{r fig-8a-mae-norm-cohort5, fig.width=8,fig.height=4,eval=TRUE}
-load("../output/revisions/lapl_check/plot_N_predict_revision.RData")
+```{r fig-8a-mae-norm-cohort5,eval=TRUE}
+load("../output/revisions/aug_run/plot_N_predict_revision.RData")
 current_cohort <- 5 # cohort 1 looks worse than rest
@@
 
-```{r fig-7a-pred-all-cohorts-box-mae,eval=TRUE, fig.width=8, fig.height=4}
+```{r fig-7a-pred-all-cohorts-box-mae,eval=TRUE}
 ### updated to revision
-load("../output/revisions/lapl_check/plot_N_predict_revision.RData")
+load("../output/revisions/aug_run/plot_N_predict_revision.RData")
 
@@
           "revisions",
-          "lapl_check",
+          "aug_run",
           "plot_rank_predict.RData"))
@@
 ```{r fig-7b-pred-rank-spearman-all-cohorts}
-load("../output/revisions/lapl_check/plot_rank_predict.RData")
+load("../output/revisions/aug_run/plot_rank_predict.RData")
 
@@
   all_cohort_rank_df,
-  aes(x = method, y = spearman, fill = method)
-) +
+  aes(x = method, y = spearman,
+      fill = method)) +
   # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +

### 2021-09-25 lib/matrixPlotParameter.R

@@ -264,7 +264,7 @@ my.image.plot <- function(..., add = FALSE, xlab = NULL, ylab = NULL,
 # ----- Define a function for plotting multiple matrices ----- #
 myMultiMatrixPlot <- function(X, xLabels, yLabels, min, max, colorPalette, no_matrix, n_row,
                               if.emp = TRUE, emp.ROW, emp.COL, emp.color, title_lst, reverse.col = TRUE,
-                              title_cex = 2.8, axis_cex = 2.2, col_axis, fake_matrix = TRUE, out.title = NULL,
+                              title_cex = 2.8, axis_cex = 1.1, col_axis, fake_matrix = TRUE, out.title = NULL,
                               matrix.mar = NULL, legend.mar = NULL, title.line = NULL) {
   if (is.null(matrix.mar)) {
     if (is.null(out.title)) {

### 2021-12-28 output_scripts/Paper_Plots.Rmd
tidy up repo some more. delete files which aren't needed, rename some to be more standard

--- 2021-09-20 output_scripts/Paper_Plots.Rmd
@@
 
-data_path <- "../output/revisions/lapl_check/"
+# data_path <- "../output/revisions/lapl_check/"
 
@@
 ```{r fig-8a-mae-norm-cohort5, fig.width=8,fig.height=4,eval=TRUE}
-load("../output/revisions/lapl_check/plot_N_predict_revision.RData")
+load("../output/revisions/aug_run/plot_N_predict_revision.RData")
 current_cohort <- 5 # cohort 1 looks worse than rest
@@
 ### updated to revision
-load("../output/revisions/lapl_check/plot_N_predict_revision.RData")
+load("../output/revisions/aug_run/plot_N_predict_revision.RData")
 

### 2021-12-28 run_scripts/c_mmhp_dc.R

@@ -101,7 +101,7 @@ print(paste("Cohort", current_cohort))
 #### fit the stan model ####
 # print(paste("Cohort", current_cohort))
 # 
-dc_model <- cmdstan_model("lib/model3_dc_lapl_aug.stan")
+dc_model <- cmdstan_model("lib/model3.stan")
 # 
 stan_input_lst <- prepareDataStan(current_cohort)
 stan_input_lst$alpha_id <- expert_rank_10[[current_cohort]][1]

### 2021-12-28 run_scripts/comm_rate_run/agg_rank.R

@@ -1,113 +1,0 @@
-# this file refits the corrected aggregate ranking model
-# with unconstrained parameters b and c
-
-
-
-### code ###
-## run this section if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
-# ### set cohort_id based on job num
-jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
-jobid <- as.numeric(jobid)
-cohort_id <- jobid
-#cohort_id <- 1
-#####
-
-save_data_path <- "output/common_rate/"
-
-
-library(rstan)
-options(mc.cores = parallel::detectCores())
-
-
-library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
-library(dplyr)
-#library(R.utils)
-#library(fields)
-
-
-
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
-source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
-
-
-
-
-
-#### then load in the data here ###
-
-full_data <- readRDS("data/mice.RData")
-# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
-cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cut_off <- 3
-mice_number <- 12
-
-
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
-
[…]

### 2021-12-28 run_scripts/comm_rate_run/c_dchp.R

@@ -1,204 +1,0 @@
-### fit degree corrected cohort hawkes process
-
-### code ###
-# run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
-# ### set cohort_id based on job num
-jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
-jobid <- as.numeric(jobid)
-cohort_id <- jobid
-
-save_data_path <- "output/common_rate/"
-library(rstan)
-options(mc.cores = parallel::detectCores())
-
-
-library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
-library(dplyr)
-#library(R.utils)
-#library(fields)
-
-
-
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
-source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
-
-
-
-
-#### then load in the data here ####
-
-full_data <- readRDS("data/mice.RData")
-# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
-cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cut_off <- 3
-mice_number <- 12
-
-
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
-
-model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
-                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
[…]

### 2021-12-28 run_scripts/comm_rate_run/c_hp.R

@@ -1,211 +1,0 @@
-### fit cohort hawkes process
-
-### code ####
-# #run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
-# ### set cohort_id based on job num
-jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
-jobid <- as.numeric(jobid)
-cohort_id <- jobid
-#cohort_id <- 1
-#####
-
-save_data_path <- "output/common_rate/"
-
-library(rstan)
-options(mc.cores = parallel::detectCores())
-
-
-library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
-library(dplyr)
-#library(R.utils)
-#library(fields)
-
-
-
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
-source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
-
-
-
-
-
-#### then load in the stan fit here ###
-
-full_data <- readRDS("data/mice.RData")
-# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
-cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cut_off <- 3
-mice_number <- 12
-
-
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
-
-model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
[…]

### 2021-12-28 run_scripts/comm_rate_run/c_mmhp.R

@@ -1,374 +1,0 @@
-# this file refits the complete C-MMHP model
-# including prediction and Pearson residuals for each cohort
-#
-
-### code ###
-## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
-# ### set cohort_id based on job num
-jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
-jobid <- as.numeric(jobid)
-cohort_id <- jobid
-#cohort_id <- 1
-####
-save_data_path <- "output/common_rate/"  #"output_june30/"
-
-### specify the number of segments here
-no_segments <- 500
-
-library(rstan)
-options(mc.cores = parallel::detectCores())
-
-
-library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
-library(dplyr)
-#library(R.utils)
-#library(fields)
-
-
-
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
-source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
-
-
-
-
-
-#### load the data ####
-full_data <- readRDS("data/mice.RData")
-# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
-cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cut_off <- 3
-mice_number <- 12
-
-
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
-
[…]

### 2021-12-28 run_scripts/comm_rate_run/cluster_setup.R

@@ -1,5 +1,0 @@
-### script to be sourced to run on the cluster
-
-
-.libPaths("/rigel/stats/users/ogw2103/rpackages")
-setwd("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/")

### 2021-12-28 run_scripts/comm_rate_run/diagnostics.R

@@ -1,417 +1,0 @@
-### Diagnostics at a cohort level ####
-
-### Construct cohort level diagnostic statistics for model fit for each of the
-### 4 models (c-hp,dc-hp,c-mmhp,i-mmhp) fit in this paper
-
-
-### code ###
-## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
-### set cohort_id based on job num
-jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
-jobid <- as.numeric(jobid)
-cohort_id <- jobid
-# cohort_id <- 1
-####
-data_path <- "output/common_rate/"
-
-
-# library(rstan)
-# options(mc.cores = parallel::detectCores())
-
-
-library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
-library(dplyr)
-#library(R.utils)
-#library(fields)
-
-
-
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
-source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
-
-
-
-
-
-
-#### then load in the data ####
-
-full_data <- readRDS("data/mice.RData")
-# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
-cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cut_off <- 3
-mice_number <- 12
-
-
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
-
[…]

### 2021-12-28 run_scripts/comm_rate_run/dsnl.R

@@ -1,157 +1,0 @@
-#### Fit the dsnl model ####
-
-
-### code ###
-## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
-# ### set cohort_id based on job num
-jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
-jobid <- as.numeric(jobid)
-cohort_id <- jobid
-# cohort_id <- 1
-####
-save_data_path <- "output/common_rate/"
-
-library(rstan)
-options(mc.cores = parallel::detectCores())
-
-
-library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
-library(dplyr)
-#library(R.utils)
-#library(fields)
-
-
-
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
-source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
-
-
-
-
-
-
-#### then load in the data ###
-
-full_data <- readRDS("data/mice.RData")
-# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
-cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cut_off <- 3
-mice_number <- 12
-
-
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
-
-model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
[…]

### 2021-12-28 run_scripts/comm_rate_run/i_mmhp.R

@@ -1,326 +1,0 @@
-# this file refits the complete I-MMHP model
-# including prediction and Pearson residuals for each cohort
-
-
-### code ###
-## run this section if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
-source("run_scripts/cluster_setup.R")
-### set cohort_id based on job num
-jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
-jobid <- as.numeric(jobid)
-cohort_id <- jobid
-#cohort_id <- 1
-#####
-
-save_data_path <- "output/common_rate/"
-
-no_segments <- 500
-
-library(rstan)
-options(mc.cores = parallel::detectCores())
-
-
-library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
-library(dplyr)
-#library(R.utils)
-#library(fields)
-
-
-
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
-source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
-
-
-
-
-
-#### then load in the data here ###
-
-full_data <- readRDS("data/mice.RData")
-# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
-cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cut_off <- 3
-mice_number <- 12
-
-
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
-
[…]

### 2021-12-28 run_scripts/comm_rate_run/overall_predict.R

@@ -1,512 +1,0 @@
-### Predictions at overall level ####
-
-
-### code ###
-## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
-# ### set cohort_id based on job num
-# jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
-# jobid <- as.numeric(jobid)
-# cohort_id <- jobid
-# cohort_id <- 1
-####
-data_path <- "output/common_rate/"
-
-library(rstan)
-options(mc.cores = parallel::detectCores())
-
-library(PlayerRatings)
-library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-library(wCorr)
-#library(tidyverse)
-library(dplyr)
-#library(R.utils)
-#library(fields)
-
-
-
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
-source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
-
-
-
-
-
-
-#### then load in the data  ####
-
-full_data <- readRDS("data/mice.RData")
-# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
-cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cut_off <- 3
-mice_number <- 12
-
-
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){
-  return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))
-  })
-
-model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){
[…]

### 2021-12-28 run_scripts/comm_rate_run/predict.R

@@ -1,264 +1,0 @@
-### Predictions at a cohort level ####
-
-
-### code ###
-## run this if running on the cluster
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
-### set cohort_id based on job num
-jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
-jobid <- as.numeric(jobid)
-cohort_id <- jobid
-#cohort_id <- 1
-####
-data_path <- "output/common_rate/"
-
-
-library(rstan)
-options(mc.cores = parallel::detectCores())
-
-
-library(compete)
-#library(RColorBrewer)
-#library(Hmisc)
-#library(wCorr)
-#library(tidyverse)
-library(dplyr)
-library(R.utils)
-#library(fields)
-
-
-
-source('lib/naiveRankHierarchy.R')
-source('lib/expertRankHierarchy.R')
-source('lib/cleanData.R') 
-source('lib/prepareDataStan.R') 
-source('lib/inferLatentMmhp.R')
-source('lib/plotUtil.R') 
-source('lib/mmhp.R')
-source('lib/uniHawkes.R')
-source('lib/simulatePrediction.R')
-source('lib/myGlicko.R')
-source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")
-source('lib/matrixPlotParameter.R')
-source('lib/residualStructureScore.R')
-
-
-
-
-
-
-#### then load in the data ####
-
-full_data <- readRDS("data/mice.RData")
-# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
-cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
-cut_off <- 3
-mice_number <- 12
-
-
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
-
-model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
[…]

### 2021-12-28 run_scripts/comm_rate_run/sim_fits.R

@@ -1,247 +1,0 @@
-#### Rerun the modified simulation fits based on the modified Stan models ####
-
-
-#### if running on cluster ####
-source("/rigel/stats/users/ogw2103/code/MMHP/MMHP_Latent/run_scripts/cluster_setup.R")
-
-data_path <- "output/common_rate/sims_m3/"
-
-library(rstan)
-options(mc.cores = parallel::detectCores())
-jobid <- Sys.getenv("SLURM_ARRAY_TASK_ID")
-jobid <- as.numeric(jobid)
-sim_id <- jobid
-
-#Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
-
-
-#### Load source code from ../lib/ ####
-source('lib/uniHawkes.R')
-source('lib/mmhp.R')
-source('lib/simulatePrediction.R')
-source('lib/plotUtil.R')
-source('lib/inferLatentMmhp.R')
-source('lib/drawIntensity.R')
-#source('lib/prepareDataStan.R')
-#source('lib/cleanData.R')
-# Define global variable
-n_sim <- 50
-cut_off <- 3
-
-model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})
-
-model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
-                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
-                  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
-
-
-#### Save the simulation parameters ####
-
-object_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
-                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
-                  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})
-
-object_par <- list(sim_lambda_0 = 0.08,
-                   sim_lambda_1 = 0.16,
-                   sim_eta_1=2.5,
-                   #gamma_var = c(0.01, 0.02, 0.03, 0.06, 0.07),
-                   #zeta_var = c(0.075, 0.02, 0.03, 0.05, 0.08),
-                   sim_eta_2 = 0.6,
-                   sim_eta_3 = 5,
-                   sim_beta = 1.5,
[…]

### 2021-12-28 run_scripts/comm_rate_run/submit.sh

@@ -1,22 +1,0 @@
-#!/bin/sh
-#
-#SBATCH -A tzsts
-#SBATCH -J cmmhp
-#SBATCH -c 4
-#SBATCH -t 720:00
-#SBATCH --mem-per-cpu 8gb
-#SBATCH -a 1,2,3
-#SBATCH --mail-user=ogw2103@columbia.edu
-#SBATCH --mail-type=ALL
-##SBATCH -o cmmhp-%A.%a.out
-##SBATCH --error=cmmhp-%A.%a.err 
-
-module load R
-echo "Launching R"
-date
-
-R CMD BATCH --no-save --vanilla c_mmhp.R routput_cmmhp_$SLURM_ARRAY_TASK_ID
-echo "Completed"
-date
-
-#end of script
